### 2023-09-29 documentation/paper/main.tex
mv docs

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[ngerman]{babel}
\usepackage[acronym]{glossaries}
%\usepackage{setspace}
\makeglossaries
\newacronym{sg}{SG}{Serious Games}
\newacronym{xr}{XR}{Extended Reality}
\newacronym{vr}{VR}{Virtual Reality}
\newacronym{ar}{AR}{Augmented Reality}
\newacronym{cg}{CG}{Computer Grafik}
\newacronym{gbl}{GBL}{Game-Based Learning}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Anwendung des Serious Gamings mittels erweiterter Realität in der hochschuldidaktischen Lehre\\
%{\footnotesize \textsuperscript{*}Wissenschaftliches Arbeiten WS2021/2022 Fachhochschule Aachen}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Marcel Werner Heinrich Friedrich Ochsendorf}
\IEEEauthorblockA{\textit{Fachhochschule Aachen} \\
\textit{Fachbereich 5 Elektrotechnik und Informationstechnik}\\
Aachen, Deutschland \\
marcel.ochsendorf@alumni.fh-aachen.de}
%\and
}

\maketitle

%-----------------------------------------------------------------------------------------------------------------------------------------------
% \gls{uscf}
\begin{abstract}
Die Integration moderner Medien in die hochschuldidaktische Lehre hat seit der Jahrtausendwende stetig an Bedeutung gewonnen.
Dieses Papier zeigt eine Möglichkeit zur Vermittlung von Wissen und die Motivation zum Lernen mittels \gls{xr} am Beispiel der Vorlesung
\gls{cg} basierend auf den Erkenntnissen von bereits etablierten Lösungen.
Wissen soll hierbei durch softwarebasierte Spiele, den \gls{sg}, vermittelt werden.
Anders als bei existierenden 2D Display-Anwendungen werden bei \gls{xr} visuelle Informationen mittels virtuellen Umgebungen, Objekten und Interaktionen mit diesen vermittelt.
Die Studierenden können Situationen aus einem Blickwinkel ihrer Wahl erkunden und erlernen und können zudem durch Wiederholen von Aufgaben in verschiedenen Blickwinkeln
ihr Wissen anpassen.
Meist ohne unterstützende Lehrkörper werden Studierende innerhalb dieser Umgebung einzeln oder in Gruppen mit Aufgaben und Informationen konfrontiert,
welche die Interaktions- und Imaginationsinstinkte ansprechen.
Insbesondere die untersuchte Lehrveranstaltung \gls{cg} ermöglicht viele Umsetzungen des \gls{sg}-Ansatzes, da technologische Themenbereiche und die grafischen Unterschiede
mittels \gls{xr} hervorgehoben werden können.
\end{abstract}

\begin{IEEEkeywords}
Serious Gaming (\gls{sg}), \gls{vr}, Extended Reality (\gls{xr}), Computer Grafik (\gls{cg})
\end{IEEEkeywords}

\section{Einleitung}
Die Anwendung von 3D-Technologien und virtuellen Umgebungen hat in der Vergangenheit stark zugenommen
und wird erheblich weiter steigen, wie Statistiken aus den USA zeigen\cite{eduxrvrar2020usa}.
Die Variationen und Möglichkeiten der \gls{vr}-Technologien werden durch das rapide Wachstum von schneller und erschwingliche Hardware, Software und Netzwerken begünstigt\cite{evallearningmixedreality2020}.
Mit Veränderungen des alltäglichen Umfelds und dem wachsenden Umfang von Wissen muss sich auch die Lehre diesen Veränderungen anpassen und kann daraus auch
Nutzen ziehen.
\gls{gbl} nutzt jene Technologien, um Lehrinhalte und Informationen spielerisch an Nutzer, in diesem Falle Studierende, zu vermitteln und somit die
Motivation zum Lernen zu steigern.
Die Möglichkeiten der Umsetzung sind vielfältig und bieten verschiedene Vor- und Nachteile.
Die Umsetzung ist komplex, da anders als bei 2D-Display-Anwendungen die \gls{xr}-Technologien zusammen mit Interaktionsoptionen für jeden Studierenden
die finanzielle Belastung selten aufgebracht werden kann. Für ein einzelnes Fach ist der Aufwand groß. Zudem ist die Umsetzung insbesondere für mehrere Studierende zeitintensiver.
Die Ergebnisse für die Lehre sind fast ausschließlich positiv und werden in der Evaluation dieses Papiers gesondert beleuchtet.
Studierende reflektieren erlerntes Wissen besser und nehmen den Lehrprozess positiver wahr;
mehr als Zweidrittel der Studierenden befürworten eine verstärkte Integration von \gls{xr} in der Lehre\cite{a7}.\\

Im Folgenden werden die verschiedenen Begriffe definiert und voneinander abgegrenzt;
anschließend werden Möglichkeiten des Einsatzes von \gls{xr} in der Lehre der \gls{cg} der Fachhochschule Aachen vorgestellt.

%-----------------------------------------------------------------------------------------------------------------------------------------------
%ERLÄUTERUNGEN

\section{Serious Gaming und extended Reality Technologien}

Um \gls{sg} in der Lehre der \gls{cg} evaluieren und einsetzen zu können, werden zuerst die Themenbereiche voneinander abgegrenzt und erläutert.

\subsection{Game-Based Learning (\gls{gbl})}
Mittels \gls{gbl} soll spielerisch Wissen vermittelt werden. Man unterscheidet in Board Game Simulations und Digital \gls{gbl}.
Erstere sind rein haptische und nicht digitale Spiele, wie beispielsweise Schach, welches strategisches Denken lehrt und fördert.
Letztere beinhalten die Wissensvermittlung mittels digitaler Möglichkeiten und ermöglichen genau wie Ersteres regelbasiert Aktionen und Interaktionen,
durch den digitalen Anteil ist die Varianz deutlich erhöht und die Komplexität wird gesteigert.
Zudem können zusätzliche Komponenten, wie Ton, Bild oder Reaktionen verwendet und die Aufmerksamkeit des Anwenders gesteuert werden.
Der Lernprozess soll durch das Spielen nicht nur kognitiv, sondern durch eine Vielzahl an Sinnesorganen angesprochen werden, sodass die Erinnerungsleistung der
synaptischen Repräsentation im Gehirn erhöht wird\cite{fabulagames}.
Mittels digitaler Medien kann zudem das Spiel dezentral und / oder vernetzt umgesetzt werden\cite{a3}.

\begin{figure}[htbp]
\centerline{\includegraphics[width=8cm]{serious-games.png}}
\caption{Definition Serious Games.\cite{a10}}
\label{sgdef_fig}
\end{figure}

\subsection{Serious Gaming (\gls{sg})}
Mit dem Ziel der Vermittlung von Inhalten und Kompetenzen sind \gls{sg}s, Instrumente zur Wissensvermittlung (s. Abbildung \ref{sgdef_fig}).
Wörtlich übersetzt bedeutet es ``Spiel mit ernsthaftem (Lern-)Ziel''.
Unterhaltung ist nur ein untergeordnetes Ziel dieser Spiele, jedoch nicht unbedeutend, da der Anwender im Spiel motiviert werden soll.
Einerseits kann erlerntes Wissen vertieft und wiederholt und andererseits neues Wissen erlernt werden.
Es ist zu beachten, dass \gls{sg} auch 2D und / oder nicht \gls{xr}-basierende Spiele beinhaltet.
Demnach können auch nicht digitale Spiele, wie Board Game Simulations, den \gls{sg} zugeordnet werden.
Nachfolgend wird den \gls{sg}s nur in Bezug auf \gls{xr}-basierte Spiele betrachtet.
Nicht digitale oder Spiele für 2D Ausgabegeräte werden hierbei nicht berücksichtigt.

\begin{figure}[htbp]
\centerline{\includegraphics[width=9cm]{ibm_ar.png}}
\caption{Zusammenhang von \gls{xr} zu \gls{vr} und \gls{ar}.\cite{a9}}
\label{xrvrar_fig}
\end{figure}

\subsection{Extended Reality (\gls{xr})}
\gls{xr} (oder auch Cross Reality) ist eine Sammelbezeichnung für alle Kombinationen aus realen und virtuellen Umgebungen,
welche mittels Technologien erzeugt und über Mensch-Maschine-Interaktion gesteuert werden.
Dies schließt auch alle zukünftigen Technologien ein.
Mittels dieser Technologien und zugehörigen Computerprogrammen werden virtuelle, mehrdimensionale Umgebungen erzeugt (\gls{vr}) oder virtuelle Komponenten
der realen Umgebung ergänzt (\gls{ar}) (s. Abbildung \ref{xrvrar_fig}).
Die visuelle Wahrnehmung lässt Umgebungen real erfahren und spricht vermehrt sensorische Reize an.
Werden \gls{xr} als Basis für \gls{sg} verwendet, können diese Reize angesprochen und somit langfristig Informationen und detaillierteres Wissen vermittelt und
vom Gehirn gespeichert werden. Dies verbessert die Qualität des \gls{sg}, bedarf aber eines höheren Aufwands in Vorbereitung und Umsetzung als 2D oder nicht digitale Spiele.

\subsection{Lehrveranstaltung Computergrafik (\gls{cg})}
Im Allgemeinen beschreibt die Lehrveranstaltung \gls{cg} die Modellierung und Erzeugung virtueller Welten, sowie deren Abbildung bzw. Projektion auf 2D-Bilder. Es wird der Informatik zugeordnet.
Die Modellierung und Kombination von komplexen Geometrien und Formen und auch die Berechnung dieser Komponenten sind Teil der \gls{cg}.
Grafische Grundfunktionen, wie Farbdarstellungen oder simple Geometrien, sind Basis dieser Modellierungen.
Beschrieben werden alle diese Modellierungen durch diverse mathematische und computergestützte Algorithmen.
Zudem beinhaltet es die Darstellung von Objekten und Umgebungen in der Ebene, sowie die Abbildung von 3D Umgebungen auf 2D Medien.
Die Computergrafik ist Basis aller \gls{xr} Technologien.
Unabhängig davon, ob einzelne virtuelle Objekte dargestellt werden sollen oder vollständige Umgebungen erzeugt werden, müssen alle Bestandteile
mittels \gls{cg} berechnet und modelliert werden.

Nachfolgend wird ein Beispiel analysiert, welche die hochschuldidaktische Lehre der \gls{cg} mittels \gls{sg} und \gls{xr} unterstützen und fördern kann.

%-----------------------------------------------------------------------------------------------------------------------------------------------
%METHODIKEN

\section{Auswahl an verfügbaren Methoden der \gls{sg}-gestützten Lehre}

Die Variationen an Möglichkeiten der \gls{xr}-gestützten hochschuldidaktischen Lehre ist enorm und wächst stetig an\cite{eduxrvrar2020usa}.
Die Auswahl der verfügbaren und angewendeten Methodiken ist derzeit noch begrenzt.
2D \gls{sg} wird bereits als Lehrmedium verwendet, \gls{xr}-gestützte Medien sind seltener vertreten; 
beide Medien werden zukünftig mehr Einfluss auf die Lehre haben.
Das Besondere an der Integration von \gls{xr} in der Lehre ist die Tatsache,
dass die Lehre der \gls{cg} die Erstellung von \gls{xr} und computergestützten Bildern beschreibt.
Das bedeutet, es kann mithilfe des Mediums selbst den Studierenden vermittelt werden, wie \gls{xr} erstellt und angewendet wird.
Die Bilder und Szenen, die das \gls{sg} den Studierenden mittels \gls{xr} zeigt, sollen beschreiben, wie \gls{xr} funktioniert.
Es bildet somit einen Kreislauf aus der Verwendung von \gls{cg} Inhalten und der Erklärung wie diese Inhalte erstellt werden können.
Anders als in anderen Themenbereichen, wo die Verwendung der \gls{xr} Technologien nur Mittel zum Zweck ist, kann das Mittel hierbei auch die Lehre mitgestalten.

\subsection{2D \gls{sg} Lösung in der hochschuldidaktischen Lehre am Beispiel der Business Simulation \gls{sg}}

Eine Variante der \gls{sg} sind Business Simulation Anwendungen.
Diese sind oft als Planspiel ausgeführt und bieten sich insbesondere in den Lehrveranstaltungen der Wirtschaftswissenschaften an.
Allgemein sind diese i. d. R. als Browser-basierte Varianten ausgeführt und die Benutzerinteraktion beschränkt sich dabei meistens auf das Ausfüllen von Textfeldern und das Lesen von Texten\cite{a11}.
Der \gls{sg} Aspekt entsteht dabei durch das Spielen im Team und gegen gegnerische Teams.
Die Hochschule Osnabrück setzt in der Wirtschaftslehre \gls{sg} bereits erfolgreich ein\cite{a3}.
Studierende werden einzeln oder in Gruppen mit Inhalten konfrontiert, müssen Vorträge halten, für imaginäre Unternehmen Berichte und Protokolle verfassen und ihren
Lernfortschritt festhalten und individuell verbessern\cite{a3}.
Das \gls{sg} kann auch über Kontinente hinweg in verschiedenen Sprachen stattfinden. Somit entsteht nicht nur eine Interaktion mit anderen Studierenden aus der Lehrveranstaltung,
sondern die einzelnen Teilnehmer, das Erlernen von Fachbegriffen und der Umgang mit unternehmensbezogenen Situationen und Aufgaben stehen dabei im Vordergrund\cite{a3}.
Die Spiele werden dabei von der Hochschule erworben, dazu gehören insbesondere die Anbieter TOPSIM, SIMCON GmbH und McGraw-Hill Education, Inc\cite{a3}.
Die Fachhochschule Aachen verwendet ebenfalls TOPSIM im Bereich der Wirtschaftslehre für Informatiker und Ingenieure.
Der Anbieter TOPSIM bietet Cloud-basierte Browser-Anwendungen, bei welchen sich der Nutzer anmeldet, um am 2D Spiel teilzunehmen.
Auch gedruckte Ausgaben sind möglich. Eine \gls{xr} Integration oder Umsetzung ist bisher nicht vorgesehen.
Die Lehrenden der Hochschule Osnabrück konnten eine Verbesserung unter den Studierenden feststellen, die ohne \gls{sg} weniger hervorragende Leistungen erbringen.
Leistungsstärkere Studierende profitieren weniger, jedoch wird bei allen Studierenden eine erhöhte Sozialkompetenz festgestellt.
Nachteilig sind die hohen Kosten für die Spiellizenzen, die komplexe Einarbeitung in das System und die oft unübersichtliche Aufgabengestaltung,
die Studierende zur Prokrastination verleitet\cite{a3}.
Derartige Spiele z.B. Wirtschaftssimulationen\cite{a11} gilt es nun in \gls{xr} zu transferieren und die Lehre der Wirtschaftswissenschaften durch \gls{cg} zu erweitern, ohne die Vorteile des Spiels zu verlieren.

\subsection{Aspekte des \gls{sg}s in der \gls{cg} Lehre und eine mögliche Umsetzungsstrategie mittels \gls{xr}}

Bevor ein \gls{sg} für eine Lehrveranstaltung erstellt werden kann, müssen nach\cite{a14} drei Teilbereiche umgesetzt werden:
Realität (wie das Spiel mit der physischen Welt verbunden ist), Bedeutung (welcher Wert erreicht werden soll)
und Spiel (wie man spielerische Aktivitäten schafft)\cite{a14}.
Feng, Amor, Gonzales und Lovreglio\cite{a15} formulieren elf Fragen, um diese drei Hauptaspekte zu erlangen.
Insbesondere pädagogische und verhaltensbezogene Aspekte und Ergebnisse stehen dabei im Vordergrund.

\begin{table}[]
\caption{Systematische literaturbezogene Forschungsfragen nach\cite{a14}}
\begin{tabular}{|l|l|}
\hline
1  & Welche Unterrichtsmethoden werden verwendet?                                                                                                                           \\ \hline
2  & Welche Lernziele werden verfolgt?                                                                                                                                      \\ \hline
3  & Wie sehen die Lernmaßnahmen aus?                                                                                                                                       \\ \hline
4  & Welche Ergebnisse bezüglich des Verhaltens werden erzielt?                                                                                                                                \\ \hline
5  & Wie sehen die Verhaltensmaßnahmen aus?                                                                                                                                      \\ \hline
6  & Welche Navigations-Lösungen gibt es?                                                                                                                                   \\ \hline
7  & Wie werden Sinne angeregt?                                                                                                                                             \\ \hline
8  & \begin{tabular}[c]{@{}l@{}}Welche narrativen Methoden gibt es, um Teilnehmer zu\\ermutigen, der Spielhandlung zu folgen und sie abzuschließen?\end{tabular} \\ \hline
9  & Wie werden Gefahren simuliert?                                                                                                                                         \\ \hline
10 & \begin{tabular}[c]{@{}l@{}}Gibt es nicht spielbare Charaktere und was tragen\\sie zum Spiel bei?\end{tabular}                                                                                              \\ \hline
11 & Wie kann man die Erfahrungen der Teilnahme bewerten?                                                                                                                   \\ \hline
\end{tabular}
\label{table:firsttable}
\end{table}
%\cite{a14}

Die Varianz der Darstellung der Lehre der \gls{cg} ist groß. 
Eine mögliche Umsetzung wäre die Modellierung und Berechnung eines eigenen \gls{xr} Erlebnisses,
welches mit neu erlernten Funktionen immer komplexer wird. Angefangen beim schwarzen oder durchsichtigen Bildschirm lassen sich Aufgaben und Fragen stellen,
die den Studierenden neue mathematische Funktionen vermitteln und aus diesen Objekte, Strukturen und Segmente erzeugen. 
Studierende können ihre Berechnung bzw. das modellierte Ergebnis direkt auf der \gls{vr} sehen und vergleichen und bekommen unmittelbar Feedback. 
\gls{cg} wird mittels \gls{xr} für Studierende greifbar gemacht. 
Die Komplexität wird langsam gesteigert, Funktionen und Modellierungen überlagern sich und ergeben ein Gesamtwerk, welches das Ziel der Vorlesung ist.

Bezieht man die Forschungsfragen aus Tabelle \ref{table:firsttable} auf die Lehre der \gls{cg} und die Software des \gls{xr} auf die Erstellung eines solchen Erlebnisses,
lässt sich u.a. diese Umsetzungsmöglichkeit finden, welche im nachfolgenden Absatz detaillierter aufgegriffen wird:

\begin{itemize}
\item Die Lehre beinhaltet Methoden und Schwierigkeiten der Abbildung einer dreidimensionalen Szene (real oder modelliert) auf ein zweidimensionales Ausgabegerät (Bildschirm)\cite{scholl}.
\item 1: Mittels \gls{xr} soll \gls{cg} erklärt werden; da \gls{xr} ein Teilgebiet der \gls{cg} ist, kann hier eine aufbauende Methodik verwendet werden,
beispielsweise angefangen vom einfachen Farbton und dessen Berechnungen über Geometrien und Modellierungen bis hin zu Konvertierungen.
Programme und Funktionen, welche Studierende selbst programmieren, können direkten Einfluss auf das \gls{xr} Ergebnis haben.
\item 2: Neben graphischen Grundfunktionen werden 3D Objekte geometrisch modelliert und diese auf 2D Ausgabegeräten dargestellt und die GPU-Programmierung eingeführt.
\item 3: Studierende erkennen Zusammenhänge zwischen mathematischen Funktionen und deren Parametern zur Darstellung von Objekten.
\item 4: Ziel ist das Verständnis der mathematischen Verfahren und der Algorithmen, die zur Erzeugung von Grafiken in der Computergrafik eingesetzt werden;
Computergrafiken sollen unter Anwendung der erlernten Verfahren programmiert werden.
\item 5: Studierende erarbeiten einzeln und in Gruppen schrittweise einzelne Funktionen und erzielen zum Schluss ein \gls{xr} Gesamtergebnis.
\item 6: Neben der Strukturierung durch vorgegebene mathematische Funktionen, sortiert nach Komplexität,
erfolgt die Hardware-Steuerung mittels händischer Steuerung mit aktiver Sensorik.
\item 7: Sinne werden durch die \gls{cg} vorrangig grafisch angesprochen.
Akustisch können Aktionen, Anwendungen von Gleichungen und Funktionen untermalt werden und abhängig vom Ton positive und negative Ergebnisse betont werden.
Haptisch und olfaktorisch entfallen bei der hier gewählten Lösung.
\item 8: Das Ziel des Spiels ist ein Gesamtwerk; eine Transformation der eigenen Funktionen und 3D Modellierungen auf eine 2D Oberfläche;
Spieler werden angehalten, ihre Oberfläche themenabhängig mit sämtlichen verfügbaren Funktionen kreativ zu gestalten.
\item 9: Gefahren, Schwierigkeiten und Fehler werden durch grafische Fehldarstellungen oder fehlerhafte Programmierung betont
und akustisch untermalt.
\item 10: Lehrende und Mentoren, können von außen das Spiel beeinflussen und unterstützend zur Seite stehen.
\item 11: Bewertet werden das Gesamtergebnis und die Integration aller verfügbaren Komponenten und deren Kombination.
Studierende sollen ihr Ergebnis parametrisierbar und veränderlich gestalten und somit beweisen, dass sie die Varianz der \gls{cg} verstanden haben.
\end{itemize}

Die aufgeführten Stichpunkte beinhalten eine Lösungsmöglichkeit der Umsetzung der Lehre der \gls{cg} mittels \gls{xr}.
Weitere Möglichkeiten, wie Rollenspiele oder Abenteuer mit mathematischen und modellierbaren Hindernissen und Aufgaben, sind ebenso möglich.
Nachfolgend wird die Umsetzung eines eigenen \gls{cg} Projektes mit \gls{xr} als Anzeigemedium mittels einer verfügbaren Software betrachtet.

%-----------------------------------------------------------------------------------------------------------------------------------------------
%SHADER

\subsection{Umsetzung mittels einer beispielhaften kommerziell-verfügbaren Software-Applikation}

Am Beispiel der Shader-Erstellung wird nun die zuvor definierte Umsetzung des \gls{sg}s erläutert. 
Ein wichtiger Bestandteil der \gls{cg} ist die Entwicklung von Shadern. 
Dies sind kleine Programme, welche direkt auf dem Grafikbeschleuniger eines Computers ausgeführt werden können.
Die Darstellung (Rendering) von 3D Objekten auf dem Anzeigegerät wird maßgeblich durch Shader beeinflusst. 
Hierbei durchläuft ein Objekt eine Reihe von mathematischen Operationen, welche die visuelle Darstellung beeinflussen (Renderpipeline). 
So lassen sich unter anderem Licht-Reflexionen auf das Objekt projizieren oder Weichzeichner-Effekte darstellen.
Das Entwickeln solcher Programme ist ein wichtiger Bestandteil der \gls{cg} Lehrveranstaltung.
Hier erstellen die Studierenden im Verlauf eines Projekts verschiedene Shader-Programme.
Im Rahmen der Vorlesung wird der Aufbau dieser anhand von Beispielen exemplarisch gezeigt und die Studierenden können diese Beispiele im Nachhinein nachvollziehen.

Es bieten eine visuelle Repräsentation der erstellten Renderpipeline und deren Einzelschritte diverse Vorteile.
Änderungen eines Schrittes können direkt visuell nachvollzogen werden, welche allein durch den Quellcode nicht direkt ersichtlich sind.
Diese Darstellungsform unterstütz einen effizienten Wissenstransfer, da das Verständnis einzelner Funktionen sowie deren Zusammenspiel interaktiv dargestellt wird.
Exemplarisch bietet die Shadertool-Software\cite{shadertool} solch eine Darstellung an.
Hier wird die Renderpipeline in einem 2D-Modus visuell dargestellt (s. Abbildung \ref{shadertool1_fig}) und Änderungen werden fortlaufend visualisiert.

\begin{figure}[htbp]
\centerline{\includegraphics[width=8cm]{shadertool_1.png}}
\caption{Shadertool Software im 2D Modus\cite{shadertool}}
\label{shadertool1_fig}
\end{figure}

Da im Bereich der \gls{cg} und somit auch in der \gls{cg} Lehrveranstaltung nahezu ausschließlich mit 3D Objekten gearbeitet wird,
bietet sich zusätzlich die Verwendung der \gls{xr} Technologie an.
Mit dieser ist es möglich, die erstellten Objekte, Grafiken und Shader-Effekte immersiv zu erleben und zudem qualitativ beurteilen zu können.

Am Beispiel der Shadertool Software\cite{shadertool} ist es möglich, diese in einen \gls{vr}-Modus zu schalten, welcher zum einen die erstellte Renderpipeline räumlich darstellt
und zum anderen die visuellen Darstellungen der Objekte erlebbar macht.
Somit ist es schnell möglich, visuelle Unstimmigkeiten, welche durch die Shader-Programme erzeugt werden, zu identifizieren, jedoch bietet dieser Ansatz keine direkten \gls{sg} Möglichkeiten.
Die Software wurde als simples Werkzeug konzipiert.
Um solch eine Software mittels \gls{sg} Ansatz verwenden zu können, müssen spielerische Elemente sowie gezielte Aufgabenstellungen für zu erreichenden Lernziele hinzugefügt werden.

\subsection{Analyse der Umsetzung}

Bei dem eben erläuterten Shader-Tool handelt es sich um eine spezialisierte Lösung, welche nur für diesen Einsatzbereich
verwendet werden kann. Jedoch ist der Aufwand zur Umsetzung bis in die aktive Lehrveranstaltung arbeitsintensiv.
Zudem gibt es im Bereich der Shader-Programme, insbesondere in der \gls{cg}, kaum Möglichkeiten, diese auch in anderen Veranstaltungen einzusetzen.
Jedoch bieten diese Lösungen den Vorteil, dass diese auf den bestmöglichen Lernerfolg ausgelegt werden können.
Bei der Verwendung solcher Software mit zusätzlicher \gls{xr} Komponente (auch ohne das Ziel eines expliziten \gls{sg} Ansatzes), ist es möglich, mit wenig Aufwand eine immersive Erfahrung zu erzeugen.
Dies ist insbesondere auf das Themengebiet der \gls{cg} zurückzuführen, in der die Lehrinhalte und insbesondere das Erstellen und Visualisieren von 3D-Objekten, schnell grafisch dargestellt werden können.
Viele der verfügbaren 3D-Grafikprogramme (z. B. Blender\cite{blender} ab Version 3.0) und 3D-Engines (z. B. Unity\cite{unity3d}) unterstützen bereits \gls{xr} Funktionen sowohl in der Darstellung von 3D-Szenen und Objekten als auch während der Bearbeitung.
Da einige dieser Software-Lösungen bereits in der \gls{cg} eingesetzt werden, ist hier eine Integration von \gls{xr} ohne viel Aufwand möglich.

Ein zusätzlicher Nachteil dieser Software und der oben genannten Alternativen ist, dass diese leistungsstarke Hardware erfordern.
Hier wird ein für die Anwendung geeigneter Computer, welcher mit einem leistungsstarken Grafikbeschleuniger ausgestattet ist, benötigt.
Zudem muss auch ein \gls{vr}-Headset verwendet werden, welches den Anforderungen der Software gerecht wird.
Diese Hardwarelimitierungen erschweren die Skalierbarkeit in Lehrveranstaltungen mit mehreren Studierenden und Gruppenarbeiten.

Um dieses Problem zu lösen, muss auf kostengünstige Hardware zurückgegriffen werden, um eine kostengünstige Skalierung zu ermöglichen.
Die Verwendung eines modernen Mobiltelefons (smartes Endgerät), welche über hochauflösende Bildschirme, sowie schnelle Prozessoren verfügen, können hier Abhilfe schaffen.
Zusätzlich wird eine Halterung benötigt, welche im Zusammenspiel mit dem Mobiltelefon als \gls{vr}-Headset fungiert.
Ein bekanntes Beispiel für eine kostengünstige Lösung, ist das von Google entwickelte Open-Source Projekt Google Cardboard\cite{googlecardboard}.

Hier wird das Mobiltelefon in einen einfachen Papierrahmen eingehängt, welcher dann vor den Augen befestigt werden kann.
Somit steht eine einfache Möglichkeit \gls{vr}-Inhalte mittels spezieller dafür angepasster Applikationen darstellen zu können zur Verfügung.

Durch den einfachen Aufbau des Headsets bietet dies keine weiteren Interaktionsmöglichkeiten für die Nutzer.
Hier kann nur sehr eingeschränkt direkt mit dem Inhalt interagiert werden, welches einen Einsatz bei Spielen oder \gls{cg}-Anwendungen erschwert.

Dazu können verschiedene externe Eingabegeräte verwendet werden.
U.a. ist es möglich mittels Hand-Controller, Handgesten an die Anwendung zu übermitteln.
Alle externen Controller werden dabei i. d. R. kabellos per Bluetooth mit dem Mobiltelefon gekoppelt.
Somit ist auch ein Ausleihen solcher Controller an die Studierenden möglich.

Da bei dieser Lösung ein Mobiltelefon zum Einsatz kommt, kann die in diesem Beispiel untersuchte Shader-Tool Software\cite{shadertool} nicht auf dieser Hardware-Plattform ausgeführt werden.
Es gibt keine direkte Alternative, jedoch zeigen Webseiten, wie z. B. Shadertoy\cite{shadertoy}, dass es möglich ist, eindrucksvolle Shader performant im Browser darzustellen.
Dabei können verschiedene Shader direkt im Browser erstellt und bearbeitet werden und können somit auch direkt auf einem Mobiltelefon angezeigt werden.
Lediglich die \gls{xr} oder insbesondere \gls{vr} Unterstützung fehlen.

Andere Software-Pakete, wie Unity\cite{unity3d}, bieten hier bereits eine vollständige Entwicklungsumgebung für \gls{xr} Anwendungen an.
Diese können nach dem Erstellen einer Applikation auf das Mobiltelefon geladen werden und z. B. mittels des Google Cardboard-Headsets\cite{googlecardboard} ausprobiert werden.

Eine solche Lösung eignet sich für eine weitere Untersuchung im Einsatz in der \gls{cg}-Lehre.
Da es sich zum einen um eine kostengünstige, gut skalierbare \gls{vr}-Plattform handelt und es zum anderen bereits einige Softwarekomponenten gibt, 
welche sich mit den Lehrinhalten der \gls{cg} verwenden lassen und mit dieser kompatibel sind.
Die Skalierbarkeit des Systems macht es nicht nur für neue Lerninhalte einfacher erweiterbar, sondern auch für weitere, zukünftige \gls{xr} Technologien modular integrierbar.

%-----------------------------------------------------------------------------------------------------------------------------------------------
%VERGLEICHE

\section{Evaluation}

Ein wichtiger Punkt bei der Verwendung von \gls{sg} in der Lehre, ist die anschließende Evaluation des Lernerfolgs.
Zusätzlich zur Wissensvermittlung ist auch die Akzeptanz des Zielpublikums eine wichtige Messgröße.
Hierzu hat die Hochschule Osnabrück eine Handlungsempfehlung aus gewonnenen Erkenntnissen aus dem \gls{gbl} Gebiet zusammengestellt\cite{a3}.
Diese umfasst zudem die folgenden Punkte, um \gls{sg} in der Lehre evaluieren zu können.
Das Einholen von Feedback von den Lehrenden sowie von den Studierenden ist essenziell.
Dies geschieht zum einen mit Teilnehmern, bei denen eine Wissensvermittlung mittels \gls{sg} erfolgte und zum anderen mit einer zweiten Gruppe,
bei der die Wissensvermittlung durch klassische Aufgaben umgesetzt wurde.

Dieser Feedback-Prozess ist insbesondere bei der Wissensvermittlung durch \gls{xr} Technologien relevant.
Jeder Studierende nimmt die \gls{xr} Umgebung unter Umständen anders wahr und interagiert unterschiedlich mit dieser.
Anders als bei einer fest vorgegebenen \gls{sg} Anwendung, welche unter Umständen nur wenige Interaktionsmöglichkeiten bietet, ist die \gls{xr} Technologie
darauf ausgelegt, den Teilnehmern mehr Interaktionsmöglichkeiten zu bieten.

Demnach muss auch der Feedback-Prozess angepasst werden. Hierzu kann nicht nur auf ein reines Feedback der Teilnehmer,
sondern es muss auch auf eine externe Gruppe zugrückgegriffen werden, welche die Teilnehmerinteraktionen während der Anwendung in \gls{xr} beobachtet.
Diese Erkenntnisse, wie die Teilnehmer in der \gls{xr} Umgebung interagieren, geben zusätzlich zu dem oben genannten Feedback-Prozess Aufschluss,
ob die Anwendung den Teilnehmerfokus auf die Wissensvermittlung lenkt.

Für die Evaluation im Bereich der Lehre der \gls{cg} empfiehlt sich eine Evaluation des Gesamtergebnisses.
Diese beinhaltet die von den Studierenden erstellte \gls{xr} Umgebung und die darin verwendeten \gls{cg} Komponenten und Funktionen.
Um Studierende von der Verwendung der \gls{xr} Technologie in der Lehre nicht auszuschließen, ist eine zusätzliche Gruppe von Betreuern, wie Tutoren, nötig,
welche den Prozess und die Beteiligung der Studierenden begleiten.

Zudem sollte keine Momentaufnahme als Evaluation betrachtet werden, sondern ein Vergleich der Ergebnisse der Teilnehmergruppen über verschiedene Semester zu Rate gezogen werden,
um Aufschluss über mögliche Änderungen, Verbesserungen oder gar Verschlechterungen geben zu können.

Abschließend ist festzuhalten, dass u. U. nicht jeder Studierende an dem \gls{xr} Erlebnis teilnehmen möchte oder dieses nicht anwenden kann. 
Zudem dürfen jene, welche das Projekt im Verlauf des Semesters nicht abschließen können, nicht ausgeschlossen werden.
Für diese muss ein konservativer Lösungsweg angeboten werden.
%-----------------------------------------------------------------------------------------------------------------------------------------------
%FAZIT

\section{Fazit und Ausblick}

\gls{sg}, insbesondere in Verbindung mit \gls{xr}, bietet in der hochschuldidaktischen Lehre ein großes Potential.
Die z. T. bereits etablierte Anwendung des 2D \gls{sg}s in der Wirtschaftslehre hat bewiesen, 
dass die Methodik sowohl umsetzbar ist, als auch Studierende aller Leistungsbereiche fördert. 
Anhand der exemplarischen Umsetzungsmöglichkeit in der \gls{cg} Lehrveranstaltung wurde gezeigt,
dass es möglich ist, \gls{xr} Technologien so einzusetzen, dass diese eine Wissensvermittlung unterstützen. 
Die Varianz an Umsetzungsmöglichkeit ist enorm; 
da \gls{xr} ein Teilbereich der \gls{cg} ist, bietet sich hier ein direkter Zusammenhang zwischen beiden Mitteln an.
Die Lehre der \gls{cg} kann mittels \gls{xr} erklärt werden.
Die Studierenden erstellen eine \gls{xr} Umgebung und erlernen zeitgleich Methodiken der \gls{cg}. 
Somit entsteht ein effizienter Kreislauf. 
Eine mögliche Umsetzungsform ist hierbei die Verwendung von bereits bestehender Software, welche keinerlei spielerische Elemente besitzt.
Diese kann durch eine Anpassung und Weiterentwicklung mit derartigen Elementen versehen werden um somit den Anforderungen der \gls{cg} gerecht zu werden.
Die im Beispiel analysierte Software, bietet zudem direkt eine Unterstützung für den \gls{xr} Modus und eignet sich somit für eine Evaluation.

Andere Software-Applikationen, welche sich für die Verwendung in der \gls{cg} Lehrveranstaltung eignen, bringen diese Features i. d. R. nicht mit.
Einige andere können die zuvor erstellten Modelle bzw. 3D-Welten in einer \gls{xr} Umgebung darstellen.
Das Erstellen dieser geschieht im 2D-Modus an einem PC.
Hier bietet diese Symbiose zwischen der Erstellung und dem Betrachten im \gls{xr} den Vorteil, dass die erlernten Konzepte immersiv erforscht werden können.
Dabei können die positiven Erfahrungen aus den bereits angewendeten 2D-\gls{sg}s übernommen und durch die Erweiterung mittels \gls{xr} gesteigert werden.

Nachteilig ist hierbei, dass all diese Ansätze mit einem hohen Arbeits- und Kostenaufwand verbunden sind.
Potenzielle Software, welche nicht über \gls{sg} Elemente sowie \gls{xr} Funktionalitäten verfügt, muss aufwändig angepasst werden.

Ebenso stellt die benötigte \gls{xr}-Hardware einen Kostenfaktor dar, da bestimmte Spezifikationen erfüllt werden müssen.

Eine Möglichkeit ist die Verwendung kostengünstiger \gls{xr} Ansätze, welche ein modernes Mobiltelefon als Grundlage verwenden.
Diese sind heutzutage in der Lage, komplexe \gls{xr}-Anwendungen auszuführen, bieten aber ohne externe Eingabegeräte kaum Möglichkeiten einer Interaktion mit der \gls{xr} Umgebung.
Durch die Ergänzung von z. B. Hand-Controllern, welche an Studierende verliehen werden können, ist es möglich in der \gls{cg} Lehrveranstaltung ein nahezu vollständiges \gls{xr} Erlebnis zu bieten.

Abschließend ist festzuhalten, dass eine Integration von \gls{sg} Ansätzen in die Lehre und insbesondere die Integration von \gls{xr} in die Lehre der \gls{cg} sinnvoll und zukunftsorientiert ist
und zudem Wissen effizienter vermittelt.
Studierende und Lehrende profitieren. Hürden, wie Hardware und Arbeitsaufwand, erschweren diese, sind aber nach einmaliger Umsetzung dauerhaft anwendbar.
Eine Integration ist somit zu empfehlen.

%-----------------------------------------------------------------------------------------------------------------------------------------------
\begingroup

%\setstretch{1.05}
\begin{thebibliography}{00}
\bibitem{eduxrvrar2020usa} Thomas Alsop: "Leading applications of immersive technologies in the education sector in the next two years according to XR/AR/VR/MR industry
experts in the United States in 2020", in: Internetseite Statista, URL: https://www.statista.com/statistics/1185078/applications-immersive-technologies-xr-ar-vr-mr-education/, Abruf am 17.11.2021.

\vskip 0.05in
\bibitem{evallearningmixedreality2020} Y. M. Tang; K. M. Au; H. C. W. Lau; G. T. S. Ho, C. H. Wu; "Evaluating the effectiveness of learning design with mixed reality (MR) in higher education", Springer-Verlag London Ltd, 28.02.2020

\vskip 0.05in
\bibitem{a7} Linda Stege, Giel van Lankveld, Pieter Spronck; "Serious Games in Education", International Journal of Computer Science in Sport, 2011

\vskip 0.05in
\bibitem{fabulagames} Fabula Games, "LERNEN KANN SOOO BUNT SEIN", in: Internetseite Fabula Games, URL: https://fabula-games.de/, Abruf am 22.11.2021.

\vskip 0.05in
\bibitem{a3} Axel Jacob, Frank Teuteberg; "Game-Based Learning, Serious Games, Business Games und Gamification –Lernförderliche Anwendungsszenarien, gewonnene Erkenntnisse und Handlungsempfehlungen", Springer Fachmedien Wiesbaden GmbH, 2017

\vskip 0.05in
\bibitem{grundlagencg2001} Thomas Strothotte, Stefan Schlechtweg; "Grundlagen der Computergraphik", 2001

\vskip 0.05in
\bibitem{shadertool} Stefan Kraus, Timo Armbruster; "ShaderTool", in: Internetseite Steam, URL: https://store.steampowered.com/app/314720/ShaderTool/, Abruf 02.12.2021

\vskip 0.05in
\bibitem{a9} IBM Institute for Business Value; "Extended Reality (XR) can boost workforce efficiency and resilience by reimagining how work is done.", in: Internetseite IBM Institute for Business Value, URL: https://www.ibm.com/thought-leadership/institute-business-value/report/ar-vr-workplace, Abruf am 22.11.2021.

\vskip 0.05in
\bibitem{a10} Joseph F. Frederick; "Defining Serious Games", in: Internetseite flowleadership, URL: https://flowleadership.org/serious-games/, Abruf am 22.11.2021.

\vskip 0.05in
\bibitem{blender} Blender Foundation; "Blender", in: Internetseite Blender, URL: https://wiki.blender.org/wiki/Reference/Release\_Notes/3.0, Abruf am 22.11.2021.

\vskip 0.05in
\bibitem{unity3d} Unity Technologies; "Unity VR", in: Internetseite Unity Technologies, URL: https://unity.com/de/case-study\#games-vr, Abruf am 22.11.2021.

\vskip 0.05in
\bibitem{a11} TOPSIM; "TOPSIM-General Management-Teilnehmerhandbuch", in: Internetseite TOPSIM, URL: https://www.css.msm.uni-due.de/fileadmin/Dateien/MSM/Topsim-Gr8/01\_General\_Management\_Teilnehmerhandbuch\_STD\_15\_3.pdf, Abruf am 22.11.2021.

\vskip 0.05in
\bibitem{a14} Zehnan Feng, Robert Amor, Vicente Gonzales, Ruggiero Lovreglio; "Immersive Virtual Reality Serious Games for Evacuation Training and Research: A Systematic Literature Review", ResearchGate, 05.2018

\vskip 0.05in
\bibitem{a15} Rüppel, Schatz; "Designing a BIM-based serious game for fire safety evacuation simulations"; Advanced Engineering Informatics; 2011

\vskip 0.05in
\bibitem{googlecardboard} Google LLC; "Google Cardboard", in: Internetseite google.com, URL: https://arvr.google.com/intl/de\_de/cardboard/apps/, Abruf am 22.11.2021.

\vskip 0.05in
\bibitem{shadertoy} Inigo Quilez, Pol Jeremias; "Shadertoy", in: Internetseite shadertoy.com, URL: https://www.shadertoy.com, Abruf am 22.11.2021.

\vskip 0.05in
\bibitem{scholl} Ingrid Scholl, "Computergrafik" in: Internetseite Vorlesung Computergrafik von Fr. Prof. Scholl, Ingrid; URL: https://www.fh-aachen.de/menschen/scholl/lehre/computergrafik, Abruf am 01.12.2021.

\end{thebibliography}
\endgroup

\end{document}

### 2023-09-29 documentation/thesis/thesis_declaration.tex
mv docs

I hereby declare that I have prepared this thesis independently and
without outside assistance. Text passages, which are based literally or
in the sense on publications or lectures of other authors, are marked as
such. The work has not yet been submitted to any other examination
authority and has not yet been published.

Aachen, \datum  \_\_\_\_\_\_\_\_\_\_\_\_,
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

### 2023-09-29 documentation/thesis/thesis_document.tex
mv docs

\hypertarget{motivation}{%
\chapter{Motivation}\label{motivation}}

\hypertarget{tables}{%
\chapter{Tables}\label{tables}}

\begin{longtable}[]{@{}lllll@{}}
\caption{Das ist eine tolle Tabelle
\label{Das_ist_eine_tolle_Tabelle.csv}}\tabularnewline
\toprule
year & make & model & description & price\tabularnewline
\midrule
\endfirsthead
\toprule
year & make & model & description & price\tabularnewline
\midrule
\endhead
1997 & Ford & E350 & ac, abs, moon & 3000.00\tabularnewline
1999 & Chevy & Venture «Extended Edition» & & 4900.00\tabularnewline
1996 & Jeep & Grand Cherokee & MUST SELL! air, moon roof, loaded &
4799.00\tabularnewline
\bottomrule
\end{longtable}

Tabelle ist toll: \ref{Das_ist_eine_tolle_Tabelle.csv}

\hypertarget{images}{%
\section{Images}\label{images}}

\begin{figure}
\centering
\includegraphics{./generated_images/border_Dies_ist_ein_Testbild.png}
\caption{Dies ist ein Testbild \label{Dies_ist_ein_Testbild.png}}
\end{figure}

Das Bild ist toll: \ref{Dies_ist_ein_Testbild.png}

### 2023-09-29 src/MagneticReadoutProcessing/udpp/UDPPFunctionCollection.py

@@ -9,6 +9,7 @@ __fix_import__()
 
 
 from MRP import MRPReading
+from MRP import MRPSimulation
 import  UDPPFLogger
 from UDPPFLogger import UDPFLogger as logger
 
@@ -22,6 +23,17 @@ class UDPPFunctionCollectionException(Exception):
 class UDPPFunctionCollection:
     """This class only includes static methods which are able to used in a user defined pipeline"""
 
+
+    @staticmethod
+    def simulate_magnet(_count: int = 1, _random_polarisation: bool = False, _random_magnetisation: bool = False) -> [MRPReading.MRPReading]:
+        ret: [MRPReading.MRPReading] = []
+
+        for idx in range(_count):
+            rnd = MRPSimulation.MRPSimulation.generate_reading(_randomize_magnetization=_random_magnetisation, _add_random_polarisation=_random_polarisation)
+            rnd.set_additional_data("simulate_magnet", idx)
+            ret.append(rnd)
+
+        return ret
     @staticmethod
     def readings_passthrough(readings: [MRPReading.MRPReading]) -> [MRPReading.MRPReading]:
         """

### 2023-09-29 src/UnifiedMagBoardFirmware/include/baseSensor.h

@@ -1,0 +1,99 @@
+#ifndef __baseSensor_h__
+#define __baseSensor_h__
+
+#ifdef USING_PLATFORMIO
+    #include "Arduino.h"
+#endif
+
+#include "Wire.h"
+
+
+// PRIVATE LIBS
+#include <Tlv493d.h>
+#include <Adafruit_MMC56x3.h>
+
+
+//CUSTOM CLASSES
+#include "helper.h"
+#include "usf_plattform.h"
+
+typedef enum ImplementedSensors{
+    SIMULATED = 0,
+    TLV493D = Tlv493d_Address::TLV493D_ADDRESS1,
+    TLV493D_ALT = Tlv493d_Address::TLV493D_ADDRESS2,
+    MMC56X3 = MMC56X3_DEFAULT_ADDRESS
+}ImplementedSensors_t;
+
+
+
+struct sensor_result{
+    float x;
+    float y;
+    float z;
+    float b;
+    float t;
+    long ts;
+
+    sensor_result(){
+
+    };
+
+    void set(sensor_result _other){
+        this->x = _other.x;
+        this->y = _other.y;
+        this->z = _other.z;
+        this->b = _other.b;
+        this->t = _other.t;
+        this->ts = _other.ts;
+    };
+}sensor_result_t;
+
+
+class baseSensor
+{
+    public:
+        
+
+    baseSensor();
+    bool begin(TwoWire &_wire_instance);
+    bool is_valid();
+    
+    String capabilities();
+    String get_sensor_name();
+
+    
+    bool query_sensor();
+    sensor_result get_result();
+
+    
+
+    private:
+        TwoWire* i2c_inst;
+
+
+        
+        ImplementedSensors found_sensor = ImplementedSensors::SIMULATED;
+        sensor_result last_query_result;
+        //POSSIBLE FOUND SENSOR INSTANCES HERE
+        Tlv493d_Address_t addr = Tlv493d_Address::TLV493D_ADDRESS1;
+        Adafruit_MMC5603* mmc = nullptr; //Adafruit_MMC5603(12345);
+        
+        Tlv493d* tlv493d_instance = nullptr;
+        
+};
+
+
+struct sensor_info{
+
+    
+    int index = -1;
+    int tca_channel = 0;
+    bool valid = false;
+    baseSensor sensor_instance = baseSensor();
+
+    sensor_info(){
+        valid = false;
+    };
+} sensor_info_t;
+
+#endif

### 2023-09-29 src/UnifiedMagBoardFirmware/include/main.h

@@ -1,7 +1,7 @@
 #ifndef __main_h__
 #define __main_h__
 
-#include "plattform.h"
+#include "usf_plattform.h"
 #include "version.h"
 
 #ifdef USING_PLATFORMIO
@@ -9,16 +9,16 @@
 #endif
 
 // PRIVATE LIBS
-#include <Tlv493d.h>
 #include <CommandParser.h>
 #include "ArduinoUniqueID.h"
 
 
 
 // PRIVATE CLASSES
+#include "baseSensor.h"
 #include "TCA9458A.h"
 #include "sync_timer.h"
-
+#include "helper.h"
 
 
 #define READOUT_SPEED_IN_SINGLEMODE_HZ 100 // Hz
@@ -60,32 +60,8 @@ const String System_State_STR[5] = {
 };
 
 
-struct sensor_info{
-    
-    Tlv493d_Address_t addr = Tlv493d_Address::TLV493D_ADDRESS1;
-    int index = -1;
-    int tca_channel = 0;
-    bool valid = false;
-    Tlv493d sensor_instance;
-
-    sensor_info(){
-        valid = false;
-    };
-} sensor_info_t;
 
 
-struct sensor_result{
-    float x;
-    float y;
-    float z;
-    float b;
-    float t;
-    long ts;
-
-    sensor_result(){
-
-    };
-}sensor_result_t;
 
 
 

### 2023-09-29 src/UnifiedMagBoardFirmware/src/baseSensor.cpp

@@ -1,0 +1,110 @@
+#include "baseSensor.h"
+
+baseSensor::baseSensor()
+{
+}
+
+/*
+
+      Tlv493d_Address_t addr = Tlv493d_Address::TLV493D_ADDRESS1;
+        Adafruit_MMC5603* mmc = nullptr; //Adafruit_MMC5603(12345);
+
+        Tlv493d* tlv493d_instance = nullptr;
+
+*/
+bool baseSensor::begin(TwoWire &_wire_instance)
+{   
+    i2c_inst = _wire_instance;
+    //AVOID ERRORS DUE TO CALL BEGIN AGAIN
+    if(tlv493d_instance){
+        delete tlv493d_instance;
+    }
+
+    if(mmc){
+        delete mmc;
+    }
+    // scan for sensors
+    if (is_i2c_device_present(i2c_inst, ImplementedSensors::TLV493D))
+    {
+        found_sensor = ImplementedSensors::TLV493D;
+        addr = Tlv493d_Address::TLV493D_ADDRESS1;
+        tlv493d_instance = new Tlv493d();
+    }
+    else if (is_i2c_device_present(i2c_inst, ImplementedSensors::TLV493D_ALT))
+    {
+        found_sensor = ImplementedSensors::TLV493D;
+        addr = Tlv493d_Address::TLV493D_ADDRESS2;
+        tlv493d_instance = new Tlv493d();
+    }
+    else if (is_i2c_device_present(i2c_inst, ImplementedSensors::MMC56X3))
+    {
+        found_sensor = ImplementedSensors::MMC56X3;
+        Adafruit_MMC5603 *mmc = new Adafruit_MMC5603(); // Adafruit_MMC5603(12345);
+        mmc->begin(ImplementedSensors::MMC56X3, i2c_inst);
+        mmc->setDataRate(100);
+    }
+    else
+    {
+        return false;
+    }
+
+    // init sensor instances
+}
+
+String baseSensor::capabilities()
+{
+}
+String baseSensor::get_sensor_name()
+{
+    switch (found_sensor)
+    {
+    case ImplementedSensors::SIMULATED:
+        return "SIMULATED";
+    case ImplementedSensors::TLV493D:
+        return "TLV493D";
+    case ImplementedSensors::MMC56X3:
+        return "MMC56X3";
+    default:
+        return "UNKNOWN";
+    }
+}
+
+bool baseSensor::query_sensor()
+{
+    bool succ = false;
[…]

### 2023-09-29 src/UnifiedMagBoardFirmware/src/helper.cpp

@@ -1,0 +1,71 @@
+#include "helper.h"
+
+bool i2c_scan(TwoWire &_wire_instance, const int _check_for_addr = -1, const bool _log = true)
+{
+  byte error, address;
+  int nDevices;
+
+  if (_log)
+  {
+    DEBUG_SERIAL.println("Scanning...");
+  }
+
+  bool addr_found = false;
+  nDevices = 0;
+  for (address = 1; address < 127; address++)
+  {
+    // The i2c_scanner uses the return value of
+    // the Write.endTransmisstion to see if
+    // a device did acknowledge to the address.
+    _wire_instance.beginTransmission(address);
+    error = _wire_instance.endTransmission();
+    if (_log)
+    {
+      if (error == 0)
+      {
+        DEBUG_SERIAL.print("I2C device found at address 0x");
+        if (address < 16)
+        {
+          DEBUG_SERIAL.print("0");
+        }
+        DEBUG_SERIAL.print(address, HEX);
+        DEBUG_SERIAL.println("  !");
+
+        nDevices++;
+      }
+      else if (error == 4)
+      {
+        DEBUG_SERIAL.print("Unknown error at address 0x");
+        if (address < 16)
+        {
+          DEBUG_SERIAL.print("0");
+        }
+        DEBUG_SERIAL.println(address, HEX);
+      }
+    }
+
+    if (_check_for_addr >= 0 && _check_for_addr == address && error == 0)
+    {
+      addr_found = true;
+    }
+  }
+  if (_log)
+  {
+    if (nDevices == 0)
+    {
+      DEBUG_SERIAL.println("No I2C devices found\n");
+    }
+    else
+    {
+      DEBUG_SERIAL.println("done\n");
+    }
+  }
+
+  return addr_found;
+}
+
+
+bool is_i2c_device_present(TwoWire &_i2c_interface, const byte _addr)
+{
+  return i2c_scan(_i2c_interface, _addr, false);
+}

### 2023-09-29 src/UnifiedMagBoardFirmware/src/main.cpp

@@ -7,8 +7,8 @@
 // CUSTOM INCLUDES
 #include "main.h"
 
- #ifdef ARDUINO_ARCH_MBED
-    REDIRECT_STDOUT_TO(DEBUG_SERIAL)  // MBED  printf(...) to console
+#ifdef ARDUINO_ARCH_MBED
+REDIRECT_STDOUT_TO(DEBUG_SERIAL) // MBED  printf(...) to console
 #endif
 
 // CLASSES
@@ -17,16 +17,11 @@ TCA9548A tca9584a(SENSOR_WIRE);
 DBGCommandParser debug_command_parser;
 HostCommandParser host_command_parser;
 
-
-
-
 #if defined(HOST_SERIAL_RX) && defined(HOST_SERIAL_TX)
 HardwareSerial HOST_SERIAL(HOST_SERIAL_RX, HOST_SERIAL_TX); // RX TX  // FOR SERIAL ANC
-#else
-
 #endif
-sync_timer readout_timer(READOUT_SPEED_IN_SINGLEMODE_DELAY, false);
 
+sync_timer readout_timer(READOUT_SPEED_IN_SINGLEMODE_DELAY, false);
 sensor_info sensors_found[MAX_TLV_SENSORS] = {sensor_info()}; // TWO POSSIBLE SENSORS PER TCA CHANNEL S0 16 SENSORS PER SLICE
 sensor_result sensor_results[MAX_TLV_SENSORS] = {sensor_result()};
 System_State system_state = System_State_Error;
@@ -34,73 +29,6 @@ System_State system_state = System_State_Error;
 long readout_index = 0;
 int sensor_number = 0;
 int anc_base_id = -1;
-
-
-
-
-bool i2c_scan(TwoWire &_wire_instance, const int _check_for_addr = -1, const bool _log = true)
-{
-  byte error, address;
-  int nDevices;
-
-  if (_log)
-  {
-    DEBUG_SERIAL.println("Scanning...");
-  }
-
-  bool addr_found = false;
-  nDevices = 0;
-  for (address = 1; address < 127; address++)
-  {
-    // The i2c_scanner uses the return value of
-    // the Write.endTransmisstion to see if
-    // a device did acknowledge to the address.
-    _wire_instance.beginTransmission(address);
-    error = _wire_instance.endTransmission();
-    if (_log)
-    {
-      if (error == 0)
-      {
-        DEBUG_SERIAL.print("I2C device found at address 0x");
[…]

### 2023-09-29 documentation/paper/main.tex
.

@@
 
-\title{Anwendung des Serious Gamings mittels erweiterter Realität in der hochschuldidaktischen Lehre\\
-%{\footnotesize \textsuperscript{*}Wissenschaftliches Arbeiten WS2021/2022 Fachhochschule Aachen}
-%\thanks{Identify applicable funding agency here. If none, delete this.}
+\title{Implementation of an Open-Source modular mangetic field camera for usage in Low-Field MRI Systems\\
+
 }
@@
 \IEEEauthorblockA{\textit{Fachhochschule Aachen} \\
-\textit{Fachbereich 5 Elektrotechnik und Informationstechnik}\\
+\textit{Electrical Engineering and Information Technology}\\
 Aachen, Deutschland \\
-marcel.ochsendorf@alumni.fh-aachen.de}
+marcelochsendorf@alumni.fh-aachen.de}
 %\and
@@
 \begin{abstract}
-Die Integration moderner Medien in die hochschuldidaktische Lehre hat seit der Jahrtausendwende stetig an Bedeutung gewonnen.
-Dieses Papier zeigt eine Möglichkeit zur Vermittlung von Wissen und die Motivation zum Lernen mittels \gls{xr} am Beispiel der Vorlesung
-\gls{cg} basierend auf den Erkenntnissen von bereits etablierten Lösungen.
-Wissen soll hierbei durch softwarebasierte Spiele, den \gls{sg}, vermittelt werden.
-Anders als bei existierenden 2D Display-Anwendungen werden bei \gls{xr} visuelle Informationen mittels virtuellen Umgebungen, Objekten und Interaktionen mit diesen vermittelt.
-Die Studierenden können Situationen aus einem Blickwinkel ihrer Wahl erkunden und erlernen und können zudem durch Wiederholen von Aufgaben in verschiedenen Blickwinkeln
-ihr Wissen anpassen.
-Meist ohne unterstützende Lehrkörper werden Studierende innerhalb dieser Umgebung einzeln oder in Gruppen mit Aufgaben und Informationen konfrontiert,
-welche die Interaktions- und Imaginationsinstinkte ansprechen.
-Insbesondere die untersuchte Lehrveranstaltung \gls{cg} ermöglicht viele Umsetzungen des \gls{sg}-Ansatzes, da technologische Themenbereiche und die grafischen Unterschiede
-mittels \gls{xr} hervorgehoben werden können.
+
 \end{abstract}
@@
 
-\section{Einleitung}
-Die Anwendung von 3D-Technologien und virtuellen Umgebungen hat in der Vergangenheit stark zugenommen
-und wird erheblich weiter steigen, wie Statistiken aus den USA zeigen\cite{eduxrvrar2020usa}.
-Die Variationen und Möglichkeiten der \gls{vr}-Technologien werden durch das rapide Wachstum von schneller und erschwingliche Hardware, Software und Netzwerken begünstigt\cite{evallearningmixedreality2020}.
-Mit Veränderungen des alltäglichen Umfelds und dem wachsenden Umfang von Wissen muss sich auch die Lehre diesen Veränderungen anpassen und kann daraus auch
-Nutzen ziehen.
-\gls{gbl} nutzt jene Technologien, um Lehrinhalte und Informationen spielerisch an Nutzer, in diesem Falle Studierende, zu vermitteln und somit die
-Motivation zum Lernen zu steigern.
-Die Möglichkeiten der Umsetzung sind vielfältig und bieten verschiedene Vor- und Nachteile.
-Die Umsetzung ist komplex, da anders als bei 2D-Display-Anwendungen die \gls{xr}-Technologien zusammen mit Interaktionsoptionen für jeden Studierenden
-die finanzielle Belastung selten aufgebracht werden kann. Für ein einzelnes Fach ist der Aufwand groß. Zudem ist die Umsetzung insbesondere für mehrere Studierende zeitintensiver.
-Die Ergebnisse für die Lehre sind fast ausschließlich positiv und werden in der Evaluation dieses Papiers gesondert beleuchtet.
-Studierende reflektieren erlerntes Wissen besser und nehmen den Lehrprozess positiver wahr;
-mehr als Zweidrittel der Studierenden befürworten eine verstärkte Integration von \gls{xr} in der Lehre\cite{a7}.\\
-
-Im Folgenden werden die verschiedenen Begriffe definiert und voneinander abgegrenzt;
-anschließend werden Möglichkeiten des Einsatzes von \gls{xr} in der Lehre der \gls{cg} der Fachhochschule Aachen vorgestellt.
+\section{Introduction}
 
@@
 
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=8cm]{serious-games.png}}
-\caption{Definition Serious Games.\cite{a10}}
-\label{sgdef_fig}
-\end{figure}
-
 \subsection{Serious Gaming (\gls{sg})}
@@
 Nicht digitale oder Spiele für 2D Ausgabegeräte werden hierbei nicht berücksichtigt.
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=9cm]{ibm_ar.png}}
-\caption{Zusammenhang von \gls{xr} zu \gls{vr} und \gls{ar}.\cite{a9}}
-\label{xrvrar_fig}
-\end{figure}
 
@@
 
-Die Variationen an Möglichkeiten der \gls{xr}-gestützten hochschuldidaktischen Lehre ist enorm und wächst stetig an\cite{eduxrvrar2020usa}.
-Die Auswahl der verfügbaren und angewendeten Methodiken ist derzeit noch begrenzt.
-2D \gls{sg} wird bereits als Lehrmedium verwendet, \gls{xr}-gestützte Medien sind seltener vertreten; 
-beide Medien werden zukünftig mehr Einfluss auf die Lehre haben.
-Das Besondere an der Integration von \gls{xr} in der Lehre ist die Tatsache,
-dass die Lehre der \gls{cg} die Erstellung von \gls{xr} und computergestützten Bildern beschreibt.
-Das bedeutet, es kann mithilfe des Mediums selbst den Studierenden vermittelt werden, wie \gls{xr} erstellt und angewendet wird.
-Die Bilder und Szenen, die das \gls{sg} den Studierenden mittels \gls{xr} zeigt, sollen beschreiben, wie \gls{xr} funktioniert.
-Es bildet somit einen Kreislauf aus der Verwendung von \gls{cg} Inhalten und der Erklärung wie diese Inhalte erstellt werden können.
-Anders als in anderen Themenbereichen, wo die Verwendung der \gls{xr} Technologien nur Mittel zum Zweck ist, kann das Mittel hierbei auch die Lehre mitgestalten.
-
 \subsection{2D \gls{sg} Lösung in der hochschuldidaktischen Lehre am Beispiel der Business Simulation \gls{sg}}
-
-Eine Variante der \gls{sg} sind Business Simulation Anwendungen.
-Diese sind oft als Planspiel ausgeführt und bieten sich insbesondere in den Lehrveranstaltungen der Wirtschaftswissenschaften an.
-Allgemein sind diese i. d. R. als Browser-basierte Varianten ausgeführt und die Benutzerinteraktion beschränkt sich dabei meistens auf das Ausfüllen von Textfeldern und das Lesen von Texten\cite{a11}.
-Der \gls{sg} Aspekt entsteht dabei durch das Spielen im Team und gegen gegnerische Teams.
-Die Hochschule Osnabrück setzt in der Wirtschaftslehre \gls{sg} bereits erfolgreich ein\cite{a3}.
-Studierende werden einzeln oder in Gruppen mit Inhalten konfrontiert, müssen Vorträge halten, für imaginäre Unternehmen Berichte und Protokolle verfassen und ihren
-Lernfortschritt festhalten und individuell verbessern\cite{a3}.
-Das \gls{sg} kann auch über Kontinente hinweg in verschiedenen Sprachen stattfinden. Somit entsteht nicht nur eine Interaktion mit anderen Studierenden aus der Lehrveranstaltung,
-sondern die einzelnen Teilnehmer, das Erlernen von Fachbegriffen und der Umgang mit unternehmensbezogenen Situationen und Aufgaben stehen dabei im Vordergrund\cite{a3}.
-Die Spiele werden dabei von der Hochschule erworben, dazu gehören insbesondere die Anbieter TOPSIM, SIMCON GmbH und McGraw-Hill Education, Inc\cite{a3}.
-Die Fachhochschule Aachen verwendet ebenfalls TOPSIM im Bereich der Wirtschaftslehre für Informatiker und Ingenieure.
-Der Anbieter TOPSIM bietet Cloud-basierte Browser-Anwendungen, bei welchen sich der Nutzer anmeldet, um am 2D Spiel teilzunehmen.
-Auch gedruckte Ausgaben sind möglich. Eine \gls{xr} Integration oder Umsetzung ist bisher nicht vorgesehen.
-Die Lehrenden der Hochschule Osnabrück konnten eine Verbesserung unter den Studierenden feststellen, die ohne \gls{sg} weniger hervorragende Leistungen erbringen.
-Leistungsstärkere Studierende profitieren weniger, jedoch wird bei allen Studierenden eine erhöhte Sozialkompetenz festgestellt.
-Nachteilig sind die hohen Kosten für die Spiellizenzen, die komplexe Einarbeitung in das System und die oft unübersichtliche Aufgabengestaltung,
-die Studierende zur Prokrastination verleitet\cite{a3}.
-Derartige Spiele z.B.
-Wirtschaftssimulationen\cite{a11} gilt es nun in \gls{xr} zu transferieren und die Lehre der Wirtschaftswissenschaften durch \gls{cg} zu erweitern, ohne die Vorteile des Spiels zu verlieren.
-
-\subsection{Aspekte des \gls{sg}s in der \gls{cg} Lehre und eine mögliche Umsetzungsstrategie mittels \gls{xr}}
-
-Bevor ein \gls{sg} für eine Lehrveranstaltung erstellt werden kann, müssen nach\cite{a14} drei Teilbereiche umgesetzt werden:
-Realität (wie das Spiel mit der physischen Welt verbunden ist), Bedeutung (welcher Wert erreicht werden soll)
-und Spiel (wie man spielerische Aktivitäten schafft)\cite{a14}.
-Feng, Amor, Gonzales und Lovreglio\cite{a15} formulieren elf Fragen, um diese drei Hauptaspekte zu erlangen.
-Insbesondere pädagogische und verhaltensbezogene Aspekte und Ergebnisse stehen dabei im Vordergrund.
-
-\begin{table}[]
-\caption{Systematische literaturbezogene Forschungsfragen nach\cite{a14}}
-\begin{tabular}{|l|l|}
-\hline
-1  & Welche Unterrichtsmethoden werden verwendet?                                                                                                                           \\ \hline
-2  & Welche Lernziele werden verfolgt?                                                                                                                                      \\ \hline
-3  & Wie sehen die Lernmaßnahmen aus?                                                                                                                                       \\ \hline
-4  & Welche Ergebnisse bezüglich des Verhaltens werden erzielt?                                                                                                                                \\ \hline
-5  & Wie sehen die Verhaltensmaßnahmen aus?                                                                                                                                      \\ \hline
-6  & Welche Navigations-Lösungen gibt es?                                                                                                                                   \\ \hline
-7  & Wie werden Sinne angeregt?                                                                                                                                             \\ \hline
-8  & \begin{tabular}[c]{@{}l@{}}Welche narrativen Methoden gibt es, um Teilnehmer zu\\ermutigen, der Spielhandlung zu folgen und sie abzuschließen?\end{tabular} \\ \hline
-9  & Wie werden Gefahren simuliert?                                                                                                                                         \\ \hline
-10 & \begin{tabular}[c]{@{}l@{}}Gibt es nicht spielbare Charaktere und was tragen\\sie zum Spiel bei?\end{tabular}                                                                                              \\ \hline
-11 & Wie kann man die Erfahrungen der Teilnahme bewerten?                                                                                                                   \\ \hline
-\end{tabular}
-\label{table:firsttable}
-\end{table}
-%\cite{a14}
-
-Die Varianz der Darstellung der Lehre der \gls{cg} ist groß. 
-Eine mögliche Umsetzung wäre die Modellierung und Berechnung eines eigenen \gls{xr} Erlebnisses,
-welches mit neu erlernten Funktionen immer komplexer wird. Angefangen beim schwarzen oder durchsichtigen Bildschirm lassen sich Aufgaben und Fragen stellen,
-die den Studierenden neue mathematische Funktionen vermitteln und aus diesen Objekte, Strukturen und Segmente erzeugen. 
-Studierende können ihre Berechnung bzw. das modellierte Ergebnis direkt auf der \gls{vr} sehen und vergleichen und bekommen unmittelbar Feedback. 
-\gls{cg} wird mittels \gls{xr} für Studierende greifbar gemacht. 
-Die Komplexität wird langsam gesteigert, Funktionen und Modellierungen überlagern sich und ergeben ein Gesamtwerk, welches das Ziel der Vorlesung ist.
-
-Bezieht man die Forschungsfragen aus Tabelle \ref{table:firsttable} auf die Lehre der \gls{cg} und die Software des \gls{xr} auf die Erstellung eines solchen Erlebnisses,
-lässt sich u.a. diese Umsetzungsmöglichkeit finden, welche im nachfolgenden Absatz detaillierter aufgegriffen wird:
-
-\begin{itemize}
-\item Die Lehre beinhaltet Methoden und Schwierigkeiten der Abbildung einer dreidimensionalen Szene (real oder modelliert) auf ein zweidimensionales Ausgabegerät (Bildschirm)\cite{scholl}.
-\item 1: Mittels \gls{xr} soll \gls{cg} erklärt werden; da \gls{xr} ein Teilgebiet der \gls{cg} ist, kann hier eine aufbauende Methodik verwendet werden,
-beispielsweise angefangen vom einfachen Farbton und dessen Berechnungen über Geometrien und Modellierungen bis hin zu Konvertierungen.
-Programme und Funktionen, welche Studierende selbst programmieren, können direkten Einfluss auf das \gls{xr} Ergebnis haben.
-\item 2: Neben graphischen Grundfunktionen werden 3D Objekte geometrisch modelliert und diese auf 2D Ausgabegeräten dargestellt und die GPU-Programmierung eingeführt.
-\item 3: Studierende erkennen Zusammenhänge zwischen mathematischen Funktionen und deren Parametern zur Darstellung von Objekten.
-\item 4: Ziel ist das Verständnis der mathematischen Verfahren und der Algorithmen, die zur Erzeugung von Grafiken in der Computergrafik eingesetzt werden;
-Computergrafiken sollen unter Anwendung der erlernten Verfahren programmiert werden.
-\item 5: Studierende erarbeiten einzeln und in Gruppen schrittweise einzelne Funktionen und erzielen zum Schluss ein \gls{xr} Gesamtergebnis.
-\item 6: Neben der Strukturierung durch vorgegebene mathematische Funktionen, sortiert nach Komplexität,
-erfolgt die Hardware-Steuerung mittels händischer Steuerung mit aktiver Sensorik.
-\item 7: Sinne werden durch die \gls{cg} vorrangig grafisch angesprochen.
-Akustisch können Aktionen, Anwendungen von Gleichungen und Funktionen untermalt werden und abhängig vom Ton positive und negative Ergebnisse betont werden.
-Haptisch und olfaktorisch entfallen bei der hier gewählten Lösung.
-\item 8: Das Ziel des Spiels ist ein Gesamtwerk; eine Transformation der eigenen Funktionen und 3D Modellierungen auf eine 2D Oberfläche;
-Spieler werden angehalten, ihre Oberfläche themenabhängig mit sämtlichen verfügbaren Funktionen kreativ zu gestalten.
-\item 9: Gefahren, Schwierigkeiten und Fehler werden durch grafische Fehldarstellungen oder fehlerhafte Programmierung betont
-und akustisch untermalt.
-\item 10: Lehrende und Mentoren, können von außen das Spiel beeinflussen und unterstützend zur Seite stehen.
-\item 11: Bewertet werden das Gesamtergebnis und die Integration aller verfügbaren Komponenten und deren Kombination.
-Studierende sollen ihr Ergebnis parametrisierbar und veränderlich gestalten und somit beweisen, dass sie die Varianz der \gls{cg} verstanden haben.
-\end{itemize}
-
-Die aufgeführten Stichpunkte beinhalten eine Lösungsmöglichkeit der Umsetzung der Lehre der \gls{cg} mittels \gls{xr}.
-Weitere Möglichkeiten, wie Rollenspiele oder Abenteuer mit mathematischen und modellierbaren Hindernissen und Aufgaben, sind ebenso möglich.
-Nachfolgend wird die Umsetzung eines eigenen \gls{cg} Projektes mit \gls{xr} als Anzeigemedium mittels einer verfügbaren Software betrachtet.
 
@@
 
-\subsection{Umsetzung mittels einer beispielhaften kommerziell-verfügbaren Software-Applikation}
+\section{Embedded System Software}
 
-Am Beispiel der Shader-Erstellung wird nun die zuvor definierte Umsetzung des \gls{sg}s erläutert. 
-Ein wichtiger Bestandteil der \gls{cg} ist die Entwicklung von Shadern. 
-Dies sind kleine Programme, welche direkt auf dem Grafikbeschleuniger eines Computers ausgeführt werden können.
-Die Darstellung (Rendering) von 3D Objekten auf dem Anzeigegerät wird maßgeblich durch Shader beeinflusst. 
-Hierbei durchläuft ein Objekt eine Reihe von mathematischen Operationen, welche die visuelle Darstellung beeinflussen (Renderpipeline). 
-So lassen sich unter anderem Licht-Reflexionen auf das Objekt projizieren oder Weichzeichner-Effekte darstellen.
-Das Entwickeln solcher Programme ist ein wichtiger Bestandteil der \gls{cg} Lehrveranstaltung.
-Hier erstellen die Studierenden im Verlauf eines Projekts verschiedene Shader-Programme.
-Im Rahmen der Vorlesung wird der Aufbau dieser anhand von Beispielen exemplarisch gezeigt und die Studierenden können diese Beispiele im Nachhinein nachvollziehen.
+\subsection{Automatic Sensor Numbering}
 
-Es bieten eine visuelle Repräsentation der erstellten Renderpipeline und deren Einzelschritte diverse Vorteile.
-Änderungen eines Schrittes können direkt visuell nachvollzogen werden, welche allein durch den Quellcode nicht direkt ersichtlich sind.
-Diese Darstellungsform unterstütz einen effizienten Wissenstransfer, da das Verständnis einzelner Funktionen sowie deren Zusammenspiel interaktiv dargestellt wird.
-Exemplarisch bietet die Shadertool-Software\cite{shadertool} solch eine Darstellung an.
-Hier wird die Renderpipeline in einem 2D-Modus visuell dargestellt (s. Abbildung \ref{shadertool1_fig}) und Änderungen werden fortlaufend visualisiert.
+\section{Analysis Software Framework}
 
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=8cm]{shadertool_1.png}}
-\caption{Shadertool Software im 2D Modus\cite{shadertool}}
-\label{shadertool1_fig}
-\end{figure}
-
-Da im Bereich der \gls{cg} und somit auch in der \gls{cg} Lehrveranstaltung nahezu ausschließlich mit 3D Objekten gearbeitet wird,
-bietet sich zusätzlich die Verwendung der \gls{xr} Technologie an.
-Mit dieser ist es möglich, die erstellten Objekte, Grafiken und Shader-Effekte immersiv zu erleben und zudem qualitativ beurteilen zu können.
-
-Am Beispiel der Shadertool Software\cite{shadertool} ist es möglich, diese in einen \gls{vr}-Modus zu schalten, welcher zum einen die erstellte Renderpipeline räumlich darstellt
-und zum anderen die visuellen Darstellungen der Objekte erlebbar macht.
-Somit ist es schnell möglich, visuelle Unstimmigkeiten, welche durch die Shader-Programme erzeugt werden, zu identifizieren, jedoch bietet dieser Ansatz keine direkten \gls{sg} Möglichkeiten.
-Die Software wurde als simples Werkzeug konzipiert.
-Um solch eine Software mittels \gls{sg} Ansatz verwenden zu können, müssen spielerische Elemente sowie gezielte Aufgabenstellungen für zu erreichenden Lernziele hinzugefügt werden.
-
-\subsection{Analyse der Umsetzung}
-
-Bei dem eben erläuterten Shader-Tool handelt es sich um eine spezialisierte Lösung, welche nur für diesen Einsatzbereich
-verwendet werden kann. Jedoch ist der Aufwand zur Umsetzung bis in die aktive Lehrveranstaltung arbeitsintensiv.
-Zudem gibt es im Bereich der Shader-Programme, insbesondere in der \gls{cg}, kaum Möglichkeiten, diese auch in anderen Veranstaltungen einzusetzen.
-Jedoch bieten diese Lösungen den Vorteil, dass diese auf den bestmöglichen Lernerfolg ausgelegt werden können.
-Bei der Verwendung solcher Software mit zusätzlicher \gls{xr} Komponente (auch ohne das Ziel eines expliziten \gls{sg} Ansatzes), ist es möglich, mit wenig Aufwand eine immersive Erfahrung zu erzeugen.
-Dies ist insbesondere auf das Themengebiet der \gls{cg} zurückzuführen, in der die Lehrinhalte und insbesondere das Erstellen und Visualisieren von 3D-Objekten, schnell grafisch dargestellt werden können.
-Viele der verfügbaren 3D-Grafikprogramme (z.
-B.
-Blender\cite{blender} ab Version 3.0) und 3D-Engines (z.
-B.
-Unity\cite{unity3d}) unterstützen bereits \gls{xr} Funktionen sowohl in der Darstellung von 3D-Szenen und Objekten als auch während der Bearbeitung.
-Da einige dieser Software-Lösungen bereits in der \gls{cg} eingesetzt werden, ist hier eine Integration von \gls{xr} ohne viel Aufwand möglich.
-
-Ein zusätzlicher Nachteil dieser Software und der oben genannten Alternativen ist, dass diese leistungsstarke Hardware erfordern.
-Hier wird ein für die Anwendung geeigneter Computer, welcher mit einem leistungsstarken Grafikbeschleuniger ausgestattet ist, benötigt.
-Zudem muss auch ein \gls{vr}-Headset verwendet werden, welches den Anforderungen der Software gerecht wird.
-Diese Hardwarelimitierungen erschweren die Skalierbarkeit in Lehrveranstaltungen mit mehreren Studierenden und Gruppenarbeiten.
-
-Um dieses Problem zu lösen, muss auf kostengünstige Hardware zurückgegriffen werden, um eine kostengünstige Skalierung zu ermöglichen.
-Die Verwendung eines modernen Mobiltelefons (smartes Endgerät), welche über hochauflösende Bildschirme, sowie schnelle Prozessoren verfügen, können hier Abhilfe schaffen.
-Zusätzlich wird eine Halterung benötigt, welche im Zusammenspiel mit dem Mobiltelefon als \gls{vr}-Headset fungiert.
-Ein bekanntes Beispiel für eine kostengünstige Lösung, ist das von Google entwickelte Open-Source Projekt Google Cardboard\cite{googlecardboard}.
-
-Hier wird das Mobiltelefon in einen einfachen Papierrahmen eingehängt, welcher dann vor den Augen befestigt werden kann.
-Somit steht eine einfache Möglichkeit \gls{vr}-Inhalte mittels spezieller dafür angepasster Applikationen darstellen zu können zur Verfügung.
-
-Durch den einfachen Aufbau des Headsets bietet dies keine weiteren Interaktionsmöglichkeiten für die Nutzer.
-Hier kann nur sehr eingeschränkt direkt mit dem Inhalt interagiert werden, welches einen Einsatz bei Spielen oder \gls{cg}-Anwendungen erschwert.
-
-Dazu können verschiedene externe Eingabegeräte verwendet werden.
-U.a. ist es möglich mittels Hand-Controller, Handgesten an die Anwendung zu übermitteln.
-Alle externen Controller werden dabei i. d. R. kabellos per Bluetooth mit dem Mobiltelefon gekoppelt.
-Somit ist auch ein Ausleihen solcher Controller an die Studierenden möglich.
-
-Da bei dieser Lösung ein Mobiltelefon zum Einsatz kommt, kann die in diesem Beispiel untersuchte Shader-Tool Software\cite{shadertool} nicht auf dieser Hardware-Plattform ausgeführt werden.
-Es gibt keine direkte Alternative, jedoch zeigen Webseiten, wie z. B. Shadertoy\cite{shadertoy}, dass es möglich ist, eindrucksvolle Shader performant im Browser darzustellen.
-Dabei können verschiedene Shader direkt im Browser erstellt und bearbeitet werden und können somit auch direkt auf einem Mobiltelefon angezeigt werden.
-Lediglich die \gls{xr} oder insbesondere \gls{vr} Unterstützung fehlen.
-
-Andere Software-Pakete, wie Unity\cite{unity3d}, bieten hier bereits eine vollständige Entwicklungsumgebung für \gls{xr} Anwendungen an.
-Diese können nach dem Erstellen einer Applikation auf das Mobiltelefon geladen werden und z. B. mittels des Google Cardboard-Headsets\cite{googlecardboard} ausprobiert werden.
-
-Eine solche Lösung eignet sich für eine weitere Untersuchung im Einsatz in der \gls{cg}-Lehre.
-Da es sich zum einen um eine kostengünstige, gut skalierbare \gls{vr}-Plattform handelt und es zum anderen bereits einige Softwarekomponenten gibt, 
-welche sich mit den Lehrinhalten der \gls{cg} verwenden lassen und mit dieser kompatibel sind.
-Die Skalierbarkeit des Systems macht es nicht nur für neue Lerninhalte einfacher erweiterbar, sondern auch für weitere, zukünftige \gls{xr} Technologien modular integrierbar.
+\subsection{Data analysis pipeline}
 
@@
 
-Ein wichtiger Punkt bei der Verwendung von \gls{sg} in der Lehre, ist die anschließende Evaluation des Lernerfolgs.
-Zusätzlich zur Wissensvermittlung ist auch die Akzeptanz des Zielpublikums eine wichtige Messgröße.
-Hierzu hat die Hochschule Osnabrück eine Handlungsempfehlung aus gewonnenen Erkenntnissen aus dem \gls{gbl} Gebiet zusammengestellt\cite{a3}.
-Diese umfasst zudem die folgenden Punkte, um \gls{sg} in der Lehre evaluieren zu können.
-Das Einholen von Feedback von den Lehrenden sowie von den Studierenden ist essenziell.
-Dies geschieht zum einen mit Teilnehmern, bei denen eine Wissensvermittlung mittels \gls{sg} erfolgte und zum anderen mit einer zweiten Gruppe,
-bei der die Wissensvermittlung durch klassische Aufgaben umgesetzt wurde.
-
-Dieser Feedback-Prozess ist insbesondere bei der Wissensvermittlung durch \gls{xr} Technologien relevant.
-Jeder Studierende nimmt die \gls{xr} Umgebung unter Umständen anders wahr und interagiert unterschiedlich mit dieser.
-Anders als bei einer fest vorgegebenen \gls{sg} Anwendung, welche unter Umständen nur wenige Interaktionsmöglichkeiten bietet, ist die \gls{xr} Technologie
-darauf ausgelegt, den Teilnehmern mehr Interaktionsmöglichkeiten zu bieten.
-
-Demnach muss auch der Feedback-Prozess angepasst werden. Hierzu kann nicht nur auf ein reines Feedback der Teilnehmer,
-sondern es muss auch auf eine externe Gruppe zugrückgegriffen werden, welche die Teilnehmerinteraktionen während der Anwendung in \gls{xr} beobachtet.
-Diese Erkenntnisse, wie die Teilnehmer in der \gls{xr} Umgebung interagieren, geben zusätzlich zu dem oben genannten Feedback-Prozess Aufschluss,
-ob die Anwendung den Teilnehmerfokus auf die Wissensvermittlung lenkt.
-
-Für die Evaluation im Bereich der Lehre der \gls{cg} empfiehlt sich eine Evaluation des Gesamtergebnisses.
-Diese beinhaltet die von den Studierenden erstellte \gls{xr} Umgebung und die darin verwendeten \gls{cg} Komponenten und Funktionen.
-Um Studierende von der Verwendung der \gls{xr} Technologie in der Lehre nicht auszuschließen, ist eine zusätzliche Gruppe von Betreuern, wie Tutoren, nötig,
-welche den Prozess und die Beteiligung der Studierenden begleiten.
-
-Zudem sollte keine Momentaufnahme als Evaluation betrachtet werden, sondern ein Vergleich der Ergebnisse der Teilnehmergruppen über verschiedene Semester zu Rate gezogen werden,
-um Aufschluss über mögliche Änderungen, Verbesserungen oder gar Verschlechterungen geben zu können.
-
-Abschließend ist festzuhalten, dass u. U. nicht jeder Studierende an dem \gls{xr} Erlebnis teilnehmen möchte oder dieses nicht anwenden kann. 
-Zudem dürfen jene, welche das Projekt im Verlauf des Semesters nicht abschließen können, nicht ausgeschlossen werden.
-Für diese muss ein konservativer Lösungsweg angeboten werden.
 %-----------------------------------------------------------------------------------------------------------------------------------------------
@@
 
-\section{Fazit und Ausblick}
-
-\gls{sg}, insbesondere in Verbindung mit \gls{xr}, bietet in der hochschuldidaktischen Lehre ein großes Potential.
-Die z. T. bereits etablierte Anwendung des 2D \gls{sg}s in der Wirtschaftslehre hat bewiesen, 
-dass die Methodik sowohl umsetzbar ist, als auch Studierende aller Leistungsbereiche fördert. 
-Anhand der exemplarischen Umsetzungsmöglichkeit in der \gls{cg} Lehrveranstaltung wurde gezeigt,
-dass es möglich ist, \gls{xr} Technologien so einzusetzen, dass diese eine Wissensvermittlung unterstützen. 
-Die Varianz an Umsetzungsmöglichkeit ist enorm; 
-da \gls{xr} ein Teilbereich der \gls{cg} ist, bietet sich hier ein direkter Zusammenhang zwischen beiden Mitteln an.
-Die Lehre der \gls{cg} kann mittels \gls{xr} erklärt werden.
-Die Studierenden erstellen eine \gls{xr} Umgebung und erlernen zeitgleich Methodiken der \gls{cg}. 
-Somit entsteht ein effizienter Kreislauf. 
-Eine mögliche Umsetzungsform ist hierbei die Verwendung von bereits bestehender Software, welche keinerlei spielerische Elemente besitzt.
-Diese kann durch eine Anpassung und Weiterentwicklung mit derartigen Elementen versehen werden um somit den Anforderungen der \gls{cg} gerecht zu werden.
-Die im Beispiel analysierte Software, bietet zudem direkt eine Unterstützung für den \gls{xr} Modus und eignet sich somit für eine Evaluation.
-
-Andere Software-Applikationen, welche sich für die Verwendung in der \gls{cg} Lehrveranstaltung eignen, bringen diese Features i. d. R. nicht mit.
-Einige andere können die zuvor erstellten Modelle bzw. 3D-Welten in einer \gls{xr} Umgebung darstellen.
-Das Erstellen dieser geschieht im 2D-Modus an einem PC.
-Hier bietet diese Symbiose zwischen der Erstellung und dem Betrachten im \gls{xr} den Vorteil, dass die erlernten Konzepte immersiv erforscht werden können.
-Dabei können die positiven Erfahrungen aus den bereits angewendeten 2D-\gls{sg}s übernommen und durch die Erweiterung mittels \gls{xr} gesteigert werden.
-
-Nachteilig ist hierbei, dass all diese Ansätze mit einem hohen Arbeits- und Kostenaufwand verbunden sind.
-Potenzielle Software, welche nicht über \gls{sg} Elemente sowie \gls{xr} Funktionalitäten verfügt, muss aufwändig angepasst werden.
-
-Ebenso stellt die benötigte \gls{xr}-Hardware einen Kostenfaktor dar, da bestimmte Spezifikationen erfüllt werden müssen.
-
-Eine Möglichkeit ist die Verwendung kostengünstiger \gls{xr} Ansätze, welche ein modernes Mobiltelefon als Grundlage verwenden.
-Diese sind heutzutage in der Lage, komplexe \gls{xr}-Anwendungen auszuführen, bieten aber ohne externe Eingabegeräte kaum Möglichkeiten einer Interaktion mit der \gls{xr} Umgebung.
-Durch die Ergänzung von z. B. Hand-Controllern, welche an Studierende verliehen werden können, ist es möglich in der \gls{cg} Lehrveranstaltung ein nahezu vollständiges \gls{xr} Erlebnis zu bieten.
-
-Abschließend ist festzuhalten, dass eine Integration von \gls{sg} Ansätzen in die Lehre und insbesondere die Integration von \gls{xr} in die Lehre der \gls{cg} sinnvoll und zukunftsorientiert ist
-und zudem Wissen effizienter vermittelt.
-Studierende und Lehrende profitieren. Hürden, wie Hardware und Arbeitsaufwand, erschweren diese, sind aber nach einmaliger Umsetzung dauerhaft anwendbar.
-Eine Integration ist somit zu empfehlen.
+\section{Conclusion}
 

### 2023-09-29 documentation/sciencemeeting/dist_pdf/dist/main.2.37a89ccc187897bf765b.bundle.js
added dist

@@ -1,0 +1,1 @@
+(window.webpackJsonp=window.webpackJsonp||[]).push([[2],{12:function(n,t,e){e(13),n.exports=e(31)},28:function(n,t,e){var r={"./0-title.md":29,"./1-content.md":30};function o(n){var t=u(n);return e(t)}function u(n){if(!e.o(r,n)){var t=new Error("Cannot find module '"+n+"'");throw t.code="MODULE_NOT_FOUND",t}return r[n]}o.keys=function(){return Object.keys(r)},o.resolve=u,n.exports=o,o.id=28},29:function(n,t,e){"use strict";e.r(t),e.d(t,"slides",(function(){return l})),e.d(t,"fusumaProps",(function(){return s})),e.d(t,"default",(function(){return f}));var r=e(1),o=e.n(r),u=e(2),a=["components"];function c(){return(c=Object.assign?Object.assign.bind():function(n){for(var t=1;t<arguments.length;t++){var e=arguments[t];for(var r in e)Object.prototype.hasOwnProperty.call(e,r)&&(n[r]=e[r])}return n}).apply(this,arguments)}function i(n,t){if(null==n)return{};var e,r,o=function(n,t){if(null==n)return{};var e,r,o={},u=Object.keys(n);for(r=0;r<u.length;r++)e=u[r],t.indexOf(e)>=0||(o[e]=n[e]);return o}(n,t);if(Object.getOwnPropertySymbols){var u=Object.getOwnPropertySymbols(n);for(r=0;r<u.length;r++)e=u[r],t.indexOf(e)>=0||Object.prototype.propertyIsEnumerable.call(n,e)&&(o[e]=n[e])}return o}var l=[function(n){return Object(u.a)(o.a.Fragment,null,Object(u.a)("h1",null,"A short introduction into the MagneticReadoutProcessing ecosystem"))}],s=[{}],p={};function f(n){var t=n.components,e=i(n,a);return Object(u.a)("wrapper",c({},p,e,{components:t,mdxType:"MDXLayout"}),Object(u.a)("h1",null,"A short introduction into the MagneticReadoutProcessing ecosystem"))}f.isMDXComponent=!0},30:function(n,t,e){"use strict";e.r(t),e.d(t,"slides",(function(){return l})),e.d(t,"fusumaProps",(function(){return s})),e.d(t,"default",(function(){return f}));var r=e(1),o=e.n(r),u=e(2),a=["components
[…]

### 2023-09-29 documentation/sciencemeeting/dist_pdf/dist/runtime.3e2fa6cf750654d58c79.bundle.js

@@ -1,0 +1,1 @@
+!function(e){function r(r){for(var n,o,s=r[0],u=r[1],d=r[2],f=r[3]||[],l=0,v=[];l<s.length;l++)o=s[l],Object.prototype.hasOwnProperty.call(a,o)&&a[o]&&v.push(a[o][0]),a[o]=0;for(n in u)Object.prototype.hasOwnProperty.call(u,n)&&(e[n]=u[n]);for(p&&p(r),c.push.apply(c,f);v.length;)v.shift()();return i.push.apply(i,d||[]),t()}function t(){for(var e,r=0;r<i.length;r++){for(var t=i[r],n=!0,o=1;o<t.length;o++){var d=t[o];0!==a[d]&&(n=!1)}n&&(i.splice(r--,1),e=u(u.s=t[0]))}return 0===i.length&&(c.forEach((function(e){if(void 0===a[e]){a[e]=null;var r=document.createElement("link");u.nc&&r.setAttribute("nonce",u.nc),r.rel="prefetch",r.as="script",r.href=s(e),document.head.appendChild(r)}})),c.length=0),e}var n={},o={4:0},a={4:0},i=[],c=[];function s(e){return u.p+""+({0:"vendors~Sidebar~presenter.host~presenter.view",1:"vendors~presenter.host~presenter.view",3:"presenter.view",6:"vendors~Mermaid",7:"vendors~Sidebar",8:"vendors~live",9:"vendors~presenter.host"}[e]||e)+"."+e+"."+{0:"27b21a38bcf442f654e6",1:"7ee3e38ac96ee028bcca",3:"6740b04b846b84ea7034",6:"6cd255889c4c329a8edf",7:"824de7816f8244f3b4ea",8:"4cee62df89dceafa9064",9:"dbaca795fbaa026812db"}[e]+".bundle.js"}function u(r){if(n[r])return n[r].exports;var t=n[r]={i:r,l:!1,exports:{}};return e[r].call(t.exports,t,t.exports,u),t.l=!0,t.exports}u.e=function(e){var r=[];o[e]?r.push(o[e]):0!==o[e]&&{1:1,3:1,8:1,9:1}[e]&&r.push(o[e]=new Promise((function(r,t){for(var n=({0:"vendors~Sidebar~presenter.host~presenter.view",1:"vendors~presenter.host~presenter.view",3:"presenter.view",6:"vendors~Mermaid",7:"vendors~Sideba
[…]

### 2023-09-29 documentation/sciencemeeting/dist_pdf/dist/vendors~live.8.4cee62df89dceafa9064.bundle.js

@@ -1,0 +1,15 @@
+(window.webpackJsonp=window.webpackJsonp||[]).push([[8],{181:function(t,e,r){"use strict";r.r(e),r.d(e,"CommentsList",(function(){return So}));var n=r(1),o=r.n(n);
+/*! *****************************************************************************
+Copyright (c) Microsoft Corporation.
+
+Permission to use, copy, modify, and/or distribute this software for any
+purpose with or without fee is hereby granted.
+
+THE SOFTWARE IS PROVIDED "AS IS" AND THE AUTHOR DISCLAIMS ALL WARRANTIES WITH
+REGARD TO THIS SOFTWARE INCLUDING ALL IMPLIED WARRANTIES OF MERCHANTABILITY
+AND FITNESS. IN NO EVENT SHALL THE AUTHOR BE LIABLE FOR ANY SPECIAL, DIRECT,
+INDIRECT, OR CONSEQUENTIAL DAMAGES OR ANY DAMAGES WHATSOEVER RESULTING FROM
+LOSS OF USE, DATA OR PROFITS, WHETHER IN AN ACTION OF CONTRACT, NEGLIGENCE OR
+OTHER TORTIOUS ACTION, ARISING OUT OF OR IN CONNECTION WITH THE USE OR
+PERFORMANCE OF THIS SOFTWARE.
[…]

### 2023-09-29 documentation/sciencemeeting/dist_pdf/dist/vendors~presenter.host.9.dbaca795fbaa026812db.bundle.js

@@ -1,0 +1,18 @@
+(window.webpackJsonp=window.webpackJsonp||[]).push([[9],{164:function(e,t,n){"use strict";Object.defineProperty(t,"__esModule",{value:!0});var r,o=n(165),i=(r=o)&&r.__esModule?r:{default:r};t.default=i.default,e.exports=t.default},165:function(e,t,n){"use strict";function r(e){return(r="function"==typeof Symbol&&"symbol"==typeof Symbol.iterator?function(e){return typeof e}:function(e){return e&&"function"==typeof Symbol&&e.constructor===Symbol&&e!==Symbol.prototype?"symbol":typeof e})(e)}Object.defineProperty(t,"__esModule",{value:!0}),t.bodyOpenClassName=t.portalClassName=void 0;var o=Object.assign||function(e){for(var t=1;t<arguments.length;t++){var n=arguments[t];for(var r in n)Object.prototype.hasOwnProperty.call(n,r)&&(e[r]=n[r])}return e},i=function(){function e(e,t){for(var n=0;n<t.length;n++){var r=t[n];r.enumerable=r.enumerable||!1,r.configurable=!0,"value"in r&&(r.writable=!0),Object.defineProperty(e,r.key,r)}}return function(t,n,r){return n&&e(t.prototype,n),r&&e(t,r),t}}(),a=n(1),l=y(a),u=y(n(8)),c=y(n(36)),s=y(n(166)),f=function(e){if(e&&e.__esModule)return e;var t={};if(null!=e)for(var n in e)Object.prototype.hasOwnProperty.call(e,n)&&(t[n]=e[n]);return t.default=e,t}(n(81)),p=n(54),d=y(p),h=n(173);function y(e){return e&&e.__esModule?e:{default:e}}function m(e,t){if(!(e instanceof t))throw new TypeError("Cannot call a class as a function")}function v(e,t){if(!e)throw new ReferenceError("this hasn't been initialised - super() hasn't been called");return!t||"object"!==r(t)&&"function"!=typeof t?e:t}var b=t.portalClassName="ReactModalPortal",g=t.bodyOpenClassName="ReactModal__Body--open",w=p.canUseDOM&&void 0!==u.default.createPortal,O=function(e){return document.createElement(e)},S=function(){return w?u.default.createPortal:u.default.unstable_renderSubtreeIntoContainer};function E(e){return e()}var C=function(e){function t(){var e,n,r;m(this,t);for(var i=arguments.length,a=Array(i
[…]

### 2023-09-29 documentation/thesis/deploly_server/.vitepress/dist/assets/index.md.c68979f2.lean.js

@@ -1,0 +1,1 @@
+import{_ as e,o as t,c as a}from"./chunks/framework.e51e4293.js";const p=JSON.parse('{"title":"","description":"","frontmatter":{"layout":"home","hero":{"name":"Awesome Master Thesis","text":"A online thesis viewer","tagline":"My great project tagline"},"features":[{"title":"Download PDF","details":"Lorem ipsum dolor sit amet, consectetur adipiscing elit","actions":[{"theme":"brand","text":"Markdown Examples","link":"/markdown-examples"},{"theme":"alt","text":"API Examples","link":"/api-examples"}]}]},"headers":[],"relativePath":"index.md","filePath":"index.md"}'),n={name:"index.md"};function s(i,o,r,l,m,d){return t(),a("div")}const x=e(n,[["render",s]]);export{p as __pageData,x as default};

### 2023-09-29 documentation/thesis/build_thesis_docker.sh
.

@@ -1,14 +1,14 @@
 #!/bin/bash
-
-if [[ "$(docker images -q mrpthesis:latest 2> /dev/null)" == "" ]]; then
+IMAGE=mrpthesis:latest
+if [[ "$(docker images -q $IMAGE 2> /dev/null)" == "" ]]; then
   echo "mrpthesis:latest IMAGE BUILD STARTED"
-  docker build -t mrpthesis:latest .
+  docker build -t $IMAGE .
 else
- echo "markdownthesisbuilder:latest IMAGE EXISTS; NO BUILD REQUIRED"
+ echo "IMAGE EXISTS; NO BUILD REQUIRED"
 fi
 
 
-docker run -i --rm -v "$(pwd)":/var/thesis mrpthesis:latest
+docker run -i --rm -v "$(pwd)":/var/thesis $IMAGE
 
 
 

### 2023-09-29 src/MagneticReadoutProcessing/udpp/static/dist/Main.js

@@ -1,0 +1,9 @@
+// --- IMPORTS ---
+import { InspectorPanel } from './UI/InspectorPanel.js';
+import { NodePanel } from './UI/NodePanel.js';
+import { OptionPanel } from './UI/OptionPanel.js';
+import { cogIcon, nodePanel, optionPanel } from './UI/Shared.js';
+// Initialize the app
+let inspector = new InspectorPanel();
+let nodeGraph = new NodePanel(nodePanel, inspector);
+let options = new OptionPanel(cogIcon, optionPanel);

### 2023-09-29 src/MagneticReadoutProcessing/udpp/static/dist/UI/Block.js

@@ -1,0 +1,193 @@
+import { elementToBlock, uuidv4 } from "./Shared.js";
+export class Block {
+    SetProperties(properties) {
+        this.properties = properties;
+        for (const prop in this.properties) {
+            this.properties[prop].setValue = (val) => {
+                if (val === null)
+                    return;
+                this.properties[prop].value = val;
+                this.OnPropertyChanged(prop);
+            };
+        }
+        // Let all props know they changed
+        for (const prop in this.properties) {
+            this.OnPropertyChanged(prop);
+        }
+        // Refresh the properties
+        this.inspector.refreshProperties();
+    }
+    DeepCopyProperties() {
+        let copy = {};
+        for (const prop in this.properties) {
+            const propValue = this.properties[prop];
+            const propCopy = {
+                type: propValue.type,
+                value: JSON.parse(JSON.stringify(propValue.value))
+            };
+            copy[prop] = propCopy;
+        }
+        return copy;
+    }
+    constructor(inspector) {
+        // The position of the block in the workspace
+        this.position = [0, 0];
+        // The scale of the block
+        this.scale = 1;
+        this.cachedValue = [];
+        this.isDirty = true;
+        this.properties = {
+            "Name": { type: "input", value: "default" },
+            "Prompt": { type: "textarea", value: "Some prompt" },
+            "Generate": { type: "button", value: "Click me" },
+            "Creativity": { type: "slider", value: 50 },
+            "Code": { type: "textarea", value: "return 5;" },
+            // add as many properties as you like...
+        };
+        if (inspector === null)
+            throw new Error("Inspector cannot be null!");
+        this.inspector = inspector;
+        this.uuid = uuidv4();
+        // Execute the code on the input
+        this.promise = (input) => {
+            // Execute the Copy property
+            const code = this.properties["Code"].value;
+            // Function(..) the code and return the result
+            let output = Function("input", code)(input);
+            // If the output is not an array, wrap it in one
+            if (!Array.isArray(output))
+                output = [output];
+            return Promise.resolve(output);
+        };
+        this.inputs = [];
+        this.outputs = [];
+        this.size = [100, 100];
+        this.element = this.CreateBlockHTML(0, 0);
+        elementToBlock.set(this.element, this);
+        for (const prop in this.properties) {
[…]

### 2023-09-29 src/MagneticReadoutProcessing/udpp/static/dist/UI/NodePanel.js

@@ -1,0 +1,335 @@
+// --- IMPORTS ---
+import { Block } from './Block.js';
+import { Socket } from './Socket.js';
+import { Edge } from './Edge.js';
+import { SocketType, ToBlock, ToSocket, nodeConnections, contextMenu, nodePanel, nodeTypes, workspace, elementToBlock } from './Shared.js';
+export class NodePanel {
+    constructor(document, inspector) {
+        this.selectedSocket = null;
+        this.selectedBlock = null;
+        this.lastMousePosition = null;
+        this.connectorPath = null;
+        this.shouldDragNode = false;
+        this.shouldDragGraph = false;
+        this.graphOffset = { x: 0, y: 0 };
+        this.scaleFactor = 1;
+        this.inspector = null;
+        this.edges = [];
+        this.blocks = [];
+        this.panel = document;
+        this.inspector = inspector;
+        this.AddListeners();
+    }
+    AddListeners() {
+        this.panel.addEventListener('mousedown', (evt) => this.OnLeftClickDown(evt));
+        this.panel.addEventListener('mouseup', (evt) => this.OnLeftClickUp(evt));
+        this.panel.addEventListener('mousemove', (evt) => this.OnMouseMove(evt));
+        this.panel.addEventListener('contextmenu', (evt) => this.OnRightClick(evt));
+        this.panel.addEventListener('wheel', (evt) => this.OnMouseWheel(evt));
+        // This needs to listen from document, not panel
+        document.addEventListener('keydown', (evt) => this.OnKeyDown(evt));
+    }
+    GetElementOffset(el) {
+        let _x = 0;
+        let _y = 0;
+        while (el && !isNaN(el.offsetLeft) && !isNaN(el.offsetTop)) {
+            _x += el.offsetLeft - el.scrollLeft;
+            _y += el.offsetTop - el.scrollTop;
+            el = el.offsetParent;
+        }
+        return { top: _y, left: _x };
+    }
+    CreateConnection(startSocket) {
+        const path = document.createElementNS('http://www.w3.org/2000/svg', 'path');
+        path.setAttribute('stroke', startSocket.color);
+        path.setAttribute('stroke-width', '3');
+        path.setAttribute('fill', 'none');
+        path.classList.add('edge');
+        nodeConnections.appendChild(path);
+        return path;
+    }
+    UpdateConnection(path, startSocket, endSocket, event) {
+        const startPos = this.GetElementOffset(startSocket.element);
[…]

### 2023-09-29 src/MagneticReadoutProcessing/udpp/static/dist/UI/Socket.js

@@ -1,0 +1,92 @@
+import { SocketType, elementToSocket, socketColorTable } from "./Shared.js";
+export class Socket {
+    constructor(owner, name, dataType, socketType, socketNumber) {
+        this.socketNumber = 0;
+        this.owner = owner;
+        this.name = name;
+        this.dataType = dataType;
+        this.socketType = socketType;
+        this.edges = [];
+        this.connected = false;
+        this.size = [10, 10];
+        this.color = socketColorTable[dataType] || socketColorTable['default'];
+        this.socketNumber = socketNumber;
+        this.element = this.CreateElement();
+        elementToSocket.set(this.element, this);
+    }
+    Connect(edge) {
+        var _a;
+        this.edges.push(edge);
+        this.connected = true;
+        (_a = this.element.querySelector('.socket-label')) === null || _a === void 0 ? void 0 : _a.classList.add('connected');
+        this.owner.SetDirty();
+    }
+    Disconnect(edge) {
+        var _a;
+        this.edges.splice(this.edges.indexOf(edge), 1);
+        this.connected = this.edges.length > 0;
+        (_a = this.element.querySelector('.socket-label')) === null || _a === void 0 ? void 0 : _a.classList.remove('connected');
+        this.owner.SetDirty();
+    }
+    DisconnectAll() {
+        var _a;
+        for (let edge of this.edges) {
+            if (edge.startSocket === this) {
+                edge.endSocket.Disconnect(edge);
+            }
+            else {
+                edge.startSocket.Disconnect(edge);
+            }
+            edge.Destroy();
+        }
+        this.edges = [];
+        this.connected = false;
+        (_a = this.element.querySelector('.socket-label')) === null || _a === void 0 ? void 0 : _a.classList.remove('connected');
+        this.owner.SetDirty();
+    }
+    CreateElement() {
+        let newSocket = document.createElement('div');
+        let socketName = (this.socketType === SocketType.INPUT ? 'input' : 'output');
+        newSocket.className = 'socket ' + socketName + ' ' + this.dataType;
+        newSocket.style.width = this.size[0] + 'px';
+        newSocket.style.height = this.size[1] + 'px';
+        newSocket.style.backgroundColor = this.color;
+        let label = document.createElement('span');
+        label.className = 'socket-label';
+        label.innerHTML = this.name;
+        if (this.socketType === SocketType.INPUT) {
+            newSocket.appendChild(label);
+        }
+        else {
+            newSocket.insertBefore(label, newSocket.firstChild);
+        }
[…]

### 2023-09-29 src/MagneticReadoutProcessing/udpp/static/ts/Main.ts

@@ -1,0 +1,11 @@
+// --- IMPORTS ---
+import { InspectorPanel } from './UI/InspectorPanel.js';
+import { NodePanel } from './UI/NodePanel.js';
+import { OptionPanel } from './UI/OptionPanel.js';
+import { cogIcon, nodePanel, optionPanel } from './UI/Shared.js';
+
+
+// Initialize the app
+let inspector: InspectorPanel = new InspectorPanel();
+let nodeGraph: NodePanel = new NodePanel(nodePanel, inspector);
+let options: OptionPanel = new OptionPanel(cogIcon, optionPanel);

### 2023-09-29 src/MagneticReadoutProcessing/udpp/static/ts/UI/Block.ts

@@ -1,0 +1,249 @@
+import { InspectorPanel } from "./InspectorPanel.js";
+import { elementToBlock, uuidv4 } from "./Shared.js";
+import { Socket } from "./Socket.js";
+
+interface BlockProperty {
+    type: "input" | "textarea" | "button" | "slider";
+    value: any;
+    setValue?: (val: any) => void;
+}
+
+export class Block {
+    public element: HTMLElement;
+    public inputs: Socket[];
+    public outputs: Socket[];
+    // The position of the block in the workspace
+    public position = [0, 0];
+    // The scale of the block
+    public scale = 1;
+
+    private promise: (inputValues: any[][]) => Promise<any[]>;
+    private uuid: string;
+    private size: number[];
+    private inspector: InspectorPanel;
+
+    private cachedValue: any[] = [];
+    private isDirty: boolean = true;
+
+    private properties: { [key: string]: BlockProperty; } = {
+        "Name": { type: "input", value: "default" },
+        "Prompt": { type: "textarea", value: "Some prompt" },
+        "Generate": { type: "button", value: "Click me" },
+        "Creativity": { type: "slider", value: 50 },
+        "Code": { type: "textarea", value: "return 5;" },
+
+        // add as many properties as you like...
+    };
+
+    public SetProperties(properties: { [key: string]: BlockProperty; }) {
+        this.properties = properties;
+
+        for (const prop in this.properties) {
+            this.properties[prop].setValue = (val: any) => {
+                if (val === null) return;
+
+                this.properties[prop].value = val;
+                this.OnPropertyChanged(prop);
+            }
+        }
+        // Let all props know they changed
+        for (const prop in this.properties) {
+            this.OnPropertyChanged(prop);
+        }
+        // Refresh the properties
+        this.inspector.refreshProperties();
+    }
+
+    public DeepCopyProperties(): { [key: string]: BlockProperty; } {
+        let copy: { [key: string]: BlockProperty; } = {};
+        for (const prop in this.properties) {
+            const propValue = this.properties[prop];
+            const propCopy: BlockProperty = {
+                type: propValue.type,
+                value: JSON.parse(JSON.stringify(propValue.value))
+            };
+            copy[prop] = propCopy;
+        }
+        return copy;
+    }
+
+    constructor(inspector: InspectorPanel | null) {
+        if (inspector === null) throw new Error("Inspector cannot be null!");
+
+        this.inspector = inspector;
+        this.uuid = uuidv4();
[…]

### 2023-09-29 src/MagneticReadoutProcessing/udpp/static/ts/UI/InspectorPanel.ts

@@ -1,0 +1,81 @@
+import { Block } from "./Block.js";
+
+export class InspectorPanel {
+    private selectedNode: Block | null = null;
+    private inspectorElement: HTMLElement;
+    private propertyContainer: HTMLElement;
+
+    constructor() {
+        this.inspectorElement = document.getElementById("inspector")!;
+        this.propertyContainer = document.getElementById("inspector-properties")!;
+    }
+
+    selectNode(node: Block) {
+        this.selectedNode = node;
+        this.refreshProperties();
+        this.inspectorElement.classList.remove("inspector-closed");
+        this.inspectorElement.classList.add("inspector-open");
+    }
+
+    deselectNode() {
+        this.selectedNode = null;
+        this.inspectorElement.classList.remove("inspector-open");
+        this.inspectorElement.classList.add("inspector-closed");
+    }
+
+    refreshProperties() {
+        this.propertyContainer.innerHTML = '';
+        if (this.selectedNode) {
+            for (const [key, prop] of Object.entries(this.selectedNode.GetProperties())) {
+                const propDiv = document.createElement('div');
+                propDiv.textContent = key;
+
+                switch (prop.type) {
+                    case 'slider':
+                        const slider = document.createElement('input');
+                        slider.type = 'range';
+                        slider.value = prop.value;
+                        slider.oninput = (e) => {
+                            if (prop.setValue !== undefined) {
+                                prop.setValue((e.target as HTMLInputElement).value);
+                            }
+                        };
+                        propDiv.appendChild(slider);
+                        break;
+
+                    case 'input':
+                        const input = document.createElement('input');
+                        input.type = 'text';
+                        input.value = prop.value;
+                        input.oninput = (e) => {
+                            if (prop.setValue !== undefined) {
+                                prop.setValue((e.target as HTMLInputElement).value);
+                            }
+                        };
+                        propDiv.appendChild(input);
+                        break;
+
+                    case 'textarea':
+                        const textarea = document.createElement('textarea');
+                        textarea.textContent = prop.value;
+                        textarea.oninput = (e) => {
+                            if (prop.setValue !== undefined) {
+                                prop.setValue((e.target as HTMLInputElement).value);
+                            }
+                        };
+                        propDiv.appendChild(textarea);
+                        break;
+
+                    case 'button':
+                        const button = document.createElement('button');
+                        button.textContent = prop.value;
[…]

### 2023-09-29 src/MagneticReadoutProcessing/udpp/static/ts/UI/NodePanel.ts

@@ -1,0 +1,389 @@
+// --- IMPORTS ---
+import { Block } from './Block.js';
+import { Socket } from './Socket.js';
+import { Edge } from './Edge.js';
+import { InspectorPanel } from './InspectorPanel.js';
+import { SocketType, ToBlock, ToSocket, nodeConnections, contextMenu, nodePanel, nodeTypes, workspace, elementToBlock } from './Shared.js';
+
+interface Offset {
+    top: number;
+    left: number;
+}
+
+export class NodePanel {
+    panel: HTMLElement;
+    selectedSocket: Socket | null = null;
+    selectedBlock: Block | null = null;
+    lastMousePosition: { x: number; y: number } | null = null;
+    connectorPath: SVGPathElement | null = null;
+    shouldDragNode = false;
+    shouldDragGraph = false;
+    graphOffset = { x: 0, y: 0 };
+    scaleFactor = 1;
+    inspector: InspectorPanel | null = null;
+
+    edges: Edge[] = [];
+    blocks: Block[] = [];
+
+    constructor(document: HTMLElement, inspector: InspectorPanel) {
+        this.panel = document;
+        this.inspector = inspector;
+        this.AddListeners();
+    }
+
+    private AddListeners() {
+        this.panel.addEventListener('mousedown', (evt) => this.OnLeftClickDown(evt));
+        this.panel.addEventListener('mouseup', (evt) => this.OnLeftClickUp(evt));
+        this.panel.addEventListener('mousemove', (evt) => this.OnMouseMove(evt));
+        this.panel.addEventListener('contextmenu', (evt) => this.OnRightClick(evt));
+        this.panel.addEventListener('wheel', (evt) => this.OnMouseWheel(evt));
+
+        // This needs to listen from document, not panel
+        document.addEventListener('keydown', (evt) => this.OnKeyDown(evt));
+    }
+
+    private GetElementOffset(el: HTMLElement): Offset {
+        let _x = 0;
+        let _y = 0;
+        while (el && !isNaN(el.offsetLeft) && !isNaN(el.offsetTop)) {
+            _x += el.offsetLeft - el.scrollLeft;
+            _y += el.offsetTop - el.scrollTop;
+            el = el.offsetParent as HTMLElement;
+        }
+        return { top: _y, left: _x };
+    }
+
+    private CreateConnection(startSocket: Socket): SVGPathElement {
+        const path = document.createElementNS('http://www.w3.org/2000/svg', 'path');
[…]

### 2023-09-29 src/MagneticReadoutProcessing/udpp/static/ts/UI/Shared.ts

@@ -1,0 +1,50 @@
+import { Block } from "./Block.js";
+import { Edge } from "./Edge.js";
+import { Socket } from "./Socket.js";
+
+export function uuidv4(): string {
+    return 'xxxxxxxx-xxxx-4xxx-yxxx-xxxxxxxxxxxx'.replace(/[xy]/g, (c) => {
+        const r = (Math.random() * 16) | 0;
+        const v = c === 'x' ? r : (r & 0x3) | 0x8;
+        return v.toString(16);
+    });
+}
+
+// Enum for input/output sockets
+export enum SocketType {
+    INPUT,
+    OUTPUT
+}
+
+export const socketColorTable: { [key: string]: string } = {
+    number: '#007fff',
+    string: '#8a2be2',
+    boolean: '#ff0080',
+    default: '#ff5800'
+};
+
+// Global params
+export const elementToBlock = new Map<HTMLElement, Block>();
+export const elementToSocket = new Map<HTMLElement, Socket>();
+export const elementToEdge = new Map<SVGElement, Edge>();
+export const nodePanel = document.getElementById('nodes') as HTMLElement;
+export const nodeConnections = document.getElementById('connections') as HTMLElement;
+export const workspace = document.getElementById('workspace') as HTMLElement;
+export const contextMenu = document.getElementById('context-menu') as HTMLElement;
+export const optionPanel = document.getElementById('option-panel') as HTMLElement;
+export const cogIcon = document.getElementById('cog-icon') as HTMLElement;
+export const nodeTypes: string[] = ['NodeType1', 'NodeType2', 'NodeType3'];
+
+
+export function ToBlock(element: HTMLElement): Block | undefined {
+    return elementToBlock.get(element);
+}
+
+export function ToSocket(element: HTMLElement): Socket | undefined {
+    if (element.classList.contains('socket-label')) {
+        return elementToSocket.get(element.parentElement!);
+    }
+    else {
+        return elementToSocket.get(element);
+    }
+}

### 2023-09-29 src/MagneticReadoutProcessing/udpp/static/ts/UI/Socket.ts

@@ -1,0 +1,110 @@
+import { Block } from "./Block.js";
+import { Edge } from "./Edge.js";
+import { SocketType, elementToSocket, socketColorTable } from "./Shared.js";
+
+export class Socket {
+    owner: Block;
+    name: string;
+    dataType: string;
+    socketType: SocketType;
+    edges: Edge[];
+    connected: boolean;
+    size: number[];
+    color: string;
+    element: HTMLElement;
+    socketNumber: number = 0;
+
+    constructor(owner: Block, name: string, dataType: string, socketType: SocketType, socketNumber: number) {
+        this.owner = owner;
+        this.name = name;
+        this.dataType = dataType;
+        this.socketType = socketType;
+        this.edges = [];
+        this.connected = false;
+        this.size = [10, 10];
+        this.color = socketColorTable[dataType] || socketColorTable['default'];
+        this.socketNumber = socketNumber;
+        this.element = this.CreateElement();
+        elementToSocket.set(this.element, this);
+    }
+
+    Connect(edge: Edge) {
+        this.edges.push(edge);
+        this.connected = true;
+        this.element.querySelector('.socket-label')?.classList.add('connected');
+        this.owner.SetDirty();
+    }
+
+    Disconnect(edge: Edge) {
+        this.edges.splice(this.edges.indexOf(edge), 1);
+        this.connected = this.edges.length > 0;
+        this.element.querySelector('.socket-label')?.classList.remove('connected');
+        this.owner.SetDirty();
+    }
+
+    DisconnectAll() {
+        for (let edge of this.edges) {
+            if (edge.startSocket === this) {
+                edge.endSocket.Disconnect(edge);
+            } else {
+                edge.startSocket.Disconnect(edge);
+            }
+            edge.Destroy();
+        }
+
+        this.edges = [];
+        this.connected = false;
+        this.element.querySelector('.socket-label')?.classList.remove('connected');
+        this.owner.SetDirty();
+    }
+
+    CreateElement(): HTMLElement {
+        let newSocket = document.createElement('div');
+        let socketName = (this.socketType === SocketType.INPUT ? 'input' : 'output');
+        newSocket.className = 'socket ' + socketName + ' ' + this.dataType;
+        newSocket.style.width = this.size[0] + 'px';
+        newSocket.style.height = this.size[1] + 'px';
+        newSocket.style.backgroundColor = this.color;
+
+        let label = document.createElement('span');
+        label.className = 'socket-label';
+        label.innerHTML = this.name;
[…]

### 2023-10-03 documentation/thesis/thesis_abstract.tex
.

Especially in the construction of low-field MRI devices based on
permanent magnets, a large number of magnets are used. In order to
realize a homogeneous B0 field with these magnets, which is necessary
for many setups, the magnetic properties of these magnets should be as
similar as possible.

Due to the complex manufacturing process, especially of neodymium
magnets, the different properties, especially the direction of
magnetization, can deviate from each other, which affects the
homogeneity of the field.

To adjust the field afterwards, a passive shimming process is typically
performed, which is complex and time-consuming and requires manual
corrections to the magnets used.

To avoid this process, magnets can be systematically measured in
advance. However, in this methodology, the recording, data storage and
subsequent evaluation of the data play an important role.

The various existing solutions implement individual aspects, but do not
provide a data pipeline from aqusation to analysis.

For this use case, the MagneticReadoutProcessing library was created,
which implements different aspects of data acquisition, data storage,
analysis, and each intermediate step can be customized by the user
without having to create everything from scratch, favoring an exchange
between different user groups.

### 2023-10-03 documentation/thesis/thesis_document.tex
.

@@
-\hypertarget{motivation}{%
-\chapter{Motivation}\label{motivation}}
+\hypertarget{introduction}{%
+\chapter{Introduction}\label{introduction}}
 
-\hypertarget{tables}{%
-\chapter{Tables}\label{tables}}
+\hypertarget{fundamentals}{%
+\chapter{Fundamentals}\label{fundamentals}}
 
-\begin{longtable}[]{@{}lllll@{}}
-\caption{Das ist eine tolle Tabelle
-\label{Das_ist_eine_tolle_Tabelle.csv}}\tabularnewline
-\toprule
-year & make & model & description & price\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-year & make & model & description & price\tabularnewline
-\midrule
-\endhead
-1997 & Ford & E350 & ac, abs, moon & 3000.00\tabularnewline
-1999 & Chevy & Venture «Extended Edition» & & 4900.00\tabularnewline
-1996 & Jeep & Grand Cherokee & MUST SELL! air, moon roof, loaded &
-4799.00\tabularnewline
-\bottomrule
-\end{longtable}
+\hypertarget{permanent-magnet-mri}{%
+\section{Permanent magnet MRI}\label{permanent-magnet-mri}}
 
-Tabelle ist toll: \ref{Das_ist_eine_tolle_Tabelle.csv}
+\hypertarget{typical-b0-magnet-structures}{%
+\subsection{Typical B0 Magnet
+structures}\label{typical-b0-magnet-structures}}
 
-\hypertarget{images}{%
-\section{Images}\label{images}}
+\hypertarget{shimming-procedure}{%
+\section{Shimming procedure}\label{shimming-procedure}}
 
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Dies_ist_ein_Testbild.png}
-\caption{Dies ist ein Testbild \label{Dies_ist_ein_Testbild.png}}
-\end{figure}
+\hypertarget{state-of-the-art}{%
+\chapter{State of the art}\label{state-of-the-art}}
 
-Das Bild ist toll: \ref{Dies_ist_ein_Testbild.png}
+\hypertarget{opensource-projects}{%
+\section{Opensource projects}\label{opensource-projects}}
+
+\hypertarget{unified-sensor-interface}{%
+\section{Unified Sensor Interface}\label{unified-sensor-interface}}
+
+\hypertarget{sensor-selection}{%
+\section{Sensor selection}\label{sensor-selection}}
+
+\hypertarget{mechanical}{%
+\section{Mechanical}\label{mechanical}}
+
+\hypertarget{electrical-interface}{%
+\section{Electrical Interface}\label{electrical-interface}}
+
+\hypertarget{software-implementation}{%
+\chapter{Software implementation}\label{software-implementation}}
+
+\hypertarget{library}{%
+\section{Library}\label{library}}
+
+\hypertarget{concepts}{%
+\subsection{Concepts}\label{concepts}}
+
+\hypertarget{user-interaction-points}{%
+\subsection{User interaction points}\label{user-interaction-points}}
+
+\hypertarget{datastructures}{%
+\subsection{Datastructures}\label{datastructures}}
+
+\hypertarget{datapoints}{%
+\subsubsection{Datapoints}\label{datapoints}}
+
+\hypertarget{meta-data-management}{%
+\subsubsection{Meta-Data management}\label{meta-data-management}}
+
+\hypertarget{implementation}{%
+\subsection{Implementation}\label{implementation}}
+
+\hypertarget{examples}{%
+\subsection{Examples}\label{examples}}
+
+\hypertarget{concepts-1}{%
+\subsection{Concepts}\label{concepts-1}}
+
+\hypertarget{usability-improvements}{%
+\chapter{Usability improvements}\label{usability-improvements}}
+
+\hypertarget{commandline-interface}{%
+\section{Commandline interface}\label{commandline-interface}}
+
+\hypertarget{programmable-data-processing-pipeline}{%
+\section{Programmable data processing
+pipeline}\label{programmable-data-processing-pipeline}}
+
+\hypertarget{web-base-pipeline-configuration}{%
+\subsection{Web base pipeline
+configuration}\label{web-base-pipeline-configuration}}
+
+\hypertarget{third-party-software-support}{%
+\section{Third party software
+support}\label{third-party-software-support}}
+
+\hypertarget{package-management}{%
+\section{Package management}\label{package-management}}
+
+\hypertarget{documentation}{%
+\subsection{Documentation}\label{documentation}}
+
+\hypertarget{distribution}{%
+\subsection{Distribution}\label{distribution}}
+
+\hypertarget{continuous-integration}{%
+\subsection{Continuous Integration}\label{continuous-integration}}
+
+\hypertarget{end-to-end-testing}{%
+\subsection{End to end testing}\label{end-to-end-testing}}
+
+\hypertarget{evaluation}{%
+\chapter{Evaluation}\label{evaluation}}
+
+\hypertarget{prequesites-for-evaluation}{%
+\section{Prequesites for evaluation}\label{prequesites-for-evaluation}}
+
+\hypertarget{evaluation-confiugration}{%
+\section{Evaluation confiugration}\label{evaluation-confiugration}}
+
+\hypertarget{sensor-readout}{%
+\subsection{Sensor readout}\label{sensor-readout}}
+
+\hypertarget{processing-pipeline}{%
+\subsection{Processing pipeline}\label{processing-pipeline}}
+
+\hypertarget{test-scenarios}{%
+\section{Test scenarios}\label{test-scenarios}}
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\hypertarget{conclusion-and-dicussion}{%
+\chapter{Conclusion and dicussion}\label{conclusion-and-dicussion}}
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+\hypertarget{problems}{%
+\section{Problems}\label{problems}}
+
+\hypertarget{outlook}{%
+\section{Outlook}\label{outlook}}

### 2023-10-03 src/MagneticReadoutProcessing/udpp/UDPPFunctionCollection.py

@@ -25,15 +25,17 @@ class UDPPFunctionCollection:
 
 
     @staticmethod
-    def simulate_magnet(_count: int = 1, _random_polarisation: bool = False, _random_magnetisation: bool = False) -> [MRPReading.MRPReading]:
+    def simulate_magnet(IP_count: int = 1, IP_random_polarisation: bool = False, IP_random_magnetisation: bool = False) -> [MRPReading.MRPReading]:
         ret: [MRPReading.MRPReading] = []
 
-        for idx in range(_count):
-            rnd = MRPSimulation.MRPSimulation.generate_reading(_randomize_magnetization=_random_magnetisation, _add_random_polarisation=_random_polarisation)
+        for idx in range(IP_count):
+            rnd = MRPSimulation.MRPSimulation.generate_reading(_randomize_magnetization=IP_random_polarisation, _add_random_polarisation=IP_random_magnetisation)
             rnd.set_additional_data("simulate_magnet", idx)
             ret.append(rnd)
 
         return ret
+
+
     @staticmethod
     def readings_passthrough(readings: [MRPReading.MRPReading]) -> [MRPReading.MRPReading]:
         """
@@ -92,38 +94,38 @@ class UDPPFunctionCollection:
         return rd
 
     @staticmethod
-    def import_readings(input_folder:str = "", file_regex: str = "(.)*.mag.json") -> [MRPReading.MRPReading]:
+    def import_readings(IP_input_folder:str = "", IP_file_regex: str = "(.)*.mag.json") -> [MRPReading.MRPReading]:
         """
         Imports all readings found in the folder given from the input_folder.
         It restores all meta-data and datapoints.
 
-        :param input_folder: Folder with .mag.json readings ABS or REL-Paths are allowed
-        :type input_folder: str
+        :param IP_input_folder: Folder with .mag.json readings ABS or REL-Paths are allowed
+        :type IP_input_folder: str
 
-        :param file_regex: to only allow certain filenames using a regex string
-        :type file_regex: str
+        :param IP_file_regex: to only allow certain filenames using a regex string
+        :type IP_file_regex: str
 
         :returns: Returns the imported readings as [MRPReading.MRPReading] instances
         :rtype: [MRPReading.MRPReading]
         """
 
-        if input_folder is None or len(input_folder) <= 0:
+        if IP_input_folder is None or len(IP_input_folder) <= 0:
             raise UDPPFunctionCollectionException("import_readings: input_folder parameter empty")
[…]

### 2023-10-03 src/MagneticReadoutProcessing/udpp/UDPPFunctionTranslator.py

@@ -1,6 +1,7 @@
 """This class is handling all the pipeline translations between the user level and the actual python function execution"""
 import os
 import queue
+import random
 from pathlib import Path
 import yaml
 from queue import Queue
@@ -8,13 +9,12 @@ import networkx as nx
 from matplotlib import pyplot as plt
 
 from import_MRP import __fix_import__
-__fix_import__()
 
+__fix_import__()
 
 import inspect
 from optparse import OptionParser
 from UDPPFunctionCollection import UDPPFunctionCollection
-
 
 
 class UDPPFunctionTranslatorException(Exception):
@@ -22,29 +22,29 @@ class UDPPFunctionTranslatorException(Exception):
         self.message = message
         super().__init__(self.message)
 
+
 class IterableQueue():
     """simple queue pyrhon iterator, which allows iteration and insertion of new items during iteration"""
-    def __init__(self,source_queue):
-            self.source_queue = source_queue
+
+    def __init__(self, source_queue):
+        self.source_queue = source_queue
+
     def __iter__(self):
         while True:
             try:
-               yield self.source_queue.get_nowait()
+                yield self.source_queue.get_nowait()
             except queue.Empty:
-               return
-
+                return
 
 
 # (a, b, x='blah')
-
-
 
 
 class UDPPFunctionTranslator():
     """This class is handling all the pipeline translations between the user level and the actual python function execution"""
 
     @staticmethod
-    def get_parameter_from_step(_pipelines: dict, _step: str, _only_step_dependencies:bool = False) -> [str]:
+    def get_parameter_from_step(_pipelines: dict, _step: str, _only_step_dependencies: bool = False) -> [str]:
         """
         renders an image of a given nx.Graph for debug purposes
 
@@ -95,28 +95,32 @@ class UDPPFunctionTranslator():
             if 'function' in stage_v:
                 fkt: str = stage_v['function']
                 if not fkt in functions:
-                    raise UDPPFunctionTranslatorException("function value ({}) for stage: {} is invalid or not present in UDPPFunctionCollection".format(fkt, stage_k))
+                    raise UDPPFunctionTranslatorException(
+                        "function value ({}) for stage: {} is invalid or not present in UDPPFunctionCollection".format(
+                            fkt, stage_k))
             else:
                 raise UDPPFunctionTranslatorException("function is not defined in stage: {}".format(stage_k))
 
         return True
 
-
     @staticmethod
[…]

### 2023-10-03 src/MagneticReadoutProcessing/udpp/static/dist/API/UDPPApi.js

@@ -12,7 +12,7 @@ export class UDPPApi {
         if (!_apiendpoint.startsWith("http://")) {
             _apiendpoint = "http://" + _apiendpoint;
         }
-        let url = _apiendpoint + "getpipeline/" + _pipelinename;
+        let url = _apiendpoint + "getpipeline/" + _pipelinename + '?canvas_size_x=' + window.innerWidth + '&canvas_size_y=' + window.innerHeight;
         console.log(url);
         const response = await fetch(url, {
             method: 'GET',

### 2023-10-03 src/MagneticReadoutProcessing/udpp/static/dist/Main.js

@@ -2,8 +2,14 @@
 import { InspectorPanel } from './UI/InspectorPanel.js';
 import { NodePanel } from './UI/NodePanel.js';
 import { OptionPanel } from './UI/OptionPanel.js';
+import { Pipeline } from './UI/Pipeline.js';
 import { cogIcon, nodePanel, optionPanel } from './UI/Shared.js';
 // Initialize the app
 let inspector = new InspectorPanel();
+// Initialize the pipeline loader
 let nodeGraph = new NodePanel(nodePanel, inspector);
+let pipeline = Pipeline.getInstance();
+pipeline.set_node_panel(nodeGraph);
+pipeline.set_insepctor_panel(inspector);
 let options = new OptionPanel(cogIcon, optionPanel);
+// options panel is used as entry point to load pipeline data in

### 2023-10-03 src/MagneticReadoutProcessing/udpp/static/dist/UI/OptionPanel.js

@@ -1,4 +1,4 @@
-import { UDPPApi } from "../API/UDPPApi.js";
+import { Pipeline } from "./Pipeline.js";
 export class OptionPanel {
     constructor(icon, panel) {
         this.icon = icon;
@@ -12,26 +12,26 @@ export class OptionPanel {
         const urlParams = new URLSearchParams(queryString);
         console.log(urlParams);
         var reload = false;
-        if (urlParams.has('pipeline') && urlParams.get('pipeline') !== this.GetPipelineName()) {
+        if (urlParams.has('pipeline') && urlParams.get('pipeline') !== OptionPanel.GetPipelineName()) {
             this.pipelineinput.setAttribute('value', urlParams.get('pipeline') || "pipeline.yaml");
             reload = true;
         }
-        else if (this.GetPipelineName() === "") {
+        else if (OptionPanel.GetPipelineName() === "") {
             this.pipelineinput.setAttribute('value', "pipeline.yaml");
         }
         else {
-            this.pipelineinput.setAttribute('value', this.GetPipelineName() || "pipeline.yaml");
+            this.pipelineinput.setAttribute('value', OptionPanel.GetPipelineName() || "pipeline.yaml");
         }
-        if (urlParams.has('apiendpoint') && urlParams.get('apiendpoint') !== this.GetApiEndpoint()) {
+        if (urlParams.has('apiendpoint') && urlParams.get('apiendpoint') !== OptionPanel.GetApiEndpoint()) {
             this.apiendpoint.setAttribute('value', urlParams.get('apiendpoint') || "http://127.0.0.1:5555/api");
             reload = true;
         }
-        else if (this.GetApiEndpoint() === "") {
+        else if (OptionPanel.GetApiEndpoint() === "") {
             this.apiendpoint.setAttribute('value', "http://127.0.0.1:5555/api");
             reload = true;
         }
         else {
-            this.apiendpoint.setAttribute('value', this.GetApiEndpoint() || "http://127.0.0.1:5555/api");
+            this.apiendpoint.setAttribute('value', OptionPanel.GetApiEndpoint() || "http://127.0.0.1:5555/api");
         }
         console.log(this.pipelineinput.value);
         console.log(this.apiendpoint.value);
@@ -47,7 +47,7 @@ export class OptionPanel {
     AddListeners() {
         // Add event listeners
         this.save_button.addEventListener('mousedown', () => this.SaveSettings());
[…]

### 2023-10-03 src/MagneticReadoutProcessing/udpp/static/dist/UI/Pipeline.js

@@ -1,0 +1,51 @@
+import { OptionPanel } from "./OptionPanel.js";
+import { UDPPApi } from "../API/UDPPApi.js";
+import { Block } from "./Block.js";
+export class Pipeline {
+    constructor() {
+    }
+    set_node_panel(_nodeGraph) {
+        this.nodeGraph = _nodeGraph;
+    }
+    set_insepctor_panel(_inspectorPanel) {
+        this.insepctorPanel = _inspectorPanel;
+    }
+    static getInstance() {
+        if (!Pipeline.instance) {
+            Pipeline.instance = new Pipeline();
+        }
+        return Pipeline.instance;
+    }
+    load_set_pipeline() {
+        if (this.nodeGraph === undefined || this.nodeGraph === null) {
+            throw Error("nodeGraph is undefined");
+        }
+        if (this.insepctorPanel === undefined || this.insepctorPanel === null) {
+            throw Error("insepctorPanel is none");
+        }
+        if (this.nodeGraph === undefined || this.nodeGraph === null) {
+            throw Error("nodeGraph is none");
+        }
+        console.log("load_set_pipeline using:");
+        console.log("pipeline", OptionPanel.GetPipelineName());
+        console.log("api", OptionPanel.GetApiEndpoint());
+        // load pipeline json object from api
+        const resolve_pipeline = UDPPApi.getPipeline(OptionPanel.GetPipelineName(), OptionPanel.GetApiEndpoint());
+        Promise.resolve(resolve_pipeline).then((pipeline) => {
+            const stage = pipeline.stages[0];
+            console.log(stage);
+            // @ts-ignore
+            let block = new Block(this.insepctorPanel);
+            block.AddOrSetTitle(`${stage.name} [${stage.function}]`);
+            let blockElement = block.GetElement(stage.position.x, stage.position.y);
+            //block.CreateBlockHTML()
+            // block.AddInputSocket(new Socket(block, 'input1', 'default', SocketType.INPUT, 0));
+            // block.AddInputSocket(new Socket(block, 'input2', 'number', SocketType.INPUT, 1));
+            // block.AddInputSocket(new Socket(block, 'input3', 'string', SocketType.INPUT, 2));
+            // block.AddOutputSocket(new Socket(block, 'output1', 'number', SocketType.OUTPUT, 0));
+            // block.AddOutputSocket(new Socket(block, 'output2', 'boolean', SocketType.OUTPUT, 1));
+            // @ts-ignore
+            this.nodeGraph.blocks.push();
+        });
+    }
+}

### 2023-10-03 src/MagneticReadoutProcessing/udpp/static/ts/API/UDPPApi.ts

@@ -3,7 +3,7 @@
 
 
 
- interface PipelineRoot {
+export interface PipelineRoot {
     settings: PipelineSettings;
     stages: PipelineStages[];
 };
@@ -14,10 +14,16 @@ interface PipelineSettings {
     name: string;
 };
 
+interface PipelineStagePosition{
+    x: number;
+    y: number;
+}
 export interface PipelineStages {
     function: string;
     name: string;
+    position: PipelineStagePosition;
     parameters: PipelineStageParameter[];
+    inspector_parameters: PipelineStageParameter[];
 };
 
 export interface PipelineStageParameter {
@@ -34,19 +40,19 @@ export class UDPPApi {
 
     static async getPipeline(_pipelinename: string, _apiendpoint: string = "http://127.0.0.1:5555/api"): Promise<PipelineRoot> {
 
-        if(!_apiendpoint.endsWith("/")){
+        if (!_apiendpoint.endsWith("/")) {
             _apiendpoint += "/";
         }
 
-        if(!_apiendpoint.startsWith("http://")){
+        if (!_apiendpoint.startsWith("http://")) {
             _apiendpoint = "http://" + _apiendpoint;
         }
 
 
-        let url: string = _apiendpoint + "getpipeline/" + _pipelinename;
+        let url: string = _apiendpoint + "getpipeline/" + _pipelinename + '?canvas_size_x=' + window.innerWidth + '&canvas_size_y=' +  window.innerHeight;
 
         console.log(url);
-        const response: Response= await fetch(url, {
+        const response: Response = await fetch(url, {
             method: 'GET',
             headers: {
                 'Accept': 'application/json',
@@ -57,18 +63,21 @@ export class UDPPApi {
             redirect: "follow"
         });
         console.log(response);
-        if (!response.ok) { throw new Error('No response generated. !ok'); }
-        if (response.body === null) {throw new Error('No response generated. bdy==null');}
+        if (!response.ok) {
+            throw new Error('No response generated. !ok');
+        }
+        if (response.body === null) {
+            throw new Error('No response generated. bdy==null');
+        }
 
 
-      // let json: object = await response.json();
-       //console.log(json)
+        // let json: object = await response.json();
+        //console.log(json)
 
 
+        let pipeline: PipelineRoot = await response.json();//= Object.create(PipelineRoot.prototype);
 
-       let pipeline: PipelineRoot = await response.json();//= Object.create(PipelineRoot.prototype);
-
[…]

### 2023-10-03 src/MagneticReadoutProcessing/udpp/static/ts/Main.ts

@@ -2,10 +2,28 @@
 import { InspectorPanel } from './UI/InspectorPanel.js';
 import { NodePanel } from './UI/NodePanel.js';
 import { OptionPanel } from './UI/OptionPanel.js';
+import { Pipeline } from './UI/Pipeline.js';
 import { cogIcon, nodePanel, optionPanel } from './UI/Shared.js';
-
 
 // Initialize the app
 let inspector: InspectorPanel = new InspectorPanel();
+
+// Initialize the pipeline loader
 let nodeGraph: NodePanel = new NodePanel(nodePanel, inspector);
+
+let pipeline = Pipeline.getInstance();
+pipeline.set_node_panel(nodeGraph);
+pipeline.set_insepctor_panel(inspector)
+
+
 let options: OptionPanel = new OptionPanel(cogIcon, optionPanel);
+
+
+
+
+
+
+
+
+
+// options panel is used as entry point to load pipeline data in

### 2023-10-03 src/MagneticReadoutProcessing/udpp/static/ts/UI/OptionPanel.ts

@@ -1,4 +1,5 @@
 import {UDPPApi} from "../API/UDPPApi.js";
+import {Pipeline} from "./Pipeline.js";
 export class OptionPanel {
 
 
@@ -9,6 +10,9 @@ export class OptionPanel {
     private load_button: HTMLButtonElement;
     private icon: HTMLElement;
     private static API: UDPPApi;
+
+
+
 
     constructor(icon: HTMLElement, panel: HTMLElement) {
         this.icon = icon;
@@ -25,23 +29,23 @@ export class OptionPanel {
 
         console.log(urlParams)
         var reload: boolean = false;
-        if(urlParams.has('pipeline') && urlParams.get('pipeline') !== this.GetPipelineName()){
+        if(urlParams.has('pipeline') && urlParams.get('pipeline') !== OptionPanel.GetPipelineName()){
             this.pipelineinput.setAttribute('value', urlParams.get('pipeline') || "pipeline.yaml");
             reload = true;
-        }else if(this.GetPipelineName() === ""){
+        }else if(OptionPanel.GetPipelineName() === ""){
             this.pipelineinput.setAttribute('value', "pipeline.yaml");
         }else{
-            this.pipelineinput.setAttribute('value', this.GetPipelineName() || "pipeline.yaml");
+            this.pipelineinput.setAttribute('value', OptionPanel.GetPipelineName() || "pipeline.yaml");
         }
 
-        if(urlParams.has('apiendpoint') && urlParams.get('apiendpoint') !== this.GetApiEndpoint()){
+        if(urlParams.has('apiendpoint') && urlParams.get('apiendpoint') !== OptionPanel.GetApiEndpoint()){
             this.apiendpoint.setAttribute('value', urlParams.get('apiendpoint') || "http://127.0.0.1:5555/api");
             reload = true;
-        }else if(this.GetApiEndpoint() === ""){
+        }else if(OptionPanel.GetApiEndpoint() === ""){
             this.apiendpoint.setAttribute('value', "http://127.0.0.1:5555/api");
             reload = true;
         }else{
-            this.apiendpoint.setAttribute('value', this.GetApiEndpoint() || "http://127.0.0.1:5555/api");
+            this.apiendpoint.setAttribute('value', OptionPanel.GetApiEndpoint() || "http://127.0.0.1:5555/api");
         }
 
         console.log(this.pipelineinput.value);
@@ -62,7 +66,8 @@ export class OptionPanel {
     AddListeners() {
         // Add event listeners
[…]

### 2023-10-03 src/MagneticReadoutProcessing/udpp/static/ts/UI/Pipeline.ts

@@ -1,0 +1,89 @@
+import {OptionPanel} from "./OptionPanel.js";
+import {PipelineRoot, PipelineStages, UDPPApi} from "../API/UDPPApi.js";
+import {NodePanel} from "./NodePanel.js";
+import {Block} from "./Block.js";
+import {Socket} from "./Socket.js";
+import {SocketType} from "./Shared.js";
+import {InspectorPanel} from "./InspectorPanel.js";
+export class Pipeline {
+    private static instance: Pipeline;
+
+    private static OPTS: OptionPanel;
+
+
+    private nodeGraph: NodePanel | undefined;
+    private insepctorPanel: InspectorPanel | undefined;
+
+
+    private constructor() {
+
+
+    }
+
+    public set_node_panel(_nodeGraph: NodePanel){
+        this.nodeGraph = _nodeGraph;
+    }
+
+    public set_insepctor_panel(_inspectorPanel: InspectorPanel){
+        this.insepctorPanel = _inspectorPanel;
+    }
+
+    public static getInstance(): Pipeline {
+        if (!Pipeline.instance) {
+            Pipeline.instance = new Pipeline();
+        }
+
+        return Pipeline.instance;
+    }
+
+
+    load_set_pipeline(){
+        if(this.nodeGraph === undefined || this.nodeGraph === null){
+            throw Error("nodeGraph is undefined");
+        }
+
+        if(this.insepctorPanel === undefined || this.insepctorPanel === null){
+            throw  Error("insepctorPanel is none");
+        }
+
+        if(this.nodeGraph === undefined || this.nodeGraph === null){
+            throw  Error("nodeGraph is none");
+        }
+
+
+        console.log("load_set_pipeline using:")
+        console.log("pipeline", OptionPanel.GetPipelineName())
+        console.log("api", OptionPanel.GetApiEndpoint())
+
+
+        // load pipeline json object from api
+        const resolve_pipeline = UDPPApi.getPipeline(OptionPanel.GetPipelineName(), OptionPanel.GetApiEndpoint());
+
+       Promise.resolve(resolve_pipeline).then((pipeline: PipelineRoot) => {
+
+           const stage  = pipeline.stages[0]
+            console.log(stage)
+
+           // @ts-ignore
+           let block = new Block(this.insepctorPanel);
+
+           block.AddOrSetTitle( `${stage.name} [${stage.function}]`)
[…]

### 2023-10-03 src/MagneticReadoutProcessing/udpp/udpp_editor.py

@@ -52,10 +52,14 @@ def getpipeline(filename: str):
     filename = bleach.clean(filename)
 
 
+    # OPTIONAL READ WINDOW SIZE TO CALCULATE NODE POSITIONS IN BROWSER WINDOW
+    canvas_size_x: int = request.args.get("canvas_size_x", default=100, type=int)
+    canvas_size_y: int = request.args.get("canvas_size_y", default=100, type=int)
+
     pipelines:dict = UDPPFunctionTranslator.load_pipelines(udpp_config.PIPELINES_FOLDER)
     # pipeline found
     if filename in pipelines:
-        return jsonify(UDPPFunctionTranslator.get_stages_as_array(pipelines[filename]))
+        return jsonify(UDPPFunctionTranslator.EDITOR_get_stages_as_array(pipelines[filename], _canvas_view_size_x=canvas_size_x, _canvas_view_size_y=canvas_size_y))
 
     # create new pipeline and return content
     pipeline: dict = UDPPFunctionTranslator.create_empty_pipeline(filename, udpp_config.PIPELINES_FOLDER)

### 2023-10-09 documentation/paper/main.tex
.

@@
 \makeglossaries
-\newacronym{sg}{SG}{Serious Games}
+\newacronym{mri}{MRI}{Serious Games}
 \newacronym{xr}{XR}{Extended Reality}
@@
 \begin{IEEEkeywords}
-Serious Gaming (\gls{sg}), \gls{vr}, Extended Reality (\gls{xr}), Computer Grafik (\gls{cg})
+%Serious Gaming (\gls{sg}), \gls{vr}, Extended Reality (\gls{xr}), Computer Grafik (\gls{cg})
 \end{IEEEkeywords}
 
+% Introduction
+%-----------------------------------------------------------------------------------------------------------------------------------------------
 \section{Introduction}
 
+\subsection{Use Cases}
+
+% Hardware
 %-----------------------------------------------------------------------------------------------------------------------------------------------
-%ERLÄUTERUNGEN
 
-\section{Serious Gaming und extended Reality Technologien}
+\section{Hardware}
 
-Um \gls{sg} in der Lehre der \gls{cg} evaluieren und einsetzen zu können, werden zuerst die Themenbereiche voneinander abgegrenzt und erläutert.
+\subsection{Sensor-Selection}
+%tabelle möglicherdigitaler sensoren
 
-\subsection{Game-Based Learning (\gls{gbl})}
-Mittels \gls{gbl} soll spielerisch Wissen vermittelt werden. Man unterscheidet in Board Game Simulations und Digital \gls{gbl}.
-Erstere sind rein haptische und nicht digitale Spiele, wie beispielsweise Schach, welches strategisches Denken lehrt und fördert.
-Letztere beinhalten die Wissensvermittlung mittels digitaler Möglichkeiten und ermöglichen genau wie Ersteres regelbasiert Aktionen und Interaktionen,
-durch den digitalen Anteil ist die Varianz deutlich erhöht und die Komplexität wird gesteigert.
-Zudem können zusätzliche Komponenten, wie Ton, Bild oder Reaktionen verwendet und die Aufmerksamkeit des Anwenders gesteuert werden.
-Der Lernprozess soll durch das Spielen nicht nur kognitiv, sondern durch eine Vielzahl an Sinnesorganen angesprochen werden, sodass die Erinnerungsleistung der
-synaptischen Repräsentation im Gehirn erhöht wird\cite{fabulagames}.
-Mittels digitaler Medien kann zudem das Spiel dezentral und / oder vernetzt umgesetzt werden\cite{a3}.
+\subsection{Communication Bus}
+% possible bus systems
 
-\subsection{Serious Gaming (\gls{sg})}
-Mit dem Ziel der Vermittlung von Inhalten und Kompetenzen sind \gls{sg}s, Instrumente zur Wissensvermittlung (s. Abbildung \ref{sgdef_fig}).
-Wörtlich übersetzt bedeutet es ``Spiel mit ernsthaftem (Lern-)Ziel''.
-Unterhaltung ist nur ein untergeordnetes Ziel dieser Spiele, jedoch nicht unbedeutend, da der Anwender im Spiel motiviert werden soll.
-Einerseits kann erlerntes Wissen vertieft und wiederholt und andererseits neues Wissen erlernt werden.
-Es ist zu beachten, dass \gls{sg} auch 2D und / oder nicht \gls{xr}-basierende Spiele beinhaltet.
-Demnach können auch nicht digitale Spiele, wie Board Game Simulations, den \gls{sg} zugeordnet werden.
-Nachfolgend wird den \gls{sg}s nur in Bezug auf \gls{xr}-basierte Spiele betrachtet.
-Nicht digitale oder Spiele für 2D Ausgabegeräte werden hierbei nicht berücksichtigt.
-
-\subsection{Extended Reality (\gls{xr})}
-\gls{xr} (oder auch Cross Reality) ist eine Sammelbezeichnung für alle Kombinationen aus realen und virtuellen Umgebungen,
-welche mittels Technologien erzeugt und über Mensch-Maschine-Interaktion gesteuert werden.
-Dies schließt auch alle zukünftigen Technologien ein.
-Mittels dieser Technologien und zugehörigen Computerprogrammen werden virtuelle, mehrdimensionale Umgebungen erzeugt (\gls{vr}) oder virtuelle Komponenten
-der realen Umgebung ergänzt (\gls{ar}) (s. Abbildung \ref{xrvrar_fig}).
-Die visuelle Wahrnehmung lässt Umgebungen real erfahren und spricht vermehrt sensorische Reize an.
-Werden \gls{xr} als Basis für \gls{sg} verwendet, können diese Reize angesprochen und somit langfristig Informationen und detaillierteres Wissen vermittelt und
-vom Gehirn gespeichert werden. Dies verbessert die Qualität des \gls{sg}, bedarf aber eines höheren Aufwands in Vorbereitung und Umsetzung als 2D oder nicht digitale Spiele.
-
-\subsection{Lehrveranstaltung Computergrafik (\gls{cg})}
-Im Allgemeinen beschreibt die Lehrveranstaltung \gls{cg} die Modellierung und Erzeugung virtueller Welten, sowie deren Abbildung bzw. Projektion auf 2D-Bilder. Es wird der Informatik zugeordnet.
-Die Modellierung und Kombination von komplexen Geometrien und Formen und auch die Berechnung dieser Komponenten sind Teil der \gls{cg}.
-Grafische Grundfunktionen, wie Farbdarstellungen oder simple Geometrien, sind Basis dieser Modellierungen.
-Beschrieben werden alle diese Modellierungen durch diverse mathematische und computergestützte Algorithmen.
-Zudem beinhaltet es die Darstellung von Objekten und Umgebungen in der Ebene, sowie die Abbildung von 3D Umgebungen auf 2D Medien.
-Die Computergrafik ist Basis aller \gls{xr} Technologien.
-Unabhängig davon, ob einzelne virtuelle Objekte dargestellt werden sollen oder vollständige Umgebungen erzeugt werden, müssen alle Bestandteile
-mittels \gls{cg} berechnet und modelliert werden.
-
-Nachfolgend wird ein Beispiel analysiert, welche die hochschuldidaktische Lehre der \gls{cg} mittels \gls{sg} und \gls{xr} unterstützen und fördern kann.
+\subsection{Sensor-Selection}
+%tabelle möglicherdigitaler sensoren
 
 %-----------------------------------------------------------------------------------------------------------------------------------------------
-%METHODIKEN
-
-\section{Auswahl an verfügbaren Methoden der \gls{sg}-gestützten Lehre}
-
-\subsection{2D \gls{sg} Lösung in der hochschuldidaktischen Lehre am Beispiel der Business Simulation \gls{sg}}
-
-%-----------------------------------------------------------------------------------------------------------------------------------------------
-%SHADER
-
+% Embedded System Software
 \section{Embedded System Software}
@@
 
+\subsection{Synchronisation}
+
+In order to ensure synchronisation of all sensors in the array, in addition to the bus system used for data transmission, a clock line is shared between all sensors.
+After performing the autonumbering procedure, the clock line, which was previously used as an autonumbering return channel, is reconfigured as a digital input.
+This is done for all connected sensor modules except for the module connected to the readout host system.
+This module then specifies the read clock via this data line, which can be configured in the software.
+All other sensors use this signal to trigger a readout interrupt.
+
+This procedure also ensures that the rest of the system maintains a synchronised state even if sensor modules fail or are restarted.
+Modules that fall into an out-of-sync status can thus be resynchronised directly after a synchronisation pulse.
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
+%Analysis Software Framework
 \section{Analysis Software Framework}
+
+The collection and subsequent processing of the data read from the sensor array is carried out on another computer system (host).
+For this purpose, the Python framework is used, which was specially developed for the automated processing of magnetic field sensor data.
+By adapting the sensor software on the basis of the documentation, a direct evaluation of the sensor is possible through the library.
+Through the implemented auto-numbering routine and the feedback of this to the host software, each individual sensor is assigned to an individual measurement in the host software.
 
@@
 
+\subsection{Calibration Run}
+
+cli einstellungen
++ ergebnis
+
+\subsection{Measurement Run}
+
 %-----------------------------------------------------------------------------------------------------------------------------------------------
-%VERGLEICHE
+%Evaluation
 
@@
 %-----------------------------------------------------------------------------------------------------------------------------------------------
-%FAZIT
+%Conclusion
 
@@
 %\setstretch{1.05}
-\begin{thebibliography}{00}
-\bibitem{eduxrvrar2020usa} Thomas Alsop: "Leading applications of immersive technologies in the education sector in the next two years according to XR/AR/VR/MR industry
-experts in the United States in 2020", in: Internetseite Statista, URL: https://www.statista.com/statistics/1185078/applications-immersive-technologies-xr-ar-vr-mr-education/, Abruf am 17.11.2021.
+\begin{modhhsf}{00}
+\bibitem{eduxrvrar2020usa} Marcel Ochsendorf: "Development of a hardware and software framework for the automated characterization of permanent magnets for low-field MRI systemsg" [Online].
+Available: https://www.researchgate.net/publication/374388764_Development_of_a_permanent_magnet_characterization_framework_for_use_in_low-field_MRI_systems, visited on 17.11.2021.
 
 \vskip 0.05in
-\bibitem{evallearningmixedreality2020} Y.
-M.
-Tang; K.
-M.
-Au; H.
-C.
-W.
-Lau; G.
-T.
-S.
-Ho, C.
-H.
-Wu; "Evaluating the effectiveness of learning design with mixed reality (MR) in higher education", Springer-Verlag London Ltd, 28.02.2020
-
-\vskip 0.05in
-\bibitem{a7} Linda Stege, Giel van Lankveld, Pieter Spronck; "Serious Games in Education", International Journal of Computer Science in Sport, 2011
-
-\vskip 0.05in
-\bibitem{fabulagames} Fabula Games, "LERNEN KANN SOOO BUNT SEIN", in: Internetseite Fabula Games, URL: https://fabula-games.de/, Abruf am 22.11.2021.
-
-\vskip 0.05in
-\bibitem{a3} Axel Jacob, Frank Teuteberg; "Game-Based Learning, Serious Games, Business Games und Gamification –Lernförderliche Anwendungsszenarien, gewonnene Erkenntnisse und Handlungsempfehlungen", Springer Fachmedien Wiesbaden GmbH, 2017
-
-\vskip 0.05in
-\bibitem{grundlagencg2001} Thomas Strothotte, Stefan Schlechtweg; "Grundlagen der Computergraphik", 2001
-
-\vskip 0.05in
-\bibitem{shadertool} Stefan Kraus, Timo Armbruster; "ShaderTool", in: Internetseite Steam, URL: https://store.steampowered.com/app/314720/ShaderTool/, Abruf 02.12.2021
-
-\vskip 0.05in
-\bibitem{a9} IBM Institute for Business Value; "Extended Reality (XR) can boost workforce efficiency and resilience by reimagining how work is done.", in: Internetseite IBM Institute for Business Value, URL: https://www.ibm.com/thought-leadership/institute-business-value/report/ar-vr-workplace, Abruf am 22.11.2021.
-
-\vskip 0.05in
-\bibitem{a10} Joseph F. Frederick; "Defining Serious Games", in: Internetseite flowleadership, URL: https://flowleadership.org/serious-games/, Abruf am 22.11.2021.
-
-\vskip 0.05in
-\bibitem{blender} Blender Foundation; "Blender", in: Internetseite Blender, URL: https://wiki.blender.org/wiki/Reference/Release\_Notes/3.0, Abruf am 22.11.2021.
-
-\vskip 0.05in
-\bibitem{unity3d} Unity Technologies; "Unity VR", in: Internetseite Unity Technologies, URL: https://unity.com/de/case-study\#games-vr, Abruf am 22.11.2021.
-
-\vskip 0.05in
-\bibitem{a11} TOPSIM; "TOPSIM-General Management-Teilnehmerhandbuch", in: Internetseite TOPSIM, URL: https://www.css.msm.uni-due.de/fileadmin/Dateien/MSM/Topsim-Gr8/01\_General\_Management\_Teilnehmerhandbuch\_STD\_15\_3.pdf, Abruf am 22.11.2021.
-
-\vskip 0.05in
-\bibitem{a14} Zehnan Feng, Robert Amor, Vicente Gonzales, Ruggiero Lovreglio; "Immersive Virtual Reality Serious Games for Evacuation Training and Research: A Systematic Literature Review", ResearchGate, 05.2018
-
-\vskip 0.05in
-\bibitem{a15} Rüppel, Schatz; "Designing a BIM-based serious game for fire safety evacuation simulations"; Advanced Engineering Informatics; 2011
-
-\vskip 0.05in
-\bibitem{googlecardboard} Google LLC; "Google Cardboard", in: Internetseite google.com, URL: https://arvr.google.com/intl/de\_de/cardboard/apps/, Abruf am 22.11.2021.
-
-\vskip 0.05in
-\bibitem{shadertoy} Inigo Quilez, Pol Jeremias; "Shadertoy", in: Internetseite shadertoy.com, URL: https://www.shadertoy.com, Abruf am 22.11.2021.
-
-\vskip 0.05in
-\bibitem{scholl} Ingrid Scholl, "Computergrafik" in: Internetseite Vorlesung Computergrafik von Fr.
-Prof.
-Scholl, Ingrid; URL: https://www.fh-aachen.de/menschen/scholl/lehre/computergrafik, Abruf am 01.12.2021.
+\bibitem{MagneticReadoutProcessingLib} M.O.: "MagneticReadoutProcessing" [Online]. Available:https://github.com/LFB-MRI/MagneticReadoutProcessing, visited on 17.11.2021
 

### 2023-10-09 documentation/paper/main.tex
.

@@
 \subsection{Communication Bus}
-% possible bus systems
+To ensure modularity and easy expandability of the sensor system, it is necessary to be able to integrate several sensors into the system.
+On the electrical level, a CAN bus was implemented to connect the individual microprocessors to which up to 16 magnetic field sensors can be digitally connected to an overall system.
+
+In addition to the bus system, the supply voltage and a separate synchronisation signal are necessary to enable automatic recognition of connected sensors.
+This is connected in a daisy chain between the modules.
 
@@
 
+\subsection{Powermanagement}
+sensor on off
+
+\subsection{}
 %-----------------------------------------------------------------------------------------------------------------------------------------------
@@
 
-\subsection{Automatic Sensor Numbering}
+\subsection{Automatic Sub-Sensor Detection}
 

### 2023-10-09 src/MagneticReadoutProcessing/udpp/static/ts/UI/Pipeline.ts
.

@@ -59,15 +59,24 @@ export class Pipeline {
 
         // CLEAR EXISTING NODES
         this.nodeGraph?.Reset();
+
+
         // load pipeline json object from api
         const resolve_pipeline = UDPPApi.getPipeline(OptionPanel.GetPipelineName(), OptionPanel.GetApiEndpoint());
 
        Promise.resolve(resolve_pipeline).then((pipeline: PipelineRoot) => {
             const stage  = pipeline.stages[0]
-            console.log(stage)
+            console.log(stage);
+           // CREATE NODES
             for (let i = 0; i < pipeline.stages.length; i++) {
                 this.nodeGraph?.CreatePipelineBlock(pipeline.stages[i]);
             }
+
+           // CREATE CONNECTIONS
+           for (let i = 0; i < pipeline.stages.length; i++) {
+
+               //this.nodeGraph?.CreatePipelineBlock(pipeline.stages[i]);
+           }
         });
 
 

### 2023-10-09 documentation/paper/main.tex
.

--- 2023-10-09 documentation/paper/main.tex
@@
 \usepackage[acronym]{glossaries}
+\usepackage{url}
 %\usepackage{setspace}
@@
 \newacronym{mri}{MRI}{Serious Games}
-\newacronym{xr}{XR}{Extended Reality}
-\newacronym{vr}{VR}{Virtual Reality}
-\newacronym{ar}{AR}{Augmented Reality}
-\newacronym{cg}{CG}{Computer Grafik}
-\newacronym{gbl}{GBL}{Game-Based Learning}
 
@@
 
-\title{Implementation of an Open-Source modular mangetic field camera for usage in Low-Field MRI Systems\\
-
-}
+\title{Implementation of an Open-Source modular mangetic field camera for usage in Low-Field MRI Systems}
 
@@
 
+% magnet measurements
+% field visualisation
+% static analysis
+% CI based tests
+
 % Hardware
@@
 
-\subsection{Sensor-Selection}
+% modular
+% low cost
+%easy to reproduce
+
+\subsection{Sensor selection}
 %tabelle möglicherdigitaler sensoren
+% mixture of sensors
+% tablee with ranges
+% digital only at the moment
+\subsection{Sensor slice}
+% 
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=8cm]{magcam_sensor_module.png}}
+\caption{Sensor Slice with eight TLV493d sensors.\cite{magcam_sensor_module}}
+\label{magcam_sensor_module_fig}
+\end{figure}
 
-\subsection{Communication Bus}
-% possible bus systems
+\subsection{Communication bus}
+To ensure modularity and easy expandability of the sensor system, it is necessary to be able to integrate several sensor slices into the system.
+On the electrical level, a CAN bus was implemented to connect the individual microprocessors to which up to 16 magnetic field sensors can be digitally connected to an overall system.
+
+In addition to the bus system, a supply voltage and a separate synchronisation signal are necessary to enable automatic recognition of connected sensors.
+This is connected in a daisy chain between the slices.
+This enables the microcontroller of a sensor slice to recognise whether it is integrated into a network and to register itself via the system bus.
+
+\subsection{Powermanagement}
+sensor on off
 
@@
 
+\subsection{Mechanical integration}
+
+% 3d printed cases for magnet holders
+%
 %-----------------------------------------------------------------------------------------------------------------------------------------------
@@
 After performing the autonumbering procedure, the clock line, which was previously used as an autonumbering return channel, is reconfigured as a digital input.
-This is done for all connected sensor modules except for the module connected to the readout host system.
+This is done for all connected sensor modules except for the slices connected to the readout host system.
 This module then specifies the read clock via this data line, which can be configured in the software.
@@
 
-This procedure also ensures that the rest of the system maintains a synchronised state even if sensor modules fail or are restarted.
+This procedure also ensures that the rest of the system maintains a synchronised state even if sensor slices fail or are restarted.
 Modules that fall into an out-of-sync status can thus be resynchronised directly after a synchronisation pulse.
@@
 
+\subsection{Comparison}
+% mit mechanischen aufbau
+% durch feste positionen nur zurückrechenbar
+
 %-----------------------------------------------------------------------------------------------------------------------------------------------
@@
 \begingroup
-
+\begin{thebibliography}{00}
 %\setstretch{1.05}
-\begin{modhhsf}{00}
-\bibitem{eduxrvrar2020usa} Marcel Ochsendorf: "Development of a hardware and software framework for the automated characterization of permanent magnets for low-field MRI systemsg" [Online].
-Available: https://www.researchgate.net/publication/374388764_Development_of_a_permanent_magnet_characterization_framework_for_use_in_low-field_MRI_systems, visited on 17.11.2021.
+\bibitem{modhhsf} Marcel Ochsendorf: Development of a hardware and software framework for the automated characterization of permanent magnets for low-field MRI systems.
+Available: \url{https://www.researchgate.net/publication/374388764_Development_of_a_permanent_magnet_characterization_framework_for_use_in_low-field_MRI_systems}, 17.11.2021.
 
 \vskip 0.05in
-\bibitem{MagneticReadoutProcessingLib} M.O.: "MagneticReadoutProcessing" [Online]. Available:https://github.com/LFB-MRI/MagneticReadoutProcessing, visited on 17.11.2021
+\bibitem{MagneticReadoutProcessingLib} Marcel Ochsendorf: MagneticReadoutProcessing-Framework. \url{https://github.com/LFB-MRI/MagneticReadoutProcessing}, 17.11.2021
 

### 2023-10-09 documentation/paper/build.sh

@@ -43,7 +43,7 @@ pdflatex ./main.tex ./main.pdf
 pdflatex ./main.tex ./main.pdf
 
 
-cp ./main.pdf ./paperwssarbeiten.pdf
+mv ./main.pdf ./paper.pdf
 echo "------------- PDF EXPORT FINISHED -----------"
 
 

### 2023-10-10 documentation/paper/main.tex
.

@@
 \subsection{Sensor slice}
-% 
+
+Each sensor slice has its own microprocessor as a communication element. this takes over the task of reading the connected sensors and transmitting the results via the system bus.
+The interfaces for different sensor types are also implemented in its firmware.
+this makes it possible to mix different sensor types on one slice.
+the slice presents itself to the rest of the system as a uniform sensor with a uniform measurement result.
+For this purpose, calibration and unit conversions are automatically applied in the firmware of the slice, depending on which sensor has been detected.
+
 \begin{figure}[htbp]
 \centerline{\includegraphics[width=8cm]{magcam_sensor_module.png}}
-\caption{Sensor Slice with eight TLV493d sensors.\cite{magcam_sensor_module}}
+\caption{Sensor Slice with eight TLV493d sensors}
 \label{magcam_sensor_module_fig}
@@
 \subsection{Communication bus}
+
 To ensure modularity and easy expandability of the sensor system, it is necessary to be able to integrate several sensor slices into the system.
@@
 \subsection{Automatic Sub-Sensor Detection}
+
+Due to the modular hardware design, it is necessary for the software to be able to recognise the individual slices automatically.
+without the user having to enter the number of connected slices in the software.
+
+Due to the can-bus used, however, it is not possible to directly recognise the sequence of the modules and therefore the individual sensors cannot be directly addressed.
+Through an additional auto-numbering sequence after the system start, all connected modules address themselves automatically.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=8cm]{anp.png}}
+\caption{Auto numbering protocol for multible connected slices}
+\label{anp_fig}
+\end{figure}
+
+For this purpose, an additional clock line is used to carry out the protocol described (Figure \ref{anp_fig}).
+Later, this is used for synchronisation in order to have to use as few data lines as possible between the slices.
+% each slice gets its own id and transmits +1 to the next
 

### 2023-10-11 documentation/paper/main.tex
.

@@
 \makeglossaries
-\newacronym{mri}{MRI}{Serious Games}
+\newacronym{mri}{MRI}{Magnetic resonance imaging}
 
@@
 
-\title{Implementation of an Open-Source modular mangetic field camera for usage in Low-Field MRI Systems}
+\title{Implementation of an Open-Source modular mangetic field camera hardware for usage in Low-Field MRI Systems}
 
@@
 \begin{IEEEkeywords}
-%Serious Gaming (\gls{sg}), \gls{vr}, Extended Reality (\gls{xr}), Computer Grafik (\gls{cg})
+magnetic resonance imaging (\gls{mri})
 \end{IEEEkeywords}
@@
 \subsection{Sensor selection}
-%tabelle möglicherdigitaler sensoren
+
+\begin{table}
+    \centering
+    \begin{tabular}{|l|c|}
+    \hline
+    \textbf{Name} & \textbf{Range (mT)} \\
+    \hline
+    Honeywell HMC5883L & 1.3 - 8.1 mT \\
+    STMicroelectronics LIS3MDL & 4 - 16 mT \\
+    TDK InvenSense ICM-20948 & 49 mT \\
+    \hline
+    \end{tabular}
+    \caption{Implemented 3D Magnetometer ICs}
+\end{table}
+
 % mixture of sensors
@@
 
+The sensor slice shown in Figure \ref{anpmagcam_sensor_module_fig_fig} consists of 8 TLV493d sensors spaced 8mm apart on an 8mm x 64mm PCB.
+To build a larger sensor array, the golf finger pads of the board can be soldered to other similar boards in a daisy chain configuration.
+
+The daisy chain design simplifies connectivity as multiple slices can be connected in a linear fashion, reducing complex wiring.
+This approach simplifies expansion and troubleshooting, as new slices can be easily added or removed without disrupting the entire system.
+
+In this way, an 8x8 sensor array can be built quickly, and the mechanical stability and alignment is ensured by the interconnection of the golf finger pads.
+
 \subsection{Communication bus}
@@
 \subsection{Powermanagement}
-sensor on off
 
-\subsection{Sensor-Selection}
-%tabelle möglicherdigitaler sensoren
+Each sensor slice also implements its own power management of the sensors, both at the hardware and software level, but this is optional.
+
+Depending on the type of sensor used, the current flowing through the individual layers can influence its measurement result.
+Therefore, the control logic and voltage converter components were placed separately from the sensors in the board layout.
+In addition, individual sensors can be specifically supplied with voltage. This was implemented using a switchable power supply (PCF847). 
+The software is later (when activated) able to activate only the sensor that is to be read out at the current time.
+A disadvantage of this implementation, however, is that each sensor must be reconfigured after activating the power supply.
+Depending on the selected sensor, this can take up to an additional 10ms per sensor measurement.
 
@@
 %
+
 %-----------------------------------------------------------------------------------------------------------------------------------------------

### 2023-10-12 src/MagneticReadoutProcessing/udpp/static/dist/UI/NodePanel.js
.

@@ -488,11 +488,11 @@ export class NodePanel {
             console.log("target_socket", target_socket);
             //let endSocket = ToSocket(evt.target as HTMLElement);
             //if (endSocket && this.connectorPath) {
-            //    this.connectorPath = this.UpdateConnection(this.connectorPath, this.selectedSocket, endSocket, evt);
-            //    let edge = new Edge(this.connectorPath, this.selectedSocket, endSocket);
+            // this.connectorPath = this.UpdateConnection(this.connectorPath, this.selectedSocket, endSocket, evt);
+            //     let edge = new Edge(this.connectorPath, source_socket, target_socket);
             // Add the edges
-            //    this.selectedSocket.Connect(edge);
-            //    endSocket.Connect(edge);
+            // this.selectedSocket.Connect(edge);
+            // endSocket.Connect(edge);
             // Add the edge to the list
             //    this.edges.push(edge);
             //this.nodeGraph?.CreatePipelineBlock(pipeline.stages[i]);

### 2023-10-12 src/MagneticReadoutProcessing/udpp/static/ts/UI/NodePanel.ts

@@ -603,8 +603,8 @@ export class NodePanel {
 
             //let endSocket = ToSocket(evt.target as HTMLElement);
             //if (endSocket && this.connectorPath) {
-            this.connectorPath = this.UpdateConnection(this.connectorPath, this.selectedSocket, endSocket, evt);
-            let edge = new Edge(this.connectorPath, source_socket, target_socket);
+           // this.connectorPath = this.UpdateConnection(this.connectorPath, this.selectedSocket, endSocket, evt);
+       //     let edge = new Edge(this.connectorPath, source_socket, target_socket);
 
 
             // Add the edges

### 2023-10-12 src/MagneticReadoutProcessing/udpp/udpp_editor.py

@@ -46,7 +46,18 @@ def updateinspectorparameter(pipeline:str, stagename:str, parameter:str, value: 
     value = bleach.clean(value)
 
 
-    # TODO CHECK PIPELINE EXISTS
+    # CHECK PIPELINE EXIST
+    pipelines = UDPPFunctionTranslator.load_pipelines(udpp_config.PIPELINES_FOLDER)
+    if pipeline not in pipelines:
+        return jsonify({'error': 'pipeline does not exist'}), 500
+
+    pipeline_data:dict = pipelines[pipeline]
+
+    # CHECK STAGE EXIST
+    stage = UDPPFunctionTranslator.extract_pipelines_steps(_pipeline=pipeline_data)
+    if stagename not in stage:
+        return jsonify({'error': 'stage does not exist'}), 500
+
     # TODO CHECK STAGE EXISTS
     # TODO CHECK FUNCTION EXSTS
     # TODO PARSE TO FUNCTION TYPE

### 2023-10-13 documentation/paper/main.tex
.

@@
 
+\subsection{Calibration strategy \label{ref_calib}}
+
+\subsection{Measurement Run}
+
 \subsection{Data analysis pipeline}
 
-\subsection{Calibration Run}
-
-cli einstellungen
-+ ergebnis
-
-\subsection{Measurement Run}
+For this purpose, the framework was extended by a CLI-based batch processing, which allows measurements of all sensors with the appropriate calibration measurements (offset, temperature) to be processed automatically.
+The parameterisation is done by means of a customised configuration file in which the folders for raw and calibration measurements are specified.
+The assignment is then done by a regex rule.
 
@@
 \section{Evaluation}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=8cm]{magnets_with_holder.jpg}}
+\caption{12x12x12mm N45 neodymium test magnets }
+\label{mag_with_holder_fig}
+\end{figure}
+
+The test setup used consists of an 8x8 sensor array, which consists of 8 sensor slices with 8 TLV493d sensors each.
+The test objects to be characterised were 12x12x12mm N45 neodymium magnets \ref{mag_with_holder_fig}.
+These were mounted in a 3D-printed backlash-free holder with a distance of 10mm to the top of the sensor board \ref{mag_pcb_side_cut_fig}.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=8cm]{magnet_pcb_drawing.png}}
+\caption{Sectional side cut: circle marks the center point of manget with sensor pcb on the bottom}
+\label{mag_pcb_side_cut_fig}
+\end{figure}
 

### 2023-10-15 documentation/paper/main.tex
.

@@
 By adapting the sensor software on the basis of the documentation, a direct evaluation of the sensor is possible through the library.
-Through the implemented auto-numbering routine and the feedback of this to the host software, each individual sensor is assigned to an individual measurement in the host software.
+Through the implemented auto-numbering routine and the feedback of this to the host software, each individual sensor is assigned to an individual measurement file in the host software.
+
+For this purpose, the framework was extended by a CLI-based batch processing, which allows measurements of all sensors with the appropriate calibration measurements (offset, temperature) to be processed automatically.
+The parameterisation is done by means of a customised configuration file in which the folders for raw and calibration measurements are specified.
+The assignment is then done by a regex rule.
 
@@
 \subsection{Data analysis pipeline}
-
-For this purpose, the framework was extended by a CLI-based batch processing, which allows measurements of all sensors with the appropriate calibration measurements (offset, temperature) to be processed automatically.
-The parameterisation is done by means of a customised configuration file in which the folders for raw and calibration measurements are specified.
-The assignment is then done by a regex rule.
 

### 2023-10-20 documentation/paper/main.tex
.

@@
     \caption{Implemented 3D Magnetometer ICs}
+    \label{implemented_sensors_fig}
 \end{table}
@@
 Therefore, the control logic and voltage converter components were placed separately from the sensors in the board layout.
-In addition, individual sensors can be specifically supplied with voltage. This was implemented using a switchable power supply (PCF847). 
+In addition, individual sensors can be specifically supplied with voltage. This was implemented using a remote GPIO expander IC PCF847.
+
+This was designed as a switchable voltage source, as each of the 8 outputs can supply up to 50 mA.
+All currently implemented sensors from \ref{implemented_sensors_fig} require less than 10 mA in measurement mode, so the PCF847 is a cost-effective solution.
+To operate sensors with a higher power consumption, the PCF847 can be bypassed or an additional power distribution circuit breaker IC such as the TPS22 can be used.
+
 The software is later (when activated) able to activate only the sensor that is to be read out at the current time.
@@
 %
+\subsection{Limitierungen}
 
@@
 
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=8cm]{dataprocessing_pipeline.png}}
+\caption{Implemented Data analysis pipeline}
+\label{dataprocessing_pipeline_fig}
+\end{figure}
+
 %-----------------------------------------------------------------------------------------------------------------------------------------------

### 2023-10-21 documentation/paper/main.tex
.

@@
 % digital only at the moment
+
 \subsection{Sensor slice}
@@
 
+Since all of the digital sensors listed in \ref{implemented_sensors_fig} are connected via an I2C bus, they can be addressed via an individual address.
+When using several identical sensors on one sensor slice, however, address collisions occur on the I2C bus.
+Some I2C devices offer the option of changing the address in hardware via the wiring of address inputs, but this requires a change in the hardware.
+In order to prevent this, an I2C multiplexer switch IC .was used here. Thus, in the current hardware version, up to eight identical sensors with the same address can be used per slice.
+
 \begin{figure}[htbp]
 \centerline{\includegraphics[width=8cm]{magcam_sensor_module.png}}
-\caption{Sensor Slice with eight TLV493d sensors}
+\caption{Sensor Slice with eight TLV493d sensors and readout electronics (STM32G031, PCF8574 and TCA9548)on the lieft side.}
 \label{magcam_sensor_module_fig}
@@
 
-The sensor slice shown in Figure \ref{anpmagcam_sensor_module_fig_fig} consists of 8 TLV493d sensors spaced 8mm apart on an 8mm x 64mm PCB.
-To build a larger sensor array, the golf finger pads of the board can be soldered to other similar boards in a daisy chain configuration.
+The sensor slice shown in Figure \ref{anpmagcam_sensor_module_fig} consists of eight TLV493d sensors spaced 8mm apart on an 8mm x 64mm PCB.
+To build a larger sensor array, the gold finger pads of the board can be soldered to other similar boards in a daisy chain configuration.
 
@@
 
-In this way, an 8x8 sensor array can be built quickly, and the mechanical stability and alignment is ensured by the interconnection of the golf finger pads.
+In this way, an n*8x8 sensor array can be built quickly. The mechanical stability and alignment is ensured by the interconnection of the golf finger pads.
 
@@
 
-\subsection{Automatic Sub-Sensor Detection}
+\subsection{Automatic Sensor-Slice Detection}
 
@@
 Modules that fall into an out-of-sync status can thus be resynchronised directly after a synchronisation pulse.
+
+* currently limited by software to 50hz
+* canbus speed limitations
+* enable average algorithms between bus send to allow a higher readout rate.
 

### 2023-12-13 documentation/thesis/thesis_abstract.tex
thesis

@@
-Especially in the construction of low-field MRI devices based on
-permanent magnets, a large number of magnets are used. In order to
-realize a homogeneous B0 field with these magnets, which is necessary
-for many setups, the magnetic properties of these magnets should be as
-similar as possible.
-
-Due to the complex manufacturing process, especially of neodymium
-magnets, the different properties, especially the direction of
-magnetization, can deviate from each other, which affects the
-homogeneity of the field.
-
-To adjust the field afterwards, a passive shimming process is typically
-performed, which is complex and time-consuming and requires manual
-corrections to the magnets used.
-
-To avoid this process, magnets can be systematically measured in
-advance. However, in this methodology, the recording, data storage and
-subsequent evaluation of the data play an important role.
-
-The various existing solutions implement individual aspects, but do not
-provide a data pipeline from aqusation to analysis.
-
+In the construction of low-field MRI devices based on permanent magnets,
+a large number of magnets are used. In order to realize a homogeneous B0
+field with these magnets, which is necessary for many setups, the
+magnetic properties of these magnets have to be as similar to a certain
+degree. Due to the complex manufacturing process of neodymium magnets,
+the different properties, the direction of magnetization, can deviate
+from each other, which affects the homogeneity of the field. To adjust
+the field afterwards, a passive shimming process is typically performed,
+which is complex and time-consuming and requires manual corrections to
+the magnets used. To avoid this process, magnets can be systematically
+measured in advance. In this methodology, the recording, data storage
+and subsequent evaluation of the data play an important role. Various
+existing open-source solutions implement individual parts, but do not
+provide a complete data processing pipeline from aqusation to analysis
+and the data storage formats of these are not compatible to each other.
 For this use case, the MagneticReadoutProcessing library was created,
-which implements different aspects of data acquisition, data storage,
-analysis, and each intermediate step can be customized by the user
-without having to create everything from scratch, favoring an exchange
-between different user groups.
+which implements all major aspects of acquisition, storage, analysis,
+and each intermediate step can be customized by the user without having
+to create everything from scratch, favoring an exchange between
+different user groups. Complete documentation, tutorials and tests
+enable users to use and adapt the FRamework as quickly as possible. The
+framework for the characterisation of different N45 neodymium magnets,
+which requires the integration of magnetic field sensors, was used for
+the evaluation.

### 2023-12-13 documentation/thesis/thesis_document.tex
thesis

@@
 
-\hypertarget{fundamentals}{%
-\chapter{Fundamentals}\label{fundamentals}}
+\hypertarget{background-and-motivation}{%
+\section{Background and Motivation}\label{background-and-motivation}}
 
-\hypertarget{permanent-magnet-mri}{%
-\section{Permanent magnet MRI}\label{permanent-magnet-mri}}
-
-\hypertarget{typical-b0-magnet-structures}{%
-\subsection{Typical B0 Magnet
-structures}\label{typical-b0-magnet-structures}}
+\hypertarget{low-field-mri}{%
+\subsection{Low-Field MRI}\label{low-field-mri}}
 
 \hypertarget{shimming-procedure}{%
-\section{Shimming procedure}\label{shimming-procedure}}
+\subsection{Shimming procedure}\label{shimming-procedure}}
+
+\hypertarget{aim-of-this-thesis}{%
+\section{Aim of this Thesis}\label{aim-of-this-thesis}}
+
+\hypertarget{structure}{%
+\section{Structure}\label{structure}}
 
@@
 
-\hypertarget{unified-sensor-interface}{%
-\section{Unified Sensor Interface}\label{unified-sensor-interface}}
+\hypertarget{conceptual-design}{%
+\section{Conceptual design}\label{conceptual-design}}
+
+\begin{itemize}
+\tightlist
+\item
+  etnwicklung eines hardware uns software framework zur einfachen
+  aquirierung von Meagnetfelddaten
+\item
+  analysetools und funktionen
+\end{itemize}
+
+\hypertarget{unified-sensor}{%
+\chapter{Unified Sensor}\label{unified-sensor}}
+
+\begin{itemize}
+\tightlist
+\item
+  ziel ist es einen low cost hallsensor-interface zu entwickeln welcher
+  möglichst
+\item
+  universell
+\item
+  verschienee sensoren abbilden kann
+\item
+  mit verschienden magneten typen und formen nutzbar
+\item
+  reproduzierbar
+\item
+  1d, 2d, 3d
+\item
+  integration
+\end{itemize}
 
@@
 
-\hypertarget{mechanical}{%
-\section{Mechanical}\label{mechanical}}
+\begin{itemize}
+\item
+  list of typical low cost hall sensors
+\item
+  =\textgreater{} alle i2c in der regel
+\item ~
+  \hypertarget{mechanical-structure}{%
+  \section{Mechanical Structure}\label{mechanical-structure}}
+\item
+  3d druck toleranztest
+\item
+  magnet halterung mit kraftloser arretierung
+\item
+  motoren und andere unter umstaänden magnetische teile in der nähe des
+  sensors
+\item
+  nylon schrauben, 3d druck, 3d gedruckte klemmverbindungen
+\item
+  später rausrechnen durch kalibierung
+\end{itemize}
 
@@
 
-\hypertarget{software-implementation}{%
-\chapter{Software implementation}\label{software-implementation}}
+\begin{itemize}
+\tightlist
+\item
+  usb, ethernet
+\item
+  pps input output
+\item
+  multiplexer for i2c sensors alredy implemented
+\end{itemize}
 
-\hypertarget{library}{%
-\section{Library}\label{library}}
+\hypertarget{firmware}{%
+\section{Firmware}\label{firmware}}
+
+\begin{itemize}
+\tightlist
+\item
+  automatic sensor detation
+\item
+  serial cli support for manual mode
+\item
+  sync impulse =\textgreater{} 1 mastersensor als taktqelle
+\item
+  interene mittelung und speichern der werte im buffer
+\item
+  was durch den user implementiert werden muss klasse
+\end{itemize}
+
+\hypertarget{cli-interface}{%
+\subsection{CLI Interface}\label{cli-interface}}
+
+\begin{itemize}
+\tightlist
+\item
+  einfache bedienung durch nutzer auch ohne weitere software
+\item
+  configuration
+\item
+  debugging
+\end{itemize}
+
+\hypertarget{example-sensors}{%
+\section{Example Sensors}\label{example-sensors}}
+
+\emph{anbei werden drei erschienee sensoren für unterschiedliche
+anwedungfälle } tablle statisch dynamisch
+
+\hypertarget{d-single-sensor}{%
+\subsection{1D: Single Sensor}\label{d-single-sensor}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_fullsphere_sensor.png}
+\caption{fullsphere sensor \label{fullsphere_sensor.png}}
+\end{figure}
+
+\begin{itemize}
+\tightlist
+\item
+  einfachster aufbau rp pico + sensor
+\end{itemize}
+
+\hypertarget{d-dual-sensor}{%
+\subsection{1D: Dual Sensor}\label{d-dual-sensor}}
+
+\begin{itemize}
+\tightlist
+\item
+  gleicher abstand zwei gleicher sensoren
+\item
+  schnelle erkennung der plarisationsebene ggf offset vom mittelpunkt
+  dieser
+\end{itemize}
+
+\hypertarget{full-sphere}{%
+\subsection{Full-Sphere}\label{full-sphere}}
+
+\begin{itemize}
+\tightlist
+\item
+  komplexester aufbau sensor + mechanik
+\item
+  polar mechanisches system
+\item
+  full sphere sensor
+\end{itemize}
+
+\hypertarget{integration-of-an-professional-teslameter}{%
+\subsection{Integration of an Professional
+Teslameter}\label{integration-of-an-professional-teslameter}}
+
+\begin{itemize}
+\tightlist
+\item
+  einfach anbindung professioneller teslameter
+\item
+  Voltkraft
+\end{itemize}
+
+\hypertarget{software-readout-framework}{%
+\chapter{Software readout framework}\label{software-readout-framework}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_MRPlib_COMPLETE_FLOW.png}
+\caption{MRPlib COMPLETE FLOW \label{MRPlib_COMPLETE_FLOW.png}}
+\end{figure}
+
+\hypertarget{library-requirements}{%
+\section{Library requirements}\label{library-requirements}}
 
@@
 
+\begin{itemize}
+\tightlist
+\item
+  beispiele für projekte welche nur einzelne schnritte implementieren
+\item
+  so kann man sich auf die implementierung
+\end{itemize}
+
 \hypertarget{user-interaction-points}{%
@@
 
-\hypertarget{datastructures}{%
-\subsection{Datastructures}\label{datastructures}}
+\begin{itemize}
+\tightlist
+\item
+  grafik zeigen
+\item
+  einzelne module erleutern
+\end{itemize}
 
-\hypertarget{datapoints}{%
-\subsubsection{Datapoints}\label{datapoints}}
+\hypertarget{hal}{%
+\subsubsection{HAL}\label{hal}}
 
-\hypertarget{meta-data-management}{%
-\subsubsection{Meta-Data management}\label{meta-data-management}}
+\begin{itemize}
+\tightlist
+\item
+  aufbau hal im grunde wird nur ein die commandos an das sensor cli
+  weitergegeben
+\item
+  alle sensoren implementieren mehr oder weniger die gleichen befehle
+\item
+  hal gibt nur weiter und ist ``dumm''
+\end{itemize}
 
-\hypertarget{implementation}{%
-\subsection{Implementation}\label{implementation}}
+\hypertarget{visualisation}{%
+\subsubsection{Visualisation}\label{visualisation}}
+
+\hypertarget{export}{%
+\subsection{Export}\label{export}}
+
+\begin{itemize}
+\tightlist
+\item
+  format import export
+\item
+  matlab
+\end{itemize}
+
+\hypertarget{meta-data}{%
+\subsubsection{Meta-Data}\label{meta-data}}
+
+\hypertarget{multi-sensor-setup}{%
+\subsection{Multi-Sensor setup}\label{multi-sensor-setup}}
+
+At the moment, it is only possible to detect and use sensors that are
+directly connected to the PC with the library. This has the disadvantage
+that there must always be a physical connection. This can make it
+difficult to install multiple sensors in measurement setups where space
+or cable routing options are limited. To make sensors connected to a
+small remote PC available on the network, the `Proxy' module has been
+developed. This can be a single board computer (e.g.~a Raspberry Pi).
+The small footprint and low power consumption make it a good choice. It
+can also be used in a temperature chamber. The approach of implementing
+this via a REST interface also offers the advantage that several
+measurements or experiments can be recorded at the same time with the
+sensors.
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_MRPlib_Proxy_Module.png}
+\caption{MRPlib Proxy Module \label{MRPlib_Proxy_Module.png}}
+\end{figure}
+
+Another application example is when sensors are physically separated or
+there are long distances between them. By connecting several sensors via
+the proxy module, it is possible to link several instances and all
+sensors available in the network are available to the control PC.
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_mrp_proxy_multi.png}
+\caption{mrp proxy multi \label{mrp_proxy_multi.png}}
+\end{figure}
+
+The graphic \ref{mrp_proxy_multi.png} shows the modified multi-proxy -
+multi-sensor topology. Here, both proxy instances do not communicate
+directly with the control PC, but remote PC \#2 is connected to remote
+PC \#1. This is then visible as a sensor opposite the Control PC, even
+if there are several proxy instances behind it.
+
+\hypertarget{network-proxy}{%
+\subsubsection{Network-Proxy}\label{network-proxy}}
+
+The graphic \ref{MRPlib_Proxy_Module.png} shows the separation of the
+various HAL instances, which communicate with the physically connected
+sensors on the remote PC and the control PC side, which communicates
+with the remote side via the network. For the user, nothing changes in
+the procedure for setting up a measurement. The proxy application must
+always be started on the remote PC side.
+
+\begin{lstlisting}[language=bash]
+    # START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
+    $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B # add another proxy instance http://proxyinstance_2.local for multi-sensor, multi-proxy chain
+    Proxy started. http://0.0.0.0:5556/
+    PRECHECK: SENSOR_HAL: 1337 # SENSOR A FOUND
+    PRECHECK: SENSOR_HAL: 4242 # SENSOR B FOUND
+    Terminate  [Y/n] [y]: 
+\end{lstlisting}
+
+After the proxy instance has been successfully started, it is optionally
+possible to check the status via the REST interface:
+
+\begin{lstlisting}[language=bash]
+    # GET PROXY STATUS
+    $ wget http://proxyinstance.local:5556/proxy/status
+    {
+    "capabilities":[
+      "static",
+      "axis_b",
+      "axis_x",
+      "axis_y",
+      "axis_z",
+      "axis_temp",
+      "axis_stimestamp"
+   ],
+   "commands":[
+      "status",
+      "initialize",
+      "disconnect",
+      "combinedsensorcnt",
+      "sensorcnt",
+      "readsensor",
+      "temp"
+   ]
+   # RUN A SENSOR COMMAND AND GET THE TOTAL SENSOR COUNT
+   $ wget http://proxyinstance.local:5556/proxy/command?cmd=combinedsensorcnt
+   {
+   "output":[
+      "2"
+   ]
+}
+}
+\end{lstlisting}
+
+The query result shows that the sensors are connected correctly and that
+their capabilites have also been recognised correctly. To be able to
+configure a measurement on the other, only the IP address or host name
+of the remote PC is required:
+
+\begin{lstlisting}[language=bash]
+    # START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
+    $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B
+    Proxy started. http://0.0.0.0:5556/
+    PRECHECK: SENSOR_HAL: 1337 # SENSOR A FOUND
+    PRECHECK: SENSOR_HAL: 4242 # SENSOR B FOUND
+    Terminate  [Y/n] [y]: 
+\end{lstlisting}
+
+\hypertarget{sensor-syncronisation}{%
+\subsubsection{Sensor Syncronisation}\label{sensor-syncronisation}}
+
+\begin{itemize}
+\tightlist
+\item
+  alle clients über ptp verbunden
+\item
+  zentraler reset zwischen zwei pps pulsen um den readout counter auf 0
+  zu setzten
+\end{itemize}
+
+\hypertarget{command-router}{%
+\subsubsection{Command-Router}\label{command-router}}
+
+\begin{itemize}
+\tightlist
+\item
+  nummerieierung zuerst lokale sensoren dann weitere proxy sensoren
+\item
+  commando templating
+\end{itemize}
 
@@
 \subsection{Examples}\label{examples}}
-
-\hypertarget{concepts-1}{%
-\subsection{Concepts}\label{concepts-1}}
 
@@
 
+\begin{itemize}
+\tightlist
+\item
+  automatische sensor dedettion
+\item
+  planung verschiedener messungen mit untersch. hardware
+\item
+  zentrale abarbeitung
+\end{itemize}
+
 \hypertarget{programmable-data-processing-pipeline}{%
@@
 pipeline}\label{programmable-data-processing-pipeline}}
+
+\begin{itemize}
+\tightlist
+\item
+  datenanalyse für nicht programmieruer
+\item
+  automatisierter aufbau der call-tree
+\item
+  mit typcheck
+\item
+  alle funktionen mit bestimmer signtur werden automatisch aus globals
+  geladen und stehen nutzer zur verfühung
+\end{itemize}
 
@@
 
-\hypertarget{third-party-software-support}{%
-\section{Third party software
-support}\label{third-party-software-support}}
+\begin{itemize}
+\tightlist
+\item
+  drag\& drop system
+\item
+  automatische convertierung zum yaml system
+\end{itemize}
 
@@
 
+\begin{itemize}
+\tightlist
+\item
+  verteilung durch paketmanager
+\item
+  docker cli beispiel
+\end{itemize}
+
 \hypertarget{documentation}{%
 \subsection{Documentation}\label{documentation}}
-
-\hypertarget{distribution}{%
-\subsection{Distribution}\label{distribution}}
-
-\hypertarget{continuous-integration}{%
-\subsection{Continuous Integration}\label{continuous-integration}}
-
-\hypertarget{end-to-end-testing}{%
-\subsection{End to end testing}\label{end-to-end-testing}}
 
@@
 \section{Prequesites for evaluation}\label{prequesites-for-evaluation}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_testmagnets_in_holder.png}
+\caption{testmagnets in holder \label{testmagnets_in_holder.png}}
+\end{figure}
 
@@
 \section{Outlook}\label{outlook}}
+
+\begin{itemize}
+\tightlist
+\item
+  magfield camera
+\end{itemize}

### 2023-12-13 src/MagneticReadoutProcessing/MRP/MRPReadingSourceFullsphere.py
Update MRPReadingSourceFullsphere.py

@@ -34,7 +34,7 @@ class MRPReadingSourceFullsphere(MRPReadingSource.MRPReadingSource):
         # HOME MECHANIC
         "G28 Y",
         "G28 X",
-        "SET_IDLE_TIMEOUT TIMEOUT=60",
+        "SET_IDLE_TIMEOUT TIMEOUT=3600",
         "M220 S8000"
     ]
 

### 2023-12-13 documentation/thesis/thesis_document.tex
1.4.1

@@
 \begin{itemize}
+\tightlist
 \item
@@
   =\textgreater{} alle i2c in der regel
-\item ~
+\item
+\end{itemize}
+
 \hypertarget{mechanical-structure}{%
 \section{Mechanical Structure}\label{mechanical-structure}}
+
+\begin{itemize}
+\tightlist
 \item
@@
 
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensors_CL-Interface.png}
+\caption{Sensors CL-Interface \label{Sensors_CL-Interface.png}}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Query_sensors_b_value_using_CLI.png}
+\caption{Query sensors b value using CLI
+\label{Query_sensors_b_value_using_CLI.png}}
+\end{figure}
+
 \begin{itemize}
@@
 \end{itemize}
+
+\hypertarget{sensor-syncronsisation}{%
+\section{\texorpdfstring{Sensor Syncronsisation
+\label{CHAPTER_Sensor_Syncronsisation}}{Sensor Syncronsisation }}\label{sensor-syncronsisation}}
 
@@
 \centering
-\includegraphics{./generated_images/border_fullsphere_sensor.png}
-\caption{fullsphere sensor \label{fullsphere_sensor.png}}
+\includegraphics{./generated_images/border_1D_sensor_contrsuction_with_universal_magnet_mount.png}
+\caption{1D sensor contrsuction with universal magnet mount
+\label{1D_sensor_contrsuction_with_universal_magnet_mount.png}}
 \end{figure}
@@
 \subsection{Full-Sphere}\label{full-sphere}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
+\caption{Full-Sphere sensor implementation using two Nema17 stepper
+motors in a polar coordinate system
+\label{Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}}
+\end{figure}
 
@@
    ]
+
    # RUN A SENSOR COMMAND AND GET THE TOTAL SENSOR COUNT
@@
 \begin{lstlisting}[language=bash]
-    # START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
+    # CONFIGURE MEASUREMENT JOB USING A PROXY INSTANCE
     $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B
-    Proxy started. http://0.0.0.0:5556/
-    PRECHECK: SENSOR_HAL: 1337 # SENSOR A FOUND
-    PRECHECK: SENSOR_HAL: 4242 # SENSOR B FOUND
-    Terminate  [Y/n] [y]: 
+
 \end{lstlisting}
@@
 
+Another important aspect when using several sensors via the proxy system
+is the synchronisation of the measurement intervals between the sensors.
+Individual sensor setups do not require any additional synchronisation
+information, as this is communicated via the USB interface. If several
+sensors are connected locally, they can be connected to each other via
+their sync input using short cables. One sensor acts as the central
+clock (see chapter \ref{CHAPTER_Sensor_Syncronsisation}). However, this
+no longer works for long distances and a diversion must be made via the
+network connection.
+
+If time-critical synchronisation is required, PTP and PPS functionality
+can be used on many single-board computers (such as the RaspberryPi
+Compute Module).
+
 \begin{itemize}
@@
 \item
+  was ptp, bild pps output
+\item
   alle clients über ptp verbunden
 \item
-  zentraler reset zwischen zwei pps pulsen um den readout counter auf 0
-  zu setzten
+  dso bild von jeff gerling über rpi4 ptp
 \end{itemize}

### 2023-12-13 src/MagneticReadoutProcessing/MRP/MRPHalRest.py

@@ -65,7 +65,7 @@ class MRPHalRest(MRPHal.MRPHal):
 
     def get_serial_port_information(self) ->MRPHalSerialPortInformation:
         return self.current_port
-    def request_json(self, _command: str):
+    def request_json(self, _command: str, _request_timeout=300):
         if _command is None or not _command:
             raise MRPHalRestException("request_json _command parameter is empty")
 
@@ -84,7 +84,7 @@ class MRPHalRest(MRPHal.MRPHal):
 
         #
 
-        r = requests.get(url=url, allow_redirects=True)
+        r = requests.get(url=url, allow_redirects=True, timeout=_request_timeout)
 
         if r.status_code >= 200 and r.status_code < 300:
             # TRY TO GET SENSOR IMPLEMENTATION

### 2023-12-13 src/MagneticReadoutProcessing/setup.py

@@ -10,7 +10,7 @@ with pathlib.Path(req_path).open() as requirements_txt:
     install_requires = [str(requirement) for requirement in pkg_resources.parse_requirements(requirements_txt)]
 
 setup(name='MagneticReadoutProcessing',
-      version='1.4.0',
+      version='1.4.1',
       description='This library was created for the Low-Field MRI project and allows processing of data measured by magnetic field sensors. The focus is on visualization, followed by the provision of simple interfaces to work with this data. In general its possible to use this lib on all kinds of sensor data.',
       author='Marcel Ochsendorf',
       author_email='info@marcelochsendorf.com',

### 2023-12-13 documentation/thesis/thesis_document.tex
added customizable units

@@
 
+\begin{lstlisting}
+settings:
+ enabled: true
+ export_intermediate_results: false
+ name: pipeline_analyse_fullsphere
+
+stage import:
+ function: import_readings
+ parameters:
+   IP_input_folder: ./readings/fullsphere/
+   IP_file_regex: 360_(.)*.mag.json
+
+stage import_bias_reading:
+ function: import_readings
+ parameters:
+   IP_input_folder: ./readings/fullsphere/
+   IP_file_regex: BIAS_(.)*.mag.json
+
+stage apply_bias_offset:
+ function: apply_sensor_bias_offset
+ parameters:
+   bias_readings: stage import_bias_reading
+   readings_to_calibrate: stage import
+
+stage plot_normal_bias_offset:
+ function: plot_readings
+ parameters:
+   readings_to_plot: stage apply_bias_offset
+   IP_export_folder: ./readings/fullsphere/plots/normal/calibrated/
+   IP_plot_headline_prefix:  Sample N45 12x12x12 magnets calibrated
+
+stage plot_fullsphere:
+ function: plot_fullsphere
+ parameters:
+   readings_to_plot: stage apply_bias_offset
+   IP_export_folder: ./readings/fullsphere/plots/normal/calibrated/
+   IP_plot_headline_prefix:  Sample N45 12x12x12 magnets calibrated
+\end{lstlisting}
+
 \hypertarget{web-base-pipeline-configuration}{%

### 2023-12-13 src/MagneticReadoutProcessing/MRP/MRPDataVisualization.py

@@ -14,7 +14,7 @@ class MRPDataVisualizationException(Exception):
 class MRPDataVisualization:
 
     @staticmethod
-    def plot_error(_readings: [MRPReading.MRPReading], _title: str = '', _filename: str = None):
+    def plot_error(_readings: [MRPReading.MRPReading], _title: str = '', _filename: str = None, _unit: str = "uT"):
         """
         Plots the deviation and mean values from several readings using two plots
 
@@ -40,7 +40,7 @@ class MRPDataVisualization:
 
         # TABLE
         clust_data = []#np.random.random((len(_readings), 5))
-        collabel = ("Reading [id:sensor_id]", "Mean [mT]", "STD Deviation [mT]", "Variance [mT]", "Data-Points")
+        collabel = ("Reading [id:sensor_id]", "Mean [{}}]", "STD Deviation [{}}]", "Variance [{}}]", "Count Data-Points".format(_unit, _unit, _unit))
         labels = []
 
         for idx, reading in enumerate(_readings):
@@ -76,7 +76,7 @@ class MRPDataVisualization:
         ax1.errorbar(x, y, yerr=error, fmt='o')
         ax1.set_xticks(range(0, len(_readings)), labels)
         ax1.set_xlabel("Reading [id:sensor_id]")
-        ax1.set_ylabel("Error (Variance)")
+        ax1.set_ylabel("Error (Variance) [{}]".format(_unit))
 
 
         # SAVE FIGURE IF NEEDED
@@ -88,7 +88,7 @@ class MRPDataVisualization:
         plt.close()
 
     @staticmethod
-    def plot_scatter(_readings: [MRPReading.MRPReading], _title: str = '', _filename: str = None):
+    def plot_scatter(_readings: [MRPReading.MRPReading], _title: str = '', _filename: str = None, _unit: str = "uT"):
         """
         Plots a1 1d scatter plot of the reading data
 
@@ -127,7 +127,7 @@ class MRPDataVisualization:
 
         plt.scatter(x, y, color=coloring)
         plt.title('{} Scatter'.format(_title))
-        plt.xlabel("value [mT]")
+        plt.xlabel("value [{}]".format(_unit))
         plt.ylabel("reading [id:sensor_id]")
         plt.yticks(range(0, len(_readings)),  labels)
 
@@ -141,7 +141,7 @@ class MRPDataVisualization:
 
 
     @staticmethod
[…]

### 2023-12-13 src/MagneticReadoutProcessing/MRP/MRPPolarVisualization.py

@@ -21,6 +21,7 @@ class MRPPolarVisualization():
     sensor_id = int()
     theta_radians = 0.5 * math.pi # 90 degree half phere
     phi_radians = 2 * math.pi # 360 degree
+    title = ""
     def __init__(self, _reading: MRPReading.MRPReading):
         """
         Creates a MRPVisualization instance to plot a given reading in 2D/3D
@@ -46,6 +47,13 @@ class MRPPolarVisualization():
         self.y = self.sensor_distance_radius * np.sin(self.theta) * np.sin(self.phi)
         self.z = self.sensor_distance_radius * np.cos(self.theta)
 
+        # set default title
+        self.set_title("")
+
+    def set_title(self, _title: str):
+        if not _title or len(_title) <= 0:
+            _title = "PolarVisualisation of {}".format(self.measurement.get_name())
+        self.title = _title
     def create_plot(self):
         inp = []
         # NORMALIZE DATA
@@ -92,7 +100,9 @@ class MRPPolarVisualization():
         reshaped_reading_results = inp[:, 2].reshape((self.n_phi, self.n_theta)).T
         # Set colours and render
         fig = plt.figure(figsize=(10, 8)) # *100pixel
+
         ax = fig.add_subplot(111, projection='3d')
+        ax.set_title('{} - Temperature-Error'.format(self.title))
         # COLORMAP
         ## coolwarm -> blue = negative red = positive values
         cmap = cm.coolwarm(reshaped_reading_results)

### 2023-12-13 src/MagneticReadoutProcessing/MRPudpp/UDPPFunctionCollection.py

@@ -186,6 +186,7 @@ class UDPPFunctionCollection:
             for r in readings_to_plot:
                 filename: str = str(Path(exp_path).joinpath("plot3d_{}.png".format(str(r.get_name()).strip(" /."))))
                 visu: MRPPolarVisualization.MRPPolarVisualization = MRPPolarVisualization.MRPPolarVisualization(r)
+                visu.set_title("")
                 visu.plot3d(filename)
 
     @staticmethod

### 2023-12-13 src/MagneticReadoutProcessing/setup.py

@@ -10,7 +10,7 @@ with pathlib.Path(req_path).open() as requirements_txt:
     install_requires = [str(requirement) for requirement in pkg_resources.parse_requirements(requirements_txt)]
 
 setup(name='MagneticReadoutProcessing',
-      version='1.4.1',
+      version='1.4.3',
       description='This library was created for the Low-Field MRI project and allows processing of data measured by magnetic field sensors. The focus is on visualization, followed by the provision of simple interfaces to work with this data. In general its possible to use this lib on all kinds of sensor data.',
       author='Marcel Ochsendorf',
       author_email='info@marcelochsendorf.com',

### 2023-12-14 documentation/thesis/thesis_abstract.tex
more thesis

@@
 different user groups. Complete documentation, tutorials and tests
-enable users to use and adapt the FRamework as quickly as possible. The
-framework for the characterisation of different N45 neodymium magnets,
-which requires the integration of magnetic field sensors, was used for
-the evaluation.
+enable users to use and adapt the Framework as quickly as possible. The
+framework for the characterisation of different magnets, which requires
+the integration of magnetic field sensors, was used for the evaluation.

### 2023-12-14 documentation/thesis/thesis_document.tex
more thesis

--- 2023-12-13 documentation/thesis/thesis_document.tex
@@
 
+\begin{longtable}[]{@{}lllll@{}}
+\caption{Implemented digital halleffect sensors
+\label{Implemented_digital_halleffect_sensors.csv}}\tabularnewline
+\toprule
+& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
+\midrule
+\endhead
+Readout-Axis & 3D & 3D & 3D & 1D\tabularnewline
+Temperature-Sensor & yes & no & yes & no\tabularnewline
+Resolution {[}uT{]} & 98 & 0.2 & 0.007 & 48\tabularnewline
+Range {[}mT{]} & ±130.0 & ±0.8 & ±3 & ±50\tabularnewline
+Interface & \gls{i2c} & \gls{i2c} & \gls{i2c} & \gls{i2c}\tabularnewline
+\bottomrule
+\end{longtable}
+
 \begin{itemize}
@@
 \item
-  list of typical low cost hall sensors
+  for higher ranges analog sensoren nutzen welche jedoch eine
+  aufwändigere schaltung erfodern
 \item
-  =\textgreater{} alle i2c in der regel
+  datenblatte links ergänzen
 \item
+  alle i2c in der regel, welches eine einfache integration ermöglicht
+\item
+  eingebauter temperatursensor ermöglicht temperaturkompensation
+\item
+  conrad teslameter mit seperaten temperatursensor
 \end{itemize}
@@
 \begin{itemize}
-\tightlist
 \item
-  automatic sensor detation
+  automatic sensor detation ablaufdiagramm erst nach i2c geräte scannen
+  dann analog versuchen
 \item
@@
 \item
-  interene mittelung und speichern der werte im buffer
+  interene mittelung und speichern der werte im buffer ringubber welcher
+  bei jedem sync impuls neu belegt wird
+\item
+  \begin{enumerate}
+  \def\labelenumi{\arabic{enumi}.}
+  \setcounter{enumi}{1}
+  \tightlist
+  \item
+    core übernimmt mittelung und auswetung
+  \end{enumerate}
 \item
@@
 \hypertarget{cli-interface}{%
-\subsection{CLI Interface}\label{cli-interface}}
+\subsection{\texorpdfstring{\gls{cli})
+Interface}{ Interface}}\label{cli-interface}}
 
@@
 \centering
-\includegraphics{./generated_images/border_Query_sensors_b_value_using_CLI.png}
-\caption{Query sensors b value using CLI
-\label{Query_sensors_b_value_using_CLI.png}}
+\includegraphics{./generated_images/border_Query_sensors_b_value_using_(+cli).png}
+\caption{Query sensors b value using \gls{cli}
+\label{Query_sensors_b_value_using_(+cli).png}}
 \end{figure}
@@
 \hypertarget{sensor-syncronsisation}{%
-\section{\texorpdfstring{Sensor Syncronsisation
-\label{CHAPTER_Sensor_Syncronsisation}}{Sensor Syncronsisation }}\label{sensor-syncronsisation}}
+\section{Sensor Syncronsisation}\label{sensor-syncronsisation}}
 
@@
 
-At the moment, it is only possible to detect and use sensors that are
-directly connected to the PC with the library. This has the disadvantage
-that there must always be a physical connection. This can make it
-difficult to install multiple sensors in measurement setups where space
-or cable routing options are limited. To make sensors connected to a
-small remote PC available on the network, the `Proxy' module has been
-developed. This can be a single board computer (e.g.~a Raspberry Pi).
-The small footprint and low power consumption make it a good choice. It
-can also be used in a temperature chamber. The approach of implementing
-this via a REST interface also offers the advantage that several
-measurements or experiments can be recorded at the same time with the
-sensors.
+At the current state of implementation, it is only possible to detect
+and use sensors that are directly connected to the \gls{pc} with the
+library. This has the disadvantage that there must always be a physical
+connection. This can make it difficult to install multiple sensors in
+measurement setups where space or cable routing options are limited. To
+make sensors connected to a small \passthrough{\lstinline!remote!}
+\gls{pc} available on the network, the
+\passthrough{\lstinline!Proxy!}\ref{MRPlib_Proxy_Module.png} module has
+been developed. This can be a single board computer (e.g.~a Raspberry
+Pi). The small footprint and low power consumption make it a good
+choice. It can also be used in a temperature chamber. The approach of
+implementing this via a \gls{rest} interface also offers the advantage
+that several measurements or experiments can be recorded at the same
+time with the sensors.
 
@@
 the proxy module, it is possible to link several instances and all
-sensors available in the network are available to the control PC.
+sensors available in the network are available to the control \gls{pc}.
 
@@
 
-The graphic \ref{mrp_proxy_multi.png} shows the modified multi-proxy -
-multi-sensor topology. Here, both proxy instances do not communicate
-directly with the control PC, but remote PC \#2 is connected to remote
-PC \#1. This is then visible as a sensor opposite the Control PC, even
-if there are several proxy instances behind it.
+The graphic \ref{mrp_proxy_multi.png} shows the modified
+\passthrough{\lstinline!multi-proxy - multi-sensor!} topology. Here,
+both proxy instances do not communicate directly with the control
+\gls{pc}, but \passthrough{\lstinline!remote (+pc) \#2!} is connected to
+\passthrough{\lstinline!remote (+pc) \#1!}. This is then visible as a
+sensor opposite the Control \gls{pc}, even if there are several proxy
+instances behind it.
 
@@
 The graphic \ref{MRPlib_Proxy_Module.png} shows the separation of the
-various HAL instances, which communicate with the physically connected
-sensors on the remote PC and the control PC side, which communicates
+various \gls{hal} instances, which communicate with the physically
+connected sensors on the \passthrough{\lstinline!remote!}-\gls{pc} and
+the \passthrough{\lstinline!control!}-\gls{pc} side, which communicates
 with the remote side via the network. For the user, nothing changes in
 the procedure for setting up a measurement. The proxy application must
-always be started on the remote PC side.
+always be started on the \passthrough{\lstinline!remote!} \gls{pc} side.
 
@@
 After the proxy instance has been successfully started, it is optionally
-possible to check the status via the REST interface:
+possible to check the status via the \gls{rest} interface:
 
@@
 their capabilites have also been recognised correctly. To be able to
-configure a measurement on the other, only the IP address or host name
-of the remote PC is required:
+configure a measurement on the other, only the \gls{ip} address or host
+name of the remote \gls{pc} is required:
 
@@
   $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B
-
 \end{lstlisting}
@@
 Individual sensor setups do not require any additional synchronisation
-information, as this is communicated via the USB interface. If several
-sensors are connected locally, they can be connected to each other via
-their sync input using short cables. One sensor acts as the central
-clock (see chapter \ref{CHAPTER_Sensor_Syncronsisation}). However, this
-no longer works for long distances and a diversion must be made via the
-network connection.
+information, as this is communicated via the \gls{usb} interface. If
+several sensors are connected locally, they can be connected to each
+other via their sync input using short cables. One sensor acts as the
+central clock (see chapter \ref{sensor-syncronsisation}). However, this
+no longer works for long distances and the syncronisation must be made
+via the network connection.
 
-If time-critical synchronisation is required, PTP and PPS functionality
-can be used on many single-board computers (such as the RaspberryPi
-Compute Module).
+If time-critical synchronisation is required, \gls{ptp} and \gls{pps}
+output functionality can be used on many single-board computers, such as
+the RaspberryPi Compute Module.
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_example_measurement_analysis_pipeline.png}
+\caption{example measurement analysis pipeline
+\label{example_measurement_analysis_pipeline.png}}
+\end{figure}
+
 \begin{itemize}
@@
 
-\hypertarget{web-base-pipeline-configuration}{%
-\subsection{Web base pipeline
-configuration}\label{web-base-pipeline-configuration}}
+\begin{lstlisting}
+# pipeline_example_measurement_processing.yaml
+settings:
+ enabled: true
+ export_intermediate_results: false
+ name: pipeline_example_measurement_processing
+
+stage import_readings:
+ function: import_readings
+ parameters:
+   IP_input_folder: ./readings/fullsphere/
+   IP_file_regex: 360_(.)*.mag.json
+
+stage import_bias_reading:
+ function: import_readings
+ parameters:
+   IP_input_folder: ./readings/fullsphere/
+   IP_file_regex: bias_reading.mag.json
+
+stage apply_bias_offset:
+ function: apply_sensor_bias_offset
+ parameters:
+   bias_readings: stage import_bias_reading
+   readings_to_calibrate: stage import_readings
+
+stage apply_temp_compensation:
+ function: apply_temperature_compensation
+ parameters:
+   readings_to_calibrate: stage import_readings
+
+stage plot_normal_bias_offset:
+ function: plot_readings
+ parameters:
+   readings_to_plot: stage apply_temp_compensation
+   IP_export_folder: ./readings/fullsphere/plots/
+   IP_plot_headline_prefix:  Sample N45 12x12x12 magnets calibrated
+
+stage export_readings:
+ function: export_readings
+ parameters:
+   readings_to_plot: stage apply_temp_compensation
+   IP_export_folder: ./readings/fullsphere/plots/
+\end{lstlisting}
+
+\hypertarget{package-distribution}{%
+\section{Package distribution}\label{package-distribution}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_MagneticReadoutProcessing_library_hosted_on_PyPi.png}
+\caption{MagneticReadoutProcessing library hosted on PyPi
+\label{MagneticReadoutProcessing_library_hosted_on_PyPi.png}}
+\end{figure}
+
+One important point that improves usability for users is the simple
+installation of the library. As it was created in the Python programming
+language, there are several public package directories where users can
+provide their software modules. Here,
+\passthrough{\lstinline!PyPi!}\cite{PyPI}\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}\cite{MagneticReadoutProcessingPyPI}
+is the most commonly used package directory and offers direct support
+for the package installation programm \gls{pip}.
+
+In doing so, \gls{pip} not only manages possible package dependencies,
+but also manages the installation of different versions of a package. In
+addition, the version compatibility is also checked during the
+installation of a new package, which can be resolved manually by the
+user in the event of conflicts.
+
+\begin{lstlisting}[language=bash]
+  # https://pypi.org/project/MagneticReadoutProcessing/
+  # install the latest version
+  $ pip3 install MagneticReadoutProcessing
+  # install the specific version 1.4.0
+  $ pip3 install MagneticReadoutProcessing==1.4.0
+\end{lstlisting}
+
+To make the library compatible with the package directory, Python
+provides separate installation routines that build a package in an
+isolated environment and then provide an installation
+\passthrough{\lstinline!wheel!} archive. This can then be uploaded to
+the package directory.
+
+Since the library requires additional dependencies
+(e.g.~\passthrough{\lstinline!numpy!},
+\passthrough{\lstinline!matplotlib!}), which cannot be assumed to be
+already installed on the target system, these must be installed prior to
+the actual installation. These can be specified in the library
+installation configuration \passthrough{\lstinline!setup.py!} for this
+purpose.
+
+\begin{lstlisting}[language=Python]
+  # $ cat ./setup.py
+
+  # dynamic requirement loading using 'requirements.txt'
+  req_path = 'requirements.txt'
+  with pathlib.Path(req_path).open() as requirements_txt:
+      install_requires = [str(requirement) for requirement in pkg_resources.parse_requirements(requirements_txt)]
+
+  setup(name='MagneticReadoutProcessing',
+        version='1.4.3',
+        url='https://github.com/LFB-MRI/MagnetCharacterization/',
+        packages= ['MRP', 'MRPcli', 'MRPudpp', 'MRPproxy'],
+        install_requires=install_requires,
+        include_package_data=True,
+        package_data={"": ["**/*.mag.json", "**/*.yaml", "**/*.html", "**/*.js", "**/*.css", "**/*.md", "**/*.json", "**/*.ts", "**/*.xml"]},
+        entry_points={
+            'console_scripts': [
+              'MRPCli = MRPcli.cli:run',
+              'MRPUdpp = MRPudpp.uddp:run',
+              'MRPproxy = MRPproxy.mrpproxy:run'
+            ]
+        }
+      )
+\end{lstlisting}
+
+To make the \gls{cli} scripts written in Python easier for the user to
+execute without having to use the \passthrough{\lstinline!python3!}
+prefix. This has been configured in the installation configuration using
+the \passthrough{\lstinline!entry\_points!} option, and the following
+commands are available to the user:
 
@@
 \item
-  drag\& drop system
+  \passthrough{\lstinline!MRPcli --help!} instead of
+  \passthrough{\lstinline!python3 cli.py --help!}
 \item
-  automatische convertierung zum yaml system
+  \passthrough{\lstinline!MRPudpp --help!} instead of
+  \passthrough{\lstinline!python3 udpp.py --help!}
+\item
+  \passthrough{\lstinline!MRPproxy --help!} instead of
+  \passthrough{\lstinline!python3 proxy.py --help!}
 \end{itemize}
 
-\hypertarget{package-management}{%
-\section{Package management}\label{package-management}}
+In addition, these commands are available globally in the system without
+the terminal shell being located in the library folder.
+
+\hypertarget{documentation}{%
+\subsection{Documentation}\label{documentation}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
+\caption{MagneticReadoutProcessing documentation hosted on ReadTheDocs
+\label{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}}
+\end{figure}
+
+In order to provide comprehensive documentation for the user, the source
+code was documented using
+Python-\passthrough{\lstinline!docstrings!}\cite{PythonDocstringReference}.
+This includes, among other things:
 
@@
 \item
-  verteilung durch paketmanager
+  Function description
 \item
-  docker cli beispiel
+  Input parameters - \passthrough{\lstinline!param!} and
+  \passthrough{\lstinline!type!}
+\item
+  Return value - \passthrough{\lstinline!returns!},
+  \passthrough{\lstinline!rtype!}
 \end{itemize}
 
-\hypertarget{documentation}{%
-\subsection{Documentation}\label{documentation}}
+\begin{lstlisting}[language=Python]
+    # MRPDataVisualisation.py - example docstring
+    def plot_temperature(_readings: [MRPReading.MRPReading], _title: str = '', _filename: str = None, _unit: str = "degree C") -> str:
+        """
+        Plots a temperature plot of the reading data as bar-graph figure
+
+        :param _readings: readings to plot
+        :type _readings: list(MRPReading.MRPReading)
+
+        :param _title: Title text of the figure, embedded into the head
+        :type _title: str
+
+        :param _filename: export graphic to an given absolute filepath with .png
+        :type _filename: str
+
+        :returns: returns the filepath of the generated .png image file
+        :rtype: str
+        """
+
+        if _readings is None or len(_readings) <= 0:
+            raise MRPDataVisualizationException("no readings in _reading given")
+        num_readings = len(_readings)
+        # ...
+\end{lstlisting}
+
+Since `docstrings' only document the source code, but do not provide
+simple how-to-use instructions, the documentation framework
+\passthrough{\lstinline!Sphinx!}\cite{SphinxDocumentation} was used
+for this purpose. This framework makes it possible to generate
+\gls{html} or \gls{pdf} documentation from various source code
+documentation formats, such as the used
+\passthrough{\lstinline!docstrings!}. These are converted into a
+Markdown format in an intermediate step and this also allows to add
+further user documentation such as examples or installation
+instructions.
+
+In order to make the documentation created by
+\passthrough{\lstinline!Sphinx!} accessible to the user, there are, as
+with the package management by \passthrough{\lstinline!PyPi!} services,
+which provide Python library documentation online.
+
+\cite{ReadTheDocs}
+
+\cite{MagneticReadoutProcessingReadTheDocs}
+
+\ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
+
+\hypertarget{tests}{%
+\subsection{Tests}\label{tests}}
 

### 2023-12-14 src/MagneticReadoutProcessing/setup.py

@@ -10,7 +10,8 @@ with pathlib.Path(req_path).open() as requirements_txt:
     install_requires = [str(requirement) for requirement in pkg_resources.parse_requirements(requirements_txt)]
 
 setup(name='MagneticReadoutProcessing',
-      version='1.4.3',
+      version='1.4.3'
+              '',
       description='This library was created for the Low-Field MRI project and allows processing of data measured by magnetic field sensors. The focus is on visualization, followed by the provision of simple interfaces to work with this data. In general its possible to use this lib on all kinds of sensor data.',
       author='Marcel Ochsendorf',
       author_email='info@marcelochsendorf.com',

### 2023-12-16 documentation/thesis/thesis_document.tex
more thesis

@@
 \end{itemize}
+
+\hypertarget{usecases}{%
+\chapter{Usecases}\label{usecases}}
 
@@
 
-The graphic \ref{mrp_proxy_multi.png} shows the modified
+The figure \ref{mrp_proxy_multi.png} shows the modified
 \passthrough{\lstinline!multi-proxy - multi-sensor!} topology. Here,
@@
 
-The graphic \ref{MRPlib_Proxy_Module.png} shows the separation of the
+The figure \ref{MRPlib_Proxy_Module.png} shows the separation of the
 various \gls{hal} instances, which communicate with the physically
@@
     PRECHECK: SENSOR_HAL: 4242 # SENSOR B FOUND
-    Terminate  [Y/n] [y]: 
+    Terminate  Proxy instance [y/N] [n]: 
 \end{lstlisting}
@@
 other via their sync input using short cables. One sensor acts as the
-central clock (see chapter \ref{sensor-syncronsisation}). However, this
-no longer works for long distances and the syncronisation must be made
-via the network connection.
+central clock (see chapter \ref{sensor-syncronsisation}). this no longer
+works for long distances and the syncronisation must be made via the
+network connection.
 
@@
 \end{figure}
+
+\ref{example_measurement_analysis_pipeline.png}
 
@@
 
-\hypertarget{package-distribution}{%
-\section{Package distribution}\label{package-distribution}}
+\hypertarget{tests}{%
+\section{Tests}\label{tests}}
 
@@
 \centering
-\includegraphics{./generated_images/border_MagneticReadoutProcessing_library_hosted_on_PyPi.png}
-\caption{MagneticReadoutProcessing library hosted on PyPi
-\label{MagneticReadoutProcessing_library_hosted_on_PyPi.png}}
+\includegraphics{./generated_images/border_MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png}
+\caption{MRP library test results for different submodules executed in
+PyCharm \gls{ide}
+\label{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png}}
 \end{figure}
+
+Software tests in libraries offer numerous advantages for improving
+quality and efficiency. Firstly, they enable the identification of
+errors and vulnerabilities before software is published as a new
+version. This significantly improves the reliability of library
+applications. Tests also ensures consistent and reliable performance,
+which is particularly important when libraries are used by different
+users and for different usecases.
+
+During the development of the library, test cases were also created for
+all important functionalities and use cases. The test framework
+\passthrough{\lstinline!PyTest!}\cite{PyTest} was used for this
+purpose, as it offers direct integration in most \gls{ide}s (see
+\ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
+and also because it provides detailed and easy-to-understand test
+reports as output in order to quickly identify and correct errors. Since
+all intended use cases were mapped using the test cases created, the
+code of the test cases could later be used in slightly simplified
+variants as examples for the documentation.
+
+\begin{lstlisting}[language=Python]
+# $ cat test_mrpreading.py
+class TestMPRReading(unittest.TestCase):
+    # PREPARE A INITIAL CONFIGURATION FILE FOR ALL FOLLOWING TEST CASES IN THIS FILE
+    def setUp(self) -> None:
+        self.import_export_test_folderpath: str = os.path.join(os.path.dirname(os.path.abspath(__file__)), "tmp")
+        self.import_export_test_filepath:str = os.path.join(self.import_export_test_folderpath, "tmp")
+
+    def test_matrix(self):
+        reading: MRPReading = MRPSimulation.MRPSimulation.generate_reading()
+        matrix: np.ndarray = reading.to_numpy_matrix()
+        n_phi: float = reading.measurement_config.n_phi
+        n_theta: float = reading.measurement_config.n_theta
+        # CHECK MATRIX SHAPE
+        self.assertTrue(matrix.shape != (n_theta, ) and len(matrix.shape) <= n_phi)
+
+    def test_export_reading(self) -> None:
+        reading: MRPReading = self.test_reading_init()
+        self.assertIsNotNone(reading)
+        # EXPORT READING TO A FILE
+        reading.dump_to_file(self.import_export_test_filepath)
+
+    def test_import_reading(self):
+        # CREATE EMPTY READING
+        reading_imported:MRPReading = MRPReading.MRPReading(None)
+        # LOAD READING FROM FILE
+        reading_imported.load_from_file(self.import_export_test_filepath)
+        # CHECK IF ENTRIES ARE POPULATED
+        self.assertIsNotNone(reading_imported.additional_data)
+        self.assertIsNotNone(reading_imported.data)
+
+if __name__ == '__main__':
+    unittest.main()
+\end{lstlisting}
+
+One problem, however, is the parts of the library that require direct
+access to external hardware. These are, for example, the
+\passthrough{\lstinline!MRPHal!} and
+\passthrough{\lstinline!MRPHalRest!} modules, which are required to read
+out sensors connected via the network. Two different approaches were
+used here. In the case of local development, the test runs were carried
+out on a \gls{pc} that can reach the network hardware and thus the test
+run could be carried out with real data.
+
+In the other scenario, the tests are to be carried out before a new
+release in the repository on the basis of
+\passthrough{\lstinline!Github Actions!}\cite{GithubActions}. Here
+there is the possibility to host local runner software, which then has
+access to the hardware, but then a \gls{pc} must be permanently
+available for this task. Instead, the hardware sensors were simulated by
+software and executed via virtualisation on the systems provided by
+\passthrough{\lstinline!Github Actions!}\cite{GithubActions}.
+
+\hypertarget{package-distribution}{%
+\section{Package distribution}\label{package-distribution}}
 
@@
 for the package installation programm \gls{pip}.
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_MagneticReadoutProcessing_library_hosted_on_PyPi.png}
+\caption{MagneticReadoutProcessing library hosted on PyPi
+\label{MagneticReadoutProcessing_library_hosted_on_PyPi.png}}
+\end{figure}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
-\caption{MagneticReadoutProcessing documentation hosted on ReadTheDocs
-\label{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}}
-\end{figure}
-
-In order to provide comprehensive documentation for the user, the source
-code was documented using
-Python-\passthrough{\lstinline!docstrings!}\cite{PythonDocstringReference}.
-This includes, among other things:
+In order to provide comprehensive documentation for the enduser, the
+source code was documented using
+Python-\passthrough{\lstinline!docstrings!}\cite{PythonDocstringReference}
+and the Python3.5 type annotations:
 
@@
 \item
-  Input parameters - \passthrough{\lstinline!param!} and
+  Input parameters - using \passthrough{\lstinline!param!} and
   \passthrough{\lstinline!type!}
 \item
-  Return value - \passthrough{\lstinline!returns!},
+  Return value - using \passthrough{\lstinline!returns!},
   \passthrough{\lstinline!rtype!}
@@
 
-        :returns: returns the filepath of the generated .png image file
+        :returns: returns the abs filepath of the generated .png image file
         :rtype: str
@@
 \end{lstlisting}
+
+The use of type annotations also simplifies further development, as
+modern \gls{ide}s can more reliably display possible methods to the user
+as an assistance.
 
@@
 
-\cite{ReadTheDocs}
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
+\caption{MagneticReadoutProcessing documentation hosted on ReadTheDocs
+\label{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}}
+\end{figure}
 
-\cite{MagneticReadoutProcessingReadTheDocs}
+Once the finished documentation has been generated from static
+\gls{html} files, it is stored in the project repository. Another
+publication option is to host the documentation via online services such
+as \passthrough{\lstinline!ReadTheDocs!}\cite{ReadTheDocs}, where
+users can make documentation for typical software projects available to
+others.
 
-\ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
+The documentation has also been uploaded for
+\passthrough{\lstinline!ReadTheDocs!}\cite{MagneticReadoutProcessingReadTheDocs}
+and linked in the repository and on the overview
+page\ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
+on \passthrough{\lstinline!PyPi!}.
 
-\hypertarget{tests}{%
-\subsection{Tests}\label{tests}}
+The process of creating and publishing the documentation has been
+automated using
+\passthrough{\lstinline!GitHub Actions!}\cite{GithubActions}, so
+that it is always automatically kept up to date with new features.
 

### 2023-12-16 src/MagneticReadoutProcessing/MRP/MRPDataVisualization.py

@@ -224,3 +224,5 @@ class MRPDataVisualization:
 
         plt.close()
 
+
+

### 2023-12-16 src/UnifiedMagBoardFirmware/include/baseSensor.h

@@ -30,7 +30,6 @@ public:
     baseSensor();
     bool begin(TwoWire &_wire_instance);
     bool is_valid();
-    
     String capabilities();
     String get_sensor_name();
 

### 2023-12-17 documentation/thesis/thesis_document.tex
more thesis: code listings fix script added

@@
 
-\hypertarget{cli-interface}{%
-\subsection{\texorpdfstring{\gls{cli})
-Interface}{ Interface}}\label{cli-interface}}
+\hypertarget{user-interface}{%
+\subsection{User-Interface}\label{user-interface}}
 
@@
 \centering
-\includegraphics{./generated_images/border_Sensors_CL-Interface.png}
-\caption{Sensors CL-Interface \label{Sensors_CL-Interface.png}}
+\includegraphics{./generated_images/border_Sensors_(+cli).png}
+\caption{Sensors \gls{cli} \label{Sensors_(+cli).png}}
 \end{figure}
@@
 the procedure for setting up a measurement. The proxy application must
-always be started on the \passthrough{\lstinline!remote!} \gls{pc} side.
+always be started\ref{lst:mrpcli_proxy_start} on the
+\passthrough{\lstinline!remote!} \gls{pc} side.
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash, caption={MRPproxy usage to enable local sensor usage over network}, label=lst:mrpcli_proxy_start]
 # START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
 $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B # add another proxy instance http://proxyinstance_2.local for multi-sensor, multi-proxy chain
-    Proxy started. http://0.0.0.0:5556/
+Proxy started. http://remotepc.local:5556/
 PRECHECK: SENSOR_HAL: 1337 # SENSOR A FOUND
@@
 After the proxy instance has been successfully started, it is optionally
-possible to check the status via the \gls{rest} interface:
+possible to check the status via the \gls{rest}
+interface:\ref{lst:mrpcli_config_rest}
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash, caption={MRPproxy REST enpoiint query examples}, label=lst:mrpcli_config_rest]
     # GET PROXY STATUS
@@
 configure a measurement on the other, only the \gls{ip} address or host
-name of the remote \gls{pc} is required:
+name of the remote \gls{pc} is
+required\ref{lst:mrpcli_config_using_rpc}.
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash, caption={MRPcli usage example to connect with a network sensor}, label=lst:mrpcli_config_using_rpc]
 # CONFIGURE MEASUREMENT JOB USING A PROXY INSTANCE
-  $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B
+$ MRPcli config setupsensor testcfg --path http://proxyinstance.local:5556
+> remote sensor connected: True using proxy connection:
+> http://proxyinstance.local:5556 with 1 local sensor connected
 \end{lstlisting}
@@
 
-\hypertarget{commandline-interface}{%
-\section{Commandline interface}\label{commandline-interface}}
+\hypertarget{command-line-interface}{%
+\section{Command Line Interface}\label{command-line-interface}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_MRP_(+cli)_output_to_configure_a_new_measurement.png}
+\caption{MRP \gls{cli} output to configure a new measurement
+\label{MRP_(+cli)_output_to_configure_a_new_measurement.png}}
+\end{figure}
+
+In the first version of this library, the user had to write his own
+Python scripts even for short measurement and visualisation tasks.
+However, this was already time-consuming for reading out a sensor and
+configuring the measurement parameters and metadata and quickly required
+more than 100 lines of new Python code. Although such examples are
+provided in the documentation, it must be possible for programming
+beginners in particular to use them. To simplify these tasks, a
+\gls{cli}\ref{example_measurement_analysis_pipeline.png} was implemented
+around this library, which is then also supplied as a fixed component.
+This \gls{cli} implements the following functionalities:
 
@@
 \item
-  automatische sensor dedettion
+  Detection of connected sensors
 \item
-  planung verschiedener messungen mit untersch. hardware
+  Configuration of measurement series
 \item
-  zentrale abarbeitung
+  Recording of measured values from stored measurement series
+\item
+  Simple commands for checking recorded measurement series and their
+  data.
 \end{itemize}
+
+Thanks to this functionality of the \gls{cli}, it is now possible to
+connect a sensor to the \gls{pc}, configure a measurement series with it
+and run it at the end. The result is then an exported file with the
+measured values. These can then be read in again with the library and
+processed further. The following\ref{lst:mrpcli_config_run} bash code
+shows this procedure in detail:
+
+\begin{lstlisting}[language=bash, caption={CLI example for configuring a measurement run}, label=lst:mrpcli_config_run]
+# CLI EXAMPLE FOR CONFIGURING A MEASUREMENT RUN
+## CONFIGURE THE SENSOR TO USE
+$ MRPcli config setupsensor testcfg
+> 0 - Unified Sensor 386731533439 - /dev/cu.usbmodem3867315334391
+> Please select one of the found sensors [0]:
+> sensor connected: True 1243455
+## CONFIGURE THE MEASUREMENT
+$ MRPcli config setup testcfg
+> CONFIGURE testcfg
+> READING-NAME: [testreading]: testreading
+> OUTPUT-FOLDER [/cli/reading]: /tmp/reading_folder_path
+> NUMBER DATAPOINTS: [1]: 10
+> NUMBER AVERAGE READINGS PER DATAPOINT: [1]: 100
+# RUN THE CONFIGURED MEASUREMENT
+$ MRPcli measure run
+> STARTING MEASUREMENT RUN WITH FOLLOWING CONFIGS: ['testcfg']
+> config-test: OK
+> sensor-connection-test: OK
+> START MEASUREMENT CYCLE
+> sampling 10 datapoints with 100 average readings
+> SID:0 DP:0 B:47.359mT TEMP:23.56
+> ....
+> dump_to_file testreading_ID:525771256544952_SID:0_MAG:N45_CUBIC_12x12x12.mag.json
+\end{lstlisting}
 
@@
 
-\begin{lstlisting}
-# pipeline_example_measurement_processing.yaml
-settings:
- enabled: true
- export_intermediate_results: false
- name: pipeline_example_measurement_processing
-
+\begin{lstlisting}[caption={Example User Defined Processing Pipeline}]
 stage import_readings:
@@
 
+Software tests in libraries offer numerous advantages for improving
+quality and efficiency. Firstly, they enable the identification of
+errors and vulnerabilities before software is published as a new
+version. This significantly improves the reliability of library
+applications. Tests also ensures consistent and reliable performance,
+which is particularly important when libraries are used by different
+users and for different usecases.
+
 \begin{figure}
@@
 
-Software tests in libraries offer numerous advantages for improving
-quality and efficiency. Firstly, they enable the identification of
-errors and vulnerabilities before software is published as a new
-version. This significantly improves the reliability of library
-applications. Tests also ensures consistent and reliable performance,
-which is particularly important when libraries are used by different
-users and for different usecases.
-
 During the development of the library, test cases were also created for
@@
 and also because it provides detailed and easy-to-understand test
-reports as output in order to quickly identify and correct errors. Since
+reports as output in order to quickly identify and correct errors. It
+also allows to tag tests, which is useful for grouping tests or
+excluding certain tests in certain build environment scenarios. Since
 all intended use cases were mapped using the test cases created, the
 code of the test cases could later be used in slightly simplified
-variants as examples for the documentation.
+variants\ref{lst:pytest_example_code} as examples for the documentation.
 
-\begin{lstlisting}[language=Python]
+\begin{lstlisting}[language=Python, caption={Example pytest class for testing MRPReading module functions}, label=lst:pytest_example_code]
 # $ cat test_mrpreading.py
@@
   def setUp(self) -> None:
-        self.import_export_test_folderpath: str = os.path.join(os.path.dirname(os.path.abspath(__file__)), "tmp")
-        self.import_export_test_filepath:str = os.path.join(self.import_export_test_folderpath, "tmp")
+      self.test_folder: str = os.path.join(os.path.dirname(os.path.abspath(__file__)), "tmp")
+      self.test_file:str = os.path.join(self.import_export_test_folderpath, "tmp")
 
   def test_matrix(self):
-        reading: MRPReading = MRPSimulation.MRPSimulation.generate_reading()
+      reading: MRPReading = MRPSimulation.generate_reading()
       matrix: np.ndarray = reading.to_numpy_matrix()
@@
       # CHECK MATRIX SHAPE
-        self.assertTrue(matrix.shape != (n_theta, ) and len(matrix.shape) <= n_phi)
+      self.assertTrue(matrix.shape != (n_theta,))
+      self.assertTrue(len(matrix.shape) <= n_phi))
 
@@
       # EXPORT READING TO A FILE
-        reading.dump_to_file(self.import_export_test_filepath)
+      reading.dump_to_file(self.test_file)
 
@@
       # LOAD READING FROM FILE
-        reading_imported.load_from_file(self.import_export_test_filepath)
+      reading_imported.load_from_file(self.test_file)
       # CHECK IF ENTRIES ARE POPULATED
@@
       self.assertIsNotNone(reading_imported.data)
-
-if __name__ == '__main__':
-    unittest.main()
 \end{lstlisting}
@@
 is the most commonly used package directory and offers direct support
-for the package installation programm \gls{pip}.
+for the package installation programm
+\gls{pip}\ref{lst:setup_lib_with_pip}.
 
@@
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash, caption={Bash commands to install the MagneticReadoutProcessing library using pip}, label=lst:setup_lib_with_pip]
 # https://pypi.org/project/MagneticReadoutProcessing/
@@
 the actual installation. These can be specified in the library
-installation configuration \passthrough{\lstinline!setup.py!} for this
+installation configuration
+\passthrough{\lstinline!setup.py!}\ref{lst:setup_py_req} for this
 purpose.
 
-\begin{lstlisting}[language=Python]
-  # $ cat ./setup.py
-
+\begin{lstlisting}[language=Python, caption={setup.py with dynamic requirement parsing used given requirements.txt}, label=lst:setup_py_req]
 # dynamic requirement loading using 'requirements.txt'
-  req_path = 'requirements.txt'
+req_path = './requirements.txt'
 with pathlib.Path(req_path).open() as requirements_txt:
@@
       install_requires=install_requires,
-        include_package_data=True,
-        package_data={"": ["**/*.mag.json", "**/*.yaml", "**/*.html", "**/*.js", "**/*.css", "**/*.md", "**/*.json", "**/*.ts", "**/*.xml"]},
       entry_points={
@@
 
-\begin{lstlisting}[language=Python]
+The use of type annotations also simplifies further development, as
+modern \gls{ide}s can more reliably display possible methods to the user
+as an assistance.\ref{pydocstring}
+
+\begin{lstlisting}[language=Python, caption={Python docstring example}, label=lst:pydocstring]
     # MRPDataVisualisation.py - example docstring
@@
         """
-        Plots a temperature plot of the reading data as bar-graph figure
-
+        Plots a temperature plot of the reading data as figure
         :param _readings: readings to plot
         :type _readings: list(MRPReading.MRPReading)
-
         :param _title: Title text of the figure, embedded into the head
         :type _title: str
-
         :param _filename: export graphic to an given absolute filepath with .png
         :type _filename: str
-
-        :returns: returns the abs filepath of the generated .png image file
+        :returns: returns the abs filepath of the generated file
         :rtype: str
         """
-
         if _readings is None or len(_readings) <= 0:
@@
 \end{lstlisting}
-
-The use of type annotations also simplifies further development, as
-modern \gls{ide}s can more reliably display possible methods to the user
-as an assistance.
 

### 2023-12-17 documentation/thesis/build_thesis.sh

@@ -26,6 +26,7 @@ rm -Rf generated_images
 mkdir -p generated_images
 
 rm -f ./thesis_document_tmp.md
+rm -f ./thesis_document_tmp.md.*
 # REMOVE GENERATED TEX
 rm -f ./thesis_declaration.tex
 rm -f ./thesis_document.tex
@@ -70,7 +71,7 @@ do
     sed -e "/$str/ {" -e "r $f.md" -e 'd' -e '}' -i ./thesis_document_tmp.md 
 done
 
-# ADD IMAGE BORDERS
+
 
 
 
@@ -87,6 +88,7 @@ do
     DIR="$(dirname "${f}")" 
     filenameimageboarder="./generated_images/border_$FN"
     cp "$f" "$filenameimageboarder"
+    # ADD IMAGE BORDERS
     convert -bordercolor transparent -border 10 "$f" "$filenameimageboarder"
 
 
@@ -114,12 +116,11 @@ do
 done
 
 
+# CONVERT LISTINGS
+python3 convert_listings_head.py ./thesis_document_tmp.md 
 
 
-
-
-
-pandoc ./thesis_document_tmp.md -o ./thesis_document.tex --from markdown --biblatex --template ./pandoc_template.tex --listings --top-level-division=chapter --lua-filter ./pandoc_filters/pandoc-gls.lua
+pandoc ./thesis_document_tmp.md.listings -o ./thesis_document.tex --from markdown --biblatex --template ./pandoc_template.tex --listings --top-level-division=chapter --lua-filter ./pandoc_filters/pandoc-gls.lua #x -M codeBlockCaptions=true
 # NOW THE HACKY PART WE WANT TO USE THE STANDART cite command instead the from pandoc used cite to we use sed to hard replace the stuff
 sed -i 's/\\autocite{/\\cite{/g' ./thesis_document.tex
 # python3 ./fix-table-color-bleed.py ./thesis_document.tex > ./thesis_document.tex

### 2023-12-17 documentation/thesis/convert_listings_head.py

@@ -1,0 +1,63 @@
+import argparse
+import sys
+import re
+import json
+parser = argparse.ArgumentParser(description='Process some markdown to pandoc listings compatible listings')
+parser.add_argument('file', type=str, help='markdownfile to process')
+args = parser.parse_args()
+
+#file_to_open: str = "./thesis_document_tmp.md"
+file_to_open = args.file
+
+if not args.file:
+    sys.exit(0)
+print(file_to_open)
+
+
+
+
+
+
+
+text_content:str = ""
+lines : [str] = []
+with open(file_to_open,'r') as file:
+    text_content = file.read()
+    lines = text_content.split('\n')
+    
+    
+    
+    regex_end = re.compile(r"^[\s]*```[\s]*$", re.IGNORECASE) # FOR CLOSING CASE ```
+    regex_simple = re.compile(r"^[\s]*```([a-z0-9]*)([\s][{].*[}])*[\s]*$") # FOR SIMPLE CASES ```bash and ```php
+    #regex_json = re.compile(r"[\s]*([A-Za-z0-9]*)[=]([\"][^\"]*)[\"]")
+    # ```bash  => ~~~ { .php }
+    for idx, line in enumerate(lines):
+            result = regex_simple.search(lines[idx])
+            #lines[idx] = regex_simple.sub("~~~", lines[idx])
+            if result:
+                gres = result.groups(1)
+                if len(gres) > 0 and len(gres[0]) > 0:
+                    print(gres[0])
+
+                    if len(gres) > 1 and len(str(gres[1])) > 1: # FOR COMPLEX
+                        json_str = str(gres[1]).replace("{", "").replace("}", "")
+                        # CONSTRUCT NEW LINE ~~~ { .<language> caption="XYZ" test="123" }
+                        lines[idx] = '~~~ § {} {} $'.format(".{}".format(gres[0]), json_str).replace("§", "{").replace("$", "}")
+                        print(lines[idx])
+                    else:
+                        # CONSTRUCT NEW LINE ~~~ { .<language> }
+                        lines[idx] = '~~~ § .{} $'.format(gres[0]).replace("§", "{").replace("$", "}")
+
+                else:
+                     lines[idx] = regex_end.sub("~~~", lines[idx])
+ 
+
+
+    # ```  => ~~~
+    #for idx, line in enumerate(lines):
+    #        lines[idx] = regex_end.sub("~~~", lines[idx])
+
+
+
+with open( file_to_open + ".listings", 'w+') as writer:
+    writer.write("\n".join(lines))

### 2023-12-17 documentation/thesis/thesis_document.tex
more thesis

@@
 and use sensors that are directly connected to the \gls{pc} with the
-library. This has the disadvantage that there must always be a physical
-connection. This can make it difficult to install multiple sensors in
-measurement setups where space or cable routing options are limited. To
-make sensors connected to a small \passthrough{\lstinline!remote!}
-\gls{pc} available on the network, the
+\gls{mrp}-library. This has the disadvantage that there must always be a
+physical connection. This can make it difficult to install multiple
+sensors in measurement setups where space or cable routing options are
+limited. To make sensors connected to a small
+\passthrough{\lstinline!remote!} \gls{pc} available on the network, the
 \passthrough{\lstinline!Proxy!}\ref{MRPlib_Proxy_Module.png} module has
@@
 
+Usability improvements in software libraries are crucial for efficient
+and user-friendly development. Intuitive API documentation, clearly
+structured code examples and improved error messages promote a smooth
+developer experience. Standardised naming conventions and well
+thought-out default values simplify the application. A \gls{gui} or
+\gls{cli} application for complex libraries can make it easier to use,
+especially for developers with less experience. Continuous feedback
+through automated tests and comprehensive error logs enable faster bug
+fixing. The integration of community feedback and regular updates
+promotes the adaptability of the \gls{mrp}-library to changing needs.
+Effective usability improvements help to speed up development processes
+and increase the satisfaction of the developer community. In the
+following, some of these have been added in and around the
+\gls{mrp}-library, but they are only optional components for the
+intended use.
+
 \hypertarget{command-line-interface}{%
@@
 
-In the first version of this library, the user had to write his own
-Python scripts even for short measurement and visualisation tasks.
-However, this was already time-consuming for reading out a sensor and
-configuring the measurement parameters and metadata and quickly required
-more than 100 lines of new Python code. Although such examples are
-provided in the documentation, it must be possible for programming
+In the first version of this \gls{mrp}-library, the user had to write
+his own Python scripts even for short measurement and visualisation
+tasks. However, this was already time-consuming for reading out a sensor
+and configuring the measurement parameters and metadata and quickly
+required more than 100 lines of new Python code. Although such examples
+are provided in the documentation, it must be possible for programming
 beginners in particular to use them. To simplify these tasks, a
 \gls{cli}\ref{example_measurement_analysis_pipeline.png} was implemented
-around this library, which is then also supplied as a fixed component.
-This \gls{cli} implements the following functionalities:
+around this \gls{mrp}-library, which is then also supplied as a fixed
+component. This \gls{cli} implements the following functionalities:
 
@@
 and run it at the end. The result is then an exported file with the
-measured values. These can then be read in again with the library and
-processed further. The following\ref{lst:mrpcli_config_run} bash code
-shows this procedure in detail:
+measured values. These can then be read in again with the
+\gls{mrp}-library and processed further. The bash
+code\ref{lst:mrpcli_config_run} shows this procedure in detail.
 
@@
 
-\ref{example_measurement_analysis_pipeline.png}
+After it is very easy for users to carry out measurements using the
+\gls{cli}, the next logical step is to analyse the recorded data. This
+can involve one or several hundred data records. Again, the procedure
+for the user is to write their own evaluation scripts using the
+\gls{mrp}-library. This is particularly useful for complex analyses or
+custom algorithms, but not necessarily for simple standard tasks such as
+bias compensation or graphical plot outputs. For this purpose, a further
+\gls{cli} application was created, which enables the user to create and
+execute complex evaluation pipelines for measurement data without
+programming. The example\ref{example_measurement_analysis_pipeline.png}
+shows a typical measurement data analysis pipeline, which consists of
+the following steps:
 
@@
 \item
-  datenanalyse für nicht programmieruer
+  Import the measurements
 \item
-  automatisierter aufbau der call-tree
+  Determine sensor bias value from imported measurements using a
+  reference measurement
 \item
-  mit typcheck
+  Apply linear temperature compensation
 \item
-  alle funktionen mit bestimmer signtur werden automatisch aus globals
-  geladen und stehen nutzer zur verfühung
+  Export the modified measurements
+\item
+  Create a graphical plot of all measurements with standard deviation
 \end{itemize}
 
-\begin{lstlisting}[caption={Example User Defined Processing Pipeline}]
+In order to implement such a pipeline, the
+\passthrough{\lstinline!yaml!} file format was chosen for the definition
+of the pipeline, as this is easy to understand and can also be easily
+edited with a text editor. Detailed examples can be found in the
+documentation\cite{MagneticReadoutProcessingReadTheDocs}. The
+pipeline definition consists of sections which execute the appropriate
+Python commands in the background. The signatures in the
+\passthrough{\lstinline!yaml!} file are called using
+\passthrough{\lstinline!reflection!} and a real-time search of the
+loaded
+\passthrough{\lstinline!global() symbol table!}\cite{PythonGlobalSymbolTable}.
+This system makes almost all Python functions available to the user. To
+simplify use, a pre-defined list of tested \gls{mrp} library functions
+for use in pipelines is listed in the
+documentation\cite{MagneticReadoutProcessingReadTheDocs}. The
+following pipeline definition\ref{lst:mrpuddp_example_yaml} shows the
+previously defined steps\ref{example_measurement_analysis_pipeline.png}
+as \passthrough{\lstinline!yaml!} syntax.
+
+\begin{lstlisting}[caption={Example User Defined Processing Pipeline}, label=lst:mrpuddp_example_yaml]
 stage import_readings:
@@
 
+\begin{itemize}
+\tightlist
+\item
+  blöcke erleutern insbesondere stage
+\item
+  wie calltree gebildet
+\end{itemize}
+
 \hypertarget{tests}{%
@@
 errors and vulnerabilities before software is published as a new
-version. This significantly improves the reliability of library
-applications. Tests also ensures consistent and reliable performance,
-which is particularly important when libraries are used by different
-users and for different usecases.
+version. This significantly improves the reliability of
+\gls{mrp}-library applications. Tests also ensures consistent and
+reliable performance, which is particularly important when libraries are
+used by different users and for different usecases.
 
@@
 
-During the development of the library, test cases were also created for
-all important functionalities and use cases. The test framework
-\passthrough{\lstinline!PyTest!}\cite{PyTest} was used for this
-purpose, as it offers direct integration in most \gls{ide}s (see
+During the development of the \gls{mrp}-library, test cases were also
+created for all important functionalities and use cases. The test
+framework \passthrough{\lstinline!PyTest!}\cite{PyTest} was used for
+this purpose, as it offers direct integration in most \gls{ide}s (see
 \ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
@@
 
-One problem, however, is the parts of the library that require direct
-access to external hardware. These are, for example, the
+One problem, however, is the parts of the \gls{mrp}-library that require
+direct access to external hardware. These are, for example, the
 \passthrough{\lstinline!MRPHal!} and
@@
 One important point that improves usability for users is the simple
-installation of the library. As it was created in the Python programming
-language, there are several public package directories where users can
-provide their software modules. Here,
+installation of the \gls{mrp}-library. As it was created in the Python
+programming language, there are several public package directories where
+users can provide their software modules. Here,
 \passthrough{\lstinline!PyPi!}\cite{PyPI}\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}\cite{MagneticReadoutProcessingPyPI}
@@
 
-\begin{lstlisting}[language=bash, caption={Bash commands to install the MagneticReadoutProcessing library using pip}, label=lst:setup_lib_with_pip]
+\begin{lstlisting}[language=bash, caption={Bash commands to install the MagneticReadoutProcessing (+mrp)-library using pip}, label=lst:setup_lib_with_pip]
 # https://pypi.org/project/MagneticReadoutProcessing/
@@
 
-To make the library compatible with the package directory, Python
-provides separate installation routines that build a package in an
-isolated environment and then provide an installation
+To make the \gls{mrp}-library compatible with the package directory,
+Python provides separate installation routines that build a package in
+an isolated environment and then provide an installation
 \passthrough{\lstinline!wheel!} archive. This can then be uploaded to
@@
 
-Since the library requires additional dependencies
+Since the \gls{mrp}-library requires additional dependencies
 (e.g.~\passthrough{\lstinline!numpy!},
@@
 already installed on the target system, these must be installed prior to
-the actual installation. These can be specified in the library
+the actual installation. These can be specified in the \gls{mrp}-library
 installation configuration
@@
 In addition, these commands are available globally in the system without
-the terminal shell being located in the library folder.
+the terminal shell being located in the \gls{mrp}-library folder.
 
@@
 with the package management by \passthrough{\lstinline!PyPi!} services,
-which provide Python library documentation online.
+which provide Python \gls{mrp}-library documentation online.
 

### 2023-12-18 documentation/thesis/thesis_document.tex
more thesis

@@
 
+After it is very easy for users to carry out measurements using the
+\gls{cli}, the next logical step is to analyse the recorded data. This
+can involve one or several hundred data records. Again, the procedure
+for the user is to write their own evaluation scripts using the
+\gls{mrp}-library. This is particularly useful for complex analyses or
+custom algorithms, but not necessarily for simple standard tasks such as
+bias compensation or graphical plot outputs.
+
 \begin{figure}
@@
 
-After it is very easy for users to carry out measurements using the
-\gls{cli}, the next logical step is to analyse the recorded data. This
-can involve one or several hundred data records. Again, the procedure
-for the user is to write their own evaluation scripts using the
-\gls{mrp}-library. This is particularly useful for complex analyses or
-custom algorithms, but not necessarily for simple standard tasks such as
-bias compensation or graphical plot outputs. For this purpose, a further
-\gls{cli} application was created, which enables the user to create and
-execute complex evaluation pipelines for measurement data without
-programming. The example\ref{example_measurement_analysis_pipeline.png}
-shows a typical measurement data analysis pipeline, which consists of
-the following steps:
+For this purpose, a further \gls{cli} application was created, which
+enables the user to create and execute complex evaluation pipelines for
+measurement data without programming. The
+example\ref{example_measurement_analysis_pipeline.png} shows a typical
+measurement data analysis pipeline, which consists of the following
+steps:
 
@@
   parameters:
-    bias_readings: stage import_bias_reading
+    bias_readings: stage import_bias_reading # USE RESULT FROM FUNCTION import_bias_reading
     readings_to_calibrate: stage import_readings
@@
   parameters:
-    readings_to_calibrate: stage import_readings
+    readings_to_calibrate: stage import_readings # USE RESULT FROM FUNCTION import_readings
 
@@
 
+Each pipeline step is divided into \passthrough{\lstinline!stages!},
+which contain a name, the function to be executed and its parameters.
+The various steps are then linked by using the
+\passthrough{\lstinline!stage <name>!} as the input parameter of the
+next function to be executed (see comments in
+\ref{lst:mrpuddp_example_yaml}). It is therefore also possible to use
+the results of one function in several others without them directly
+following each other. The disadvantages of this system are as the
+following:
+
 \begin{itemize}
@@
 \item
-  blöcke erleutern insbesondere stage
+  No loops can be created
 \item
-  wie calltree gebildet
+  Complex determination of the execution sequence of the steps
+\end{itemize}
+
+To determine the order of the pipeline steps, the parser script created
+converts them into one problem of the graph theories. Each step
+represents a node in the graph and the steps referred to by the input
+parameter form the edges.
+
+After several simplification steps, determination of possible start
+steps and repeated traversal, the final execution sequence can be
+determined in the form of a call
+tree\ref{Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}.
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}
+\caption{Result step execution tree from user defined processing
+pipeline example
+\label{Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}}
+\end{figure}
+
+The individual steps are then executed along the graph. The intermediate
+results and the final result are saved for later use.
+
+\begin{itemize}
+\tightlist
+\item
+  vorteile erleutern kurz
 \end{itemize}

### 2023-12-18 documentation/thesis/thesis_document.tex
more thesis

@@
 
-\hypertarget{user-interface}{%
-\subsection{User-Interface}\label{user-interface}}
+\hypertarget{communication-interface}{%
+\subsection{Communication interface}\label{communication-interface}}
 
@@
 \end{figure}
+
+Each sensor that has been loaded with the firmware, registeres on to the
+host \gls{pc} as a serial interface. There are several ways for the user
+to interact with this:
+
+\begin{itemize}
+\tightlist
+\item
+  Use with \gls{mrp}-library (see \ref{software-readout-framework})
+\item
+  Stand-alone mode via sending commands using built-in \gls{cli}
+\end{itemize}
+
+The \gls{cli} mode is a simple text-based interface with which it is
+possible to read out current measured values, obtain debug information
+and set operating parameters. This allows you to quickly determine
+whether the hardware is working properly after installation. The
+\gls{cli} behaves like terminal programmes, displaying a detailed
+command reference\ref{Sensors_(+cli).png} to the user after connecting.
+The current measured value can be output using the
+\passthrough{\lstinline!readout!}
+command\ref{Query_sensors_b_value_using_(+cli).png}.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  einfache bedienung durch nutzer auch ohne weitere software
-\item
-  configuration
-\item
-  debugging
-\end{itemize}
+The other option is to use the \gls{mrp}-library. The serial interface
+is also used here. However, after a connection attempt by the
+\passthrough{\lstinline!MRPHal!} module\ref{hal} of the
+\gls{mrp}-library, the system switches to binary mode, which is
+initiated using the \passthrough{\lstinline!sbm!} command. However, the
+same commands are available as for \gls{cli}-based communication.
 
@@
 the results of one function in several others without them directly
-following each other. The disadvantages of this system are as the
+following each other. The disadvantages of this system are the
 following:
@@
 \item
-  No loops can be created
+  No circular parameter dependencies
 \item
@@
 
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}
+\caption{Result step execution tree from user defined processing
+pipeline example
+\label{Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
+\caption{pipeline output files after running example pipeline on a set
+of readings
+\label{pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}}
+\end{figure}
+
 After several simplification steps, determination of possible start
@@
 tree\ref{Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}.
-
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}
-\caption{Result step execution tree from user defined processing
-pipeline example
-\label{Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}}
-\end{figure}
-
 The individual steps are then executed along the graph. The intermediate
-results and the final result are saved for later use.
-
-\begin{itemize}
-\tightlist
-\item
-  vorteile erleutern kurz
-\end{itemize}
+results and the final
+results\ref{pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
+are saved for optional later use.
 
@@
 \begin{lstlisting}[language=Python, caption={Example pytest class for testing MRPReading module functions}, label=lst:pytest_example_code]
-# $ cat test_mrpreading.py
 class TestMPRReading(unittest.TestCase):
@@
       self.assertTrue(matrix.shape != (n_theta,))
-      self.assertTrue(len(matrix.shape) <= n_phi))
+      self.assertTrue(len(matrix.shape) <= n_phi)
 
   def test_export_reading(self) -> None:
-      reading: MRPReading = self.test_reading_init()
+      reading: MRPReading = MRPSimulation.generate_reading()
       self.assertIsNotNone(reading)
@@
   def test_import_reading(self):
-      # CREATE EMPTY READING
+      # CREATE EMPTY READING AND LOAD FROM FILE
       reading_imported:MRPReading = MRPReading.MRPReading(None)
-      # LOAD READING FROM FILE
       reading_imported.load_from_file(self.test_file)
-      # CHECK IF ENTRIES ARE POPULATED
-      self.assertIsNotNone(reading_imported.additional_data)
-      self.assertIsNotNone(reading_imported.data)
+      # COMPARE
+      self.assertIsNotNone(reading_imported.compare(MRPSimulation.generate_reading()))
 \end{lstlisting}

### 2023-12-18 src/MagneticReadoutProcessing/MRP/MRPDataVisualization.py

@@ -40,7 +40,7 @@ class MRPDataVisualization:
 
         # TABLE
         clust_data = []#np.random.random((len(_readings), 5))
-        collabel = ("Reading [id:sensor_id]", "Mean [{}}]", "STD Deviation [{}}]", "Variance [{}}]", "Count Data-Points".format(_unit, _unit, _unit))
+        collabel = ("Reading [id:sensor_id]", "Mean [{}]".format(_unit), "STD Deviation [{}]".format(_unit), "Variance [{}]".format(_unit), "Count Data-Points")
         labels = []
 
         for idx, reading in enumerate(_readings):

### 2023-12-18 documentation/thesis/thesis_document.tex
more thesis

@@
 
+\begin{lstlisting}[language={C++}, caption={CustomSensor-Class for adding new sensor hardware support}, label=lst:CustomSensorClass]
+#ifndef __CustomSensor_h__
+#define __CustomSensor_h__
+// register your custom sensor in implemented_sensors.h also
+class CustomSensor: public baseSensor {}
+{
+public:
+    CustomSensor();
+    ~CustomSensor();
+    // implement depending sensor communication interface
+    bool begin(TwoWire& _wire_instance); // I2C
+    bool begin(HardwareSerial& _serial_instance); // UART
+    bool begin(Pin& _pin_instance); // ANALOG like analog input / DIGITAL PIN like onewire
+    // FUNCTIONS USED BY READOUT LOGIC
+    bool is_valid() override;
+    String capabilities() override;
+    String get_sensor_name() override;
+    bool query_sensor() override;
+    sensor_result get_result() override;        
+};
+#endif
+\end{lstlisting}
+
 \hypertarget{communication-interface}{%
@@
 
-\emph{anbei werden drei erschienee sensoren für unterschiedliche
-anwedungfälle } tablle statisch dynamisch
+Two functional sensor
+platforms\ref{Build_sensors_with_different_capabilities.csv} were built
+in order to create a solid test platform for later tests and for the
+development of the \gls{mrp} library with the previously developed
+sensor concepts.
+
+\begin{longtable}[]{@{}llll@{}}
+\caption{Build sensors with different capabilities
+\label{Build_sensors_with_different_capabilities.csv}}\tabularnewline
+\toprule
+& 1D (Chapter \ref{d-single-sensor}) & 1D: dual sensor & 3D: fullsphere
+(Chapter \ref{d-fullsphere})\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+& 1D (Chapter \ref{d-single-sensor}) & 1D: dual sensor & 3D: fullsphere
+(Chapter \ref{d-fullsphere})\tabularnewline
+\midrule
+\endhead
+Maximal magnet size & Cubic 30x30x30 & Cubic 30x30x30 & Cubic
+20x20x20\tabularnewline
+Sensor type & MMC5603NJ & TLV493D & TLV493D\tabularnewline
+Sensor count & 1 & 2 & 1\tabularnewline
+Scanmode & static (1 point) & static (2 points) & dynamic
+(fullsphere)\tabularnewline
+\bottomrule
+\end{longtable}
+
+These cover all the required functions described in the
+Usecases\ref{usecases}. The biggest distinguishing feature, apart from
+the sensor used, is the \passthrough{\lstinline!scan mode!}. In this
+context, this describes whether the sensor can measure a
+\passthrough{\lstinline!static!} fixed point on the magnet or if the
+sensor can move \passthrough{\lstinline!dynamically!} around the magnet
+using a controllable manipulator.
+
+In the following, the hardware structure of a
+\passthrough{\lstinline!static!} and \passthrough{\lstinline!dynamic!}
+sensor is described. For the \passthrough{\lstinline!static!} sensor,
+only the \passthrough{\lstinline!1D!} variant is shown, as this does not
+differ significantly from the structure of the
+\passthrough{\lstinline!1D: dual sensor!}, except it uses two
+\passthrough{\lstinline!TLV493D!} sensors, mounted above and on top of
+the magnet.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  einfachster aufbau rp pico + sensor
-\end{itemize}
-
-\hypertarget{d-dual-sensor}{%
-\subsection{1D: Dual Sensor}\label{d-dual-sensor}}
-
-\begin{itemize}
-\tightlist
-\item
-  gleicher abstand zwei gleicher sensoren
-\item
-  schnelle erkennung der plarisationsebene ggf offset vom mittelpunkt
-  dieser
-\end{itemize}
-
-\hypertarget{full-sphere}{%
-\subsection{Full-Sphere}\label{full-sphere}}
+The \passthrough{\lstinline!1D!}
+sensor\ref{1D_sensor_contrsuction_with_universal_magnet_mount.png} is
+the simplest possible sensor that is compatible with the
+\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} platform
+and also with the \gls{mrp}-library\ref{software-readout-framework}.
+
+The electrical level here is based on a
+\passthrough{\lstinline!Raspberry-Pi Pico!} together with the
+\passthrough{\lstinline!MMC5603NJ!} magnetic sensor. The mechanical
+setup consists of four 3D-printed components, which are fixed together
+with nylon screws to minimise possible influences on the measurement.
+
+Since the \passthrough{\lstinline!MMC5603NJ!} only has very limited
+measuring range, even small neodymium magnets already saturate this
+range, it is possible to use 3D-printed spacers above the sensor.
+
+The standard magnet holder can be adapted for different magnet shapes
+and can be placed on the spacer without play in order to be able to
+perform a repeatable measurement without introducing measurement
+irregularities by mechanically changing the magnet.
+
+\hypertarget{d-fullsphere}{%
+\subsection{3D: Fullsphere}\label{d-fullsphere}}
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  komplexester aufbau sensor + mechanik
-\item
-  polar mechanisches system
-\item
-  full sphere sensor
-\end{itemize}
-
-\hypertarget{integration-of-an-professional-teslameter}{%
-\subsection{Integration of an Professional
-Teslameter}\label{integration-of-an-professional-teslameter}}
-
-\begin{itemize}
-\tightlist
-\item
-  einfach anbindung professioneller teslameter
-\item
-  Voltkraft
-\end{itemize}
+The
+\passthrough{\lstinline!3D Fullsphere!}\ref{Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
+sensor offers the possibility to create a 3D
+map\ref{3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}
+of the magnets. The magnet sensor is mounted on a movable arm, which can
+move 180 degrees around the magnet on one axis. In order to be able to
+map the full sphere, the magnet is mounted on a turntable. This permits
+the manipulator to move a polar coordinate system.
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}
+\caption{3D plot of an N45 12x12x12 magnet using the 3D fullsphere
+sensor
+\label{3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}}
+\end{figure}
+
+As the magnets in the motors, as with the screws used in the 1D sensor,
+can influence the measurements of the magnetic field sensor, the
+distance between these components and the sensor or magnets was
+increased. The turntable and its drive motor are connected to each other
+via a belt.
+
+On the electrical side, it also consists of a
+\passthrough{\lstinline!SKR Pico!} stepper motor controller, together
+with the \passthrough{\lstinline!TLV493D!} magnetic field sensor. This
+was chosen because of its larger measuring range and can therefore be
+used more universally without having to change the sensor of the arm.
+
+\hypertarget{integration-of-an-industry-teslameter}{%
+\subsection{Integration of an industry
+Teslameter}\label{integration-of-an-industry-teslameter}}
+
+As the sensors shown so far relate exclusively to self-built, low-cost
+hardware, the following section shows how existing hardware can be
+integrated into the system. This is shown here using a
+temperature-compensated \passthrough{\lstinline!Voltcraft GM-70!}
+telsameter\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png},
+which has a measuring range of \passthrough{\lstinline!0-3T!} with a
+resolution of 0.1mT. This offers an \passthrough{\lstinline!RS232!}
+interface with a documented protocol for connection to a \gls{pc}. This
+connectivity makes it possible to make the device compatible with the
+\gls{mrp} library using interface software \cite{VoltcraftGM70Rest}
+executable on the host \gls{pc}. However, it does not offer the range of
+functions that the
+\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} offers.
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png}
+\caption{Voltcraft GM70 teslameter with custom \gls{pc} interface board
+\label{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png}}
+\end{figure}
+
+Another option is a custom interface board between the meter and the PC.
+This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
+offer an \passthrough{\lstinline!RS232!} interface. As with the other
+sensors, this interface consists of your
+\passthrough{\lstinline!RaspberryPi Pico!} with an additional level
+shifter. The Teslameter is connected to the microcontroller using two
+free \gls{gpio}s in \gls{uart} mode. The
+\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} was
+adapted using a separate build configuration and the protocol of the
+measuring device was implemented.
+
+This software or hardware integration can be carried out on any other
+measuring device with a suitable communication interface and a known
+protocol thanks to the modular design.
 
@@
 \passthrough{\lstinline!Proxy!}\ref{MRPlib_Proxy_Module.png} module has
-been developed. This can be a single board computer (e.g.~a Raspberry
-Pi). The small footprint and low power consumption make it a good
-choice. It can also be used in a temperature chamber. The approach of
-implementing this via a \gls{rest} interface also offers the advantage
-that several measurements or experiments can be recorded at the same
-time with the sensors.
+been developed. This can be a \gls{sbc} (e.g.~a Raspberry Pi). The small
+footprint and low power consumption make it a good choice. It can also
+be used in a temperature chamber. The approach of implementing this via
+a \gls{rest} interface also offers the advantage that several
+measurements or experiments can be recorded at the same time with the
+sensors.
 
@@
 If time-critical synchronisation is required, \gls{ptp} and \gls{pps}
-output functionality can be used on many single-board computers, such as
-the RaspberryPi Compute Module.
+output functionality can be used on many \gls{sbc}, such as the
+\passthrough{\lstinline!Raspberry-Pi Compute Module 4!}.
 

### 2023-12-18 src/UnifiedMagBoardFirmware/include/baseSensor.h

@@ -32,8 +32,6 @@ public:
     bool is_valid();
     String capabilities();
     String get_sensor_name();
-
-    
     bool query_sensor();
     sensor_result get_result();
 

### 2023-12-19 documentation/thesis/thesis_document.tex
more thesis
added drawio sources

@@
   multiplexer for i2c sensors alredy implemented
+\item
+  imput / output for sync
 \end{itemize}
@@
 
-\begin{itemize}
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Unified_sensor_firmware_simplified_program_strucutre.png}
+\caption{Unified sensor firmware simplified program strucutre
+\label{Unified_sensor_firmware_simplified_program_strucutre.png}}
+\end{figure}
+
+\begin{itemize}
+\item
+  mbed
 \item
@@
 \end{itemize}
+
+\ref{Unified_sensor_firmware_simplified_program_strucutre.png}
+
+\ref{lst:CustomSensorClass}
 
@@
     bool begin(HardwareSerial& _serial_instance); // UART
-    bool begin(Pin& _pin_instance); // ANALOG like analog input / DIGITAL PIN like onewire
+    bool begin(Pin& _pin_instance); // ANALOG or DIGITAL PIN like onewire
     // FUNCTIONS USED BY READOUT LOGIC
@@
 
+\hypertarget{sensor-syncronsisation-interface}{%
+\section{Sensor syncronsisation
+interface}\label{sensor-syncronsisation-interface}}
+
 \hypertarget{communication-interface}{%
@@
 \item
-  Use with \gls{mrp}-library (see \ref{software-readout-framework})
+  Use with \gls{mrp}-library\ref{software-readout-framework}
 \item
@@
 
-\hypertarget{sensor-syncronsisation}{%
-\section{Sensor Syncronsisation}\label{sensor-syncronsisation}}
-
 \hypertarget{example-sensors}{%
@@
 \toprule
-& 1D (Chapter \ref{d-single-sensor}) & 1D: dual sensor & 3D: fullsphere
-(Chapter \ref{d-fullsphere})\tabularnewline
+& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
+Fullsphere\ref{d-fullsphere}\tabularnewline
 \midrule
@@
 resolution of 0.1mT. This offers an \passthrough{\lstinline!RS232!}
-interface with a documented protocol for connection to a \gls{pc}. This
-connectivity makes it possible to make the device compatible with the
-\gls{mrp} library using interface software \cite{VoltcraftGM70Rest}
-executable on the host \gls{pc}. However, it does not offer the range of
-functions that the
+interface with a documented
+protocol\ref{Voltcraft_GM70_serial_protocol.csv} for connection to a
+\gls{pc}. This connectivity makes it possible to make the device
+compatible with the \gls{mrp} library using interface software
+\cite{VoltcraftGM70Rest} executable on the host \gls{pc}. However,
+it does not offer the range of functions that the
 \passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} offers.
@@
 measuring device was implemented.
+
+\begin{longtable}[]{@{}lll@{}}
+\caption{Voltcraft GM70 serial protocol
+\label{Voltcraft_GM70_serial_protocol.csv}}\tabularnewline
+\toprule
+BYTE-INDEX & REPRESENTATION & VALUE\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+BYTE-INDEX & REPRESENTATION & VALUE\tabularnewline
+\midrule
+\endhead
+0 & PREAMBLE & 0x2\tabularnewline
+1 & & 0x1\tabularnewline
+2 & & 0x4\tabularnewline
+3 & UNIT & `B' =\textgreater{} Gauss `E' =\textgreater{}
+mT\tabularnewline
+5 & POLARITY & `1' =\textgreater{} \emph{0.1 `2' =\textgreater{}
+}0.01\tabularnewline
+6 & value MSB & 0x-0xFF\tabularnewline
+13 & value LSB & 0x-0xFF\tabularnewline
+14 & STOP & 0x3\tabularnewline
+\bottomrule
+\end{longtable}
 

### 2023-12-19 documentation/thesis/thesis_document.tex
more thesis

@@
 
+Microcontroller firmware is software that is executed on a
+microcontroller in embedded systems. It controls the hardware and
+enables the execution of predefined functions. The firmware is used to
+process input data, control output devices and fulfil specific tasks
+according to the program code. It handles communication with sensors,
+actuators and other peripheral devices, processing data and making
+decisions. Firmware is critical to the functioning of devices.
+
 \begin{figure}
@@
 
-\begin{itemize}
-\item
-  mbed
-\item
-  automatic sensor detation ablaufdiagramm erst nach i2c geräte scannen
-  dann analog versuchen
-\item
-  serial cli support for manual mode
-\item
-  sync impulse =\textgreater{} 1 mastersensor als taktqelle
-\item
-  interene mittelung und speichern der werte im buffer ringubber welcher
-  bei jedem sync impuls neu belegt wird
-\item
-  \begin{enumerate}
-  \def\labelenumi{\arabic{enumi}.}
-  \setcounter{enumi}{1}
-  \tightlist
-  \item
-    core übernimmt mittelung und auswetung
-  \end{enumerate}
-\item
-  was durch den user implementiert werden muss klasse
-\end{itemize}
-
-\ref{Unified_sensor_firmware_simplified_program_strucutre.png}
-
-\ref{lst:CustomSensorClass}
+The firmware is responsible for detecting the possible connected
+sensors\ref{Implemented_digital_halleffect_sensors.csv} and reading them
+out. This measured data can be forwarded to a host \gls{pc} via a user
+interface and can then be further processed there. An important
+component is that as many common sensors as possible can be easily
+connected without having to adapt the firmware. This modularity was
+implemented using \passthrough{\lstinline!abstract!} class design. These
+are initiated according to the sensors found at startup. If new hardware
+is to be integrated, only the required
+functions\ref{lst:CustomSensorClass} need to be implemented.
 
@@
 
+The flow
+chart\ref{Unified_sensor_firmware_simplified_program_strucutre.png}
+shows the start process and the subsequent main loop for processing the
+user commands and sensor results. When the microcontroller is started,
+the software checks whether known sensors are connected to \gls{i2c} or
+\gls{uart} interfaces. If any are found (using a dedicated \gls{lut}
+with sensor address information), the appropriate class instances are
+created and these can later be used to read out measurement results.
+
+Next, the subsystem for multi-sensor
+synchronisation\ref{sensor-syncronsisation-interface} is set up. The
+last step in the setup is to set up communication with the host or
+connected \gls{pc}. All microcontroller platforms used here have a
+\gls{usb} slave port. The used usb descriptor is
+\passthrough{\lstinline!Serial over (+usb)!}- ((+usb)\gls{cdc}). This is
+used to emulate a virtual RS232 communication port using a USB port on a
+\gls{pc} and usually no additional driver is needed on modern systems.
+
+Now that the setup process is complete, the system switches to an
+infinite loop, which processes several possible actions. One task is, to
+react to user commands which can be sent to the system by the user via
+the integrated \gls{cli}. All sensors are read out via a timer interval
+set in the setup procedure and their values are stored in a ringbuffer.
+Ring buffers, offer efficient data management in limited memory. Its
+cyclic structure enables continuous overwriting of older data, saves
+memory space and facilitates seamless processing of real-time data. Ring
+buffers are well suited for applications with variable data rates and
+minimise the need for complex memory management. The buffer can be read
+out by command and the result of the measurement is sent to the host.
+
 \hypertarget{sensor-syncronsisation-interface}{%
-\section{Sensor syncronsisation
+\subsection{Sensor syncronsisation
 interface}\label{sensor-syncronsisation-interface}}
+
+\begin{itemize}
+\tightlist
+\item
+  sync impulse =\textgreater{} 1 mastersensor als taktqelle
+\item
+  interene mittelung und speichern der werte im buffer ringubber welcher
+  bei jedem sync impuls neu belegt wird
+\item
+  ringbuffer
+\end{itemize}
+
+\%\%Unified\_sensor\_firmware\_multi\_sensor\_synchronisation\_procedure.drawio.png\%\%
+
+\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.drawio.png}
 
@@
 \hypertarget{example-sensors}{%
-\section{Example Sensors}\label{example-sensors}}
+\section{Example sensors}\label{example-sensors}}
 
@@
 \subsection{Integration of an industry
-Teslameter}\label{integration-of-an-industry-teslameter}}
+teslameter}\label{integration-of-an-industry-teslameter}}
 
@@
 
-\hypertarget{multi-sensor-setup}{%
-\subsection{Multi-Sensor setup}\label{multi-sensor-setup}}
+\hypertarget{multible-sensor-setup}{%
+\subsection{Multible sensor setup}\label{multible-sensor-setup}}
 
@@
 other via their sync input using short cables. One sensor acts as the
-central clock (see chapter \ref{sensor-syncronsisation}). this no longer
-works for long distances and the syncronisation must be made via the
-network connection.
+central clock as described in\ref{sensor-syncronsisationiinterface}.
+this no longer works for long distances and the syncronisation must be
+made via the network connection.
 
@@
 \begin{itemize}
-\tightlist
 \item
@@
   commando templating
+\item
+  einzelne sensor capabilites werden gemerged
+\item
+  ids werden aufsuimmiert
+\item
+  spätere sensor identifikation geschieht über die jeweilige sensor id,
+  welche über diesen index abgefragt werden kann
+\item
+  tablle mit mergin algorithmus
 \end{itemize}
@@
 \gls{cli}\ref{example_measurement_analysis_pipeline.png} was implemented
-around this \gls{mrp}-library, which is then also supplied as a fixed
-component. This \gls{cli} implements the following functionalities:
+around this \gls{mrp}-library. The (+mrp)-library-\gls{cli} implements
+the following functionalities:
 
@@
 measured values. These can then be read in again with the
-\gls{mrp}-library and processed further. The bash
-code\ref{lst:mrpcli_config_run} shows this procedure in detail.
+\gls{mrp}-library and processed further. The following bash
+code\ref{lst:mrpcli_config_run} shows the setup procedure in detail:
 

### 2023-12-21 documentation/thesis/thesis_document.tex
more thesis

@@
 // register your custom sensor in implemented_sensors.h also
-class CustomSensor: public baseSensor {}
+class CustomSensor: public baseSensor
 {
@@
 out by command and the result of the measurement is sent to the host.
+Each sensor measurement result is transmitted from the buffer to the
+host together with a time stamp and a sequential number. This ensures
+that in a multi-sensor setup with several sensors. The measurements are
+synchronized\ref{sensor-syncronsisation-interface} in time and are not
+out of sequence or drift.
 

### 2023-12-24 documentation/thesis/thesis_document.tex
more thesis

@@
 
-\hypertarget{sensor-syncronsisation-interface}{%
-\subsection{Sensor syncronsisation
-interface}\label{sensor-syncronsisation-interface}}
-
-\begin{itemize}
-\tightlist
-\item
-  sync impulse =\textgreater{} 1 mastersensor als taktqelle
-\item
-  interene mittelung und speichern der werte im buffer ringubber welcher
-  bei jedem sync impuls neu belegt wird
-\item
-  ringbuffer
-\end{itemize}
-
-\%\%Unified\_sensor\_firmware\_multi\_sensor\_synchronisation\_procedure.drawio.png\%\%
-
-\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.drawio.png}
-
 \hypertarget{communication-interface}{%
@@
 same commands are available as for \gls{cli}-based communication.
+
+\hypertarget{sensor-syncronsisation-interface}{%
+\subsection{Sensor syncronsisation
+interface}\label{sensor-syncronsisation-interface}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Multi_sensor_synchronisation_wiring_example.png}
+\caption{Multi sensor synchronisation wiring example
+\label{Multi_sensor_synchronisation_wiring_example.png}}
+\end{figure}
+
+One problem with the use of several sensors on one readout host \gls{pc}
+is that the measurements may drift over time. On the one hand, \gls{usb}
+latencies can occur. This can occur due to various factors, including
+device drivers, data transfer speed and system resources. High-quality
+\gls{usb} devices and modern drivers often minimise latencies.
+Nevertheless, complex data processing tasks and overloaded \gls{usb}
+ports can lead to delays.
+
+The other issue is sending the trigger signal from the readout
+software\ref{software-readout-framework}. Here too, unpredictable
+latencies can occur, depending on which other tasks are also executed on
+this port.
+
+In order to enable the most stable possible synchronisation between
+several sensors, an option has already been created to establish an
+electrical connection between sensors. This is used together with the
+firmware to synchronise the readout intervals. The
+schematic\ref{Multi_sensor_synchronisation_wiring_example.png} shows how
+several sensors must be wired together in order to implement this form
+of synchronisation.
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}
+\caption{Unified sensor firmware multi sensor synchronisation procedure
+\label{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}}
+\end{figure}
+
+Once the hardware has been prepared, the task of the firmware of the
+various sensors is to find a common synchronisation clock. To do this,
+the \passthrough{\lstinline!register irq on sync pin!} is overwritten.
+To set one \passthrough{\lstinline!primary!} and several
+\passthrough{\lstinline!secondary!} sensors, each sensor waits for an
+intial pulse on the
+sync-pin\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
+Each sensor starts a random timer beforehand, which sends a pulse on the
+sync line. All others receive this and switch to
+\passthrough{\lstinline!secondary!} mode and synchronise the
+measurements based on each sync pulse received. Since the presumed
+\passthrough{\lstinline!primary!} sensor cannot register its own sync
+pulse (because the pin is switched to output), there is a timeout
+\passthrough{\lstinline!got pulse within 1000ms!} and this becomes the
+\passthrough{\lstinline!primary!} sensor. This means that in a chain of
+sensors there is exactly one \passthrough{\lstinline!primary!} and many
+\passthrough{\lstinline!secondary!} sensors. In single-sensor operation,
+this automatically jumps to \passthrough{\lstinline!primary!} sensor
+operation through the
+\passthrough{\lstinline!got impulse within 1000ms!} query. The
+synchronisation status can be queried via the user
+interface\ref{communication-interface} using the
+\passthrough{\lstinline!opmode!}\ref{Query_opmode_using_(+cli).png}
+command. An important aspect of the implementation here was that there
+is no numbering or sequence of the individual sensors. This means that
+for the subsequent readout of the measurements, it is only important
+that they are taken at the same interval across all sensors. The sensor
+differentiation takes place later in the readout
+software\ref{software-readout-framework} by using the sensor
+identification number.
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Query_opmode_using_(+cli).png}
+\caption{Query opmode using \gls{cli}
+\label{Query_opmode_using_(+cli).png}}
+\end{figure}
 

### 2023-12-24 documentation/thesis/thesis_document.tex
.

@@
 
-\begin{itemize}
-\tightlist
-\item
-  usb, ethernet
-\item
-  pps input output
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_1D_sensor_schematic_and_circuit_board.png}
+\caption{1D sensor schematic and circuit board
+\label{1D_sensor_schematic_and_circuit_board.png}}
+\end{figure}
+
+\ref{1D_sensor_schematic_and_circuit_board.png}
+
+\begin{itemize}
+\tightlist
+\item
+  usb
 \item
@@
 These cover all the required functions described in the
-Usecases\ref{usecases}. The biggest distinguishing feature, apart from
-the sensor used, is the \passthrough{\lstinline!scan mode!}. In this
+Usecases\ref{usecases}. The most important difference, apart from the
+sensor used, is the \passthrough{\lstinline!scan mode!}. In this
 context, this describes whether the sensor can measure a
@@
 \centering
-\includegraphics{./generated_images/border_1D_sensor_contrsuction_with_universal_magnet_mount.png}
-\caption{1D sensor contrsuction with universal magnet mount
-\label{1D_sensor_contrsuction_with_universal_magnet_mount.png}}
+\includegraphics{./generated_images/border_1D_sensor_construction_with_universal_magnet_mount.png}
+\caption{1D sensor construction with universal magnet mount
+\label{1D_sensor_construction_with_universal_magnet_mount.png}}
 \end{figure}
@@
 The \passthrough{\lstinline!1D!}
-sensor\ref{1D_sensor_contrsuction_with_universal_magnet_mount.png} is
+sensor\ref{1D_sensor_construction_with_universal_magnet_mount.png} is
 the simplest possible sensor that is compatible with the

### 2023-12-24 documentation/sciencemeeting/dist_html/main.2.37a89ccc187897bf765b.bundle.js

@@ -1,1 +1,0 @@
-(window.webpackJsonp=window.webpackJsonp||[]).push([[2],{12:function(n,t,e){e(13),n.exports=e(31)},28:function(n,t,e){var r={"./0-title.md":29,"./1-content.md":30};function o(n){var t=u(n);return e(t)}function u(n){if(!e.o(r,n)){var t=new Error("Cannot find module '"+n+"'");throw t.code="MODULE_NOT_FOUND",t}return r[n]}o.keys=function(){return Object.keys(r)},o.resolve=u,n.exports=o,o.id=28},29:function(n,t,e){"use strict";e.r(t),e.d(t,"slides",(function(){return l})),e.d(t,"fusumaProps",(function(){return s})),e.d(t,"default",(function(){return f}));var r=e(1),o=e.n(r),u=e(2),a=["components"];function c(){return(c=Object.assign?Object.assign.bind():function(n){for(var t=1;t<arguments.length;t++){var e=arguments[t];for(var r in e)Object.prototype.hasOwnProperty.call(e,r)&&(n[r]=e[r])}return n}).apply(this,arguments)}function i(n,t){if(null==n)return{};var e,r,o=function(n,t){if(null==n)return{};var e,r,o={},u=Object.keys(n);for(r=0;r<u.length;r++)e=u[r],t.indexOf(e)>=0||(o[e]=n[e]);return o}(n,t);if(Object.getOwnPropertySymbols){var u=Object.getOwnPropertySymbols(n);for(r=0;r<u.length;r++)e=u[r],t.indexOf(e)>=0||Object.prototype.propertyIsEnumerable.call(n,e)&&(o[e]=n[e])}return o}var l=[function(n){return Object(u.a)(o.a.Fragment,null,Object(u.a)("h1",null,"A short introduction into the MagneticReadoutProcessing ecosystem"))}],s=[{}],p={};function f(n){var t=n.components,e=i(n,a);return Object(u.a)("wrapper",c({},p,e,{components:t,mdxType:"MDXLayout"}),Object(u.a)("h1",null,"A short introduction into the MagneticReadoutProcessing ecosystem"))}f.isMDXComponent=!0},30:function(n,t,e){"use strict";e.r(t),e.d(t,"slides",(function(){return l})),e.d(t,"fusumaProps",(function(){return s})),e.d(t,"default",(function(){return f}));var r=e(1),o=e.n(r),u=e(2),a=["components
[…]

### 2023-12-24 documentation/sciencemeeting/dist_pdf/dist/presenter.view.3.6740b04b846b84ea7034.bundle.js

@@ -1,1 +1,0 @@
-(window.webpackJsonp=window.webpackJsonp||[]).push([[3],{162:function(t,e,r){var n=r(3),o=r(163);"string"==typeof(o=o.__esModule?o.default:o)&&(o=[[t.i,o,""]]);var i={insert:"head",singleton:!1},a=(n(o,i),o.locals?o.locals:{});t.exports=a},163:function(t,e,r){},183:function(t,e,r){"use strict";r.r(e);var n=r(1),o=r.n(n),i=r(4);function a(t){return(a="function"==typeof Symbol&&"symbol"==typeof Symbol.iterator?function(t){return typeof t}:function(t){return t&&"function"==typeof Symbol&&t.constructor===Symbol&&t!==Symbol.prototype?"symbol":typeof t})(t)}function u(t,e){for(var r=0;r<e.length;r++){var n=e[r];n.enumerable=n.enumerable||!1,n.configurable=!0,"value"in n&&(n.writable=!0),Object.defineProperty(t,(o=n.key,i=void 0,i=function(t,e){if("object"!==a(t)||null===t)return t;var r=t[Symbol.toPrimitive];if(void 0!==r){var n=r.call(t,e||"default");if("object"!==a(n))return n;throw new TypeError("@@toPrimitive must return a primitive value.")}return("string"===e?String:Number)(t)}(o,"string"),"symbol"===a(i)?i:String(i)),n)}var o,i}var c=function(){function t(){!function(t,e){if(!(t instanceof e))throw new TypeError("Cannot call a class as a function")}(this,t),this.apiType=navigator.presentation&&navigator.presentation.receiver?"presentation":"localStorage","presentation"===this.apiType&&this.setUp()}var e,r,n;return e=t,(r=[{key:"registerEvent",value:function(t,e){navigator.presentation.receiver.connectionList.then((function(r){r.connections.forEach((function(r){r.addEventListener(t,e)})),r.addEventListener("connectionavailable",(function(t){e(t.connection)}))}))}},{key:"setUp",value:function(){this.registerEvent("close",(function(t){console.log(t)}))}},{key:"onChangePage",value:function(t){"presentation"===this.apiType?this.registerEvent("message",(function(e){var r=JSON.parse(e.data).page;t(r)})):window.addEventListener("storage",(functio
[…]

### 2023-12-24 documentation/sciencemeeting/dist_pdf/dist/runtime.3e2fa6cf750654d58c79.bundle.js

@@ -1,1 +1,0 @@
-!function(e){function r(r){for(var n,o,s=r[0],u=r[1],d=r[2],f=r[3]||[],l=0,v=[];l<s.length;l++)o=s[l],Object.prototype.hasOwnProperty.call(a,o)&&a[o]&&v.push(a[o][0]),a[o]=0;for(n in u)Object.prototype.hasOwnProperty.call(u,n)&&(e[n]=u[n]);for(p&&p(r),c.push.apply(c,f);v.length;)v.shift()();return i.push.apply(i,d||[]),t()}function t(){for(var e,r=0;r<i.length;r++){for(var t=i[r],n=!0,o=1;o<t.length;o++){var d=t[o];0!==a[d]&&(n=!1)}n&&(i.splice(r--,1),e=u(u.s=t[0]))}return 0===i.length&&(c.forEach((function(e){if(void 0===a[e]){a[e]=null;var r=document.createElement("link");u.nc&&r.setAttribute("nonce",u.nc),r.rel="prefetch",r.as="script",r.href=s(e),document.head.appendChild(r)}})),c.length=0),e}var n={},o={4:0},a={4:0},i=[],c=[];function s(e){return u.p+""+({0:"vendors~Sidebar~presenter.host~presenter.view",1:"vendors~presenter.host~presenter.view",3:"presenter.view",6:"vendors~Mermaid",7:"vendors~Sidebar",8:"vendors~live",9:"vendors~presenter.host"}[e]||e)+"."+e+"."+{0:"27b21a38bcf442f654e6",1:"7ee3e38ac96ee028bcca",3:"6740b04b846b84ea7034",6:"6cd255889c4c329a8edf",7:"824de7816f8244f3b4ea",8:"4cee62df89dceafa9064",9:"dbaca795fbaa026812db"}[e]+".bundle.js"}function u(r){if(n[r])return n[r].exports;var t=n[r]={i:r,l:!1,exports:{}};return e[r].call(t.exports,t,t.exports,u),t.l=!0,t.exports}u.e=function(e){var r=[];o[e]?r.push(o[e]):0!==o[e]&&{1:1,3:1,8:1,9:1}[e]&&r.push(o[e]=new Promise((function(r,t){for(var n=({0:"vendors~Sidebar~presenter.host~presenter.view",1:"vendors~presenter.host~presenter.view",3:"presenter.view",6:"vendors~Mermaid",7:"vendors~Sideba
[…]

### 2023-12-24 documentation/sciencemeeting/dist_pdf/dist/vendors~live.8.4cee62df89dceafa9064.bundle.js

@@ -1,15 +1,0 @@
-(window.webpackJsonp=window.webpackJsonp||[]).push([[8],{181:function(t,e,r){"use strict";r.r(e),r.d(e,"CommentsList",(function(){return So}));var n=r(1),o=r.n(n);
-/*! *****************************************************************************
-Copyright (c) Microsoft Corporation.
-
-Permission to use, copy, modify, and/or distribute this software for any
-purpose with or without fee is hereby granted.
-
-THE SOFTWARE IS PROVIDED "AS IS" AND THE AUTHOR DISCLAIMS ALL WARRANTIES WITH
-REGARD TO THIS SOFTWARE INCLUDING ALL IMPLIED WARRANTIES OF MERCHANTABILITY
-AND FITNESS. IN NO EVENT SHALL THE AUTHOR BE LIABLE FOR ANY SPECIAL, DIRECT,
-INDIRECT, OR CONSEQUENTIAL DAMAGES OR ANY DAMAGES WHATSOEVER RESULTING FROM
-LOSS OF USE, DATA OR PROFITS, WHETHER IN AN ACTION OF CONTRACT, NEGLIGENCE OR
-OTHER TORTIOUS ACTION, ARISING OUT OF OR IN CONNECTION WITH THE USE OR
-PERFORMANCE OF THIS SOFTWARE.
[…]

### 2023-12-24 documentation/sciencemeeting/dist_pdf/vendors~Sidebar.7.824de7816f8244f3b4ea.bundle.js

@@ -1,7 +1,0 @@
-(window.webpackJsonp=window.webpackJsonp||[]).push([[7],{100:function(t,e,n){"use strict";Object.defineProperty(e,"__esModule",{value:!0});var r,a=n(35),i=(r=a)&&r.__esModule?r:{default:r};e.default=(0,i.default)({menuWrap:function(t){return{MozTransform:t?"":"translate3d(0, -100%, 0)",MsTransform:t?"":"translate3d(0, -100%, 0)",OTransform:t?"":"translate3d(0, -100%, 0)",WebkitTransform:t?"":"translate3d(0, -100%, 0)",transform:t?"":"translate3d(0, -100%, 0)",transition:"all 0.5s ease-in-out"}},pageWrap:function(t,e,n){return{MozTransform:t?"":n?"translate3d(-"+e+", 0, 0)":"translate3d("+e+", 0, 0)",MsTransform:t?"":n?"translate3d(-"+e+", 0, 0)":"translate3d("+e+", 0, 0)",OTransform:t?"":n?"translate3d(-"+e+", 0, 0)":"translate3d("+e+", 0, 0)",WebkitTransform:t?"":n?"translate3d(-"+e+", 0, 0)":"translate3d("+e+", 0, 0)",transform:t?"":n?"translate3d(-"+e+", 0, 0)":"translate3d("+e+", 0, 0)",transition:"all 0.5s"}},outerContainer:function(t){return{perspective:"1500px",perspectiveOrigin:"0% 50%",overflow:t?"":"hidden"}}}),t.exports=e.default},101:function(t,e,n){"use strict";Object.defineProperty(e,"__esModule",{value:!0});var r,a=n(35),i=(r=a)&&r.__esModule?r:{default:r};e.default=(0,i.default)({menuWrap:function(t,e,n){return{MozTransform:"translate3d(0, 0, 0)",MsTransform:"translate3d(0, 0, 0)",OTransform:"translate3d(0, 0, 0)",WebkitTransform:"translate3d(0, 0, 0)",transform:"translate3d(0, 0, 0)",zIndex:t?1e3:-1}},overlay:function(t,e,n){return{zIndex:1400,MozTransform:t?n?"translate3d(-"+e+", 0, 0)":"translate3d("+e+", 0, 0)":"translate3d(0, 0, 0)",MsTransform:t?n?"translate3d(-"+e+", 0, 0)":"translate3d("+e+
[…]

### 2023-12-24 documentation/sciencemeeting/dist_pdf/vendors~Sidebar~presenter.host~presenter.view.0.27b21a38bcf442f654e6.bundle.js

@@ -1,1 +1,0 @@
-(window.webpackJsonp=window.webpackJsonp||[]).push([[0],{42:function(t,c,n){"use strict";n.d(c,"k",(function(){return r})),n.d(c,"a",(function(){return v})),n.d(c,"b",(function(){return i})),n.d(c,"c",(function(){return e})),n.d(c,"d",(function(){return u})),n.d(c,"f",(function(){return h})),n.d(c,"e",(function(){return o})),n.d(c,"g",(function(){return d})),n.d(c,"i",(function(){return g})),n.d(c,"j",(function(){return l})),n.d(c,"l",(function(){return f})),n.d(c,"h",(function(){return s}));var a=n(0);function r(t){return Object(a.a)({tag:"svg",attr:{viewBox:"0 0 512 512"},child:[{tag:"path",attr:{d:"M459.37 151.716c.325 4.548.325 9.097.325 13.645 0 138.72-105.583 298.558-298.558 298.558-59.452 0-114.68-17.219-161.137-47.106 8.447.974 16.568 1.299 25.34 1.299 49.055 0 94.213-16.568 130.274-44.832-46.132-.975-84.792-31.188-98.112-72.772 6.498.974 12.995 1.624 19.818 1.624 9.421 0 18.843-1.3 27.614-3.573-48.081-9.747-84.143-51.98-84.143-102.985v-1.299c13.969 7.797 30.214 12.67 47.431 13.319-28.264-18.843-46.781-51.005-46.781-87.391 0-19.492 5.197-37.36 14.294-52.954 51.655 63.675 129.3 105.258 216.365 109.807-1.624-7.797-2.599-15.918-2.599-24.04 0-57.828 46.782-104.934 104.934-104.934 30.213 0 57.502 12.67 76.67 33.137 23.715-4.548 46.456-13.32 66.599-25.34-7.798 24.366-24.366 44.833-46.132 57.827 21.117-2.273 41.584-8.122 60.426-16.243-14.292 20.791-32.161 39.308-52.628 54.253z"}}]})(t)}function v(t){return Object(a.a)({tag:"svg",attr:{viewBox:"0 0 320 512"},child:[{tag:"path",attr:{d:"M31.3 192h
[…]

### 2023-12-24 documentation/sciencemeeting/dist_pdf/vendors~presenter.host.9.dbaca795fbaa026812db.bundle.js

@@ -1,18 +1,0 @@
-(window.webpackJsonp=window.webpackJsonp||[]).push([[9],{164:function(e,t,n){"use strict";Object.defineProperty(t,"__esModule",{value:!0});var r,o=n(165),i=(r=o)&&r.__esModule?r:{default:r};t.default=i.default,e.exports=t.default},165:function(e,t,n){"use strict";function r(e){return(r="function"==typeof Symbol&&"symbol"==typeof Symbol.iterator?function(e){return typeof e}:function(e){return e&&"function"==typeof Symbol&&e.constructor===Symbol&&e!==Symbol.prototype?"symbol":typeof e})(e)}Object.defineProperty(t,"__esModule",{value:!0}),t.bodyOpenClassName=t.portalClassName=void 0;var o=Object.assign||function(e){for(var t=1;t<arguments.length;t++){var n=arguments[t];for(var r in n)Object.prototype.hasOwnProperty.call(n,r)&&(e[r]=n[r])}return e},i=function(){function e(e,t){for(var n=0;n<t.length;n++){var r=t[n];r.enumerable=r.enumerable||!1,r.configurable=!0,"value"in r&&(r.writable=!0),Object.defineProperty(e,r.key,r)}}return function(t,n,r){return n&&e(t.prototype,n),r&&e(t,r),t}}(),a=n(1),l=y(a),u=y(n(8)),c=y(n(36)),s=y(n(166)),f=function(e){if(e&&e.__esModule)return e;var t={};if(null!=e)for(var n in e)Object.prototype.hasOwnProperty.call(e,n)&&(t[n]=e[n]);return t.default=e,t}(n(81)),p=n(54),d=y(p),h=n(173);function y(e){return e&&e.__esModule?e:{default:e}}function m(e,t){if(!(e instanceof t))throw new TypeError("Cannot call a class as a function")}function v(e,t){if(!e)throw new ReferenceError("this hasn't been initialised - super() hasn't been called");return!t||"object"!==r(t)&&"function"!=typeof t?e:t}var b=t.portalClassName="ReactModalPortal",g=t.bodyOpenClassName="ReactModal__Body--open",w=p.canUseDOM&&void 0!==u.default.createPortal,O=function(e){return document.createElement(e)},S=function(){return w?u.default.createPortal:u.default.unstable_renderSubtreeIntoContainer};function E(e){return e()}var C=function(e){function t(){var e,n,r;m(this,t);for(var i=arguments.length,a=Array(i
[…]

### 2023-12-25 documentation/thesis/thesis_document.tex
more thesis

@@
 
-\begin{itemize}
-\tightlist
-\item
-  ziel ist es einen low cost hallsensor-interface zu entwickeln welcher
-  möglichst
-\item
-  universell
-\item
-  verschienee sensoren abbilden kann
-\item
-  mit verschienden magneten typen und formen nutzbar
-\item
-  reproduzierbar
-\item
-  1d, 2d, 3d
-\item
-  integration
-\end{itemize}
+The main aim of this project is to develop a low-cost Hall sensor
+interface that is also universally expandable. The focus is on mapping
+different sensors and being compatible with different magnet types and
+shapes. This ensures broad applicability in different scenarios. Another
+goal is reproducibility to ensure consistent results. Easy communication
+with standard PC hardware maximises the user-friendliness of the
+interface. The flexibility to support different sensors and magnets
+makes the system versatile and opens up possibilities for different
+applications. This low-cost Hall sensor interface will therefore not
+only be economically attractive, but also facilitate the integration of
+Hall sensors in different contexts. In addition, the low-cost Hall
+sensor interface will serve as a development platform for the data
+evaluation \gls{mrp} library and provide real measurement data from
+magnets. In addition, the interface firmware creates a basis for the
+development of a data protocol for exchanging measured values. This
+makes it easy to integrate your own measuring devices into the \gls{mrp}
+ecosystem at a later date. This is only possible with a minimal
+functional hardware and firmware setup and was developed for this
+purpose first.
 
@@
 \section{Sensor selection}\label{sensor-selection}}
+
+The selection process for possible magnetic field sensors initially
+focussed on the most common and cost-effective ones, especially those
+that are already used in smartphones and are therefore widely available.
+A key aspect of this selection was the preference for sensors with
+digital interfaces to facilitate implementation in the circuit layout.
+The integration of integrated temperature sensors represents a
+significant enhancement that will later enable precise temperature
+compensation.
+
+Linear analogue Hall sensors were deliberately omitted, although they
+are suitable for more precise measurements and extended measuring
+ranges. They were excluded due to the more complex circuit layouts
+required and more complex power management. In the context of the
+desired goal of developing a cost-efficient and universally expandable
+Hall sensor interface, the decision in favour of digital sensors seems
+appropriate.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  for higher ranges analog sensoren nutzen welche jedoch eine
-  aufwändigere schaltung erfodern
-\item
-  datenblatte links ergänzen
-\item
-  alle i2c in der regel, welches eine einfache integration ermöglicht
-\item
-  eingebauter temperatursensor ermöglicht temperaturkompensation
-\item
-  conrad teslameter mit seperaten temperatursensor
-\end{itemize}
+Focussing on digital interfaces not only facilitates implementation, but
+also contributes to overall cost efficiency. At the same time, the
+integration of temperature sensors enables precise measurements under
+varying environmental conditions. This strategic choice forms the basis
+for a flexible, universally applicable Hall sensor interface that can be
+seamlessly integrated into various existing systems.
+
+The table\ref{Implemented_digital_halleffect_sensors.csv} shows a
+selection of sensors for which hardware and software support has been
+implemented. The resolution of the selected sensors covers the expected
+range of values required by the various magnets to be tested.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  3d druck toleranztest
-\item
-  magnet halterung mit kraftloser arretierung
-\item
-  motoren und andere unter umstaänden magnetische teile in der nähe des
-  sensors
-\item
-  nylon schrauben, 3d druck, 3d gedruckte klemmverbindungen
-\item
-  später rausrechnen durch kalibierung
-\end{itemize}
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_1D_sensor_mechanical_3D_printed_structure.png}
+\caption{1D sensor mechanical 3D printed structure
+\label{1D_sensor_mechanical_3D_printed_structure.png}}
+\end{figure}
+
+The mechanical structure of a sensor is kept very simple for the
+following tests. The focus was on providing a stable foundation for the
+sensor \gls{ic} and an exchangeable holder for different magnets.
+
+The following figure\ref{1D_sensor_mechanical_3D_printed_structure.png},
+shows a sectional view of the \gls{cad} drawing of the
+\passthrough{\lstinline!1D: Single sensor!}\ref{d-single-sensor}.
+
+All parts were produced using the 3D printing process. The sensor
+circuit board was glued underneath the magnet holder. This is
+interchangeable, so different distances between sensor and magnet can be
+realised.
+
+The exchangeable magnetic holder (shown in green) can be adapted to
+different magnets. It can be produced quickly due to the small amount of
+material used. The two recesses lock the holder with the inserted magnet
+over the sensor. Due to predetermined tolerances, the magnet can be
+inserted into the holder with repeat accuracy and without play. This is
+important if several magnets have to be measured, where the positioning
+over the sensor must always be the same.
 
@@
 \gls{usb} slave port. The used usb descriptor is
-\passthrough{\lstinline!Serial over (+usb)!}- ((+usb)\gls{cdc}). This is
+\passthrough{\lstinline!Serial over (+usb)!}-((+usb)\gls{cdc}). This is
 used to emulate a virtual RS232 communication port using a USB port on a
@@
 ports can lead to delays.
+
+\begin{longtable}[]{@{}llllll@{}}
+\caption{Measured sensor readout to processing using host software
+\label{Measured_sensor_readout_to_processing_using_host_software.csv}}\tabularnewline
+\toprule
+\begin{minipage}[b]{0.02\columnwidth}\raggedright
+Run\strut
+\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedright
+Datapoints\strut
+\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\raggedright
+Host software runtime {[}ms{]}\strut
+\end{minipage} & \begin{minipage}[b]{0.29\columnwidth}\raggedright
+Average Sensor communication time per reading {[}ms{]}\strut
+\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedright
+Communication jitter time {[}ms{]}\strut
+\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
+Comment\strut
+\end{minipage}\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{0.02\columnwidth}\raggedright
+Run\strut
+\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedright
+Datapoints\strut
+\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\raggedright
+Host software runtime {[}ms{]}\strut
+\end{minipage} & \begin{minipage}[b]{0.29\columnwidth}\raggedright
+Average Sensor communication time per reading {[}ms{]}\strut
+\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedright
+Communication jitter time {[}ms{]}\strut
+\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
+Comment\strut
+\end{minipage}\tabularnewline
+\midrule
+\endhead
+\begin{minipage}[t]{0.02\columnwidth}\raggedright
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+9453\strut
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+1.44\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+0\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright
+2\strut
+\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+9864\strut
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+1.5\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+0\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright
+3\strut
+\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
+10\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+12984\strut
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+1.22\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+0.9\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright
+4\strut
+\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
+10\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+12673\strut
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+1.13\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+1.1\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright
+5\strut
+\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
+10\strut
+\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+43264\strut
+\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+2.19\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+4.2\strut
+\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+High host system cpu load\strut
+\end{minipage}\tabularnewline
+\bottomrule
+\end{longtable}
+
+The table
+shows\ref{Measured_sensor_readout_to_processing_using_host_software.csv}
+shows various jitter measurements. These were performed on a
+\passthrough{\lstinline!RaspberryPi 4 4GB!}-\gls{sbc} together with an
+\passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor} and the
+following software settings:
+
+\begin{itemize}
+\tightlist
+\item
+  \passthrough{\lstinline!Raspberry Pi OS Lite!} -
+  \passthrough{\lstinline!debian bookworm x64!},
+\item
+  \gls{mrp}\ref{software-readout-framework}-library - version
+  \passthrough{\lstinline!1.4.1!}
+\item
+  \passthrough{\lstinline!Unified Sensor Firmware!}\ref{unified-sensor}
+  - version \passthrough{\lstinline!1.0.1!}
+\end{itemize}
+
+It can be seen that a jitter time of up to an additional
+\passthrough{\lstinline!1ms!} is added between the triggering of the
+measurements by the host system and the receipt of the command by the
+sensor hardware. If the host system is still under load, this value
+increases many times over. This means that synchronising several sensors
+via the \gls{usb} connection alone is not sufficient.
 

### 2023-12-26 documentation/thesis/thesis_document.tex
more thesis

@@
 
-\ref{1D_sensor_schematic_and_circuit_board.png}
-
-\begin{itemize}
-\tightlist
-\item
-  usb
-\item
-  multiplexer for i2c sensors alredy implemented
-\item
-  imput / output for sync
-\end{itemize}
+As with the mechanical design, the electronics should be kept as simple
+as possible so that it is possible to use the microcontroller and a
+magnetic field sensor.
+
+The focus here was on utilising existing microcontroller development and
+evaluation boards, which already integrate all the components required
+for smooth operation. This not only enabled a time-saving
+implementation, but also ensured a cost-efficient realisation.
+
+A decisive step in my work was the in-house PCB
+design\ref{1D_sensor_schematic_and_circuit_board.png}, which leads out
+all the important connections. The placement and alignment of the
+components optimised the wiring, which in turn improved the reliability
+of the sensor tests. Particular attention was paid to the implementation
+of a \passthrough{\lstinline!SYNC!}-\gls{gpio}, which enables subsequent
+multi-sensor synchronisation. This functionality opens up the
+possibility of synchronising data from different sensors to achieve
+precise and coherent measurement results. Overall, this integrated
+approach represents an effective solution for the flexible evaluation of
+sensors and helps to optimise the development process.
 
@@
 \passthrough{\lstinline!Serial over (+usb)!}-((+usb)\gls{cdc}). This is
-used to emulate a virtual RS232 communication port using a USB port on a
-\gls{pc} and usually no additional driver is needed on modern systems.
+used to emulate a virtual RS232 communication port using a \gls{usb}
+port on a \gls{pc} and usually no additional driver is needed on modern
+systems.
 
@@
 host \gls{pc} as a serial interface. There are several ways for the user
-to interact with this:
+to interact with the sensor:
 
@@
 possible to read out current measured values, obtain debug information
-and set operating parameters. This allows you to quickly determine
-whether the hardware is working properly after installation. The
-\gls{cli} behaves like terminal programmes, displaying a detailed
-command reference\ref{Sensors_(+cli).png} to the user after connecting.
-The current measured value can be output using the
+and set operating parameters. This allows to quickly determine whether
+the hardware is working properly after installation. The \gls{cli}
+behaves like terminal programmes, displaying a detailed command
+reference\ref{Sensors_(+cli).png} to the user after connecting. The
+current measured value can be output using the
 \passthrough{\lstinline!readout!}
@@
 \gls{mrp}-library, the system switches to binary mode, which is
-initiated using the \passthrough{\lstinline!sbm!} command. However, the
-same commands are available as for \gls{cli}-based communication.
+initiated using the \passthrough{\lstinline!sbm!} command. The same
+commands are available as for \gls{cli}-based communication.
 
@@
 Run\strut
-\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedright
-Datapoints\strut
-\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{0.04\columnwidth}\raggedright
+Points\strut
+\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright
 Host software runtime {[}ms{]}\strut
-\end{minipage} & \begin{minipage}[b]{0.29\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{0.32\columnwidth}\raggedright
 Average Sensor communication time per reading {[}ms{]}\strut
-\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{0.20\columnwidth}\raggedright
 Communication jitter time {[}ms{]}\strut
-\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{0.09\columnwidth}\raggedright
 Comment\strut
@@
 1\strut
-\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
 1\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
 9453\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
 1.44\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
 0\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
 \strut
@@
 2\strut
-\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
 1\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
 9864\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
 1.5\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
 0\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
 \strut
@@
 3\strut
-\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
 10\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
 12984\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
 1.22\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
 0.9\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
 \strut
@@
 4\strut
-\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
 10\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
 12673\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
 1.13\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
 1.1\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
 \strut
@@
 5\strut
-\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
 10\strut
-\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
 43264\strut
-\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
 2.19\strut
-\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
-4.2\strut
-\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
-High host system cpu load\strut
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
+8.2\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
+96\% system load\strut
 \end{minipage}\tabularnewline
@@
 Since the \passthrough{\lstinline!MMC5603NJ!} only has very limited
-measuring range, even small neodymium magnets already saturate this
+measuring range, even small neodymium magnets already saturate its
 range, it is possible to use 3D-printed spacers above the sensor.
@@
 which has a measuring range of \passthrough{\lstinline!0-3T!} with a
-resolution of 0.1mT. This offers an \passthrough{\lstinline!RS232!}
+resolution of 0.1mT. It offers an \passthrough{\lstinline!RS232!}
 interface with a documented
@@
 and use sensors that are directly connected to the \gls{pc} with the
-\gls{mrp}-library. This has the disadvantage that there must always be a
+\gls{mrp}-library. It has the disadvantage that there must always be a
 physical connection. This can make it difficult to install multiple
@@
 
-If time-critical synchronisation is required, \gls{ptp} and \gls{pps}
-output functionality can be used on many \gls{sbc}, such as the
+If time-critical synchronisation over the network is required, \gls{ptp}
+and \gls{pps} output functionality\cite{PTPIEEE1588} can be used on
+many \gls{sbc}, such as the
 \passthrough{\lstinline!Raspberry-Pi Compute Module 4!}.
-
-\begin{itemize}
-\tightlist
-\item
-  was ptp, bild pps output
-\item
-  alle clients über ptp verbunden
-\item
-  dso bild von jeff gerling über rpi4 ptp
-\end{itemize}
 
@@
 installation of the \gls{mrp}-library. As it was created in the Python
-programming language, there are several public package directories where
+programming language, there are several public package registry where
 users can provide their software modules. Here,
 \passthrough{\lstinline!PyPi!}\cite{PyPI}\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}\cite{MagneticReadoutProcessingPyPI}
-is the most commonly used package directory and offers direct support
-for the package installation programm
-\gls{pip}\ref{lst:setup_lib_with_pip}.
+is the most commonly used package registry and offers direct support for
+the package installation programm \gls{pip}\ref{lst:setup_lib_with_pip}.
 
@@
 
-To make the \gls{mrp}-library compatible with the package directory,
+To make the \gls{mrp}-library compatible with the package registry,
 Python provides separate installation routines that build a package in
@@
 \passthrough{\lstinline!wheel!} archive. This can then be uploaded to
-the package directory.
+the package registry.
 
@@
 further user documentation such as examples or installation
-instructions.
-
-In order to make the documentation created by
+instructions. In order to make the documentation created by
 \passthrough{\lstinline!Sphinx!} accessible to the user, there are, as
@@
 
-\hypertarget{prequesites-for-evaluation}{%
-\section{Prequesites for evaluation}\label{prequesites-for-evaluation}}
+This work successfully implemented a universal hardware and software
+framework for the automated characterisation of permanent magnets. This
+framework consists of a low-cost hardware interface that supports
+various magnetic field sensors and a library for automating and
+analysing the measurement data. The process of this framework comprises
+several steps, which I will explain below:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  \textbf{Hardware preperation} Users can prepare measurements using the
+  implemented framework. This includes the placement of the sensors and
+  the selection of the relevant parameters for the characterisation of
+  the permanent magnets.
+\item
+  \textbf{Configuration of the measurement} The software provides a
+  user-friendly interface for configuring the measurement parameters.
+  Users can make the desired settings here and customise the framework
+  to their specific requirements.
+\item
+  \textbf{Custom algorithm implementation} An important contribution of
+  the \gls{mrp} echosystem is the possibility for users to implement
+  their own algorithm for data analysis. This allows customisation to
+  specific research questions or experimental requirements.
+\item
+  \textbf{Execution of analysis pipeline} The analysis pipeline can then
+  be executed with the implemented algorithm. The collected measurement
+  data is automatically processed and analysed to extract characteristic
+  parameters of the permanent magnets.
+\end{enumerate}
+
+This process covers all the essential functionalities required for a
+comprehensive characterisation of permanent magnets\ref{usecases}. The
+developed framework not only offers a cost-effective and flexible
+hardware solution, but also enables customisation of the analysis
+algorithms to meet the requirements of different research projects.
+
+\hypertarget{hardware-preperation}{%
+\section{Hardware preperation}\label{hardware-preperation}}
 
@@
 
-\hypertarget{evaluation-confiugration}{%
-\section{Evaluation confiugration}\label{evaluation-confiugration}}
-
-\hypertarget{sensor-readout}{%
-\subsection{Sensor readout}\label{sensor-readout}}
-
-\hypertarget{processing-pipeline}{%
-\subsection{Processing pipeline}\label{processing-pipeline}}
-
-\hypertarget{test-scenarios}{%
-\section{Test scenarios}\label{test-scenarios}}
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
+For the hardware setup, the
+\passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere} sensor was
+used for the evaulation of the framework. As this is equipped with an
+exchangeable magnetic holder mount, suitable holders are required for
+the magnets to be measured. Ten random
+\passthrough{\lstinline!N45 12x12x12mm!} neodymium magnets were used
+here. These were placed in modified 3D printed
+holders\ref{testmagnets_in_holder.png} and then numbered. This allows
+them to be matched to the measurement results later.
+
+\hypertarget{configuration-of-the-measurement}{%
+\section{Configuration of the
+measurement}\label{configuration-of-the-measurement}}
+
+The configured hardware was then connected and connected to the host
+system using the
+\passthrough{\lstinline!MRPcli config setupsensor eval\_measurement\_config!}-\gls{cli}
+command. The measurement was then
+configured\ref{lst:evaluation_measurement_config}.
+
+\begin{lstlisting}[language=bash, caption={Measurement configuration for evaluation measurement}, label=lst:evaluation_measurement_config]
+## CONFIGURE THE MEASUREMENT
+$ MRPcli config setup eval_measurement_config
+> READING-NAME: 360_eval_magnet_<id>
+> OUTPUT-FOLDER: ./readings/evaluation/
+> NUMBER DATAPOINTS: 18 # FOR A FULLSPHERE READING USE MULTIBLE OF 18
+> NUMBER AVERAGE READINGS PER DATAPOINT: 10
+\end{lstlisting}
+
+The \passthrough{\lstinline!MRPcli measure run!} command was then called
+up for each individual magnet to carry out a measurement. After each
+run, the \passthrough{\lstinline!READING-NAME!} parameter was filled
+with the id of the next magnet so that all measurements could be
+assigned to the physical magnets.
+
+\hypertarget{custom-algorithm-implementation}{%
+\section{Custom algorithm
+implementation}\label{custom-algorithm-implementation}}
+
+The next step for the user is the implementation of the filter
+algorithm\ref{lst:custom_find_similar_values_algorithm}. This can have
+any function signature and is implemented in the file
+\passthrough{\lstinline!UDPPFunctionCollection.py!}. This Python file is
+loaded when the pipeline is started and all functions that are imported
+here as a module or implemented directly can be called via the pipeline.
+As this is a short algorithm, it was inserted directly into the file.
+The parameter \passthrough{\lstinline!\_readings!} should later receive
+the imported measurements from the
+\passthrough{\lstinline!stage import!} and the optional
+\passthrough{\lstinline!IP\_return\_count!} parameter specifies the
+number of best measurements that are returned. The return parameter is a
+list of measurements and should contain the measurements that are
+closest to the mean value of all measurements after the function has
+been executed.
+
+\begin{lstlisting}[language=Python, caption={User implemented custom find most similar readings algorithm}, label=lst:custom_find_similar_values_algorithm]
+    @staticmethod
+    def customFindSimilarValuesAlgorithm(_readings: [MRPReading.MRPReading], IP_return_count: int = -1) -> [MRPReading.MRPReading]:
+        import heapq
+        heap = []
+        # SET RESULT VALUE COUNT
+        IP_return_count = max([int(IP_return_count),len(_readings)])
+        if IP_return_count < 0:
+            IP_return_count = len(_readings) / 5
+        # CALCULATE TARGET VALUE: MEAN FROM ALL VALUES
+        target_value = 0.0
+        for idx, r in enumerate(_readings):
+            mean: float = MRPAnalysis.MRPAnalysis.calculate_mean(r)
+            target_value = target_value + mean
+        target_value = target_value / len(_readings)
+        # PUSH READINGS TO HEAP
+        for value in _readings:
+            # USE DIFF AS PRIORITY VALUE IN MIN-HEAP
+            diff = abs(value - target_value)
+            heapq.heappush(heap, (diff, value))
+        # RETURN X BEST ITEMS FROM HEAP
+        similar_values = [item[1] for item in heapq.nsmallest(IP_return_count, heap)]
+        # CLEAN UP USED LIBRARIES AND RETURN RESULT
+        del heapq
+        return similar_values
+\end{lstlisting}
+
+The python \passthrough{\lstinline!heapq!}\cite{heapq} module, which
+implements a priority queue, is used for this purpose. The calculated
+distances from the mean value of the measurements to the global mean
+value are inserted into this queue. Subsequently, as many elements of
+the queue are returned as defined by the
+\passthrough{\lstinline!IP\_return\_count!} parameter. The actual
+sorting was carried out by the queue in the background.
+
+\hypertarget{execution-of-analysis-pipeline}{%
+\section{Execution of analysis
+pipeline}\label{execution-of-analysis-pipeline}}
+
+Once the filter function has been implemented, it still needs to be
+integrated into the analysis
+pipeline\ref{lst:pipeline_mrp_evaluation_yaml}. Here, the example
+pipeline \ref{example_measurement_analysis_pipeline.png} is simplified
+and an additional stage \passthrough{\lstinline!find\_similar\_values!}
+has been added, which has set
+\passthrough{\lstinline!customFindSimilarValuesAlgorithm!} as the
+function to be called. As a final step, the result is used in the
+\passthrough{\lstinline!plot\_filtered!} stage for visualisation.
+
+\begin{lstlisting}[caption={User defined processing pipeline using custom implemented filter algorithm}, label=lst:pipeline_mrp_evaluation_yaml]
+settings:
+  enabled: true
+  export_intermediate_results: false
+  name: pipeline_mrp_evaluation
+
+stage import:
+  function: import_readings
+  parameters:
+    IP_input_folder: ./readings/evaluation/
+    IP_file_regex: 360_(.)*.mag.json
+
+stage find_similar_values:
+  function: custom_find_similar_values_algorithm
+  parameters:
+    _readings: stage import # USE RESULTS FROM import STAGE
+    IP_return_count: 4 # RETURN BEST 4 of 10 READINGS
+
+stage plot_filtered:
+  function: plot_readings
+  parameters:
+    readings_to_plot: stage find_similar_values # USE RESULTS FROM find_similar_values STAGE
+    IP_export_folder: ./readings/evaluation/plots/plot_filtered/
+    IP_plot_headline_prefix:  MRP evaluation - filtered
+\end{lstlisting}
+
+The final pipeline has been saved in the pipeline directory as
+\passthrough{\lstinline!pipeline\_mrp\_evaluation.yaml!} file and is
+ready for execution. This is carried out using the
+\passthrough{\lstinline!MRPudpp!}-(cli)\ref{lst:bash_pipeline_mrp_evaluation_yaml}.
+After the run has been successfully completed, the results are saved in
+the result folder specified in the pipeline using the
+\passthrough{\lstinline!IP\_export\_folder!} parameter.
+
+\begin{lstlisting}[language=bash, caption={Bash result log of evaluation pipeline run}, label=lst:bash_pipeline_mrp_evaluation_yaml]
+# LIST ACTIVE PIPELINES IN PIPELINE DIRECTORY 
+$ MRPudpp pipeline listenabledpipelines
+> Found enabled pipelines:
+> 1. pipeline_mrp_evaluation.yaml
+# EXECUTE THE EVALUATION PIPELINE
+$ MRPudpp pipeline run
+> loading pipeline pipeline_mrp_evaluation.yaml
+> stage nodes: ['import', 'find_similar_values', 'plot_raw', 'plot_filtered']
+> =====> stage: import 
+> =====> stage: find_similar_values 
+> =====> stage plot_filtered 
+> Process finished with exit code 0
+\end{lstlisting}
+
+The figure \ref{MRP_evaluation_result.png} shows this result. The plot
+of the raw measured values is shown on the left. The variance of the
+determined \passthrough{\lstinline!Mean [uT]!} mean values is plotted on
+ten individual measured values. Here you can see that there are measured
+values with larger deviations (see measurement
+\passthrough{\lstinline!7:0!},\passthrough{\lstinline!10-2:0!},\passthrough{\lstinline!10-1:0!}).
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_MRP_evaluation_result.png}
+\caption{MRP evaluation result \label{MRP_evaluation_result.png}}
+\end{figure}
+
+On the right-hand side\ref{MRP_evaluation_result.png}, the measured
+values are plotted as a result of the filter algorithm. As the
+\passthrough{\lstinline!IP\_return\_count!} parameter was set to four,
+only the four most similar measurements were exported here. It can be
+seen from the plotted mean values \passthrough{\lstinline!Mean [uT]!}
+that these are closest to the global mean value
+\passthrough{\lstinline!208.8 uT!}. The algorithm was thus successfully
+executed using the pipeline and the results could be validated.
 

### 2023-12-26 src/MagneticReadoutProcessing/MRPudpp/UDPPFunctionCollection.py

@@ -394,3 +394,29 @@ class UDPPFunctionCollection:
         return new_readings
 
 
+    @staticmethod
+    def custom_find_similar_values_algorithm(_readings: [MRPReading.MRPReading], IP_return_count: int = -1) -> [MRPReading.MRPReading]:
+        import heapq
+        heap = []
+        # SET RESULT VALUE COUNT
+        IP_return_count = int(IP_return_count)
+        if IP_return_count < 0:
+            IP_return_count = int(len(_readings) / 5)
+        # CALCULATE TARGET VALUE: MEAN FROM ALL VALUES
+        target_value: float = 0.0
+        for idx, r in enumerate(_readings):
+            mean: float = MRPAnalysis.MRPAnalysis.calculate_mean(r)
+            target_value = target_value + mean
+        target_value = (target_value / len(_readings))
+        # PUSH READINGS TO HEAP
+        for reading in _readings:
+            reading_mean: float = MRPAnalysis.MRPAnalysis.calculate_mean(reading)
+            # USE DIFF AS PRIORITY VALUE IN MIN-HEAP
+            diff: float = abs(reading_mean - target_value)
+            heapq.heappush(heap, (diff, reading))
+        # RETURN X BEST ITEMS FROM HEAP
+        similar_values: [MRPReading.MRPReading] = [item[1] for item in heapq.nsmallest(IP_return_count, heap)]
+        # CLEAN UP USED LIBRARIES AND RETURN RESULT
+        del heapq
+        return similar_values
+

### 2023-12-26 documentation/thesis/thesis_document.tex
more thesis

@@
 \section{Structure}\label{structure}}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  State of the art
+\item
+  Usecases
+\item
+  Unified Sensor
+\item
+  Software readout framework
+\item
+  Usability improvements
+\item
+  Evaluation
+\end{enumerate}
 
@@
 makes the system versatile and opens up possibilities for different
-applications. This low-cost Hall sensor interface will therefore not
-only be economically attractive, but also facilitate the integration of
-Hall sensors in different contexts. In addition, the low-cost Hall
-sensor interface will serve as a development platform for the data
-evaluation \gls{mrp} library and provide real measurement data from
-magnets. In addition, the interface firmware creates a basis for the
-development of a data protocol for exchanging measured values. This
-makes it easy to integrate your own measuring devices into the \gls{mrp}
-ecosystem at a later date. This is only possible with a minimal
-functional hardware and firmware setup and was developed for this
-purpose first.
+applications. A low-cost Hall sensor interface will therefore not only
+be economically attractive, but also facilitate the integration of Hall
+sensors in different contexts. In addition, the low-cost Hall sensor
+interface will serve as a development platform for the data evaluation
+\gls{mrp} library and provide real measurement data from magnets. In
+addition, the interface firmware creates a basis for the development of
+a data protocol for exchanging measured values. This makes it easy to
+integrate your own measuring devices into the \gls{mrp} ecosystem at a
+later date. This is only possible with a minimal functional hardware and
+firmware setup and was developed for this purpose first.
 
@@
 design\ref{1D_sensor_schematic_and_circuit_board.png}, which leads out
-all the important connections. The placement and alignment of the
-components optimised the wiring, which in turn improved the reliability
-of the sensor tests. Particular attention was paid to the implementation
-of a \passthrough{\lstinline!SYNC!}-\gls{gpio}, which enables subsequent
+all the important connections. The placement and alignment of components
+optimised the wiring, which in turn improved the reliability of the
+sensor tests. Particular attention was paid to the implementation of a
+\passthrough{\lstinline!SYNC!}-\gls{gpio}, which enables subsequent
 multi-sensor synchronisation. This functionality opens up the
@@
 out. This measured data can be forwarded to a host \gls{pc} via a user
-interface and can then be further processed there. An important
-component is that as many common sensors as possible can be easily
-connected without having to adapt the firmware. This modularity was
-implemented using \passthrough{\lstinline!abstract!} class design. These
-are initiated according to the sensors found at startup. If new hardware
-is to be integrated, only the required
+interface and can then be further processed there.
+
+An important component is that as many common sensors as possible can be
+easily connected without having to adapt the firmware. This modularity
+was implemented using \passthrough{\lstinline!abstract!} class design.
+These are initiated according to the sensors found at startup. If new
+hardware is to be integrated, only the required
 functions\ref{lst:CustomSensorClass} need to be implemented.
@@
 cyclic structure enables continuous overwriting of older data, saves
-memory space and facilitates seamless processing of real-time data. Ring
-buffers are well suited for applications with variable data rates and
-minimise the need for complex memory management. The buffer can be read
-out by command and the result of the measurement is sent to the host.
-Each sensor measurement result is transmitted from the buffer to the
-host together with a time stamp and a sequential number. This ensures
-that in a multi-sensor setup with several sensors. The measurements are
-synchronized\ref{sensor-syncronsisation-interface} in time and are not
-out of sequence or drift.
+memory space and facilitates seamless processing of real-time data.
+
+Ring buffers are well suited for applications with variable data rates
+and minimise the need for complex memory management. The buffer can be
+read out by command and the result of the measurement is sent to the
+host. Each sensor measurement result is transmitted from the buffer to
+the host together with a time stamp and a sequential number. This
+ensures that in a multi-sensor setup with several sensors. The
+measurements are synchronized\ref{sensor-syncronsisation-interface} in
+time and are not out of sequence or drift.
 
@@
 
+\hypertarget{library-requirements}{%
+\section{Library requirements}\label{library-requirements}}
+
+\hypertarget{concepts}{%
+\subsection{Concepts}\label{concepts}}
+
+\begin{itemize}
+\tightlist
+\item
+  beispiele für projekte welche nur einzelne schnritte implementieren
+\item
+  so kann man sich auf die implementierung
+\end{itemize}
+
+\hypertarget{user-interaction-points}{%
+\subsection{User interaction points}\label{user-interaction-points}}
+
 \begin{figure}
@@
 
-\hypertarget{library-requirements}{%
-\section{Library requirements}\label{library-requirements}}
-
-\hypertarget{concepts}{%
-\subsection{Concepts}\label{concepts}}
+\hypertarget{extension-modules}{%
+\section{Extension Modules}\label{extension-modules}}
+
+Im folgenden werden die einzelnen module, welche vom user modifiziert
+und ersetzt werden können im details erleutert.
+
+\hypertarget{hal}{%
+\subsection{HAL}\label{hal}}
 
@@
 \item
-  beispiele für projekte welche nur einzelne schnritte implementieren
-\item
-  so kann man sich auf die implementierung
+  aufbau hal im grunde wird nur ein die commandos an das sensor cli
+  weitergegeben
+\item
+  alle sensoren implementieren mehr oder weniger die gleichen befehle
+\item
+  hal gibt nur weiter und ist ``dumm''
 \end{itemize}
 
-\hypertarget{user-interaction-points}{%
-\subsection{User interaction points}\label{user-interaction-points}}
+\hypertarget{visualisation}{%
+\subsection{Visualisation}\label{visualisation}}
+
+\hypertarget{storage}{%
+\subsection{Storage}\label{storage}}
 
@@
 \item
-  grafik zeigen
-\item
-  einzelne module erleutern
+  metadata management
 \end{itemize}
 
-\hypertarget{hal}{%
-\subsubsection{HAL}\label{hal}}
+\hypertarget{export}{%
+\subsection{Export}\label{export}}
 
@@
 \item
-  aufbau hal im grunde wird nur ein die commandos an das sensor cli
-  weitergegeben
-\item
-  alle sensoren implementieren mehr oder weniger die gleichen befehle
-\item
-  hal gibt nur weiter und ist ``dumm''
-\end{itemize}
-
-\hypertarget{visualisation}{%
-\subsubsection{Visualisation}\label{visualisation}}
-
-\hypertarget{export}{%
-\subsection{Export}\label{export}}
-
-\begin{itemize}
-\tightlist
-\item
   format import export
@@
 
-\hypertarget{meta-data}{%
-\subsubsection{Meta-Data}\label{meta-data}}
-
 \hypertarget{multible-sensor-setup}{%
-\subsection{Multible sensor setup}\label{multible-sensor-setup}}
+\section{Multible sensor setup}\label{multible-sensor-setup}}
 
@@
 \hypertarget{network-proxy}{%
-\subsubsection{Network-Proxy}\label{network-proxy}}
+\subsection{Network-Proxy}\label{network-proxy}}
 
@@
 \hypertarget{sensor-syncronisation}{%
-\subsubsection{Sensor Syncronisation}\label{sensor-syncronisation}}
+\subsection{Sensor Syncronisation}\label{sensor-syncronisation}}
 
@@
 \hypertarget{command-router}{%
-\subsubsection{Command-Router}\label{command-router}}
+\subsection{Command-Router}\label{command-router}}
 
@@
 \hypertarget{examples}{%
-\subsection{Examples}\label{examples}}
+\section{Examples}\label{examples}}
+
+The following shows some examples of how the \gls{mrp} library can be
+used. These examples are limited to a functional minimum for selected
+modules of the \gls{mrp} library. The documentation\ref{documentation}
+contains further and more detailed examples. Many basic examples are
+also supplied in the form of test cases\ref{tests}.
+
+\hypertarget{mrpanalysis}{%
+\subsection{MRPAnalysis}\label{mrpanalysis}}
+
+Dieses beispiel zeigt
+
+\begin{lstlisting}[language=Python]
+from MRP import MRPAnalysis
+from MRP import MRPDataVisualization
+# Create a empty reading with no settings. Only the raw values are needed, no metadata
+reading = MRPReading.MRPReading()
+# CREATE A SAMPLE MEASUREMENT
+for i in range(1000):
+    measurement = MRPReadingEntry.MRPReadingEntry()
+    # readout sensor or use dummy data and assign result
+    measurement.value = (random.random() -0.5) * 2
+    reading.insert_reading_instance(measurement, False)
+
+# PLOT MEAN VISUALIZATION
+MRPDataVisualization.MRPDataVisualization.plot_error([reading])
+# APPLY COMPENSATION
+# Here the ``calculate_mean`` function is used
+# see MRPAnalysis module for alternatives
+reading_mean_value = MRPAnalysis.MRPAnalysis.calculate_mean(reading)
+# we want to subtract the mean value from all readings
+reading_mean_value = -reading_mean_value
+# modify measurement values
+MRPAnalysis.MRPAnalysis.apply_global_offset_inplace(reading, reading_mean_value)
+\end{lstlisting}
+
+\hypertarget{mrphallbacharraygenerator}{%
+\subsection{MRPHallbachArrayGenerator}\label{mrphallbacharraygenerator}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}
+\caption{Generated hallbach array with generated cutouts for eight
+magnets
+\label{Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}}
+\end{figure}
+
+The following example code\ref{lst:mrpexample_hallbach}, shows how a
+simple Hallbach magnetic ring can be generated. Eight random
+measurements are generated here. It is important that the magnet type
+(here \passthrough{\lstinline!N45\_CUBIC\_15x15x15!}) is specified. This
+is necessary so that the correct magnet cutouts can be generated when
+creating the 3D model. After the measurements have been generated, they
+are provided with a position and rotation offset according to the
+Hallbach design and calucation
+scheme\cite{HallbachMagnetDesignPaper} using the
+\passthrough{\lstinline!MRPHallbachArrayGenerator!} module.
+
+\begin{lstlisting}[language=Python, caption={MRPHallbachArrayGenerator example for generating an OpenSCAD based hallbach ring}, label=lst:mrpexample_hallbach]
+readings = []
+for idx in range(8):
+  # GENERATE EXAMPLE READINGS USING N45 CUBIC 15x15x15 MAGNETS
+  readings.append(MRPSimulation.MRPSimulation.generate_reading(MRPMagnetTypes.MagnetType.N45_CUBIC_15x15x15))
+## GENERATE HALLBACH
+hallbach_array: MRPHallbachArrayGenerator.MRPHallbachArrayResult = MRPHallbachArrayGenerator.MRPHallbachArrayGenerator.generate_1k_hallbach_using_polarisation_direction(readings)
+# EXPORT TO OPENSCAD
+## 2D MODE DXF e.g. for lasercutting
+MRPHallbachArrayGenerator.MRPHallbachArrayGenerator.generate_openscad_model([hallbach_array], "./2d_test.scad",_2d_object_code=True)
+## 3D MODE e.g. for 3D printing
+MRPHallbachArrayGenerator.MRPHallbachArrayGenerator.generate_openscad_model([hallbach_array], "./3d_test.scad",_2d_object_code=False)
+\end{lstlisting}
+
+In the last step, a 3D model with the dimensions of the magnet type set
+is generated from the generated magnet positions. The result is an
+\passthrough{\lstinline!OpenSCAD!}\cite{OpenSCAD} file, which
+contains the generated \passthrough{\lstinline!OpenSCAD!}
+sourcecode\ref{Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}.
 
@@
     @staticmethod
-    def customFindSimilarValuesAlgorithm(_readings: [MRPReading.MRPReading], IP_return_count: int = -1) -> [MRPReading.MRPReading]:
+    def FindSimilarValuesAlgorithm(_readings: [MRPReading.MRPReading], IP_return_count: int = -1) -> [MRPReading.MRPReading]:
         import heapq
@@
 has been added, which has set
-\passthrough{\lstinline!customFindSimilarValuesAlgorithm!} as the
-function to be called. As a final step, the result is used in the
+\passthrough{\lstinline!FindSimilarValuesAlgorithm!} as the function to
+be called. As a final step, the result is used in the
 \passthrough{\lstinline!plot\_filtered!} stage for visualisation.
@@
 
-\hypertarget{problems}{%
-\section{Problems}\label{problems}}
+This work describes the development of a universal Python library that
+is used to efficiently process data from magnetic field sensors from
+acquisition to analysis. In order to ensure a practical application and
+to give users the opportunity to directly acquire their own magnetic
+field data, cost-effective and easily reproducible hardware was also
+developed.
+
+The hardware is based on widely used magnetic field sensors and low-cost
+microcontrollers, which enables an easily expandable and applicable
+solution for measuring magnets with repeatable accuracy. A particular
+focus was placed on expandability by the user. Interchangeable modules
+allow the user to develop their own analysis algorithms without having
+to redesign everything from scratch.
+
+This extensibility and customisability was successfully demonstrated
+during the evaluation. This underlines the performance of the developed
+framework and shows that it is not only effective in the processing of
+magnetic field sensor data, but also offers a flexible platform for the
+implementation of user-specific analyses.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  magfield camera
-\end{itemize}
+In this version of the framework, a solid foundation has been laid that
+includes all the necessary features and is ready for use. During
+development, particular emphasis was placed on comprehensive
+documentation to make it easier to get started. Together with examples
+for various use cases, a user can quickly evaluate the framework.
+
+However, it should be noted that the framework is still in its infancy.
+The stable version distributed via the package registry is well suited
+for the intended purpose. All tests and evaluations took place under
+normal conditions, especially for the developed hardware sensors, as the
+\gls{mrp} library works successfully with the measurement data.
+
+On the software side, the focus is on integration for the support of
+more professional measuring devices. Only in this way is it possible to
+evaluate and improve the sensor hardware and quantify the measurement
+results.
+
+To summarise, it can be said that a solid software framework has been
+created that can be used directly for the intended purpose. It provides
+a good foundation, but can be further developed by integrating
+professional measurement devices to enable a more comprehensive
+evaluation and improvement of the sensor hardware.

### 2024-01-02 documentation/thesis/thesis_declaration.tex
more thesis

@@
-I hereby declare that I have prepared this thesis independently and
-without outside assistance. Text passages, which are based literally or
-in the sense on publications or lectures of other authors, are marked as
-such. The work has not yet been submitted to any other examination
-authority and has not yet been published.
+Hiermit versichere ich, dass ich die vorliegende Arbeit selbstständig
+verfasst und keine anderen als die im Literaturverzeichnis angegebenen
+Quellen benutzt habe. Stellen, die wörtlich oder sinngemäß aus
+veröffentlichten oder noch nicht veröffentlichten Quellen entnommen
+sind, sind als solche kenntlich gemacht. Die Zeichnungen oder
+Abbildungen in dieser Arbeit sind von mir selbst erstellt worden oder
+mit einem entsprechenden Nachweis versehen. Diese Arbeit ist in gleicher
+oder ähnlicher Form noch bei keiner anderen Prüfungsbehörde eingereicht
+worden.
+
+I hereby certify that I have written this thesis independently and have
+not used any sources other than those listed in the bibliography. Any
+passages taken verbatim or in spirit from published or unpublished
+sources are labelled as such. The drawings or illustrations in this work
+have been created by myself or have been labelled accordingly. This
+thesis has not been submitted in the same or a similar form to any other
+examination authority.
 

### 2024-01-02 documentation/thesis/thesis_document.tex
more thesis

@@
 
+This work is divided into six main chapters, which deal with the
+approach and implementation. The techniques and concepts used are
+explained in detail. Specific examples provide an overview of the
+possible use of the developed solution by the user.
+
+\ref{state-of-the-art}. \textbf{State of the art} describes the current
+state of technology and forms the basis for further development.
+Existing measurement methods and findings are shown here in order to
+define the context for the current project.
+
+\ref{usecases}. \textbf{Usecases} are the application cases in which the
+project is to be used. They illustrate the practical scenarios and
+define how the product can be used in the real world. This is crucial
+for understanding the needs of the target group and designing the end
+result accordingly.
+
+\ref{unified-sensor}. \textbf{Unified Sensor} refers to the integration
+of different sensors into a standardised solution. This enables simple
+data acquisition and serves as a basic hardware system on which the
+subsequent data processing library can be applied.
+
+\ref{software-readout-framework}. \textbf{Software readout framework}
+chapter describes the implementation of the data readout framework. This
+includes an explanation of the various modules and specific application
+examples.
+
+\ref{usability-improvements}. \textbf{Usability improvements} refers to
+measures to improve user-friendliness. This involves optimising
+interfaces, interactions and processes to ensure intuitive and efficient
+use of the product. This includes, code documentation or the
+distribution of source code to users.
+
+\ref{evaluation}. \textbf{Evaluation} comprises the systematic review
+and assessment of the overall system. This includes the demonstration of
+the implemented capabilities of the overall system against the
+previously defined use cases.
+
+\hypertarget{state-of-the-art}{%
+\chapter{State of the art}\label{state-of-the-art}}
+
+\hypertarget{opensource-projects}{%
+\section{Opensource projects}\label{opensource-projects}}
+
+\hypertarget{conceptual-design}{%
+\section{Conceptual design}\label{conceptual-design}}
+
+\begin{itemize}
+\tightlist
+\item
+  etnwicklung eines hardware uns software framework zur einfachen
+  aquirierung von Meagnetfelddaten
+\item
+  analysetools und funktionen
+\end{itemize}
+
+\hypertarget{usecases}{%
+\chapter{Usecases}\label{usecases}}
+
 \begin{enumerate}
 \def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
 \tightlist
 \item
-  State of the art
-\item
-  Usecases
-\item
-  Unified Sensor
-\item
-  Software readout framework
-\item
-  Usability improvements
-\item
-  Evaluation
 \end{enumerate}
-
-\hypertarget{state-of-the-art}{%
-\chapter{State of the art}\label{state-of-the-art}}
-
-\hypertarget{opensource-projects}{%
-\section{Opensource projects}\label{opensource-projects}}
-
-\hypertarget{conceptual-design}{%
-\section{Conceptual design}\label{conceptual-design}}
-
-\begin{itemize}
-\tightlist
-\item
-  etnwicklung eines hardware uns software framework zur einfachen
-  aquirierung von Meagnetfelddaten
-\item
-  analysetools und funktionen
-\end{itemize}
-
-\hypertarget{usecases}{%
-\chapter{Usecases}\label{usecases}}
 
@@
   "temp"
-   ]
-
+]}
 # RUN A SENSOR COMMAND AND GET THE TOTAL SENSOR COUNT
@@
   "2"
-   ]
-}
-}
+]}
 \end{lstlisting}
@@
 
+\hypertarget{mrpreading}{%
+\subsection{MRPReading}\label{mrpreading}}
+
+\begin{lstlisting}[language=Python]
+from MRP import MRPReading, MRPMeasurementConfig
+# [OPTIONAL] CONFIGURE READING USING MEASUREMENT CONFIG INSTANCE
+config: MRPMeasurementConfig = MRPMeasurementConfig
+config.sensor_distance_radius(40) # 40mm DISTANCE BETWEEN MAGNET AND SENSOR
+config.magnet_type(N45_CUBIC_12x12x12) # CHECK MRPMagnetTypes.py FOR IMPLEMENTED TYPES
+# CREATE READING
+reading: MRPReading = MRPReading(config)
+# ADD METADATA
+reading.set_name("example reading")
+## ADD FURTHER DETAILS
+reading.set_additional_data("description", "abc")
+reading.set_additional_data("test-number", 1)
+# INSERT A DATAPOINT
+measurement = MRPReadingEntry.MRPReadingEntry()
+measurement.value = random.random()
+reading.insert_reading_instance(measurement, False)
+# USE MEASURED VALUES IN OTHER FRAMEWORKS / DATAFORMATS
+## NUMPY
+npmatrix: np.ndarray = reading.to_numpy_matrix()
+## CSV
+csv: []= reading.to_value_array()
+## JSON
+js: dict= reading.dump()
+# EXPORT READING TO FILE
+reading.dump_to_file("exported_reading.mag.json")
+
+# IMPORT READING
+imported_reading: MRPReading = MRPReading()
+imported_reading.load_from_file("exported_reading.mag.json")
+\end{lstlisting}
+
+\hypertarget{mrphal}{%
+\subsection{MRPHal}\label{mrphal}}
+
+\begin{lstlisting}[language=Python]
+from MRP import MRPHalSerialPortInformation, MRPHal, MRPBaseSensor, MRPReadingSource
+# SEARCH FOR CONNECTED SENSORS
+system_ports: MRPHalSerialPortInformation = MRPHalSerialPortInformation.list_serial_ports()
+sensor = MRPHal(system_ports[0])
+# OR USE SPECIFIED SENSOR DEVICE
+device_path: MRPHalSerialPortInformation = MRPHalSerialPortInformation("/dev/serial/by-name/UNFSensor1")
+sensor = MRPHal(device_path)
+# RAW SENSOR INTERACTION MODE
+sensor.connect()
+basesensor = MRPBaseSensor.MRPBaseSensor(sensor)
+basesensor.query_readout()
+print(basesensor.get_b()) # GET RAW MEASUREMENT
+print(basesensor.get_b(1)) # GET RAW DATA FROM SENSOR WITH ID 1
+# TO GENERATE A READING THE perform_measurement FUNCTION CAN BE USED
+reading_source: MRPReadingSource = MRPReadingSourceHelper.createReadingSourceInstance(sensor)
+result_readings: [MRPReading] = reading_source.perform_measurement(_readings=1, _hwavg=1)
+\end{lstlisting}
+
+\hypertarget{mrpsimulation}{%
+\subsection{MRPSimulation}\label{mrpsimulation}}
+
+\begin{lstlisting}[language=Python]
+from MRP import MRPSimulation, MRPPolarVisualization, MRPReading
+# GENERATE SILUMATED READING USING A SIMULATED HALLSENSOR FROM magpy LIBRARY
+reading: MRPReading = MRPSimulation.generate_reading(MRPMagnetTypes.MagnetType.N45_CUBIC_12x12x12,_add_random_polarisation=True)
+# GENERATE A FULLSPHERE MAP READING
+reading_fullsphere: MRPReading = MRPSimulation.generate_random_full_sphere_reading()
+# RENDER READING TO FILE IN 3D
+visu = MRPPolarVisualization(reading)
+visu.plot3d(None)
+visu.plot3d("simulated_reading.mag.png")
+# EXPORT READING
+reading.dump_to_file("simulated_reading.mag.json")
+\end{lstlisting}
+
 \hypertarget{mrpanalysis}{%
@@
 \begin{lstlisting}[language=Python]
-from MRP import MRPAnalysis
-from MRP import MRPDataVisualization
-# Create a empty reading with no settings. Only the raw values are needed, no metadata
+from MRP import MRPAnalysis, MRPDataVisualization, MRPReading
+# CREATE EMPTY READING
 reading = MRPReading.MRPReading()
@@
     reading.insert_reading_instance(measurement, False)
-
 # PLOT MEAN VISUALIZATION
@@
 # Here the ``calculate_mean`` function is used
-# see MRPAnalysis module for alternatives
 reading_mean_value = MRPAnalysis.MRPAnalysis.calculate_mean(reading)
@@
 \end{lstlisting}
+
+\hypertarget{mrpvisualisation}{%
+\subsection{MRPVisualisation}\label{mrpvisualisation}}
 
@@
 \passthrough{\lstinline!OpenSCAD!}\cite{OpenSCAD} file, which
-contains the generated \passthrough{\lstinline!OpenSCAD!}
-sourcecode\ref{Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}.
+contains the module generated. After computing the model using the
+\passthrough{\lstinline!OpenSCAD!}-\gls{cli} utility, the following
+model
+rendering\ref{Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}
+can be generated.
 
@@
   """
-        Plots a temperature plot of the reading data as figure
+  Plots a temperature bar graph of the reading data entries as figure
   :param _readings: readings to plot

### 2024-01-02 src/MagneticReadoutProcessing/tests/test_MRPSimulation.py

@@ -6,7 +6,7 @@ import random
 import unittest
 import numpy as np
 
-from MRP import MRPPolarVisualization, MRPSimulation
+from MRP import MRPPolarVisualization, MRPSimulation, MRPMagnetTypes
 class TestMPRSimulation(unittest.TestCase):
 
     # PREPARE A INITIAL CONFIGURATION FILE
@@ -19,43 +19,41 @@ class TestMPRSimulation(unittest.TestCase):
     @unittest.skip
     def test_simulation_random_full_sphere(self):
         reading = MRPSimulation.MRPSimulation.generate_random_full_sphere_reading(False)
-        visu = MRPVisualization.MRPVisualization(reading)
+        visu = MRPPolarVisualization.MRPPolarVisualization(reading)
         #visu.plot3d(None)
 
     @unittest.skip
     def test_simulation_random_full_sphere_random(self):
         reading = MRPSimulation.MRPSimulation.generate_random_full_sphere_reading(True)
-        visu = MRPVisualization.MRPVisualization(reading)
+        visu = MRPPolarVisualization.MRPPolarVisualization(reading)
         #visu.plot3d(None)
 
     @unittest.skip
     def test_simulation_cubic_magnet(self):
         no_samples = 10
-        magnet_size = 12 # mm
         add_random_factor = True
         for sample in range(no_samples):
-            reading = MRPSimulation.MRPSimulation.generate_reading(magnet_size, add_random_factor)
-            visu = MRPVisualization.MRPVisualization(reading)
+            reading = MRPSimulation.MRPSimulation.generate_reading(MRPMagnetTypes.MagnetType.N45_CUBIC_12x12x12, add_random_factor)
+            visu = MRPPolarVisualization.MRPPolarVisualization(reading)
             visu.plot3d(None)
 
-            name = os.path.join(self.batch_generation_folder_path, 'test_simulation_cubic_magnet_' + str(magnet_size) + "mm_" + str(sample))
+            name = os.path.join(self.batch_generation_folder_path, 'test_simulation_cubic_magnet_' + str(MRPMagnetTypes.MagnetType.N45_CUBIC_9x9x9) + "mm_" + str(sample))
             visu.plot3d(name + ".mag.pkl.png")
             reading.dump_to_file( name + ".mag.pkl")
 
     @unittest.skip
     def test_simulation_cubic_magnet_with_random_polarisazion(self):
         no_samples = 10
-        magnet_size = 12 # mm
[…]

### 2024-01-02 documentation/thesis/thesis_document.tex
.

@@
 
+The following section defines some use cases that the future project
+should be able to cover. They illustrate practical situations and help
+to understand the functionality and added value of the implemented
+project for the user. These were defined in the course of project
+planning and provide an overview of how the user interacts with the
+project and what functionalities can be expected. In the later
+evaluation\ref{evaluation} process, the defined usecases are also used
+as a reference to demonstrate the implemented capabilities of the
+solution.
+
 \begin{enumerate}
 \def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
+\item
+  \textbf{Ready to use hardware sensor designs}
+\item
+  \textbf{Taking automatic measurements from sensors}
+\item
+  \textbf{Ready to use data analysis functions}
+\item
+  \textbf{Open storage formats for data export}
+\item
+  \textbf{Easy software configuration}
+\item
+  \textbf{User expandable data processing pipelines}
 \end{enumerate}
@@
 \item
-  tablle mit mergin algorithmus
+  grafik mit mergin algorithmus
 \end{itemize}
@@
 
-\begin{lstlisting}[language=Python]
+The \passthrough{\lstinline!MRPReading!} module is the cornerstone of
+the \gls{mrp} library. It is used to manage the measurement data and can
+be imported and exported. The following
+example\ref{lst:mrpexample_reading} shows how a measurement is created
+and measurement points are added in the form of
+\passthrough{\lstinline!MRPReadingEntry!} instances. An important point
+is the management of the meta data, which further describes the
+measurement. This is realised in the example using the
+\passthrough{\lstinline!set\_additional\_data!} function.
+
+\begin{lstlisting}[language=Python, caption={MRPReading example for setting up an basic measurement}, label=lst:mrpexample_reading]
 from MRP import MRPReading, MRPMeasurementConfig
@@
 reading.dump_to_file("exported_reading.mag.json")
-
 # IMPORT READING
@@
 
+Finally, the measurement is exported for archiving and further
+processing; various export formats are available. Using the
+\passthrough{\lstinline!dump\_to\_file!} function, the measurement can
+be converted into an open \gls{json} format. This file can then be
+imported again at a later date using
+\passthrough{\lstinline!load\_from\_file!}.
+
 \hypertarget{mrphal}{%
@@
 
-\begin{lstlisting}[language=Python]
+After generating simple measurements with random values in the previous
+example\ref{mrpreading}, the next step is to record real sensor data.
+For this purpose, the MRPHal module was developed, which can interact
+with all
+\passthrough{\lstinline!Unified Sensor!}\ref{unified-sensor}-compatible
+sensors. In the following example\ref{lst:mrpexample_hal}, an
+\passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor} is
+connected locally to the host \gls{pc}.
+
+\begin{lstlisting}[language=Python, caption={MRPHal example to use an connected hardware sensor to store readings inside of an measurement}, label=lst:mrpexample_hal]
 from MRP import MRPHalSerialPortInformation, MRPHal, MRPBaseSensor, MRPReadingSource
 # SEARCH FOR CONNECTED SENSORS
-system_ports: MRPHalSerialPortInformation = MRPHalSerialPortInformation.list_serial_ports()
+## LISTS LOCAL CONNECTED OR NETWORK SENSORS
+system_ports: MRPHalSerialPortInformation = MRPHalSerialPortInformation.list_sensors()
 sensor = MRPHal(system_ports[0])
 # OR USE SPECIFIED SENSOR DEVICE
-device_path: MRPHalSerialPortInformation = MRPHalSerialPortInformation("/dev/serial/by-name/UNFSensor1")
+device_path: MRPHalSerialPortInformation = MRPHalSerialPortInformation("UNFSensor1")
 sensor = MRPHal(device_path)
@@
 \end{lstlisting}
+
+In general, a sensor can be connected using its specific system path or
+the sensor-\gls{id} via the MRPHalSerialPortInformation function.
+Locally connected or network sensors can also be automatically
+recognised using the \passthrough{\lstinline!list\_sensors!} function.
+Once connected, these are then converted into a usable data source using
+the MRPReadingSource module. This automatically recognises the type of
+sensor and generated an \passthrough{\lstinline!MRPReading!} instance
+with the measured values of the sensor.
 

### 2024-01-02 src/MagneticReadoutProcessing/MRP/MRPHalSerialPortInformation.py

@@ -66,6 +66,12 @@ class MRPHalSerialPortInformation:
             return True
         return False
 
+
+    @staticmethod
+    def list_sensors() -> []:
+        l: [MRPHalSerialPortInformation] = MRPHalSerialPortInformation.list_serial_ports()
+        r: [MRPHalSerialPortInformation] = MRPHalSerialPortInformation.list_remote_serial_ports
+        return l + r
     @staticmethod
     def list_remote_serial_ports() -> []:
         sock = socket(AF_INET, SOCK_DGRAM)

### 2024-01-02 documentation/thesis/thesis_document.tex
more thesis

@@
 the proxy module, it is possible to link several instances and all
-sensors available in the network are available to the control \gls{pc}.
+sensors available in the network are available to the
+\passthrough{\lstinline!control!} \gls{pc}.
 
@@
 \passthrough{\lstinline!multi-proxy - multi-sensor!} topology. Here,
-both proxy instances do not communicate directly with the control
-\gls{pc}, but \passthrough{\lstinline!remote (+pc) \#2!} is connected to
-\passthrough{\lstinline!remote (+pc) \#1!}. This is then visible as a
-sensor opposite the Control \gls{pc}, even if there are several proxy
-instances behind it.
+both proxy instances do not communicate directly with the
+\passthrough{\lstinline!control!} \gls{pc}, but
+\passthrough{\lstinline!remote!}\gls{pc}\passthrough{\lstinline!\#2!} is
+connected to
+\passthrough{\lstinline!remote!}\gls{pc}\passthrough{\lstinline!\#1!}.
+This is then visible as a sensor opposite the Control \gls{pc}, even if
+there are several proxy instances behind it.
 
@@
 various \gls{hal} instances, which communicate with the physically
-connected sensors on the \passthrough{\lstinline!remote!}-\gls{pc} and
-the \passthrough{\lstinline!control!}-\gls{pc} side, which communicates
+connected sensors on the \passthrough{\lstinline!remote!} \gls{pc} and
+the \passthrough{\lstinline!control!} \gls{pc} side, which communicates
 with the remote side via the network. For the user, nothing changes in
@@
 
-\begin{itemize}
-\item
-  nummerieierung zuerst lokale sensoren dann weitere proxy sensoren
-\item
-  commando templating
-\item
-  einzelne sensor capabilites werden gemerged
-\item
-  ids werden aufsuimmiert
-\item
-  spätere sensor identifikation geschieht über die jeweilige sensor id,
-  welche über diesen index abgefragt werden kann
-\item
-  grafik mit mergin algorithmus
-\end{itemize}
+As it is possible to connect many identical sensors to one host using
+the \passthrough{\lstinline!network proxy!}, it must be possible to
+address them separately. This separation is done by the
+\passthrough{\lstinline!MRPProxy.proxy!} module and is therefore not
+part of the core \gls{mrp} library.
+
+Each connected sensor is addressed via the text-based \gls{cli} or the
+binary interface, this is initially the same for each sensor. The only
+identification feature is the sensor \gls{id}.
+
+The \passthrough{\lstinline!network proxy!} instance pretends to be a
+sensor to the \gls{mrp} host, so the multiple sensors must be combined
+into one. This is done in several steps, in the
+\passthrough{\lstinline!network proxy!} start procedure:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  \textbf{Construct the Sensor ID LookUp-Table}
+\item
+  \textbf{Merging the sensor capabilities}
+\item
+  \textbf{Dynamic extension of the available network proxy commands}
+\end{enumerate}
 
@@
 example\ref{mrpreading}, the next step is to record real sensor data.
-For this purpose, the MRPHal module was developed, which can interact
-with all
+For this purpose, the \passthrough{\lstinline!MRPHal!} module was
+developed, which can interact with all
 \passthrough{\lstinline!Unified Sensor!}\ref{unified-sensor}-compatible
@@
 \passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor} is
-connected locally to the host \gls{pc}.
+connected locally to the host-\gls{pc}.
 
@@
 ## LISTS LOCAL CONNECTED OR NETWORK SENSORS
-system_ports: MRPHalSerialPortInformation = MRPHalSerialPortInformation.list_sensors()
+system_ports = MRPHalSerialPortInformation.list_sensors()
 sensor = MRPHal(system_ports[0])
 # OR USE SPECIFIED SENSOR DEVICE
-device_path: MRPHalSerialPortInformation = MRPHalSerialPortInformation("UNFSensor1")
+device_path = MRPHalSerialPortInformation("UNFSensor1")
 sensor = MRPHal(device_path)
@@
 # TO GENERATE A READING THE perform_measurement FUNCTION CAN BE USED
-reading_source: MRPReadingSource = MRPReadingSourceHelper.createReadingSourceInstance(sensor)
+reading_source = MRPReadingSourceHelper.createReadingSourceInstance(sensor)
 result_readings: [MRPReading] = reading_source.perform_measurement(_readings=1, _hwavg=1)
@@
 In general, a sensor can be connected using its specific system path or
-the sensor-\gls{id} via the MRPHalSerialPortInformation function.
-Locally connected or network sensors can also be automatically
-recognised using the \passthrough{\lstinline!list\_sensors!} function.
-Once connected, these are then converted into a usable data source using
-the MRPReadingSource module. This automatically recognises the type of
-sensor and generated an \passthrough{\lstinline!MRPReading!} instance
-with the measured values of the sensor.
+the sensor-\gls{id} via the
+\passthrough{\lstinline!MRPHalSerialPortInformation!} function. Locally
+connected or network sensors can also be automatically recognised using
+the \passthrough{\lstinline!list\_sensors!} function. Once connected,
+these are then converted into a usable data source using the
+\passthrough{\lstinline!MRPReadingSource!} module. This automatically
+recognises the type of sensor and generated an
+\passthrough{\lstinline!MRPReading!} instance with the measured values
+of the sensor.
 
@@
 
-\begin{lstlisting}[language=Python]
+If no hardware sensor is available or for the generation of test data,
+the \passthrough{\lstinline!MRPSimulation!} module is available. This
+contains a series of functions that simulate various magnets and their
+fields. The result is a complete \passthrough{\lstinline!MRPReading!}
+measurement with a wide range of set meta data. The
+example\ref{lst:mrpexample_simulation} illustrated the basic usage.
+Different variations of the \passthrough{\lstinline!generate\_reading!}
+function offers the user additional parameterisation options, such as
+random polarisation direction or a defined centre-of-gravity vector. The
+data is generated in the background using the
+\passthrough{\lstinline!magpylib!}\cite{ortner2020magpylib} library
+according to the specified parameters.
+
+\begin{lstlisting}[language=Python, caption={MRPSimulation example illustrates the usage of several data analysis functions}, label=lst:mrpexample_simulation]
 from MRP import MRPSimulation, MRPPolarVisualization, MRPReading
 # GENERATE SILUMATED READING USING A SIMULATED HALLSENSOR FROM magpy LIBRARY
-reading: MRPReading = MRPSimulation.generate_reading(MRPMagnetTypes.MagnetType.N45_CUBIC_12x12x12,_add_random_polarisation=True)
+reading = MRPSimulation.generate_reading(MagnetType.N45_CUBIC_12x12x12,_add_random_polarisation=True)
 # GENERATE A FULLSPHERE MAP READING
-reading_fullsphere: MRPReading = MRPSimulation.generate_random_full_sphere_reading()
+reading_fullsphere = MRPSimulation.generate_random_full_sphere_reading()
 # RENDER READING TO FILE IN 3D
@@
 visu.plot3d(None)
-visu.plot3d("simulated_reading.mag.png")
+visu.plot3d("simulated_reading.png")
 # EXPORT READING
@@
 
-Dieses beispiel zeigt
-
-\begin{lstlisting}[language=Python]
-from MRP import MRPAnalysis, MRPDataVisualization, MRPReading
-# CREATE EMPTY READING
-reading = MRPReading.MRPReading()
-# CREATE A SAMPLE MEASUREMENT
-for i in range(1000):
-    measurement = MRPReadingEntry.MRPReadingEntry()
-    # readout sensor or use dummy data and assign result
-    measurement.value = (random.random() -0.5) * 2
-    reading.insert_reading_instance(measurement, False)
-# PLOT MEAN VISUALIZATION
-MRPDataVisualization.MRPDataVisualization.plot_error([reading])
-# APPLY COMPENSATION
-# Here the ``calculate_mean`` function is used
-reading_mean_value = MRPAnalysis.MRPAnalysis.calculate_mean(reading)
-# we want to subtract the mean value from all readings
-reading_mean_value = -reading_mean_value
-# modify measurement values
-MRPAnalysis.MRPAnalysis.apply_global_offset_inplace(reading, reading_mean_value)
+Once data can be acquired using hardware or software sensors, the next
+step is to analyse this data. The \gls{mrp} library provides some simple
+analysis functions for this purpose. The code example shows the basic
+use of the module. The
+\passthrough{\lstinline!Evaluation!}\ref{evaluation} chapter shows how
+the user can implement their own algorithms and add them to the library.
+
+\begin{lstlisting}[language=Python, caption={MRPAnalysis example code performs several data analysis steps}, label=lst:mrpexample_analysis]
+from MRP import MRPAnalysis, MRPReading
+# CREATE A SAMPLE MEASUREMENT WITH SIMULATED DATA
+reading = MRPSimulation.generate_reading(MagnetType.N45_CUBIC_10x10x10)
+# CALCULATE MEAN
+print(MRPAnalysis.calculate_mean(reading))
+# CALCULATE STD DEVIATION ON TEMPERATURE AXIS
+print(MRPAnalysis.calculate_std_deviation(reading, _temperature_axis=True))
+# CALCULATE CENTER OF GRAVITY
+(x, y, z) = MRPAnalysis.calculate_center_of_gravity(reading)
+# APPLY CALIBRATION READING TO REMOVE BACKGROUND NOISE
+calibration_reading = MRPSimulation.generate_reading(MagnetType.N45_CUBIC_10x10x10, _ideal = True)
+MRPAnalysis.apply_calibration_data_inplace(calibration_reading, reading)
 \end{lstlisting}
@@
 \subsection{MRPVisualisation}\label{mrpvisualisation}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
+\caption{Example full sphere plot of an measurement using the
+MRPVisualisation module
+\label{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}}
+\end{figure}
+
+This final example shows the use of the MRP Visualisation module, which
+provides general functions for visualising measurements. This makes it
+possible to visually assess the results of a measurement. This is
+particularly helpful for full-sphere measurements recorded with the
+\passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere} sensor. The
+sub-module `MRPPolarVisualisation' is specially designed for these. The
+figure\ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
+shows a plot of a fullsphere measurement.
+
+It is also possible to export the data from the MRPAnalysis module
+graphically as diagrams. The \passthrough{\lstinline!MRPVisualisation!}
+modules are used here. The following
+example\ref{lst:mrpexample_visualisation} shows the use of both modules.
+
+\begin{lstlisting}[language=Python, caption={MRPVisualisation example which plots a fullsphere to an image file}, label=lst:mrpexample_visualisation]
+from MRP import MRPPolarVisualization
+# CREATE MRPPolarVisualization INSTANCE
+## IT CAN BE REUSED CALLING plot2d AGAIN, AFTER LINKED READING DATA WERE MODIFIED
+visu = MRPPolarVisualization.MRPPolarVisualization(reading)
+# 2D PLOT INTO A WINDOW
+visu.plot2d_top(None)
+visu.plot2d_side(None)
+# 3D PLOT TO FILE
+visu.plot3d(os.path.join('./plot3d_3d.png'))
+
+# PLOT ANALYSIS RESULTS
+from MRP import MRPDataVisualization
+MRPDataVisualization.MRPDataVisualization.plot_error([reading_a, reading_b, reading_c])
+\end{lstlisting}
 

### 2024-01-02 documentation/thesis/thesis_document.tex
more thesis

@@
 As it is possible to connect many identical sensors to one host using
-the \passthrough{\lstinline!network proxy!}, it must be possible to
-address them separately. This separation is done by the
+the \passthrough{\lstinline!Network-Proxy!}\ref{network-proxy}, it must
+be possible to address them separately. This separation is done by the
 \passthrough{\lstinline!MRPProxy.proxy!} module and is therefore not
@@
 
-The \passthrough{\lstinline!network proxy!} instance pretends to be a
-sensor to the \gls{mrp} host, so the multiple sensors must be combined
-into one. This is done in several steps, in the
-\passthrough{\lstinline!network proxy!} start procedure:
+The \passthrough{\lstinline!Network-Proxy!}\ref{network-proxy} instance
+pretends to be a sensor to the \gls{mrp} host, so the multiple sensors
+must be combined into one. This is done in several steps, in the
+\passthrough{\lstinline!Network-Proxy!}\ref{network-proxy} start
+procedure:
 
@@
 \def\labelenumi{\arabic{enumi}.}
+\tightlist
 \item
   \textbf{Construct the Sensor ID LookUp-Table}
+\end{enumerate}
+
+Immediately after starting the
+\passthrough{\lstinline!network-proxy!}\ref{network-proxy}, the
+\gls{id}s of all locally connected sensors are read out. These are
+stored together with the instance of the
+\passthrough{\lstinline!MRPHal!} module in a \gls{lut}. This makes it
+possible to address a sensor directly using its \gls{id}.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
 \item
   \textbf{Merging the sensor capabilities}
-\item
-  \textbf{Dynamic extension of the available network proxy commands}
 \end{enumerate}
+
+\begin{longtable}[]{@{}llll@{}}
+\caption{Sensor capabilities merging
+\label{Sensor_capabilities_merging.csv}}\tabularnewline
+\toprule
+SENSOR A & SENSOR B & MERGED CAPABILITIES & CAPABLE SENSORS ID
+LUT\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+SENSOR A & SENSOR B & MERGED CAPABILITIES & CAPABLE SENSORS ID
+LUT\tabularnewline
+\midrule
+\endhead
+static & & static & A\tabularnewline
+& dynamic & dynamic & B\tabularnewline
+axis\_temp & axis\_temp & axis\_temp & A B\tabularnewline
+axis\_x & axis\_x & axis\_x & A B\tabularnewline
+\bottomrule
+\end{longtable}
+
+When using sensors with different capabilites, these must be combined.
+These are used to select the appropriate measurement mode for a
+measurement. For this purpose, the \passthrough{\lstinline!info!}
+command of each sensor is queried. This information is added to the
+previously created \gls{lut}. Duplicate entries are summarized (see
+Table:\ref{Sensor_capabilities_merging.csv}) and returned to the host
+when the \passthrough{\lstinline!info!}\ref{lst:mtsc} command is
+received over network.
+
+\begin{lstlisting}[language=bash, caption={MRPproxy REST enpoiint query examples}, label=lst:mtsc]
+  # QUERY Network-Proxy capabilities
+  $ wget http://proxyinstance.local:5556/proxy/status
+  {"capabilities":[
+  "static",
+  "dynamic",
+  "axis_temp",
+  "axis_x"
+  ]}
+\end{lstlisting}
+
+The same procedure is performed for the
+\passthrough{\lstinline!commands!} \gls{cli}-command of each sensor, to
+merge to available commands of connected sensors into the \gls{lut}.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  \textbf{Dynamic extension of the available network proxy commands} In
+  order for the host to be able to send a command to the network
+  multi-sensor setup, the command received must be forwarded to the
+  correct sensor. In addition, there are commands such as the previously
+  used \passthrough{\lstinline!info!} or
+  \passthrough{\lstinline!status!} command, which must be intercepted by
+  the \passthrough{\lstinline!MRPProxy!} module so that it can be
+  handled differently (see example \ref{lst:mtsc}).
+\end{enumerate}
+
+To realize this, a \gls{lut} was created in the previous steps, which
+contains information regarding
+\passthrough{\lstinline!requested capability!} -\textgreater{}
+\passthrough{\lstinline!sensor!}-\gls{id} -\textgreater{}
+\passthrough{\lstinline!physical sensor!} and allows the commands to be
+routed.
+
+For commands where there are several entries for
+\passthrough{\lstinline!CAPABLE SENSORS ID LUT!}\ref{Sensor_capabilities_merging.csv},
+there are two possible approaches to how the command is processed:
+
+\begin{itemize}
+\tightlist
+\item
+  redirect to each capable sensor
+\item
+  extend commands using an id parameter
+\end{itemize}
+
+These two methods have been implemented and are applied automatically.
+The decision is based on which hardware sensors are connected. In a
+setup where only the same sensor variants are connected,
+\passthrough{\lstinline!redirect to each capable sensor!} is applied.
+This offers a time advantage as fewer commands need to be sent from the
+host. Thus, with a \passthrough{\lstinline!readsensor!} command, all
+sensors are read out via one command and the summarized result is
+transmitted to the host.
+
+The \passthrough{\lstinline!extend commands using an id parameter!}
+strategy is used for different sensors. Each command is extended on the
+\passthrough{\lstinline!network-proxy!}\ref{network-proxy} by another
+\gls{id} parameter, according to the following scheme:
+
+\begin{itemize}
+\tightlist
+\item
+  \passthrough{\lstinline!readsensor <axis> <sensor number>!}-\textgreater{}
+  \passthrough{\lstinline!readsensor <axis> <ID>!}
+\item
+  \passthrough{\lstinline!opmode!}-\textgreater{}
+  \passthrough{\lstinline!opmode <ID>!}
+\end{itemize}
+
+This allows the host to address individual sensors directly via their
+specific \gls{id}.
 

### 2024-01-03 documentation/thesis/thesis_document.tex
more thesis

@@
 \item
-  \textbf{Ready to use hardware sensor designs}
-\item
-  \textbf{Taking automatic measurements from sensors}
-\item
-  \textbf{Ready to use data analysis functions}
-\item
-  \textbf{Open storage formats for data export}
-\item
-  \textbf{Easy software configuration}
-\item
-  \textbf{User expandable data processing pipelines}
+  \textbf{Ready to use hardware sensor designs} A universal,
+  easy-to-integrate Hall sensor design allows users to evaluate the
+  framework quickly and cost-effectively. The pre-built hardware sensors
+  provide an optimal solution for research, reducing development time
+  and achieving repeatable measurement results. Once successfully
+  evaluated, the Hall sensor design should be easily adaptable to other
+  sensors without the need for major firmware changes.
+\item
+  \textbf{Taking automatic measurements from sensors} The purpose of the
+  framework is to enable the automated acquisition of measurement data
+  from various connected hadware sensors. The user should be able to
+  configure various measurement series, which should then be carried out
+  by the framework without further user interaction.
+\item
+  \textbf{Open storage formats for data export} The use of open storage
+  formats for the export of data enables an interoperable data exchange
+  environment. The implementation of standardized formats improves the
+  portability and long-term availability of data. This encourages the
+  exchange and further processing of measurement data in other software
+  tools.
+\item
+  \textbf{Ready to integrate data analysis functions} Once it is
+  possible to record and store measured values, it should be possible
+  for the user to analyse and visualize this data using various
+  algorithms. The focus here should be on extending the framework with
+  user-created algorithms.
+\item
+  \textbf{User programmable data processing pipelines} User-programmable
+  data processing pipelines enable the flexible design of data
+  processing sequences by users. The framework should enable users to
+  create their own Anylse pipelines with the previously defined data
+  analysis functions.
 \end{enumerate}
@@
 
-The main aim of this project is to develop a low-cost Hall sensor
-interface that is also universally expandable. The focus is on mapping
-different sensors and being compatible with different magnet types and
-shapes. This ensures broad applicability in different scenarios. Another
-goal is reproducibility to ensure consistent results. Easy communication
-with standard PC hardware maximises the user-friendliness of the
-interface. The flexibility to support different sensors and magnets
-makes the system versatile and opens up possibilities for different
-applications. A low-cost Hall sensor interface will therefore not only
-be economically attractive, but also facilitate the integration of Hall
-sensors in different contexts. In addition, the low-cost Hall sensor
-interface will serve as a development platform for the data evaluation
-\gls{mrp} library and provide real measurement data from magnets. In
-addition, the interface firmware creates a basis for the development of
-a data protocol for exchanging measured values. This makes it easy to
-integrate your own measuring devices into the \gls{mrp} ecosystem at a
-later date. This is only possible with a minimal functional hardware and
-firmware setup and was developed for this purpose first.
+A defined main objective of this project is the development of a
+cost-effective Hall sensor interface that is also universally
+expandable. The focus is on mapping different sensors and being
+compatible with different magnet types and shapes. This ensures broad
+applicability in different scenarios. Another goal is reproducibility to
+ensure consistent results. Easy communication with standard PC hardware
+maximises the user-friendliness of the interface. The flexibility to
+support different sensors and magnets makes the system versatile and
+opens up possibilities for different applications. A low-cost Hall
+sensor interface will therefore not only be economically attractive, but
+also facilitate the integration of Hall sensors in different contexts.
+In addition, the low-cost Hall sensor interface will serve as a
+development platform for the data evaluation \gls{mrp} library and
+provide real measurement data from magnets. In addition, the interface
+firmware creates a basis for the development of a data protocol for
+exchanging measured values. This makes it easy to integrate your own
+measuring devices into the \gls{mrp} ecosystem at a later date. This is
+only possible with a minimal functional hardware and firmware setup and
+was developed for this purpose first.
 

### 2024-01-07 documentation/thesis/thesis_abstract.tex
more thesis
more thesis - first external review

--- 2023-10-03 documentation/thesis/thesis_abstract.tex
@@
-Especially in the construction of low-field MRI devices based on
-permanent magnets, a large number of magnets are used. In order to
-realize a homogeneous B0 field with these magnets, which is necessary
-for many setups, the magnetic properties of these magnets should be as
-similar as possible.
-
-Due to the complex manufacturing process, especially of neodymium
-magnets, the different properties, especially the direction of
-magnetization, can deviate from each other, which affects the
-homogeneity of the field.
-
-To adjust the field afterwards, a passive shimming process is typically
-performed, which is complex and time-consuming and requires manual
-corrections to the magnets used.
-
-To avoid this process, magnets can be systematically measured in
-advance. However, in this methodology, the recording, data storage and
-subsequent evaluation of the data play an important role.
-
-The various existing solutions implement individual aspects, but do not
-provide a data pipeline from aqusation to analysis.
-
-For this use case, the MagneticReadoutProcessing library was created,
-which implements different aspects of data acquisition, data storage,
-analysis, and each intermediate step can be customized by the user
-without having to create everything from scratch, favoring an exchange
-between different user groups.
+A large number of magnets are used in the construction of low-field MRI
+equipment on the basis of permanent magnets. The magnetic properties of
+these magnets must be similar to a certain degree in order to achieve a
+homogeneous B0 field, which is necessary for many setups. Due to the
+complex manufacturing process of neodymium magnets, the different
+properties, i.e.~the direction of magnetisation, can deviate from each
+other. This affects the homogeneity of the field. A passive shimming
+process is typically used to adjust the field afterwards. This is
+complex and time-consuming and requires manual corrections to the
+magnets used. To avoid this process, magnets can be systematically
+measured in advance. Data acquisition, storage and subsequent analysis
+play an important role in this methodology. Several existing open source
+solutions implement individual parts, but do not provide a complete data
+processing pipeline from acquisition to analysis, and their data storage
+formats are not compatible with each other. For this use case, the
+MagneticReadoutProcessing library has been created. It implements all
+important aspects of acquisition, storage and analysis, and each
+intermediate step can be customised by the user without having to create
+everything from scratch, thus encouraging exchange between different
+user groups. Complete documentation, tutorials and tests enable users to
+use and adapt the framework as quickly as possible. The framework was
+used to characterise different magnets, which requires integrating
+magnetic field sensors.

### 2024-01-07 documentation/thesis/thesis_document.tex
more thesis - first external review

--- 2024-01-02 documentation/thesis/thesis_document.tex
@@
 \hypertarget{shimming-procedure}{%
-\subsection{Shimming procedure}\label{shimming-procedure}}
+\subsection{Shimming Procedure}\label{shimming-procedure}}
 
@@
 \section{Aim of this Thesis}\label{aim-of-this-thesis}}
+
+\ref{usecases}
 
@@
 
-\ref{state-of-the-art}. \textbf{State of the art} describes the current
-state of technology and forms the basis for further development.
-Existing measurement methods and findings are shown here in order to
-define the context for the current project.
-
-\ref{usecases}. \textbf{Usecases} are the application cases in which the
-project is to be used. They illustrate the practical scenarios and
-define how the product can be used in the real world. This is crucial
-for understanding the needs of the target group and designing the end
-result accordingly.
-
-\ref{unified-sensor}. \textbf{Unified Sensor} refers to the integration
-of different sensors into a standardised solution. This enables simple
-data acquisition and serves as a basic hardware system on which the
-subsequent data processing library can be applied.
-
-\ref{software-readout-framework}. \textbf{Software readout framework}
-chapter describes the implementation of the data readout framework. This
-includes an explanation of the various modules and specific application
-examples.
-
-\ref{usability-improvements}. \textbf{Usability improvements} refers to
-measures to improve user-friendliness. This involves optimising
-interfaces, interactions and processes to ensure intuitive and efficient
-use of the product. This includes, code documentation or the
-distribution of source code to users.
-
-\ref{evaluation}. \textbf{Evaluation} comprises the systematic review
-and assessment of the overall system. This includes the demonstration of
-the implemented capabilities of the overall system against the
-previously defined use cases.
+\begin{itemize}
+\item
+  Chapter \ref{state-of-the-art}. \textbf{State of the Art} describes
+  the current state of technology and forms the basis for further
+  development. Existing measurement methods and findings are shown here
+  in order to define the context for the current project.
+\item
+  Chapter \ref{usecases}. \textbf{Usecases} are the application cases in
+  which the project is to be used. They illustrate the practical
+  scenarios and define how the product can be used in the real world.
+  This is crucial for understanding the needs of the target group and
+  designing the end result accordingly.
+\item
+  Chapter \ref{unified-sensor}. \textbf{Unified Sensor} refers to the
+  integration of different sensors into a standardised solution. This
+  enables simple data acquisition and serves as a basic hardware system
+  on which the subsequent data processing library can be applied.
+\item
+  Chapter \ref{software-readout-framework}. \textbf{Software Readout
+  Framework} describes the implementation of the data readout framework.
+  This includes an explanation of the various modules and specific
+  application examples.
+\item
+  Chapter \ref{usability-improvements}. \textbf{Usability Improvements}
+  refers to additional activities to improve user-friendliness. This
+  includes the optimisation of interfaces, interactions and processes to
+  ensure intuitive and efficient use of the product. This also includes
+  the documentation of code and the distribution of the source code as a
+  package to users.
+\item
+  Chapter \ref{evaluation}. \textbf{Evaluation} comprises the systematic
+  review and assessment of the overall system. This includes the
+  demonstration of the implemented capabilities of the overall system
+  against the previously defined usecases.
+\end{itemize}
 
 \hypertarget{state-of-the-art}{%
-\chapter{State of the art}\label{state-of-the-art}}
+\chapter{State of the Art}\label{state-of-the-art}}
 
 \hypertarget{opensource-projects}{%
-\section{Opensource projects}\label{opensource-projects}}
+\section{Opensource Projects}\label{opensource-projects}}
 
 \hypertarget{conceptual-design}{%
-\section{Conceptual design}\label{conceptual-design}}
+\section{Conceptual Design}\label{conceptual-design}}
 
@@
 
+accomplished
+
 \hypertarget{usecases}{%
@@
 
-The following section defines some use cases that the future project
-should be able to cover. They illustrate practical situations and help
-to understand the functionality and added value of the implemented
-project for the user. These were defined in the course of project
-planning and provide an overview of how the user interacts with the
-project and what functionalities can be expected. In the later
-evaluation\ref{evaluation} process, the defined usecases are also used
-as a reference to demonstrate the implemented capabilities of the
-solution.
+The following section defines some usecases that the future project
+should be able to cover. These illustrate practical situations to
+understand the functionality and added value of the implemented solution
+for the user. These were defined in the course of project planning and
+provide an overview of how the user interacts with the project and what
+functionalities can be expected. In the later accomplished evaluation
+process \ref{evaluation}, the defined usecases are also used as a
+reference to demonstrate the implemented capabilities of the solution.
 
@@
 \def\labelenumi{\arabic{enumi}.}
+\tightlist
 \item
   \textbf{Ready to use hardware sensor designs}
+\end{enumerate}
+
+A universal, easy-to-integrate Hall sensor design allows users to
+evaluate the framework quickly and cost-effectively. The pre-built
+hardware sensors provide an optimal solution for research, reducing
+development time and achieving repeatable measurement results. Once
+successfully evaluated, the Hall sensor design should be easily
+adaptable to other sensors without the need for major firmware changes.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
 \item
   \textbf{Taking automatic measurements from sensors}
-\item
-  \textbf{Ready to use data analysis functions}
+\end{enumerate}
+
+The purpose of the framework is to enable the automated acquisition of
+measurement data from various connected hadware sensors. The user should
+be able to configure various measurement series, which should then be
+carried out by the framework without further user interaction.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
 \item
   \textbf{Open storage formats for data export}
-\item
-  \textbf{Easy software configuration}
-\item
-  \textbf{User expandable data processing pipelines}
 \end{enumerate}
+
+The use of open storage formats for the export of data enables an
+interoperable data exchange environment. The implementation of
+standardized formats improves the portability and long-term availability
+of data. This encourages the exchange and further processing of
+measurement data in other software tools.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{3}
+\tightlist
+\item
+  \textbf{Ready to integrate data analysis functions}
+\end{enumerate}
+
+Once it is possible to record and store measured values, it should be
+possible for the user to analyse and visualize this data using various
+algorithms. The focus here should be on extending the framework with
+user-created algorithms.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{4}
+\tightlist
+\item
+  \textbf{User programmable data processing pipelines}
+\end{enumerate}
+
+User-programmable data processing pipelines enable the flexible design
+of data processing sequences as pipeline by users. The framework should
+enable users to create their own pipelines with the previously defined
+data analysis functions.
 
@@
 
-The main aim of this project is to develop a low-cost Hall sensor
-interface that is also universally expandable. The focus is on mapping
-different sensors and being compatible with different magnet types and
-shapes. This ensures broad applicability in different scenarios. Another
-goal is reproducibility to ensure consistent results. Easy communication
-with standard PC hardware maximises the user-friendliness of the
-interface. The flexibility to support different sensors and magnets
-makes the system versatile and opens up possibilities for different
-applications. A low-cost Hall sensor interface will therefore not only
-be economically attractive, but also facilitate the integration of Hall
-sensors in different contexts. In addition, the low-cost Hall sensor
+A defined main objective of this project is the development of a
+cost-effective magnetic field sensors interface that is also universally
+expandable. The focus is on mapping different sensors and being
+compatible with different magnet types and shapes. This ensures broad
+applicability in different scenarios. Another goal is reproducibility to
+ensure consistent results. Easy communication with standard PC hardware
+maximises the user-friendliness of the interface. The flexibility to
+support different sensors and magnets makes the system versatile and
+opens the possibility for use in different applications. A low-cost
+magnetic field sensors interface will therefore not only be economically
+attractive, but also facilitate the integration of magnetic field
+sensors in different contexts. In addition, the low-cost sensor
 interface will serve as a development platform for the data evaluation
@@
 \hypertarget{sensor-selection}{%
-\section{Sensor selection}\label{sensor-selection}}
+\section{Sensor Selection}\label{sensor-selection}}
 
@@
 
-Linear analogue Hall sensors were deliberately omitted, although they
-are suitable for more precise measurements and extended measuring
-ranges. They were excluded due to the more complex circuit layouts
-required and more complex power management. In the context of the
-desired goal of developing a cost-efficient and universally expandable
-Hall sensor interface, the decision in favour of digital sensors seems
+The use of analog sensors was purposefully avoided, though they are
+suitable for more precise measurements and extended measuring ranges.
+They were excluded because they require more carefully designed circuits
+and more complicated energy management. In the context of the desired
+goal of developing a cost-efficient and universally expandable Hall
+sensor interface, the decision in favour of digital sensors seems
 appropriate.
 
+Focussing on the digital \gls{i2c} interface not only facilitates
+implementation, but also contributes to overall cost efficiency. At the
+same time, the integration of temperature sensors enables precise
+measurements under varying environmental conditions. This strategic
+choice forms the basis for a flexible, universally applicable Hall
+sensor interface that can be seamlessly integrated into various existing
+systems.
+
 \begin{longtable}[]{@{}lllll@{}}
-\caption{Implemented digital halleffect sensors
-\label{Implemented_digital_halleffect_sensors.csv}}\tabularnewline
+\caption{Implemented digital magnetic field sensors
+\label{Implemented_digital_magnetic_field_sensors.csv}}\tabularnewline
 \toprule
@@
 
-Focussing on digital interfaces not only facilitates implementation, but
-also contributes to overall cost efficiency. At the same time, the
-integration of temperature sensors enables precise measurements under
-varying environmental conditions. This strategic choice forms the basis
-for a flexible, universally applicable Hall sensor interface that can be
-seamlessly integrated into various existing systems.
-
-The table\ref{Implemented_digital_halleffect_sensors.csv} shows a
+The table \ref{Implemented_digital_magnetic_field_sensors.csv} shows a
 selection of sensors for which hardware and software support has been
@@
 
-The mechanical structure of a sensor is kept very simple for the
-following tests. The focus was on providing a stable foundation for the
-sensor \gls{ic} and an exchangeable holder for different magnets.
-
-The following figure\ref{1D_sensor_mechanical_3D_printed_structure.png},
-shows a sectional view of the \gls{cad} drawing of the
-\passthrough{\lstinline!1D: Single sensor!}\ref{d-single-sensor}.
-
-All parts were produced using the 3D printing process. The sensor
-circuit board was glued underneath the magnet holder. This is
-interchangeable, so different distances between sensor and magnet can be
-realised.
+The mechanical design of a sensor would be kept as simple as possible so
+that it can be replicated as easily as possible. The focus was on
+providing a stable foundation for the sensor \gls{ic} and an
+exchangeable holder for different magnets.
+
+The following figure
+\ref{1D_sensor_mechanical_3D_printed_structure.png}, shows a sectional
+view of the \gls{cad} drawing of the 1D-Single sensor
+\ref{d-single-sensor}.
+
+All parts were produced using the 3D printing additive manufacturing
+processes. The sensor circuit board was glued underneath the magnet
+holder. This is interchangeable, so different distances between sensor
+and magnet can be realised.
 
@@
 different magnets. It can be produced quickly due to the small amount of
-material used. The two recesses lock the holder with the inserted magnet
-over the sensor. Due to predetermined tolerances, the magnet can be
-inserted into the holder with repeat accuracy and without play. This is
-important if several magnets have to be measured, where the positioning
-over the sensor must always be the same.
+parts used. The two recesses lock the magnet holder with the inserted
+magnet over the sensor. The specified tolerances allow the magnet to be
+inserted into the holder with repeat accuracy and without backlash. This
+is important if several magnets have to be measured, where the
+positioning over the sensor must always be the same.
 
@@
 
-As with the mechanical design, the electronics should be kept as simple
-as possible so that it is possible to use the microcontroller and a
-magnetic field sensor.
+The electronics consist of the magnetic field sensor and the electrical
+interface to connect it to a \gls{pc} in the form of a microcontroller.
 
@@
 evaluation boards, which already integrate all the components required
-for smooth operation. This not only enabled a time-saving
-implementation, but also ensured a cost-efficient realisation.
-
-A decisive step in my work was the in-house PCB
-design\ref{1D_sensor_schematic_and_circuit_board.png}, which leads out
-all the important connections. The placement and alignment of components
-optimised the wiring, which in turn improved the reliability of the
-sensor tests. Particular attention was paid to the implementation of a
-\passthrough{\lstinline!SYNC!}-\gls{gpio}, which enables subsequent
-multi-sensor synchronisation. This functionality opens up the
-possibility of synchronising data from different sensors to achieve
-precise and coherent measurement results. Overall, this integrated
-approach represents an effective solution for the flexible evaluation of
-sensors and helps to optimise the development process.
+for basic operation. This not only enabled a time-saving implementation,
+but also ensured a cost-efficient realisation.
+
+All the necessary components and their circuitry were then recorded on a
+\gls{pcb} \ref{1D_sensor_schematic_and_circuit_board.png} and
+subsequently manufactured. In addition, footprints were provided for
+various sensor \gls{ic} packages. By placing mounting holes on the
+\gls{pcb}, it is possible to attach various mechanical mounts ontop of
+the sensor \gls{ic}s.
+
+Special attention was paid to the provision of an accessible
+SYNC-\gls{gpio} connector. This enables subsequent multi-sensor
+synchronization and also offers options for later extensions. This
+functionality opens up the possibility of synchronising data from
+different sensors to achieve precise and coherent measurement results.
+Overall, this integrated approach represents an effective solution for
+the flexible evaluation of sensors and helps to optimise the development
+process.
 
@@
 
-Microcontroller firmware is software that is executed on a
-microcontroller in embedded systems. It controls the hardware and
+The microcontroller firmware is software that is executed on a
+microcontroller in an embedded system. It controls the hardware and
 enables the execution of predefined functions. The firmware is used to
-process input data, control output devices and fulfil specific tasks
+process input data, control output devices and performs specific tasks
 according to the program code. It handles communication with sensors,
@@
 
-The firmware is responsible for detecting the possible connected
-sensors\ref{Implemented_digital_halleffect_sensors.csv} and reading them
-out. This measured data can be forwarded to a host \gls{pc} via a user
-interface and can then be further processed there.
+The firmware is responsible for detecting the possible connected sensors
+\ref{Implemented_digital_magnetic_field_sensors.csv} and query
+measurements. This measured data can be forwarded to a host \gls{pc} via
+a user interface and can then be further processed there.
 
@@
 easily connected without having to adapt the firmware. This modularity
-was implemented using \passthrough{\lstinline!abstract!} class design.
-These are initiated according to the sensors found at startup. If new
-hardware is to be integrated, only the required
-functions\ref{lst:CustomSensorClass} need to be implemented.
+was implemented using abstract class design. These are initiated
+according to the sensors found at startup. If new hardware is to be
+integrated, only the required functions \ref{lst:CustomSensorClass} need
+to be implemented.
 
@@
 
-The flow
-chart\ref{Unified_sensor_firmware_simplified_program_strucutre.png}
-shows the start process and the subsequent main loop for processing the
-user commands and sensor results. When the microcontroller is started,
-the software checks whether known sensors are connected to \gls{i2c} or
+The flow chart
+\ref{Unified_sensor_firmware_simplified_program_strucutre.png} shows the
+start process and the subsequent main loop for processing the user
+commands and sensor results. When the microcontroller is started, the
+software checks whether known sensors are connected to \gls{i2c} or
 \gls{uart} interfaces. If any are found (using a dedicated \gls{lut}
-with sensor address information), the appropriate class instances are
-created and these can later be used to read out measurement results.
-
-Next, the subsystem for multi-sensor
-synchronisation\ref{sensor-syncronsisation-interface} is set up. The
-last step in the setup is to set up communication with the host or
-connected \gls{pc}. All microcontroller platforms used here have a
-\gls{usb} slave port. The used usb descriptor is
-\passthrough{\lstinline!Serial over (+usb)!}-((+usb)\gls{cdc}). This is
-used to emulate a virtual RS232 communication port using a \gls{usb}
-port on a \gls{pc} and usually no additional driver is needed on modern
-systems.
-
-Now that the setup process is complete, the system switches to an
-infinite loop, which processes several possible actions. One task is, to
-react to user commands which can be sent to the system by the user via
-the integrated \gls{cli}. All sensors are read out via a timer interval
-set in the setup procedure and their values are stored in a ringbuffer.
-Ring buffers, offer efficient data management in limited memory. Its
-cyclic structure enables continuous overwriting of older data, saves
-memory space and facilitates seamless processing of real-time data.
+with sensor address translation information), the appropriate class
+instances are created and these can later be used to read out
+measurement results.
+
+The next initialisation system is dedicated for multi-sensor
+synchronisation \ref{sensor-syncronsisation-interface}. The last step in
+the setup is to configure communication with the host or connected
+\gls{pc}. All implemented microcontroller platforms used (Raspberry Pi
+Pico, STM32F4) have a \gls{usb} slave port. The used usb descriptor is a
+\gls{usb} \gls{cdc}. This is used to emulate a virtual RS232
+communication port using a \gls{usb} port on a \gls{pc} and usually no
+additional driver is needed on modern host systems.
+
+After the setup process is complete, the system switches to an infinite
+loop, which processes several possible actions. One task is, to react to
+user commands which can be sent to the system by the user via the
+integrated \gls{cli}. All sensors are read out via a timer interval set
+in the setup procedure and their values are stored in a ringbuffer. Ring
+buffer offers efficient data management in limited memory. Its cyclic
+structure enables continuous overwriting of older data, saves memory
+space and facilitates seamless processing of real-time data.
 
@@
 ensures that in a multi-sensor setup with several sensors. The
-measurements are synchronized\ref{sensor-syncronsisation-interface} in
+measurements are synchronized \ref{sensor-syncronsisation-interface} in
 time and are not out of sequence or drift.
@@
 \item
-  Use with \gls{mrp}-library\ref{software-readout-framework}
+  Use with \gls{mrp} \ref{software-readout-framework}-libaray
 \item
@@
 behaves like terminal programmes, displaying a detailed command
-reference\ref{Sensors_(+cli).png} to the user after connecting. The
+reference \ref{Sensors_(+cli).png} to the user after connecting. The
 current measured value can be output using the
@@
 
-The other option is to use the \gls{mrp}-library. The serial interface
-is also used here. However, after a connection attempt by the
-\passthrough{\lstinline!MRPHal!} module\ref{hal} of the
-\gls{mrp}-library, the system switches to binary mode, which is
-initiated using the \passthrough{\lstinline!sbm!} command. The same
-commands are available as for \gls{cli}-based communication.
+The other option is to use the \gls{mrp}
+\ref{software-readout-framework}-library. The serial interface is also
+used here. However, after a connection attempt by the
+\passthrough{\lstinline!MRPHal!}\ref{hal} module of the \gls{mrp}
+\ref{software-readout-framework}-library, the system switches to binary
+mode, which is initiated using the \passthrough{\lstinline!sbm!}
+command. The same commands are available as for \gls{cli}-based
+communication.
 
@@
 
-\begin{longtable}[]{@{}llllll@{}}
+\begin{longtable}[]{@{}lllll@{}}
 \caption{Measured sensor readout to processing using host software
@@
 \toprule
-\begin{minipage}[b]{0.02\columnwidth}\raggedright
-Run\strut
-\end{minipage} & \begin{minipage}[b]{0.04\columnwidth}\raggedright
-Points\strut
-\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright
-Host software runtime {[}ms{]}\strut
-\end{minipage} & \begin{minipage}[b]{0.32\columnwidth}\raggedright
+\begin{minipage}[b]{0.08\columnwidth}\raggedright
+Data-Points\strut
+\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\raggedright
+Run runtime {[}ms{]}\strut
+\end{minipage} & \begin{minipage}[b]{0.35\columnwidth}\raggedright
 Average Sensor communication time per reading {[}ms{]}\strut
-\end{minipage} & \begin{minipage}[b]{0.20\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{0.22\columnwidth}\raggedright
 Communication jitter time {[}ms{]}\strut
-\end{minipage} & \begin{minipage}[b]{0.09\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
 Comment\strut
@@
 \endhead
-\begin{minipage}[t]{0.02\columnwidth}\raggedright
+\begin{minipage}[t]{0.08\columnwidth}\raggedright
 1\strut
-\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
-1\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
 9453\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 1.44\strut
-\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
 0\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright
-2\strut
-\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
+\begin{minipage}[t]{0.08\columnwidth}\raggedright
 1\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
 9864\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 1.5\strut
-\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
 0\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright
-3\strut
-\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
+\begin{minipage}[t]{0.08\columnwidth}\raggedright
 10\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
 12984\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 1.22\strut
-\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
 0.9\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright
-4\strut
-\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
+\begin{minipage}[t]{0.08\columnwidth}\raggedright
 10\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
 12673\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 1.13\strut
-\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
 1.1\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
 \strut
 \end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright
-5\strut
-\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
+\begin{minipage}[t]{0.08\columnwidth}\raggedright
 10\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright
 43264\strut
-\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
 2.19\strut
-\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
 8.2\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
 96\% system load\strut
@@
 \item
-  \passthrough{\lstinline!Raspberry Pi OS Lite!} -
-  \passthrough{\lstinline!debian bookworm x64!},
-\item
-  \gls{mrp}\ref{software-readout-framework}-library - version
+  Raspberry Pi OS Lite - \passthrough{\lstinline!debian bookworm x64!},
+\item
+  \gls{mrp} \ref{software-readout-framework}-library - version
   \passthrough{\lstinline!1.4.1!}
 \item
-  \passthrough{\lstinline!Unified Sensor Firmware!}\ref{unified-sensor}
-  - version \passthrough{\lstinline!1.0.1!}
+  Unified Sensor \ref{unified-sensor}-firmware - version
+  \passthrough{\lstinline!1.0.1!}
 \end{itemize}
@@
 
-The other issue is sending the trigger signal from the readout
-software\ref{software-readout-framework}. Here too, unpredictable
-latencies can occur, depending on which other tasks are also executed on
-this port.
+The other issue is sending the trigger signal from the readout software
+\ref{software-readout-framework}. Here too, unpredictable latencies can
+occur, depending on which other tasks are also executed on this port.
 
@@
 electrical connection between sensors. This is used together with the
-firmware to synchronise the readout intervals. The
-schematic\ref{Multi_sensor_synchronisation_wiring_example.png} shows how
-several sensors must be wired together in order to implement this form
-of synchronisation.
+firmware to synchronise the readout intervals. The schematic
+\ref{Multi_sensor_synchronisation_wiring_example.png} shows how several
+sensors must be wired together in order to implement this form of
+synchronisation.
 
@@
 various sensors is to find a common synchronisation clock. To do this,
-the \passthrough{\lstinline!register irq on sync pin!} is overwritten.
-To set one \passthrough{\lstinline!primary!} and several
+the function \passthrough{\lstinline!register irq on sync pin!} is
+overwritten. To set one \passthrough{\lstinline!primary!} and several
 \passthrough{\lstinline!secondary!} sensors, each sensor waits for an
-intial pulse on the
-sync-pin\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
+intial pulse on the SYNC-\gls{gpio}
+\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
 Each sensor starts a random timer beforehand, which sends a pulse on the
@@
 \passthrough{\lstinline!primary!} sensor cannot register its own sync
-pulse (because the pin is switched to output), there is a timeout
-\passthrough{\lstinline!got pulse within 1000ms!} and this becomes the
-\passthrough{\lstinline!primary!} sensor. This means that in a chain of
-sensors there is exactly one \passthrough{\lstinline!primary!} and many
+pulse (because the pin is switched to output), there is a timeout branch
+condition \passthrough{\lstinline!got pulse within 1000ms!} and this
+becomes the \passthrough{\lstinline!primary!} sensor. This means that in
+a chain of sensors there is exactly one
+\passthrough{\lstinline!primary!} and many
 \passthrough{\lstinline!secondary!} sensors. In single-sensor operation,
@@
 operation through the
-\passthrough{\lstinline!got impulse within 1000ms!} query. The
-synchronisation status can be queried via the user
-interface\ref{communication-interface} using the
+\passthrough{\lstinline!got impulse within 1000ms!} branch result. The
+synchronisation status can be queried via the user interface
+\ref{communication-interface} using the
 \passthrough{\lstinline!opmode!}\ref{Query_opmode_using_(+cli).png}
@@
 that they are taken at the same interval across all sensors. The sensor
-differentiation takes place later in the readout
-software\ref{software-readout-framework} by using the sensor
-identification number.
+differentiation takes place later in the \gls{mrp}
+\ref{software-readout-framework}-library by using the sensor \gls{id}.
 
@@
 
-Two functional sensor
-platforms\ref{Build_sensors_with_different_capabilities.csv} were built
-in order to create a solid test platform for later tests and for the
-development of the \gls{mrp} library with the previously developed
-sensor concepts.
+Two functional sensor platforms
+\ref{Build_sensors_with_different_capabilities.csv} were built in order
+to create a solid test platform for later tests and for the development
+of the \gls{mrp} \ref{software-readout-framework}-library with the
+previously developed sensor concepts.
 
@@
 
-These cover all the required functions described in the
-Usecases\ref{usecases}. The most important difference, apart from the
-sensor used, is the \passthrough{\lstinline!scan mode!}. In this
-context, this describes whether the sensor can measure a
+These cover all the required functions described in the usecases
+\ref{usecases}. The most important difference, apart from the sensor
+used, is the \passthrough{\lstinline!scan mode!}. In this context, this
+describes whether the sensor can measure a
 \passthrough{\lstinline!static!} fixed point on the magnet or if the
@@
 
-The \passthrough{\lstinline!1D!}
-sensor\ref{1D_sensor_construction_with_universal_magnet_mount.png} is
-the simplest possible sensor that is compatible with the
-\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} platform
-and also with the \gls{mrp}-library\ref{software-readout-framework}.
+The 1D sensor
+\ref{1D_sensor_construction_with_universal_magnet_mount.png} is the
+simplest possible sensor that is compatible with the Unified Sensor
+firmware \ref{firmware} platform.
 
@@
 \passthrough{\lstinline!MMC5603NJ!} magnetic sensor. The mechanical
-setup consists of four 3D-printed components, which are fixed together
+setup consists of four 3D printed components, which are fixed together
 with nylon screws to minimise possible influences on the measurement.
 
-Since the \passthrough{\lstinline!MMC5603NJ!} only has very limited
-measuring range, even small neodymium magnets already saturate its
-range, it is possible to use 3D-printed spacers above the sensor.
-
-The standard magnet holder can be adapted for different magnet shapes
-and can be placed on the spacer without play in order to be able to
+Since the \passthrough{\lstinline!MMC5603NJ!} only has limited
+measurement range of total \passthrough{\lstinline!6uT!}, even small
+coin sized neodymium magnets already saturates the sensor. It is
+possible to mount 3D printed spacers over the sensor to increase the
+distance between the magnet and the sensor and thus also measure these
+magnets.
+
+The designed magnet holder can be adapted for different magnet shapes
+and can be placed on the spacer without backlash in order to be able to
 perform a repeatable measurement without introducing measurement
@@
 
-The
-\passthrough{\lstinline!3D Fullsphere!}\ref{Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
-sensor offers the possibility to create a 3D
-map\ref{3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}
-of the magnets. The magnet sensor is mounted on a movable arm, which can
-move 180 degrees around the magnet on one axis. In order to be able to
-map the full sphere, the magnet is mounted on a turntable. This permits
-the manipulator to move a polar coordinate system.
+The 3D fullsphere sensor
+\ref{Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
+offers the possibility to create a 3D map of the inserted magnet.
+
+The graphic
+\ref{3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}
+shows the visualisation of such a scan in the form of a spherical 3D
+map. On the sphere is the magnetic field strength, which was detected by
+the sensor at the position. The transition from a fully positive field
+strength (red) to a negative field strength (blue) is clearly
+recognisable and corresponds to the orientation of the magnet in the
+holder.
+
+The magnet sensor is mounted on a movable arm, which can move 180
+degrees around the magnet on one axis. In order to be able to map the
+full sphere, the magnet is mounted on a turntable. This permits the
+manipulator to move a polar coordinate system.
 
@@
 On the electrical side, it also consists of a
-\passthrough{\lstinline!SKR Pico!} stepper motor controller, together
+\passthrough{\lstinline!SKR-Pico!} stepper motor controller, together
 with the \passthrough{\lstinline!TLV493D!} magnetic field sensor. This
@@
 hardware, the following section shows how existing hardware can be
-integrated into the system. This is shown here using a
-temperature-compensated \passthrough{\lstinline!Voltcraft GM-70!}
-telsameter\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png},
-which has a measuring range of \passthrough{\lstinline!0-3T!} with a
-resolution of 0.1mT. It offers an \passthrough{\lstinline!RS232!}
-interface with a documented
-protocol\ref{Voltcraft_GM70_serial_protocol.csv} for connection to a
-\gls{pc}. This connectivity makes it possible to make the device
-compatible with the \gls{mrp} library using interface software
+integrated into the system. A temperature-compensated
+\passthrough{\lstinline!Voltcraft GM-70!} telsameter
+\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
+used, which has a measuring range of \passthrough{\lstinline!0-3T!} with
+a resolution of \passthrough{\lstinline!0.1mT!}. It offers an
+\passthrough{\lstinline!RS232!} interface with a documented protocol
+\ref{Voltcraft_GM70_serial_protocol.csv} for connection to a \gls{pc}.
+This connectivity makes it possible to make the device compatible with
+the Unified Sensor ecosystem using a separate interface software
 \cite{VoltcraftGM70Rest} executable on the host \gls{pc}. However,
-it does not offer the range of functions that the
-\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} offers.
+it does not offer the range of functions that the Unified Sensor
+firmware offers.
 
@@
 This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
-offer an \passthrough{\lstinline!RS232!} interface. As with the other
-sensors, this interface consists of your
+offer an physical \passthrough{\lstinline!RS232!} interface. As with the
+other sensors, this interface consists of your
 \passthrough{\lstinline!RaspberryPi Pico!} with an additional level
 shifter. The Teslameter is connected to the microcontroller using two
-free \gls{gpio}s in \gls{uart} mode. The
-\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} was
-adapted using a separate build configuration and the protocol of the
-measuring device was implemented.
+free \gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
+separate build configuration and the protocol of the measuring device
+was implemented.
 
@@
 
-\hypertarget{multible-sensor-setup}{%
-\section{Multible sensor setup}\label{multible-sensor-setup}}
-
-At the current state of implementation, it is only possible to detect
-and use sensors that are directly connected to the \gls{pc} with the
+\hypertarget{multi-sensor-setup}{%
+\section{Multi Sensor Setup}\label{multi-sensor-setup}}
+
+At the current described scenarios, it is only possible to detect and
+use sensors that are directly connected to the \gls{pc} with the
 \gls{mrp}-library. It has the disadvantage that there must always be a
@@
 sensors in measurement setups where space or cable routing options are
-limited. To make sensors connected to a small
-\passthrough{\lstinline!remote!} \gls{pc} available on the network, the
-\passthrough{\lstinline!Proxy!}\ref{MRPlib_Proxy_Module.png} module has
-been developed. This can be a \gls{sbc} (e.g.~a Raspberry Pi). The small
+limited. So multibe sensor can be connected to a
+\passthrough{\lstinline!remote!} \gls{pc} which is available on the
+network. This can be a \gls{sbc} (e.g.~a Raspberry Pi). The small
 footprint and low power consumption make it a good choice. It can also
-be used in a temperature chamber. The approach of implementing this via
-a \gls{rest} interface also offers the advantage that several
-measurements or experiments can be recorded at the same time with the
-sensors.
+be used in a temperature chamber.
+
+The \passthrough{\lstinline!MRPProxy!}\ref{MRPlib_Proxy_Module.png}
+module has been developed to allow forwarding and interaction with
+several sensors over a network connection using a \gls{rest} interface.
+
+The approach of implementing this via a \gls{rest} interface also offers
+the advantage that several measurements or experiments can be recorded
+at the same time with one remote sensor setup.
 
@@
 both proxy instances do not communicate directly with the
-\passthrough{\lstinline!control!} \gls{pc}, but
-\passthrough{\lstinline!remote!}\gls{pc}\passthrough{\lstinline!\#2!} is
-connected to
+\passthrough{\lstinline!control!} \gls{pc}, but the proxy instance
+\passthrough{\lstinline!remote!}\gls{pc}\passthrough{\lstinline!\#2!}
+can acces the proxy running on
 \passthrough{\lstinline!remote!}\gls{pc}\passthrough{\lstinline!\#1!}.
-This is then visible as a sensor opposite the Control \gls{pc}, even if
-there are several proxy instances behind it.
+
+The \passthrough{\lstinline!control!} \gls{pc} only communicates with
+the \passthrough{\lstinline!remote!} \gls{pc}
+\passthrough{\lstinline!\#1!}, but can access all sensors in this chain.
 
@@
 with the remote side via the network. For the user, nothing changes in
-the procedure for setting up a measurement. The proxy application must
-always be started\ref{lst:mrpcli_proxy_start} on the
-\passthrough{\lstinline!remote!} \gls{pc} side.
+the procedure for setting up a measurement. The
+\passthrough{\lstinline!MRPProxy!} \gls{cli} application must always be
+started \ref{lst:mrpcli_proxy_start} on the \gls{pc} with connected
+hardware sensors attached.
 
@@
 After the proxy instance has been successfully started, it is optionally
-possible to check the status via the \gls{rest}
-interface:\ref{lst:mrpcli_config_rest}
-
-\begin{lstlisting}[language=bash, caption={MRPproxy REST enpoiint query examples}, label=lst:mrpcli_config_rest]
+possible to check the status via the \gls{rest} interface:
+\ref{lst:mrpcli_config_rest}
+
+\begin{lstlisting}[language=bash, caption={MRPProxy REST endpoint query examples}, label=lst:mrpcli_config_rest]
 # GET PROXY STATUS
@@
 their capabilites have also been recognised correctly. To be able to
-configure a measurement on the other, only the \gls{ip} address or host
-name of the remote \gls{pc} is
+configure a measurement on the \passthrough{\lstinline!control!}
+\gls{pc}, only the \gls{ip} address or hostname of the \gls{pc} running
+an \passthrough{\lstinline!MRPProxy!} instance is
 required\ref{lst:mrpcli_config_using_rpc}.
@@
 other via their sync input using short cables. One sensor acts as the
-central clock as described in\ref{sensor-syncronsisationiinterface}.
+central clock as described in \ref{sensor-syncronsisationiinterface}.
 this no longer works for long distances and the syncronisation must be
-made via the network connection.
+made via a shared network connection.
 
@@
 
-As it is possible to connect many identical sensors to one host using
-the \passthrough{\lstinline!Network-Proxy!}\ref{network-proxy}, it must
+As it is possible to connect many identical sensors to one host, it must
 be possible to address them separately. This separation is done by the
-\passthrough{\lstinline!MRPProxy.proxy!} module and is therefore not
-part of the core \gls{mrp} library.
-
-Each connected sensor is addressed via the text-based \gls{cli} or the
-binary interface, this is initially the same for each sensor. The only
-identification feature is the sensor \gls{id}.
-
-The \passthrough{\lstinline!Network-Proxy!}\ref{network-proxy} instance
-pretends to be a sensor to the \gls{mrp} host, so the multiple sensors
-must be combined into one. This is done in several steps, in the
-\passthrough{\lstinline!Network-Proxy!}\ref{network-proxy} start
-procedure:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  \textbf{Construct the Sensor ID LookUp-Table}
-\end{enumerate}
-
-Immediately after starting the
-\passthrough{\lstinline!network-proxy!}\ref{network-proxy}, the
+\passthrough{\lstinline!MRPProxy!} module and is a separate part from
+the core \gls{mrp}-library, to keep installation package dependencies
+small.
+
+Each connected sensor is accessed via the text-based \gls{cli}, this is
+initially the same for each sensor. The only identification feature is
+the sensor \gls{id} by using the \passthrough{\lstinline!id!} command of
+the sensor \gls{cli}.
+
+The \passthrough{\lstinline!MRPProxy!} instance claims to be a sensor to
+the host \gls{pc} running \gls{mrp} \gls{cli}, so the multiple sensors
+must be combined into one virtual one. This is done in several steps,
+start procedure described by the following sub-chapters.
+
+\hypertarget{construct-the-sensor-id-lookup-table}{%
+\subsubsection{Construct the Sensor ID
+LookUp-Table}\label{construct-the-sensor-id-lookup-table}}
+
+Immediately after starting the \passthrough{\lstinline!MRPProxy!}, the
 \gls{id}s of all locally connected sensors are read out. These are
-stored together with the instance of the
+stored together with the class instance of the
 \passthrough{\lstinline!MRPHal!} module in a \gls{lut}. This makes it
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  \textbf{Merging the sensor capabilities}
-\end{enumerate}
+\hypertarget{merging-the-sensor-capabilities}{%
+\subsubsection{Merging the sensor
+capabilities}\label{merging-the-sensor-capabilities}}
 
@@
 previously created \gls{lut}. Duplicate entries are summarized (see
-Table:\ref{Sensor_capabilities_merging.csv}) and returned to the host
+Table \ref{Sensor_capabilities_merging.csv}) and returned to the host
 when the \passthrough{\lstinline!info!}\ref{lst:mtsc} command is
@@
 \passthrough{\lstinline!commands!} \gls{cli}-command of each sensor, to
-merge to available commands of connected sensors into the \gls{lut}.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  \textbf{Dynamic extension of the available network proxy commands} In
-  order for the host to be able to send a command to the network
+merge available commands of connected sensors into the \gls{lut}.
+
+\hypertarget{dynamic-extension-of-the-available-network-proxy-commands}{%
+\subsubsection{Dynamic extension of the available network proxy
+commands}\label{dynamic-extension-of-the-available-network-proxy-commands}}
+
+In order for the host to be able to send a command to the network
 multi-sensor setup, the command received must be forwarded to the
 correct sensor. In addition, there are commands such as the previously
-  used \passthrough{\lstinline!info!} or
-  \passthrough{\lstinline!status!} command, which must be intercepted by
-  the \passthrough{\lstinline!MRPProxy!} module so that it can be
-  handled differently (see example \ref{lst:mtsc}).
-\end{enumerate}
+used \passthrough{\lstinline!info!} or \passthrough{\lstinline!status!}
+command, which must be intercepted by the
+\passthrough{\lstinline!MRPProxy!} module so that it can be handled
+differently (see example \ref{lst:mtsc}).
 
@@
 strategy is used for different sensors. Each command is extended on the
-\passthrough{\lstinline!network-proxy!}\ref{network-proxy} by another
+\passthrough{\lstinline!Network-Proxy!}\ref{network-proxy} by another
 \gls{id} parameter, according to the following scheme:
@@
 
-The following shows some examples of how the \gls{mrp} library can be
+The following shows some examples of how the \gls{mrp}-library can be
 used. These examples are limited to a functional minimum for selected
-modules of the \gls{mrp} library. The documentation\ref{documentation}
+modules of the \gls{mrp}-library. The documentation \ref{documentation}
 contains further and more detailed examples. Many basic examples are
-also supplied in the form of test cases\ref{tests}.
+also supplied in the form of the test scripts used for testing
+\ref{testing}.
 
@@
 
-The \passthrough{\lstinline!MRPReading!} module is the cornerstone of
-the \gls{mrp} library. It is used to manage the measurement data and can
-be imported and exported. The following
-example\ref{lst:mrpexample_reading} shows how a measurement is created
-and measurement points are added in the form of
+The \passthrough{\lstinline!MRPReading!} is the key module of the
+\gls{mrp} core. It is used to manage the measurement data and can be
+imported and exported. The following example
+\ref{lst:mrpexample_reading} shows how a measurement is created and
+measurement points are added in the form of
 \passthrough{\lstinline!MRPReadingEntry!} instances. An important point
@@
 be converted into an open \gls{json} format. This file can then be
-imported again at a later date using
-\passthrough{\lstinline!load\_from\_file!}.
+imported again using the \passthrough{\lstinline!load\_from\_file!}
+function.
 
@@
 After generating simple measurements with random values in the previous
-example\ref{mrpreading}, the next step is to record real sensor data.
+example \ref{mrpreading}, the next step is to record real sensor data.
 For this purpose, the \passthrough{\lstinline!MRPHal!} module was
@@
 \passthrough{\lstinline!Unified Sensor!}\ref{unified-sensor}-compatible
-sensors. In the following example\ref{lst:mrpexample_hal}, an
+sensors. In the following example \ref{lst:mrpexample_hal}, an
 \passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor} is
-connected locally to the host-\gls{pc}.
+connected locally to the host \gls{pc}.
 
@@
 fields. The result is a complete \passthrough{\lstinline!MRPReading!}
-measurement with a wide range of set meta data. The
-example\ref{lst:mrpexample_simulation} illustrated the basic usage.
-Different variations of the \passthrough{\lstinline!generate\_reading!}
-function offers the user additional parameterisation options, such as
-random polarisation direction or a defined centre-of-gravity vector. The
-data is generated in the background using the
+measurement with a wide range of set meta data. The example
+\ref{lst:mrpexample_simulation} illustrated the basic usage. Different
+variations of the \passthrough{\lstinline!generate\_reading!} function
+offers the user additional parameterisation options, such as random
+polarisation direction or a defined centre-of-gravity vector. The data
+is generated in the background using the
 \passthrough{\lstinline!magpylib!}\cite{ortner2020magpylib} library
@@
 Once data can be acquired using hardware or software sensors, the next
-step is to analyse this data. The \gls{mrp} library provides some simple
-analysis functions for this purpose. The code example shows the basic
-use of the module. The
-\passthrough{\lstinline!Evaluation!}\ref{evaluation} chapter shows how
-the user can implement their own algorithms and add them to the library.
+step is to analyse this data. \gls{mrp} provides some simple analysis
+functions for this purpose. The code example shows the basic use of the
+module. The \textbf{Evaluation}\ref{evaluation} chapter shows how the
+user can implement their own algorithms and add them to the library.
 
@@
 \passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere} sensor. The
-sub-module `MRPPolarVisualisation' is specially designed for these. The
-figure\ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
+sub-module \passthrough{\lstinline!MRPPolarVisualisation!} is specially
+designed for these. The figure
+\ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
 shows a plot of a fullsphere measurement.
@@
 graphically as diagrams. The \passthrough{\lstinline!MRPVisualisation!}
-modules are used here. The following
-example\ref{lst:mrpexample_visualisation} shows the use of both modules.
+modules are used here. The following example
+\ref{lst:mrpexample_visualisation} shows the usage of both modules.
 
@@
 
-The following example code\ref{lst:mrpexample_hallbach}, shows how a
-simple Hallbach magnetic ring can be generated. Eight random
+The following example code \ref{lst:mrpexample_hallbach}, shows how a
+simple hallbach magnetic ring can be generated. Eight random
 measurements are generated here. It is important that the magnet type
@@
 \passthrough{\lstinline!OpenSCAD!}-\gls{cli} utility, the following
-model
-rendering\ref{Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}
+model rendering
+\ref{Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}
 can be generated.
@@
 structured code examples and improved error messages promote a smooth
-developer experience. Standardised naming conventions and well
-thought-out default values simplify the application. A \gls{gui} or
-\gls{cli} application for complex libraries can make it easier to use,
-especially for developers with less experience. Continuous feedback
-through automated tests and comprehensive error logs enable faster bug
-fixing. The integration of community feedback and regular updates
-promotes the adaptability of the \gls{mrp}-library to changing needs.
-Effective usability improvements help to speed up development processes
-and increase the satisfaction of the developer community. In the
-following, some of these have been added in and around the
-\gls{mrp}-library, but they are only optional components for the
+developer experience. A \gls{gui} or \gls{cli} application for complex
+libraries can make it easier to use, especially for developers with less
+experience. Continuous feedback through automated tests and
+comprehensive error logs enable faster bug fixing. The integration of
+user feedback and regular updates promotes the adaptability of the
+\gls{mrp}-library. Effective usability improvements help to speed up
+development processes and increase the satisfaction of the developer
+community. In the following, some of these have been added in and around
+the \gls{mrp}-library, but they are only optional components for the
 intended use.
@@
 
-In the first version of this \gls{mrp}-library, the user had to write
-his own Python scripts even for short measurement and visualisation
-tasks. However, this was already time-consuming for reading out a sensor
-and configuring the measurement parameters and metadata and quickly
-required more than 100 lines of new Python code. Although such examples
-are provided in the documentation, it must be possible for programming
+In the first version of the \gls{mrp}-library, the user had to write his
+own Python scripts even for short measurement and visualisation tasks.
+However, this was already time-consuming for reading out a sensor and
+configuring the measurement parameters and metadata and quickly required
+more than 100 lines of new Python code. Although such examples are
+provided in the documentation, it must be possible for programming
 beginners in particular to use them. To simplify these tasks, a
-\gls{cli}\ref{example_measurement_analysis_pipeline.png} was implemented
-around this \gls{mrp}-library. The (+mrp)-library-\gls{cli} implements
-the following functionalities:
+\gls{cli} \ref{example_measurement_analysis_pipeline.png} was
+implemented. The libaray \gls{cli} implements the following
+functionalities:
 
@@
 and run it at the end. The result is then an exported file with the
-measured values. These can then be read in again with the
-\gls{mrp}-library and processed further. The following bash
-code\ref{lst:mrpcli_config_run} shows the setup procedure in detail:
+measured values. These can then be read in again using the
+\passthrough{\lstinline!MRPReading!} module and processed further. The
+following bash code \ref{lst:mrpcli_config_run} shows the setup
+procedure in detail:
 
@@
 
-After it is very easy for users to carry out measurements using the
+After it is easy for users to carry out measurements using the
 \gls{cli}, the next logical step is to analyse the recorded data. This
@@
 enables the user to create and execute complex evaluation pipelines for
-measurement data without programming. The
-example\ref{example_measurement_analysis_pipeline.png} shows a typical
+measurement data without programming. The example
+\ref{example_measurement_analysis_pipeline.png} shows a typical
 measurement data analysis pipeline, which consists of the following
@@
 \passthrough{\lstinline!yaml!} file format was chosen for the definition
-of the pipeline, as this is easy to understand and can also be easily
-edited with a text editor. Detailed examples can be found in the
+of the pipeline, as this is for non programmers to understand and can
+also be easily edited with a plain text editor. Detailed examples can be
+found in the
 documentation\cite{MagneticReadoutProcessingReadTheDocs}. The
@@
 This system makes almost all Python functions available to the user. To
-simplify use, a pre-defined list of tested \gls{mrp} library functions
-for use in pipelines is listed in the
+simplify use, a pre-defined list of verified functions for use in
+pipelines is listed in the
 documentation\cite{MagneticReadoutProcessingReadTheDocs}. The
-following pipeline definition\ref{lst:mrpuddp_example_yaml} shows the
-previously defined steps\ref{example_measurement_analysis_pipeline.png}
+following pipeline definition \ref{lst:mrpuddp_example_yaml} shows the
+previously defined steps \ref{example_measurement_analysis_pipeline.png}
 as \passthrough{\lstinline!yaml!} syntax.
 
-\begin{lstlisting}[caption={Example User Defined Processing Pipeline}, label=lst:mrpuddp_example_yaml]
+\begin{lstlisting}[caption={Example YAML code of an user defined processing pipeline with six stages linked together}, label=lst:mrpuddp_example_yaml]
 stage import_readings:
@@
 The various steps are then linked by using the
-\passthrough{\lstinline!stage <name>!} as the input parameter of the
+\passthrough{\lstinline!stage <name>!} makro as input parameter of the
 next function to be executed (see comments in
@@
 steps and repeated traversal, the final execution sequence can be
-determined in the form of a call
-tree\ref{Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}.
+determined in the form of a call tree
+\ref{Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}.
 The individual steps are then executed along the graph. The intermediate
-results and the final
-results\ref{pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
+results and the final results
+\ref{pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
 are saved for optional later use.
 
-\hypertarget{tests}{%
-\section{Tests}\label{tests}}
+\hypertarget{testing}{%
+\section{Testing}\label{testing}}
 
@@
 During the development of the \gls{mrp}-library, test cases were also
-created for all important functionalities and use cases. The test
+created for all important functionalities and usecases. The test
 framework \passthrough{\lstinline!PyTest!}\cite{PyTest} was used for
@@
 excluding certain tests in certain build environment scenarios. Since
-all intended use cases were mapped using the test cases created, the
-code of the test cases could later be used in slightly simplified
-variants\ref{lst:pytest_example_code} as examples for the documentation.
+all intended usecases were mapped using the test cases created, the code
+of the test cases could later be used in slightly simplified variants
+\ref{lst:pytest_example_code} as examples for the documentation.
 
@@
 One important point that improves usability for users is the simple
-installation of the \gls{mrp}-library. As it was created in the Python
+installation of all \gls{mrp} modules. As it was created in the Python
 programming language, there are several public package registry where
 users can provide their software modules. Here,
-\passthrough{\lstinline!PyPi!}\cite{PyPI}\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}\cite{MagneticReadoutProcessingPyPI}
+\passthrough{\lstinline!PyPi!}\cite{PyPI}
+\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}\cite{MagneticReadoutProcessingPyPI}
 is the most commonly used package registry and offers direct support for
-the package installation programm \gls{pip}\ref{lst:setup_lib_with_pip}.
+the package installation programm \gls{pip}
+\ref{lst:setup_lib_with_pip}.
 
@@
 
-\begin{lstlisting}[language=bash, caption={Bash commands to install the MagneticReadoutProcessing (+mrp)-library using pip}, label=lst:setup_lib_with_pip]
+\begin{lstlisting}[language=bash, caption={Bash commands to install the MagneticReadoutProcessing library using pip}, label=lst:setup_lib_with_pip]
 # https://pypi.org/project/MagneticReadoutProcessing/
@@
 
-To make the \gls{mrp}-library compatible with the package registry,
-Python provides separate installation routines that build a package in
-an isolated environment and then provide an installation
+To make the \gls{mrp} file strucutre compatible with the package
+registry, Python provides separate installation routines that build a
+package in an isolated environment and then provide an installation
 \passthrough{\lstinline!wheel!} archive. This can then be uploaded to
@@
 
-Since the \gls{mrp}-library requires additional dependencies
+Since the \gls{mrp}-library requires additional Python dependencies
 (e.g.~\passthrough{\lstinline!numpy!},
@@
 already installed on the target system, these must be installed prior to
-the actual installation. These can be specified in the \gls{mrp}-library
+the actual installation. These can be specified in the library
 installation configuration
@@
 modern \gls{ide}s can more reliably display possible methods to the user
-as an assistance.\ref{pydocstring}
-
-\begin{lstlisting}[language=Python, caption={Python docstring example}, label=lst:pydocstring]
+as an assistance. \ref{lst:pydocstring}
+
+\begin{lstlisting}[language=Python, caption={Documentation using Python docstring example}, label=lst:pydocstring]
 # MRPDataVisualisation.py - example docstring
@@
 
-Since `docstrings' only document the source code, but do not provide
-simple how-to-use instructions, the documentation framework
+Since \passthrough{\lstinline!docstrings!} only document the source
+code, but do not provide simple how-to-use instructions, the
+documentation framework
 \passthrough{\lstinline!Sphinx!}\cite{SphinxDocumentation} was used
@@
 with the package management by \passthrough{\lstinline!PyPi!} services,
-which provide Python \gls{mrp}-library documentation online.
+which provide the \gls{mrp}-library documentation online.
 
@@
 \passthrough{\lstinline!ReadTheDocs!}\cite{MagneticReadoutProcessingReadTheDocs}
-and linked in the repository and on the overview
-page\ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
+and linked in the repository and on the overview page
+\ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
 on \passthrough{\lstinline!PyPi!}.
@@
   \textbf{Custom algorithm implementation} An important contribution of
-  the \gls{mrp} echosystem is the possibility for users to implement
+  the \gls{mrp} ecosystem is the possibility for users to implement
   their own algorithm for data analysis. This allows customisation to
@@
 This process covers all the essential functionalities required for a
-comprehensive characterisation of permanent magnets\ref{usecases}. The
+comprehensive characterisation of permanent magnets. These were
+previously described in the Usecases \ref{usecases} chapter. The
 developed framework not only offers a cost-effective and flexible
@@
 \centering
-\includegraphics{./generated_images/border_testmagnets_in_holder.png}
-\caption{testmagnets in holder \label{testmagnets_in_holder.png}}
-\end{figure}
-
-For the hardware setup, the
-\passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere} sensor was
+\includegraphics{./generated_images/border_Ten_numbered_test_magnets_in_separate_holders.png}
+\caption{Ten numbered test magnets in separate holders
+\label{Ten_numbered_test_magnets_in_separate_holders.png}}
+\end{figure}
+
+For the hardware setup, the 3D-Fullsphere\ref{d-fullsphere} sensor was
 used for the evaulation of the framework. As this is equipped with an
@@
 \passthrough{\lstinline!N45 12x12x12mm!} neodymium magnets were used
-here. These were placed in modified 3D printed
-holders\ref{testmagnets_in_holder.png} and then numbered. This allows
-them to be matched to the measurement results later.
+here. These were placed in modified 3D printed holders
+\ref{Ten_numbered_test_magnets_in_separate_holders.png} and then
+numbered. This allows them to be matched to the measurement results
+later.
 
@@
 system using the
-\passthrough{\lstinline!MRPcli config setupsensor eval\_measurement\_config!}-\gls{cli}
-command. The measurement was then
-configured\ref{lst:evaluation_measurement_config}.
+\passthrough{\lstinline!MRPcli config setupsensor!}-\gls{cli} command.
+The measurement was then configured for an measurement run, using the
+following configuration commands
+\ref{lst:evaluation_measurement_config}.
 
@@
 The \passthrough{\lstinline!MRPcli measure run!} command was then called
-up for each individual magnet to carry out a measurement. After each
-run, the \passthrough{\lstinline!READING-NAME!} parameter was filled
-with the id of the next magnet so that all measurements could be
-assigned to the physical magnets.
+up for each individual magnet to execute a measurement. After each run,
+the \passthrough{\lstinline!READING-NAME!} parameter was filled with the
+id of the next magnet so that all measurements could be assigned to the
+physical magnets.
 
@@
 
-The next step for the user is the implementation of the filter
-algorithm\ref{lst:custom_find_similar_values_algorithm}. This can have
-any function signature and is implemented in the file
+The next step for the user is the implementation of the filter algorithm
+\ref{lst:custom_find_similar_values_algorithm}. This can have any
+function signature and is implemented in the file
 \passthrough{\lstinline!UDPPFunctionCollection.py!}. This Python file is
@@
 the imported measurements from the
-\passthrough{\lstinline!stage import!} and the optional
-\passthrough{\lstinline!IP\_return\_count!} parameter specifies the
-number of best measurements that are returned. The return parameter is a
-list of measurements and should contain the measurements that are
-closest to the mean value of all measurements after the function has
-been executed.
+\passthrough{\lstinline!stage rawimport!}\ref{lst:pipeline_mrp_evaluation_yaml}
+and the optional \passthrough{\lstinline!IP\_return\_count!} parameter
+specifies the number of best measurements that are returned. The return
+parameter is a list of measurements and should contain the measurements
+that are closest to the mean value of all measurements after the
+function has been executed.
 
@@
 
-stage import:
+stage rawimport:
   function: import_readings
@@
   parameters:
-    _readings: stage import # USE RESULTS FROM import STAGE
+    _readings: stage rawimport # USE RESULTS FROM rawimport STAGE
     IP_return_count: 4 # RETURN BEST 4 of 10 READINGS
@@
 ready for execution. This is carried out using the
-\passthrough{\lstinline!MRPudpp!}-(cli)\ref{lst:bash_pipeline_mrp_evaluation_yaml}.
-After the run has been successfully completed, the results are saved in
-the result folder specified in the pipeline using the
+\passthrough{\lstinline!MRPudpp!}-(cli)
+\ref{lst:bash_pipeline_mrp_evaluation_yaml}. After the run has been
+successfully completed, the results are saved in the result folder
+specified in the pipeline using the
 \passthrough{\lstinline!IP\_export\_folder!} parameter.
@@
 
-On the right-hand side\ref{MRP_evaluation_result.png}, the measured
+On the right-hand side \ref{MRP_evaluation_result.png}, the measured
 values are plotted as a result of the filter algorithm. As the
@@
 that these are closest to the global mean value
-\passthrough{\lstinline!208.8 uT!}. The algorithm was thus successfully
-executed using the pipeline and the results could be validated.
+\passthrough{\lstinline!208.8uT!}. The filter algorithm implemented by
+the user was thus successfully executed using the user-programmable
+pipeline. The calculation result was successfully verified using raw
+measurement data and the final result of the algorithm.
 
@@
 
-In this version of the framework, a solid foundation has been laid that
-includes all the necessary features and is ready for use. During
-development, particular emphasis was placed on comprehensive
+A solid foundation has been built in this version of the framework,
+which contains all the necessary functions and is ready for immediate
+use. During development, particular emphasis was placed on comprehensive
 documentation to make it easier to get started. Together with examples
-for various use cases, a user can quickly evaluate the framework.
-
-However, it should be noted that the framework is still in its infancy.
-The stable version distributed via the package registry is well suited
-for the intended purpose. All tests and evaluations took place under
-normal conditions, especially for the developed hardware sensors, as the
-\gls{mrp} library works successfully with the measurement data.
+for various usecases, a user can quickly evaluate the framework.
+
+However, it should be noted that the framework has already been released
+with its first stable version, but extensions and improvements are still
+necessary. The stable version distributed via the package registry is
+well suited for the intended purpose. All tests and evaluations took
+place under normal conditions, especially for the developed hardware
+sensors, as the \gls{mrp} library works successfully with the
+measurement data.
 

### 2024-01-09 documentation/thesis/thesis_document.tex
more thesis

@@
 \subsection{Shimming Procedure}\label{shimming-procedure}}
+
+\hypertarget{charakterisation-of-permanent-magnets}{%
+\subsection{Charakterisation of Permanent
+Magnets}\label{charakterisation-of-permanent-magnets}}
+
+\begin{itemize}
+\item
+  zeigt ansätzte einfacher magnet vermesseungen
+  \cite{Wickenbrock_2021}
+\item
+  contruction of hallbach ringe \cite{cmr.a.20165}
+\end{itemize}
 
@@
 \item
-  Raspberry Pi OS Lite - \passthrough{\lstinline!debian bookworm x64!},
-\item
-  \gls{mrp} \ref{software-readout-framework}-library - version
+  Raspberry Pi OS Lite - \gls{os}
+  \passthrough{\lstinline!debian bookworm x64!},
+\item
+  \gls{mrp} \ref{software-readout-framework}-library - Version
   \passthrough{\lstinline!1.4.1!}
 \item
-  Unified Sensor \ref{unified-sensor}-firmware - version
+  Unified Sensor \ref{unified-sensor}-firmware - Version
   \passthrough{\lstinline!1.0.1!}
@@
 free \gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
-separate build configuration and the protocol of the measuring device
-was implemented.
+separate build configuration. In order to be able to read and correctly
+interpret the data from the microcontoller, the serial protocol from
+table \ref{Voltcraft_GM70_serial_protocol.csv} of the sensor was
+implemented in a customized version of the
+\passthrough{\lstinline!CustomSensor!} class
+\ref{lst:CustomSensorClass}.
 
@@
 
-\hypertarget{extension-modules}{%
-\section{Extension Modules}\label{extension-modules}}
-
-Im folgenden werden die einzelnen module, welche vom user modifiziert
-und ersetzt werden können im details erleutert.
-
-\hypertarget{hal}{%
-\subsection{HAL}\label{hal}}
-
 \begin{itemize}
@@
 \item
-  aufbau hal im grunde wird nur ein die commandos an das sensor cli
-  weitergegeben
-\item
-  alle sensoren implementieren mehr oder weniger die gleichen befehle
-\item
-  hal gibt nur weiter und ist ``dumm''
+  jeder schritt nach der DAQ basiert auf dem gleichen grundtyp datentyp
+\item
+  meta-daten werden bei jedem weiteren schritt hinzugeügt um
+  nachverfolgbarkeit zu gewärleisten
 \end{itemize}
 
-\hypertarget{visualisation}{%
-\subsection{Visualisation}\label{visualisation}}
-
-\hypertarget{storage}{%
-\subsection{Storage}\label{storage}}
+\hypertarget{modules}{%
+\section{Modules}\label{modules}}
+
+The library consists of various modules, which are divided into two
+categories:
 
@@
 \item
-  metadata management
+  Core - All modules related to measurement data management
+\item
+  Extensions - Contains modules for visualizations, hardware sensor
+  access
 \end{itemize}
 
-\hypertarget{export}{%
-\subsection{Export}\label{export}}
+An overview of these is given in the subchapters as the following. There
+are also introductory examples which provide an overview of the basic
+functions in the \passthrough{\lstinline!Examples!}\ref{examples}
+section, as well as further examples in the online documentation.
+\cite{MagneticReadoutProcessingReadTheDocs}
+
+\hypertarget{core-modules}{%
+\subsection{Core Modules}\label{core-modules}}
+
+\hypertarget{extension-modules}{%
+\subsection{Extension Modules}\label{extension-modules}}
+
+\hypertarget{sensor-interface}{%
+\subsubsection{Sensor Interface}\label{sensor-interface}}
+
+Another collection of optional modules provided by the library is the
+connection of external hardware sensors. All compatible sensors that are
+compatible with the firmware developed in the
+\passthrough{\lstinline!Unified Sensor!}\ref{unified-sensor} chapter are
+supported here. The library provides the following sensor \gls{hal}
+modules for this purpose:
 
@@
 \item
-  format import export
-\item
-  matlab
+  \passthrough{\lstinline!MRPHal!} - Firmware protocol implementation
+\item
+  \passthrough{\lstinline!MRPHalLocal!} - \gls{usb} sensor interface
+\item
+  \passthrough{\lstinline!MRPHalRemote!} - Remote sensor interface
 \end{itemize}
+
+These provide functions to communicate with a connected hardware sensor
+and send commands to it. To generate these and convert the received
+measurement data into the appropriate format for the core modules, there
+is a suitable module for each sensor type:
+
+\begin{itemize}
+\tightlist
+\item
+  \passthrough{\lstinline!MRPReadingSourceStatic!} - for 1D and 2D
+  sensor such as
+  \passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor}
+\item
+  \passthrough{\lstinline!MRPReadingSourceFullsphere!} - for 3D sensors
+  such as \passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere}
+\end{itemize}
+
+The decision which of these modules to use is made automatically
+depending on the connected hardware. For this purpose, a static function
+\passthrough{\lstinline!createReadingSourceInstance!} is implemented in
+the base class \passthrough{\lstinline!MRPReadingSource!}, which
+automatically creates the appropriate instance based on the sensor
+capabilites.
+
+\hypertarget{visualisation}{%
+\subsubsection{Visualisation}\label{visualisation}}
+
+\hypertarget{analysis}{%
+\subsubsection{Analysis}\label{analysis}}
+
+\hypertarget{storage-and-datamanagement}{%
+\section{Storage and Datamanagement}\label{storage-and-datamanagement}}
+
+An important aspect is data import and export. On the one hand, this
+allows the library to reuse and archive the measurements. On the other
+hand, the focus during development was that it is also possible to use
+the data in other programs. For this purpose, an open, documented export
+format must be selected. Ideally, this should be human-readable and
+viewable with a simple text editor. This eliminates all binary-based
+formats such as the Python pickle built into Python.
+
+Taking these points into account, the \gls{json} format was chosen. This
+is human and machine readable and there is a compatible parser for
+almost every programming language.
+
+The following code snippet \ref{lst:json_export_format_example} shows
+the \gls{json} structure which is generated when a measurement thatt
+using the library is exported. Here you can see that by using the
+\gls{json} format, all measurement points and metadata are available in
+readable plain text. This means that they can also be read out in other
+programs. Using serialization, the \passthrough{\lstinline!MRPReading!}
+class inherited from Python-\passthrough{\lstinline!Object!} class is
+serialized via an dictionary conversion step. This \gls{json} string can
+then be processed directly or written to the file system as a file.
+
+\begin{lstlisting}[caption={JSON export structure of an MRPReading based measurement}, label=lst:json_export_format_example]
+{
+  "time_start": "Wed Sep 20 08:50:13 2023",
+  "time_end": "Wed Sep 20 08:50:13 2023",
+  "additional_data": {
+      "sensor_device_path": "/dev/cu.usbmodem3867315334391",
+      "sensor_name": "Unified Sensor Single Sensor",
+      "sensor_id": "386731533439",
+      "sensor_capabilities": ["static", "axis_b", "axis_x", "axis_y", "axis_z", "axis_temp", "axis_stimestamp"],
+      "configname": "calibrationtemp30.yaml",
+      "runner": "cli"
+  },
+  "data": [{
+      "value": 0.135,
+      "is_valid": true,
+      "id": 0,
+      "temperature": 34.32
+  }],
+  "measurement_config": {
+      "id": "525771256544952",
+      "sensor_distance_radius": 40.0,
+      "magnet_type": 0
+  },
+  "name": "calibrationtemp30",
+}
+\end{lstlisting}
+
+The exported example \ref{lst:json_export_format_example} contains the
+following different object keys, which contain the following
+information:
+
+\begin{itemize}
+\tightlist
+\item
+  \passthrough{\lstinline!additional\_data!} - Additional user-defined
+  metadata
+\item
+  \passthrough{\lstinline!data!} - Measured values with value and
+  measured value \gls{id}
+\item
+  \passthrough{\lstinline!measurement\_config!} - Information about the
+  sensor used for measurement
+\end{itemize}
+
+In addition, further custom objects can be inserted into the \gls{json}
+using the functions provided.
+
+Since there are popular data processing frameworks such as
+Numpy\cite{harris2020array}, or the program for mathematical
+calculations, Matlab are often used, the library also supports export
+formats for these systems.
+
+The different formats can be triggered by the user by calling up the
+corresponding \passthrough{\lstinline!MRPReading!} class functions:
+
+\begin{itemize}
+\tightlist
+\item
+  \passthrough{\lstinline!.dump()!} - \gls{json}
+\item
+  \passthrough{\lstinline!.to\_numpy\_matrix()!} - Numpy-Array of
+  \passthrough{\lstinline!data!} object with different options
+\item
+  \passthrough{\lstinline!.dump\_savemat()!} - Matlab mat-file with
+  measurement values and temperatures
+\end{itemize}
+
+Currently, data re-import of an exported measurement is only supported
+via the \gls{json} format, as an export using the other options (Numpy,
+Matlab)loses data during the export procedure.
 
@@
 At the current described scenarios, it is only possible to detect and
-use sensors that are directly connected to the \gls{pc} with the
-\gls{mrp}-library. It has the disadvantage that there must always be a
-physical connection. This can make it difficult to install multiple
-sensors in measurement setups where space or cable routing options are
-limited. So multibe sensor can be connected to a
-\passthrough{\lstinline!remote!} \gls{pc} which is available on the
-network. This can be a \gls{sbc} (e.g.~a Raspberry Pi). The small
-footprint and low power consumption make it a good choice. It can also
-be used in a temperature chamber.
+use sensors that are directly connected to the host \gls{pc}. It has the
+disadvantage that there must always be a physical connection. This can
+make it difficult to install multiple sensors in measurement setups
+where space or cable routing options are limited. So multibe sensor can
+be connected to a \passthrough{\lstinline!remote!} \gls{pc} which is
+available on the network. This can be a \gls{sbc} (e.g.~a Raspberry Pi).
+The small footprint and low power consumption make it a good choice. It
+can also be used in a temperature chamber.
 
@@
 \item
-  redirect to each capable sensor
-\item
-  extend commands using an id parameter
+  Redirect to each capable sensor
+\item
+  Extend commands using an id parameter
 \end{itemize}
@@
 \item
-  Input parameters - using \passthrough{\lstinline!param!} and
+  Input parameters, using \passthrough{\lstinline!param!} and
   \passthrough{\lstinline!type!}
 \item
-  Return value - using \passthrough{\lstinline!returns!},
+  Return value, using \passthrough{\lstinline!returns!},
   \passthrough{\lstinline!rtype!}

### 2024-01-09 src/MagneticReadoutProcessing/MRP/MRPReading.py

@@ -6,6 +6,8 @@ import numpy as np
 import json
 import sys
 
+import scipy
+
 from MRP import MRPHelpers, MRPReadingEntry, MRPMagnetTypes, MRPMeasurementConfig
 
 
@@ -139,6 +141,10 @@ class MRPReading():
 
     def get_magnet_type(self) -> MRPMagnetTypes.MagnetType:
         return self.measurement_config.magnet_type
+
+    def savemat(self):
+        import scipy.io
+        scipy.io.savemat('test.mat', dict(x=x, y=y))
 
     def to_numpy_cartesian(self, _normalize: bool = True, _use_sensor_distance: bool = False) -> np.array:
 
@@ -428,6 +434,30 @@ class MRPReading():
             fout = open(_filepath_name, 'w')
             fout.write(self.dump())
             fout.close()
+        except Exception as e:
+            sys.stderr.write(str(e))
+        return _filepath_name
+
+
+    def dump_savemat(self, _filepath_name: str) -> str:
+        """
+        Dumps the reading class instance into a matlab .mat file
+        Includes datapoints only
+
+        :param _filepath_name: File path to which the file will be exported
+        :type _filepath_name: str
+
+        :returns: File path to which the file is exported, including filename
+        :rtype: str
+        """
+        if '.mat' not in _filepath_name:
+            _filepath_name = _filepath_name + '.mat'
+        print("dump_to_file with {0}".format(_filepath_name))
+
+
+        # FINALLY EXPORT TO FILE USING SCIPY AS EXPORT MIDDLEWARE
+        try:
+            scipy.io.savemat(_filepath_name, dict(x=self.to_value_array(), y=self.to_temperature_value_array()))
         except Exception as e:
             sys.stderr.write(str(e))
         return _filepath_name

### 2024-01-09 src/MagneticReadoutProcessing/MRP/MRPReadingSource.py

@@ -1,5 +1,5 @@
 from abc import ABC, abstractmethod
-from MRP import MRPHal, MRPReading
+from MRP import MRPHal, MRPReading, MRPReadingSourceHelper
 
 
 class MRPReadingSourceException(Exception):
@@ -9,6 +9,10 @@ class MRPReadingSourceException(Exception):
 
 
 class MRPReadingSource(ABC):
+
+    @staticmethod
+    def createReadingSourceInstance(_hal: MRPHal.MRPHal):
+        return MRPReadingSourceHelper.MRPReadingSourceHelper.createReadingSourceInstance(_hal)
 
     @abstractmethod
     def __init__(self, _hal: MRPHal.MRPHal):

### 2024-01-09 documentation/thesis/thesis_document.tex
more thesis

@@
 functions in the \passthrough{\lstinline!Examples!}\ref{examples}
-section, as well as further examples in the online documentation.
-\cite{MagneticReadoutProcessingReadTheDocs}
+section, as well as further examples in the online
+documentation\cite{MagneticReadoutProcessingReadTheDocs}.
 
@@
 
-\hypertarget{extension-modules}{%
-\subsection{Extension Modules}\label{extension-modules}}
-
-\hypertarget{sensor-interface}{%
-\subsubsection{Sensor Interface}\label{sensor-interface}}
-
-Another collection of optional modules provided by the library is the
-connection of external hardware sensors. All compatible sensors that are
-compatible with the firmware developed in the
-\passthrough{\lstinline!Unified Sensor!}\ref{unified-sensor} chapter are
-supported here. The library provides the following sensor \gls{hal}
-modules for this purpose:
+The included core modules are essential for using the library. Basic
+data types are implemented, as well as functions for import and export.
+In addition, there are other support scripts that are required
+internally.
+
+The following modules are implemented in detail:
 
@@
 \item
-  \passthrough{\lstinline!MRPHal!} - Firmware protocol implementation
-\item
-  \passthrough{\lstinline!MRPHalLocal!} - \gls{usb} sensor interface
-\item
-  \passthrough{\lstinline!MRPHalRemote!} - Remote sensor interface
+  \passthrough{\lstinline!MRPReading!} - storage of measured values
+\item
+  \passthrough{\lstinline!MRPMeasurementConfig!} - storage of the
+  measurement parameters
+\item
+  \passthrough{\lstinline!MRPMagnetTypes!} - various physical constants
+  for basic magnet types
 \end{itemize}
 
-These provide functions to communicate with a connected hardware sensor
-and send commands to it. To generate these and convert the received
-measurement data into the appropriate format for the core modules, there
-is a suitable module for each sensor type:
-
-\begin{itemize}
-\tightlist
-\item
-  \passthrough{\lstinline!MRPReadingSourceStatic!} - for 1D and 2D
-  sensor such as
-  \passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor}
-\item
-  \passthrough{\lstinline!MRPReadingSourceFullsphere!} - for 3D sensors
-  such as \passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere}
-\end{itemize}
-
-The decision which of these modules to use is made automatically
-depending on the connected hardware. For this purpose, a static function
-\passthrough{\lstinline!createReadingSourceInstance!} is implemented in
-the base class \passthrough{\lstinline!MRPReadingSource!}, which
-automatically creates the appropriate instance based on the sensor
-capabilites.
-
-\hypertarget{visualisation}{%
-\subsubsection{Visualisation}\label{visualisation}}
-
-\hypertarget{analysis}{%
-\subsubsection{Analysis}\label{analysis}}
+The \passthrough{\lstinline!MRPReading!} module performs a crucial role
+in streamlining the centralized management of measurement data. It
+serves as a storage provider for various measurements, offering
+functionalities that facilitate the creation and addition of data
+records. To customize and add meta-data, users have the flexibility to
+configure parameters through the dedicated
+\passthrough{\lstinline!MRPMeasurementConfig!} module into an
+\passthrough{\lstinline!MRPReading!} instance.
+
+Within the realm of measurement data, a diverse range of data points can
+be seamlessly incorporated. The process is initiated by employing
+specialized functions designed for the creation and addition of data
+records. To configure parameters, ensuring a tailored approach to the
+entire measurement process, these parameters act as a crucial bridge
+between user preferences and the robust capabilities of the
+\passthrough{\lstinline!MRPReading!} module.
+
+The system is also designed to be compatible with
+\passthrough{\lstinline!Extension Modules!}\ref{extension-modules},
+allowing the generation of measurement data through various modules.
+This extensibility enhances the versatility of the system, accommodating
+diverse measurement scenarios and expanding its utility across different
+domains.
+
+To enhance the accessibility and interpretability of the recorded data,
+a dedicated module, MRPMagnetTypes, comes into play. This module is
+specifically designed for the storage of physical parameters pertaining
+to the magnets targeted for measurement. By centralizing this
+information, users can streamline the subsequent phases of evaluation
+and analysis, simplifying the overall process and ensuring a more
+efficient and insightful exploration of the collected data.
+
+At the end of processing, the collected data is typically exported;
+various functions are provided for this purpose. These are described as
+the following.
 
 \hypertarget{storage-and-datamanagement}{%
-\section{Storage and Datamanagement}\label{storage-and-datamanagement}}
+\subsubsection{Storage and
+Datamanagement}\label{storage-and-datamanagement}}
 
@@
   "time_start": "Wed Sep 20 08:50:13 2023",
-  "time_end": "Wed Sep 20 08:50:13 2023",
+  "time_end": "Wed Sep 20 08:54:13 2023",
   "additional_data": {
@@
 Matlab)loses data during the export procedure.
+
+\hypertarget{extension-modules}{%
+\subsection{Extension Modules}\label{extension-modules}}
+
+\hypertarget{sensor-interface}{%
+\subsubsection{Sensor Interface}\label{sensor-interface}}
+
+Another collection of optional modules provided by the library is the
+connection of external hardware sensors. All compatible sensors that are
+compatible with the firmware developed in the
+\passthrough{\lstinline!Unified Sensor!}\ref{unified-sensor} chapter are
+supported here. The library provides the following sensor \gls{hal}
+modules for this purpose:
+
+\begin{itemize}
+\tightlist
+\item
+  \passthrough{\lstinline!MRPHal!} - Firmware protocol implementation
+\item
+  \passthrough{\lstinline!MRPHalLocal!} - \gls{usb} sensor interface
+\item
+  \passthrough{\lstinline!MRPHalRemote!} - Remote sensor interface
+\end{itemize}
+
+These provide functions to communicate with a connected hardware sensor
+and send commands to it. To generate these and convert the received
+measurement data into the appropriate format for the core modules, there
+is a suitable module for each sensor type:
+
+\begin{itemize}
+\tightlist
+\item
+  \passthrough{\lstinline!MRPReadingSourceStatic!} - for 1D and 2D
+  sensor such as
+  \passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor}
+\item
+  \passthrough{\lstinline!MRPReadingSourceFullsphere!} - for 3D sensors
+  such as \passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere}
+\end{itemize}
+
+The decision which of these modules to use is made automatically
+depending on the connected hardware. For this purpose, a static function
+\passthrough{\lstinline!createReadingSourceInstance!} is implemented in
+the base class \passthrough{\lstinline!MRPReadingSource!}, which
+automatically creates the appropriate instance based on the sensor
+capabilites.
+
+\hypertarget{visualisation}{%
+\subsubsection{Visualisation}\label{visualisation}}
+
+In order to give the user the possibility to display the recorded data
+visually, two modules were created, which can graphically prepare
+\passthrough{\lstinline!MRPReading!} instances:
+
+\begin{itemize}
+\tightlist
+\item
+  \passthrough{\lstinline!MRPVisualization!} - different table, graph
+  based plots
+\item
+  \passthrough{\lstinline!MRPPolarVisualization!} - fullsphere map plots
+\end{itemize}
+
+On the one hand, it is possible with the
+\passthrough{\lstinline!MRPVisualization!} module to display measurement
+data as a table or streamplot, lineplot. This makes it possible, for
+example, to visually identify outliers or trends in the measurement
+data. These can also be saved as an image file. The module is compatible
+with all measurement data.
+
+In contrast to the \passthrough{\lstinline!MRPPolarVisualization!}
+module, this provides functions to create 2D map plots in the polar
+coordinate system. This requires measurement data with additionally set
+spatial coordinates. These can be generated automatically with the
+\passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere} sensor, or
+the user must provide the spatial information from another source.
+
+\hypertarget{analysis}{%
+\subsubsection{Analysis}\label{analysis}}
 

### 2024-01-09 documentation/thesis/thesis_document.tex
more thesis

@@
 In contrast to the \passthrough{\lstinline!MRPPolarVisualization!}
-module, this provides functions to create 2D map plots in the polar
+module, this provides functions to create 2D map plots a polar
 coordinate system. This requires measurement data with additionally set

### 2024-01-10 documentation/thesis/thesis_document.tex
more thesis

@@
 
-\ref{usecases}
+The present work aims to provide an efficient and comprehensive solution
+for the design of low-field MRI devices by developing and implementing a
+software and hardware framework.
+
+The scope of the software library is to lay the foundation for the
+systematic characterization of magnets based on permanent magnets. The
+library will enable data acquisition, storage and analysis of magnetic
+properties, with customization possible at each step of the process. The
+work aims to facilitate magnetic field characterization and improve the
+exchange of data between different user groups. Complete documentation,
+tutorials and tests will enable users to use the framework efficiently
+and adapt it to their specific requirements. The application of the
+developed framework for the characterization of different magnets and
+the integration of magnetic field sensors serve as practical
+applications and validation of the developed solution.
 
@@
 The next initialisation system is dedicated for multi-sensor
-synchronisation \ref{sensor-syncronsisation-interface}. The last step in
+synchronisation \ref{sensor-syncronisation-interface}. The last step in
 the setup is to configure communication with the host or connected
@@
 ensures that in a multi-sensor setup with several sensors. The
-measurements are synchronized \ref{sensor-syncronsisation-interface} in
+measurements are synchronized \ref{sensor-syncronisation-interface} in
 time and are not out of sequence or drift.
@@
 
-\hypertarget{sensor-syncronsisation-interface}{%
-\subsection{Sensor syncronsisation
-interface}\label{sensor-syncronsisation-interface}}
+\hypertarget{sensor-syncronisation-interface}{%
+\subsection{Sensor Syncronisation
+Interface}\label{sensor-syncronisation-interface}}
 
@@
 To enhance the accessibility and interpretability of the recorded data,
-a dedicated module, MRPMagnetTypes, comes into play. This module is
-specifically designed for the storage of physical parameters pertaining
-to the magnets targeted for measurement. By centralizing this
-information, users can streamline the subsequent phases of evaluation
-and analysis, simplifying the overall process and ensuring a more
-efficient and insightful exploration of the collected data.
-
-At the end of processing, the collected data is typically exported;
-various functions are provided for this purpose. These are described as
-the following.
+a dedicated module, \passthrough{\lstinline!MRPMagnetTypes!}, comes into
+play. This module is specifically designed for the storage of physical
+parameters pertaining to the magnets targeted for measurement. By
+centralizing this information, users can streamline the subsequent
+phases of evaluation and analysis, simplifying the overall process and
+ensuring a more efficient and insightful exploration of the collected
+data.
+
+At the end of processing, the collected and modified data are typically
+exported; various functions are provided for this purpose. This process
+is described in the following subchapter.
 
@@
 
+The extention modules build on the core modules and offer the user
+additional basic functionalities. These include functions for data
+acquisition, visualization and analysis.
+
 \hypertarget{sensor-interface}{%
@@
   \passthrough{\lstinline!MRPReadingSourceStatic!} - for 1D and 2D
-  sensor such as
+  sensors such as
   \passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor}
@@
 \item
-  \passthrough{\lstinline!MRPVisualization!} - different table, graph
+  \passthrough{\lstinline!MRPVisualization!} - different table and graph
   based plots
@@
 
+Data analysis offers the user the greatest flexibility to implement
+their own modules. For this reason \passthrough{\lstinline!MRPAnalysis!}
+contains functions for calculating the following data analyses, which
+are compatible with class instances of
+\passthrough{\lstinline!MRPReading!}:
+
+\begin{itemize}
+\tightlist
+\item
+  \passthrough{\lstinline!std\_deviation!} - standard deviation
+\item
+  \passthrough{\lstinline!mean!} - mean value
+\item
+  \passthrough{\lstinline!variance!} - variance
+\item
+  \passthrough{\lstinline!center\_of\_gravity!} - center of gravity
+\item
+  \passthrough{\lstinline!binning!} - distribution of a sample by means
+  of a histogram
+\item
+  \passthrough{\lstinline!k-nearest!} - k-nearest neighbors
+\end{itemize}
+
+In addition, the export function
+\passthrough{\lstinline!.to\_numpy\_matrix!} enables further processing
+of the data in the
+\passthrough{\lstinline!Numpy!}\cite{harris2020array} framework, in
+which many other standard analysis functions are implemented.
+
 \hypertarget{multi-sensor-setup}{%
@@
 where space or cable routing options are limited. So multibe sensor can
-be connected to a \passthrough{\lstinline!remote!} \gls{pc} which is
-available on the network. This can be a \gls{sbc} (e.g.~a Raspberry Pi).
-The small footprint and low power consumption make it a good choice. It
-can also be used in a temperature chamber.
+be connected to any \gls{pc} which is available on the network. This can
+be a \gls{sbc} (e.g.~a Raspberry Pi). The small footprint and low power
+consumption make it a good choice. It can also be used in a temperature
+chamber.
 
@@
 other via their sync input using short cables. One sensor acts as the
-central clock as described in \ref{sensor-syncronsisationiinterface}.
+central clock as described in \ref{sensor-syncronisation-interface}.
 this no longer works for long distances and the syncronisation must be

### 2024-01-12 documentation/thesis/thesis_document.tex
more thesis

@@
 \subsection{Shimming Procedure}\label{shimming-procedure}}
+
+Der Shimming-Prozess ist ein entscheidender Schritt bei der
+Magnetresonanztomographie (MRT), um homogene Magnetfelder für präzise
+Bildgebung zu gewährleisten. Shimming korrigiert Unregelmäßigkeiten im
+statischen Magnetfeld, die durch äußere Einflüsse oder interne
+Systemfehler entstehen können. Dieser Prozess optimiert die
+Feldhomogenität, was für hochauflösende und artefaktfreie Bilder
+entscheidend ist.
+
+Die Quellen für den Shimming-Prozess können Hardware- und
+Software-basiert sein. Hardware-Shimming beinhaltet den Einsatz von
+Gradienten- und Radiofrequenzspulen, die gezielt platziert werden, um
+das Magnetfeld auszurichten. Software-Shimming hingegen verwendet
+Algorithmen, um die Steuerparameter des MRT-Systems anzupassen und die
+Homogenität zu verbessern.
+
+Forschungspublikationen wie ``Shimming Techniques in Magnetic Resonance
+Imaging'' (DOI: 10.1007/978-1-4939-2815-6\_3) bieten detaillierte
+Einblicke in verschiedene Shimming-Methoden und Techniken. Diese
+Fortschritte in der Shimming-Technologie tragen dazu bei, die
+diagnostische Genauigkeit und Bildqualität in der MRT erheblich zu
+verbessern.
 
@@
 library will enable data acquisition, storage and analysis of magnetic
-properties, with customization possible at each step of the process. The
-work aims to facilitate magnetic field characterization and improve the
-exchange of data between different user groups. Complete documentation,
-tutorials and tests will enable users to use the framework efficiently
-and adapt it to their specific requirements. The application of the
-developed framework for the characterization of different magnets and
-the integration of magnetic field sensors serve as practical
-applications and validation of the developed solution.
+properties, with customization possible at each step of the process.
+
+The work aims to facilitate magnetic field characterization and improve
+the exchange of data between different user groups. Complete
+documentation, tutorials and tests will enable users to use the
+framework efficiently and adapt it to their specific requirements.
+
+The application of the developed framework for the characterization of
+different magnets and the integration of magnetic field sensors serve as
+practical applications and validation of the developed solution.
 
@@
 differentiation takes place later in the \gls{mrp}
-\ref{software-readout-framework}-library by using the sensor \gls{id}.
+\ref{software-readout-framework}-library by using the sensor \gls{uuid}.
 
@@
 
-\hypertarget{library-requirements}{%
-\section{Library requirements}\label{library-requirements}}
-
-\hypertarget{concepts}{%
-\subsection{Concepts}\label{concepts}}
+The software readout framework is the central software component that
+was developed as part of this work. This software framework is intended
+to provide a user-oriented data acquisition and analysis environment.
+For this purpose, typical individual steps that occur in relation to
+these tasks were implemented:
 
@@
 \item
-  beispiele für projekte welche nur einzelne schnritte implementieren
-\item
-  so kann man sich auf die implementierung
+  Data acquisition - e.g.~from hardware sensors \ref{unified-sensor}
+\item
+  Storage - export of data in various open formats
+  \ref{storage-and-datamanagement}
+\item
+  Analysis - algorithms to analyze different data sets \ref{analysis}
 \end{itemize}
 
+All these possible task parts were divided into different blocks and
+users were given the possibility of adding their own functionalities.
+
+As the following, this concept is referred to as
+\passthrough{\lstinline!user interaction points!}\ref{user-interaction-points}
+and is explained in the following chapter.
+
 \hypertarget{user-interaction-points}{%
-\subsection{User interaction points}\label{user-interaction-points}}
+\section{User Interaction Points}\label{user-interaction-points}}
 
@@
 \centering
-\includegraphics{./generated_images/border_MRPlib_COMPLETE_FLOW.png}
-\caption{MRPlib COMPLETE FLOW \label{MRPlib_COMPLETE_FLOW.png}}
+\includegraphics{./generated_images/border_MRP_library_module_high_level_overview.png}
+\caption{MRP library module high level overview
+\label{MRP_library_module_high_level_overview.png}}
 \end{figure}
 
-\begin{itemize}
+User interaction points represent the core concept of the developed
+library and are intended to provide user-friendliness on the one hand
+and the rapid development of own analysis and optimization algorithms on
+the other. For this purpose, the library was divided into individual
+modules, which are shown in the graphic
+\ref{MRP_library_module_high_level_overview.png}. In combination, these
+represent a typical measurement-analysis-evaluation workflow of data.
+For this purpose, a module system with standardised functional patterns
+and data types was developed and packed together in a extendable Python
+library.
+
+According to this concept, the user should be able to replace individual
+components from this chain with their own modules without having to
+worry about implementing other of these to make the project work.
+
+\hypertarget{user-interaction-points-example}{%
+\subsection{User Interaction Points
+Example}\label{user-interaction-points-example}}
+
+The following example shows the advantages of using the
+\passthrough{\lstinline!User interaction points!}:
+
+A project called
+\passthrough{\lstinline!HalbachOptimization!}\cite{HalbachOptimization}
+implements a data analysis step and optimizes a magnetic field that is
+as homogeneous as possible within a circular section using given
+mechanical dimensions as input parameters of the magnets used. For this
+purpose, a mutation of the magnet positions and rotations is performed.
+The result is a list of positions for each magnet.
+
+The
+\passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner}
+opensource project, can generate basic \gls{cad} drawings for \gls{mri}
+magnets in a Hallbach configuration. To do this, the number of magnets
+and additional parameters for the properties of the \gls{cad} model to
+be created are passed to the function provided as input parameters using
+a \gls{json} file. The result is then an
+\passthrough{\lstinline!OpenSCAD!}\cite{OpenSCAD} based 3D model of
+the magnet holder.
+
+As a result, there are two projects which are both suitable for the task
+of optimizing and creating Hallbach magnets for \gls{mri} applications.
+However, their data structures are not compatible with each other.
+However, they are executed manually one after the other in order to
+obtain a final result.
+
+The library created is intended to solve one problem by providing
+standardized and flexible data structures for use with this form of
+magnetic field data. On the other hand, by separating the processing
+pipeline into defined sub-steps, it should be possible to make
+individual modules and as a result functionalities interchangeable by
+the user.
+
+The implementation of the same functionalities looks as follows after
+using the library:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
 \tightlist
 \item
-  jeder schritt nach der DAQ basiert auf dem gleichen grundtyp datentyp
-\item
-  meta-daten werden bei jedem weiteren schritt hinzugeügt um
-  nachverfolgbarkeit zu gewärleisten
-\end{itemize}
+  \textbf{Create a static set of magnets}
+\end{enumerate}
+
+The input parameters of the
+\passthrough{\lstinline!HalbachOptimization!}\cite{HalbachOptimization}
+project are on the one hand the mechanical dimensions and the number of
+magnets to be used. We assume ideal magnets here. However, it should
+also be possible to import field data in a more measured form later on.
+Using the DataAquisition sub-step, it is possible to generate any number
+of ideal magnets.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  \textbf{Add custom analysis processing step}
+\end{enumerate}
+
+Next, the user creates his own analysis step in order to be able to call
+up its functions. In the case of the
+\passthrough{\lstinline!HalbachOptimization!}\cite{HalbachOptimization}
+project, the function signature of the start function must be changed.
+This receives the result of the previous step, in this case the
+generated magnet data. By optionally setting meta data in the universal
+bilbiothekt data type, constants can be replaced in the analysis
+function and made dynamically configurable. The return result also
+corresponds to this data type so that subsequent steps are compatible
+and contains the magnet data with modified position and rotation data.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  \textbf{Generate fabrication data}
+\end{enumerate}
+
+The last step is to call up the
+\passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner}
+project, which creates the \gls{cad} model of the magnet holder. The
+data can also be exported as files here. To make the project compatible,
+the function signatures are also adapted here. In this case, more
+changes are required, as the configuration file is loaded from the file
+system. This logic must be removed in order to use the added meta data
+in the input parameter instead.
+
+After these customization steps, it is possible to execute both projects
+one after the other and all required configuration parameters are
+contained in the data structure looped through the individual steps as
+meta data. This also maps the functionality of a project file, which can
+be executed or passed on repeatedly. This also fulfills the goal of
+making individual user-created algorithms interchangeable. If the user
+now wishes to use a different \gls{cad} algorithm instead of the
+\passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner},
+the other steps can simply be preserved.
+
+The individual modules and their functions are explained in detail in
+the following chapters.
 
@@
 
-The library consists of various modules, which are divided into two
+In order to realise the concept of user interaction points, the library
+was divided into different modules. These can be divided into two main
 categories:
@@
 
-An overview of these is given in the subchapters as the following. There
-are also introductory examples which provide an overview of the basic
-functions in the \passthrough{\lstinline!Examples!}\ref{examples}
-section, as well as further examples in the online
+In each of these categories there are then several sub-categories
+divided into User Interaction Points. An overview of these is given in
+the subchapters as the following. There are also introductory examples
+which provide an overview of the basic functions in the
+\passthrough{\lstinline!Examples!}\ref{examples} section, as well as
+further examples in the online
 documentation\cite{MagneticReadoutProcessingReadTheDocs}.
@@
   \passthrough{\lstinline!data!} - Measured values with value and
-  measured value \gls{id}
+  measured value \gls{uuid}
 \item
@@
 initially the same for each sensor. The only identification feature is
-the sensor \gls{id} by using the \passthrough{\lstinline!id!} command of
-the sensor \gls{cli}.
+the sensor \gls{uuid} by using the \passthrough{\lstinline!id!} command
+of the sensor \gls{cli}.
 
@@
 Immediately after starting the \passthrough{\lstinline!MRPProxy!}, the
-\gls{id}s of all locally connected sensors are read out. These are
+\gls{uuid}s of all locally connected sensors are read out. These are
 stored together with the class instance of the
 \passthrough{\lstinline!MRPHal!} module in a \gls{lut}. This makes it
-possible to address a sensor directly using its \gls{id}.
+possible to address a sensor directly using its \gls{uuid}.
 
@@
 \passthrough{\lstinline!requested capability!} -\textgreater{}
-\passthrough{\lstinline!sensor!}-\gls{id} -\textgreater{}
+\passthrough{\lstinline!sensor!}-\gls{uuid} -\textgreater{}
 \passthrough{\lstinline!physical sensor!} and allows the commands to be
@@
 \passthrough{\lstinline!Network-Proxy!}\ref{network-proxy} by another
-\gls{id} parameter, according to the following scheme:
+\gls{uuid} parameter, according to the following scheme:
 
@@
 This allows the host to address individual sensors directly via their
-specific \gls{id}.
+specific \gls{uuid}.
 
@@
 In general, a sensor can be connected using its specific system path or
-the sensor-\gls{id} via the
+the sensor-\gls{uuid} via the
 \passthrough{\lstinline!MRPHalSerialPortInformation!} function. Locally

### 2024-01-12 documentation/thesis/thesis_document.tex
more thesis

@@
 \section{Background and Motivation}\label{background-and-motivation}}
+
+As the following, the motivation for the development of this framework
+is listed. A brief introduction to the topic of low-field \gls{mri} is
+given, followed by the research problem to be solved by this work.
 
@@
 
+In this work, reference is made exclusively to the hardware shim
+process. Since this project is to be used in the future to construct a
+low-field \gls{mri} B0 field magnet from permanent magnets.
+
 \hypertarget{charakterisation-of-permanent-magnets}{%
@@
 
-\hypertarget{opensource-projects}{%
-\section{Opensource Projects}\label{opensource-projects}}
-
 \hypertarget{conceptual-design}{%
@@
 \end{itemize}
-
-accomplished
 
@@
 \passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner},
-the other steps can simply be preserved.
-
-The individual modules and their functions are explained in detail in
-the following chapters.
+the other steps can simply be preserved and only the new step needs to
+be implemented.
 

### 2024-01-13 documentation/thesis/thesis_declaration.tex
more thesis

@@
 
-I hereby certify that I have written this thesis independently and have
-not used any sources other than those listed in the bibliography. Any
-passages taken verbatim or in spirit from published or unpublished
-sources are labelled as such. The drawings or illustrations in this work
-have been created by myself or have been labelled accordingly. This
-thesis has not been submitted in the same or a similar form to any other
-examination authority.
-
 Aachen, \datum  \_\_\_\_\_\_\_\_\_\_\_\_,

### 2024-01-13 documentation/thesis/thesis_document.tex
more thesis

@@
 \subsection{Low-Field MRI}\label{low-field-mri}}
+
+Low-field magnetic resonance imaging (low-field \gls{mri}) is a
+\gls{mri} technique that operates at a lower magnetic field strength
+compared to conventional high-field \gls{mri} scanners. Typically, the
+magnetic field in low-field MRI systems between
+\passthrough{\lstinline!0.1T!} and \passthrough{\lstinline!0.3T!}
+compared to the usual \passthrough{\lstinline!1.5T!} to
+\passthrough{\lstinline!3T!} in high-field \gls{mri}
+scanners.\cite{Hori2021-pt}
+
+This technology is used in medical imaging as well as in preclinical
+research. The main advantage of low-field MRI is the improved imaging of
+soft tissues, especially when examining joints and muscles. It also
+offers more cost-effective alternatives to high-field MRI
+systems.\cite{Hori2021-pt}
+
+\hypertarget{magnet-system}{%
+\subsection{Magnet System}\label{magnet-system}}
 
@@
 
+\hypertarget{state-of-the-art}{%
+\section{State of the Art}\label{state-of-the-art}}
+
 \hypertarget{aim-of-this-thesis}{%
@@
 The present work aims to provide an efficient and comprehensive solution
-for the design of low-field MRI devices by developing and implementing a
-software and hardware framework.
+for the design of low-field \gls{mri} devices by developing and
+implementing a software and hardware framework.
 
@@
   against the previously defined usecases.
-\end{itemize}
-
-\hypertarget{state-of-the-art}{%
-\chapter{State of the Art}\label{state-of-the-art}}
-
-\hypertarget{conceptual-design}{%
-\section{Conceptual Design}\label{conceptual-design}}
-
-\begin{itemize}
-\tightlist
-\item
-  etnwicklung eines hardware uns software framework zur einfachen
-  aquirierung von Meagnetfelddaten
-\item
-  analysetools und funktionen
 \end{itemize}

### 2024-01-13 documentation/thesis/thesis_document.tex
more thesis

@@
 compared to the usual \passthrough{\lstinline!1.5T!} to
-\passthrough{\lstinline!3T!} in high-field \gls{mri}
+\passthrough{\lstinline!3T!} and above in high-field \gls{mri}
 scanners.\cite{Hori2021-pt}
@@
 
-Der Shimming-Prozess ist ein entscheidender Schritt bei der
-Magnetresonanztomographie (MRT), um homogene Magnetfelder für präzise
-Bildgebung zu gewährleisten. Shimming korrigiert Unregelmäßigkeiten im
-statischen Magnetfeld, die durch äußere Einflüsse oder interne
-Systemfehler entstehen können. Dieser Prozess optimiert die
-Feldhomogenität, was für hochauflösende und artefaktfreie Bilder
-entscheidend ist.
-
-Die Quellen für den Shimming-Prozess können Hardware- und
-Software-basiert sein. Hardware-Shimming beinhaltet den Einsatz von
-Gradienten- und Radiofrequenzspulen, die gezielt platziert werden, um
-das Magnetfeld auszurichten. Software-Shimming hingegen verwendet
-Algorithmen, um die Steuerparameter des MRT-Systems anzupassen und die
-Homogenität zu verbessern.
-
-Forschungspublikationen wie ``Shimming Techniques in Magnetic Resonance
-Imaging'' (DOI: 10.1007/978-1-4939-2815-6\_3) bieten detaillierte
-Einblicke in verschiedene Shimming-Methoden und Techniken. Diese
-Fortschritte in der Shimming-Technologie tragen dazu bei, die
-diagnostische Genauigkeit und Bildqualität in der MRT erheblich zu
-verbessern.
+The shimming process is a crucial step in magnetic resonance imaging
+\gls{mri} to ensure homogeneous magnetic fields for precise imaging.
+Shimming corrects irregularities in the static magnetic field that can
+be caused by external influences or internal system errors. This process
+optimizes field homogeneity, which is crucial for high-resolution and
+artifact-free images.\cite{10.3389/fphy.2021.704566}
+
+The sources for the shimming process can be hardware and software based.
+Hardware shimming involves the use of gradient and radio frequency coils
+that are specifically placed to align the magnetic field. Software
+shimming, on the other hand, uses algorithms to adjust the control
+parameters of the \gls{mri} system and improve
+homogeneity.\cite{10.3389/fphy.2021.704566}
 

### 2024-01-14 documentation/thesis/thesis_document.tex
more thesis

@@
 
+\begin{itemize}
+\tightlist
+\item
+  hinzugügen bei lowmir werden durch die geringe feldstärkre oft
+  permanentmagnet systeme eingesetzt.
+\item
+  typische konstruktionen sind dabei hallbach arrays
+\end{itemize}
+
 \hypertarget{shimming-procedure}{%
@@
 \begin{itemize}
+\item
+  durch fabrikatio von permantentmagneten kann es zu abweichungen
+  kommen*
+\item
+  vorallem wenn diese \textgreater N45 klassifikation sind
+\item
+  es gibt temperaturkompensierte Magnetene welche teuer sind
+\item
+  deswegen gibt es den ansatz zur vermessung
+\item
+  \begin{enumerate}
+  \def\labelenumi{\arabic{enumi}.}
+  \tightlist
+  \item
+    per algorithmus können diese dann aussortiert werden
+  \end{enumerate}
+\item
+  \begin{enumerate}
+  \def\labelenumi{\arabic{enumi}.}
+  \setcounter{enumi}{1}
+  \tightlist
+  \item
+    oder position bzw rotation angepasst werden um irregualtritie welche
+    von anderen magneten ausgehen auszucanceln
+  \end{enumerate}
 \item

### 2024-01-14 documentation/thesis/thesis_document.tex
more thesis

--- 2024-01-13 documentation/thesis/thesis_document.tex
@@
 compared to the usual \passthrough{\lstinline!1.5T!} to
-\passthrough{\lstinline!3T!} and above in high-field \gls{mri}
-scanners.\cite{Hori2021-pt}
+\passthrough{\lstinline!3T!} and above in high-field \gls{mri} scanners
+\cite{Hori2021-pt}.
 
@@
 soft tissues, especially when examining joints and muscles. It also
-offers more cost-effective alternatives to high-field MRI
-systems.\cite{Hori2021-pt}
+offers more cost-effective alternatives to high-field MRI systems
+\cite{Hori2021-pt}.
 
@@
 \subsection{Magnet System}\label{magnet-system}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Example_hallbach_ring_magnet_with_cutouts_for_eight_cubical_permanent_magnets.png}
+\caption{Example hallbach ring magnet with cutouts for eight cubical
+permanent magnets
+\label{Example_hallbach_ring_magnet_with_cutouts_for_eight_cubical_permanent_magnets.png}}
+\end{figure}
+
+Halbach ring magnets \cite{Halbach1980DesignOP} have become a common
+design for low field \gls{mri} and \gls{nmr} systems
+\cite{cmr.a.20165}.
+
+They have the ability to generate extremely homogeneous magnetic flux
+densities, produce virtually no stray fields and are particularly
+attractive for larger magnets as their design has the best flux-to-mass
+ratio \cite{Wickenbrock_2021}.
+
+A halbach ring of this type is usually based on a ring with permanent
+magnets arranged in a circle. The graphic
+\ref{Example_hallbach_ring_magnet_with_cutouts_for_eight_cubical_permanent_magnets.png}
+shows an example \gls{cad} model of such a ring, in which in this case
+eight cubic \passthrough{\lstinline!12x12x12mm!} magnets are embedded to
+generate homogeneous magnetic flux densities of around
+\passthrough{\lstinline!20mT!}.
+
+The homogeneity in this configuration depends, among other things, on
+the following aspects:
+
+\begin{itemize}
+\item
+  \textbf{Material}
+
+  The magnetic properties of a material influence the generated field
+  strength. Different materials have different magnetic
+  susceptibilities.
+\item
+  \textbf{Magnetization}
+
+  The orientation of the magnetic moments in the material influences the
+  field strength. A higher magnetization leads to a stronger field
+  strength.
+\item
+  \textbf{Temperature}
+
+  Temperature can influence the magnetic properties of a material. The
+  magnetization of some materials decreases with increasing temperature.
+\item
+  \textbf{Manufacturing process}
+
+  The manufacturing process can influence the magnetic properties of the
+  material. This is dependent on the purity of the starting materials
+  used and the processing methods. There may also be deviations in field
+  strength if different magnets from different production batches are
+  compared.
+\end{itemize}
+
+These aspects can also be applied to individual magnets. As a result,
+this also complicates the effect on the structure of a Halbach ring
+magnet. If these are joined together to form a ring, positioning
+tolerances are also added.
+
+In order to compensate for inhomogeneities in a finished system, there
+are various so-called shimming procedures which further improve
+homogeneity after the system has been assembled.
 
@@
 optimizes field homogeneity, which is crucial for high-resolution and
-artifact-free images.\cite{10.3389/fphy.2021.704566}
+artifact-free images \cite{10.3389/fphy.2021.704566}.
 
@@
 shimming, on the other hand, uses algorithms to adjust the control
-parameters of the \gls{mri} system and improve
-homogeneity.\cite{10.3389/fphy.2021.704566}
+parameters of the \gls{mri} system and improve homogeneity
+\cite{10.3389/fphy.2021.704566}.
 
@@
 process. Since this project is to be used in the future to construct a
-low-field \gls{mri} B0 field magnet from permanent magnets.
+low-field \gls{mri} field magnet from permanent magnets.
 
@@
 
+The shimming process described describes how, after the field magnet has
+been set up, if the homogeneous magnetic flux densities are not
+sufficient, these can be adjusted manually by means of adjustments to
+the setup or, if the hardware allows it, by software. In addition, the
+causes that cause the inhomogeneity, the output permanent magnet, are
+also known.
+
+As a result, there is the possibility of using the shimming process or
+checking the permanent magnets used in advance before they are used in a
+Hallbach configuration.
+
+There are two ways of using the data from the magnets that were
+previously measured:
+
 \begin{itemize}
-\item
-  zeigt ansätzte einfacher magnet vermesseungen
+\tightlist
+\item
+  By using binning or sorting algorithms to filter for the most similar
+  magnets
+\item
+  Adjustment of the rotation and position within the Hallbach
+  configuration
+\end{itemize}
+
 \cite{Wickenbrock_2021}
-\item
-  contruction of hallbach ringe \cite{cmr.a.20165}
-\end{itemize}
 
@@
 current measured value can be output using the
-\passthrough{\lstinline!readout!}
-command\ref{Query_sensors_b_value_using_(+cli).png}.
+\passthrough{\lstinline!readout!} command
+\ref{Query_sensors_b_value_using_(+cli).png}.
 
@@
 \ref{software-readout-framework}-library. The serial interface is also
-used here. However, after a connection attempt by the
-\passthrough{\lstinline!MRPHal!}\ref{hal} module of the \gls{mrp}
+used here. However, after a connection attempt by the \gls{hal}
+\ref{mrphal} module of the \gls{mrp}
 \ref{software-readout-framework}-library, the system switches to binary
@@
 command. The same commands are available as for \gls{cli}-based
-communication.
+communication, but in a binary format.
 
@@
 \passthrough{\lstinline!RaspberryPi 4 4GB!}-\gls{sbc} together with an
-\passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor} and the
-following software settings:
+\passthrough{\lstinline!1D: Single Sensor!} \ref{d-single-sensor} and
+the following software settings:
 
@@
 synchronisation status can be queried via the user interface
-\ref{communication-interface} using the
-\passthrough{\lstinline!opmode!}\ref{Query_opmode_using_(+cli).png}
-command. An important aspect of the implementation here was that there
-is no numbering or sequence of the individual sensors. This means that
-for the subsequent readout of the measurements, it is only important
-that they are taken at the same interval across all sensors. The sensor
-differentiation takes place later in the \gls{mrp}
-\ref{software-readout-framework}-library by using the sensor \gls{uuid}.
+\ref{communication-interface} using the \passthrough{\lstinline!opmode!}
+\ref{Query_opmode_using_(+cli).png} command. An important aspect of the
+implementation here was that there is no numbering or sequence of the
+individual sensors. This means that for the subsequent readout of the
+measurements, it is only important that they are taken at the same
+interval across all sensors. The sensor differentiation takes place
+later in the \gls{mrp} \ref{software-readout-framework}-library by using
+the sensor \gls{uuid}.
 
@@
 \item
-  Data acquisition - e.g.~from hardware sensors \ref{unified-sensor}
+  Data acquisition - from hardware sensors \ref{unified-sensor} or other
+  data sources
 \item
@@
 As the following, this concept is referred to as
-\passthrough{\lstinline!user interaction points!}\ref{user-interaction-points}
-and is explained in the following chapter.
+\passthrough{\lstinline!user interaction points!}
+\ref{user-interaction-points} and is explained in the following chapter.
 
@@
 
-A project called
-\passthrough{\lstinline!HalbachOptimization!}\cite{HalbachOptimization}
-implements a data analysis step and optimizes a magnetic field that is
-as homogeneous as possible within a circular section using given
-mechanical dimensions as input parameters of the magnets used. For this
-purpose, a mutation of the magnet positions and rotations is performed.
-The result is a list of positions for each magnet.
-
-The
-\passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner}
-opensource project, can generate basic \gls{cad} drawings for \gls{mri}
-magnets in a Hallbach configuration. To do this, the number of magnets
-and additional parameters for the properties of the \gls{cad} model to
-be created are passed to the function provided as input parameters using
-a \gls{json} file. The result is then an
-\passthrough{\lstinline!OpenSCAD!}\cite{OpenSCAD} based 3D model of
-the magnet holder.
+A project called \passthrough{\lstinline!HalbachOptimisation!}
+\cite{HalbachOptimisation} implements a data analysis step and
+optimizes a magnetic field that is as homogeneous as possible within a
+circular section using given mechanical dimensions as input parameters
+of the magnets used. For this purpose, a mutation of the magnet
+positions and rotations is performed. The result is a list of positions
+for each magnet.
+
+The \passthrough{\lstinline!HalbachMRIDesigner!}
+\cite{HalbachMRIDesigner} opensource project, can generate basic
+\gls{cad} drawings for \gls{mri} magnets in a Hallbach configuration. To
+do this, the number of magnets and additional parameters for the
+properties of the \gls{cad} model to be created are passed to the
+function provided as input parameters using a \gls{json} file. The
+result is then an \passthrough{\lstinline!OpenSCAD!} \cite{OpenSCAD}
+based 3D model of the magnet holder.
 
@@
 The input parameters of the
-\passthrough{\lstinline!HalbachOptimization!}\cite{HalbachOptimization}
-project are on the one hand the mechanical dimensions and the number of
-magnets to be used. We assume ideal magnets here. However, it should
-also be possible to import field data in a more measured form later on.
-Using the DataAquisition sub-step, it is possible to generate any number
-of ideal magnets.
+\passthrough{\lstinline!HalbachOptimisation!}
+\cite{HalbachOptimisation} project are on the one hand the
+mechanical dimensions and the number of magnets to be used. We assume
+ideal magnets here. However, it should also be possible to import field
+data in a more measured form later on. Using the DataAquisition
+sub-step, it is possible to generate any number of ideal magnets.
 
@@
 up its functions. In the case of the
-\passthrough{\lstinline!HalbachOptimization!}\cite{HalbachOptimization}
-project, the function signature of the start function must be changed.
-This receives the result of the previous step, in this case the
-generated magnet data. By optionally setting meta data in the universal
-bilbiothekt data type, constants can be replaced in the analysis
-function and made dynamically configurable. The return result also
-corresponds to this data type so that subsequent steps are compatible
-and contains the magnet data with modified position and rotation data.
+\passthrough{\lstinline!HalbachOptimisation!}
+\cite{HalbachOptimisation} project, the function signature of the
+start function must be changed. This receives the result of the previous
+step, in this case the generated magnet data. By optionally setting meta
+data in the universal bilbiothekt data type, constants can be replaced
+in the analysis function and made dynamically configurable. The return
+result also corresponds to this data type so that subsequent steps are
+compatible and contains the magnet data with modified position and
+rotation data.
 
@@
 The last step is to call up the
-\passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner}
-project, which creates the \gls{cad} model of the magnet holder. The
-data can also be exported as files here. To make the project compatible,
-the function signatures are also adapted here. In this case, more
-changes are required, as the configuration file is loaded from the file
-system. This logic must be removed in order to use the added meta data
-in the input parameter instead.
+\passthrough{\lstinline!HalbachMRIDesigner!}
+\cite{HalbachMRIDesigner} project, which creates the \gls{cad} model
+of the magnet holder. The data can also be exported as files here. To
+make the project compatible, the function signatures are also adapted
+here. In this case, more changes are required, as the configuration file
+is loaded from the file system. This logic must be removed in order to
+use the added meta data in the input parameter instead.
 
@@
 now wishes to use a different \gls{cad} algorithm instead of the
-\passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner},
-the other steps can simply be preserved and only the new step needs to
-be implemented.
+\passthrough{\lstinline!HalbachMRIDesigner!}
+\cite{HalbachMRIDesigner}, the other steps can simply be preserved
+and only the new step needs to be implemented.
 
@@
 which provide an overview of the basic functions in the
-\passthrough{\lstinline!Examples!}\ref{examples} section, as well as
-further examples in the online
-documentation\cite{MagneticReadoutProcessingReadTheDocs}.
+\passthrough{\lstinline!Examples!} \ref{examples} section, as well as
+further examples in the online documentation
+\cite{MagneticReadoutProcessingReadTheDocs}.
 
@@
 The system is also designed to be compatible with
-\passthrough{\lstinline!Extension Modules!}\ref{extension-modules},
+\passthrough{\lstinline!Extension Modules!} \ref{extension-modules},
 allowing the generation of measurement data through various modules.
@@
   "additional_data": {
-      "sensor_device_path": "/dev/cu.usbmodem3867315334391",
+      "sensor_device_path": "/dev/ttyUnifiedSensorSingle",
       "sensor_name": "Unified Sensor Single Sensor",
@@
 Since there are popular data processing frameworks such as
-Numpy\cite{harris2020array}, or the program for mathematical
-calculations, Matlab are often used, the library also supports export
-formats for these systems.
+\passthrough{\lstinline!Numpy!} \cite{harris2020array}, or the
+program for mathematical calculations, Matlab are often used, the
+library also supports export formats for these systems.
 
@@
 \item
-  \passthrough{\lstinline!.to\_numpy\_matrix()!} - Numpy-Array of
+  \passthrough{\lstinline!.to\_numpy\_matrix()!} -
+  \passthrough{\lstinline!Numpy!}-Array of
   \passthrough{\lstinline!data!} object with different options
@@
 Currently, data re-import of an exported measurement is only supported
-via the \gls{json} format, as an export using the other options (Numpy,
-Matlab)loses data during the export procedure.
+via the \gls{json} format, as an export using the other options
+(\passthrough{\lstinline!Numpy!}, \passthrough{\lstinline!Matlab!})loses
+data during the export procedure. \}
 
@@
 compatible with the firmware developed in the
-\passthrough{\lstinline!Unified Sensor!}\ref{unified-sensor} chapter are
-supported here. The library provides the following sensor \gls{hal}
+\passthrough{\lstinline!Unified Sensor!} \ref{unified-sensor} chapter
+are supported here. The library provides the following sensor \gls{hal}
 modules for this purpose:
@@
   \passthrough{\lstinline!MRPReadingSourceStatic!} - for 1D and 2D
-  sensors such as
-  \passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor}
+  sensors such as \passthrough{\lstinline!1D: Single Sensor!}
+  \ref{d-single-sensor}
 \item
   \passthrough{\lstinline!MRPReadingSourceFullsphere!} - for 3D sensors
-  such as \passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere}
+  such as \passthrough{\lstinline!3D: Fullsphere!} \ref{d-fullsphere}
 \end{itemize}
@@
 \passthrough{\lstinline!MRPVisualization!} module to display measurement
-data as a table or streamplot, lineplot. This makes it possible, for
-example, to visually identify outliers or trends in the measurement
-data. These can also be saved as an image file. The module is compatible
-with all measurement data.
+data as a table or plot (e.g.~stream, line, point). This makes it
+possible, for example, to visually identify outliers or trends in the
+measurement data. These can also be saved as an image file. The module
+is compatible with all measurement data.
 
@@
 spatial coordinates. These can be generated automatically with the
-\passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere} sensor, or
+\passthrough{\lstinline!3D: Fullsphere!} \ref{d-fullsphere} sensor, or
 the user must provide the spatial information from another source.
@@
 \passthrough{\lstinline!.to\_numpy\_matrix!} enables further processing
-of the data in the
-\passthrough{\lstinline!Numpy!}\cite{harris2020array} framework, in
-which many other standard analysis functions are implemented.
+of the data in the \passthrough{\lstinline!Numpy!}
+\cite{harris2020array} framework, in which many other standard
+analysis functions are implemented.
 
@@
 
-The \passthrough{\lstinline!MRPProxy!}\ref{MRPlib_Proxy_Module.png}
+The \passthrough{\lstinline!MRPProxy!} \ref{MRPlib_Proxy_Module.png}
 module has been developed to allow forwarding and interaction with
@@
 \gls{pc}, only the \gls{ip} address or hostname of the \gls{pc} running
-an \passthrough{\lstinline!MRPProxy!} instance is
-required\ref{lst:mrpcli_config_using_rpc}.
+an \passthrough{\lstinline!MRPProxy!} instance is required
+\ref{lst:mrpcli_config_using_rpc}.
 
@@
 If time-critical synchronisation over the network is required, \gls{ptp}
-and \gls{pps} output functionality\cite{PTPIEEE1588} can be used on
+and \gls{pps} output functionality \cite{PTPIEEE1588} can be used on
 many \gls{sbc}, such as the
@@
 Table \ref{Sensor_capabilities_merging.csv}) and returned to the host
-when the \passthrough{\lstinline!info!}\ref{lst:mtsc} command is
+when the \passthrough{\lstinline!info!} \ref{lst:mtsc} command is
 received over network.
@@
 For commands where there are several entries for
-\passthrough{\lstinline!CAPABLE SENSORS ID LUT!}\ref{Sensor_capabilities_merging.csv},
-there are two possible approaches to how the command is processed:
+\passthrough{\lstinline!CAPABLE SENSORS ID LUT!}
+\ref{Sensor_capabilities_merging.csv}, there are two possible approaches
+to how the command is processed:
 
@@
 strategy is used for different sensors. Each command is extended on the
-\passthrough{\lstinline!Network-Proxy!}\ref{network-proxy} by another
+\passthrough{\lstinline!Network-Proxy!} \ref{network-proxy} by another
 \gls{uuid} parameter, according to the following scheme:
@@
 developed, which can interact with all
-\passthrough{\lstinline!Unified Sensor!}\ref{unified-sensor}-compatible
+\passthrough{\lstinline!Unified Sensor!} \ref{unified-sensor}-compatible
 sensors. In the following example \ref{lst:mrpexample_hal}, an
-\passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor} is
+\passthrough{\lstinline!1D: Single Sensor!} \ref{d-single-sensor} is
 connected locally to the host \gls{pc}.
@@
 is generated in the background using the
-\passthrough{\lstinline!magpylib!}\cite{ortner2020magpylib} library
+\passthrough{\lstinline!magpylib!} \cite{ortner2020magpylib} library
 according to the specified parameters.
@@
 functions for this purpose. The code example shows the basic use of the
-module. The \textbf{Evaluation}\ref{evaluation} chapter shows how the
+module. The \textbf{Evaluation} \ref{evaluation} chapter shows how the
 user can implement their own algorithms and add them to the library.
@@
 particularly helpful for full-sphere measurements recorded with the
-\passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere} sensor. The
+\passthrough{\lstinline!3D: Fullsphere!} \ref{d-fullsphere} sensor. The
 sub-module \passthrough{\lstinline!MRPPolarVisualisation!} is specially
@@
 The following example code \ref{lst:mrpexample_hallbach}, shows how a
-simple hallbach magnetic ring can be generated. Eight random
-measurements are generated here. It is important that the magnet type
-(here \passthrough{\lstinline!N45\_CUBIC\_15x15x15!}) is specified. This
-is necessary so that the correct magnet cutouts can be generated when
-creating the 3D model. After the measurements have been generated, they
-are provided with a position and rotation offset according to the
-Hallbach design and calucation
-scheme\cite{HallbachMagnetDesignPaper} using the
+simple hallbach magnetic ring can be generated.
+
+This can then be used to construct a Halbach ring magnet (see chapter
+\ref{Charakterisation of Permanent Magnets}) for a low-field \gls{mri}.
+
+Eight random measurements are generated here. It is important that the
+magnet type (here \passthrough{\lstinline!N45\_CUBIC\_15x15x15!}) is
+specified. This is necessary so that the correct magnet cutouts can be
+generated when creating the 3D model. After the measurements have been
+generated, they are provided with a position and rotation offset
+according to the Hallbach design and calucation scheme
+\cite{HallbachMagnetDesignPaper} using the
 \passthrough{\lstinline!MRPHallbachArrayGenerator!} module.
@@
 is generated from the generated magnet positions. The result is an
-\passthrough{\lstinline!OpenSCAD!}\cite{OpenSCAD} file, which
+\passthrough{\lstinline!OpenSCAD!} \cite{OpenSCAD} file, which
 contains the module generated. After computing the model using the
-\passthrough{\lstinline!OpenSCAD!}-\gls{cli} utility, the following
+\passthrough{\lstinline!OpenSCAD!} \gls{cli} utility, the following
 model rendering
@@
 also be easily edited with a plain text editor. Detailed examples can be
-found in the
-documentation\cite{MagneticReadoutProcessingReadTheDocs}. The
-pipeline definition consists of sections which execute the appropriate
-Python commands in the background. The signatures in the
-\passthrough{\lstinline!yaml!} file are called using
-\passthrough{\lstinline!reflection!} and a real-time search of the
-loaded
-\passthrough{\lstinline!global() symbol table!}\cite{PythonGlobalSymbolTable}.
-This system makes almost all Python functions available to the user. To
-simplify use, a pre-defined list of verified functions for use in
-pipelines is listed in the
-documentation\cite{MagneticReadoutProcessingReadTheDocs}. The
-following pipeline definition \ref{lst:mrpuddp_example_yaml} shows the
-previously defined steps \ref{example_measurement_analysis_pipeline.png}
-as \passthrough{\lstinline!yaml!} syntax.
+found in the documentation
+\cite{MagneticReadoutProcessingReadTheDocs}. The pipeline definition
+consists of sections which execute the appropriate Python commands in
+the background. The signatures in the \passthrough{\lstinline!yaml!}
+file are called using \passthrough{\lstinline!reflection!} and a
+real-time search of the loaded \passthrough{\lstinline!global()!}
+functions symbol table \cite{PythonGlobalSymbolTable}. This system
+makes almost all Python functions available to the user. To simplify
+use, a pre-defined list of verified functions for use in pipelines is
+listed in the documentation
+\cite{MagneticReadoutProcessingReadTheDocs}. The following pipeline
+definition \ref{lst:mrpuddp_example_yaml} shows the previously defined
+steps \ref{example_measurement_analysis_pipeline.png} as
+\passthrough{\lstinline!yaml!} syntax.
 
@@
 created for all important functionalities and usecases. The test
-framework \passthrough{\lstinline!PyTest!}\cite{PyTest} was used for
-this purpose, as it offers direct integration in most \gls{ide}s (see
+framework \passthrough{\lstinline!PyTest!} \cite{PyTest} was used
+for this purpose, as it offers direct integration in most \gls{ide}s
+(see
 \ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
@@
 release in the repository on the basis of
-\passthrough{\lstinline!Github Actions!}\cite{GithubActions}. Here
+\passthrough{\lstinline!Github Actions!} \cite{GithubActions}. Here
 there is the possibility to host local runner software, which then has
@@
 software and executed via virtualisation on the systems provided by
-\passthrough{\lstinline!Github Actions!}\cite{GithubActions}.
+\passthrough{\lstinline!Github Actions!}.
 
@@
 \passthrough{\lstinline!PyPi!}\cite{PyPI}
-\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}\cite{MagneticReadoutProcessingPyPI}
-is the most commonly used package registry and offers direct support for
-the package installation programm \gls{pip}
-\ref{lst:setup_lib_with_pip}.
+\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}
+\cite{MagneticReadoutProcessingPyPI} is the most commonly used
+package registry and offers direct support for the package installation
+programm \gls{pip} \ref{lst:setup_lib_with_pip}.
 
@@
 (e.g.~\passthrough{\lstinline!numpy!},
-\passthrough{\lstinline!matplotlib!}), which cannot be assumed to be
-already installed on the target system, these must be installed prior to
-the actual installation. These can be specified in the library
-installation configuration
-\passthrough{\lstinline!setup.py!}\ref{lst:setup_py_req} for this
-purpose.
+\passthrough{\lstinline!matplotlib!} packages), which cannot be assumed
+to be already installed on the target system, these must be installed
+prior to the actual installation. These can be specified in the library
+installation configuration \passthrough{\lstinline!setup.py!}
+\ref{lst:setup_py_req} for this purpose.
 
@@
 source code was documented using
-Python-\passthrough{\lstinline!docstrings!}\cite{PythonDocstringReference}
-and the Python3.5 type annotations:
+Python-\passthrough{\lstinline!docstrings!}
+\cite{PythonDocstringReference} and the Python3.5 type annotations:
 
@@
 code, but do not provide simple how-to-use instructions, the
-documentation framework
-\passthrough{\lstinline!Sphinx!}\cite{SphinxDocumentation} was used
-for this purpose. This framework makes it possible to generate
-\gls{html} or \gls{pdf} documentation from various source code
-documentation formats, such as the used
+documentation framework \passthrough{\lstinline!Sphinx!}
+\cite{SphinxDocumentation} was used for this purpose. This framework
+makes it possible to generate \gls{html} or \gls{pdf} documentation from
+various source code documentation formats, such as the used
 \passthrough{\lstinline!docstrings!}. These are converted into a
@@
 publication option is to host the documentation via online services such
-as \passthrough{\lstinline!ReadTheDocs!}\cite{ReadTheDocs}, where
+as \passthrough{\lstinline!ReadTheDocs!} \cite{ReadTheDocs}, where
 users can make documentation for typical software projects available to
@@
 
-The documentation has also been uploaded for
-\passthrough{\lstinline!ReadTheDocs!}\cite{MagneticReadoutProcessingReadTheDocs}
-and linked in the repository and on the overview page
+The documentation has also been uploaded to
+\passthrough{\lstinline!ReadTheDocs!}
+\cite{MagneticReadoutProcessingReadTheDocs} and linked in the
+repository and on the overview page
 \ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
@@
 The process of creating and publishing the documentation has been
-automated using
-\passthrough{\lstinline!GitHub Actions!}\cite{GithubActions}, so
-that it is always automatically kept up to date with new features.
+automated using \passthrough{\lstinline!GitHub Actions!}, so that it is
+always automatically kept up to date with new features.
 
@@
 the imported measurements from the
-\passthrough{\lstinline!stage rawimport!}\ref{lst:pipeline_mrp_evaluation_yaml}
-and the optional \passthrough{\lstinline!IP\_return\_count!} parameter
-specifies the number of best measurements that are returned. The return
-parameter is a list of measurements and should contain the measurements
-that are closest to the mean value of all measurements after the
-function has been executed.
+\passthrough{\lstinline!stage rawimport!}
+\ref{lst:pipeline_mrp_evaluation_yaml} and the optional
+\passthrough{\lstinline!IP\_return\_count!} parameter specifies the
+number of best measurements that are returned. The return parameter is a
+list of measurements and should contain the measurements that are
+closest to the mean value of all measurements after the function has
+been executed.
 
@@
 
-The python \passthrough{\lstinline!heapq!}\cite{heapq} module, which
-implements a priority queue, is used for this purpose. The calculated
-distances from the mean value of the measurements to the global mean
-value are inserted into this queue. Subsequently, as many elements of
-the queue are returned as defined by the
+The python \passthrough{\lstinline!heapq!} \cite{heapq} module,
+which implements a priority queue, is used for this purpose. The
+calculated distances from the mean value of the measurements to the
+global mean value are inserted into this queue. Subsequently, as many
+elements of the queue are returned as defined by the
 \passthrough{\lstinline!IP\_return\_count!} parameter. The actual
@@
 ready for execution. This is carried out using the
-\passthrough{\lstinline!MRPudpp!}-(cli)
+\passthrough{\lstinline!MRPudpp!} (cli)
 \ref{lst:bash_pipeline_mrp_evaluation_yaml}. After the run has been

### 2024-01-15 documentation/thesis/thesis_document.tex
more thesis

@@
 
-\hypertarget{charakterisation-of-permanent-magnets}{%
-\subsection{Charakterisation of Permanent
-Magnets}\label{charakterisation-of-permanent-magnets}}
+\hypertarget{state-of-the-art}{%
+\section{State of the Art}\label{state-of-the-art}}
 
@@
 causes that cause the inhomogeneity, the output permanent magnet, are
-also known.
-
-As a result, there is the possibility of using the shimming process or
-checking the permanent magnets used in advance before they are used in a
-Hallbach configuration.
+also known. As a result, there is the possibility of using the shimming
+process or checking the permanent magnets used in advance before they
+are used in a Hallbach configuration.
+
+In order to measure the magnets individually, there are already
+implementations that use different measurement methods to determine the
+field strength of individual magnets. Individual measuring points are
+recorded. This data is then evaluated in separate software
+\cite{Wickenbrock_2021}.
 
@@
 
-\cite{Wickenbrock_2021}
-
-\hypertarget{state-of-the-art}{%
-\section{State of the Art}\label{state-of-the-art}}
+This form of data processing of previously characterized magnetic data
+is currently being implemented experimentally in projects using various
+algorithms \cite{Wickenbrock_2021}. Standard sorting algorithms are
+used as well as specialized algorithms for optimizing homogeneity by
+rotating the individual magnets in a Hallbach ring relative to each
+other \cite{HalbachMRIDesigner}.
+
+These are each separate projects that implement individual aspects of
+data processing, which realize the process of measuring individual
+magnets by manual combination. However, there are still compatibility
+problems and limitations in the adaptation of hardware and software.
+
+Special algorithms from various projects are used to optimize
+homogeneity. The challenge here is to ensure the seamless integration
+and compatibility of these algorithms into the overall process. This
+should make it possible to create a workflow from the individual magnet
+to the finished optimized \gls{cad} model of a halbach ring.
 
@@
 The application of the developed framework for the characterization of
-different magnets and the integration of magnetic field sensors serve as
-practical applications and validation of the developed solution.
+different magnets and the integration of various available magnetic
+field sensors serve the practical application and validation of the
+developed solution.
 

### 2024-01-15 documentation/thesis/thesis_document.tex
more thesis

@@
 \begin{longtable}[]{@{}llll@{}}
-\caption{Sensor capabilities merging
-\label{Sensor_capabilities_merging.csv}}\tabularnewline
+\caption{Sensor capabilities merging algorithm
+\label{Sensor_capabilities_merging_algorithm.csv}}\tabularnewline
 \toprule
@@
 previously created \gls{lut}. Duplicate entries are summarized (see
-Table \ref{Sensor_capabilities_merging.csv}) and returned to the host
-when the \passthrough{\lstinline!info!} \ref{lst:mtsc} command is
-received over network.
+Table \ref{Sensor_capabilities_merging_algorithm.csv}) and returned to
+the host when the \passthrough{\lstinline!info!} \ref{lst:mtsc} command
+is received over network.
 

### 2024-01-15 documentation/thesis/thesis_document.tex
more thesis
first: all chapters filles :)

@@
 understand the functionality and added value of the implemented solution
-for the user. These were defined in the course of project planning and
-provide an overview of how the user interacts with the project and what
+for the user.
+
+These were defined in the course of project planning and provide an
+overview of how the user interacts with the project and what
 functionalities can be expected. In the later accomplished evaluation
@@
 expandable. The focus is on mapping different sensors and being
-compatible with different magnet types and shapes. This ensures broad
-applicability in different scenarios. Another goal is reproducibility to
-ensure consistent results. Easy communication with standard PC hardware
-maximises the user-friendliness of the interface. The flexibility to
-support different sensors and magnets makes the system versatile and
-opens the possibility for use in different applications. A low-cost
-magnetic field sensors interface will therefore not only be economically
-attractive, but also facilitate the integration of magnetic field
-sensors in different contexts. In addition, the low-cost sensor
-interface will serve as a development platform for the data evaluation
-\gls{mrp} library and provide real measurement data from magnets. In
-addition, the interface firmware creates a basis for the development of
-a data protocol for exchanging measured values. This makes it easy to
-integrate your own measuring devices into the \gls{mrp} ecosystem at a
-later date. This is only possible with a minimal functional hardware and
-firmware setup and was developed for this purpose first.
+compatible with different magnet types and shapes.
+
+This ensures broad applicability in different scenarios. Another goal is
+reproducibility to ensure consistent results. Easy communication with
+standard PC hardware maximises the user-friendliness of the interface.
+
+The flexibility to support different sensors and magnets makes the
+system versatile and opens the possibility for use in different
+applications. A low-cost magnetic field sensors interface will therefore
+not only be economically attractive, but also facilitate the integration
+of magnetic field sensors in different contexts.
+
+In addition, the low-cost sensor interface will serve as a development
+platform for the data evaluation \gls{mrp} library and provide real
+measurement data from magnets. In addition, the interface firmware
+creates a basis for the development of a data protocol for exchanging
+measured values.
+
+This makes it easy to integrate your own measuring devices into the
+\gls{mrp} ecosystem at a later date. This is only possible with a
+minimal functional hardware and firmware setup and was developed for
+this purpose first.
 
@@
 that are already used in smartphones and are therefore widely available.
+
 A key aspect of this selection was the preference for sensors with
@@
 They were excluded because they require more carefully designed circuits
-and more complicated energy management. In the context of the desired
-goal of developing a cost-efficient and universally expandable Hall
-sensor interface, the decision in favour of digital sensors seems
-appropriate.
+and more complicated energy management.
+
+In the context of the desired goal of developing a cost-efficient and
+universally expandable Hall sensor interface, the decision in favour of
+digital sensors seems appropriate.
 
@@
 process input data, control output devices and performs specific tasks
-according to the program code. It handles communication with sensors,
-actuators and other peripheral devices, processing data and making
-decisions. Firmware is critical to the functioning of devices.
+according to the program code.
+
+It handles communication with sensors, actuators and other peripheral
+devices, processing data and making decisions. Firmware is critical to
+the functioning of devices.
 
@@
 software checks whether known sensors are connected to \gls{i2c} or
-\gls{uart} interfaces. If any are found (using a dedicated \gls{lut}
-with sensor address translation information), the appropriate class
-instances are created and these can later be used to read out
-measurement results.
+\gls{uart} interfaces.
+
+If any are found (using a dedicated \gls{lut} with sensor address
+translation information), the appropriate class instances are created
+and these can later be used to read out measurement results.
 
@@
 \gls{pc}. All implemented microcontroller platforms used (Raspberry Pi
-Pico, STM32F4) have a \gls{usb} slave port. The used usb descriptor is a
-\gls{usb} \gls{cdc}. This is used to emulate a virtual RS232
-communication port using a \gls{usb} port on a \gls{pc} and usually no
-additional driver is needed on modern host systems.
+Pico, STM32F4) have a \gls{usb} slave port.
+
+The used usb descriptor is a \gls{usb} \gls{cdc}. This is used to
+emulate a virtual RS232 communication port using a \gls{usb} port on a
+\gls{pc} and usually no additional driver is needed on modern host
+systems.
 
@@
 \passthrough{\lstinline!secondary!} mode and synchronise the
-measurements based on each sync pulse received. Since the presumed
-\passthrough{\lstinline!primary!} sensor cannot register its own sync
-pulse (because the pin is switched to output), there is a timeout branch
-condition \passthrough{\lstinline!got pulse within 1000ms!} and this
-becomes the \passthrough{\lstinline!primary!} sensor. This means that in
-a chain of sensors there is exactly one
-\passthrough{\lstinline!primary!} and many
-\passthrough{\lstinline!secondary!} sensors. In single-sensor operation,
-this automatically jumps to \passthrough{\lstinline!primary!} sensor
-operation through the
+measurements based on each sync pulse received.
+
+Since the presumed \passthrough{\lstinline!primary!} sensor cannot
+register its own sync pulse (because the pin is switched to output),
+there is a timeout branch condition
+\passthrough{\lstinline!got pulse within 1000ms!} and this becomes the
+\passthrough{\lstinline!primary!} sensor. This means that in a chain of
+sensors there is exactly one \passthrough{\lstinline!primary!} and many
+\passthrough{\lstinline!secondary!} sensors.
+
+In single-sensor operation, this automatically jumps to
+\passthrough{\lstinline!primary!} sensor operation through the
 \passthrough{\lstinline!got impulse within 1000ms!} branch result. The
@@
 implementation here was that there is no numbering or sequence of the
-individual sensors. This means that for the subsequent readout of the
-measurements, it is only important that they are taken at the same
-interval across all sensors. The sensor differentiation takes place
-later in the \gls{mrp} \ref{software-readout-framework}-library by using
-the sensor \gls{uuid}.
+individual sensors.
+
+This means that for the subsequent readout of the measurements, it is
+only important that they are taken at the same interval across all
+sensors. The sensor differentiation takes place later in the \gls{mrp}
+\ref{software-readout-framework}-library by using the sensor \gls{uuid}.
 
@@
 \ref{Voltcraft_GM70_serial_protocol.csv} for connection to a \gls{pc}.
+
 This connectivity makes it possible to make the device compatible with
@@
 \passthrough{\lstinline!RaspberryPi Pico!} with an additional level
-shifter. The Teslameter is connected to the microcontroller using two
-free \gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
+shifter.
+
+The Teslameter is connected to the microcontroller using two free
+\gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
 separate build configuration. In order to be able to read and correctly
@@
 and the rapid development of own analysis and optimization algorithms on
-the other. For this purpose, the library was divided into individual
-modules, which are shown in the graphic
+the other.
+
+For this purpose, the library was divided into individual modules, which
+are shown in the graphic
 \ref{MRP_library_module_high_level_overview.png}. In combination, these
@@
 meta data. This also maps the functionality of a project file, which can
-be executed or passed on repeatedly. This also fulfills the goal of
-making individual user-created algorithms interchangeable. If the user
-now wishes to use a different \gls{cad} algorithm instead of the
-\passthrough{\lstinline!HalbachMRIDesigner!}
+be executed or passed on repeatedly.
+
+This also fulfills the goal of making individual user-created algorithms
+interchangeable. If the user now wishes to use a different \gls{cad}
+algorithm instead of the \passthrough{\lstinline!HalbachMRIDesigner!}
 \cite{HalbachMRIDesigner}, the other steps can simply be preserved
@@
 specialized functions designed for the creation and addition of data
-records. To configure parameters, ensuring a tailored approach to the
-entire measurement process, these parameters act as a crucial bridge
-between user preferences and the robust capabilities of the
+records.
+
+To configure parameters, ensuring a tailored approach to the entire
+measurement process, these parameters act as a crucial bridge between
+user preferences and the robust capabilities of the
 \passthrough{\lstinline!MRPReading!} module.
@@
 play. This module is specifically designed for the storage of physical
-parameters pertaining to the magnets targeted for measurement. By
-centralizing this information, users can streamline the subsequent
+parameters pertaining to the magnets targeted for measurement.
+
+By centralizing this information, users can streamline the subsequent
 phases of evaluation and analysis, simplifying the overall process and
@@
 hand, the focus during development was that it is also possible to use
-the data in other programs. For this purpose, an open, documented export
-format must be selected. Ideally, this should be human-readable and
-viewable with a simple text editor. This eliminates all binary-based
-formats such as the Python pickle built into Python.
+the data in other programs.
+
+For this purpose, an open, documented export format must be selected.
+Ideally, this should be human-readable and viewable with a simple text
+editor. This eliminates all binary-based formats such as the Python
+pickle built into Python.
 
@@
 \gls{json} format, all measurement points and metadata are available in
-readable plain text. This means that they can also be read out in other
-programs. Using serialization, the \passthrough{\lstinline!MRPReading!}
-class inherited from Python-\passthrough{\lstinline!Object!} class is
-serialized via an dictionary conversion step. This \gls{json} string can
-then be processed directly or written to the file system as a file.
+readable plain text.
+
+This means that they can also be read out in other programs. Using
+serialization, the \passthrough{\lstinline!MRPReading!} class inherited
+from Python-\passthrough{\lstinline!Object!} class is serialized via an
+dictionary conversion step. This \gls{json} string can then be processed
+directly or written to the file system as a file.
 
@@
 make it difficult to install multiple sensors in measurement setups
-where space or cable routing options are limited. So multibe sensor can
-be connected to any \gls{pc} which is available on the network. This can
-be a \gls{sbc} (e.g.~a Raspberry Pi). The small footprint and low power
-consumption make it a good choice. It can also be used in a temperature
-chamber.
+where space or cable routing options are limited.
+
+Multibe sensor can be connected to any \gls{pc} which is available on
+the network. This can be a \gls{sbc} (e.g.~a Raspberry Pi). The small
+footprint and low power consumption make it a good choice. It can also
+be used in a temperature chamber.
 
@@
 Individual sensor setups do not require any additional synchronisation
-information, as this is communicated via the \gls{usb} interface. If
-several sensors are connected locally, they can be connected to each
+information, as this is communicated via the \gls{usb} interface.
+
+If several sensors are connected locally, they can be connected to each
 other via their sync input using short cables. One sensor acts as the
@@
 measurement points are added in the form of
-\passthrough{\lstinline!MRPReadingEntry!} instances. An important point
-is the management of the meta data, which further describes the
-measurement. This is realised in the example using the
+\passthrough{\lstinline!MRPReadingEntry!} instances.
+
+An important point is the management of the meta data, which further
+describes the measurement. This is realised in the example using the
 \passthrough{\lstinline!set\_additional\_data!} function.
@@
 fields. The result is a complete \passthrough{\lstinline!MRPReading!}
-measurement with a wide range of set meta data. The example
-\ref{lst:mrpexample_simulation} illustrated the basic usage. Different
-variations of the \passthrough{\lstinline!generate\_reading!} function
-offers the user additional parameterisation options, such as random
-polarisation direction or a defined centre-of-gravity vector. The data
-is generated in the background using the
+measurement with a wide range of set meta data.
+
+The example \ref{lst:mrpexample_simulation} illustrated the basic usage.
+Different variations of the \passthrough{\lstinline!generate\_reading!}
+function offers the user additional parameterisation options, such as
+random polarisation direction or a defined centre-of-gravity vector. The
+data is generated in the background using the
 \passthrough{\lstinline!magpylib!} \cite{ortner2020magpylib} library
@@
 functions for this purpose. The code example shows the basic use of the
-module. The \textbf{Evaluation} \ref{evaluation} chapter shows how the
-user can implement their own algorithms and add them to the library.
+module. The \passthrough{\lstinline!Evaluation!} \ref{evaluation}
+chapter shows how the user can implement their own algorithms and add
+them to the library.
 
@@
 specified. This is necessary so that the correct magnet cutouts can be
-generated when creating the 3D model. After the measurements have been
-generated, they are provided with a position and rotation offset
-according to the Hallbach design and calucation scheme
-\cite{HallbachMagnetDesignPaper} using the
+generated when creating the 3D model.
+
+After the measurements have been generated, they are provided with a
+position and rotation offset according to the Hallbach design and
+calucation scheme \cite{HallbachMagnetDesignPaper} using the
 \passthrough{\lstinline!MRPHallbachArrayGenerator!} module.
@@
 experience. Continuous feedback through automated tests and
-comprehensive error logs enable faster bug fixing. The integration of
-user feedback and regular updates promotes the adaptability of the
-\gls{mrp}-library. Effective usability improvements help to speed up
-development processes and increase the satisfaction of the developer
-community. In the following, some of these have been added in and around
-the \gls{mrp}-library, but they are only optional components for the
-intended use.
+comprehensive error logs enable faster bug fixing.
+
+The integration of user feedback and regular updates promotes the
+adaptability of the \gls{mrp}-library. Effective usability improvements
+help to speed up development processes and increase the satisfaction of
+the developer community. In the following, some of these have been added
+in and around the \gls{mrp}-library, but they are only optional
+components for the intended use.
 
@@
 configuring the measurement parameters and metadata and quickly required
-more than 100 lines of new Python code. Although such examples are
-provided in the documentation, it must be possible for programming
-beginners in particular to use them. To simplify these tasks, a
-\gls{cli} \ref{example_measurement_analysis_pipeline.png} was
-implemented. The libaray \gls{cli} implements the following
-functionalities:
+more than 100 lines of new Python code.
+
+Although such examples are provided in the documentation, it must be
+possible for programming beginners in particular to use them. To
+simplify these tasks, a \gls{cli}
+\ref{example_measurement_analysis_pipeline.png} was implemented. The
+libaray \gls{cli} implements the following functionalities:
 
@@
 for the user is to write their own evaluation scripts using the
-\gls{mrp}-library. This is particularly useful for complex analyses or
-custom algorithms, but not necessarily for simple standard tasks such as
-bias compensation or graphical plot outputs.
+\gls{mrp}-library.
+
+This is particularly useful for complex analyses or custom algorithms,
+but not necessarily for simple standard tasks such as bias compensation
+or graphical plot outputs.
 
@@
 consists of sections which execute the appropriate Python commands in
-the background. The signatures in the \passthrough{\lstinline!yaml!}
-file are called using \passthrough{\lstinline!reflection!} and a
-real-time search of the loaded \passthrough{\lstinline!global()!}
-functions symbol table \cite{PythonGlobalSymbolTable}. This system
-makes almost all Python functions available to the user. To simplify
-use, a pre-defined list of verified functions for use in pipelines is
-listed in the documentation
+the background.
+
+The signatures in the \passthrough{\lstinline!yaml!} file are called
+using \passthrough{\lstinline!reflection!} and a real-time search of the
+loaded \passthrough{\lstinline!global()!} functions symbol table
+\cite{PythonGlobalSymbolTable}. This system makes almost all Python
+functions available to the user. To simplify use, a pre-defined list of
+verified functions for use in pipelines is listed in the documentation
 \cite{MagneticReadoutProcessingReadTheDocs}. The following pipeline
@@
 next function to be executed (see comments in
-\ref{lst:mrpuddp_example_yaml}). It is therefore also possible to use
-the results of one function in several others without them directly
-following each other. The disadvantages of this system are the
-following:
+\ref{lst:mrpuddp_example_yaml}).
+
+It is therefore also possible to use the results of one function in
+several others without them directly following each other. The
+disadvantages of this system are the following:
 
@@
 errors and vulnerabilities before software is published as a new
-version. This significantly improves the reliability of
-\gls{mrp}-library applications. Tests also ensures consistent and
-reliable performance, which is particularly important when libraries are
-used by different users and for different usecases.
+version.
+
+This significantly improves the reliability of \gls{mrp}-library
+applications. Tests also ensures consistent and reliable performance,
+which is particularly important when libraries are used by different
+users and for different usecases.
 
@@
 \passthrough{\lstinline!N45 12x12x12mm!} neodymium magnets were used
-here. These were placed in modified 3D printed holders
+here.
+
+These were placed in modified 3D printed holders
 \ref{Ten_numbered_test_magnets_in_separate_holders.png} and then
@@
 As this is a short algorithm, it was inserted directly into the file.
+
 The parameter \passthrough{\lstinline!\_readings!} should later receive
@@
 microcontrollers, which enables an easily expandable and applicable
-solution for measuring magnets with repeatable accuracy. A particular
-focus was placed on expandability by the user. Interchangeable modules
-allow the user to develop their own analysis algorithms without having
-to redesign everything from scratch.
+solution for measuring magnets with repeatable accuracy.
+
+A particular focus was placed on expandability by the user.
+Interchangeable modules allow the user to develop their own analysis
+algorithms without having to redesign everything from scratch.
 

### 2024-01-16 documentation/thesis/thesis_document.tex
more thesis
v3

@@
 compared to conventional high-field \gls{mri} scanners. Typically, the
-magnetic field in low-field MRI systems between
+magnetic field in low-field MRI systems measured between
 \passthrough{\lstinline!0.1T!} and \passthrough{\lstinline!0.3T!}
@@
 
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Example_hallbach_ring_magnet_with_cutouts_for_eight_cubical_permanent_magnets.png}
-\caption{Example hallbach ring magnet with cutouts for eight cubical
-permanent magnets
-\label{Example_hallbach_ring_magnet_with_cutouts_for_eight_cubical_permanent_magnets.png}}
-\end{figure}
+\%\%Example\_hallbach\_ring\_magnet\_with\_cutouts\_for\_eight\_cubical\_permanent\_magnets.png\%\%
 
@@
 \item
-  \textbf{Material}
-
-  The magnetic properties of a material influence the generated field
-  strength. Different materials have different magnetic
+  \textbf{Material}: The magnetic properties of a material influence the
+  generated field strength. Different materials have different magnetic
   susceptibilities.
 \item
-  \textbf{Magnetization}
-
-  The orientation of the magnetic moments in the material influences the
-  field strength. A higher magnetization leads to a stronger field
-  strength.
-\item
-  \textbf{Temperature}
-
-  Temperature can influence the magnetic properties of a material. The
-  magnetization of some materials decreases with increasing temperature.
-\item
-  \textbf{Manufacturing process}
-
-  The manufacturing process can influence the magnetic properties of the
-  material. This is dependent on the purity of the starting materials
-  used and the processing methods. There may also be deviations in field
-  strength if different magnets from different production batches are
-  compared.
+  \textbf{Magnetization}: The orientation of the magnetic moments in the
+  material influences the field strength. A higher magnetization leads
+  to a stronger field strength.
+\item
+  \textbf{Temperature}: Temperature can influence the magnetic
+  properties of a material. The magnetization of some materials
+  decreases with increasing temperature.
+\item
+  \textbf{Manufacturing process}: The manufacturing process can
+  influence the magnetic properties of the material. This is dependent
+  on the purity of the starting materials used and the processing
+  methods. There may also be deviations in field strength if different
+  magnets from different production batches are compared.
 \end{itemize}
@@
 
-\begin{itemize}
-\item
-  Chapter \ref{state-of-the-art}. \textbf{State of the Art} describes
-  the current state of technology and forms the basis for further
-  development. Existing measurement methods and findings are shown here
-  in order to define the context for the current project.
-\item
 Chapter \ref{usecases}. \textbf{Usecases} are the application cases in
-  which the project is to be used. They illustrate the practical
-  scenarios and define how the product can be used in the real world.
-  This is crucial for understanding the needs of the target group and
-  designing the end result accordingly.
-\item
+which the project is to be used. They illustrate the practical scenarios
+and define how the product can be used in the real world. This is
+crucial for understanding the needs of the target group and designing
+the end result accordingly.
+
 Chapter \ref{unified-sensor}. \textbf{Unified Sensor} refers to the
 integration of different sensors into a standardised solution. This
-  enables simple data acquisition and serves as a basic hardware system
-  on which the subsequent data processing library can be applied.
-\item
+enables simple data acquisition and serves as a basic hardware system on
+which the subsequent data processing library can be applied.
+
 Chapter \ref{software-readout-framework}. \textbf{Software Readout
@@
 application examples.
-\item
+
 Chapter \ref{usability-improvements}. \textbf{Usability Improvements}
@@
 package to users.
-\item
+
 Chapter \ref{evaluation}. \textbf{Evaluation} comprises the systematic
@@
 against the previously defined usecases.
-\end{itemize}
 
@@
 
-This ensures broad applicability in different scenarios. Another goal is
-reproducibility to ensure consistent results. Easy communication with
-standard PC hardware maximises the user-friendliness of the interface.
+This ensures a wide range of applications in different scenarios.
+Another goal is reproducibility to ensure uniform results, which as a
+result reduces the susceptibility to errors. Easy communication with
+standard \gls{pc} hardware, which offers a variety of common interface
+options, maximizes the user-friendliness.
 
@@
 \centering
-\includegraphics{./generated_images/border_1D_sensor_mechanical_3D_printed_structure.png}
-\caption{1D sensor mechanical 3D printed structure
-\label{1D_sensor_mechanical_3D_printed_structure.png}}
+\includegraphics{./generated_images/border_Mechanical_components_for_the_1D_sensor_using_3D_printed_parts.png}
+\caption{Mechanical components for the 1D sensor using 3D printed parts
+\label{Mechanical_components_for_the_1D_sensor_using_3D_printed_parts.png}}
 \end{figure}
@@
 The following figure
-\ref{1D_sensor_mechanical_3D_printed_structure.png}, shows a sectional
-view of the \gls{cad} drawing of the 1D-Single sensor
+\ref{Mechanical_components_for_the_1D_sensor_using_3D_printed_parts.png},
+shows a sectional view of the \gls{cad} drawing of the 1D-Single sensor
 \ref{d-single-sensor}.
@@
 
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Unified_sensor_firmware_simplified_program_structure.png}
+\caption{Unified sensor firmware simplified program structure
+\label{Unified_sensor_firmware_simplified_program_structure.png}}
+\end{figure}
+
 The microcontroller firmware is software that is executed on a
@@
 the functioning of devices.
-
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Unified_sensor_firmware_simplified_program_strucutre.png}
-\caption{Unified sensor firmware simplified program strucutre
-\label{Unified_sensor_firmware_simplified_program_strucutre.png}}
-\end{figure}
 
@@
 The flow chart
-\ref{Unified_sensor_firmware_simplified_program_strucutre.png} shows the
+\ref{Unified_sensor_firmware_simplified_program_structure.png} shows the
 start process and the subsequent main loop for processing the user
@@
 
-After the setup process is complete, the system switches to an infinite
-loop, which processes several possible actions. One task is, to react to
-user commands which can be sent to the system by the user via the
-integrated \gls{cli}. All sensors are read out via a timer interval set
-in the setup procedure and their values are stored in a ringbuffer. Ring
-buffer offers efficient data management in limited memory. Its cyclic
-structure enables continuous overwriting of older data, saves memory
-space and facilitates seamless processing of real-time data.
+After execution of the setup routine is completed, the system switches
+to an infinite loop, which processes several possible actions. One task
+is, to react to user commands which can be sent to the system by the
+user via the integrated \gls{cli}. All sensors are read out via a timer
+interval set in the setup procedure and their values are stored in a
+ringbuffer. Ring buffer offers efficient data management in limited
+memory. Its cyclic structure enables continuous overwriting of older
+data, saves memory space and facilitates seamless processing of
+real-time data.
 
@@
 \hypertarget{communication-interface}{%
-\subsection{Communication interface}\label{communication-interface}}
+\subsection{Communication Interface}\label{communication-interface}}
 
@@
 \hypertarget{example-sensors}{%
-\section{Example sensors}\label{example-sensors}}
+\section{Example Sensors}\label{example-sensors}}
 
@@
 Since the \passthrough{\lstinline!MMC5603NJ!} only has limited
-measurement range of total \passthrough{\lstinline!6uT!}, even small
-coin sized neodymium magnets already saturates the sensor. It is
-possible to mount 3D printed spacers over the sensor to increase the
-distance between the magnet and the sensor and thus also measure these
-magnets.
+measurement range of total 6uT, even small coin sized neodymium magnets
+already saturates the sensor. It is possible to mount 3D printed spacers
+over the sensor to increase the distance between the magnet and the
+sensor and thus also measure these magnets.
 
@@
 \hypertarget{integration-of-an-industry-teslameter}{%
-\subsection{Integration of an industry
-teslameter}\label{integration-of-an-industry-teslameter}}
+\subsection{Integration of an
+Industry-Teslameter}\label{integration-of-an-industry-teslameter}}
 
@@
 \ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
-used, which has a measuring range of \passthrough{\lstinline!0-3T!} with
-a resolution of \passthrough{\lstinline!0.1mT!}. It offers an
-\passthrough{\lstinline!RS232!} interface with a documented protocol
+used, which has a measuring range of 0T to 3T with a resolution of
+0.1mT. It offers an RS232 interface with a documented protocol
 \ref{Voltcraft_GM70_serial_protocol.csv} for connection to a \gls{pc}.
@@
 This connectivity makes it possible to make the device compatible with
-the Unified Sensor ecosystem using a separate interface software
+the unified sensor ecosystem using a separate interface software
 \cite{VoltcraftGM70Rest} executable on the host \gls{pc}. However,
-it does not offer the range of functions that the Unified Sensor
+it does not offer the range of functions that the unified sensor
 firmware offers.
-
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png}
-\caption{Voltcraft GM70 teslameter with custom \gls{pc} interface board
-\label{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png}}
-\end{figure}
 
@@
 This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
-offer an physical \passthrough{\lstinline!RS232!} interface. As with the
-other sensors, this interface consists of your
-\passthrough{\lstinline!RaspberryPi Pico!} with an additional level
-shifter.
-
-The Teslameter is connected to the microcontroller using two free
+offer an physical RS232 interface. As with the other sensors, this
+interface consists of your \passthrough{\lstinline!Raspberry-Pi Pico!}
+with an additional level shifter.
+
+The teslameter is connected to the microcontroller using two free
 \gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
@@
 \ref{lst:CustomSensorClass}.
+
+This software or hardware integration can be carried out on any other
+measuring device with a suitable communication interface and a known
+protocol thanks to the modular design.
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png}
+\caption{Voltcraft GM70 teslameter with custom \gls{pc} interface board
+\label{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png}}
+\end{figure}
 
@@
 
-This software or hardware integration can be carried out on any other
-measuring device with a suitable communication interface and a known
-protocol thanks to the modular design.
-
 \hypertarget{software-readout-framework}{%
-\chapter{Software readout framework}\label{software-readout-framework}}
+\chapter{Software Readout Framework}\label{software-readout-framework}}
 
@@
 \section{User Interaction Points}\label{user-interaction-points}}
-
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_MRP_library_module_high_level_overview.png}
-\caption{MRP library module high level overview
-\label{MRP_library_module_high_level_overview.png}}
-\end{figure}
 
@@
 
+\newpage
+
 According to this concept, the user should be able to replace individual
@@
 worry about implementing other of these to make the project work.
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_MRP_library_module_high_level_overview.png}
+\caption{MRP library module high level overview
+\label{MRP_library_module_high_level_overview.png}}
+\end{figure}
 
@@
 function provided as input parameters using a \gls{json} file. The
-result is then an \passthrough{\lstinline!OpenSCAD!} \cite{OpenSCAD}
+result is an \passthrough{\lstinline!OpenSCAD!} \cite{OpenSCAD}
 based 3D model of the magnet holder.
@@
 of optimizing and creating Hallbach magnets for \gls{mri} applications.
-However, their data structures are not compatible with each other.
-However, they are executed manually one after the other in order to
-obtain a final result.
+The data structures are not compatible with each other. However, they
+are executed manually one after the other to obtain a final result with
+manual data conversation.
 
@@
 standardized and flexible data structures for use with this form of
-magnetic field data. On the other hand, by separating the processing
-pipeline into defined sub-steps, it should be possible to make
-individual modules and as a result functionalities interchangeable by
-the user.
+magnetic field data. By separating the processing pipeline into defined
+sub-steps, it should be possible to make individual modules and as a
+result functionalities interchangeable by the user.
 
@@
 step, in this case the generated magnet data. By optionally setting meta
-data in the universal bilbiothekt data type, constants can be replaced
-in the analysis function and made dynamically configurable. The return
+data in the universal library data type, constants can be replaced in
+the analysis function and made dynamically configurable. The return
 result also corresponds to this data type so that subsequent steps are
@@
 
-After these customization steps, it is possible to execute both projects
+After these customisation steps, it is possible to execute both projects
 one after the other and all required configuration parameters are
@@
 In order to realise the concept of user interaction points, the library
-was divided into different modules. These can be divided into two main
-categories:
+was divided into different modules. These modules can be divided into
+two main categories:
 
@@
 \item
-  Extensions - Contains modules for visualizations, hardware sensor
+  Extensions - Contains modules for visualisations, hardware sensor
   access
@@
 \hypertarget{storage-and-datamanagement}{%
-\subsubsection{Storage and
+\subsection{Storage and
 Datamanagement}\label{storage-and-datamanagement}}
@@
 \item
-  \passthrough{\lstinline!data!} - Measured values with value and
-  measured value \gls{uuid}
+  \passthrough{\lstinline!data!} - Datapoint storage consists of
+  measured value, \gls{uuid} and temperature, among other parameters
 \item
@@
 \passthrough{\lstinline!Numpy!} \cite{harris2020array}, or the
-program for mathematical calculations, Matlab are often used, the
-library also supports export formats for these systems.
+program for mathematical calculations, \passthrough{\lstinline!MATLAB!}
+are often used, the library also supports export formats for these
+systems.
 
@@
 \item
-  \passthrough{\lstinline!.dump\_savemat()!} - Matlab mat-file with
-  measurement values and temperatures
+  \passthrough{\lstinline!.dump\_savemat()!} -
+  \passthrough{\lstinline!MATLAB!} mat-file with measurement values and
+  temperatures
 \end{itemize}
@@
 via the \gls{json} format, as an export using the other options
-(\passthrough{\lstinline!Numpy!}, \passthrough{\lstinline!Matlab!})loses
-data during the export procedure. \}
+(\passthrough{\lstinline!Numpy!}, \passthrough{\lstinline!MATLAB!})loses
+data during the export procedure.
 
@@
 additional basic functionalities. These include functions for data
-acquisition, visualization and analysis.
+acquisition, visualisation and analysis.
 
@@
 \item
-  \passthrough{\lstinline!std\_deviation!} - standard deviation
-\item
-  \passthrough{\lstinline!mean!} - mean value
-\item
-  \passthrough{\lstinline!variance!} - variance
-\item
-  \passthrough{\lstinline!center\_of\_gravity!} - center of gravity
-\item
-  \passthrough{\lstinline!binning!} - distribution of a sample by means
+  \passthrough{\lstinline!std\_deviation!} - Standard deviation
+\item
+  \passthrough{\lstinline!mean!} - Mean value
+\item
+  \passthrough{\lstinline!variance!} - Variance
+\item
+  \passthrough{\lstinline!center\_of\_gravity!} - Center of gravity
+\item
+  \passthrough{\lstinline!binning!} - Distribution of a sample by means
   of a histogram
 \item
-  \passthrough{\lstinline!k-nearest!} - k-nearest neighbors
+  \passthrough{\lstinline!k-nearest!} - K-nearest neighbors
 \end{itemize}
@@
 \passthrough{\lstinline!control!} \gls{pc}, but the proxy instance
-\passthrough{\lstinline!remote!}\gls{pc}\passthrough{\lstinline!\#2!}
-can acces the proxy running on
-\passthrough{\lstinline!remote!}\gls{pc}\passthrough{\lstinline!\#1!}.
+\passthrough{\lstinline!remote!}\gls{pc} \passthrough{\lstinline!\#2!}
+can acces the proxy running on \passthrough{\lstinline!remote!}\gls{pc}
+\passthrough{\lstinline!\#1!}.
 
@@
 many \gls{sbc}, such as the
-\passthrough{\lstinline!Raspberry-Pi Compute Module 4!}.
+\passthrough{\lstinline!Raspberry-Pi Compute Module!}.
 
@@
 \hypertarget{merging-the-sensor-capabilities}{%
-\subsubsection{Merging the sensor
-capabilities}\label{merging-the-sensor-capabilities}}
+\subsubsection{Merging the Sensor
+Capabilities}\label{merging-the-sensor-capabilities}}
 
@@
 command of each sensor is queried. This information is added to the
-previously created \gls{lut}. Duplicate entries are summarized (see
+previously created \gls{lut}. Duplicate entries are summarised (see
 Table \ref{Sensor_capabilities_merging_algorithm.csv}) and returned to
@@
 \hypertarget{dynamic-extension-of-the-available-network-proxy-commands}{%
-\subsubsection{Dynamic extension of the available network proxy
-commands}\label{dynamic-extension-of-the-available-network-proxy-commands}}
+\subsubsection{Dynamic extension of the available Network-Proxy
+Commands}\label{dynamic-extension-of-the-available-network-proxy-commands}}
 
@@
 \passthrough{\lstinline!CAPABLE SENSORS ID LUT!}
-\ref{Sensor_capabilities_merging.csv}, there are two possible approaches
-to how the command is processed:
+\ref{Sensor_capabilities_merging_algorithm.csv}, there are two possible
+approaches to how the command is processed:
 
@@
 \item
-  \passthrough{\lstinline!readsensor <axis> <sensor number>!}-\textgreater{}
-  \passthrough{\lstinline!readsensor <axis> <ID>!}
+  \passthrough{\lstinline!readsensor <axis> <sensor number>!}
+  -\textgreater{} \passthrough{\lstinline!readsensor <axis> <ID>!}
 \item
@@
 
-\begin{lstlisting}[language=Python, caption={MRPHal example to use an connected hardware sensor to store readings inside of an measurement}, label=lst:mrpexample_hal]
+\begin{lstlisting}[language=Python, caption={MRPHal example to use an connected hardware sensor to store readings inside of a measurement}, label=lst:mrpexample_hal]
 from MRP import MRPHalSerialPortInformation, MRPHal, MRPBaseSensor, MRPReadingSource
@@
 
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
-\caption{Example full sphere plot of an measurement using the
-MRPVisualisation module
-\label{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}}
-\end{figure}
-
-This final example shows the use of the MRP Visualisation module, which
-provides general functions for visualising measurements. This makes it
-possible to visually assess the results of a measurement. This is
-particularly helpful for full-sphere measurements recorded with the
-\passthrough{\lstinline!3D: Fullsphere!} \ref{d-fullsphere} sensor. The
-sub-module \passthrough{\lstinline!MRPPolarVisualisation!} is specially
-designed for these. The figure
+This final example shows the use of the
+\passthrough{\lstinline!MRPVisualisation!} module, which provides
+general functions for visualising measurements. The visualisation
+optionsmakes it possible to visually assess the results of a
+measurement. This is particularly helpful for full-sphere measurements
+recorded with the \passthrough{\lstinline!3D: Fullsphere!}
+\ref{d-fullsphere} sensor. The sub-module
+\passthrough{\lstinline!MRPPolarVisualisation!} is specially designed
+for these. The figure
 \ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
-shows a plot of a fullsphere measurement.
-
-It is also possible to export the data from the MRPAnalysis module
+shows a plot of a fullsphere measurement. It is also possible to export
+the data from the \passthrough{\lstinline!MRPAnalysis!} module
 graphically as diagrams. The \passthrough{\lstinline!MRPVisualisation!}
@@
 visu.plot3d(os.path.join('./plot3d_3d.png'))
-
 # PLOT ANALYSIS RESULTS
@@
 
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
+\caption{Example full sphere plot of an measurement using the
+MRPVisualisation module
+\label{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}}
+\end{figure}
+
 \hypertarget{mrphallbacharraygenerator}{%
@@
 
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}
-\caption{Generated hallbach array with generated cutouts for eight
-magnets
-\label{Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}}
-\end{figure}
-
 The following example code \ref{lst:mrpexample_hallbach}, shows how a
-simple hallbach magnetic ring can be generated.
+simple Hallbach magnetic ring can be generated.
 
 This can then be used to construct a Halbach ring magnet (see chapter
-\ref{Charakterisation of Permanent Magnets}) for a low-field \gls{mri}.
+\ref{magnet-system}) for a low-field \gls{mri}.
 
@@
 model rendering
-\ref{Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}
+\ref{Generated_Hallbach_array_with_generated_cutouts_for_eight_magnets.png}
 can be generated.
 
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Generated_Hallbach_array_with_generated_cutouts_for_eight_magnets.png}
+\caption{Generated Hallbach array with generated cutouts for eight
+magnets
+\label{Generated_Hallbach_array_with_generated_cutouts_for_eight_magnets.png}}
+\end{figure}
+
 \hypertarget{usability-improvements}{%
-\chapter{Usability improvements}\label{usability-improvements}}
+\chapter{Usability Improvements}\label{usability-improvements}}
 
@@
   Simple commands for checking recorded measurement series and their
-  data.
+  data
 \end{itemize}
@@
 connect a sensor to the \gls{pc}, configure a measurement series with it
-and run it at the end. The result is then an exported file with the
-measured values. These can then be read in again using the
+and run it at the end. The result is an exported file with the measured
+values. These can then be read in again using the
 \passthrough{\lstinline!MRPReading!} module and processed further. The
@@
 \hypertarget{programmable-data-processing-pipeline}{%
-\section{Programmable data processing
-pipeline}\label{programmable-data-processing-pipeline}}
+\section{Programmable Data Processing
+Pipeline}\label{programmable-data-processing-pipeline}}
 
@@
 
-\begin{itemize}
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
 \tightlist
@@
   Create a graphical plot of all measurements with standard deviation
-\end{itemize}
+\end{enumerate}
 
@@
 which contain a name, the function to be executed and its parameters.
+
+\newpage
+
 The various steps are then linked by using the
@@
 represents a node in the graph and the steps referred to by the input
-parameter form the edges.
+parameter form the edges. After several simplification steps,
+determination of possible start steps and repeated traversal, the final
+execution sequence can be determined in the form of a call tree
+\ref{Example_result_of_an_step_execution_tree_from_user_defined_processing_pipeline.png}.
+The individual steps are then executed along the graph. The intermediate
+results and the final results
+\ref{pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
+are saved for optional later use.
 
@@
 \centering
-\includegraphics{./generated_images/border_Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}
-\caption{Result step execution tree from user defined processing
-pipeline example
-\label{Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}}
+\includegraphics{./generated_images/border_Example_result_of_an_step_execution_tree_from_user_defined_processing_pipeline.png}
+\caption{Example result of an step execution tree from user defined
+processing pipeline
+\label{Example_result_of_an_step_execution_tree_from_user_defined_processing_pipeline.png}}
 \end{figure}
@@
 
-After several simplification steps, determination of possible start
-steps and repeated traversal, the final execution sequence can be
-determined in the form of a call tree
-\ref{Result_step_execution_tree_from_user_defined_processing_pipeline_example.png}.
-The individual steps are then executed along the graph. The intermediate
-results and the final results
-\ref{pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
-are saved for optional later use.
-
 \hypertarget{testing}{%
 \section{Testing}\label{testing}}
-
-Software tests in libraries offer numerous advantages for improving
-quality and efficiency. Firstly, they enable the identification of
-errors and vulnerabilities before software is published as a new
-version.
-
-This significantly improves the reliability of \gls{mrp}-library
-applications. Tests also ensures consistent and reliable performance,
-which is particularly important when libraries are used by different
-users and for different usecases.
 
@@
 \end{figure}
+
+Software tests in libraries offer numerous advantages for improving
+quality and efficiency. Software tests make it possible to identify
+errors and vulnerabilities before the software is released as a new
+version.
+
+This significantly improves the reliability of \gls{mrp}-library
+applications. Tests also ensures consistent and reliable performance,
+which is particularly important when libraries are used by different
+users and for different usecases.
 
@@
 
-One problem, however, is the parts of the \gls{mrp}-library that require
-direct access to external hardware. These are, for example, the
+One problem, is the parts of the \gls{mrp}-library that require direct
+access to external hardware. These are, for example, the
 \passthrough{\lstinline!MRPHal!} and
@@
 run could be carried out with real data.
+
+\newpage
 
@@
 \hypertarget{package-distribution}{%
-\section{Package distribution}\label{package-distribution}}
+\section{Package Distribution}\label{package-distribution}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_MagneticReadoutProcessing_library_hosted_on_PyPi.png}
+\caption{MagneticReadoutProcessing library hosted on PyPi
+\label{MagneticReadoutProcessing_library_hosted_on_PyPi.png}}
+\end{figure}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_MagneticReadoutProcessing_library_hosted_on_PyPi.png}
-\caption{MagneticReadoutProcessing library hosted on PyPi
-\label{MagneticReadoutProcessing_library_hosted_on_PyPi.png}}
-\end{figure}
-
-In doing so, \gls{pip} not only manages possible package dependencies,
-but also manages the installation of different versions of a package. In
+\gls{pip} not only manages possible package dependencies, but also
+manages the installation of different versions of a package. In
 addition, the version compatibility is also checked during the
@@
 
-To make the \gls{mrp} file strucutre compatible with the package
+To make the \gls{mrp} file structure compatible with the package
 registry, Python provides separate installation routines that build a
@@
 \passthrough{\lstinline!wheel!} archive. This can then be uploaded to
-the package registry.
-
-Since the \gls{mrp}-library requires additional Python dependencies
-(e.g.~\passthrough{\lstinline!numpy!},
+the package registry. Since the \gls{mrp}-library requires additional
+Python dependencies (e.g.~\passthrough{\lstinline!numpy!},
 \passthrough{\lstinline!matplotlib!} packages), which cannot be assumed
@@
 Python-\passthrough{\lstinline!docstrings!}
-\cite{PythonDocstringReference} and the Python3.5 type annotations:
+\cite{PythonDocstringReference} and the Python 3.5 type annotations:
 
@@
 various source code documentation formats, such as the used
-\passthrough{\lstinline!docstrings!}. These are converted into a
-Markdown format in an intermediate step and this also allows to add
-further user documentation such as examples or installation
-instructions. In order to make the documentation created by
+\passthrough{\lstinline!docstrings!}.
+
+These are converted into a Markdown format in an intermediate step and
+this also allows to add further user documentation such as examples or
+installation instructions. In order to make the documentation created by
 \passthrough{\lstinline!Sphinx!} accessible to the user, there are, as
@@
 which provide the \gls{mrp}-library documentation online.
+
+Once the finished documentation has been generated from static
+\gls{html} files, it is stored in the project repository. Another
+publication option is to host the documentation via online services such
+as \passthrough{\lstinline!ReadTheDocs!} \cite{ReadTheDocs}, where
+users can make documentation for typical software projects available to
+others.
+
+The documentation has also been uploaded to
+\passthrough{\lstinline!ReadTheDocs!}
+\cite{MagneticReadoutProcessingReadTheDocs} and linked in the
+repository and on the overview page
+\ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
+on \passthrough{\lstinline!PyPi!}.
+
+The process of creating and publishing the documentation has been
+automated using \passthrough{\lstinline!GitHub Actions!}, so that it is
+always automatically kept up to date with new features.
 
@@
 
-Once the finished documentation has been generated from static
-\gls{html} files, it is stored in the project repository. Another
-publication option is to host the documentation via online services such
-as \passthrough{\lstinline!ReadTheDocs!} \cite{ReadTheDocs}, where
-users can make documentation for typical software projects available to
-others.
-
-The documentation has also been uploaded to
-\passthrough{\lstinline!ReadTheDocs!}
-\cite{MagneticReadoutProcessingReadTheDocs} and linked in the
-repository and on the overview page
-\ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
-on \passthrough{\lstinline!PyPi!}.
-
-The process of creating and publishing the documentation has been
-automated using \passthrough{\lstinline!GitHub Actions!}, so that it is
-always automatically kept up to date with new features.
-
 \hypertarget{evaluation}{%
@@
 analysing the measurement data. The process of this framework comprises
-several steps, which I will explain below:
+several steps, which will be explain below:
 
@@
 \item
-  \textbf{Hardware preperation} Users can prepare measurements using the
-  implemented framework. This includes the placement of the sensors and
-  the selection of the relevant parameters for the characterisation of
-  the permanent magnets.
-\item
-  \textbf{Configuration of the measurement} The software provides a
+  \textbf{Hardware preperation}: Users can prepare measurements using
+  the implemented framework. This includes the placement of the sensors
+  and the selection of the relevant parameters for the characterisation
+  of the permanent magnets.
+\item
+  \textbf{Configuration of the measurement}: The software provides a
   user-friendly interface for configuring the measurement parameters.
@@
 \item
-  \textbf{Custom algorithm implementation} An important contribution of
+  \textbf{Custom algorithm implementation}: An important contribution of
   the \gls{mrp} ecosystem is the possibility for users to implement
@@
 \item
-  \textbf{Execution of analysis pipeline} The analysis pipeline can then
-  be executed with the implemented algorithm. The collected measurement
-  data is automatically processed and analysed to extract characteristic
-  parameters of the permanent magnets.
+  \textbf{Execution of analysis pipeline}: The analysis pipeline can
+  then be executed with the implemented algorithm. The collected
+  measurement data is automatically processed and analysed to extract
+  characteristic parameters of the permanent magnets.
 \end{enumerate}
@@
 the magnets to be measured. Ten random
-\passthrough{\lstinline!N45 12x12x12mm!} neodymium magnets were used
-here.
+\passthrough{\lstinline!N45 12x12x12mm!} neodymium magnets were used,
+which are shown in figure
+\ref{Ten_numbered_test_magnets_in_separate_holders.png}.
 
@@
 \section{Configuration of the
-measurement}\label{configuration-of-the-measurement}}
-
-The configured hardware was then connected and connected to the host
-system using the
+Measurement}\label{configuration-of-the-measurement}}
+
+The configured hardware was then connected to the host system using the
 \passthrough{\lstinline!MRPcli config setupsensor!}-\gls{cli} command.
-The measurement was then configured for an measurement run, using the
-following configuration commands
+Afterwards, the measurement was configured for an measurement run, using
+the following configuration commands
 \ref{lst:evaluation_measurement_config}.
+
+\newpage
 
@@
 \hypertarget{custom-algorithm-implementation}{%
-\section{Custom algorithm
-implementation}\label{custom-algorithm-implementation}}
+\section{Custom Algorithm
+Implementation}\label{custom-algorithm-implementation}}
 
@@
 
-The python \passthrough{\lstinline!heapq!} \cite{heapq} module,
+The Python \passthrough{\lstinline!heapq!} \cite{heapq} module,
 which implements a priority queue, is used for this purpose. The
@@
 \hypertarget{execution-of-analysis-pipeline}{%
-\section{Execution of analysis
-pipeline}\label{execution-of-analysis-pipeline}}
+\section{Execution of Analysis
+Pipeline}\label{execution-of-analysis-pipeline}}
 
@@
 determined \passthrough{\lstinline!Mean [uT]!} mean values is plotted on
-ten individual measured values. Here you can see that there are measured
-values with larger deviations (see measurement
+ten individual measured values. Here it can be seen that there are
+measured values with larger deviations (see measurement
 \passthrough{\lstinline!7:0!},\passthrough{\lstinline!10-2:0!},\passthrough{\lstinline!10-1:0!}).
@@
 seen from the plotted mean values \passthrough{\lstinline!Mean [uT]!}
-that these are closest to the global mean value
-\passthrough{\lstinline!208.8uT!}. The filter algorithm implemented by
-the user was thus successfully executed using the user-programmable
-pipeline. The calculation result was successfully verified using raw
-measurement data and the final result of the algorithm.
+that these are closest to the global mean value 208.8uT. The filter
+algorithm implemented by the user was thus successfully executed using
+the user-programmable pipeline. The calculation result was successfully
+verified using raw measurement data and the final result of the
+algorithm.
 
 \hypertarget{conclusion-and-dicussion}{%
-\chapter{Conclusion and dicussion}\label{conclusion-and-dicussion}}
+\chapter{Conclusion and Dicussion}\label{conclusion-and-dicussion}}
 
@@
 created that can be used directly for the intended purpose. It provides
-a good foundation, but can be further developed by integrating
-professional measurement devices to enable a more comprehensive
-evaluation and improvement of the sensor hardware.
+a suitable working foundation, but can be further developed by
+integrating professional measurement devices to enable a more
+comprehensive evaluation and improvement of the sensor hardware.

### 2024-01-16 documentation/thesis/thesis_document.tex
more thesis

@@
 \item
-  \passthrough{\lstinline!center\_of\_gravity!} - Center of gravity
+  \passthrough{\lstinline!CoG!} - Center of gravity
 \item
@@
 \centering
-\includegraphics{./generated_images/border_mrp_proxy_multi.png}
-\caption{mrp proxy multi \label{mrp_proxy_multi.png}}
+\includegraphics{./generated_images/border_Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png}
+\caption{Example MRP proxy module usage, using two remote \gls{pc}s
+\label{Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png}}
 \end{figure}
 
-The figure \ref{mrp_proxy_multi.png} shows the modified
-\passthrough{\lstinline!multi-proxy - multi-sensor!} topology. Here,
-both proxy instances do not communicate directly with the
-\passthrough{\lstinline!control!} \gls{pc}, but the proxy instance
+The figure
+\ref{Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png} shows
+the modified \passthrough{\lstinline!multi-proxy - multi-sensor!}
+topology. Here, both proxy instances do not communicate directly with
+the \passthrough{\lstinline!control!} \gls{pc}, but the proxy instance
 \passthrough{\lstinline!remote!}\gls{pc} \passthrough{\lstinline!\#2!}
@@
 simplify these tasks, a \gls{cli}
-\ref{example_measurement_analysis_pipeline.png} was implemented. The
+\ref{Example_measurement_analysis_pipeline.png} was implemented. The
 libaray \gls{cli} implements the following functionalities:
@@
 \centering
-\includegraphics{./generated_images/border_example_measurement_analysis_pipeline.png}
-\caption{example measurement analysis pipeline
-\label{example_measurement_analysis_pipeline.png}}
+\includegraphics{./generated_images/border_Example_measurement_analysis_pipeline.png}
+\caption{Example measurement analysis pipeline
+\label{Example_measurement_analysis_pipeline.png}}
 \end{figure}
@@
 measurement data without programming. The example
-\ref{example_measurement_analysis_pipeline.png} shows a typical
+\ref{Example_measurement_analysis_pipeline.png} shows a typical
 measurement data analysis pipeline, which consists of the following
@@
 definition \ref{lst:mrpuddp_example_yaml} shows the previously defined
-steps \ref{example_measurement_analysis_pipeline.png} as
+steps \ref{Example_measurement_analysis_pipeline.png} as
 \passthrough{\lstinline!yaml!} syntax.
@@
 results and the final results
-\ref{pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
+\ref{Pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
 are saved for optional later use.
@@
 \centering
-\includegraphics{./generated_images/border_pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
-\caption{pipeline output files after running example pipeline on a set
+\includegraphics{./generated_images/border_Pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
+\caption{Pipeline output files after running example pipeline on a set
 of readings
-\label{pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}}
+\label{Pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}}
 \end{figure}
@@
 number of best measurements that are returned. The return parameter is a
-list of measurements and should contain the measurements that are
-closest to the mean value of all measurements after the function has
-been executed.
+list of measurements containing the most similar measurements, measured
+by the smallest distance between all measurements. The distance for each
+measurement is determined using the center of gravity function
+\passthrough{\lstinline!CoG!}, the length is then calculated from the
+result vector. This value can then be used for sorting.
 
@@
   import heapq
+  import math
   heap = []
@@
       IP_return_count = len(_readings) / 5
-  # CALCULATE TARGET VALUE: MEAN FROM ALL VALUES
+  # CALCULATE TARGET VALUE: CENTER OF GRAVITY MAGNITUDE FOR ALL READINGS
   target_value = 0.0
   for idx, r in enumerate(_readings):
-      mean: float = MRPAnalysis.MRPAnalysis.calculate_mean(r)
-      target_value = target_value + mean
+      cog_vecotr = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(r)
+      # COMPUTE LENGTH OF VECTOR
+      cog:float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
+      target_value = target_value + cog
   target_value = target_value / len(_readings)
@@
   del heapq
+  del math
   return similar_values
@@
 which implements a priority queue, is used for this purpose. The
-calculated distances from the mean value of the measurements to the
-global mean value are inserted into this queue. Subsequently, as many
+calculated distances from the \passthrough{\lstinline!CoG!} value of the
+measurements to are inserted into this queue. Subsequently, as many
 elements of the queue are returned as defined by the
@@
 pipeline\ref{lst:pipeline_mrp_evaluation_yaml}. Here, the example
-pipeline \ref{example_measurement_analysis_pipeline.png} is simplified
+pipeline \ref{Example_measurement_analysis_pipeline.png} is simplified
 and an additional stage \passthrough{\lstinline!find\_similar\_values!}
@@
 
-The figure \ref{MRP_evaluation_result.png} shows this result. The plot
-of the raw measured values is shown on the left. The variance of the
-determined \passthrough{\lstinline!Mean [uT]!} mean values is plotted on
-ten individual measured values. Here it can be seen that there are
-measured values with larger deviations (see measurement
+The figure
+\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png}
+shows this result. The plot of the raw measured values is shown on the
+left. The value of the determined \passthrough{\lstinline!GoG [uT]!}
+values is plotted on ten individual measured values. Here it can be seen
+that there are measured values with larger deviations (see measurement
 \passthrough{\lstinline!7:0!},\passthrough{\lstinline!10-2:0!},\passthrough{\lstinline!10-1:0!}).
@@
 \centering
-\includegraphics{./generated_images/border_MRP_evaluation_result.png}
-\caption{MRP evaluation result \label{MRP_evaluation_result.png}}
+\includegraphics{./generated_images/border_MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png}
+\caption{MRP evaluation result after execution of the user defined
+pipeline, using find similar values algorithm
+\label{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png}}
 \end{figure}
 
-On the right-hand side \ref{MRP_evaluation_result.png}, the measured
-values are plotted as a result of the filter algorithm. As the
-\passthrough{\lstinline!IP\_return\_count!} parameter was set to four,
-only the four most similar measurements were exported here. It can be
-seen from the plotted mean values \passthrough{\lstinline!Mean [uT]!}
-that these are closest to the global mean value 208.8uT. The filter
-algorithm implemented by the user was thus successfully executed using
-the user-programmable pipeline. The calculation result was successfully
-verified using raw measurement data and the final result of the
-algorithm.
+On the right-hand side
+\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png},
+the measured values are plotted as a result of the filter algorithm. As
+the \passthrough{\lstinline!IP\_return\_count!} parameter was set to
+four, only the four most similar measurements were exported here. It can
+be seen from the plotted \passthrough{\lstinline!CoG [uT]!} deviation
+values, that these are closest to an ideal Magnet with a
+\passthrough{\lstinline!CoG!} value of 0uT. This ideal value was
+calculated with the function
+\passthrough{\lstinline!MRP.MRPSimulation.generate\_simulated\_reading!},
+with the same measurement parameters (magnet type, dimensions, sensor
+distance) as they correspond to the mechanical structure of the used
+hardware sensor \ref{d-fullsphere}. The filter algorithm implemented by
+the user was thus successfully executed using the user-programmable
+pipeline. The calculation result was successfully verified using raw
+measurement data and the final result of the algorithm.
 

### 2024-01-17 documentation/thesis/thesis_document.tex
more thesis
some additions to evaluation

@@
   for idx, r in enumerate(_readings):
-      cog_vecotr = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(r)
+      cog = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(r)
       # COMPUTE LENGTH OF VECTOR
-      cog:float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
+      cog_value: float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
       target_value = target_value + cog
@@
       # USE DIFF AS PRIORITY VALUE IN MIN-HEAP
-      diff = abs(value - target_value)
-      heapq.heappush(heap, (diff, value))
+      cog = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(value)
+      cog_value: float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
+      diff = abs(cog_value - target_value)
+      heapq.heappush(heap, (diff, cog_value))
   # RETURN X BEST ITEMS FROM HEAP
@@
 sorting was carried out by the queue in the background.
+
+\hypertarget{alternative-filter-algorithm-implementation}{%
+\subsection{Alternative Filter Algorithm
+Implementation}\label{alternative-filter-algorithm-implementation}}
+
+Another possibility here would be for the user to use a reference
+measurement instead of a simulated ideal magnet as a reference. This can
+come from a magnet selected as a reference magnet. As a result, the
+filter algorithm returns the measurements that are most similar to the
+selected reference magnet.The code snipped
+\ref{lst:custom_find_similar_values_algorithm_refmagnet} shows the
+modified filter algorithm code, with added
+\passthrough{\lstinline!\_ref!} input parameter for the reference
+measurement.
+
+\begin{lstlisting}[language=Python, caption={Modified user implemented custom find algorithm using a reference magnet reading}, label=lst:custom_find_similar_values_algorithm_refmagnet]
+@staticmethod
+def FindSimilarValuesAlgorithmREF(_readings: [MRPReading.MRPReading], _ref: [MRPReading.MRPReading], IP_return_count: int = 4) -> [MRPReading.MRPReading]:
+  # CALCULATE CoG VALUE OF REFERENCE MAGNET
+  cog_ref = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(_ref[0])
+  ref_value: float = math.sqrt(cog_ref[0]**2 + cog_ref[1]**2 cog_ref[2]**2)
+  # PUSH READINGS TO HEAP
+  for value in _readings:
+      # USE DIFF AS PRIORITY VALUE IN MIN-HEAP
+      cog = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(value)
+      cog_value: float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
+      heapq.heappush(heap, (abs(cog_value - ref_value), cog_value))
+  # RETURN X BEST ITEMS FROM HEAP
+  return [item[1] for item in heapq.nsmallest(IP_return_count, heap)]
+\end{lstlisting}
 
@@
 distance) as they correspond to the mechanical structure of the used
-hardware sensor \ref{d-fullsphere}. The filter algorithm implemented by
-the user was thus successfully executed using the user-programmable
-pipeline. The calculation result was successfully verified using raw
-measurement data and the final result of the algorithm.
+hardware sensor \ref{d-fullsphere}.
+
+The filter algorithm implemented by the user was thus successfully
+executed using the user-programmable pipeline. The calculation result
+was successfully verified using raw measurement data and the final
+result of the algorithm.
 

### 2024-02-09 src/MagneticReadoutProcessing/MRP/MRPDataVisualization.py
.

@@ -17,7 +17,77 @@ class MRPDataVisualizationException(Exception):
 class MRPDataVisualization:
 
     @staticmethod
-    def plot_histogram(_reading: MRPReading.MRPReading, _title: str = '', _filename: str = None, _unit: str = "uT"):
+    def plot_linearity(_readings: [MRPReading.MRPReading], _title: str = '', _filename: str = None, _unit: str = "$\mu$T"):
+        """
+        Plots the linearityfrom several readings
+
+        :param _readings:
+        :type _readings: list(MRPReading.MRPReading)
+
+        :param _title: title of the graphic
+        :type _title: str
+
+        :param _filename: export graphic to abs filepath with .png
+        :type _filename: str
+        """
+        if _readings is None or len(_readings) <= 0:
+            raise MRPDataVisualizationException("no readings in _reading given")
+
+        x = np.linspace(0, len(_readings), len(_readings), dtype=np.int32)
+        xlabels: [str] = []
+        for reading in _readings:
+
+
+            name: str = reading.get_name().split("_")
+            distance_was_in: bool = False
+            for n in reading.get_name().split("_"):
+                if 'DISTANCE=' in n:
+                    distance_was_in = True
+                    xlabels.append(n.split('DISTANCE=')[1])
+
+            if not distance_was_in:
+                xlabels.append('-')
+
+        y: [float] = []
+        for reading in _readings:
+            y.append(MRPAnalysis.MRPAnalysis.calculate_mean(reading))
+        #raw_y = _reading.to_value_array()
+
+
+
+
+        # Create 2x2 sub plots
+        gs = gridspec.GridSpec(1, 1)
+
+        fig = plt.figure()
+        fig.suptitle('{}'.format(_title), fontsize=12)
+
+        distance_plot = plt.subplot(gs[0, 0])
+        distance_plot.set_xlabel('Distance', fontsize=8)
+        distance_plot.set_ylabel('Reading Mean Value $\mu_{nl}$ ['+ _unit + ']', fontsize=8)
+        distance_plot.set_xticklabels(xlabels)
+        #distance_plot.set_yticklabels(ylabels)
+        distance_plot.plot(x, y, linewidth=0.8)
[…]

### 2024-02-09 src/MagneticReadoutProcessing/MRP/MRPReading.py

@@ -59,7 +59,9 @@ class MRPReading():
             else:
                 self.measurement_config.id = 0
 
-
+    import_scale_factor: float = 1.0
+    def set_unit_import_scale_factor(self, _factor: float = 1.0):
+        self.import_scale_factor = _factor
 
     def load_from_dict(self, _jsondict: dict):
         self.time_start = None
@@ -75,7 +77,7 @@ class MRPReading():
         self.data = []
         for idx, entry in enumerate(_jsondict['data']):
             _re = MRPReadingEntry.MRPReadingEntry()
-            _re.from_dict(entry)
+            _re.from_dict(entry, self.import_scale_factor)
             self.data.append(_re)
 
         self.measurement_config = MRPMeasurementConfig.MRPMeasurementConfig()

### 2024-02-09 src/MagneticReadoutProcessing/MRP/MRPReadingEntry.py

@@ -93,10 +93,10 @@ class MRPReadingEntry:
             self._is_valid = p_is_valid
             self._temperature = p_temperature
 
-    def from_dict(self, _dict: dict):
+    def from_dict(self, _dict: dict, _import_scale_factor: float = 1.0):
         errors = 0
         if 'value' in _dict:
-            self._value = float(_dict['value'])
+            self._value = float(_dict['value']) * _import_scale_factor
             errors = errors + 1
 
         if 'phi' in _dict:

### 2024-02-09 src/MagneticReadoutProcessing/tests/test_MRPDataVisualization.py

@@ -18,19 +18,89 @@ class TestMPRDataVisualization(unittest.TestCase):
     # CALLED BEFORE EACH SUB-TESTCASE
     def setUp(self) -> None:
         self.result_folder_path = os.path.join(os.path.dirname(os.path.abspath(__file__)), "generated_plots")
-        self.asset_folder_path = os.path.join(os.path.dirname(os.path.abspath(__file__)), "assets/test_histogram")
+        self.asset_histogram_folder_path = os.path.join(os.path.dirname(os.path.abspath(__file__)), "assets/test_histogram")
+        self.asset_linearity_folder_path = os.path.join(os.path.dirname(os.path.abspath(__file__)), "assets/test_linearity")
         if not os.path.exists(self.result_folder_path):
             os.makedirs(self.result_folder_path)
 
 
+
+    def test_linearity_realdata(self):
+        files = [f for f in os.listdir(self.asset_linearity_folder_path) if re.match(r'(.)*.mag.json', f)]
+
+        sensors:set = set()
+
+        for e in files:
+            sp: [str] = e.split('_')
+            sensors.add(sp[0])
+
+
+        to_process: dict = {}
+        for sensor in sensors:
+            to_process[sensor] = {
+                'files': [],
+                'distance': [],
+                'N': [],
+                'RUN': []
+            }
+        for s in sensors:
+            for e in files:
+                if e.startswith(s):
+                    DISTANCE = ""
+                    N = ""
+                    RUN = ""
+                    splr: [str] = e.split('_')
+                    for sp in splr:
+                        if "DISTANCE=" in sp:
+                            DISTANCE = sp.split("=")[1]
+                        elif "RUN=" in sp:
+                            RUN = sp.split("=")[1]
+                        elif "N=" in sp:
+                            N = sp.split("=")[1]
+
+                    to_process[s]['files'].append(e)
+                    to_process[s]['distance'].append(DISTANCE)
+                    to_process[s]['N'].append(N)
+                    to_process[s]['RUN'].append(RUN)
+
+        for k in to_process:
+            e = to_process[k]
+
+
+            reading_name: str = "linearity_sensor=" + k + "_readingcount=" + str(len(e['files']))
+            export_filename: str = os.path.join(self.result_folder_path, reading_name.replace(" ", "_") + ".png")
+
+            # IMPORT READINGS
+            readings: [MRPReading.MRPReading] = []
+            for idx, r in enumerate(e['files']):
[…]

### 2024-02-09 documentation/thesis/thesis_document.tex
more thesis

@@
 range of values required by the various magnets to be tested.
+
+In the Evaluation \ref{evaluation} chapter, basic characterisation
+methods are used to evaluate the sensors listed in
+\ref{Implemented_digital_magnetic_field_sensors.csv} with regard to
+their sensitivity and other parameters. This is done at this point, as
+the components of the readout interface that enable interaction with the
+sensors are considered first.
 
@@
 
+TODO: fix links o evaluation
+
 \hypertarget{evaluation}{%
@@
 
+\hypertarget{hardware-evaluation}{%
+\section{Hardware Evaluation}\label{hardware-evaluation}}
+
+\begin{itemize}
+\tightlist
+\item
+  cheap sensors used
+\item
+  used hardware list
+\item
+  tested sensor tlv mmc, da diese zum zeitpunkt des tests zur verfüung
+  standen
+\end{itemize}
+
+\hypertarget{read-noise}{%
+\subsection{Read Noise}\label{read-noise}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_noise_measurements.png}
+\caption{Sensor evaluation setup for noise measurements
+\label{Sensor_evaluation_setup_for_noise_measurements.png}}
+\end{figure}
+
+Measuring the noise in a magnetic field sensor requires a precise
+procedure and a special measurement setup. First, the magnetic field
+sensor is placed in a quiet environment to minimize external
+interference.
+
+The sensor platform used here is a ready-built
+\passthrough{\lstinline!1D: Single Sensor!} \ref{d-single-sensor} sensor
+platform, which has been equipped with the sensors to be measured one
+after the other.
+
+The procedure begins with the acquisition of the baseline by operating
+the sensor without external magnetic fields. For this purpose, a sample
+size of N=10000 measured values was recorded for the reference
+measurement.
+
+The output signal of the sensor is then continuously measured and
+recorded. It is important to carry out the measurement over a
+sufficiently long period of time in order to record both short-term and
+long-term fluctuations. For this purpose, N=1000 measured values were
+also taken with a trigger and readout rate of one measurement per
+second.
+
+The baseline measurement and the continuous measurement were configured
+in advance using \passthrough{\lstinline!MRPCli!} \gls{cli}.
+
+In order to quantify the noise, the standard deviation or the mean
+square deviation of the signal is calculated. These parameters provide
+information about the variation of the signal over time and therefore
+about the sensor background noise.
+
+After the measurements were completed, the data was evaluated using the
+available MRPDataVisualization and MRPAnalysis functions. These
+graphically represent the following measured values:
+
+\begin{itemize}
+\tightlist
+\item
+  Plot of the raw measurement data, as well as its mean value
+  \passthrough{\lstinline!$\\mu\_\{rv\}$!} using Baselin
+\item
+  Plot of the temperature curve over the complete measurement series,
+  which was recorded with the sensor's internal temperature sensor
+\item
+  Noise level as a percentage deviation from the baseline
+\item
+  Histogram of the noise level with marked standard deviation
+\end{itemize}
+
+\hypertarget{temperature-deviation}{%
+\subsection{Temperature Deviation}\label{temperature-deviation}}
+
+using same setup as in read noise but with programmed temperature
+controller of the chamber
+
+\hypertarget{linearity}{%
+\subsection{Linearity}\label{linearity}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_linearity_measurements.png}
+\caption{Sensor evaluation setup for linearity measurements
+\label{Sensor_evaluation_setup_for_linearity_measurements.png}}
+\end{figure}
+
+\begin{itemize}
+\tightlist
+\item
+  minimal distance between sensor and magnet due to messbreich
+\end{itemize}
+
+\hypertarget{result-analysis}{%
+\subsubsection{Result Analysis}\label{result-analysis}}
+
+are they suitable for \textless1000ppm ?
+
+\begin{itemize}
+\tightlist
+\item
+  https://onlinelibrary.wiley.com/doi/epdf/10.1002/mrm.28396
+\item
+  27cm / 50mT bore
+\item
+  nmr probes for better results
+\end{itemize}
+
+\hypertarget{software-evaluation}{%
+\section{Software Evaluation}\label{software-evaluation}}
+
+TODO: HOW TO TEST library SOFTWARE
+
 \begin{enumerate}
@@
 \hypertarget{hardware-preperation}{%
-\section{Hardware preperation}\label{hardware-preperation}}
+\subsection{Hardware preperation}\label{hardware-preperation}}
 
@@
 \hypertarget{configuration-of-the-measurement}{%
-\section{Configuration of the
+\subsection{Configuration of the
 Measurement}\label{configuration-of-the-measurement}}
@@
 \hypertarget{custom-algorithm-implementation}{%
-\section{Custom Algorithm
+\subsection{Custom Algorithm
 Implementation}\label{custom-algorithm-implementation}}
@@
 \hypertarget{alternative-filter-algorithm-implementation}{%
-\subsection{Alternative Filter Algorithm
+\subsubsection{Alternative Filter Algorithm
 Implementation}\label{alternative-filter-algorithm-implementation}}
@@
 \hypertarget{execution-of-analysis-pipeline}{%
-\section{Execution of Analysis
+\subsection{Execution of Analysis
 Pipeline}\label{execution-of-analysis-pipeline}}
@@
 
+\hypertarget{result-analysis-1}{%
+\subsection{Result Analysis}\label{result-analysis-1}}
+
 The figure
@@
 
+If the alternative filter algorithm from chapter
+\passthrough{\lstinline!Alternative Filter Algorithm Implementation!}
+\ref{alternative-filter-algorithm-implementation} is executed here, the
+same result is returned if the magnet measurement with \gls{id}
+\passthrough{\lstinline!5:0!} is used as the reference magnet.
+
 The filter algorithm implemented by the user was thus successfully

### 2024-02-13 documentation/thesis/thesis_document.tex
build

@@
 
+As the following, the motivation for the development of this framework
+is listed. The chapter provides a brief introduction into the problem
+domain, delineates the scope and boundaries of the present research,
+surveys the current state of the art in low-field MRI research and
+applications, articulates the research question driving this thesis and
+delineates the anticipated use cases and benefits that will be explored
+and analyzed throughout the study.
+
 \hypertarget{background-and-motivation}{%
@@
 
-As the following, the motivation for the development of this framework
-is listed. A brief introduction to the topic of low-field \gls{mri} is
-given, followed by the research problem to be solved by this work.
+Magnetic Resonance Imaging \gls{mri} stands as a cornerstone in clinical
+diagnostics, utilizing the principles of nuclear magnetic resonance
+\gls{nmr} to generate cross-sectional black-and-white images of the
+body. This indispensable method plays a crucial role in contemporary
+medicine and research, contributing significantly to saving lives.
+Despite its widespread use, traditional MRI systems often rely on large,
+heavy, and expensive magnets to achieve the necessary homogeneity of the
+magnetic field for accurate imaging. \cite{Nitz2016}
+
+Various types of magnets find application in different \gls{mri}
+systems. Permanent magnets generate a steady yet relatively weak
+magnetic field, electro magnets are energized by electrical currents,
+and superconducting electro magnets produce magnetic fields through
+electricity and induction. Regardless of the type, the primary objective
+is to create a homogeneous magnetic field within the \gls{mri}. The
+higher the homogeneity, the more accurate the measurements. This uniform
+magnetic field aligns the molecules within the body or object, setting
+the stage for a second magnetic system to stimulate these molecules for
+measurements.
+
+The challenge with conventional first-order homogeneity systems lies in
+their substantial size, weight, and cost. Even when targeting smaller
+areas of the body, large devices are often necessary. In response to
+this, there is a growing interest in developing low-field \gls{mri}
+systems that utilize various magnet types, including permanent magnets.
+These systems, while offering advantages in energy efficiency and
+reduced complexity, face a significant challenge related to the inherent
+variability in the strength of permanent magnets. Achieving homogeneity
+in the magnetic field is crucial for accurate imaging or comparative
+analyses. While incapable of producing images due to lower magnetic
+field strength, low-field systems facilitate the comparison of different
+field behaviors and the identification of anomalies. O'Reilly and
+Teeuwisse and de Gans \cite{OReilly2019-rn} have already
+demonstrated low-cost and small-scale implementations with low-field
+\gls{mri} in 2021.
+
+Permanent magnets, usually arranged in a circular ``Hallbach array''
+around the \gls{mri}, are commonly employed in low-field systems.
+However, their drawback is the inherent variability in strength,
+complicating the achievement of a homogeneous field and requiring
+precise strength information for correct magnet ordering and \gls{mri}
+construction.
+
+The focus of this thesis is on advancing low-frequency \gls{mri}
+technology by addressing the sensor-usability of permanent magnets used
+in these systems. The variability in the strength of permanent magnets
+poses a significant obstacle to constructing an \gls{mri} with the
+necessary precision for homogenous field generation.
+
+To address this challenge, the thesis proposes the development of a
+comprehensive hardware and software framework. The hardware system aims
+to selectively measure magnetic fields at different locations or fully
+around a permanent magnet using different sensors. The accompanying
+open-source software is designed not only to facilitate measurements
+with different sensors but also to enable the characterization of
+different objects.
+
+The sensor testing process involves two key tests. Firstly, the
+linearity of the magnetic fields is measured with all sensors to assess
+the feasibility of using specific sensors. Secondly, the homogeneity of
+the sensors is evaluated to determine its capability to measure with
+precision greater than 1,000 \gls{ppm}.
+
+This research initiative seeks to contribute to the improvement of
+low-frequency \gls{mri} systems by enhancing the accuracy of permanent
+magnet characterization. The outcomes of this thesis will provide
+insights into the selection and evaluation of sensors for future
+low-field \gls{mri} research, ultimately contributing to advancements in
+medical imaging technologies.
 
@@
 \cite{Hori2021-pt}.
+
+Contemporary most MRI machines employ high-field superconducting magnets
+cooled cryogenically, delivering exceptional image resolution. However,
+the associated costs, space requirements, and safety considerations can
+be substantial. In contrast, permanent magnets present an economical and
+space-efficient alternative. Nevertheless, they generate lower magnetic
+field strengths, impacting the signal-to-noise ratio (SNR) and resulting
+in lower image resolution within clinically viable scan times.
+\cite{Arnold2023-cn}
+
+In response to these challenges, recent endeavors in both academia and
+industry aim to leverage the benefits of lower field strength---such as
+reduced costs, a smaller device footprint, and diminished safety
+concerns---while addressing the inherent drawbacks that compromise image
+quality (refer to Table 1). The optimization of low-field approaches is
+becoming increasingly prevalent, tailored to specific clinical inquiries
+and contexts.
+
+To overcome limitations associated with lower field strengths, ongoing
+research focuses on the meticulous selection and validation of use
+cases. This strategic approach is essential for ensuring that the
+advantages of lower cost and reduced device size are harnessed without
+sacrificing diagnostic accuracy or compromising patient outcomes.
+\cite{Arnold2023-cn}
 
@@
 separate build configuration. In order to be able to read and correctly
-interpret the data from the microcontoller, the serial protocol from
-table \ref{Voltcraft_GM70_serial_protocol.csv} of the sensor was
-implemented in a customized version of the
+interpret the data from the microcontoller, the serial protocol of the
+sensor was implemented in a customized version of the
 \passthrough{\lstinline!CustomSensor!} class
@@
 \end{figure}
-
-\begin{longtable}[]{@{}lll@{}}
-\caption{Voltcraft GM70 serial protocol
-\label{Voltcraft_GM70_serial_protocol.csv}}\tabularnewline
-\toprule
-BYTE-INDEX & REPRESENTATION & VALUE\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-BYTE-INDEX & REPRESENTATION & VALUE\tabularnewline
-\midrule
-\endhead
-0 & PREAMBLE & 0x2\tabularnewline
-1 & & 0x1\tabularnewline
-2 & & 0x4\tabularnewline
-3 & UNIT & `B' =\textgreater{} Gauss `E' =\textgreater{}
-mT\tabularnewline
-5 & POLARITY & `1' =\textgreater{} \emph{0.1 `2' =\textgreater{}
-}0.01\tabularnewline
-6 & value MSB & 0x-0xFF\tabularnewline
-13 & value LSB & 0x-0xFF\tabularnewline
-14 & STOP & 0x3\tabularnewline
-\bottomrule
-\end{longtable}
 

### 2024-02-13 documentation/thesis/thesis_document.tex
.

@@
 This technology is used in medical imaging as well as in preclinical
-research. The main advantage of low-field MRI is the improved imaging of
-soft tissues, especially when examining joints and muscles. It also
-offers more cost-effective alternatives to high-field MRI systems
-\cite{Hori2021-pt}.
-
-Contemporary most MRI machines employ high-field superconducting magnets
-cooled cryogenically, delivering exceptional image resolution. However,
-the associated costs, space requirements, and safety considerations can
-be substantial. In contrast, permanent magnets present an economical and
-space-efficient alternative. Nevertheless, they generate lower magnetic
-field strengths, impacting the signal-to-noise ratio (SNR) and resulting
-in lower image resolution within clinically viable scan times.
-\cite{Arnold2023-cn}
+research. The main advantage of low-field \gls{mri} is the improved
+imaging of soft tissues, especially when examining joints and muscles.
+It also offers more cost-effective alternatives to high-field \gls{mri}
+systems \cite{Hori2021-pt}.
+
+Contemporary most \gls{mri} machines employ high-field superconducting
+magnets cooled cryogenically, delivering exceptional image resolution.
+However, the associated costs, space requirements, and safety
+considerations can be substantial. In contrast, permanent magnets
+present an economical and space-efficient alternative. Nevertheless,
+they generate lower magnetic field strengths, impacting the \gls{snr}
+and resulting in lower image resolution within clinically viable scan
+times. \cite{Arnold2023-cn}
 
@@
 concerns---while addressing the inherent drawbacks that compromise image
-quality (refer to Table 1). The optimization of low-field approaches is
-becoming increasingly prevalent, tailored to specific clinical inquiries
-and contexts.
+quality. The optimization of low-field approaches is becoming
+increasingly prevalent, tailored to specific clinical inquiries and
+contexts.
 
@@
 used, which has a measuring range of 0T to 3T with a resolution of
-0.1mT. It offers an RS232 interface with a documented protocol
-\ref{Voltcraft_GM70_serial_protocol.csv} for connection to a \gls{pc}.
+0.1mT. It offers an RS232 interface with a documented protocol for
+connection to a \gls{pc}.
 
@@
 
+\begin{itemize}
+\tightlist
+\item
+  TODO
+\end{itemize}
+
 \hypertarget{hardware-evaluation}{%
 \section{Hardware Evaluation}\label{hardware-evaluation}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
+\caption{Sensor evaluation plattform with TLV493D and MMC5603 sensors
+placed with thermal conductive glue on an aluminium baseplate
+\label{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}}
+\end{figure}
 
@@
 \end{itemize}
+
+The sensor platform used here is an adapted version of the
+\passthrough{\lstinline!1D: Single Sensor!} \ref{d-single-sensor} sensor
+platform. The sensors to be measured were fixed together on an aluminium
+plate with thermally conductive adhesive. This compensates for thermal
+differences.
+
+This is crucial for the subsequent temperature deviation tests in order
+to obtain comparable measurement results. The graphic
+\ref{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
+shows this basic setup, the Raspberry Pi Pico shown here was used as the
+readout hardware, on which the Unified Sensor Firmware version
+\passthrough{\lstinline!1.0.2!} is running.
+
+A separate \passthrough{\lstinline!KA30005D!} laboratory power supply is
+used as the power supply for the sensors. An Raspberry Pi 4 is used as
+the host computer, which is connected to the sensors via a
+\passthrough{\lstinline!Hailege ADUM3160!} \gls{usb} isolator and is
+placed outside the temperature chamber. \passthrough{\lstinline!MRPCli!}
+\ref{command-line-interface} version \passthrough{\lstinline!1.5.0!} was
+used to control and record the measurement series, with the functions of
+the \passthrough{\lstinline!MRPDataVisualisation!}
+\ref{mrpvisualisation} and \passthrough{\lstinline!MRPAnalysis!}
+\ref{mrpanalysis} packages from the library
+\ref{software-readout-framework} being used for subsequent evaluation.
+The recorded measurement series are automatically analysed using the
+\passthrough{\lstinline!Programmable-  Data Pprocessing Pipeline!}
+\ref{programmable-data-processing-pipeline} and the results are
+visualised.
 
@@
 interference.
-
-The sensor platform used here is a ready-built
-\passthrough{\lstinline!1D: Single Sensor!} \ref{d-single-sensor} sensor
-platform, which has been equipped with the sensors to be measured one
-after the other.
 

### 2024-02-14 documentation/thesis/thesis_document.tex
.

@@
 applications, articulates the research question driving this thesis and
-delineates the anticipated use cases and benefits that will be explored
+delineates the anticipated usecases and benefits that will be explored
 and analyzed throughout the study.
@@
 and superconducting electro magnets produce magnetic fields through
-electricity and induction. Regardless of the type, the primary objective
-is to create a homogeneous magnetic field within the \gls{mri}. The
-higher the homogeneity, the more accurate the measurements. This uniform
-magnetic field aligns the molecules within the body or object, setting
-the stage for a second magnetic system to stimulate these molecules for
-measurements.
-
-The challenge with conventional first-order homogeneity systems lies in
-their substantial size, weight, and cost. Even when targeting smaller
-areas of the body, large devices are often necessary. In response to
-this, there is a growing interest in developing low-field \gls{mri}
-systems that utilize various magnet types, including permanent magnets.
-These systems, while offering advantages in energy efficiency and
-reduced complexity, face a significant challenge related to the inherent
+electric induction. Regardless of the type, the primary objective is to
+create a homogeneous magnetic field within the \gls{mri}. The higher the
+homogeneity, the more accurate the measurements. This uniform magnetic
+field aligns the molecules within the body or object, setting the stage
+for a second magnetic system to stimulate these molecules for
+spin-measurements.
+
+The challenge with conventional homogeneity systems lies in their
+substantial size, weight, and cost. Even when targeting smaller areas of
+the body, large devices are often necessary. In response to this, there
+is a growing interest in developing low-field \gls{mri} systems that
+utilize various magnet types, including permanent magnets. These
+systems, while offering advantages in energy efficiency and reduced
+complexity, face a significant challenge related to the inherent
 variability in the strength of permanent magnets. Achieving homogeneity
@@
 
-Permanent magnets, usually arranged in a circular ``Hallbach array''
+Permanent magnets, usually arranged in a circular ``Halbach array''
 around the \gls{mri}, are commonly employed in low-field systems.
@@
 precise strength information for correct magnet ordering and \gls{mri}
-construction.
+construction. Completed MRI systems pose significant challenges for
+retrospective adjustments, particularly when individual magnets impact
+the overall homogeneity of the magnetic field. While deviations in
+homogeneity can be measured post-assembly, the intricate task of
+readjustment becomes formidable. An approach dictates that meticulous
+adjustments to the magnets should be undertaken proactively, prior to
+the finalization of the MRI system.
 
@@
 the sensors is evaluated to determine its capability to measure with
-precision greater than 1,000 \gls{ppm}.
+precision greater than 1,000 \gls{ppm}. In the end, the sensors should
+also measure how uniform the magnetic field is in a completed \gls{mri}
+system.
 
@@
 \subsection{Low-Field MRI}\label{low-field-mri}}
+
+In the realm of modern medical imaging, high-field superconducting
+magnets dominate most \gls{mri} machines, providing high blac-withe
+image resolution. However, the substantial costs, space prerequisites,
+and safety considerations associated with these systems pose
+considerable challenges.
+
+Magnetic resonance imaging \gls{mri} relies on the presence of a robust
+magnetic field, and over time, there has been a continual push to
+enhance the strength of these magnetic fields. This strength is
+quantified in units of Tesla {[}T{]}, commonly referred to as the B0
+field in medical contexts, while physicists use the term magnetic field
+induction. The \gls{snr} is proprtional to the magnetic B0 field;
+growing magnetic field leads automatically to higher \gls{snr}.
+
+Notably, the focus on high-field systems predominated discussions until
+around 1991 when the possibility of constructing \gls{mri} machines with
+lower magnetic field strengths began to emerge. This marked a pivotal
+shift in exploring the potential advantages and applications of
+low-field \gls{mri} systems. \cite{Nitz2016}
 
@@
 It also offers more cost-effective alternatives to high-field \gls{mri}
-systems \cite{Hori2021-pt}.
-
-Contemporary most \gls{mri} machines employ high-field superconducting
-magnets cooled cryogenically, delivering exceptional image resolution.
-However, the associated costs, space requirements, and safety
-considerations can be substantial. In contrast, permanent magnets
-present an economical and space-efficient alternative. Nevertheless,
-they generate lower magnetic field strengths, impacting the \gls{snr}
-and resulting in lower image resolution within clinically viable scan
-times. \cite{Arnold2023-cn}
-
-In response to these challenges, recent endeavors in both academia and
-industry aim to leverage the benefits of lower field strength---such as
-reduced costs, a smaller device footprint, and diminished safety
-concerns---while addressing the inherent drawbacks that compromise image
-quality. The optimization of low-field approaches is becoming
-increasingly prevalent, tailored to specific clinical inquiries and
-contexts.
-
-To overcome limitations associated with lower field strengths, ongoing
-research focuses on the meticulous selection and validation of use
-cases. This strategic approach is essential for ensuring that the
-advantages of lower cost and reduced device size are harnessed without
-sacrificing diagnostic accuracy or compromising patient outcomes.
+systems \cite{Hori2021-pt}, cost reduction, a smaller device
+footprint, alleviated safety concerns and leading to diminished image
+resolution within clinically feasible scan durations.
 \cite{Arnold2023-cn}
+
+Low-field \gls{mri} systems are predominantly composed of permanent
+magnets. Through the connection of these permanent magnets, a consistent
+magnetic field of up to 0.35 Tesla can be generated. However, this
+achievement comes at the cost of an average system weight of 14 tons.
+Despite their cost-effectiveness in production and maintenance,
+permanent magnets exhibit drawbacks such as high temperature dependence
+and a limited \gls{snr} due to the constrained field strength.
+\cite{Nitz2016}
+
+In particular, the advantages of the small design, the fast and simple
+image acquisition and the low costs are advantages that will become
+increasingly important in the future. However, the use of permanent
+magnets and their structure is particularly important in such systems
+and need to be analysed.
 
@@
 
-\%\%Example\_hallbach\_ring\_magnet\_with\_cutouts\_for\_eight\_cubical\_permanent\_magnets.png\%\%
-
-Halbach ring magnets \cite{Halbach1980DesignOP} have become a common
-design for low field \gls{mri} and \gls{nmr} systems
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Example_Hallbach_ring_with_cutouts_for_eight_magnets.png}
+\caption{Example Hallbach ring with cutouts for eight magnets
+\label{Example_Hallbach_ring_with_cutouts_for_eight_magnets.png}}
+\end{figure}
+
+The positioning of permanent magnets holds a pivotal role in
+constructing an MRI and influencing the homogeneity of the B0 magnetic
+field. Halbach ring magnets \cite{Halbach1980DesignOP} have become a
+common design for low field \gls{mri} and \gls{nmr} systems
 \cite{cmr.a.20165}.
 
-They have the ability to generate extremely homogeneous magnetic flux
-densities, produce virtually no stray fields and are particularly
-attractive for larger magnets as their design has the best flux-to-mass
-ratio \cite{Wickenbrock_2021}.
+This positioning has the ability to generate extremely homogeneous
+magnetic flux densities, produce virtually no stray fields and is
+particularly attractive for larger magnets as their design has the best
+flux-to-mass ratio \cite{Wickenbrock_2021}.
 
@@
 magnets arranged in a circle. The graphic
-\ref{Example_hallbach_ring_magnet_with_cutouts_for_eight_cubical_permanent_magnets.png}
-shows an example \gls{cad} model of such a ring, in which in this case
-eight cubic \passthrough{\lstinline!12x12x12mm!} magnets are embedded to
+\ref{Example_Hallbach_ring_with_cutouts_for_eight_magnets.png} shows an
+example \gls{cad} model of such a ring, in which in this case eight
+cubic \passthrough{\lstinline!12x12x12mm!} magnets are embedded to
 generate homogeneous magnetic flux densities of around
@@
   magnets from different production batches are compared.
+  \cite{inbook}
 \end{itemize}
@@
 
+Halbach magnetic arrays present a compelling choice for mobile NMR due
+to their ability to produce highly homogeneous and robust magnetic
+fields per unit of magnetic mass, coupled with minimal stray fields. The
+term ``Halbach Array'' (commonly known as ``magic rings'') denotes a
+precise configuration of permanent magnets designed to amplify magnetic
+flux on one side while concurrently mitigating or eliminating it on the
+opposite side. \cite{inbook}
+
+The Halbach magnetic array emerges as a crucial element for future
+Magnet Characterization. Given that this thesis centers on assessing the
+sensors' applicability, the Halbach magnetic array serves as a tool for
+measurements, although its implementation and further discussion will
+not be the primary focus.
+
 In order to compensate for inhomogeneities in a finished system, there
 are various so-called shimming procedures which further improve
-homogeneity after the system has been assembled.
+homogeneity after the system has been assembled. This procedure is
+explained in the following chapter.
 
@@
 
+Optimal homogeneity is attained through intricate designs facilitating
+active shimming, a technique crucial for achieving high-resolution
+spectroscopy. Beyond this, simpler combinations and adaptations of
+Halbach rings offer versatility, making them suitable for variable field
+magnets or magnets that can be effortlessly opened without applying
+force. \cite{inbook}
+
 The sources for the shimming process can be hardware and software based.
@@
 \section{State of the Art}\label{state-of-the-art}}
+
+\textbf{Low-Field MRI}
+
+According to Wolfgang R. Nitz in 2016, just 13.4\% of actively used v
+systems are low-field \gls{mri} (66.6\% 1.5T systems, 20\% 3.0 T system,
+14.4\% low field with \textless0.5T). {[}Nitz2016{]} Nitz also
+highlights that presently, the landscape of \gls{mri} technology is
+dominated by a single manufacturer dealing with resistive magnets,
+namely Stand-up \gls{mri} from FONAR Corp.~In contrast, the industry
+giants such as Siemens, General Electric, Philips, Toshiba, among
+others, predominantly rely on either permanent magnets or
+superconducting magnets in their \gls{mri} systems. This notable
+concentration underscores the distinctive position of Stand-up \gls{mri}
+as a trailblazer in utilizing resistive magnets within the competitive
+realm of magnetic resonance imaging. {[}Nitz2016{]}
+
+Within the research domain, various implementations have emerged. An
+exemplar instance is the work by O'Reilly, Teeuwisse, and Webb, who
+introduced a groundbreaking ``three-dimensional \gls{mri} in a
+homogeneous 27 cm diameter Bore Halbach Array magnet''
+\cite{OReilly2019-rn} in 2019. This innovative setup was
+subsequently employed in 2020 to acquire in vivo MR images, showcasing
+the practical applications of their pioneering research
+\cite{OReilly2021-ep}. 2023 veröffentlichten de Vos, Remis und Webb
+eine zusammenfassung zur gestaltng eines oint-of-care halbach array
+low-field \gls{mri} system \cite{De_Vos2023-pb}.
+
+The objective of this \gls{mri} system is to prioritize
+cost-effectiveness while efficiently capturing low-frequency images of
+the head. The emphasis lies on swift and accurate imaging, achieved
+through a streamlined approach that favors simplicity in the resultant
+images. This \gls{mri} system is strategically designed with a primary
+focus on cost-effectiveness, aiming to efficiently capture low-frequency
+images of the head. The overarching goal is to achieve rapid and
+accurate imaging through a simplified approach, prioritizing clarity and
+ease in the resulting images.
+
+The Halbach magnet incorporated in this system boasts a 27cm diameter, a
+B0 field strength of 50.4 mT, and an impressive homogeneity of 2400 ppm
+over a 20cm diameter using smaller magnets (\(12 x 12 x 12 mm^3\)). This
+exceptional homogeneity enables the utilization of coil-based gradients
+for spatial encoding, significantly enhancing the flexibility of image
+acquisition.
+
+To further refine the magnet's homogeneity, optimization techniques are
+employed by adjusting the radius of the Halbach cylinder along the
+length of the magnet. The deliberate choice of smaller magnets, as
+opposed to other Halbach designs, serves to compensate for inherent
+manufacturing imperfections in each individual magnet. This strategic
+decision not only mitigates structural demands on the magnet housing in
+terms of strength and weight but also augments safety throughout the
+construction process.
+
+\textbf{Magnet Characerisation}
 
@@
 \item
-  Adjustment of the rotation and position within the Hallbach
+  Adjustment of the rotation and position within the Halbach
   configuration
@@
 
-This form of data processing of previously characterized magnetic data
+This form of data processing of previously characterised magnetic data
 is currently being implemented experimentally in projects using various
@@
 used as well as specialized algorithms for optimizing homogeneity by
-rotating the individual magnets in a Hallbach ring relative to each
-other \cite{HalbachMRIDesigner}.
+rotating the individual magnets in a Halbach ring relative to each other
+\cite{HalbachMRIDesigner}.
 
@@
 
+Within the framework of the ``DeLoRI'' (Dedicated Low-field \gls{mri}
+for breast) project, Fraunhofer MEVIS in Bremen is actively engaged in
+crafting a compact and mobile low-field \gls{mri} unit tailored
+specifically for screening purposes. As described since 1991 low-field
+\gls{mri}s have evolved into a burgeoning realm of research, showcasing
+substantial promise within the field of medical technology. The endeavor
+by Fraunhofer MEVIS exemplifies the ongoing commitment to harnessing the
+potential of low-field \gls{mri} for enhanced breast screening
+applications.
+
+The focus of the ongoing efforts is to enhance the homogeneity of
+magnets within low-field MRI systems below 1.000ppm, primarily driven by
+the goal of establishing a compact low-field \gls{mri} for breast cancer
+detection.
+
+Beyond the development and prototype construction of low-field \gls{mri}
+scanners, the project encompasses electromagnetic simulation of
+components within the low-field MRI system, coupled with machine
+learning-driven control and data acquisition. The resultant software
+will be instrumental in reconstruction, with a specific focus on
+leveraging AI-based methodologies.
+
+This comprehensive effort serves to bolster the prototyping phase of the
+low-field \gls{mri}. Diverging from the approach implemented by
+O'Reilly, Teeuwisse, and Webb, DeLoRI aims to design an open \gls{mri},
+departing from the circular \gls{mri} configuration discussed in the
+publication. This innovation is geared towards streamlining breast
+examinations, offering enhanced accessibility, and minimizing the
+spatial requirements during installation. In addition DeLoRI endeavors
+to achieve heightened accuracy, striving for precision levels below
+1,000 ppm. While O'Reilly, Teeuwisse, and Webb were able to modify the
+ring diameter to influence field homogeneity, the unique goal here is to
+characterize the magnets pre-installation, allowing for proactive
+assessments of homogeneity characteristics. This nuanced approach aims
+to provide insights into magnetic field uniformity before the magnets
+are integrated, thereby streamlining the optimization process.
+Furthermore,
+
+It is important to note that the primary objective of this thesis is not
+merely to characterize the magnet itself; rather, the emphasis lies in
+the selection and comparison of potential sensors for the
+characterization process.
+
+To achieve this, a versatile hardware setup is in development, designed
+to accommodate various sensors for the measurement of magnets or other
+objects. Simultaneously, a software interface is being crafted to
+universally read data from different sensors and interact seamlessly
+with the diverse firmware associated with various Halbach sensors. A key
+feature of this system is the ease of sensor interchangeability,
+facilitating adaptability and versatility in the characterization
+process.
+
 The scope of the software library is to lay the foundation for the
-systematic characterization of magnets based on permanent magnets. The
+systematic characterisation of magnets based on permanent magnets. The
 library will enable data acquisition, storage and analysis of magnetic
 properties, with customization possible at each step of the process.
-
-The work aims to facilitate magnetic field characterization and improve
-the exchange of data between different user groups. Complete
-documentation, tutorials and tests will enable users to use the
+Complete documentation, tutorials and tests will enable users to use the
 framework efficiently and adapt it to their specific requirements.
 
-The application of the developed framework for the characterization of
+The application of the developed framework for the characterisation of
 different magnets and the integration of various available magnetic
@@
 
+Two sensors have been meticulously chosen for inclusion in the study.
+The ultimate objective is to assess whether these selected sensors align
+with the stringent criteria of achieving an accuracy level of 1,000 ppm.
+Furthermore, the study seeks to validate whether the measuring range of
+these sensors appropriately corresponds to the required field strength,
+ensuring their suitability for the intended application.
+
+\hypertarget{research-question-and-approach}{%
+\section{Research Question and
+Approach}\label{research-question-and-approach}}
+
+Concerning the DeLoRI project, this study exclusively delves into the
+realm of permanent magnets employed for creating a homogeneous B0 field
+through Halbach rings. Other systems and spin generation for
+measurements are deliberately excluded from consideration but will be
+necessary in later stages of the DeLoRI project.
+
+The primary objectives of this work revolve around addressing two
+pivotal research questions:
+
+\begin{itemize}
+\item
+  Sensor Characterization: Can the carefully selected sensors
+  effectively measure a magnet? Specifically, this involves
+  investigating the saturation of the sensors, the linearity of field
+  strength concerning distance from the sensor, and, in a subsequent
+  phase, exploring temperature dependence.
+\item
+  Homogeneity Measurement: Can the chosen sensors be adeptly utilized to
+  measure the homogeneity of a Halbach ring-based B0 field within the
+  stringent limit of less than 1,000 ppm? The desired outcome is a
+  measurement of less than 50 \(\mu\)T at 1,000 ppm, with a specific
+  focus on determining the sensors' viability for noise measurements.
+\end{itemize}
+
+It is crucial to emphasize that the intention is not to characterize the
+magnets per se; rather, the emphasis lies in deriving meaningful
+insights about the sensors deployed.
+
+This work distinctly prioritizes the development of both hardware and
+software tailored for sensor utilization and final testing. Physical
+properties and considerations take a secondary role in comparison to the
+overarching goal of refining the sensor-based methodologies.
+
+\hypertarget{usecases}{%
+\section{Usecases}\label{usecases}}
+
+The following section defines some usecases that the future project
+should be able to cover. These usecases define the setup of the hard-
+and software. These illustrate practical situations to understand the
+functionality and added value of the implemented solution for the user.
+
+The usecases were defined in the course of project planning and provide
+an overview of how the user interacts with the project and what
+functionalities can be expected. In the later accomplished evaluation
+process \ref{usecase-evaluation}, the defined usecases are also used as
+a reference to demonstrate the implemented capabilities of the solution.
+This is crucial for understanding the needs of the target group and
+designing the end result accordingly.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  \textbf{Ready to use hardware sensor designs}
+\end{enumerate}
+
+A universal, easy-to-integrate Hall sensor design allows users to
+evaluate the framework quickly and cost-effectively. The pre-built
+hardware sensors provide an optimal solution for research, reducing
+development time and achieving repeatable measurement results. Once
+successfully evaluated, the Hall sensor design should be easily
+adaptable to other sensors without the need for major firmware changes.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  \textbf{Taking automatic measurements from sensors}
+\end{enumerate}
+
+The purpose of the framework is to enable the automated acquisition of
+measurement data from various connected hadware sensors. The user should
+be able to configure various measurement series, which should then be
+carried out by the framework without further user interaction.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  \textbf{Open storage formats for data export}
+\end{enumerate}
+
+The use of open storage formats for the export of data enables an
+interoperable data exchange environment. The implementation of
+standardized formats improves the portability and long-term availability
+of data. This encourages the exchange and further processing of
+measurement data in other software tools.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{3}
+\tightlist
+\item
+  \textbf{Ready to integrate data analysis functions}
+\end{enumerate}
+
+Once it is possible to record and store measured values, it should be
+possible for the user to analyse and visualize this data using various
+algorithms. The focus here should be on extending the framework with
+user-created algorithms.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{4}
+\tightlist
+\item
+  \textbf{User programmable data processing pipelines}
+\end{enumerate}
+
+User-programmable data processing pipelines enable the flexible design
+of data processing sequences as pipeline by users. The framework should
+enable users to create their own pipelines with the previously defined
+data analysis functions.
+
 \hypertarget{structure}{%
@@
 This work is divided into six main chapters, which deal with the
-approach and implementation. The techniques and concepts used are
-explained in detail. Specific examples provide an overview of the
-possible use of the developed solution by the user.
-
-Chapter \ref{usecases}. \textbf{Usecases} are the application cases in
-which the project is to be used. They illustrate the practical scenarios
-and define how the product can be used in the real world. This is
-crucial for understanding the needs of the target group and designing
-the end result accordingly.
+approach, implementation and evaluation. The techniques and concepts
+used are explained in detail. Specific examples provide an overview of
+the possible use of the developed solution by the user.
 
@@
 
-Chapter \ref{evaluation}. \textbf{Evaluation} comprises the systematic
-review and assessment of the overall system. This includes the
-demonstration of the implemented capabilities of the overall system
-against the previously defined usecases.
-
-\hypertarget{usecases}{%
-\chapter{Usecases}\label{usecases}}
-
-The following section defines some usecases that the future project
-should be able to cover. These illustrate practical situations to
-understand the functionality and added value of the implemented solution
-for the user.
-
-These were defined in the course of project planning and provide an
-overview of how the user interacts with the project and what
-functionalities can be expected. In the later accomplished evaluation
-process \ref{evaluation}, the defined usecases are also used as a
-reference to demonstrate the implemented capabilities of the solution.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  \textbf{Ready to use hardware sensor designs}
-\end{enumerate}
-
-A universal, easy-to-integrate Hall sensor design allows users to
-evaluate the framework quickly and cost-effectively. The pre-built
-hardware sensors provide an optimal solution for research, reducing
-development time and achieving repeatable measurement results. Once
-successfully evaluated, the Hall sensor design should be easily
-adaptable to other sensors without the need for major firmware changes.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  \textbf{Taking automatic measurements from sensors}
-\end{enumerate}
-
-The purpose of the framework is to enable the automated acquisition of
-measurement data from various connected hadware sensors. The user should
-be able to configure various measurement series, which should then be
-carried out by the framework without further user interaction.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  \textbf{Open storage formats for data export}
-\end{enumerate}
-
-The use of open storage formats for the export of data enables an
-interoperable data exchange environment. The implementation of
-standardized formats improves the portability and long-term availability
-of data. This encourages the exchange and further processing of
-measurement data in other software tools.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{3}
-\tightlist
-\item
-  \textbf{Ready to integrate data analysis functions}
-\end{enumerate}
-
-Once it is possible to record and store measured values, it should be
-possible for the user to analyse and visualize this data using various
-algorithms. The focus here should be on extending the framework with
-user-created algorithms.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{4}
-\tightlist
-\item
-  \textbf{User programmable data processing pipelines}
-\end{enumerate}
-
-User-programmable data processing pipelines enable the flexible design
-of data processing sequences as pipeline by users. The framework should
-enable users to create their own pipelines with the previously defined
-data analysis functions.
+Chapter \ref{usecase-evaluation}. \textbf{Usecase Evaluation} describes
+the application of the framework to the previously defined usecases and
+thus forms the basis for later evaluation.
+
+Chapter \ref{evaluation}. \textbf{Evaluation} outlines the evaluation
+process for permanent magnets using the developed framework. The
+research questions posed regarding the suitability of the sensors used
+for the characterisation of permanent magnets are examined.
+
+Chapter \ref{conclusion-and-discussion}. \textbf{Conclusion and
+Discussion} bringing together essential research components, it
+synthesizes study outcomes, discusses implications, and provides
+insights for future work. This section ensures closure and aids readers
+in grasping the broader context and significance of the research.
+
+Finally, a comprehensive hardware and software framework must be
+established, capable of measuring diverse objects using various sensors.
+Additionally, conclusive remarks should be provided regarding the
+suitability of the employed sensors for magnetic field measurements.
 
@@
 reference \ref{Sensors_(+cli).png} to the user after connecting. The
-current measured value can be output using the
-\passthrough{\lstinline!readout!} command
+current measured value can be output using the \emph{readout} command
 \ref{Query_sensors_b_value_using_(+cli).png}.
@@
 \ref{software-readout-framework}-library, the system switches to binary
-mode, which is initiated using the \passthrough{\lstinline!sbm!}
-command. The same commands are available as for \gls{cli}-based
-communication, but in a binary format.
+mode, which is initiated using the \emph{sbm} command. The same commands
+are available as for \gls{cli}-based communication, but in a binary
+format.
 
@@
 shows various jitter measurements. These were performed on a
-\passthrough{\lstinline!RaspberryPi 4 4GB!}-\gls{sbc} together with an
-\passthrough{\lstinline!1D: Single Sensor!} \ref{d-single-sensor} and
-the following software settings:
+\emph{RaspberryPi 4 4GB}-\gls{sbc} together with an \emph{1D: Single
+Sensor} \ref{d-single-sensor} and the following software settings:
 
@@
 \item
-  Raspberry Pi OS Lite - \gls{os}
-  \passthrough{\lstinline!debian bookworm x64!},
+  Raspberry Pi OS Lite - \gls{os} \emph{debian bookworm x64},
 \item
   \gls{mrp} \ref{software-readout-framework}-library - Version
-  \passthrough{\lstinline!1.4.1!}
-\item
-  Unified Sensor \ref{unified-sensor}-firmware - Version
-  \passthrough{\lstinline!1.0.1!}
+  \emph{1.4.1}
+\item
+  Unified Sensor \ref{unified-sensor}-firmware - Version \emph{1.0.1}
 \end{itemize}
 
-It can be seen that a jitter time of up to an additional
-\passthrough{\lstinline!1ms!} is added between the triggering of the
-measurements by the host system and the receipt of the command by the
-sensor hardware. If the host system is still under load, this value
-increases many times over. This means that synchronising several sensors
-via the \gls{usb} connection alone is not sufficient.
+It can be seen that a jitter time of up to an additional \emph{1ms} is
+added between the triggering of the measurements by the host system and
+the receipt of the command by the sensor hardware. If the host system is
+still under load, this value increases many times over. This means that
+synchronising several sensors via the \gls{usb} connection alone is not
+sufficient.
 
@@
 various sensors is to find a common synchronisation clock. To do this,
-the function \passthrough{\lstinline!register irq on sync pin!} is
-overwritten. To set one \passthrough{\lstinline!primary!} and several
-\passthrough{\lstinline!secondary!} sensors, each sensor waits for an
-intial pulse on the SYNC-\gls{gpio}
+the function \emph{register irq on sync pin} is overwritten. To set one
+\emph{primary} and several \emph{secondary} sensors, each sensor waits
+for an intial pulse on the SYNC-\gls{gpio}
 \ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
 Each sensor starts a random timer beforehand, which sends a pulse on the
-sync line. All others receive this and switch to
-\passthrough{\lstinline!secondary!} mode and synchronise the
-measurements based on each sync pulse received.
-
-Since the presumed \passthrough{\lstinline!primary!} sensor cannot
-register its own sync pulse (because the pin is switched to output),
-there is a timeout branch condition
-\passthrough{\lstinline!got pulse within 1000ms!} and this becomes the
-\passthrough{\lstinline!primary!} sensor. This means that in a chain of
-sensors there is exactly one \passthrough{\lstinline!primary!} and many
-\passthrough{\lstinline!secondary!} sensors.
-
-In single-sensor operation, this automatically jumps to
-\passthrough{\lstinline!primary!} sensor operation through the
-\passthrough{\lstinline!got impulse within 1000ms!} branch result. The
-synchronisation status can be queried via the user interface
-\ref{communication-interface} using the \passthrough{\lstinline!opmode!}
+sync line. All others receive this and switch to \emph{secondary} mode
+and synchronise the measurements based on each sync pulse received.
+
+Since the presumed \emph{primary} sensor cannot register its own sync
+pulse (because the pin is switched to output), there is a timeout branch
+condition \emph{got pulse within 1000ms} and this becomes the
+\emph{primary} sensor. This means that in a chain of sensors there is
+exactly one \emph{primary} and many \emph{secondary} sensors.
+
+In single-sensor operation, this automatically jumps to \emph{primary}
+sensor operation through the \emph{got impulse within 1000ms} branch
+result. The synchronisation status can be queried via the user interface
+\ref{communication-interface} using the \emph{opmode}
 \ref{Query_opmode_using_(+cli).png} command. An important aspect of the
@@
 \ref{usecases}. The most important difference, apart from the sensor
-used, is the \passthrough{\lstinline!scan mode!}. In this context, this
-describes whether the sensor can measure a
-\passthrough{\lstinline!static!} fixed point on the magnet or if the
-sensor can move \passthrough{\lstinline!dynamically!} around the magnet
-using a controllable manipulator.
-
-In the following, the hardware structure of a
-\passthrough{\lstinline!static!} and \passthrough{\lstinline!dynamic!}
-sensor is described. For the \passthrough{\lstinline!static!} sensor,
-only the \passthrough{\lstinline!1D!} variant is shown, as this does not
-differ significantly from the structure of the
-\passthrough{\lstinline!1D: dual sensor!}, except it uses two
-\passthrough{\lstinline!TLV493D!} sensors, mounted above and on top of
-the magnet.
+used, is the \emph{scan mode}. In this context, this describes whether
+the sensor can measure a \emph{static} fixed point on the magnet or if
+the sensor can move \emph{dynamically} around the magnet using a
+controllable manipulator.
+
+In the following, the hardware structure of a \emph{static} and
+\emph{dynamic} sensor is described. For the \emph{static} sensor, only
+the \emph{1D} variant is shown, as this does not differ significantly
+from the structure of the \emph{1D: dual sensor}, except it uses two
+\emph{TLV493D} sensors, mounted above and on top of the magnet.
 
@@
 
-The electrical level here is based on a
-\passthrough{\lstinline!Raspberry-Pi Pico!} together with the
-\passthrough{\lstinline!MMC5603NJ!} magnetic sensor. The mechanical
-setup consists of four 3D printed components, which are fixed together
-with nylon screws to minimise possible influences on the measurement.
-
-Since the \passthrough{\lstinline!MMC5603NJ!} only has limited
-measurement range of total 6uT, even small coin sized neodymium magnets
-already saturates the sensor. It is possible to mount 3D printed spacers
-over the sensor to increase the distance between the magnet and the
-sensor and thus also measure these magnets.
+The electrical level here is based on a \emph{Raspberry-Pi Pico}
+together with the \passthrough{\lstinline!MMC5603NJ!} magnetic sensor.
+The mechanical setup consists of four 3D printed components, which are
+fixed together with nylon screws to minimise possible influences on the
+measurement.
+
+Since the \emph{MMC5603NJ} only has limited measurement range of total
+6uT, even small coin sized neodymium magnets already saturates the
+sensor. It is possible to mount 3D printed spacers over the sensor to
+increase the distance between the magnet and the sensor and thus also
+measure these magnets.
 
@@
 
-On the electrical side, it also consists of a
-\passthrough{\lstinline!SKR-Pico!} stepper motor controller, together
-with the \passthrough{\lstinline!TLV493D!} magnetic field sensor. This
-was chosen because of its larger measuring range and can therefore be
-used more universally without having to change the sensor of the arm.
+On the electrical side, it also consists of a \emph{SKR-Pico} stepper
+motor controller, together with the \emph{TLV493D} magnetic field
+sensor. This was chosen because of its larger measuring range and can
+therefore be used more universally without having to change the sensor
+of the arm.
 
@@
 hardware, the following section shows how existing hardware can be
-integrated into the system. A temperature-compensated
-\passthrough{\lstinline!Voltcraft GM-70!} telsameter
+integrated into the system. A temperature-compensated \emph{Voltcraft
+GM-70} telsameter
 \ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
@@
 offer an physical RS232 interface. As with the other sensors, this
-interface consists of your \passthrough{\lstinline!Raspberry-Pi Pico!}
-with an additional level shifter.
+interface consists of your \emph{Raspberry-Pi Pico} with an additional
+level shifter.
 
@@
 sensor was implemented in a customized version of the
-\passthrough{\lstinline!CustomSensor!} class
-\ref{lst:CustomSensorClass}.
+\emph{CustomSensor} class \ref{lst:CustomSensorClass}.
 
@@
 
-As the following, this concept is referred to as
-\passthrough{\lstinline!user interaction points!}
-\ref{user-interaction-points} and is explained in the following chapter.
+As the following, this concept is referred to as \emph{user interaction
+points} \ref{user-interaction-points} and is explained in the following
+chapter.
 
@@
 
-The following example shows the advantages of using the
-\passthrough{\lstinline!User interaction points!}:
-
-A project called \passthrough{\lstinline!HalbachOptimisation!}
+The following example shows the advantages of using the \emph{User
+interaction points}:
+
+A project called \emph{HalbachOptimisation}
 \cite{HalbachOptimisation} implements a data analysis step and
@@
 
-The \passthrough{\lstinline!HalbachMRIDesigner!}
-\cite{HalbachMRIDesigner} opensource project, can generate basic
-\gls{cad} drawings for \gls{mri} magnets in a Hallbach configuration. To
-do this, the number of magnets and additional parameters for the
-properties of the \gls{cad} model to be created are passed to the
-function provided as input parameters using a \gls{json} file. The
-result is an \passthrough{\lstinline!OpenSCAD!} \cite{OpenSCAD}
+The \emph{HalbachMRIDesigner} \cite{HalbachMRIDesigner} opensource
+project, can generate basic \gls{cad} drawings for \gls{mri} magnets in
+a Halbach configuration. To do this, the number of magnets and
+additional parameters for the properties of the \gls{cad} model to be
+created are passed to the function provided as input parameters using a
+\gls{json} file. The result is an \emph{OpenSCAD} \cite{OpenSCAD}
 based 3D model of the magnet holder.
@@
 As a result, there are two projects which are both suitable for the task
-of optimizing and creating Hallbach magnets for \gls{mri} applications.
+of optimizing and creating Halbach magnets for \gls{mri} applications.
 The data structures are not compatible with each other. However, they
@@
 
-The input parameters of the
-\passthrough{\lstinline!HalbachOptimisation!}
+The input parameters of the \emph{HalbachOptimisation}
 \cite{HalbachOptimisation} project are on the one hand the
@@
 Next, the user creates his own analysis step in order to be able to call
-up its functions. In the case of the
-\passthrough{\lstinline!HalbachOptimisation!}
+up its functions. In the case of the \emph{HalbachOptimisation}
 \cite{HalbachOptimisation} project, the function signature of the
@@
 
-The last step is to call up the
-\passthrough{\lstinline!HalbachMRIDesigner!}
+The last step is to call up the \emph{HalbachMRIDesigner}
 \cite{HalbachMRIDesigner} project, which creates the \gls{cad} model
@@
 interchangeable. If the user now wishes to use a different \gls{cad}
-algorithm instead of the \passthrough{\lstinline!HalbachMRIDesigner!}
+algorithm instead of the \emph{HalbachMRIDesigner}
 \cite{HalbachMRIDesigner}, the other steps can simply be preserved
@@
 the subchapters as the following. There are also introductory examples
-which provide an overview of the basic functions in the
-\passthrough{\lstinline!Examples!} \ref{examples} section, as well as
-further examples in the online documentation
-\cite{MagneticReadoutProcessingReadTheDocs}.
+which provide an overview of the basic functions in the \emph{Examples}
+\ref{examples} section, as well as further examples in the online
+documentation \cite{MagneticReadoutProcessingReadTheDocs}.
 
@@
 \item
-  \passthrough{\lstinline!MRPReading!} - storage of measured values
-\item
-  \passthrough{\lstinline!MRPMeasurementConfig!} - storage of the
-  measurement parameters
-\item
-  \passthrough{\lstinline!MRPMagnetTypes!} - various physical constants
-  for basic magnet types
+  \emph{MRPReading} - storage of measured values
+\item
+  \emph{MRPMeasurementConfig} - storage of the measurement parameters
+\item
+  \emph{MRPMagnetTypes} - various physical constants for basic magnet
+  types
 \end{itemize}
 
-The \passthrough{\lstinline!MRPReading!} module performs a crucial role
-in streamlining the centralized management of measurement data. It
-serves as a storage provider for various measurements, offering
-functionalities that facilitate the creation and addition of data
-records. To customize and add meta-data, users have the flexibility to
-configure parameters through the dedicated
-\passthrough{\lstinline!MRPMeasurementConfig!} module into an
+The \emph{MRPReading} module performs a crucial role in streamlining the
+centralized management of measurement data. It serves as a storage
+provider for various measurements, offering functionalities that
+facilitate the creation and addition of data records. To customize and
+add meta-data, users have the flexibility to configure parameters
+through the dedicated \emph{MRPMeasurementConfig} module into an
 \passthrough{\lstinline!MRPReading!} instance.
@@
 measurement process, these parameters act as a crucial bridge between
-user preferences and the robust capabilities of the
-\passthrough{\lstinline!MRPReading!} module.
-
-The system is also designed to be compatible with
-\passthrough{\lstinline!Extension Modules!} \ref{extension-modules},
-allowing the generation of measurement data through various modules.
-This extensibility enhances the versatility of the system, accommodating
-diverse measurement scenarios and expanding its utility across different
-domains.
+user preferences and the robust capabilities of the \emph{MRPReading}
+module.
+
+The system is also designed to be compatible with \emph{Extension
+Modules} \ref{extension-modules}, allowing the generation of measurement
+data through various modules. This extensibility enhances the
+versatility of the system, accommodating diverse measurement scenarios
+and expanding its utility across different domains.
 
 To enhance the accessibility and interpretability of the recorded data,
-a dedicated module, \passthrough{\lstinline!MRPMagnetTypes!}, comes into
-play. This module is specifically designed for the storage of physical
-parameters pertaining to the magnets targeted for measurement.
+a dedicated module, \emph{MRPMagnetTypes}, comes into play. This module
+is specifically designed for the storage of physical parameters
+pertaining to the magnets targeted for measurement.
 
@@
 This means that they can also be read out in other programs. Using
-serialization, the \passthrough{\lstinline!MRPReading!} class inherited
-from Python-\passthrough{\lstinline!Object!} class is serialized via an
-dictionary conversion step. This \gls{json} string can then be processed
-directly or written to the file system as a file.
+serialization, the \emph{MRPReading} class inherited from
+Python-\emph{Object} class is serialized via an dictionary conversion
+step. This \gls{json} string can then be processed directly or written
+to the file system as a file.
 
@@
 \item
-  \passthrough{\lstinline!additional\_data!} - Additional user-defined
-  metadata
-\item
-  \passthrough{\lstinline!data!} - Datapoint storage consists of
-  measured value, \gls{uuid} and temperature, among other parameters
-\item
-  \passthrough{\lstinline!measurement\_config!} - Information about the
-  sensor used for measurement
+  \emph{additional\_data} - Additional user-defined metadata
+\item
+  \emph{data} - Datapoint storage consists of measured value, \gls{uuid}
+  and temperature, among other parameters
+\item
+  \emph{measurement\_config} - Information about the sensor used for
+  measurement
 \end{itemize}
@@
 
-Since there are popular data processing frameworks such as
-\passthrough{\lstinline!Numpy!} \cite{harris2020array}, or the
-program for mathematical calculations, \passthrough{\lstinline!MATLAB!}
-are often used, the library also supports export formats for these
-systems.
+Since there are popular data processing frameworks such as \emph{Numpy}
+\cite{harris2020array}, or the program for mathematical
+calculations, \emph{MATLAB} are often used, the library also supports
+export formats for these systems.
 
 The different formats can be triggered by the user by calling up the
-corresponding \passthrough{\lstinline!MRPReading!} class functions:
+corresponding \emph{MRPReading} class functions:
 
@@
 \item
-  \passthrough{\lstinline!.dump()!} - \gls{json}
-\item
-  \passthrough{\lstinline!.to\_numpy\_matrix()!} -
-  \passthrough{\lstinline!Numpy!}-Array of
-  \passthrough{\lstinline!data!} object with different options
-\item
-  \passthrough{\lstinline!.dump\_savemat()!} -
-  \passthrough{\lstinline!MATLAB!} mat-file with measurement values and
-  temperatures
+  *.dump()` - \gls{json}
+\item
+  \emph{.to\_numpy\_matrix()} - \emph{Numpy}-Array of \emph{data} object
+  with different options
+\item
+  \emph{.dump\_savemat()} - \emph{MATLAB} mat-file with measurement
+  values and temperatures
 \end{itemize}
@@
 via the \gls{json} format, as an export using the other options
-(\passthrough{\lstinline!Numpy!}, \passthrough{\lstinline!MATLAB!})loses
-data during the export procedure.
+(\emph{Numpy}, \emph{MATLAB})loses data during the export procedure.
 
@@
 connection of external hardware sensors. All compatible sensors that are
-compatible with the firmware developed in the
-\passthrough{\lstinline!Unified Sensor!} \ref{unified-sensor} chapter
-are supported here. The library provides the following sensor \gls{hal}
-modules for this purpose:
+compatible with the firmware developed in the \emph{Unified Sensor}
+\ref{unified-sensor} chapter are supported here. The library provides
+the following sensor \gls{hal} modules for this purpose:
 
@@
 \item
-  \passthrough{\lstinline!MRPHal!} - Firmware protocol implementation
-\item
-  \passthrough{\lstinline!MRPHalLocal!} - \gls{usb} sensor interface
-\item
-  \passthrough{\lstinline!MRPHalRemote!} - Remote sensor interface
+  \emph{MRPHal} - Firmware protocol implementation
+\item
+  \emph{MRPHalLocal} - \gls{usb} sensor interface
+\item
+  \emph{MRPHalRemote} - Remote sensor interface
 \end{itemize}
@@
 \item
-  \passthrough{\lstinline!MRPReadingSourceStatic!} - for 1D and 2D
-  sensors such as \passthrough{\lstinline!1D: Single Sensor!}
-  \ref{d-single-sensor}
-\item
-  \passthrough{\lstinline!MRPReadingSourceFullsphere!} - for 3D sensors
-  such as \passthrough{\lstinline!3D: Fullsphere!} \ref{d-fullsphere}
+  \emph{MRPReadingSourceStatic} - for 1D and 2D sensors such as
+  \emph{1D: Single Sensor} \ref{d-single-sensor}
+\item
+  \emph{MRPReadingSourceFullsphere} - for 3D sensors such as \emph{3D:
+  Fullsphere} \ref{d-fullsphere}
 \end{itemize}
@@
 depending on the connected hardware. For this purpose, a static function
-\passthrough{\lstinline!createReadingSourceInstance!} is implemented in
-the base class \passthrough{\lstinline!MRPReadingSource!}, which
-automatically creates the appropriate instance based on the sensor
-capabilites.
+\emph{createReadingSourceInstance} is implemented in the base class
+\emph{MRPReadingSource}, which automatically creates the appropriate
+instance based on the sensor capabilites.
 
@@
 visually, two modules were created, which can graphically prepare
-\passthrough{\lstinline!MRPReading!} instances:
+\emph{MRPReading} instances:
 
@@
 \item
-  \passthrough{\lstinline!MRPVisualization!} - different table and graph
-  based plots
-\item
-  \passthrough{\lstinline!MRPPolarVisualization!} - fullsphere map plots
+  \emph{MRPVisualization} - different table and graph based plots
+\item
+  \emph{MRPPolarVisualization} - fullsphere map plots
 \end{itemize}
 
-On the one hand, it is possible with the
-\passthrough{\lstinline!MRPVisualization!} module to display measurement
-data as a table or plot (e.g.~stream, line, point). This makes it
-possible, for example, to visually identify outliers or trends in the
-measurement data. These can also be saved as an image file. The module
-is compatible with all measurement data.
-
-In contrast to the \passthrough{\lstinline!MRPPolarVisualization!}
-module, this provides functions to create 2D map plots a polar
-coordinate system. This requires measurement data with additionally set
-spatial coordinates. These can be generated automatically with the
-\passthrough{\lstinline!3D: Fullsphere!} \ref{d-fullsphere} sensor, or
-the user must provide the spatial information from another source.
+On the one hand, it is possible with the \emph{MRPVisualization} module
+to display measurement data as a table or plot (e.g.~stream, line,
+point). This makes it possible, for example, to visually identify
+outliers or trends in the measurement data. These can also be saved as
+an image file. The module is compatible with all measurement data.
+
+In contrast to the \emph{MRPPolarVisualization} module, this provides
+functions to create 2D map plots a polar coordinate system. This
+requires measurement data with additionally set spatial coordinates.
+These can be generated automatically with the \emph{3D: Fullsphere}
+\ref{d-fullsphere} sensor, or the user must provide the spatial
+information from another source.
 
@@
 Data analysis offers the user the greatest flexibility to implement
-their own modules. For this reason \passthrough{\lstinline!MRPAnalysis!}
-contains functions for calculating the following data analyses, which
-are compatible with class instances of
-\passthrough{\lstinline!MRPReading!}:
+their own modules. For this reason \emph{MRPAnalysis} contains functions
+for calculating the following data analyses, which are compatible with
+class instances of \emph{MRPReading}:
 
@@
 \item
-  \passthrough{\lstinline!std\_deviation!} - Standard deviation
-\item
-  \passthrough{\lstinline!mean!} - Mean value
-\item
-  \passthrough{\lstinline!variance!} - Variance
-\item
-  \passthrough{\lstinline!CoG!} - Center of gravity
-\item
-  \passthrough{\lstinline!binning!} - Distribution of a sample by means
-  of a histogram
-\item
-  \passthrough{\lstinline!k-nearest!} - K-nearest neighbors
+  \emph{std\_deviation} - Standard deviation
+\item
+  \emph{mean} - Mean value
+\item
+  \emph{variance} - Variance
+\item
+  \emph{CoG} - Center of gravity
+\item
+  \emph{binning} - Distribution of a sample by means of a histogram
+\item
+  \emph{k-nearest} - K-nearest neighbors
 \end{itemize}
 
-In addition, the export function
-\passthrough{\lstinline!.to\_numpy\_matrix!} enables further processing
-of the data in the \passthrough{\lstinline!Numpy!}
+In addition, the export function \emph{.to\_numpy\_matrix} enables
+further processing of the data in the \emph{Numpy}
 \cite{harris2020array} framework, in which many other standard
@@
 
-The \passthrough{\lstinline!MRPProxy!} \ref{MRPlib_Proxy_Module.png}
-module has been developed to allow forwarding and interaction with
-several sensors over a network connection using a \gls{rest} interface.
+The \emph{MRPProxy} \ref{MRPlib_Proxy_Module.png} module has been
+developed to allow forwarding and interaction with several sensors over
+a network connection using a \gls{rest} interface.
 
@@
 the proxy module, it is possible to link several instances and all
-sensors available in the network are available to the
-\passthrough{\lstinline!control!} \gls{pc}.
+sensors available in the network are available to the \emph{control}
+\gls{pc}.
 
@@
 \ref{Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png} shows
-the modified \passthrough{\lstinline!multi-proxy - multi-sensor!}
-topology. Here, both proxy instances do not communicate directly with
-the \passthrough{\lstinline!control!} \gls{pc}, but the proxy instance
-\passthrough{\lstinline!remote!}\gls{pc} \passthrough{\lstinline!\#2!}
-can acces the proxy running on \passthrough{\lstinline!remote!}\gls{pc}
-\passthrough{\lstinline!\#1!}.
-
-The \passthrough{\lstinline!control!} \gls{pc} only communicates with
-the \passthrough{\lstinline!remote!} \gls{pc}
-\passthrough{\lstinline!\#1!}, but can access all sensors in this chain.
+the modified \emph{multi-proxy - multi-sensor} topology. Here, both
+proxy instances do not communicate directly with the \emph{control}
+\gls{pc}, but the proxy instance \emph{remote} \gls{pc} \emph{\#2} can
+acces the proxy running on \emph{remote} \gls{pc} \emph{\#1}.
+
+The \emph{control} \gls{pc} only communicates with the \emph{remote}
+\gls{pc} \emph{\#1}, but can access all sensors in this chain.
 
@@
 various \gls{hal} instances, which communicate with the physically
-connected sensors on the \passthrough{\lstinline!remote!} \gls{pc} and
-the \passthrough{\lstinline!control!} \gls{pc} side, which communicates
-with the remote side via the network. For the user, nothing changes in
-the procedure for setting up a measurement. The
-\passthrough{\lstinline!MRPProxy!} \gls{cli} application must always be
+connected sensors on the \emph{remote} \gls{pc} and the \emph{control}
+\gls{pc} side, which communicates with the remote side via the network.
+For the user, nothing changes in the procedure for setting up a
+measurement. The \emph{MRPProxy} \gls{cli} application must always be
 started \ref{lst:mrpcli_proxy_start} on the \gls{pc} with connected
@@
 their capabilites have also been recognised correctly. To be able to
-configure a measurement on the \passthrough{\lstinline!control!}
-\gls{pc}, only the \gls{ip} address or hostname of the \gls{pc} running
-an \passthrough{\lstinline!MRPProxy!} instance is required
-\ref{lst:mrpcli_config_using_rpc}.
+configure a measurement on the \emph{control} \gls{pc}, only the
+\gls{ip} address or hostname of the \gls{pc} running an \emph{MRPProxy}
+instance is required \ref{lst:mrpcli_config_using_rpc}.
 
@@
 and \gls{pps} output functionality \cite{PTPIEEE1588} can be used on
-many \gls{sbc}, such as the
-\passthrough{\lstinline!Raspberry-Pi Compute Module!}.
+many \gls{sbc}, such as the \emph{Raspberry-Pi Compute Module}.
 
@@
 be possible to address them separately. This separation is done by the
-\passthrough{\lstinline!MRPProxy!} module and is a separate part from
-the core \gls{mrp}-library, to keep installation package dependencies
-small.
+\emph{MRPProxy} module and is a separate part from the core
+\gls{mrp}-library, to keep installation package dependencies small.
 
@@
 initially the same for each sensor. The only identification feature is
-the sensor \gls{uuid} by using the \passthrough{\lstinline!id!} command
-of the sensor \gls{cli}.
-
-The \passthrough{\lstinline!MRPProxy!} instance claims to be a sensor to
-the host \gls{pc} running \gls{mrp} \gls{cli}, so the multiple sensors
-must be combined into one virtual one. This is done in several steps,
-start procedure described by the following sub-chapters.
+the sensor \gls{uuid} by using the \emph{id} command of the sensor
+\gls{cli}.
+
+The \emph{MRPProxy} instance claims to be a sensor to the host \gls{pc}
+running \gls{mrp} \gls{cli}, so the multiple sensors must be combined
+into one virtual one. This is done in several steps, start procedure
+described by the following sub-chapters.
 
@@
 
-Immediately after starting the \passthrough{\lstinline!MRPProxy!}, the
-\gls{uuid}s of all locally connected sensors are read out. These are
-stored together with the class instance of the
-\passthrough{\lstinline!MRPHal!} module in a \gls{lut}. This makes it
-possible to address a sensor directly using its \gls{uuid}.
+Immediately after starting the \emph{MRPProxy}, the \gls{uuid}s of all
+locally connected sensors are read out. These are stored together with
+the class instance of the \emph{MRPHal} module in a \gls{lut}. This
+makes it possible to address a sensor directly using its \gls{uuid}.
 
@@
 These are used to select the appropriate measurement mode for a
-measurement. For this purpose, the \passthrough{\lstinline!info!}
-command of each sensor is queried. This information is added to the
-previously created \gls{lut}. Duplicate entries are summarised (see
-Table \ref{Sensor_capabilities_merging_algorithm.csv}) and returned to
-the host when the \passthrough{\lstinline!info!} \ref{lst:mtsc} command
-is received over network.
+measurement. For this purpose, the \emph{info} command of each sensor is
+queried. This information is added to the previously created \gls{lut}.
+Duplicate entries are summarised (see Table
+\ref{Sensor_capabilities_merging_algorithm.csv}) and returned to the
+host when the \emph{info} \ref{lst:mtsc} command is received over
+network.
 
@@
 
-The same procedure is performed for the
-\passthrough{\lstinline!commands!} \gls{cli}-command of each sensor, to
-merge available commands of connected sensors into the \gls{lut}.
+The same procedure is performed for the \emph{commands}
+\gls{cli}-command of each sensor, to merge available commands of
+connected sensors into the \gls{lut}.
 
@@
 correct sensor. In addition, there are commands such as the previously
-used \passthrough{\lstinline!info!} or \passthrough{\lstinline!status!}
-command, which must be intercepted by the
-\passthrough{\lstinline!MRPProxy!} module so that it can be handled
-differently (see example \ref{lst:mtsc}).
+used \emph{info} or \emph{status} command, which must be intercepted by
+the \emph{MRPProxy} module so that it can be handled differently (see
+example \ref{lst:mtsc}).
 
 To realize this, a \gls{lut} was created in the previous steps, which
-contains information regarding
-\passthrough{\lstinline!requested capability!} -\textgreater{}
-\passthrough{\lstinline!sensor!}-\gls{uuid} -\textgreater{}
-\passthrough{\lstinline!physical sensor!} and allows the commands to be
-routed.
-
-For commands where there are several entries for
-\passthrough{\lstinline!CAPABLE SENSORS ID LUT!}
-\ref{Sensor_capabilities_merging_algorithm.csv}, there are two possible
-approaches to how the command is processed:
+contains information regarding \emph{requested capability}
+-\textgreater{} \emph{sensor}-\gls{uuid} -\textgreater{} \emph{physical
+sensor} and allows the commands to be routed.
+
+For commands where there are several entries for \emph{CAPABLE SENSORS
+ID LUT} \ref{Sensor_capabilities_merging_algorithm.csv}, there are two
+possible approaches to how the command is processed:
 
@@
 The decision is based on which hardware sensors are connected. In a
-setup where only the same sensor variants are connected,
-\passthrough{\lstinline!redirect to each capable sensor!} is applied.
-This offers a time advantage as fewer commands need to be sent from the
-host. Thus, with a \passthrough{\lstinline!readsensor!} command, all
-sensors are read out via one command and the summarized result is
-transmitted to the host.
-
-The \passthrough{\lstinline!extend commands using an id parameter!}
-strategy is used for different sensors. Each command is extended on the
-\passthrough{\lstinline!Network-Proxy!} \ref{network-proxy} by another
-\gls{uuid} parameter, according to the following scheme:
+setup where only the same sensor variants are connected, \emph{redirect
+to each capable sensor} is applied. This offers a time advantage as
+fewer commands need to be sent from the host. Thus, with a
+\emph{readsensor} command, all sensors are read out via one command and
+the summarized result is transmitted to the host.
+
+The \emph{extend commands using an id parameter} strategy is used for
+different sensors. Each command is extended on the \emph{Network-Proxy}
+\ref{network-proxy} by another \gls{uuid} parameter, according to the
+following scheme:
 
@@
 \item
-  \passthrough{\lstinline!readsensor <axis> <sensor number>!}
-  -\textgreater{} \passthrough{\lstinline!readsensor <axis> <ID>!}
-\item
-  \passthrough{\lstinline!opmode!}-\textgreater{}
-  \passthrough{\lstinline!opmode <ID>!}
+  \emph{readsensor } -\textgreater{} \emph{readsensor }
+\item
+  \emph{opmode} -\textgreater{} \emph{opmode }
 \end{itemize}
@@
 
-The \passthrough{\lstinline!MRPReading!} is the key module of the
-\gls{mrp} core. It is used to manage the measurement data and can be
-imported and exported. The following example
-\ref{lst:mrpexample_reading} shows how a measurement is created and
-measurement points are added in the form of
-\passthrough{\lstinline!MRPReadingEntry!} instances.
+The \emph{MRPReading} is the key module of the \gls{mrp} core. It is
+used to manage the measurement data and can be imported and exported.
+The following example \ref{lst:mrpexample_reading} shows how a
+measurement is created and measurement points are added in the form of
+\emph{MRPReadingEntry} instances.
 
@@
 describes the measurement. This is realised in the example using the
-\passthrough{\lstinline!set\_additional\_data!} function.
+\emph{set\_additional\_data} function.
 
@@
 processing; various export formats are available. Using the
-\passthrough{\lstinline!dump\_to\_file!} function, the measurement can
-be converted into an open \gls{json} format. This file can then be
-imported again using the \passthrough{\lstinline!load\_from\_file!}
-function.
+\emph{dump\_to\_file} function, the measurement can be converted into an
+open \gls{json} format.
 
@@
 example \ref{mrpreading}, the next step is to record real sensor data.
-For this purpose, the \passthrough{\lstinline!MRPHal!} module was
-developed, which can interact with all
-\passthrough{\lstinline!Unified Sensor!} \ref{unified-sensor}-compatible
-sensors. In the following example \ref{lst:mrpexample_hal}, an
-\passthrough{\lstinline!1D: Single Sensor!} \ref{d-single-sensor} is
-connected locally to the host \gls{pc}.
+For this purpose, the \emph{MRPHal} module was developed, which can
+interact with all \emph{Unified Sensor} \ref{unified-sensor}-compatible
+sensors. In the following example \ref{lst:mrpexample_hal}, an \emph{1D:
+Single Sensor} \ref{d-single-sensor} is connected locally to the host
+\gls{pc}.
 
@@
 In general, a sensor can be connected using its specific system path or
-the sensor-\gls{uuid} via the
-\passthrough{\lstinline!MRPHalSerialPortInformation!} function. Locally
-connected or network sensors can also be automatically recognised using
-the \passthrough{\lstinline!list\_sensors!} function. Once connected,
+the sensor-\gls{uuid} via the \emph{MRPHalSerialPortInformation}
+function. Locally connected or network sensors can also be automatically
+recognised using the \emph{list\_sensors} function. Once connected,
 these are then converted into a usable data source using the
-\passthrough{\lstinline!MRPReadingSource!} module. This automatically
-recognises the type of sensor and generated an
-\passthrough{\lstinline!MRPReading!} instance with the measured values
-of the sensor.
+\emph{MRPReadingSource} module. This automatically recognises the type
+of sensor and generated an \emph{MRPReading} instance with the measured
+values of the sensor.
 
@@
 If no hardware sensor is available or for the generation of test data,
-the \passthrough{\lstinline!MRPSimulation!} module is available. This
-contains a series of functions that simulate various magnets and their
-fields. The result is a complete \passthrough{\lstinline!MRPReading!}
-measurement with a wide range of set meta data.
+the \emph{MRPSimulation} module is available. This contains a series of
+functions that simulate various magnets and their fields. The result is
+a complete \emph{MRPReading} measurement with a wide range of set meta
+data.
 
 The example \ref{lst:mrpexample_simulation} illustrated the basic usage.
-Different variations of the \passthrough{\lstinline!generate\_reading!}
-function offers the user additional parameterisation options, such as
-random polarisation direction or a defined centre-of-gravity vector. The
-data is generated in the background using the
-\passthrough{\lstinline!magpylib!} \cite{ortner2020magpylib} library
-according to the specified parameters.
+Different variations of the \emph{generate\_reading} function offers the
+user additional parameterisation options, such as random polarisation
+direction or a defined centre-of-gravity vector. The data is generated
+in the background using the \emph{magpylib}
+\cite{ortner2020magpylib} library according to the specified
+parameters.
 
@@
 functions for this purpose. The code example shows the basic use of the
-module. The \passthrough{\lstinline!Evaluation!} \ref{evaluation}
-chapter shows how the user can implement their own algorithms and add
-them to the library.
+module. The \emph{Evaluation} \ref{evaluation} chapter shows how the
+user can implement their own algorithms and add them to the library.
 
@@
 
-This final example shows the use of the
-\passthrough{\lstinline!MRPVisualisation!} module, which provides
-general functions for visualising measurements. The visualisation
-optionsmakes it possible to visually assess the results of a
-measurement. This is particularly helpful for full-sphere measurements
-recorded with the \passthrough{\lstinline!3D: Fullsphere!}
-\ref{d-fullsphere} sensor. The sub-module
-\passthrough{\lstinline!MRPPolarVisualisation!} is specially designed
-for these. The figure
+This final example shows the use of the \emph{MRPVisualisation} module,
+which provides general functions for visualising measurements. The
+visualisation optionsmakes it possible to visually assess the results of
+a measurement. This is particularly helpful for full-sphere measurements
+recorded with the \emph{3D: Fullsphere} \ref{d-fullsphere} sensor. The
+sub-module \emph{MRPPolarVisualisation} is specially designed for these.
+The figure
 \ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
 shows a plot of a fullsphere measurement. It is also possible to export
-the data from the \passthrough{\lstinline!MRPAnalysis!} module
-graphically as diagrams. The \passthrough{\lstinline!MRPVisualisation!}
-modules are used here. The following example
+the data from the \emph{MRPAnalysis} module graphically as diagrams. The
+\emph{MRPVisualisation} modules are used here. The following example
 \ref{lst:mrpexample_visualisation} shows the usage of both modules.
@@
 
-\hypertarget{mrphallbacharraygenerator}{%
-\subsection{MRPHallbachArrayGenerator}\label{mrphallbacharraygenerator}}
+\hypertarget{mrphalbacharraygenerator}{%
+\subsection{MRPHalbachArrayGenerator}\label{mrphalbacharraygenerator}}
 
 The following example code \ref{lst:mrpexample_hallbach}, shows how a
-simple Hallbach magnetic ring can be generated.
+simple Halbach magnetic ring can be generated.
 
@@
 Eight random measurements are generated here. It is important that the
-magnet type (here \passthrough{\lstinline!N45\_CUBIC\_15x15x15!}) is
-specified. This is necessary so that the correct magnet cutouts can be
-generated when creating the 3D model.
+magnet type (here \emph{N45\_CUBIC\_15x15x15}) is specified. This is
+necessary so that the correct magnet cutouts can be generated when
+creating the 3D model.
 
 After the measurements have been generated, they are provided with a
-position and rotation offset according to the Hallbach design and
+position and rotation offset according to the Halbach design and
 calucation scheme \cite{HallbachMagnetDesignPaper} using the
-\passthrough{\lstinline!MRPHallbachArrayGenerator!} module.
-
-\begin{lstlisting}[language=Python, caption={MRPHallbachArrayGenerator example for generating an OpenSCAD based hallbach ring}, label=lst:mrpexample_hallbach]
+\emph{MRPHalbachArrayGenerator} module.
+
+\begin{lstlisting}[language=Python, caption={MRPHalbachArrayGenerator example for generating an OpenSCAD based halbach ring}, label=lst:mrpexample_halbach]
 readings = []
@@
   readings.append(MRPSimulation.MRPSimulation.generate_reading(MRPMagnetTypes.MagnetType.N45_CUBIC_15x15x15))
-## GENERATE HALLBACH
-hallbach_array: MRPHallbachArrayGenerator.MRPHallbachArrayResult = MRPHallbachArrayGenerator.MRPHallbachArrayGenerator.generate_1k_hallbach_using_polarisation_direction(readings)
+## GENERATE HALBACH
+halbach_array: MRPHalbachArrayGenerator.MRPHalbachArrayResult = MRPHalbachArrayGenerator.MRPHalbachArrayGenerator.generate_1k_halbach_using_polarisation_direction(readings)
 # EXPORT TO OPENSCAD
 ## 2D MODE DXF e.g. for lasercutting
-MRPHallbachArrayGenerator.MRPHallbachArrayGenerator.generate_openscad_model([hallbach_array], "./2d_test.scad",_2d_object_code=True)
+MRPHalbachArrayGenerator.MRPHalbachArrayGenerator.generate_openscad_model([halbach_array], "./2d_test.scad",_2d_object_code=True)
 ## 3D MODE e.g. for 3D printing
-MRPHallbachArrayGenerator.MRPHallbachArrayGenerator.generate_openscad_model([hallbach_array], "./3d_test.scad",_2d_object_code=False)
+MRPHalbachArrayGenerator.MRPHalbachArrayGenerator.generate_openscad_model([halbach_array], "./3d_test.scad",_2d_object_code=False)
 \end{lstlisting}
@@
 is generated from the generated magnet positions. The result is an
-\passthrough{\lstinline!OpenSCAD!} \cite{OpenSCAD} file, which
-contains the module generated. After computing the model using the
-\passthrough{\lstinline!OpenSCAD!} \gls{cli} utility, the following
-model rendering
+\emph{OpenSCAD} \cite{OpenSCAD} file, which contains the module
+generated. After computing the model using the \emph{OpenSCAD} \gls{cli}
+utility, the following model rendering
 \ref{Generated_Hallbach_array_with_generated_cutouts_for_eight_magnets.png}
@@
 and run it at the end. The result is an exported file with the measured
-values. These can then be read in again using the
-\passthrough{\lstinline!MRPReading!} module and processed further. The
-following bash code \ref{lst:mrpcli_config_run} shows the setup
-procedure in detail:
+values. These can then be read in again using the \emph{MRPReading}
+module and processed further. The following bash code
+\ref{lst:mrpcli_config_run} shows the setup procedure in detail:
 
@@
 
-In order to implement such a pipeline, the
-\passthrough{\lstinline!yaml!} file format was chosen for the definition
-of the pipeline, as this is for non programmers to understand and can
-also be easily edited with a plain text editor. Detailed examples can be
-found in the documentation
+In order to implement such a pipeline, the \emph{yaml} file format was
+chosen for the definition of the pipeline, as this is for non
+programmers to understand and can also be easily edited with a plain
+text editor. Detailed examples can be found in the documentation
 \cite{MagneticReadoutProcessingReadTheDocs}. The pipeline definition
@@
 
-The signatures in the \passthrough{\lstinline!yaml!} file are called
-using \passthrough{\lstinline!reflection!} and a real-time search of the
-loaded \passthrough{\lstinline!global()!} functions symbol table
+The signatures in the \emph{yaml} file are called using reflection and a
+real-time search of the loaded \emph{global()} functions symbol table
 \cite{PythonGlobalSymbolTable}. This system makes almost all Python
@@
 definition \ref{lst:mrpuddp_example_yaml} shows the previously defined
-steps \ref{Example_measurement_analysis_pipeline.png} as
-\passthrough{\lstinline!yaml!} syntax.
+steps \ref{Example_measurement_analysis_pipeline.png} as \emph{yaml}
+syntax.
 
@@
 
-Each pipeline step is divided into \passthrough{\lstinline!stages!},
-which contain a name, the function to be executed and its parameters.
+Each pipeline step is divided into \emph{stages}, which contain a name,
+the function to be executed and its parameters.
 
@@
 
-The various steps are then linked by using the
-\passthrough{\lstinline!stage <name>!} makro as input parameter of the
-next function to be executed (see comments in
+The various steps are then linked by using the \emph{stage } makro as
+input parameter of the next function to be executed (see comments in
 \ref{lst:mrpuddp_example_yaml}).
@@
 created for all important functionalities and usecases. The test
-framework \passthrough{\lstinline!PyTest!} \cite{PyTest} was used
-for this purpose, as it offers direct integration in most \gls{ide}s
-(see
+framework \emph{PyTest} \cite{PyTest} was used for this purpose, as
+it offers direct integration in most \gls{ide}s (see
 \ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
@@
 One problem, is the parts of the \gls{mrp}-library that require direct
-access to external hardware. These are, for example, the
-\passthrough{\lstinline!MRPHal!} and
-\passthrough{\lstinline!MRPHalRest!} modules, which are required to read
-out sensors connected via the network. Two different approaches were
-used here. In the case of local development, the test runs were carried
-out on a \gls{pc} that can reach the network hardware and thus the test
-run could be carried out with real data.
+access to external hardware. These are, for example, the \emph{MRPHal}
+and \emph{MRPHalRest} modules, which are required to read out sensors
+connected via the network. Two different approaches were used here. In
+the case of local development, the test runs were carried out on a
+\gls{pc} that can reach the network hardware and thus the test run could
+be carried out with real data.
 
@@
 In the other scenario, the tests are to be carried out before a new
-release in the repository on the basis of
-\passthrough{\lstinline!Github Actions!} \cite{GithubActions}. Here
-there is the possibility to host local runner software, which then has
-access to the hardware, but then a \gls{pc} must be permanently
-available for this task. Instead, the hardware sensors were simulated by
-software and executed via virtualisation on the systems provided by
-\passthrough{\lstinline!Github Actions!}.
+release in the repository on the basis of \emph{Github Actions}
+\cite{GithubActions}. Here there is the possibility to host local
+runner software, which then has access to the hardware, but then a
+\gls{pc} must be permanently available for this task. Instead, the
+hardware sensors were simulated by software and executed via
+virtualisation on the systems provided by \emph{Github Actions}.
 
@@
 programming language, there are several public package registry where
-users can provide their software modules. Here,
-\passthrough{\lstinline!PyPi!}\cite{PyPI}
+users can provide their software modules. Here, \emph{PyPi}
+\cite{PyPI}
 \ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}
@@
 package in an isolated environment and then provide an installation
-\passthrough{\lstinline!wheel!} archive. This can then be uploaded to
-the package registry. Since the \gls{mrp}-library requires additional
-Python dependencies (e.g.~\passthrough{\lstinline!numpy!},
-\passthrough{\lstinline!matplotlib!} packages), which cannot be assumed
-to be already installed on the target system, these must be installed
-prior to the actual installation. These can be specified in the library
-installation configuration \passthrough{\lstinline!setup.py!}
+\emph{wheel} archive. This can then be uploaded to the package registry.
+Since the \gls{mrp}-library requires additional Python dependencies,
+which cannot be assumed to be already installed on the target system,
+these must be installed prior to the actual installation. These can be
+specified in the library installation configuration \emph{setup.py}
 \ref{lst:setup_py_req} for this purpose.
@@
 To make the \gls{cli} scripts written in Python easier for the user to
-execute without having to use the \passthrough{\lstinline!python3!}
-prefix. This has been configured in the installation configuration using
-the \passthrough{\lstinline!entry\_points!} option, and the following
-commands are available to the user:
+execute without having to use the \emph{python3} prefix. This has been
+configured in the installation configuration using the
+\emph{entry\_points} option, and the following commands are available to
+the user:
 
@@
 In order to provide comprehensive documentation for the enduser, the
-source code was documented using
-Python-\passthrough{\lstinline!docstrings!}
-\cite{PythonDocstringReference} and the Python 3.5 type annotations:
-
-\begin{itemize}
-\tightlist
-\item
-  Function description
-\item
-  Input parameters, using \passthrough{\lstinline!param!} and
-  \passthrough{\lstinline!type!}
-\item
-  Return value, using \passthrough{\lstinline!returns!},
-  \passthrough{\lstinline!rtype!}
-\end{itemize}
-
-The use of type annotations also simplifies further development, as
-modern \gls{ide}s can more reliably display possible methods to the user
-as an assistance. \ref{lst:pydocstring}
+source code was documented using Python-\emph{docstrings}
+\cite{PythonDocstringReference} and the Python type annotations. The
+use of type annotations also simplifies further development, as modern
+\gls{ide}s can more reliably display possible methods to the user as an
+assistance. \ref{lst:pydocstring}
 
@@
 
-Since \passthrough{\lstinline!docstrings!} only document the source
-code, but do not provide simple how-to-use instructions, the
-documentation framework \passthrough{\lstinline!Sphinx!}
-\cite{SphinxDocumentation} was used for this purpose. This framework
-makes it possible to generate \gls{html} or \gls{pdf} documentation from
-various source code documentation formats, such as the used
-\passthrough{\lstinline!docstrings!}.
+Since \emph{docstrings} only document the source code, but do not
+provide simple how-to-use instructions, the documentation framework
+\emph{Sphinx} \cite{SphinxDocumentation} was used for this purpose.
+This framework makes it possible to generate \gls{html} or \gls{pdf}
+documentation from various source code documentation formats, such as
+the used \emph{docstrings}.
 
@@
 installation instructions. In order to make the documentation created by
-\passthrough{\lstinline!Sphinx!} accessible to the user, there are, as
-with the package management by \passthrough{\lstinline!PyPi!} services,
-which provide the \gls{mrp}-library documentation online.
+\emph{Sphinx} accessible to the user, there are, as with the package
+management by \emph{PyPi} services, which provide the \gls{mrp}-library
+documentation online.
 
@@
 publication option is to host the documentation via online services such
-as \passthrough{\lstinline!ReadTheDocs!} \cite{ReadTheDocs}, where
-users can make documentation for typical software projects available to
-others.
-
-The documentation has also been uploaded to
-\passthrough{\lstinline!ReadTheDocs!}
+as \emph{ReadTheDocs} \cite{ReadTheDocs}, where users can make
+documentation for typical software projects available to others.
+
+The documentation has also been uploaded to \emph{ReadTheDocs}
 \cite{MagneticReadoutProcessingReadTheDocs} and linked in the
@@
 \ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
-on \passthrough{\lstinline!PyPi!}.
+on \emph{PyPi}.
 
 The process of creating and publishing the documentation has been
-automated using \passthrough{\lstinline!GitHub Actions!}, so that it is
-always automatically kept up to date with new features.
+automated using \emph{GitHub Actions}, so that it is always
+automatically kept up to date with new features.
 
@@
 
-TODO: fix links o evaluation
-
-\hypertarget{evaluation}{%
-\chapter{Evaluation}\label{evaluation}}
-
-This work successfully implemented a universal hardware and software
-framework for the automated characterisation of permanent magnets. This
-framework consists of a low-cost hardware interface that supports
-various magnetic field sensors and a library for automating and
-analysing the measurement data. The process of this framework comprises
-several steps, which will be explain below:
-
-\begin{itemize}
-\tightlist
-\item
-  TODO
-\end{itemize}
-
-\hypertarget{hardware-evaluation}{%
-\section{Hardware Evaluation}\label{hardware-evaluation}}
-
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
-\caption{Sensor evaluation plattform with TLV493D and MMC5603 sensors
-placed with thermal conductive glue on an aluminium baseplate
-\label{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}}
-\end{figure}
-
-\begin{itemize}
-\tightlist
-\item
-  cheap sensors used
-\item
-  used hardware list
-\item
-  tested sensor tlv mmc, da diese zum zeitpunkt des tests zur verfüung
-  standen
-\end{itemize}
-
-The sensor platform used here is an adapted version of the
-\passthrough{\lstinline!1D: Single Sensor!} \ref{d-single-sensor} sensor
-platform. The sensors to be measured were fixed together on an aluminium
-plate with thermally conductive adhesive. This compensates for thermal
-differences.
-
-This is crucial for the subsequent temperature deviation tests in order
-to obtain comparable measurement results. The graphic
-\ref{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
-shows this basic setup, the Raspberry Pi Pico shown here was used as the
-readout hardware, on which the Unified Sensor Firmware version
-\passthrough{\lstinline!1.0.2!} is running.
-
-A separate \passthrough{\lstinline!KA30005D!} laboratory power supply is
-used as the power supply for the sensors. An Raspberry Pi 4 is used as
-the host computer, which is connected to the sensors via a
-\passthrough{\lstinline!Hailege ADUM3160!} \gls{usb} isolator and is
-placed outside the temperature chamber. \passthrough{\lstinline!MRPCli!}
-\ref{command-line-interface} version \passthrough{\lstinline!1.5.0!} was
-used to control and record the measurement series, with the functions of
-the \passthrough{\lstinline!MRPDataVisualisation!}
-\ref{mrpvisualisation} and \passthrough{\lstinline!MRPAnalysis!}
-\ref{mrpanalysis} packages from the library
-\ref{software-readout-framework} being used for subsequent evaluation.
-The recorded measurement series are automatically analysed using the
-\passthrough{\lstinline!Programmable-  Data Pprocessing Pipeline!}
-\ref{programmable-data-processing-pipeline} and the results are
-visualised.
-
-\hypertarget{read-noise}{%
-\subsection{Read Noise}\label{read-noise}}
-
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_noise_measurements.png}
-\caption{Sensor evaluation setup for noise measurements
-\label{Sensor_evaluation_setup_for_noise_measurements.png}}
-\end{figure}
-
-Measuring the noise in a magnetic field sensor requires a precise
-procedure and a special measurement setup. First, the magnetic field
-sensor is placed in a quiet environment to minimize external
-interference.
-
-The procedure begins with the acquisition of the baseline by operating
-the sensor without external magnetic fields. For this purpose, a sample
-size of N=10000 measured values was recorded for the reference
-measurement.
-
-The output signal of the sensor is then continuously measured and
-recorded. It is important to carry out the measurement over a
-sufficiently long period of time in order to record both short-term and
-long-term fluctuations. For this purpose, N=1000 measured values were
-also taken with a trigger and readout rate of one measurement per
-second.
-
-The baseline measurement and the continuous measurement were configured
-in advance using \passthrough{\lstinline!MRPCli!} \gls{cli}.
-
-In order to quantify the noise, the standard deviation or the mean
-square deviation of the signal is calculated. These parameters provide
-information about the variation of the signal over time and therefore
-about the sensor background noise.
-
-After the measurements were completed, the data was evaluated using the
-available MRPDataVisualization and MRPAnalysis functions. These
-graphically represent the following measured values:
-
-\begin{itemize}
-\tightlist
-\item
-  Plot of the raw measurement data, as well as its mean value
-  \passthrough{\lstinline!$\\mu\_\{rv\}$!} using Baselin
-\item
-  Plot of the temperature curve over the complete measurement series,
-  which was recorded with the sensor's internal temperature sensor
-\item
-  Noise level as a percentage deviation from the baseline
-\item
-  Histogram of the noise level with marked standard deviation
-\end{itemize}
-
-\hypertarget{temperature-deviation}{%
-\subsection{Temperature Deviation}\label{temperature-deviation}}
-
-using same setup as in read noise but with programmed temperature
-controller of the chamber
-
-\hypertarget{linearity}{%
-\subsection{Linearity}\label{linearity}}
-
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_linearity_measurements.png}
-\caption{Sensor evaluation setup for linearity measurements
-\label{Sensor_evaluation_setup_for_linearity_measurements.png}}
-\end{figure}
-
-\begin{itemize}
-\tightlist
-\item
-  minimal distance between sensor and magnet due to messbreich
-\end{itemize}
-
-\hypertarget{result-analysis}{%
-\subsubsection{Result Analysis}\label{result-analysis}}
-
-are they suitable for \textless1000ppm ?
-
-\begin{itemize}
-\tightlist
-\item
-  https://onlinelibrary.wiley.com/doi/epdf/10.1002/mrm.28396
-\item
-  27cm / 50mT bore
-\item
-  nmr probes for better results
-\end{itemize}
-
-\hypertarget{software-evaluation}{%
-\section{Software Evaluation}\label{software-evaluation}}
-
-TODO: HOW TO TEST library SOFTWARE
+\hypertarget{usecase-evaluation}{%
+\chapter{Usecase Evaluation}\label{usecase-evaluation}}
+
+The practical application of the hardware and software framework is
+shown below. This is shown using the previously defined usecases
+\ref{usecases}. In the application example, various permanent magnets
+are measured and then sorted according to their field strength. The
+result should then list the magnets that deviate the least from each
+other in terms of their field strength. This is determined using a
+sorting algorithm developed by the user.
+
+The process is broken down into the following steps and the practical
+application of \emph{User Interaction Points}
+\ref{user-interaction-points} is shown:
 
@@
 \hypertarget{hardware-preperation}{%
-\subsection{Hardware preperation}\label{hardware-preperation}}
+\section{Hardware preperation}\label{hardware-preperation}}
 
@@
 exchangeable magnetic holder mount, suitable holders are required for
-the magnets to be measured. Ten random
-\passthrough{\lstinline!N45 12x12x12mm!} neodymium magnets were used,
-which are shown in figure
+the magnets to be measured. Ten random \emph{N45 12x12x12mm} neodymium
+magnets were used, which are shown in figure
 \ref{Ten_numbered_test_magnets_in_separate_holders.png}.
@@
 \hypertarget{configuration-of-the-measurement}{%
-\subsection{Configuration of the
+\section{Configuration of the
 Measurement}\label{configuration-of-the-measurement}}
@@
 The configured hardware was then connected to the host system using the
-\passthrough{\lstinline!MRPcli config setupsensor!}-\gls{cli} command.
-Afterwards, the measurement was configured for an measurement run, using
-the following configuration commands
-\ref{lst:evaluation_measurement_config}.
+\emph{MRPcli config setupsensor}-\gls{cli} command. Afterwards, the
+measurement was configured for an measurement run, using the following
+configuration commands \ref{lst:evaluation_measurement_config}.
 
@@
 
-The \passthrough{\lstinline!MRPcli measure run!} command was then called
-up for each individual magnet to execute a measurement. After each run,
-the \passthrough{\lstinline!READING-NAME!} parameter was filled with the
-id of the next magnet so that all measurements could be assigned to the
-physical magnets.
+The \emph{MRPcli measure run} command was then called up for each
+individual magnet to execute a measurement. After each run, the
+\emph{READING-NAME} parameter was filled with the id of the next magnet
+so that all measurements could be assigned to the physical magnets.
 
 \hypertarget{custom-algorithm-implementation}{%
-\subsection{Custom Algorithm
+\section{Custom Algorithm
 Implementation}\label{custom-algorithm-implementation}}
@@
 function signature and is implemented in the file
-\passthrough{\lstinline!UDPPFunctionCollection.py!}. This Python file is
-loaded when the pipeline is started and all functions that are imported
-here as a module or implemented directly can be called via the pipeline.
-As this is a short algorithm, it was inserted directly into the file.
-
-The parameter \passthrough{\lstinline!\_readings!} should later receive
-the imported measurements from the
-\passthrough{\lstinline!stage rawimport!}
+\emph{UDPPFunctionCollection.py}. This Python file is loaded when the
+pipeline is started and all functions that are imported here as a module
+or implemented directly can be called via the pipeline. As this is a
+short algorithm, it was inserted directly into the file.
+
+The parameter *\_readings* should later receive the imported
+measurements from the \emph{stage rawimport}
 \ref{lst:pipeline_mrp_evaluation_yaml} and the optional
-\passthrough{\lstinline!IP\_return\_count!} parameter specifies the
-number of best measurements that are returned. The return parameter is a
-list of measurements containing the most similar measurements, measured
-by the smallest distance between all measurements. The distance for each
+\emph{IP\_return\_count} parameter specifies the number of best
+measurements that are returned. The return parameter is a list of
+measurements containing the most similar measurements, measured by the
+smallest distance between all measurements. The distance for each
 measurement is determined using the center of gravity function
-\passthrough{\lstinline!CoG!}, the length is then calculated from the
-result vector. This value can then be used for sorting.
+\emph{CoG}, the length is then calculated from the result vector. This
+value can then be used for sorting.
 
@@
 
-The Python \passthrough{\lstinline!heapq!} \cite{heapq} module,
-which implements a priority queue, is used for this purpose. The
-calculated distances from the \passthrough{\lstinline!CoG!} value of the
-measurements to are inserted into this queue. Subsequently, as many
-elements of the queue are returned as defined by the
-\passthrough{\lstinline!IP\_return\_count!} parameter. The actual
-sorting was carried out by the queue in the background.
+The Python \emph{heapq} \cite{heapq} module, which implements a
+priority queue, is used for this purpose. The calculated distances from
+the \emph{CoG} value of the measurements to are inserted into this
+queue. Subsequently, as many elements of the queue are returned as
+defined by the \emph{IP\_return\_count} parameter. The actual sorting
+was carried out by the queue in the background.
 
 \hypertarget{alternative-filter-algorithm-implementation}{%
-\subsubsection{Alternative Filter Algorithm
+\subsection{Alternative Filter Algorithm
 Implementation}\label{alternative-filter-algorithm-implementation}}
@@
 \ref{lst:custom_find_similar_values_algorithm_refmagnet} shows the
-modified filter algorithm code, with added
-\passthrough{\lstinline!\_ref!} input parameter for the reference
-measurement.
+modified filter algorithm code, with added *\_ref* input parameter for
+the reference measurement.
 
@@
 \hypertarget{execution-of-analysis-pipeline}{%
-\subsection{Execution of Analysis
+\section{Execution of Analysis
 Pipeline}\label{execution-of-analysis-pipeline}}
@@
 pipeline \ref{Example_measurement_analysis_pipeline.png} is simplified
-and an additional stage \passthrough{\lstinline!find\_similar\_values!}
-has been added, which has set
-\passthrough{\lstinline!FindSimilarValuesAlgorithm!} as the function to
-be called. As a final step, the result is used in the
-\passthrough{\lstinline!plot\_filtered!} stage for visualisation.
+and an additional stage \emph{find\_similar\_values} has been added,
+which has set \emph{FindSimilarValuesAlgorithm} as the function to be
+called. As a final step, the result is used in the \emph{plot\_filtered}
+stage for visualisation.
 
@@
 The final pipeline has been saved in the pipeline directory as
-\passthrough{\lstinline!pipeline\_mrp\_evaluation.yaml!} file and is
-ready for execution. This is carried out using the
-\passthrough{\lstinline!MRPudpp!} (cli)
+\emph{pipeline\_mrp\_evaluation.yaml} file and is ready for execution.
+This is carried out using the \emph{MRPudpp} (cli)
 \ref{lst:bash_pipeline_mrp_evaluation_yaml}. After the run has been
 successfully completed, the results are saved in the result folder
-specified in the pipeline using the
-\passthrough{\lstinline!IP\_export\_folder!} parameter.
+specified in the pipeline using the \emph{IP\_export\_folder} parameter.
 
@@
 
-\hypertarget{result-analysis-1}{%
-\subsection{Result Analysis}\label{result-analysis-1}}
+\hypertarget{result-analysis}{%
+\section{Result Analysis}\label{result-analysis}}
 
@@
 shows this result. The plot of the raw measured values is shown on the
-left. The value of the determined \passthrough{\lstinline!GoG [uT]!}
-values is plotted on ten individual measured values. Here it can be seen
-that there are measured values with larger deviations (see measurement
-\passthrough{\lstinline!7:0!},\passthrough{\lstinline!10-2:0!},\passthrough{\lstinline!10-1:0!}).
+left. The value of the determined \emph{GoG} \(\mu\)T values is plotted
+on ten individual measured values. Here it can be seen that there are
+measured values with larger deviations (see measurement
+\emph{7:0},\emph{10-2:0},\emph{10-1:0}).
 
@@
 the measured values are plotted as a result of the filter algorithm. As
-the \passthrough{\lstinline!IP\_return\_count!} parameter was set to
-four, only the four most similar measurements were exported here. It can
-be seen from the plotted \passthrough{\lstinline!CoG [uT]!} deviation
-values, that these are closest to an ideal Magnet with a
-\passthrough{\lstinline!CoG!} value of 0uT. This ideal value was
+the \emph{IP\_return\_count} parameter was set to four, only the four
+most similar measurements were exported here. It can be seen from the
+plotted \emph{CoG} \(\mu\)T deviation values, that these are closest to
+an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal value was
 calculated with the function
-\passthrough{\lstinline!MRP.MRPSimulation.generate\_simulated\_reading!},
-with the same measurement parameters (magnet type, dimensions, sensor
-distance) as they correspond to the mechanical structure of the used
-hardware sensor \ref{d-fullsphere}.
-
-If the alternative filter algorithm from chapter
-\passthrough{\lstinline!Alternative Filter Algorithm Implementation!}
+\emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
+measurement parameters (magnet type, dimensions, sensor distance) as
+they correspond to the mechanical structure of the used hardware sensor
+\ref{d-fullsphere}.
+
+If the alternative filter algorithm from chapter \emph{Alternative
+Filter Algorithm Implementation}
 \ref{alternative-filter-algorithm-implementation} is executed here, the
 same result is returned if the magnet measurement with \gls{id}
-\passthrough{\lstinline!5:0!} is used as the reference magnet.
+\emph{5:0} is used as the reference magnet.
 
@@
 
-\hypertarget{conclusion-and-dicussion}{%
-\chapter{Conclusion and Dicussion}\label{conclusion-and-dicussion}}
+\hypertarget{evaluation}{%
+\chapter{Evaluation}\label{evaluation}}
+
+This work successfully implemented a universal hardware and software
+framework for the automated characterisation of permanent magnets. This
+framework consists of a low-cost hardware interface that supports
+various magnetic field sensors and a library for automating and
+analysing the measurement data.
+
+next step is the sensor evaluation
+
+\begin{itemize}
+\tightlist
+\item
+  software wurde erfolgreich evaluiert anhand der zuvor definierten
+  usecases.
+\item
+  folgend wird der zweite anwendungsfall evaluiert mit der frage ob die
+  magnete vermessen werden können
+\item
+  TODO
+\end{itemize}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
+\caption{Sensor evaluation plattform with TLV493D and MMC5603 sensors
+placed with thermal conductive glue on an aluminium baseplate
+\label{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}}
+\end{figure}
+
+\begin{itemize}
+\tightlist
+\item
+  cheap sensors used
+\item
+  used hardware list
+\item
+  tested sensor tlv mmc, da diese zum zeitpunkt des tests zur verfüung
+  standen
+\end{itemize}
+
+\begin{longtable}[]{@{}lllll@{}}
+\caption{Implemented digital magnetic field sensors
+\label{Implemented_digital_magnetic_field_sensors.csv}}\tabularnewline
+\toprule
+& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
+\midrule
+\endhead
+Readout-Axis & 3D & 3D & 3D & 1D\tabularnewline
+Temperature-Sensor & yes & no & yes & no\tabularnewline
+Resolution {[}uT{]} & 98 & 0.2 & 0.007 & 48\tabularnewline
+Range {[}mT{]} & ±130.0 & ±0.8 & ±3 & ±50\tabularnewline
+Interface & \gls{i2c} & \gls{i2c} & \gls{i2c} & \gls{i2c}\tabularnewline
+\bottomrule
+\end{longtable}
+
+\hypertarget{evaluation-sensor-setup}{%
+\section{Evaluation Sensor Setup}\label{evaluation-sensor-setup}}
+
+The sensor platform used here is an adapted version of the \emph{1D:
+Single Sensor} \ref{d-single-sensor} sensor platform. The sensors to be
+measured were fixed together on an aluminium plate with thermally
+conductive adhesive. This compensates for thermal differences. This is
+crucial for the subsequent temperature deviation tests in order to
+obtain comparable measurement results.
+
+The setup was placed and pre-wired in the temperature chamber 24 hours
+before the series of measurements were carried out. The insulated
+housing of a \emph{Voron 2.4} 3D printer, which has a separately
+controlled internal heating system, was used as the temperature chamber.
+To verify the temperature, an additional thermometer \emph{VC-7055BT}
+was placed on the base plate. A 10mm thick \emph{PTFE} insulation plate
+was placed between the floor and the sensor base plate to prevent direct
+and uneven heating of the base plate by the heated floor.
+
+The graphic
+\ref{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
+shows this basic setup, the \emph{Raspberry Pi Pico} shown here was used
+as the readout hardware, on which the \emph{Unified Sensor Firmware} is
+running. With additional connected switch, its possible to isolate or
+select a sensor or both sensors to be queried from the firmware.
+
+A separate battery powered supply is used as low-noise power supply for
+the sensors boards. An \emph{Raspberry Pi 4} is used as the host
+computer, which is connected to the sensors via a \emph{Hailege
+ADUM3160} \gls{usb} isolator and is placed outside the temperature
+chamber.
+
+\emph{MRPCli} \ref{command-line-interface} was used to control and
+record the measurement series, with the functions of the
+\emph{MRPDataVisualisation} \ref{mrpvisualisation} and
+\emph{MRPAnalysis} \ref{mrpanalysis} packages from the library
+\ref{software-readout-framework} being used for subsequent evaluation.
+The recorded measurement series are automatically analysed using the
+\emph{Programmable-Data Processing Pipeline}
+\ref{programmable-data-processing-pipeline} and the results are
+visualised.
+
+\hypertarget{sensor-characterisation-noise}{%
+\subsection{Sensor Characterisation:
+Noise}\label{sensor-characterisation-noise}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_noise_measurements.png}
+\caption{Sensor evaluation setup for noise measurements
+\label{Sensor_evaluation_setup_for_noise_measurements.png}}
+\end{figure}
+
+Measuring the noise in a magnetic field sensor requires a precise
+procedure and a special measurement setup. First, the magnetic field
+sensor is placed in a quiet environment to minimize external field
+interference.
+
+The procedure begins with the acquisition of the baseline by operating
+the sensor without external magnetic fields. For this purpose, a sample
+size of N=10000 measured values was recorded for the baseline
+measurement.
+
+The output signal of the sensor is then continuously measured and
+recorded. It is important to carry out the measurement over a
+sufficiently long period of time in order to record both short-term and
+long-term fluctuations. For this purpose, N=2000 further measured values
+were taken with a trigger and readout rate of one measurement per
+second.
+
+In order to quantify the noise, the standard deviation or the mean
+square deviation of the signal is calculated. These parameters provide
+information about the variation of the signal over time and therefore
+about the sensor background noise.
+
+\begin{longtable}[]{@{}lll@{}}
+\caption{Sensor noise evaluation result used symbols
+\label{Sensor_noise_evaluation_result_used_symbols.csv}}\tabularnewline
+\toprule
+Symbol & Unit & Description\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+Symbol & Unit & Description\tabularnewline
+\midrule
+\endhead
+\(\mu_{rv}\) & \(\mu\)T &\tabularnewline
+\(\mu_{t}\) & \(\mu\)T &\tabularnewline
+\(\mu_{nl}\) & \% &\tabularnewline
+\(\sigma_{nl}\) & \% &\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
+\caption{Sensor noise evaluation results for TLV493D and MMC5603NJ with
+N=2000 samples and no averaging
+\label{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}}
+\end{figure}
+
+\begin{itemize}
+\tightlist
+\item
+  Plot of the raw measurement data, as well as its mean value
+  \(\mu_{rv}\)\(\mu\)T using Baselin
+\item
+  Plot of the temperature curve over the complete measurement series,
+  which was recorded with the sensor's internal temperature sensor
+\item
+  Noise level as a percentage deviation from the baseline
+\item
+  Histogram of the noise level with marked standard deviation
+\end{itemize}
+
+TODO TABELLE EINORDNUNG MITTELUNGEN ALS TABELLE
+
+\hypertarget{temperature-sensitivity}{%
+\subsection{Temperature Sensitivity}\label{temperature-sensitivity}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}
+\caption{Sensor evaluation setup for temperature sensitivity
+measurements
+\label{Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}}
+\end{figure}
+
+using same setup as in read noise but with programmed temperature
+controller of the chamber
+
+\hypertarget{linearity}{%
+\subsection{Linearity}\label{linearity}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_linearity_measurements.png}
+\caption{Sensor evaluation setup for linearity measurements
+\label{Sensor_evaluation_setup_for_linearity_measurements.png}}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_linearity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
+\caption{Sensor linearity evaluation results for TLV493D and MMC5603NJ
+\label{Sensor_linearity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}}
+\end{figure}
+
+\begin{itemize}
+\tightlist
+\item
+  minimal distance between sensor and magnet due to messbreich
+\end{itemize}
+
+\hypertarget{result-analysis-1}{%
+\subsubsection{Result Analysis}\label{result-analysis-1}}
+
+are they suitable for \textless1000ppm ?
+
+\begin{itemize}
+\tightlist
+\item
+  https://onlinelibrary.wiley.com/doi/epdf/10.1002/mrm.28396
+\item
+  27cm / 50mT bore
+\item
+  nmr probes for better results
+\end{itemize}
+
+\hypertarget{conclusion-and-discussion}{%
+\chapter{Conclusion and Discussion}\label{conclusion-and-discussion}}
 

### 2024-02-14 documentation/thesis/thesis_document.tex
.

@@
 
-\hypertarget{sensor-characterisation-noise}{%
-\subsection{Sensor Characterisation:
-Noise}\label{sensor-characterisation-noise}}
+\hypertarget{sensor-characterisation-background-noise}{%
+\section{Sensor Characterisation:
+Background-Noise}\label{sensor-characterisation-background-noise}}
 
@@
 sensor is placed in a quiet environment to minimize external field
-interference.
+interference. The temperature chamber for all noise tests is set to
+\emph{20°C}.
 
@@
 the sensor without external magnetic fields. For this purpose, a sample
-size of N=10000 measured values was recorded for the baseline
+size of \emph{N=10000} measured values was recorded for the baseline
 measurement.
@@
 sufficiently long period of time in order to record both short-term and
-long-term fluctuations. For this purpose, N=2000 further measured values
-were taken with a trigger and readout rate of one measurement per
+long-term fluctuations. For this purpose, \emph{N=2000} further measured
+values were taken with a trigger and readout rate of one measurement per
 second.
 
-In order to quantify the noise, the standard deviation or the mean
-square deviation of the signal is calculated. These parameters provide
-information about the variation of the signal over time and therefore
-about the sensor background noise.
-
-\begin{longtable}[]{@{}lll@{}}
-\caption{Sensor noise evaluation result used symbols
-\label{Sensor_noise_evaluation_result_used_symbols.csv}}\tabularnewline
-\toprule
-Symbol & Unit & Description\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-Symbol & Unit & Description\tabularnewline
-\midrule
-\endhead
-\(\mu_{rv}\) & \(\mu\)T &\tabularnewline
-\(\mu_{t}\) & \(\mu\)T &\tabularnewline
-\(\mu_{nl}\) & \% &\tabularnewline
-\(\sigma_{nl}\) & \% &\tabularnewline
-\bottomrule
-\end{longtable}
+In order to quantify the noise, the standard deviation of the signal is
+calculated. These parameters provide information about the variation of
+the signal over time and therefore about the sensor background noise.
 
@@
 
+The following figure
+\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
+shows the measured values of these sensors. In the following, these are
+analysed for each sensor examined.
+
+The following data is shown in the plots:
+
 \begin{itemize}
@@
 \item
+  Plot of the raw data of the sensor
+\item
+  Plot of the sensor's internal temperature sensor
+\item
+  Background noise level with reference to the baseline
+\item
+  Histogram of the background noise level
+\end{itemize}
+
+\%\%Sensor\_noise\_evaluation\_results.csv\%\%
+
+\hypertarget{sensor-temperature-analysis}{%
+\subsection{Sensor Temperature
+Analysis}\label{sensor-temperature-analysis}}
+
+Compared to the \emph{MMC5603NJ}, the temperature plot of the
+\emph{TLV493D} shows that the internal temperature sensor is very noisy
+(maximum of \(\sigma^2_{t}\)=\emph{2\(^{\circ}\)C})and deviates from the
+ambient temperature at almost \emph{10\(^{\circ}\)C}. With a further
+measurement run with a different temperature setting of
+\emph{30\(^{\circ}\)C}, the offset is reduced to only
+\emph{4\(^{\circ}\)C} to the set temperature. However, the noise remains
+constant. When using an alternative sensor, this behaviour is reflected
+and therefore the internal temperature sensor of the \emph{TLV493D}
+should not be used for subsequent temperature compensation.
+
+\hypertarget{raw-sensor-data-analysis}{%
+\subsection{Raw Sensor Data Analysis}\label{raw-sensor-data-analysis}}
+
+\hypertarget{noise-level-data-analysis}{%
+\subsection{Noise Level Data Analysis}\label{noise-level-data-analysis}}
+
+\begin{itemize}
+\tightlist
+\item
   Plot of the raw measurement data, as well as its mean value
@@
 \hypertarget{temperature-sensitivity}{%
-\subsection{Temperature Sensitivity}\label{temperature-sensitivity}}
+\section{Temperature Sensitivity}\label{temperature-sensitivity}}
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
+\caption{Sensor temperature sensitivity evaluation results for TLV493D
+and MMC5603NJ
+\label{Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}}
+\end{figure}
+
 using same setup as in read noise but with programmed temperature
-controller of the chamber
+controller of the chamber and separate temperature probe under the
+sensors pcb
 
 \hypertarget{linearity}{%
-\subsection{Linearity}\label{linearity}}
+\section{Linearity}\label{linearity}}
 
@@
 \hypertarget{result-analysis-1}{%
-\subsubsection{Result Analysis}\label{result-analysis-1}}
+\section{Result Analysis}\label{result-analysis-1}}
 
@@
   nmr probes for better results
+\end{itemize}
+
+\hypertarget{recommendation-for-action}{%
+\subsection{recommendation for action}\label{recommendation-for-action}}
+
+\begin{itemize}
+\tightlist
+\item
+  folgendes setup woird für eine vermessung nach der sensor auswertung
+  emholen:
+\item
+  temperaturkomensation sowie linearitäts kompensation mit separaten
+  temperatur sensor
 \end{itemize}

### 2024-02-14 documentation/thesis/thesis_document.tex
.

@@
 the sensors is evaluated to determine its capability to measure with
-precision greater than 1,000 \gls{ppm}. In the end, the sensors should
+precision greater than 1000 \gls{ppm}. In the end, the sensors should
 also measure how uniform the magnetic field is in a completed \gls{mri}
@@
 The Halbach magnet incorporated in this system boasts a 27cm diameter, a
-B0 field strength of 50.4 mT, and an impressive homogeneity of 2400 ppm
-over a 20cm diameter using smaller magnets (\(12 x 12 x 12 mm^3\)). This
-exceptional homogeneity enables the utilization of coil-based gradients
-for spatial encoding, significantly enhancing the flexibility of image
-acquisition.
+B0 field strength of 50.4 mT, and an impressive homogeneity of 2400
+\gls{ppm} over a 20cm diameter using smaller magnets
+(\(12 x 12 x 12 mm^3\)). This exceptional homogeneity enables the
+utilization of coil-based gradients for spatial encoding, significantly
+enhancing the flexibility of image acquisition.
 
@@
 The focus of the ongoing efforts is to enhance the homogeneity of
-magnets within low-field MRI systems below 1.000ppm, primarily driven by
-the goal of establishing a compact low-field \gls{mri} for breast cancer
-detection.
+magnets within low-field MRI systems below 1000\gls{ppm}, primarily
+driven by the goal of establishing a compact low-field \gls{mri} for
+breast cancer detection.
 
@@
 spatial requirements during installation. In addition DeLoRI endeavors
-to achieve heightened accuracy, striving for precision levels below
-1,000 ppm. While O'Reilly, Teeuwisse, and Webb were able to modify the
+to achieve heightened accuracy, striving for precision levels below 1000
+\gls{ppm}. While O'Reilly, Teeuwisse, and Webb were able to modify the
 ring diameter to influence field homogeneity, the unique goal here is to
@@
 The ultimate objective is to assess whether these selected sensors align
-with the stringent criteria of achieving an accuracy level of 1,000 ppm.
-Furthermore, the study seeks to validate whether the measuring range of
-these sensors appropriately corresponds to the required field strength,
-ensuring their suitability for the intended application.
+with the stringent criteria of achieving an accuracy level of 1000
+\gls{ppm}. Furthermore, the study seeks to validate whether the
+measuring range of these sensors appropriately corresponds to the
+required field strength, ensuring their suitability for the intended
+application.
 
@@
   measure the homogeneity of a Halbach ring-based B0 field within the
-  stringent limit of less than 1,000 ppm? The desired outcome is a
-  measurement of less than 50 \(\mu\)T at 1,000 ppm, with a specific
-  focus on determining the sensors' viability for noise measurements.
+  stringent limit of less than 1,000 \gls{ppm}? The desired outcome is a
+  measurement of less than 50 \(\mu\)T at 1000 \gls{ppm}, with a
+  specific focus on determining the sensors' viability for noise
+  measurements.
 \end{itemize}
@@
 
-This work successfully implemented a universal hardware and software
-framework for the automated characterisation of permanent magnets. This
-framework consists of a low-cost hardware interface that supports
-various magnetic field sensors and a library for automating and
-analysing the measurement data.
-
-next step is the sensor evaluation
+In the previous chapter \emph{Usecase Evaluation}
+\ref{usecase-evaluation} it was shown that the implementation of the
+hardware and software framework for various magnetic field sensors was
+successfully implemented.
+
+In addition, the basic application by the user was demonstrated using an
+example. This makes it possible to systematically characterise magnets
+from the software and readout hardware side by means of data
+acquisition, storage and analysis.
+
+After discussing the developed hardware and software components in
+particular, this chapter will answer the question of whether the
+selected sensors meet the requirements:
 
@@
 \item
-  software wurde erfolgreich evaluiert anhand der zuvor definierten
-  usecases.
-\item
-  folgend wird der zweite anwendungsfall evaluiert mit der frage ob die
-  magnete vermessen werden können
-\item
-  TODO
+  Measure a wide range of different permanent magnets with regard to
+  their systematic field strength
+\item
+  Automated measurement of the homogeneity of Hallbach rings with an
+  accuracy of less than 1000 \gls{ppm}
 \end{itemize}
+
+These questions are answered in the following, as a basic readout and
+analysis functionality platform had to be created first and thus an
+automated sensor characterisation can be performed.
+
+\hypertarget{sensors-for-evaluation}{%
+\section{Sensors for Evaluation}\label{sensors-for-evaluation}}
+
+\begin{longtable}[]{@{}lll@{}}
+\caption{Digital magnetic field sensors characterised for evaluation
+\label{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}}\tabularnewline
+\toprule
+& TLV493D-A1B6 & MMC5603NJ\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+& TLV493D-A1B6 & MMC5603NJ\tabularnewline
+\midrule
+\endhead
+Readout-Axis & 3D & 3D\tabularnewline
+Temperature-Sensor & yes & yes\tabularnewline
+Resolution {[}uT{]} & 98 & 0.007\tabularnewline
+Range {[}mT{]} & ±130.0 & ±3\tabularnewline
+Background-Noise {[}uT{]} & 100 & 0.2\tabularnewline
+\bottomrule
+\end{longtable}
+
+\hypertarget{evaluation-sensor-setup}{%
+\section{Evaluation Sensor Setup}\label{evaluation-sensor-setup}}
 
@@
 \end{figure}
-
-\begin{itemize}
-\tightlist
-\item
-  cheap sensors used
-\item
-  used hardware list
-\item
-  tested sensor tlv mmc, da diese zum zeitpunkt des tests zur verfüung
-  standen
-\end{itemize}
-
-\begin{longtable}[]{@{}lllll@{}}
-\caption{Implemented digital magnetic field sensors
-\label{Implemented_digital_magnetic_field_sensors.csv}}\tabularnewline
-\toprule
-& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
-\midrule
-\endhead
-Readout-Axis & 3D & 3D & 3D & 1D\tabularnewline
-Temperature-Sensor & yes & no & yes & no\tabularnewline
-Resolution {[}uT{]} & 98 & 0.2 & 0.007 & 48\tabularnewline
-Range {[}mT{]} & ±130.0 & ±0.8 & ±3 & ±50\tabularnewline
-Interface & \gls{i2c} & \gls{i2c} & \gls{i2c} & \gls{i2c}\tabularnewline
-\bottomrule
-\end{longtable}
-
-\hypertarget{evaluation-sensor-setup}{%
-\section{Evaluation Sensor Setup}\label{evaluation-sensor-setup}}
 
@@
 
-\hypertarget{noise-level-data-analysis}{%
-\subsection{Noise Level Data Analysis}\label{noise-level-data-analysis}}
-
 \begin{itemize}
@@
 
-are they suitable for \textless1000ppm ?
+are they suitable for <1000(+\gls{ppm}) ?
 
@@
 \hypertarget{recommendation-for-action}{%
-\subsection{recommendation for action}\label{recommendation-for-action}}
+\subsection{Recommendation for Action}\label{recommendation-for-action}}
 

### 2024-02-14 documentation/thesis/thesis_document.tex
.

@@
 the sensors is evaluated to determine its capability to measure with
-precision greater than 1000 \gls{ppm}. In the end, the sensors should
+precision greater than 1000\gls{ppm}. In the end, the sensors should
 also measure how uniform the magnetic field is in a completed \gls{mri}
@@
 introduced a groundbreaking ``three-dimensional \gls{mri} in a
-homogeneous 27 cm diameter Bore Halbach Array magnet''
+homogeneous 27cm diameter Bore Halbach Array magnet''
 \cite{OReilly2019-rn} in 2019. This innovative setup was
@@
 The Halbach magnet incorporated in this system boasts a 27cm diameter, a
-B0 field strength of 50.4 mT, and an impressive homogeneity of 2400
-\gls{ppm} over a 20cm diameter using smaller magnets
+B0 field strength of 50.4 mT, and an impressive homogeneity of
+2400\gls{ppm} over a 20cm diameter using smaller magnets
 (\(12 x 12 x 12 mm^3\)). This exceptional homogeneity enables the
@@
 
-Within the framework of the ``DeLoRI'' (Dedicated Low-field \gls{mri}
+Within the framework of the \emph{DeLoRI} (Dedicated Low-field \gls{mri}
 for breast) project, Fraunhofer MEVIS in Bremen is actively engaged in
@@
 low-field \gls{mri}. Diverging from the approach implemented by
-O'Reilly, Teeuwisse, and Webb, DeLoRI aims to design an open \gls{mri},
-departing from the circular \gls{mri} configuration discussed in the
-publication. This innovation is geared towards streamlining breast
-examinations, offering enhanced accessibility, and minimizing the
-spatial requirements during installation. In addition DeLoRI endeavors
-to achieve heightened accuracy, striving for precision levels below 1000
-\gls{ppm}. While O'Reilly, Teeuwisse, and Webb were able to modify the
-ring diameter to influence field homogeneity, the unique goal here is to
-characterize the magnets pre-installation, allowing for proactive
-assessments of homogeneity characteristics. This nuanced approach aims
-to provide insights into magnetic field uniformity before the magnets
-are integrated, thereby streamlining the optimization process.
-Furthermore,
+O'Reilly, Teeuwisse, and Webb, \emph{DeLoRI} aims to design an open
+\gls{mri}, departing from the circular \gls{mri} configuration discussed
+in the publication. This innovation is geared towards streamlining
+breast examinations, offering enhanced accessibility, and minimizing the
+spatial requirements during installation. In addition \emph{DeLoRI}
+endeavors to achieve heightened accuracy, striving for precision levels
+below 1000\gls{ppm}. While O'Reilly, Teeuwisse, and Webb were able to
+modify the ring diameter to influence field homogeneity, the unique goal
+here is to characterize the magnets pre-installation, allowing for
+proactive assessments of homogeneity characteristics. This nuanced
+approach aims to provide insights into magnetic field uniformity before
+the magnets are integrated, thereby streamlining the optimization
+process. Furthermore,
 
@@
 The ultimate objective is to assess whether these selected sensors align
-with the stringent criteria of achieving an accuracy level of 1000
-\gls{ppm}. Furthermore, the study seeks to validate whether the
+with the stringent criteria of achieving an accuracy level of
+1000\gls{ppm}. Furthermore, the study seeks to validate whether the
 measuring range of these sensors appropriately corresponds to the
@@
   measure the homogeneity of a Halbach ring-based B0 field within the
-  stringent limit of less than 1,000 \gls{ppm}? The desired outcome is a
-  measurement of less than 50 \(\mu\)T at 1000 \gls{ppm}, with a
-  specific focus on determining the sensors' viability for noise
-  measurements.
+  stringent limit of less than 1000\gls{ppm}? The desired outcome is a
+  measurement of less than 50 \(\mu\)T at 1000\gls{ppm}, with a specific
+  focus on determining the sensors' viability for noise measurements.
 \end{itemize}
@@
   Automated measurement of the homogeneity of Hallbach rings with an
-  accuracy of less than 1000 \gls{ppm}
+  accuracy of less than 1000\gls{ppm}
 \end{itemize}
@@
 \section{Sensors for Evaluation}\label{sensors-for-evaluation}}
+
+The developed framework is directly compatible with a variety of
+magnetic field sensors without modifications, including those listed in
+the table \ref{Implemented_digital_magnetic_field_sensors.csv}.
 
@@
 
+For this evaluation, the sensors listed in the table
+\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
+were used for sensor characterisation. This selection was made for the
+following reasons:
+
+The developed framework is directly compatible with a variety of
+magnetic field sensors without modifications, including those listed in
+the table. For this evaluation, the sensors listed in the table were
+used for sensor characterisation. This selection was made for the
+following reasons:
+
+\begin{itemize}
+\tightlist
+\item
+  Availability of ready to use development boards
+\item
+  Specifications correspond to the application areas
+\item
+  Availability for testing
+\end{itemize}
+
+It is possible to carry out the sensor characterisation shown here for
+other compatible sensors using the same procedure. Pre-configured
+measurements \ref{command-line-interface} and analysis pipelines
+\ref{programmable-data-processing-pipeline} are available for this
+purpose.
+
 \hypertarget{evaluation-sensor-setup}{%

### 2024-02-14 documentation/thesis/thesis_document.tex
.

@@
 Within the framework of the \emph{DeLoRI} (Dedicated Low-field \gls{mri}
-for breast) project, Fraunhofer MEVIS in Bremen is actively engaged in
-crafting a compact and mobile low-field \gls{mri} unit tailored
-specifically for screening purposes. As described since 1991 low-field
-\gls{mri}s have evolved into a burgeoning realm of research, showcasing
-substantial promise within the field of medical technology. The endeavor
-by Fraunhofer MEVIS exemplifies the ongoing commitment to harnessing the
-potential of low-field \gls{mri} for enhanced breast screening
-applications.
+for breast) project, \emph{Fraunhofer MEVIS} in Bremen is actively
+engaged in crafting a compact and mobile low-field \gls{mri} unit
+tailored specifically for screening purposes. As described since 1991
+low-field \gls{mri}s have evolved into a burgeoning realm of research,
+showcasing substantial promise within the field of medical technology.
+The endeavor by \emph{Fraunhofer MEVIS} exemplifies the ongoing
+commitment to harnessing the potential of low-field \gls{mri} for
+enhanced breast screening applications.
 
@@
 \ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
-were used for sensor characterisation. This selection was made for the
-following reasons:
+were used for sensor characterisation. The additional column for the
+\emph{Background-Noise} was taken from the respective data sheets of the
+sesors and will be verified in the later \emph{Background-Noise}
+measurement \ref{sensor-characterisation-background-noise}.
+
+This selection was made for the following reasons:
 
@@
 \ref{programmable-data-processing-pipeline} are available for this
-purpose.
+purpose are packaged with library.
 
@@
 
-\emph{MRPCli} \ref{command-line-interface} was used to control and
-record the measurement series, with the functions of the
-\emph{MRPDataVisualisation} \ref{mrpvisualisation} and
+For the software setup, \emph{MRPCli} \ref{command-line-interface} was
+used to control and record the measurement series, with the functions of
+the \emph{MRPDataVisualisation} \ref{mrpvisualisation} and
 \emph{MRPAnalysis} \ref{mrpanalysis} packages from the library
@@
 \item
-  Plot of the sensor's internal temperature sensor
-\item
-  Background noise level with reference to the baseline
+  Plot of the sensors internal temperature sensor
+\item
+  Background noise level with reference to the initial baseline
 \item
@@
 
-\%\%Sensor\_noise\_evaluation\_results.csv\%\%
+\begin{longtable}[]{@{}lll@{}}
+\caption{Sensor noise evaluation results
+\label{Sensor_noise_evaluation_results.csv}}\tabularnewline
+\toprule
+Symbol & Unit & TLV493D\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+Symbol & Unit & TLV493D\tabularnewline
+\midrule
+\endhead
+\(\mu_{rv}\) & \(\mu\)T &\tabularnewline
+\(\mu_{t}\) & \(\mu\)T &\tabularnewline
+\(\mu_{nl}\) & \% &\tabularnewline
+\(\sigma_{nl}\) & \% &\tabularnewline
+\bottomrule
+\end{longtable}
 
@@
 
+In the raw data plot, as well as its mean value \(\mu_{rv}\) of both
+sensors, an offset can also be recognised, which is dependent on the
+ambient conditions. For verification, a reference measurement of the
+environment was carried out with the calibrated \emph{Voltcraft GM70}
+Telsameter. This provides a \emph{real} baseline value of
+\(\mu_{rev}\)=-21\(\mu\)T.
+
 \begin{itemize}

### 2024-02-15 documentation/thesis/thesis_document.tex
.

@@
 interference. The temperature chamber for all noise tests is set to
-\emph{20°C}.
+\(\mu_{trev}\)=21.0\(^{\circ}\) and the sensors are placed 24 hours
+before the measurement run in the final measurement configuration inside
+of the chamber.
 
@@
 
-\begin{longtable}[]{@{}lll@{}}
-\caption{Sensor noise evaluation results
-\label{Sensor_noise_evaluation_results.csv}}\tabularnewline
-\toprule
-Symbol & Unit & TLV493D\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-Symbol & Unit & TLV493D\tabularnewline
-\midrule
-\endhead
-\(\mu_{rv}\) & \(\mu\)T &\tabularnewline
-\(\mu_{t}\) & \(\mu\)T &\tabularnewline
-\(\mu_{nl}\) & \% &\tabularnewline
-\(\sigma_{nl}\) & \% &\tabularnewline
-\bottomrule
-\end{longtable}
+The table \ref{Sensor_noise_evaluation_results.csv} lists the measured
+values that were extracted from the measurement data of the sensors
+\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}.
+These measured values are categorised below.
+
+: Sensor noise evaluation results
+\label{Sensor_noise_evaluation_results.csv}
+
+~\textbar{}\\
+\hspace*{0.333em}\textbar{}\\
+\hspace*{0.333em}\textbar{}\\
+\hspace*{0.333em}\textbar{}\\
+\hspace*{0.333em}\textbar{}\\
+\hspace*{0.333em}\textbar{}\\
+\hspace*{0.333em}\textbar{}\\
+\hspace*{0.333em}\textbar{}\\
+\hspace*{0.333em}\textbar{}\\
+\hspace*{0.333em}\textbar{}\\
+\hspace*{0.333em}\textbar{}
 
@@
 
-Compared to the \emph{MMC5603NJ}, the temperature plot of the
-\emph{TLV493D} shows that the internal temperature sensor is very noisy
-(maximum of \(\sigma^2_{t}\)=\emph{2\(^{\circ}\)C})and deviates from the
-ambient temperature at almost \emph{10\(^{\circ}\)C}. With a further
-measurement run with a different temperature setting of
-\emph{30\(^{\circ}\)C}, the offset is reduced to only
-\emph{4\(^{\circ}\)C} to the set temperature. However, the noise remains
-constant. When using an alternative sensor, this behaviour is reflected
-and therefore the internal temperature sensor of the \emph{TLV493D}
-should not be used for subsequent temperature compensation.
+The temperature stability of the \emph{TLV493D} with a mean value of
+20.68\(^{\circ}\)C and a standard deviation of
+\(\sigma_{t}\)=0.53\(^{\circ}\)C indicates a consistent trend. This
+implies a constant tendency. The close grouping of the measured values
+around the mean value indicates good stability. The confidence interval
+is expected to be between 20.15\(^{\circ}\)C and 21.21\(^{\circ}\)C,
+which indicates a stable and consistent temperature measurement. This
+result is more noisy compared to the temperature stability of the
+\emph{MMC5603}.
+
+Both sensors provide an offset to the measured chamber temperature
+\(\mu_{trev}\).
+
+With an additional measurement run with a different temperature setting
+of 30.0\(^{\circ}\)C, the measured temperature deviations and offsets
+remains constant.
+
+Thus, the sensor internal temperature sensors of both tested sensors are
+suitable to perform an ambient temperature compensation of measured
+values and calibration of the sensor. This is considered in section
+\emph{Temperature Sensitivity} \ref{temperature-sensitivity}.
 
@@
 environment was carried out with the calibrated \emph{Voltcraft GM70}
-Telsameter. This provides a \emph{real} baseline value of
-\(\mu_{rev}\)=-21\(\mu\)T.
-
-\begin{itemize}
-\tightlist
-\item
-  Plot of the raw measurement data, as well as its mean value
-  \(\mu_{rv}\)\(\mu\)T using Baselin
-\item
-  Plot of the temperature curve over the complete measurement series,
-  which was recorded with the sensor's internal temperature sensor
-\item
-  Noise level as a percentage deviation from the baseline
-\item
-  Histogram of the noise level with marked standard deviation
-\end{itemize}
-
-TODO TABELLE EINORDNUNG MITTELUNGEN ALS TABELLE
+Telsameter next to the sensor \gls{ic} This provides a \emph{real}
+baseline value of \(\mu_{rev}\)=-21\(\mu\)T.
 

### 2024-02-15 documentation/thesis/thesis_document.tex
.

@@
 the setup is to configure communication with the host or connected
-\gls{pc}. All implemented microcontroller platforms used (Raspberry Pi
-Pico, STM32F4) have a \gls{usb} slave port.
+\gls{pc}. All implemented microcontroller platforms used
+(\emph{Raspberry Pi Pico}, \emph{STM32F4}) have a \gls{usb} slave port.
 
 The used usb descriptor is a \gls{usb} \gls{cdc}. This is used to
-emulate a virtual RS232 communication port using a \gls{usb} port on a
-\gls{pc} and usually no additional driver is needed on modern host
+emulate a virtual \emph{RS232} communication port using a \gls{usb} port
+on a \gls{pc} and usually no additional driver is needed on modern host
 systems.
@@
 
+The sensor linearity of a magnetic field sensor describes the ability of
+the sensor to provide a proportional linear response to changes in the
+magnetic field without non-linear distortions. This means that the
+output signals of the sensor vary directly proportional to the input
+magnetic fields without deviations or distortions and is therefore an
+important indicator for measurements of fields at different distances or
+objects.
+
 \begin{figure}
@@
 
+This is achieved here by means of an additional linear axis installed
+above the sensor setup. A holder for an \emph{N45 12x12x12mm} magnet was
+attached to the end effector of this axis, which can thus be moved at
+different distances above the respective sensor \gls{ic}. The ambient
+temperature is set to \(\mu_{trev}\)=21.0\(^{\circ}\) in the measurement
+runs and thus corresponds to the same conditions as in the
+\emph{Background-Noise}\ref{sensor-characterisation-background-noise}
+setup.
+
+The figure \ref{Sensor_evaluation_setup_for_linearity_measurements.png}
+shows this updated measurement setup with the added components. To
+control the linear axis, an additional motion controller of the type
+\emph{SKR-Pico} placed outside the temperature chamber is required,
+which can be controlled via a network interface. A bash console script
+controls the measurement process.
+
+\hypertarget{measurement-setup}{%
+\subsection{Measurement Setup}\label{measurement-setup}}
+
+After the sensor baseline has been determined with \emph{N=10000}
+samples, the magnet is inserted into the holder. The linear axis is
+moved by the user until it is maximally saturated. With the
+\emph{TLV493D}, this corresponds to \(\mu_{rev}\)=250.000\(\mu\)T and
+below in low resolution mode. \emph{MCC5603NJ} around
+\(\mu_{rev}\)=3000\(\mu\)T. This ensures that the linearity is
+determined over the entire measuring range.
+
+\hypertarget{measurement-run}{%
+\subsection{Measurement Run}\label{measurement-run}}
+
+\hypertarget{linearity-analysis}{%
+\subsection{Linearity Analysis}\label{linearity-analysis}}
+
 \begin{figure}
@@
 \end{figure}
+
+\ref{Sensor_linearity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
 

### 2024-02-15 documentation/thesis/thesis_document.tex
.

@@
 domain, delineates the scope and boundaries of the present research,
-surveys the current state of the art in low-field MRI research and
+surveys the current state of the art in low-field \gls{mri}research and
 applications, articulates the research question driving this thesis and
@@
 \gls{nmr} to generate cross-sectional black-and-white images of the
-body. This indispensable method plays a crucial role in contemporary
+body. This indispensable method plays a central role in contemporary
 medicine and research, contributing significantly to saving lives.
-Despite its widespread use, traditional MRI systems often rely on large,
-heavy, and expensive magnets to achieve the necessary homogeneity of the
-magnetic field for accurate imaging. \cite{Nitz2016}
-
-Various types of magnets find application in different \gls{mri}
-systems. Permanent magnets generate a steady yet relatively weak
-magnetic field, electro magnets are energized by electrical currents,
-and superconducting electro magnets produce magnetic fields through
-electric induction. Regardless of the type, the primary objective is to
-create a homogeneous magnetic field within the \gls{mri}. The higher the
+Despite its widespread use, traditional \gls{mri} systems often rely on
+large, heavy, and expensive magnets to achieve the necessary homogeneity
+of the magnetic field for accurate imaging. \cite{Nitz2016}
+
+Various types of magnets are applicated in different \gls{mri} systems.
+Permanent magnets generate a steady yet relatively weak magnetic field,
+electro magnets are energized by electrical currents, and
+superconducting electro magnets produce magnetic fields through electric
+induction. Regardless of the type, the primary objective is to create a
+homogeneous magnetic field within the \gls{mri}. The higher the
 homogeneity, the more accurate the measurements. This uniform magnetic
@@
 substantial size, weight, and cost. Even when targeting smaller areas of
-the body, large devices are often necessary. In response to this, there
-is a growing interest in developing low-field \gls{mri} systems that
-utilize various magnet types, including permanent magnets. These
+the body, large devices are often necessary.
+
+In response to this, there is a growing interest in developing low-field
+\gls{mri} systems that utilize in many cases permanent magnets. These
 systems, while offering advantages in energy efficiency and reduced
@@
 in the magnetic field is crucial for accurate imaging or comparative
-analyses. While incapable of producing images due to lower magnetic
-field strength, low-field systems facilitate the comparison of different
-field behaviors and the identification of anomalies. O'Reilly and
-Teeuwisse and de Gans \cite{OReilly2019-rn} have already
-demonstrated low-cost and small-scale implementations with low-field
-\gls{mri} in 2021.
+analyses. While tipically calculated images have lower resolution due to
+lower magnetic field strength, low-field systems facilitate the
+comparison of different field behaviors and the identification of all
+kinds of irritations. O'Reilly and Teeuwisse and de Gans
+\cite{OReilly2019-rn} have already demonstrated low-cost and
+small-scale implementations with low-field \gls{mri} in 2021
+calculationg images of a head sucessfully.
 
 Permanent magnets, usually arranged in a circular ``Halbach array''
-around the \gls{mri}, are commonly employed in low-field systems.
-However, their drawback is the inherent variability in strength,
-complicating the achievement of a homogeneous field and requiring
-precise strength information for correct magnet ordering and \gls{mri}
-construction. Completed MRI systems pose significant challenges for
+inside the \gls{mri}, are commonly used in low-field systems. However,
+their drawback is the inherent variability in strength, complicating the
+achievement of a homogeneous field and requiring precise strength
+information for correct magnet ordering and \gls{mri} construction.
+
+Completed \gls{mri} systems pose significant challenges for
 retrospective adjustments, particularly when individual magnets impact
@@
 homogeneity can be measured post-assembly, the intricate task of
-readjustment becomes formidable. An approach dictates that meticulous
-adjustments to the magnets should be undertaken proactively, prior to
-the finalization of the MRI system.
-
-The focus of this thesis is on advancing low-frequency \gls{mri}
-technology by addressing the sensor-usability of permanent magnets used
-in these systems. The variability in the strength of permanent magnets
-poses a significant obstacle to constructing an \gls{mri} with the
-necessary precision for homogenous field generation.
+readjustment is taken into account. It is less costintensive and less
+complicated to measure the magnets proactively, prior to the
+finalization of the \gls{mri}system.
+
+The focus of this thesis is to improve low-frequency \gls{mri}
+technology by examining the usability of magnetic field sensors for
+characterising permanent magnets used in these systems. The variability
+in the strength of permanent magnets leads to significant difficulties
+in constructing an \gls{mri} with the necessary precision for homogenous
+field generation.
 
@@
 to selectively measure magnetic fields at different locations or fully
-around a permanent magnet using different sensors. The accompanying
-open-source software is designed not only to facilitate measurements
-with different sensors but also to enable the characterization of
-different objects.
-
-The sensor testing process involves two key tests. Firstly, the
-linearity of the magnetic fields is measured with all sensors to assess
-the feasibility of using specific sensors. Secondly, the homogeneity of
-the sensors is evaluated to determine its capability to measure with
-precision greater than 1000\gls{ppm}. In the end, the sensors should
-also measure how uniform the magnetic field is in a completed \gls{mri}
-system.
-
-This research initiative seeks to contribute to the improvement of
-low-frequency \gls{mri} systems by enhancing the accuracy of permanent
-magnet characterization. The outcomes of this thesis will provide
-insights into the selection and evaluation of sensors for future
-low-field \gls{mri} research, ultimately contributing to advancements in
-medical imaging technologies.
+around a permanent magnet using different sensors. Several existing
+open-source software solutions implement individual parts, but do not
+provide a complete data processing pipeline from acquisition to
+analysis, and their data storage formats are not compatible with each
+other.
+
+The accompanying open-source software for this thesis is designed not
+only to facilitate measurements with different sensors but also to
+enable the characterisation of different objects.
+
+The sensor testing process involves three key test procedures for two
+digital sensors. Firstly, the background noise for both sensors is
+quantified by measuring with the sensors in a constant environment
+without any magnets. Secondly, the linearity of the magnetic fields is
+measured for all sensors to detect deviations from the estimated ideal
+magnetic curve.
+
+At last, the temperature drift is measured by repeating the background
+noise test in different temperature environments. Sensor noise should be
+less than \emph{50\(\mu\)T} to characterise precisely a magnetic field
+in a Halbach-Array of an \gls{mri}with precision greater than
+\emph{1000\gls{ppm}}.
+
+This research initiative contributes to the improvement of low-frequency
+\gls{mri} systems by enhancing the accuracy of permanent magnet
+characterisation. The outcomes of this thesis provides insights into the
+selection and evaluation of sensors for future low-field \gls{mri}
+research, ultimately contributing to advancements in medical imaging
+technologies.
 
@@
 
-In the realm of modern medical imaging, high-field superconducting
-magnets dominate most \gls{mri} machines, providing high blac-withe
-image resolution. However, the substantial costs, space prerequisites,
-and safety considerations associated with these systems pose
-considerable challenges.
-
-Magnetic resonance imaging \gls{mri} relies on the presence of a robust
-magnetic field, and over time, there has been a continual push to
-enhance the strength of these magnetic fields. This strength is
-quantified in units of Tesla {[}T{]}, commonly referred to as the B0
-field in medical contexts, while physicists use the term magnetic field
-induction. The \gls{snr} is proprtional to the magnetic B0 field;
-growing magnetic field leads automatically to higher \gls{snr}.
-
-Notably, the focus on high-field systems predominated discussions until
+For modern medical imaging high-field superconducting magnets dominate
+most \gls{mri} machines, providing high blac-withe image resolution.
+However, the substantial costs, space requierments and safety
+considerations cause considerable challenges.
+
+\gls{mri} relies on the presence of a robust magnetic field, and over
+time, there has been a continual push to enhance the strength of these
+magnetic fields. This strength is quantified in units of Tesla {[}T{]},
+commonly referred to as the \emph{B0} field in medical contexts, while
+physicists use the term magnetic field induction. The \gls{snr} is
+proprtional to the magnetic \emph{B0} field; growing magnetic field
+leads automatically to higher \gls{snr}. The inital \emph{B0} field of
+an \gls{mri} aims to be homogenouse, for image aquisition the second
+step requires imhomoginity of the \emph{B0} field to stimulate spin in
+the atoms of materials. For high resultion images, the initial \emph{B0}
+field aims to be a homogenouse as possible.
+
+Notably, the focus on high-field systems dominated discussions until
 around 1991 when the possibility of constructing \gls{mri} machines with
-lower magnetic field strengths began to emerge. This marked a pivotal
-shift in exploring the potential advantages and applications of
-low-field \gls{mri} systems. \cite{Nitz2016}
+lower magnetic field strengths came up. This marked a shift in exploring
+the potential advantages and applications of low-field \gls{mri}
+systems. \cite{Nitz2016}
 
@@
 compared to conventional high-field \gls{mri} scanners. Typically, the
-magnetic field in low-field MRI systems measured between
-\passthrough{\lstinline!0.1T!} and \passthrough{\lstinline!0.3T!}
-compared to the usual \passthrough{\lstinline!1.5T!} to
-\passthrough{\lstinline!3T!} and above in high-field \gls{mri} scanners
+magnetic field in low-field \gls{mri}-systems measured between
+\emph{0.1T} and \emph{0.3T} compared to the usual \emph{1.5T} to
+\emph{3T} and above in high-field \gls{mri} scanners
 \cite{Hori2021-pt}.
@@
 This technology is used in medical imaging as well as in preclinical
-research. The main advantage of low-field \gls{mri} is the improved
-imaging of soft tissues, especially when examining joints and muscles.
+research. The main advantage of low-field \gls{mri}s is the improved
+imaging of soft material, especially when examining joints and muscles.
 It also offers more cost-effective alternatives to high-field \gls{mri}
@@
 magnets. Through the connection of these permanent magnets, a consistent
-magnetic field of up to 0.35 Tesla can be generated. However, this
-achievement comes at the cost of an average system weight of 14 tons.
+magnetic field of up to \emph{0.35T} can be generated. However, this
+achievement comes at the cost of an average system weight of \emph{14t}.
 Despite their cost-effectiveness in production and maintenance,
-permanent magnets exhibit drawbacks such as high temperature dependence
-and a limited \gls{snr} due to the constrained field strength.
+permanent magnets show drawbacks such as high temperature dependence and
+a limited \gls{snr} due to the constrained field strength.
 \cite{Nitz2016}
@@
 magnets and their structure is particularly important in such systems
-and need to be analysed.
+and needs to be analysed.
 
@@
 
-The positioning of permanent magnets holds a pivotal role in
-constructing an MRI and influencing the homogeneity of the B0 magnetic
-field. Halbach ring magnets \cite{Halbach1980DesignOP} have become a
-common design for low field \gls{mri} and \gls{nmr} systems
-\cite{cmr.a.20165}.
+The positioning of permanent magnets holds an important role in
+constructing an \gls{mri} and is influencing the homogeneity of the
+\emph{B0} magnetic field. Halbach ring magnets
+\cite{Halbach1980DesignOP} have become a common design for low field
+\gls{mri} and \gls{nmr} systems \cite{cmr.a.20165}.
 
@@
 example \gls{cad} model of such a ring, in which in this case eight
-cubic \passthrough{\lstinline!12x12x12mm!} magnets are embedded to
-generate homogeneous magnetic flux densities of around
-\passthrough{\lstinline!20mT!}.
+cubic \emph{12x12x12mm} magnets are embedded to generate homogeneous
+magnetic flux densities of around \emph{20mT}.
 
 The homogeneity in this configuration depends, among other things, on
-the following aspects:
+the following main aspects:
 
@@
 
-Halbach magnetic arrays present a compelling choice for mobile NMR due
-to their ability to produce highly homogeneous and robust magnetic
-fields per unit of magnetic mass, coupled with minimal stray fields. The
-term ``Halbach Array'' (commonly known as ``magic rings'') denotes a
-precise configuration of permanent magnets designed to amplify magnetic
-flux on one side while concurrently mitigating or eliminating it on the
-opposite side. \cite{inbook}
-
-The Halbach magnetic array emerges as a crucial element for future
-Magnet Characterization. Given that this thesis centers on assessing the
-sensors' applicability, the Halbach magnetic array serves as a tool for
-measurements, although its implementation and further discussion will
-not be the primary focus.
+Halbach magnetic arrays present a choice for mobile \gls{nmr} due to
+their ability to produce highly homogeneous and robust magnetic fields
+per unit of magnetic mass, coupled with minimal stray fields. The term
+``Halbach Array'' (commonly known as ``magic rings'') denotes a precise
+configuration of permanent magnets designed to amplify magnetic flux on
+one side while concurrently mitigating or eliminating it on the opposite
+side. \cite{inbook}
+
+The Halbach magnetic array appears as a essential element for future
+Magnet characterisation. Based on this fact this thesis centers on
+assessing the sensors' applicability, the Halbach magnetic array serves
+as a tool for later measurements, although its implementation and
+further discussion will not be the primary focus.
 
@@
 
-The shimming process is a crucial step in magnetic resonance imaging
+The shimming process is a essential step in magnetic resonance imaging
 \gls{mri} to ensure homogeneous magnetic fields for precise imaging.
@@
 be caused by external influences or internal system errors. This process
-optimizes field homogeneity, which is crucial for high-resolution and
+optimizes field homogeneity, which is essential for high-resolution and
 artifact-free images \cite{10.3389/fphy.2021.704566}.
@@
 Optimal homogeneity is attained through intricate designs facilitating
-active shimming, a technique crucial for achieving high-resolution
+active shimming, a technique essential for achieving high-resolution
 spectroscopy. Beyond this, simpler combinations and adaptations of
@@
 
-In this work, reference is made exclusively to the hardware shim
-process. Since this project is to be used in the future to construct a
+In this thesis, reference is made exclusively to the hardware shimming
+processes, since this project is to be used in the future to construct a
 low-field \gls{mri} field magnet from permanent magnets.
@@
 
-According to Wolfgang R. Nitz in 2016, just 13.4\% of actively used v
-systems are low-field \gls{mri} (66.6\% 1.5T systems, 20\% 3.0 T system,
-14.4\% low field with \textless0.5T). {[}Nitz2016{]} Nitz also
-highlights that presently, the landscape of \gls{mri} technology is
-dominated by a single manufacturer dealing with resistive magnets,
-namely Stand-up \gls{mri} from FONAR Corp.~In contrast, the industry
-giants such as Siemens, General Electric, Philips, Toshiba, among
-others, predominantly rely on either permanent magnets or
-superconducting magnets in their \gls{mri} systems. This notable
-concentration underscores the distinctive position of Stand-up \gls{mri}
-as a trailblazer in utilizing resistive magnets within the competitive
-realm of magnetic resonance imaging. {[}Nitz2016{]}
+According to Wolfgang R. Nitz in 2016, just \emph{13.4\%} of actively
+used \gls{mri} systems are low-field \gls{mri} (\emph{66.6\% 1.5T
+systems, 20\% 3.0 T system, 14.4\% low field with \textless0.5T}).
+\cite{Nitz2016}
 
@@
 introduced a groundbreaking ``three-dimensional \gls{mri} in a
-homogeneous 27cm diameter Bore Halbach Array magnet''
-\cite{OReilly2019-rn} in 2019. This innovative setup was
-subsequently employed in 2020 to acquire in vivo MR images, showcasing
-the practical applications of their pioneering research
-\cite{OReilly2021-ep}. 2023 veröffentlichten de Vos, Remis und Webb
-eine zusammenfassung zur gestaltng eines oint-of-care halbach array
-low-field \gls{mri} system \cite{De_Vos2023-pb}.
-
-The objective of this \gls{mri} system is to prioritize
-cost-effectiveness while efficiently capturing low-frequency images of
-the head. The emphasis lies on swift and accurate imaging, achieved
-through a streamlined approach that favors simplicity in the resultant
-images. This \gls{mri} system is strategically designed with a primary
-focus on cost-effectiveness, aiming to efficiently capture low-frequency
-images of the head. The overarching goal is to achieve rapid and
-accurate imaging through a simplified approach, prioritizing clarity and
-ease in the resulting images.
+homogeneous \emph{27cm} diameter Bore Halbach Array magnet''
+\cite{OReilly2019-rn} in 2019.This innovative setup was subsequently
+employed in 2020 to acquire in vivo MR images, showcasing the practical
+applications of their pioneering research \cite{OReilly2021-ep}.
+2023 veröffentlichten de Vos, Remis und Webb eine zusammenfassung zur
+gestaltng eines oint-of-care halbach array low-field \gls{mri} system
+\cite{De_Vos2023-pb}.
+
+Within the research domain, various implementations came up. An exemplar
+instance is the work by O'Reilly, Teeuwisse, and Webb, who introduced a
+groundbreaking ``three-dimensional \gls{mri} in a homogeneous 27cm
+diameter Bore Halbach Array magnet'' \cite{OReilly2019-rn} in 2019.
+This innovative setup was subsequently employed in 2020 to acquire in
+vivo MR images, showcasing the practical applications of their
+pioneering research \cite{OReilly2021-ep}. In 2023, de Vos, Remis
+and Webb published a summary of the design of an oint-of-care halbach
+array low-field \gls{mri} system \cite{De_Vos2023-pb}.
 
 The Halbach magnet incorporated in this system boasts a 27cm diameter, a
-B0 field strength of 50.4 mT, and an impressive homogeneity of
+\emph{B0} field strength of 50.4mT, and an impressive homogeneity of
 2400\gls{ppm} over a 20cm diameter using smaller magnets
@@
 
-To further refine the magnet's homogeneity, optimization techniques are
-employed by adjusting the radius of the Halbach cylinder along the
-length of the magnet. The deliberate choice of smaller magnets, as
-opposed to other Halbach designs, serves to compensate for inherent
-manufacturing imperfections in each individual magnet. This strategic
-decision not only mitigates structural demands on the magnet housing in
-terms of strength and weight but also augments safety throughout the
-construction process.
+The Halbach magnet incorporated in this system boasts a \emph{27cm}
+diameter, a \emph{B0} field strength of \emph{50.4 mT}, and an
+impressive homogeneity of \emph{2400}\gls{ppm} over a \emph{20cm}
+diameter using smaller magnets (\emph{12 x 12 x 12 mm\^{}3}). This
+exceptional homogeneity enables the utilization of coil-based gradients
+for spatial encoding, significantly enhancing the flexibility of image
+acquisition.
+
+To further refine the magnet's homogeneity, optimisation techniques are
+employed by adjusting the radius of the Halbach ring along the length of
+the magnet. The deliberate choice of smaller magnets, as opposed to
+other Halbach designs, serves to compensate for inherent manufacturing
+imperfections in each individual magnet. This strategic decision not
+only mitigates structural demands on the magnet housing in terms of
+strength and weight but also augments safety throughout the construction
+process.
 
@@
 implementations that use different measurement methods to determine the
-field strength of individual magnets. Individual measuring points are
+field strength of individual magnets and individual measuring points are
 recorded. This data is then evaluated in separate software
@@
 engaged in crafting a compact and mobile low-field \gls{mri} unit
-tailored specifically for screening purposes. As described since 1991
-low-field \gls{mri}s have evolved into a burgeoning realm of research,
-showcasing substantial promise within the field of medical technology.
-The endeavor by \emph{Fraunhofer MEVIS} exemplifies the ongoing
-commitment to harnessing the potential of low-field \gls{mri} for
-enhanced breast screening applications.
-
-The focus of the ongoing efforts is to enhance the homogeneity of
-magnets within low-field MRI systems below 1000\gls{ppm}, primarily
-driven by the goal of establishing a compact low-field \gls{mri} for
-breast cancer detection.
+customised specifically for screening purposes. As described before,
+since 1991 low-field \gls{mri}s have evolved into a growing realm of
+research, showcasing significant opportunities within the field of
+medical technology. The efforts by \emph{Fraunhofer MEVIS} exemplifies
+the ongoing commitment to utilizing the potential of low-field \gls{mri}
+for enhanced breast screening applications.
+
+The focus of the ongoing efforts is to improve the homogeneity of
+magnets within low-field \gls{mri}systems below \emph{1000}\gls{ppm},
+primarily driven by the goal of establishing a compact low-field
+\gls{mri} for breast cancer detection.
 
@@
 scanners, the project encompasses electromagnetic simulation of
-components within the low-field MRI system, coupled with machine
+components within the low-field \gls{mri}system, coupled with machine
 learning-driven control and data acquisition. The resultant software
@@
 breast examinations, offering enhanced accessibility, and minimizing the
-spatial requirements during installation. In addition \emph{DeLoRI}
-endeavors to achieve heightened accuracy, striving for precision levels
-below 1000\gls{ppm}. While O'Reilly, Teeuwisse, and Webb were able to
-modify the ring diameter to influence field homogeneity, the unique goal
-here is to characterize the magnets pre-installation, allowing for
-proactive assessments of homogeneity characteristics. This nuanced
-approach aims to provide insights into magnetic field uniformity before
-the magnets are integrated, thereby streamlining the optimization
-process. Furthermore,
+spatial requirements during installation.
+
+In addition \emph{DeLoRI} efforts to achieve heightened accuracy,
+striving for precision levels below 1000\gls{ppm}. While O'Reilly,
+Teeuwisse, and Webb were able to modify the ring diameter to influence
+field homogeneity, the unique goal here is to characterize the magnets
+pre-installation, allowing for proactive assessments of homogeneity
+characteristics. This approach aims to provide insights into magnetic
+field uniformity before the magnets are integrated, thereby streamlining
+the optimisation process. Furthermore,
 
@@
 the selection and comparison of potential sensors for the
-characterization process.
+characterisation process.
 
@@
 feature of this system is the ease of sensor interchangeability,
-facilitating adaptability and versatility in the characterization
+facilitating adaptability and versatility in the characterisation
 process.
@@
 library will enable data acquisition, storage and analysis of magnetic
-properties, with customization possible at each step of the process.
+properties, with customisation possible at each step of the process.
 Complete documentation, tutorials and tests will enable users to use the
@@
 
-Concerning the DeLoRI project, this study exclusively delves into the
-realm of permanent magnets employed for creating a homogeneous B0 field
-through Halbach rings. Other systems and spin generation for
-measurements are deliberately excluded from consideration but will be
-necessary in later stages of the DeLoRI project.
+Concerning the \emph{DeLoRI} project, this study exclusively delves into
+the realm of permanent magnets employed for creating a homogeneous
+\emph{B0} field through Halbach rings. Other systems and spin generation
+for measurements are deliberately excluded from consideration but will
+be necessary in later stages of the \emph{DeLoRI} project.
+
+Before naming the research focus, it is important to understand the
+difference and connection between deviation and resulution of the
+system. To measure a deviation of better than \emph{1000}\gls{ppm} in a
+\emph{50mT} magnetic field, a resolution that is less than
+\emph{1000}\gls{ppm} of \emph{50mT} is needed.
+
+\[\frac{1000}{1000000} \times 50 \, mT = 0.05 \, mT \]
+
+To convert this into microtesla (\(\mu\)T), a multiplication by
+\emph{1000} is needed:
+
+\[ 0.05 \, mT \times 1000 = 50 \, \mu T \]
+
+This means that to measure a deviation of better than
+\emph{1000}\gls{ppm} in a \(50mT\) magnetic field, a resolution of less
+than \emph{50} \(\mu\)T is needed.
 
@@
 \item
-  Sensor Characterization: Can the carefully selected sensors
+  Sensor characterisation: Can the carefully selected sensors
   effectively measure a magnet? Specifically, this involves
@@
   measure the homogeneity of a Halbach ring-based B0 field within the
-  stringent limit of less than 1000\gls{ppm}? The desired outcome is a
-  measurement of less than 50 \(\mu\)T at 1000\gls{ppm}, with a specific
-  focus on determining the sensors' viability for noise measurements.
+  stringent limit of less than \emph{1000}\gls{ppm}? The desired outcome
+  is a measurement of less than \emph{50} \(\mu\)T at
+  \emph{1000}\gls{ppm}, with a specific focus on determining the
+  sensors' viability for noise measurements.
 \end{itemize}
 
-It is crucial to emphasize that the intention is not to characterize the
-magnets per se; rather, the emphasis lies in deriving meaningful
-insights about the sensors deployed.
-
-This work distinctly prioritizes the development of both hardware and
-software tailored for sensor utilization and final testing. Physical
-properties and considerations take a secondary role in comparison to the
+It is essential to emphasize that the intention is not to characterize
+the magnets; the sensores which might be used for characterisation are
+be analised and evaluated.
+
+This work prioritises the development of both hardware and software
+customised for sensor utilization and final testing. Physical properties
+and considerations take a secondary role in comparison to the
 overarching goal of refining the sensor-based methodologies.
@@
 
-The following section defines some usecases that the future project
-should be able to cover. These usecases define the setup of the hard-
-and software. These illustrate practical situations to understand the
+The following section defines possible usecases that the future project
+need to cover. These usecases define the setup of the hard- and
+software. These illustrate practical situations to understand the
 functionality and added value of the implemented solution for the user.
@@
 a reference to demonstrate the implemented capabilities of the solution.
-This is crucial for understanding the needs of the target group and
+This is essential for understanding the needs of the target group and
 designing the end result accordingly.
@@
 
-Finally, a comprehensive hardware and software framework must be
-established, capable of measuring diverse objects using various sensors.
-Additionally, conclusive remarks should be provided regarding the
+Finally, a comprehensive hardware and software framework needs to be
+established, which is capable of measuring diverse objects using various
+sensors. Additionally, remarks need to be provided regarding the
 suitability of the employed sensors for magnetic field measurements.
@@
 A defined main objective of this project is the development of a
-cost-effective magnetic field sensors interface that is also universally
-expandable. The focus is on mapping different sensors and being
-compatible with different magnet types and shapes.
-
-This ensures a wide range of applications in different scenarios.
+cost-effective magnetic field sensors interface that is universally
+expandable as well. The focus is on mapping different sensors and being
+compatible with different magnet types and shapes. This ensures a wide
+range of applications in different scenarios.
+
 Another goal is reproducibility to ensure uniform results, which as a
@@
 A key aspect of this selection was the preference for sensors with
-digital interfaces to facilitate implementation in the circuit layout.
-The integration of integrated temperature sensors represents a
-significant enhancement that will later enable precise temperature
-compensation.
+digital interfaces to facilitate implementation in the circuit layout
+since these kind of sensors are easy to integrate compared to
+non-digital sensors, which require specific frameworks. The integration
+of integrated temperature sensors represents a significant enhancement
+that will later enable precise temperature compensation.
 
@@
 
-The mechanical design of a sensor would be kept as simple as possible so
-that it can be replicated as easily as possible. The focus was on
-providing a stable foundation for the sensor \gls{ic} and an
-exchangeable holder for different magnets.
+The mechanical design of a sensor is kept as simple as possible so that
+it can be replicated as easily as possible. The focus is on providing a
+stable foundation for the sensor \gls{ic} and an exchangeable holder for
+different magnets.
 
@@
 
-All parts were produced using the 3D printing additive manufacturing
+All parts are produced using the 3D printing additive manufacturing
 processes. The sensor circuit board was glued underneath the magnet
@@
 
-The focus here was on utilising existing microcontroller development and
+The focus is on utilising existing microcontroller development and
 evaluation boards, which already integrate all the components required
@@
 
-All the necessary components and their circuitry were then recorded on a
+All the necessary components and their circuitry are recorded on a
 \gls{pcb} \ref{1D_sensor_schematic_and_circuit_board.png} and
-subsequently manufactured. In addition, footprints were provided for
+subsequently manufactured. In addition, footprints are provided for
 various sensor \gls{ic} packages. By placing mounting holes on the
@@
 \item
-  Raspberry Pi OS Lite - \gls{os} \emph{debian bookworm x64},
+  \emph{Raspberry Pi OS Lite} - \gls{os} \emph{debian bookworm x64},
 \item
@@
 The electrical level here is based on a \emph{Raspberry-Pi Pico}
-together with the \passthrough{\lstinline!MMC5603NJ!} magnetic sensor.
-The mechanical setup consists of four 3D printed components, which are
-fixed together with nylon screws to minimise possible influences on the
-measurement.
+together with the \emph{MMC5603NJ} magnetic sensor. The mechanical setup
+consists of four 3D printed components, which are fixed together with
+nylon screws to minimise possible influences on the measurement.
 
@@
 \ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
-used, which has a measuring range of 0T to 3T with a resolution of
-0.1mT. It offers an RS232 interface with a documented protocol for
-connection to a \gls{pc}.
+used, which has a measuring range of \emph{0T} to \emph{3T} with a
+resolution of \emph{0.1mT}. It offers an \emph{RS232} interface with a
+documented protocol for connection to a \gls{pc}.
 
@@
 This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
-offer an physical RS232 interface. As with the other sensors, this
-interface consists of your \emph{Raspberry-Pi Pico} with an additional
-level shifter.
+offer an physical \emph{RS232} interface. As with the other sensors,
+this interface consists of your \emph{Raspberry-Pi Pico} with an
+additional level shifter.
 
@@
 interpret the data from the microcontoller, the serial protocol of the
-sensor was implemented in a customized version of the
+sensor was implemented in a customised version of the
 \emph{CustomSensor} class \ref{lst:CustomSensorClass}.
@@
 library and are intended to provide user-friendliness on the one hand
-and the rapid development of own analysis and optimization algorithms on
+and the rapid development of own analysis and optimisation algorithms on
 the other.
@@
 
-The \emph{MRPReading} module performs a crucial role in streamlining the
-centralized management of measurement data. It serves as a storage
+The \emph{MRPReading} module performs a essential role in streamlining
+the centralized management of measurement data. It serves as a storage
 provider for various measurements, offering functionalities that
-facilitate the creation and addition of data records. To customize and
+facilitate the creation and addition of data records. To customise and
 add meta-data, users have the flexibility to configure parameters
 through the dedicated \emph{MRPMeasurementConfig} module into an
-\passthrough{\lstinline!MRPReading!} instance.
+\emph{MRPReading} instance.
 
@@
 To configure parameters, ensuring a tailored approach to the entire
-measurement process, these parameters act as a crucial bridge between
+measurement process, these parameters act as a cessential bridge between
 user preferences and the robust capabilities of the \emph{MRPReading}
@@
 
-The following example code \ref{lst:mrpexample_hallbach}, shows how a
+The following example code \ref{lst:mrpexample_halbach}, shows how a
 simple Halbach magnetic ring can be generated.
@@
 Eight random measurements are generated here. It is important that the
-magnet type (here \emph{N45\_CUBIC\_15x15x15}) is specified. This is
-necessary so that the correct magnet cutouts can be generated when
+magnet type (for example \emph{N45\_CUBIC\_15x15x15}) is specified. This
+is necessary so that the correct magnet cutouts can be generated when
 creating the 3D model.
@@
 
-Usability improvements in software libraries are crucial for efficient
+Usability improvements in software libraries are essential for efficient
 and user-friendly development. Intuitive API documentation, clearly
@@
 own Python scripts even for short measurement and visualisation tasks.
-However, this was already time-consuming for reading out a sensor and
+This is already a time-consuming process for reading out a sensor and
 configuring the measurement parameters and metadata and quickly required
@@
 \item
-  \passthrough{\lstinline!MRPcli --help!} instead of
-  \passthrough{\lstinline!python3 cli.py --help!}
-\item
-  \passthrough{\lstinline!MRPudpp --help!} instead of
-  \passthrough{\lstinline!python3 udpp.py --help!}
-\item
-  \passthrough{\lstinline!MRPproxy --help!} instead of
-  \passthrough{\lstinline!python3 proxy.py --help!}
+  \emph{\$ MRPcli --help} instead of \emph{\$ python3 cli.py --help}
+\item
+  \emph{\$ MRPudpp --help} instead of \emph{\$ python3 udpp.py --help}
+\item
+  \emph{\$ MRPproxy --help} instead of \emph{\$ python3 proxy.py --help}
 \end{itemize}
@@
 \emph{pipeline\_mrp\_evaluation.yaml} file and is ready for execution.
-This is carried out using the \emph{MRPudpp} (cli)
+This is carried out using the \emph{MRPudpp} \gls{cli}
 \ref{lst:bash_pipeline_mrp_evaluation_yaml}. After the run has been
@@
   Automated measurement of the homogeneity of Hallbach rings with an
-  accuracy of less than 1000\gls{ppm}
+  accuracy of less than \emph{1000\gls{ppm}}
 \end{itemize}
@@
 conductive adhesive. This compensates for thermal differences. This is
-crucial for the subsequent temperature deviation tests in order to
+essential for the subsequent temperature deviation tests in order to
 obtain comparable measurement results.
@@
 interference. The temperature chamber for all noise tests is set to
-\(\mu_{trev}\)=21.0\(^{\circ}\) and the sensors are placed 24 hours
-before the measurement run in the final measurement configuration inside
-of the chamber.
+\(\mu_{trev}\)=21.0\(^{\circ}\) and the sensors are placed \emph{24}
+hours before the measurement run in the final measurement configuration
+inside of the chamber.
 
@@
 
-In order to quantify the noise, the standard deviation of the signal is
+In order to quantify the noise, the \gls{sd} of the signal is
 calculated. These parameters provide information about the variation of
@@
 
-: Sensor noise evaluation results
-\label{Sensor_noise_evaluation_results.csv}
-
-~\textbar{}\\
-\hspace*{0.333em}\textbar{}\\
-\hspace*{0.333em}\textbar{}\\
-\hspace*{0.333em}\textbar{}\\
-\hspace*{0.333em}\textbar{}\\
-\hspace*{0.333em}\textbar{}\\
-\hspace*{0.333em}\textbar{}\\
-\hspace*{0.333em}\textbar{}\\
-\hspace*{0.333em}\textbar{}\\
-\hspace*{0.333em}\textbar{}\\
-\hspace*{0.333em}\textbar{}
+\begin{longtable}[]{@{}lllll@{}}
+\caption{Sensor noise evaluation results
+\label{Sensor_noise_evaluation_results.csv}}\tabularnewline
+\toprule
+Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
+\midrule
+\endhead
+\(\mu_{nl}\) & 0.79 & 0.00 & \% & Mean noise level\tabularnewline
+\(\sigma_{nl}\) & 0.76 & 0.00 & \% & \gls{sd} noise level\tabularnewline
+\(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Mean sensor value
+(Baseline)\tabularnewline
+\(\sigma_{rv}\) & 172.00 & 0.20 & \(\mu\)T & \gls{sd} sensor
+value\tabularnewline
+\(\mu_{t}\) & 20.68 & 19.40 & \(^{\circ}\)C & Mean sensor
+temperature\tabularnewline
+\(\sigma_{t}\) & 0.53 & 0.00 & \(^{\circ}\)C & \gls{sd} sensor
+temperature\tabularnewline
+\(\mu_{trev}\) & 21.0 & 21.0 & \(^{\circ}\)C & Ambient
+temperature\tabularnewline
+\bottomrule
+\end{longtable}
 
@@
 The temperature stability of the \emph{TLV493D} with a mean value of
-20.68\(^{\circ}\)C and a standard deviation of
-\(\sigma_{t}\)=0.53\(^{\circ}\)C indicates a consistent trend. This
-implies a constant tendency. The close grouping of the measured values
-around the mean value indicates good stability. The confidence interval
-is expected to be between 20.15\(^{\circ}\)C and 21.21\(^{\circ}\)C,
-which indicates a stable and consistent temperature measurement. This
-result is more noisy compared to the temperature stability of the
-\emph{MMC5603}.
+20.68\(^{\circ}\)C and a \gls{sd} of \(\sigma_{t}\)=0.53\(^{\circ}\)C
+indicates a consistent trend. This implies a constant tendency. The
+close grouping of the measured values around the mean value indicates
+good stability. The confidence interval is expected to be between
+20.15\(^{\circ}\)C and 21.21\(^{\circ}\)C, which indicates a stable and
+consistent temperature measurement. This result is more noisy compared
+to the temperature stability of the \emph{MMC5603}.
 
@@
 
-Thus, the sensor internal temperature sensors of both tested sensors are
+The sensor internal temperature sensors of both tested sensors are
 suitable to perform an ambient temperature compensation of measured
@@
 \emph{Temperature Sensitivity} \ref{temperature-sensitivity}.
+
+It is recommended, however, to use a separate temperature sensor when
+using the \emph{TLV493D} or to use a suitable averaging of the
+temperature and measured values in order to perform temperature
+compensation.
 
@@
 
-\hypertarget{temperature-sensitivity}{%
-\section{Temperature Sensitivity}\label{temperature-sensitivity}}
+\hypertarget{sensor-characterisation-linearity}{%
+\section{Sensor Characterisation:
+Linearity}\label{sensor-characterisation-linearity}}
 
@@
 \centering
-\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}
-\caption{Sensor evaluation setup for temperature sensitivity
-measurements
-\label{Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}}
+\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_linearity_measurements.png}
+\caption{Sensor evaluation setup for linearity measurements
+\label{Sensor_evaluation_setup_for_linearity_measurements.png}}
 \end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
-\caption{Sensor temperature sensitivity evaluation results for TLV493D
-and MMC5603NJ
-\label{Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}}
-\end{figure}
-
-using same setup as in read noise but with programmed temperature
-controller of the chamber and separate temperature probe under the
-sensors pcb
-
-\hypertarget{linearity}{%
-\section{Linearity}\label{linearity}}
 
@@
 objects.
-
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_linearity_measurements.png}
-\caption{Sensor evaluation setup for linearity measurements
-\label{Sensor_evaluation_setup_for_linearity_measurements.png}}
-\end{figure}
 
@@
 \emph{SKR-Pico} placed outside the temperature chamber is required,
-which can be controlled via a network interface. A bash console script
-controls the measurement process.
+which can be controlled via a network interface.
 
@@
 moved by the user until it is maximally saturated. With the
-\emph{TLV493D}, this corresponds to \(\mu_{rev}\)=250.000\(\mu\)T and
-below in low resolution mode. \emph{MCC5603NJ} around
-\(\mu_{rev}\)=3000\(\mu\)T. This ensures that the linearity is
-determined over the entire measuring range.
+\emph{TLV493D}, this corresponds to 250.000\(\mu\)T and below in low
+resolution mode. \emph{MCC5603NJ} around 3000\(\mu\)T. This ensures that
+the linearity is determined over the entire measuring range.
 
@@
 
+The measurement run is then started using a script. The user defines the
+path to be travelled by the linear axis. The complete range of
+\emph{120mm} in \emph{1mm} steps was selected here. The following
+automated process then runs as follows:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Move the linear axis upwards by the selected distance
+\item
+  De-energise the axis motor
+\item
+  Create measurement using \emph{MRPCli} with N=2000 data points per
+  reading
+\item
+  Export reading to filesystem with current linear axis position in
+  meta-data and filename
+\end{enumerate}
+
 \hypertarget{linearity-analysis}{%
 \subsection{Linearity Analysis}\label{linearity-analysis}}
+
+After the measurements were exported, they were analysed for linearity
+using \emph{MRPAnalysis} \ref{mrpanalysis} functions.
 
@@
 
+The figure
 \ref{Sensor_linearity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
-
-\begin{itemize}
-\tightlist
-\item
-  minimal distance between sensor and magnet due to messbreich
-\end{itemize}
+shows the visual representation of linearity as a plot. The distance
+from the magnet to the sensor is plotted in \emph{mm} on the x-axis. The
+measured value of the sensor is plotted on the y-axis. This is not
+directly comparable for both plots, as the sensors have different
+measuring ranges. To ensure comparability, the ideal curve was
+determined. In order to be able to make quantifiable statements about
+the measurement results, the mean and \gls{sd} deviation of these two
+curves was determined.
+
+For both sensors, the deviation is less than 1\% over the entire
+resolution. With the \emph{MMC5603NJ} this is on average only
+\emph{0.04\%}. With the \emph{TLV493D}, however, the \gls{sd} is
+\emph{3.64\%}, for which the deviations at the end in particular (with
+field strengths towards zero) are decisive. The previously performed
+\emph{Background-Noise} \ref{sensor-characterisation-background-noise}
+characterisation shows that the linearity deviation here is due to the
+sensitivity of the sensor.
+
+In general, the measured values correspond to the data sheet
+specifications of both sensors, which specify a value of \emph{5\%}. It
+is also possible to calculate these small deviations using curve fitting
+methods. Suitable functions are implemented in the library.
+
+\hypertarget{sensor-characterisation-temperature-sensitivity}{%
+\section{Sensor Characterisation: Temperature
+Sensitivity}\label{sensor-characterisation-temperature-sensitivity}}
+
+The temperature sensitivity of magnetic field sensors describes how
+sensitively the sensors output is sensitive to temperature changes. It
+is important to ensure that temperature fluctuations do not affect
+measurement accuracy. A low temperature sensitivity reduces errors due
+to temperature changes. An accurate temperature sensitivity
+characteristic is therefore crucial for subsequent precise magnetic
+field measurements.
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}
+\caption{Sensor evaluation setup for temperature sensitivity
+measurements
+\label{Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}}
+\end{figure}
+
+As the temperature sensor \emph{TLV493D} in particular produced very
+different results in the previous measurements, an additional
+temperature sensor was attached to the sensor circuit board for this
+measurement. The figure
+\ref{Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}
+shows these modifications in detail. These changes makes it possible to
+accurately determine the sensors \gls{ic} temperature. The temperature
+measuring device \emph{VC-7055BT} can be analysed using a \gls{pc}
+interface. The controller of the temperature chamber can also be
+programmed via a \gls{pc} interface and a target temperature can be
+specified.
+
+With this setup, it is possible to automatically acquire measured values
+from the sensors under controlled temperature conditions.
+
+The same procedure is used as for the \emph{Linearity}
+\ref{sensor-characterisation-linearity} measurement, except that instead
+of moving the linear axis, the temperature of the temperature chamber is
+systematically increased from 20\(^{\circ}\) to 50\(^{\circ}\). Between
+each of these temperature changes, the system is given a waiting time of
+30 minutes after reaching the target temperature.
+
+The field of permanent magnets is very temperature-dependent and can
+lose its magnetisation at higher temperatures (typically
+\textgreater=80\(^{\circ}\) for non-high-quality type N magnets
+\cite{magna-c}). The temperature range was selected so that it is
+within a sufficient range for the application.
+
+\hypertarget{temperature-sensitivity-analysis}{%
+\subsection{Temperature Sensitivity
+Analysis}\label{temperature-sensitivity-analysis}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
+\caption{Sensor temperature sensitivity evaluation results for TLV493D
+and MMC5603NJ
+\label{Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}}
+\end{figure}
+
+The figure
+\ref{Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
+shows the measured data as a plot with the temperature measured by the
+measuring devices on the X-axis and the sensor measured value on the
+Y-axis. The ideal baseline is also shown as a red line. It can be seen
+that the \emph{MMC5603NJ} shows a straight-line drop in the measured
+field strength with increasing temperatures. However, this is very
+constant with a value of \emph{-2 \(\mu\)T / \(^{\circ}\)C} and is
+therefore predictable.
+
+In the evaluation (see figure ), a linear function was also calculated
+using curve fitting to determine the temperature coefficients of the
+sensors. This makes it possible to calculate these deviations based on
+the ambient temperature during the software calibration.
 
@@
 
+\begin{longtable}[]{@{}lllll@{}}
+\caption{Overview of all characterised sensor properties
+\label{Overview_of_all_characterised_sensor_properties.csv}}\tabularnewline
+\toprule
+Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
+\midrule
+\endhead
+\(\mu_{nl}\) & 0.79 & 0.00 & \% & Mean noise level\tabularnewline
+\(\sigma_{nl}\) & 0.76 & 0.00 & \% & \gls{sd} noise level\tabularnewline
+\(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Mean sensor value
+(Baseline)\tabularnewline
+\(\sigma_{rv}\) & 172.00 & 0.20 & \(\mu\)T & \gls{sd} sensor
+value\tabularnewline
+\(\mu_{t}\) & 20.68 & 19.40 & \(^{\circ}\)C & Mean sensor
+temperature\tabularnewline
+\(\sigma_{t}\) & 0.53 & 0.00 & \(^{\circ}\)C & \gls{sd} sensor
+temperature\tabularnewline
+\(\mu_{trev}\) & 21.0 & 21.0 & \(^{\circ}\)C & Ambient
+temperature\tabularnewline
+\(\mu_{sl}\) & 0.25 & 0.04 & \% & Mean sensor linearity
+deviation\tabularnewline
+\(\sigma_{sl}\) & 3.64 & 0.56 & \% & \gls{sd} sensor
+linearity\tabularnewline
+\(\mu_{td}\) & -1.99 & -5.13 & \(\mu\)T / \(^{\circ}\)C & Mean sensor
+temperature coefficients\tabularnewline
+\bottomrule
+\end{longtable}
+
 are they suitable for <1000(+\gls{ppm}) ?
@@
   nmr probes for better results
+\item
+  mit software calibrierung ist es möglich vermutlich möglich sowie
+  mittelung ist es möglich auch mit dem tlv493d kanpp unter die 50uT zu
+  kommen
+\item
+  mess durchläufe mit ist es mögloch von 175uT nach 70uT zu kommen mit
+  avg=20 kommt man auf 45
+\item
+  sollte ein geeignerter ersatzsensor gefunden werden
+\item
+  beide sensoren sind jedoch durch chrakterisierung von
+  permanentmagneten geeignet
+\item
+  beim tlv493d ist es möglich absolut werte zu erfassen.
+\item
+  beim mmc ist es möglich relativ magnete untereinander zu vergleichen
 \end{itemize}

### 2024-02-15 documentation/thesis/build_thesis.sh

@@ -27,12 +27,14 @@ mkdir -p generated_images
 
 rm -f ./thesis_document_tmp.md
 rm -f ./thesis_document_tmp.md.*
+if [[ ! -v BUILD_FAST ]]; then
 # REMOVE GENERATED TEX
 rm -f ./thesis_declaration.tex
 rm -f ./thesis_document.tex
 rm -f ./thesis_document_tmp.tex
 rm -f ./thesis_abstract.tex
 rm -f ./thesis_attachments.tex
+fi
 # REMOVE GENERATED PDF
 rm -f ./thesis.pdf
 
@@ -41,6 +43,7 @@ echo "-- STARTING BUILDING THESIS DOCUMENT --"
 pandoc --version
 
 # CONVERT CSV TABLES to MARKDOWN
+if [[ ! -v BUILD_FAST ]]; then
 cp ./thesis_document.md ./thesis_document_tmp.md 
 FILES="./tables/*.csv"
 for f in $FILES
@@ -70,12 +73,12 @@ do
     echo "$str"
     sed -e "/$str/ {" -e "r $f.md" -e 'd' -e '}' -i ./thesis_document_tmp.md 
 done
+fi
 
 
 
 
-
-
+if [[ ! -v BUILD_FAST ]]; then
 # ADD IMAGES
 imagefiles="./images/*.png"
 for f in $imagefiles
@@ -114,7 +117,7 @@ do
     echo "$str"
     sed -e "/$str/ {" -e "r $f.md" -e 'd' -e '}' -i ./thesis_document_tmp.md 
 done
-
+fi
 
 # CONVERT LISTINGS
 python3 convert_listings_head.py ./thesis_document_tmp.md 

### 2024-02-15 documentation/thesis/thesis_abstract.tex
more thesis

@@
-A large number of magnets are used in the construction of low-field MRI
-equipment on the basis of permanent magnets. The magnetic properties of
-these magnets must be similar to a certain degree in order to achieve a
-homogeneous B0 field, which is necessary for many setups. Due to the
-complex manufacturing process of neodymium magnets, the different
-properties, i.e.~the direction of magnetisation, can deviate from each
-other. This affects the homogeneity of the field. A passive shimming
-process is typically used to adjust the field afterwards. This is
-complex and time-consuming and requires manual corrections to the
-magnets used. To avoid this process, magnets can be systematically
-measured in advance. Data acquisition, storage and subsequent analysis
-play an important role in this methodology. Several existing open source
-solutions implement individual parts, but do not provide a complete data
-processing pipeline from acquisition to analysis, and their data storage
-formats are not compatible with each other. For this use case, the
-MagneticReadoutProcessing library has been created. It implements all
-important aspects of acquisition, storage and analysis, and each
-intermediate step can be customised by the user without having to create
-everything from scratch, thus encouraging exchange between different
-user groups. Complete documentation, tutorials and tests enable users to
-use and adapt the framework as quickly as possible. The framework was
-used to characterise different magnets, which requires integrating
-magnetic field sensors.
+A large number of permanent magnets are used in the construction of
+low-field MRI equipment on the basis of permanent magnets. The magnetic
+properties of these magnets must be similar to a certain degree in order
+to achieve a homogeneous B0 field, which is necessary for many setups.
+
+Due to the complex manufacturing process of neodymium magnets, the
+different properties, i.e.~the direction of magnetisation, can deviate
+from each other. This affects the homogeneity of the field and the image
+acquisition.
+
+A passive shimming process is typically used to adjust the field
+afterwards. This is complex and time-consuming and requires manual
+corrections to the magnets used. To avoid this process, magnets can be
+systematically measured in advance. Sensor accuracy and repeatability
+Data acquisition, storage and subsequent analysis play an important role
+in this methodology.
+
+Several existing open source solutions implement individual parts, but
+do not provide a complete data processing pipeline from acquisition to
+analysis, and their data storage formats are not compatible with each
+other.
+
+For this use case, the MagneticReadoutProcessing library has been
+created in this work. It implements all important aspects of
+acquisition, storage and analysis, and each intermediate step can be
+customised by the user without having to create everything from scratch,
+thus encouraging exchange between different user groups.
+
+Complete documentation, tutorials and tests enable users to use and
+adapt the framework as quickly as possible. The framework was used to
+characterise different magnets, which requires integrating magnetic
+field sensors.
+
+To evaluate the software framework and hardware, two digital sensors
+were characterised and tested under the same conditions for noise,
+temperature dependence and linearity. The result is that both sensors
+can only be used under certain conditions, as the noise intensity is
+higher than the specified 50 mühT and the value ranges fluctuate too
+much as a result. It is recommended to consider analogue sensors or NMR
+probes in the future.

### 2024-02-15 documentation/thesis/thesis_document.tex
.

@@
 
-This makes it easy to integrate your own measuring devices into the
+This makes it easy to integrate an own measuring devices into the
 \gls{mrp} ecosystem at a later date. This is only possible with a
@@
 
-Each sensor that has been loaded with the firmware, registeres on to the
-host \gls{pc} as a serial interface. There are several ways for the user
-to interact with the sensor:
+Each sensor that is loaded with the firmware, registeres on to the host
+\gls{pc} as a serial interface. There are several ways for the user to
+interact with the sensor:
 
@@
 Two functional sensor platforms
-\ref{Build_sensors_with_different_capabilities.csv} were built in order
+\ref{Build_sensors_with_different_capabilities.csv} are built in order
 to create a solid test platform for later tests and for the development
@@
 Since the \emph{MMC5603NJ} only has limited measurement range of total
-6uT, even small coin sized neodymium magnets already saturates the
-sensor. It is possible to mount 3D printed spacers over the sensor to
-increase the distance between the magnet and the sensor and thus also
+\emph{6uT}, even small coin sized neodymium magnets already saturates
+the sensor. It is possible to mount 3D printed spacers over the sensor
+to increase the distance between the magnet and the sensor and thus also
 measure these magnets.
@@
 offer an physical \emph{RS232} interface. As with the other sensors,
-this interface consists of your \emph{Raspberry-Pi Pico} with an
-additional level shifter.
+this interface consists of a \emph{Raspberry-Pi Pico} with an additional
+level shifter.
 
 The teslameter is connected to the microcontroller using two free
-\gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
-separate build configuration. In order to be able to read and correctly
-interpret the data from the microcontoller, the serial protocol of the
-sensor was implemented in a customised version of the
-\emph{CustomSensor} class \ref{lst:CustomSensorClass}.
+\gls{gpio}s in \gls{uart} mode. The firmware is adapted using a separate
+build configuration. In order to be able to read and correctly interpret
+the data from the microcontoller, the serial protocol of the sensor is
+implemented in a customised version of the \emph{CustomSensor} class
+\ref{lst:CustomSensorClass}.
 
@@
 
-The software readout framework is the central software component that
-was developed as part of this work. This software framework is intended
-to provide a user-oriented data acquisition and analysis environment.
-For this purpose, typical individual steps that occur in relation to
-these tasks were implemented:
+The software readout framework is the central software component that is
+developed as part of this work. This software framework is intended to
+provide a user-oriented data acquisition and analysis environment. For
+this purpose, typical individual steps that occur in relation to these
+tasks are implemented:
 
@@
 
-All these possible task parts were divided into different blocks and
-users were given the possibility of adding their own functionalities.
+All these possible task parts is divided into different blocks and users
+is given the possibility of adding their own functionalities.
 
@@
 
-For this purpose, the library was divided into individual modules, which
+For this purpose, the library is divided into individual modules, which
 are shown in the graphic
@@
 For this purpose, a module system with standardised functional patterns
-and data types was developed and packed together in a extendable Python
+and data types is developed and packed together in a extendable Python
 library.
@@
 In order to realise the concept of user interaction points, the library
-was divided into different modules. These modules can be divided into
-two main categories:
+is divided into different modules. These modules can be divided into two
+main categories:
 
@@
 allows the library to reuse and archive the measurements. On the other
-hand, the focus during development was that it is also possible to use
+hand, the focus during development is that it is also possible to use
 the data in other programs.
@@
 
-Taking these points into account, the \gls{json} format was chosen. This
+Taking these points into account, the \gls{json} format is chosen. This
 is human and machine readable and there is a compatible parser for
@@
 the \gls{json} structure which is generated when a measurement thatt
-using the library is exported. Here you can see that by using the
+using the library is exported. It can be seen that by using the
 \gls{json} format, all measurement points and metadata are available in
@@
 
-To realize this, a \gls{lut} was created in the previous steps, which
+To realize this, a \gls{lut} is created in the previous steps, which
 contains information regarding \emph{requested capability}
@@
 example \ref{mrpreading}, the next step is to record real sensor data.
-For this purpose, the \emph{MRPHal} module was developed, which can
+For this purpose, the \emph{MRPHal} module is developed, which can
 interact with all \emph{Unified Sensor} \ref{unified-sensor}-compatible
@@
 simplify these tasks, a \gls{cli}
-\ref{Example_measurement_analysis_pipeline.png} was implemented. The
+\ref{Example_measurement_analysis_pipeline.png} is implemented. The
 libaray \gls{cli} implements the following functionalities:
@@
 
-For this purpose, a further \gls{cli} application was created, which
+For this purpose, a further \gls{cli} application is created, which
 enables the user to create and execute complex evaluation pipelines for
@@
 
-In order to implement such a pipeline, the \emph{yaml} file format was
+In order to implement such a pipeline, the \emph{yaml} file format is
 chosen for the definition of the pipeline, as this is for non
@@
 created for all important functionalities and usecases. The test
-framework \emph{PyTest} \cite{PyTest} was used for this purpose, as
+framework \emph{PyTest} \cite{PyTest} is used for this purpose, as
 it offers direct integration in most \gls{ide}s (see
@@
 One important point that improves usability for users is the simple
-installation of all \gls{mrp} modules. As it was created in the Python
+installation of all \gls{mrp} modules. As it is created in the Python
 programming language, there are several public package registry where
@@
 In order to provide comprehensive documentation for the enduser, the
-source code was documented using Python-\emph{docstrings}
+source code is documented using Python-\emph{docstrings}
 \cite{PythonDocstringReference} and the Python type annotations. The
@@
 provide simple how-to-use instructions, the documentation framework
-\emph{Sphinx} \cite{SphinxDocumentation} was used for this purpose.
+\emph{Sphinx} \cite{SphinxDocumentation} is used for this purpose.
 This framework makes it possible to generate \gls{html} or \gls{pdf}
@@
 
-For the hardware setup, the 3D-Fullsphere\ref{d-fullsphere} sensor was
+For the hardware setup, the 3D-Fullsphere\ref{d-fullsphere} sensor is
 used for the evaulation of the framework. As this is equipped with an
@@
 
-The configured hardware was then connected to the host system using the
+The configured hardware is then connected to the host system using the
 \emph{MRPcli config setupsensor}-\gls{cli} command. Afterwards, the
-measurement was configured for an measurement run, using the following
+measurement is configured for an measurement run, using the following
 configuration commands \ref{lst:evaluation_measurement_config}.
@@
 
-The \emph{MRPcli measure run} command was then called up for each
+The \emph{MRPcli measure run} command is then called up for each
 individual magnet to execute a measurement. After each run, the
-\emph{READING-NAME} parameter was filled with the id of the next magnet
+\emph{READING-NAME} parameter is filled with the id of the next magnet
 so that all measurements could be assigned to the physical magnets.
@@
 or implemented directly can be called via the pipeline. As this is a
-short algorithm, it was inserted directly into the file.
+short algorithm, it is inserted directly into the file.
 
@@
 queue. Subsequently, as many elements of the queue are returned as
-defined by the \emph{IP\_return\_count} parameter. The actual sorting
-was carried out by the queue in the background.
+defined by the \emph{IP\_return\_count} parameter. The actual sorting is
+carried out by the queue in the background.
 
@@
 plotted \emph{CoG} \(\mu\)T deviation values, that these are closest to
-an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal value was
+an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal value is
 calculated with the function
@@
 
-The filter algorithm implemented by the user was thus successfully
+The filter algorithm implemented by the user is thus successfully
 executed using the user-programmable pipeline. The calculation result
-was successfully verified using raw measurement data and the final
+waiss successfully verified using raw measurement data and the final
 result of the algorithm.
@@
 In the previous chapter \emph{Usecase Evaluation}
-\ref{usecase-evaluation} it was shown that the implementation of the
-hardware and software framework for various magnetic field sensors was
+\ref{usecase-evaluation} it is shown that the implementation of the
+hardware and software framework for various magnetic field sensors is
 successfully implemented.
 
-In addition, the basic application by the user was demonstrated using an
+In addition, the basic application by the user is demonstrated using an
 example. This makes it possible to systematically characterise magnets
@@
 were used for sensor characterisation. The additional column for the
-\emph{Background-Noise} was taken from the respective data sheets of the
+\emph{Background-Noise} is taken from the respective data sheets of the
 sesors and will be verified in the later \emph{Background-Noise}
@@
 
-This selection was made for the following reasons:
+This selection is made for the following reasons:
 
@@
 the table. For this evaluation, the sensors listed in the table were
-used for sensor characterisation. This selection was made for the
+used for sensor characterisation. This selection is made for the
 following reasons:
@@
 
-The setup was placed and pre-wired in the temperature chamber 24 hours
+The setup is placed and pre-wired in the temperature chamber 24 hours
 before the series of measurements were carried out. The insulated
 housing of a \emph{Voron 2.4} 3D printer, which has a separately
-controlled internal heating system, was used as the temperature chamber.
-To verify the temperature, an additional thermometer \emph{VC-7055BT}
-was placed on the base plate. A 10mm thick \emph{PTFE} insulation plate
-was placed between the floor and the sensor base plate to prevent direct
-and uneven heating of the base plate by the heated floor.
+controlled internal heating system, is used as the temperature chamber.
+To verify the temperature, an additional thermometer \emph{VC-7055BT} is
+placed on the base plate. A 10mm thick \emph{PTFE} insulation plate is
+placed between the floor and the sensor base plate to prevent direct and
+uneven heating of the base plate by the heated floor.
 
@@
 \ref{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
-shows this basic setup, the \emph{Raspberry Pi Pico} shown here was used
+shows this basic setup, the \emph{Raspberry Pi Pico} shown here is used
 as the readout hardware, on which the \emph{Unified Sensor Firmware} is
@@
 
-For the software setup, \emph{MRPCli} \ref{command-line-interface} was
+For the software setup, \emph{MRPCli} \ref{command-line-interface} is
 used to control and record the measurement series, with the functions of
@@
 the sensor without external magnetic fields. For this purpose, a sample
-size of \emph{N=10000} measured values was recorded for the baseline
+size of \emph{N=10000} measured values is recorded for the baseline
 measurement.
@@
 
-In the evaluation (see figure ), a linear function was also calculated
-using curve fitting to determine the temperature coefficients of the
-sensors. This makes it possible to calculate these deviations based on
-the ambient temperature during the software calibration.
+The graph of the \emph{TLV493d} is significantly steeper with a gradient
+of \emph{-5.13 \(\mu\)T / \(^{\circ}\)C}, and it is also not as linear
+as the \emph{MMC5603NJ}; there are clear jumps in the gradient. However,
+the total change between the temperature regions of 175\(\mu\)T is less
+than that of the \emph{MMC5603NJ} with 70\(\mu\)T, if the total
+measurement range of the sensors is also taken into account.
+
+In the evaluation (see figure
+\ref{Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}),
+a linear function was also calculated using curve fitting to determine
+the temperature coefficients of the sensors. This makes it possible to
+compensate these deviations based on the ambient temperature during the
+software calibration.
 
@@
 
+Table \ref{Overview_of_all_characterised_sensor_properties.csv} shows a
+summary of all recorded and analysed measured values of the two
+characterised sensors \emph{TLV493D} and \emph{MMC5603NJ}. It can be
+clearly seen that these differ significantly by a factor of \emph{x10}.
+The \emph{TLV493D} performs seriously in the Senosr Noise measurement
+and also performs worse than specified in the data sheet (98\(\mu\)T
+instead of 175\(\mu\)T), but the large measuring range, which fulfils
+the required specifications from chapter \emph{Research Question}
+\ref{Research Question and Approach}, must be taken into account here,
+which is not met by the \emph{MMC5603NJ}.
+
 are they suitable for <1000(+\gls{ppm}) ?

### 2024-02-15 documentation/thesis/thesis_document.tex
.

@@
 domain, delineates the scope and boundaries of the present research,
-surveys the current state of the art in low-field \gls{mri}research and
+surveys the current state of the art in low-field \gls{mri} research and
 applications, articulates the research question driving this thesis and
 delineates the anticipated usecases and benefits that will be explored
-and analyzed throughout the study.
+and analysed throughout the study.
 
@@
 in the magnetic field is crucial for accurate imaging or comparative
-analyses. While tipically calculated images have lower resolution due to
+analyses. While typically calculated images have lower resolution due to
 lower magnetic field strength, low-field systems facilitate the
-comparison of different field behaviors and the identification of all
+comparison of different field behaviours and the identification of all
 kinds of irritations. O'Reilly and Teeuwisse and de Gans
 \cite{OReilly2019-rn} have already demonstrated low-cost and
-small-scale implementations with low-field \gls{mri} in 2021
-calculationg images of a head sucessfully.
+small-scale implementations with low-field \gls{mri} in 2021 calculating
+images of a head successfully.
 
@@
 homogeneity can be measured post-assembly, the intricate task of
-readjustment is taken into account. It is less costintensive and less
+readjustment is taken into account. It is less cost-intensive and less
 complicated to measure the magnets proactively, prior to the
-finalization of the \gls{mri}system.
+finalization of the \gls{mri} system.
 
@@
 For modern medical imaging high-field superconducting magnets dominate
-most \gls{mri} machines, providing high blac-withe image resolution.
-However, the substantial costs, space requierments and safety
+most \gls{mri} machines, providing high black-withe image resolution.
+However, the substantial costs, space requirements and safety
 considerations cause considerable challenges.
@@
 physicists use the term magnetic field induction. The \gls{snr} is
-proprtional to the magnetic \emph{B0} field; growing magnetic field
-leads automatically to higher \gls{snr}. The inital \emph{B0} field of
-an \gls{mri} aims to be homogenouse, for image aquisition the second
-step requires imhomoginity of the \emph{B0} field to stimulate spin in
-the atoms of materials. For high resultion images, the initial \emph{B0}
-field aims to be a homogenouse as possible.
+proportional to the magnetic \emph{B0} field; growing magnetic field
+leads automatically to higher \gls{snr}. The initial \emph{B0} field of
+an \gls{mri} aims to be homogeneous, for image acquisition the second
+step requires inhomogeneity of the \emph{B0} field to stimulate spin in
+the atoms of materials. For high resolution images, the initial
+\emph{B0} field aims to be a homogeneous as possible.
 
@@
 
-A halbach ring of this type is usually based on a ring with permanent
+A Halbach ring of this type is usually based on a ring with permanent
 magnets arranged in a circle. The graphic
@@
 The Halbach magnetic array appears as a essential element for future
-Magnet characterisation. Based on this fact this thesis centers on
+Magnet characterisation. Based on this fact this thesis centres on
 assessing the sensors' applicability, the Halbach magnetic array serves
@@
 homogeneous \emph{27cm} diameter Bore Halbach Array magnet''
-\cite{OReilly2019-rn} in 2019.This innovative setup was subsequently
+\cite{OReilly2019-rn} in 2019.This innovative setup is subsequently
 employed in 2020 to acquire in vivo MR images, showcasing the practical
-applications of their pioneering research \cite{OReilly2021-ep}.
-2023 veröffentlichten de Vos, Remis und Webb eine zusammenfassung zur
-gestaltng eines oint-of-care halbach array low-field \gls{mri} system
+applications of their pioneering research \cite{OReilly2021-ep}. In
+2023, de Vos, Remis and Webb published a summary of the design of a
+point-of-care Halbach array low-field \gls{mri} system
 \cite{De_Vos2023-pb}.
@@
 diameter Bore Halbach Array magnet'' \cite{OReilly2019-rn} in 2019.
-This innovative setup was subsequently employed in 2020 to acquire in
+This innovative setup is subsequently employed in 2020 to acquire in
 vivo MR images, showcasing the practical applications of their
@@
 
-\textbf{Magnet Characerisation}
+\textbf{Magnet Characterisation}
 
@@
 process or checking the permanent magnets used in advance before they
-are used in a Hallbach configuration.
+are used in a Halbach configuration.
 
@@
 Before naming the research focus, it is important to understand the
-difference and connection between deviation and resulution of the
+difference and connection between deviation and resolution of the
 system. To measure a deviation of better than \emph{1000}\gls{ppm} in a
@@
 It is essential to emphasize that the intention is not to characterize
-the magnets; the sensores which might be used for characterisation are
-be analised and evaluated.
+the magnets; the sensors which might be used for characterisation are be
+analysed and evaluated.
 
@@
 The purpose of the framework is to enable the automated acquisition of
-measurement data from various connected hadware sensors. The user should
-be able to configure various measurement series, which should then be
-carried out by the framework without further user interaction.
+measurement data from various connected hardware sensors. The user
+should be able to configure various measurement series, which should
+then be carried out by the framework without further user interaction.
 
@@
 \gls{mrp} ecosystem at a later date. This is only possible with a
-minimal functional hardware and firmware setup and was developed for
-this purpose first.
+minimal functional hardware and firmware setup and is developed for this
+purpose first.
 
@@
 
-A key aspect of this selection was the preference for sensors with
+A key aspect of this selection is the preference for sensors with
 digital interfaces to facilitate implementation in the circuit layout
@@
 
-The use of analog sensors was purposefully avoided, though they are
+The use of analog sensors is purposefully avoided, though they are
 suitable for more precise measurements and extended measuring ranges.
@@
 All parts are produced using the 3D printing additive manufacturing
-processes. The sensor circuit board was glued underneath the magnet
+processes. The sensor circuit board is glued underneath the magnet
 holder. This is interchangeable, so different distances between sensor
@@
 various sensor \gls{ic} packages. By placing mounting holes on the
-\gls{pcb}, it is possible to attach various mechanical mounts ontop of
+\gls{pcb}, it is possible to attach various mechanical mounts on top of
 the sensor \gls{ic}s.
 
-Special attention was paid to the provision of an accessible
+Special attention is paid to the provision of an accessible
 SYNC-\gls{gpio} connector. This enables subsequent multi-sensor
@@
 easily connected without having to adapt the firmware. This modularity
-was implemented using abstract class design. These are initiated
+is implemented using abstract class design. These are initiated
 according to the sensors found at startup. If new hardware is to be
@@
 interval set in the setup procedure and their values are stored in a
-ringbuffer. Ring buffer offers efficient data management in limited
+ring buffer. Ring buffer offers efficient data management in limited
 memory. Its cyclic structure enables continuous overwriting of older
@@
 
-Each sensor that is loaded with the firmware, registeres on to the host
+Each sensor that is loaded with the firmware, registers on to the host
 \gls{pc} as a serial interface. There are several ways for the user to
@@
 \item
-  Use with \gls{mrp} \ref{software-readout-framework}-libaray
+  Use with \gls{mrp} \ref{software-readout-framework}-library
 \item
@@
 \item
-  \emph{Raspberry Pi OS Lite} - \gls{os} \emph{debian bookworm x64},
+  \emph{Raspberry Pi OS Lite} - \gls{os} \emph{Debian bookworm x64},
 \item
@@
 \emph{primary} and several \emph{secondary} sensors, each sensor waits
-for an intial pulse on the SYNC-\gls{gpio}
+for an initial pulse on the SYNC-\gls{gpio}
 \ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
@@
 \ref{Query_opmode_using_(+cli).png} command. An important aspect of the
-implementation here was that there is no numbering or sequence of the
+implementation here is that there is no numbering or sequence of the
 individual sensors.
@@
 
-\hypertarget{d-fullsphere}{%
-\subsection{3D: Fullsphere}\label{d-fullsphere}}
+\hypertarget{d-full-sphere}{%
+\subsection{3D: Full Sphere}\label{d-full-sphere}}
 
@@
 
-The 3D fullsphere sensor
+The 3D full sphere sensor
 \ref{Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
@@
 shows the visualisation of such a scan in the form of a spherical 3D
-map. On the sphere is the magnetic field strength, which was detected by
+map. On the sphere is the magnetic field strength, which is detected by
 the sensor at the position. The transition from a fully positive field
@@
 can influence the measurements of the magnetic field sensor, the
-distance between these components and the sensor or magnets was
+distance between these components and the sensor or magnets is
 increased. The turntable and its drive motor are connected to each other
@@
 
-On the electrical side, it also consists of a \emph{SKR-Pico} stepper
-motor controller, together with the \emph{TLV493D} magnetic field
-sensor. This was chosen because of its larger measuring range and can
-therefore be used more universally without having to change the sensor
-of the arm.
+On the electrical side, consists of a \emph{SKR-Pico} stepper motor
+controller on the one hand side and a \emph{TLV493D} magnetic field
+sensor on the other hand side. This is chosen because of its larger
+measuring range and can therefore be used more universally without
+having to change the sensor of the arm.
 
@@
 build configuration. In order to be able to read and correctly interpret
-the data from the microcontoller, the serial protocol of the sensor is
+the data from the microcontroller, the serial protocol of the sensor is
 implemented in a customised version of the \emph{CustomSensor} class
@@
 \item
-  Analysis - algorithms to analyze different data sets \ref{analysis}
+  Analysis - algorithms to analyse different data sets \ref{analysis}
 \end{itemize}
@@
 
-This also fulfills the goal of making individual user-created algorithms
+This also fulfils the goal of making individual user-created algorithms
 interchangeable. If the user now wishes to use a different \gls{cad}
@@
 To configure parameters, ensuring a tailored approach to the entire
-measurement process, these parameters act as a cessential bridge between
+measurement process, these parameters act as a essential bridge between
 user preferences and the robust capabilities of the \emph{MRPReading}
@@
 The following code snippet \ref{lst:json_export_format_example} shows
-the \gls{json} structure which is generated when a measurement thatt
+the \gls{json} structure which is generated when a measurement that
 using the library is exported. It can be seen that by using the
@@
 
-The extention modules build on the core modules and offer the user
+The extension modules build on the core modules and offer the user
 additional basic functionalities. These include functions for data
@@
 \item
-  \emph{CoG} - Center of gravity
+  \emph{CoG} - Centre of gravity
 \item
@@
 \item
-  \emph{k-nearest} - K-nearest neighbors
+  \emph{k-nearest} - K-nearest neighbours
 \end{itemize}
@@
 
-Multibe sensor can be connected to any \gls{pc} which is available on
+Multiple sensor can be connected to any \gls{pc} which is available on
 the network. This can be a \gls{sbc} (e.g.~a Raspberry Pi). The small
@@
 \gls{pc}, but the proxy instance \emph{remote} \gls{pc} \emph{\#2} can
-acces the proxy running on \emph{remote} \gls{pc} \emph{\#1}.
+access the proxy running on \emph{remote} \gls{pc} \emph{\#1}.
 
@@
 which provides general functions for visualising measurements. The
-visualisation optionsmakes it possible to visually assess the results of
+visualisation options make it possible to visually assess the results of
 a measurement. This is particularly helpful for full-sphere measurements
@@
 position and rotation offset according to the Halbach design and
-calucation scheme \cite{HallbachMagnetDesignPaper} using the
+calculation scheme \cite{HallbachMagnetDesignPaper} using the
 \emph{MRPHalbachArrayGenerator} module.
@@
 \ref{Example_measurement_analysis_pipeline.png} is implemented. The
-libaray \gls{cli} implements the following functionalities:
+library \gls{cli} implements the following functionalities:
 
@@
 package registry and offers direct support for the package installation
-programm \gls{pip} \ref{lst:setup_lib_with_pip}.
+program \gls{pip} \ref{lst:setup_lib_with_pip}.
 
@@
 \item
-  \textbf{Hardware preperation}: Users can prepare measurements using
+  \textbf{Hardware preparation}: Users can prepare measurements using
   the implemented framework. This includes the placement of the sensors
@@
 
-\hypertarget{hardware-preperation}{%
-\section{Hardware preperation}\label{hardware-preperation}}
+\hypertarget{hardware-preparation}{%
+\section{Hardware preparation}\label{hardware-preparation}}
 
@@
 For the hardware setup, the 3D-Fullsphere\ref{d-fullsphere} sensor is
-used for the evaulation of the framework. As this is equipped with an
+used for the evaluation of the framework. As this is equipped with an
 exchangeable magnetic holder mount, suitable holders are required for
@@
 smallest distance between all measurements. The distance for each
-measurement is determined using the center of gravity function
+measurement is determined using the centre of gravity function
 \emph{CoG}, the length is then calculated from the result vector. This
@@
 the measured values are plotted as a result of the filter algorithm. As
-the \emph{IP\_return\_count} parameter was set to four, only the four
+the \emph{IP\_return\_count} parameter is set to four, only the four
 most similar measurements were exported here. It can be seen from the
@@
 The filter algorithm implemented by the user is thus successfully
-executed using the user-programmable pipeline. The calculation result
-waiss successfully verified using raw measurement data and the final
-result of the algorithm.
+executed using the user-programmable pipeline. The calculation result is
+successfully verified using raw measurement data and the final result of
+the algorithm.
 
@@
 
-In addition, the basic application by the user is demonstrated using an
-example. This makes it possible to systematically characterise magnets
-from the software and readout hardware side by means of data
+In addition, the basic application by the user is demonstrated based on
+an example. In this way is possible to systematically characterise
+magnets from the software and readout hardware side by means of data
 acquisition, storage and analysis.
@@
 \item
-  Automated measurement of the homogeneity of Hallbach rings with an
+  Automated measurement of the homogeneity of Halbach rings with an
   accuracy of less than \emph{1000\gls{ppm}}
@@
 \emph{Background-Noise} is taken from the respective data sheets of the
-sesors and will be verified in the later \emph{Background-Noise}
+sensors and will be verified in the later \emph{Background-Noise}
 measurement \ref{sensor-characterisation-background-noise}.
@@
 To verify the temperature, an additional thermometer \emph{VC-7055BT} is
-placed on the base plate. A 10mm thick \emph{PTFE} insulation plate is
-placed between the floor and the sensor base plate to prevent direct and
-uneven heating of the base plate by the heated floor.
+placed on the base plate. A \emph{10mm} thick \emph{PTFE} insulation
+plate is placed between the floor and the sensor base plate to prevent
+direct and uneven heating of the base plate by the heated floor.
 
@@
 ambient conditions. For verification, a reference measurement of the
-environment was carried out with the calibrated \emph{Voltcraft GM70}
+environment is carried out with the calibrated \emph{Voltcraft GM70}
 Telsameter next to the sensor \gls{ic} This provides a \emph{real}
@@
 This is achieved here by means of an additional linear axis installed
-above the sensor setup. A holder for an \emph{N45 12x12x12mm} magnet was
+above the sensor setup. A holder for an \emph{N45 12x12x12mm} magnet is
 attached to the end effector of this axis, which can thus be moved at
@@
 path to be travelled by the linear axis. The complete range of
-\emph{120mm} in \emph{1mm} steps was selected here. The following
+\emph{120mm} in \emph{1mm} steps is selected here. The following
 automated process then runs as follows:
@@
 directly comparable for both plots, as the sensors have different
-measuring ranges. To ensure comparability, the ideal curve was
+measuring ranges. To ensure comparability, the ideal curve is
 determined. In order to be able to make quantifiable statements about
 the measurement results, the mean and \gls{sd} deviation of these two
-curves was determined.
+curves is determined.
 
@@
 different results in the previous measurements, an additional
-temperature sensor was attached to the sensor circuit board for this
+temperature sensor is attached to the sensor circuit board for this
 measurement. The figure
@@
 \textgreater=80\(^{\circ}\) for non-high-quality type N magnets
-\cite{magna-c}). The temperature range was selected so that it is
+\cite{magna-c}). The temperature range is selected so that it is
 within a sufficient range for the application.
@@
 clearly seen that these differ significantly by a factor of \emph{x10}.
+
 The \emph{TLV493D} performs seriously in the Senosr Noise measurement
@@
 the required specifications from chapter \emph{Research Question}
-\ref{Research Question and Approach}, must be taken into account here,
+\ref{research-question-and-approach}, must be taken into account here,
 which is not met by the \emph{MMC5603NJ}.
+
+The \emph{MMC5603NJ} can be used directly without additional software
+calibration for measuring permanent magnets. Even without additional
+measurement averaging, very precise measurement results can be achieved,
+which achieve a measurement accuracy of less than \emph{1000\gls{ppm}}.
+
+However, due to the limited measuring range of \emph{±3mT}, direct
+measurement of stronger magnets is not possible. The \emph{N45
+12x12x12mm} magnets used in the application typically have a field
+strength of around \emph{100mT} at a distance of \emph{10mm}.
+
+In the following chapter, recommendations for action are defined, which
+were derived from the analysis results.
+
+\hypertarget{recommendation-for-action}{%
+\subsection{Recommendation for Action}\label{recommendation-for-action}}
+
+\begin{itemize}
+\tightlist
+\item
+  folgendes setup woird für eine vermessung nach der sensor auswertung
+  emholen:
+\item
+  temperaturkomensation sowie linearitäts kompensation mit separaten
+  temperatur sensor
+\end{itemize}
 
@@
   beim mmc ist es möglich relativ magnete untereinander zu vergleichen
-\end{itemize}
-
-\hypertarget{recommendation-for-action}{%
-\subsection{Recommendation for Action}\label{recommendation-for-action}}
-
-\begin{itemize}
-\tightlist
-\item
-  folgendes setup woird für eine vermessung nach der sensor auswertung
-  emholen:
-\item
-  temperaturkomensation sowie linearitäts kompensation mit separaten
-  temperatur sensor
 \end{itemize}
@@
 to give users the opportunity to directly acquire their own magnetic
-field data, cost-effective and easily reproducible hardware was also
+field data, cost-effective and easily reproducible hardware is also
 developed.
@@
 
-A particular focus was placed on expandability by the user.
+A particular focus is placed on expandability by the user.
 Interchangeable modules allow the user to develop their own analysis
@@
 
-This extensibility and customisability was successfully demonstrated
+This extensibility and customisability is successfully demonstrated
 during the evaluation. This underlines the performance of the developed
@@
 which contains all the necessary functions and is ready for immediate
-use. During development, particular emphasis was placed on comprehensive
+use. During development, particular emphasis is placed on comprehensive
 documentation to make it easier to get started. Together with examples

### 2024-02-16 documentation/thesis/thesis_abstract.tex

@@
 can only be used under certain conditions, as the noise intensity is
-higher than the specified 50 mühT and the value ranges fluctuate too
+higher than the specified 50 \(\mu\)T and the value ranges fluctuate too
 much as a result. It is recommended to consider analogue sensors or NMR

### 2024-02-16 documentation/thesis/thesis_document.tex
.

@@
 
+The \emph{TLV493D}, on the other hand, is able to measure these
+directly, but does not achieve the required accuracy due to strong noise
+and steep temperature coefficients.
+
 In the following chapter, recommendations for action are defined, which
@@
 
-\begin{itemize}
-\tightlist
-\item
-  folgendes setup woird für eine vermessung nach der sensor auswertung
-  emholen:
-\item
-  temperaturkomensation sowie linearitäts kompensation mit separaten
-  temperatur sensor
-\end{itemize}
-
-are they suitable for <1000(+\gls{ppm}) ?
-
-\begin{itemize}
-\item
-  https://onlinelibrary.wiley.com/doi/epdf/10.1002/mrm.28396
-\item
-  27cm / 50mT bore
-\item
-  nmr probes for better results
-\item
-  mit software calibrierung ist es möglich vermutlich möglich sowie
-  mittelung ist es möglich auch mit dem tlv493d kanpp unter die 50uT zu
-  kommen
-\item
-  mess durchläufe mit ist es mögloch von 175uT nach 70uT zu kommen mit
-  avg=20 kommt man auf 45
-\item
-  sollte ein geeignerter ersatzsensor gefunden werden
-\item
-  beide sensoren sind jedoch durch chrakterisierung von
-  permanentmagneten geeignet
-\item
-  beim tlv493d ist es möglich absolut werte zu erfassen.
-\item
-  beim mmc ist es möglich relativ magnete untereinander zu vergleichen
-\end{itemize}
+After analysing the measurement results, it can be seen that the
+selected sensors are only partially suitable for the previously defined
+requirements.
+
+In general, further digital and analogue sensors should be characterised
+with the developed framework. In particular, the use of analogue
+Hallbach sensors with separate bias voltage should be evaluated, as a
+simplified characterisation procedure can be applied due to the lack of
+a base offset.
+
+In the following, methods will be shown with which it is nevertheless
+possible to use these sensors.
+
+\hypertarget{permanent-magnet-charakterisation}{%
+\subsubsection{Permanent Magnet
+charakterisation}\label{permanent-magnet-charakterisation}}
+
+Both sensors are suitable for precisely measuring and quantifying
+magnetic fields. To ensure the linearity of the sensors, compensation
+can be performed using a defined measurement setup. This concept has
+already been successfully realised with implemented
+\ref{example-sensors}, in particular \emph{1D: Single Sensor}
+\ref{d-single-sensor}, and proven to be functional in earlier chapters.
+
+The \emph{MMC5603NJ} sensor has a limited measuring range, which means
+that it may not the best choise for this application parameters.
+However, this limitation also makes it possible to compare relative
+magnetic field strengths with each other. Furthermore, by using
+software, it is possible to achieve absolute comparability of the
+magnetic fields by scaling the measured values accordingly. This was
+shown in the chapter \emph{Usecase Evaluation} \ref{usecase-evaluation}
+by comparing and sorting different permanent magnets using these
+sensors.
+
+Overall, both the \emph{TLV493D} and the \emph{MMC5603NJ} offer
+possibilities for characterising permanent magnets. By using suitable
+hardware setup, software calibration methods and precise
+characterisations can be carried out.
+
+\hypertarget{homogeneity-measurement-of-a-halbach-ring-based-b0-field}{%
+\subsubsection{Homogeneity Measurement of a Halbach ring-based B0
+field}\label{homogeneity-measurement-of-a-halbach-ring-based-b0-field}}
+
+The \emph{MMC5603NJ} cannot be used here due to the limited value range.
+The method of increasing the distance, as with permanent magnet
+characterisation, cannot be used here as the magnet is located within a
+limited space in the Halbach ring.
+
+In contrast, the \emph{TLV493D} has too much noise, so that the measured
+values cannot be used directly without post-processing. With software
+calibration, it is probably possible to reduce the noise to below
+50\(\mu\)T with the \emph{TLV493D}. As a test, several further
+measurement runs were carried out, which achieved results for the sensor
+noise of 71\(\mu\)T to 41\(\mu\)T when averaging \emph{100} measured
+values and \emph{1000} measured values. However, further measurement
+runs must be carried out to verify these results.
+
+In general post-processing of the measurements should, include
+temperature compensation with a separate temperature sensor, especially
+in the case of changing measurement conditions (e.g.~movement of the
+sensor in the B0 field).
 

### 2024-02-16 documentation/thesis/thesis_document.tex
.

@@
 
-There are two ways of using the data from the magnets that were
+There are two ways of using the data from the magnets that are
 previously measured:
@@
 
-The usecases were defined in the course of project planning and provide
+The usecases are defined in the course of project planning and provide
 an overview of how the user interacts with the project and what
@@
 suitable for more precise measurements and extended measuring ranges.
-They were excluded because they require more carefully designed circuits
+They are excluded because they require more carefully designed circuits
 and more complicated energy management.
@@
 shows\ref{Measured_sensor_readout_to_processing_using_host_software.csv}
-shows various jitter measurements. These were performed on a
+shows various jitter measurements. These are performed on a
 \emph{RaspberryPi 4 4GB}-\gls{sbc} together with an \emph{1D: Single
@@
 In order to give the user the possibility to display the recorded data
-visually, two modules were created, which can graphically prepare
+visually, two modules are created, which can graphically prepare
 \emph{MRPReading} instances:
@@
 
-During the development of the \gls{mrp}-library, test cases were also
+During the development of the \gls{mrp}-library, test cases are also
 created for all important functionalities and usecases. The test
@@
 excluding certain tests in certain build environment scenarios. Since
-all intended usecases were mapped using the test cases created, the code
+all intended usecases are mapped using the test cases created, the code
 of the test cases could later be used in slightly simplified variants
@@
 and \emph{MRPHalRest} modules, which are required to read out sensors
-connected via the network. Two different approaches were used here. In
-the case of local development, the test runs were carried out on a
+connected via the network. Two different approaches are used here. In
+the case of local development, the test runs are carried out on a
 \gls{pc} that can reach the network hardware and thus the test run could
@@
 \gls{pc} must be permanently available for this task. Instead, the
-hardware sensors were simulated by software and executed via
+hardware sensors are simulated by software and executed via
 virtualisation on the systems provided by \emph{Github Actions}.
@@
 This process covers all the essential functionalities required for a
-comprehensive characterisation of permanent magnets. These were
+comprehensive characterisation of permanent magnets. These are
 previously described in the Usecases \ref{usecases} chapter. The
@@
 the magnets to be measured. Ten random \emph{N45 12x12x12mm} neodymium
-magnets were used, which are shown in figure
+magnets are used, which are shown in figure
 \ref{Ten_numbered_test_magnets_in_separate_holders.png}.
 
-These were placed in modified 3D printed holders
+These are placed in modified 3D printed holders
 \ref{Ten_numbered_test_magnets_in_separate_holders.png} and then
@@
 the \emph{IP\_return\_count} parameter is set to four, only the four
-most similar measurements were exported here. It can be seen from the
+most similar measurements are exported here. It can be seen from the
 plotted \emph{CoG} \(\mu\)T deviation values, that these are closest to
@@
 In addition, the basic application by the user is demonstrated based on
-an example. In this way is possible to systematically characterise
+an example. Based on this it is possible to systematically characterise
 magnets from the software and readout hardware side by means of data
@@
 \ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
-were used for sensor characterisation. The additional column for the
+are used for sensor characterisation. The additional column for the
 \emph{Background-Noise} is taken from the respective data sheets of the
@@
 magnetic field sensors without modifications, including those listed in
-the table. For this evaluation, the sensors listed in the table were
-used for sensor characterisation. This selection is made for the
-following reasons:
+the table. For this evaluation, the sensors listed in the table are used
+for sensor characterisation. This selection is made for the following
+reasons:
 
@@
 measurements \ref{command-line-interface} and analysis pipelines
-\ref{programmable-data-processing-pipeline} are available for this
-purpose are packaged with library.
+\ref{programmable-data-processing-pipeline}, which are available for
+this purpose, are packaged within the library.
 
@@
 Single Sensor} \ref{d-single-sensor} sensor platform. The sensors to be
-measured were fixed together on an aluminium plate with thermally
+measured are fixed together on an aluminium plate with thermally
 conductive adhesive. This compensates for thermal differences. This is
@@
 The setup is placed and pre-wired in the temperature chamber 24 hours
-before the series of measurements were carried out. The insulated
-housing of a \emph{Voron 2.4} 3D printer, which has a separately
-controlled internal heating system, is used as the temperature chamber.
-To verify the temperature, an additional thermometer \emph{VC-7055BT} is
-placed on the base plate. A \emph{10mm} thick \emph{PTFE} insulation
-plate is placed between the floor and the sensor base plate to prevent
-direct and uneven heating of the base plate by the heated floor.
+before the series of measurements are carried out. The insulated housing
+of a \emph{Voron 2.4} 3D printer, which has a separately controlled
+internal heating system, is used as the temperature chamber. To verify
+the temperature, an additional thermometer \emph{VC-7055BT} is placed on
+the base plate. A \emph{10mm} thick \emph{PTFE} insulation plate is
+placed between the floor and the sensor base plate to prevent direct and
+uneven heating of the base plate by the heated floor.
 
@@
 \ref{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
-shows this basic setup, the \emph{Raspberry Pi Pico} shown here is used
-as the readout hardware, on which the \emph{Unified Sensor Firmware} is
+shows this basic setup, the \emph{Raspberry Pi Pico} is used as the
+readout hardware, on which the \emph{Unified Sensor Firmware} is
 running. With additional connected switch, its possible to isolate or
@@
 
-A separate battery powered supply is used as low-noise power supply for
-the sensors boards. An \emph{Raspberry Pi 4} is used as the host
+A separate battery power supply is used as low-noise power supply for
+the sensors boards. An \emph{Raspberry Pi 4} is implemented as the host
 computer, which is connected to the sensors via a \emph{Hailege
@@
 procedure and a special measurement setup. First, the magnetic field
-sensor is placed in a quiet environment to minimize external field
-interference. The temperature chamber for all noise tests is set to
-\(\mu_{trev}\)=21.0\(^{\circ}\) and the sensors are placed \emph{24}
+sensor is placed in a quiet and static environment to minimize external
+field interference. The temperature chamber for all noise tests is set
+to \(\mu_{trev}\)=21.0\(^{\circ}\) and the sensors are placed \emph{24}
 hours before the measurement run in the final measurement configuration
@@
 
-The procedure begins with the acquisition of the baseline by operating
+The procedure starts with the acquisition of the baseline by operating
 the sensor without external magnetic fields. For this purpose, a sample
@@
 
-The output signal of the sensor is then continuously measured and
-recorded. It is important to carry out the measurement over a
-sufficiently long period of time in order to record both short-term and
-long-term fluctuations. For this purpose, \emph{N=2000} further measured
-values were taken with a trigger and readout rate of one measurement per
-second.
+The output signal of the sensor is continuously measured and recorded.
+It is important to carry out the measurement over a sufficiently long
+period of time in order to record both short-term and long-term
+fluctuations. For this purpose, \emph{N=2000} further measured values
+are taken with a trigger and readout rate of one measurement per second.
 
@@
 \ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
-shows the measured values of these sensors. In the following, these are
+shows the measured values of these sensors. In the next phases these are
 analysed for each sensor examined.
@@
 The table \ref{Sensor_noise_evaluation_results.csv} lists the measured
-values that were extracted from the measurement data of the sensors
+values that are extracted from the measurement data of the sensors
 \ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}.
@@
 
-It is recommended, however, to use a separate temperature sensor when
-using the \emph{TLV493D} or to use a suitable averaging of the
-temperature and measured values in order to perform temperature
-compensation.
+Though it is recommended to use a separate temperature sensor when using
+the \emph{TLV493D} or to use a suitable averaging of the temperature and
+measured values in order to perform temperature compensation.
 
@@
 moved by the user until it is maximally saturated. With the
-\emph{TLV493D}, this corresponds to 250.000\(\mu\)T and below in low
-resolution mode. \emph{MCC5603NJ} around 3000\(\mu\)T. This ensures that
-the linearity is determined over the entire measuring range.
+\emph{TLV493D}, this corresponds to \emph{250.000\(\mu\)T} and below in
+low resolution mode. \emph{MCC5603NJ} around \emph{3000\(\mu\)T}. This
+ensures that the linearity is determined over the entire measuring
+range.
 
@@
 
-After the measurements were exported, they were analysed for linearity
+After the measurements are exported, they are analysed for linearity
 using \emph{MRPAnalysis} \ref{mrpanalysis} functions.

### 2024-02-16 documentation/thesis/thesis_abstract.tex
.

@@
 
-For this use case, the MagneticReadoutProcessing library has been
-created in this work. It implements all important aspects of
+For this use case, the python based MagneticReadoutProcessing library
+has been created in this work. It implements all important aspects of
 acquisition, storage and analysis, and each intermediate step can be
@@
 higher than the specified 50 \(\mu\)T and the value ranges fluctuate too
-much as a result. It is recommended to consider analogue sensors or NMR
-probes in the future.
+much as a result. It is recommended to consider the implementation of
+additional digital sensors as well as analogue sensors or NMR probes in
+the future.

### 2024-02-16 documentation/thesis/thesis_document.tex
.

@@
 in the strength of permanent magnets leads to significant difficulties
-in constructing an \gls{mri} with the necessary precision for homogenous
-field generation.
+in constructing an \gls{mri} magnet with the necessary precision for
+homogenous field generation.
 
@@
 
-The Halbach magnet incorporated in this system boasts a 27cm diameter, a
-\emph{B0} field strength of 50.4mT, and an impressive homogeneity of
-2400\gls{ppm} over a 20cm diameter using smaller magnets
-(\(12 x 12 x 12 mm^3\)). This exceptional homogeneity enables the
-utilization of coil-based gradients for spatial encoding, significantly
-enhancing the flexibility of image acquisition.
+The Halbach magnet incorporated in this system boasts a \emph{27cm}
+diameter, a \emph{B0} field strength of 50.4mT, and an impressive
+homogeneity of 2400\gls{ppm} over a \emph{20cm} diameter using smaller
+magnets (\(12 x 12 x 12 mm^3\)). This exceptional homogeneity enables
+the utilization of coil-based gradients for spatial encoding,
+significantly enhancing the flexibility of image acquisition.
 
@@
 with the stringent criteria of achieving an accuracy level of
-1000\gls{ppm}. Furthermore, the study seeks to validate whether the
-measuring range of these sensors appropriately corresponds to the
+\emph{1000}\gls{ppm}. Furthermore, the study seeks to validate whether
+the measuring range of these sensors appropriately corresponds to the
 required field strength, ensuring their suitability for the intended
@@
 
-The use of analog sensors is purposefully avoided, though they are
+The use of analogue sensors is purposefully avoided, though they are
 suitable for more precise measurements and extended measuring ranges.
@@
 #define __CustomSensor_h__
-// register your custom sensor in implemented_sensors.h also
+// register custom sensor in implemented_sensors.h also
 class CustomSensor: public baseSensor
@@
 
-The parameter *\_readings* should later receive the imported
-measurements from the \emph{stage rawimport}
-\ref{lst:pipeline_mrp_evaluation_yaml} and the optional
-\emph{IP\_return\_count} parameter specifies the number of best
-measurements that are returned. The return parameter is a list of
-measurements containing the most similar measurements, measured by the
-smallest distance between all measurements. The distance for each
+The parameter \_readings should later receive the imported measurements
+from the \emph{stage rawimport} \ref{lst:pipeline_mrp_evaluation_yaml}
+and the optional \emph{IP\_return\_count} parameter specifies the number
+of best measurements that are returned. The return parameter is a list
+of measurements containing the most similar measurements, measured by
+the smallest distance between all measurements. The distance for each
 measurement is determined using the centre of gravity function
@@
 field interference. The temperature chamber for all noise tests is set
-to \(\mu_{trev}\)=21.0\(^{\circ}\) and the sensors are placed \emph{24}
-hours before the measurement run in the final measurement configuration
-inside of the chamber.
+to \emph{\(\mu_{trev}\)=21.0\(^{\circ}\)} and the sensors are placed
+\emph{24} hours before the measurement run in the final measurement
+configuration inside of the chamber.
 
@@
 size of \emph{N=10000} measured values is recorded for the baseline
-measurement.
-
-The output signal of the sensor is continuously measured and recorded.
-It is important to carry out the measurement over a sufficiently long
-period of time in order to record both short-term and long-term
-fluctuations. For this purpose, \emph{N=2000} further measured values
-are taken with a trigger and readout rate of one measurement per second.
-
-In order to quantify the noise, the \gls{sd} of the signal is
+measurement. The output signal of the sensor is continuously measured
+and recorded. It is important to carry out the measurement over a
+sufficiently long period of time in order to record both short-term and
+long-term fluctuations. For this purpose, \emph{N=2000} further measured
+values are taken with a trigger and readout rate of one measurement per
+second. In order to quantify the noise, the \gls{sd} of the signal is
 calculated. These parameters provide information about the variation of
@@
 The temperature stability of the \emph{TLV493D} with a mean value of
-20.68\(^{\circ}\)C and a \gls{sd} of \(\sigma_{t}\)=0.53\(^{\circ}\)C
-indicates a consistent trend. This implies a constant tendency. The
-close grouping of the measured values around the mean value indicates
-good stability. The confidence interval is expected to be between
-20.15\(^{\circ}\)C and 21.21\(^{\circ}\)C, which indicates a stable and
-consistent temperature measurement. This result is more noisy compared
-to the temperature stability of the \emph{MMC5603}.
-
-Both sensors provide an offset to the measured chamber temperature
-\(\mu_{trev}\).
+\emph{20.68\(^{\circ}\)C} and a \gls{sd} of
+\emph{\(\sigma_{t}\)=0.53\(^{\circ}\)C} indicates a consistent trend.
+This implies a constant tendency. The close grouping of the measured
+values around the mean value indicates good stability. The confidence
+interval is expected to be between \emph{20.15\(^{\circ}\)C} and
+\emph{21.21\(^{\circ}\)C}, which indicates a stable and consistent
+temperature measurement. This result is more noisy compared to the
+temperature stability of the \emph{MMC5603}. Both sensors provide an
+offset to the measured chamber temperature \(\mu_{trev}\).
 
 With an additional measurement run with a different temperature setting
-of 30.0\(^{\circ}\)C, the measured temperature deviations and offsets
-remains constant.
+of \emph{30.0\(^{\circ}\)C}, the measured temperature deviations and
+offsets remains constant.
 
@@
 values and calibration of the sensor. This is considered in section
-\emph{Temperature Sensitivity} \ref{temperature-sensitivity}.
+\emph{Temperature Sensitivity}
+\ref{sensor-characterisation-temperature-sensitivity}.
 
@@
 
-In the raw data plot, as well as its mean value \(\mu_{rv}\) of both
-sensors, an offset can also be recognised, which is dependent on the
-ambient conditions. For verification, a reference measurement of the
+The noise of a sensor describes unwanted, random fluctuations or signals
+in the measured data. These are clearly recognisable in the figure ** in
+the raw data plot. The baseline determined for each sensor is shown by
+the red ** line. Here it can be seen that each sensor has a different
+mean value or baseline offset in the same environment.
+
+The noise of a sensor describes unwanted, random fluctuations or signals
+in the measured data. These are clearly recognisable in the figure
+\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
+in the raw data plot. The baseline determined for each sensor is shown
+by the red \(\mu_{rv}\) {[}\(\mu\)T{]} line. Here can be seen that each
+sensor has a different mean value or baseline offset in the same
+environment. For verification, a reference measurement of the
 environment is carried out with the calibrated \emph{Voltcraft GM70}
-Telsameter next to the sensor \gls{ic} This provides a \emph{real}
-baseline value of \(\mu_{rev}\)=-21\(\mu\)T.
+Telsameter next to the sensor \gls{ic}. This provides a reference
+baseline value of \emph{\(\mu_{rev}\)=-21.0\(\mu\)T}.
+
+The noise of the sensor is drawn around this using the blue line. For
+the \emph{TLV493D} the \gls{sd} \emph{\(\sigma_{rv}\)=172.0\(^{\mu}\)T},
+which is twice the value given by the datasheet as the noise value.
+Under the same conditions, the \emph{MMC5603NJ} undercuts the value
+specified by the manufacturer. The \gls{sd} approaches
+\emph{\(\sigma_{rv}\)=0.20\(^{\mu}\)T} and is negligible, especially
+when additional averaging is used.
+
+As the baseline was determined first for each sensor, it can be seen
+that the Another recognisable feature is Further measurement series were
+also recorded with inserted \emph{N45 12x12x12mm} magnets, so that these
+are saturated halfway through the measurement range. This allows the
+noise measurement values to be compared with a blank measurement. These
+values correspond, so it can be concluded that the noise is within the
+same range across the measuring range.
 
@@
 different distances above the respective sensor \gls{ic}. The ambient
-temperature is set to \(\mu_{trev}\)=21.0\(^{\circ}\) in the measurement
-runs and thus corresponds to the same conditions as in the
+temperature is set to \emph{\(\mu_{trev}\)=21.0\(^{\circ}\)} in the
+measurement runs and thus corresponds to the same conditions as in the
 \emph{Background-Noise}\ref{sensor-characterisation-background-noise}
@@
 \item
-  Create measurement using \emph{MRPCli} with N=2000 data points per
-  reading
+  Create measurement using \emph{MRPCli} with \emph{N=2000} data points
+  per reading
 \item
@@
 
-For both sensors, the deviation is less than 1\% over the entire
+For both sensors, the deviation is less than \emph{1\%} over the entire
 resolution. With the \emph{MMC5603NJ} this is on average only
@@
 of moving the linear axis, the temperature of the temperature chamber is
-systematically increased from 20\(^{\circ}\) to 50\(^{\circ}\). Between
-each of these temperature changes, the system is given a waiting time of
-30 minutes after reaching the target temperature.
+systematically increased from \emph{20\(^{\circ}\)} to
+\emph{50\(^{\circ}\)}. Between each of these temperature changes, the
+system is given a waiting time of 30 minutes after reaching the target
+temperature.
 
@@
 lose its magnetisation at higher temperatures (typically
-\textgreater=80\(^{\circ}\) for non-high-quality type N magnets
+\emph{\textgreater=80\(^{\circ}\)} for non-high-quality type N magnets
 \cite{magna-c}). The temperature range is selected so that it is
@@
 as the \emph{MMC5603NJ}; there are clear jumps in the gradient. However,
-the total change between the temperature regions of 175\(\mu\)T is less
-than that of the \emph{MMC5603NJ} with 70\(\mu\)T, if the total
-measurement range of the sensors is also taken into account.
+the total change between the temperature regions of \emph{175\(\mu\)T}
+is less than that of the \emph{MMC5603NJ} with \emph{70\(\mu\)T}, if the
+total measurement range of the sensors is also taken into account.
 
@@
 
-The \emph{TLV493D} performs seriously in the Senosr Noise measurement
-and also performs worse than specified in the data sheet (98\(\mu\)T
-instead of 175\(\mu\)T), but the large measuring range, which fulfils
-the required specifications from chapter \emph{Research Question}
+The \emph{TLV493D} performs in noise measurements worse than specified
+in the data sheet (\emph{98\(\mu\)T} instead of \emph{175\(\mu\)T}), but
+the large measuring range, which fulfils the required specifications
+from chapter \emph{Research Question}
 \ref{research-question-and-approach}, must be taken into account here,
@@
 However, due to the limited measuring range of \emph{±3mT}, direct
-measurement of stronger magnets is not possible. The \emph{N45
-12x12x12mm} magnets used in the application typically have a field
-strength of around \emph{100mT} at a distance of \emph{10mm}.
-
-The \emph{TLV493D}, on the other hand, is able to measure these
-directly, but does not achieve the required accuracy due to strong noise
-and steep temperature coefficients.
-
-In the following chapter, recommendations for action are defined, which
-were derived from the analysis results.
+measurement of stronger magnets is not possible using the
+\emph{MMC5603NJ}. The \emph{N45 12x12x12mm} magnets used in the
+application typically have a field strength of around \emph{100mT} at a
+distance of \emph{10mm} which is more than the \emph{MMC5603NJ} can
+measure.
+
+The \emph{TLV493D}, on the other hand, is able to measure these ranges,
+but does not achieve the required accuracy due to strong noise and steep
+temperature coefficients. In the following chapter, recommendations for
+action are defined, which were derived from the analysis results.
 
@@
 calibration, it is probably possible to reduce the noise to below
-50\(\mu\)T with the \emph{TLV493D}. As a test, several further
+\emph{50\(\mu\)T} with the \emph{TLV493D}. As a test, several further
 measurement runs were carried out, which achieved results for the sensor
-noise of 71\(\mu\)T to 41\(\mu\)T when averaging \emph{100} measured
-values and \emph{1000} measured values. However, further measurement
-runs must be carried out to verify these results.
+noise of \emph{71}\(\mu\)T* to \emph{41\(\mu\)T} when averaging
+\emph{100} measured values and \emph{1000} measured values. However,
+further measurement runs must be carried out to verify these results.
 
@@
 in the case of changing measurement conditions (e.g.~movement of the
-sensor in the B0 field).
+sensor in the \emph{B0} field).
 

### 2024-02-16 documentation/thesis/thesis_document.tex
.

@@
 
-The Python \emph{heapq} \cite{heapq} module, which implements a
-priority queue, is used for this purpose. The calculated distances from
-the \emph{CoG} value of the measurements to are inserted into this
-queue. Subsequently, as many elements of the queue are returned as
-defined by the \emph{IP\_return\_count} parameter. The actual sorting is
-carried out by the queue in the background.
+The calculated distances from the \emph{CoG} value of the measurements
+to are inserted into a heapq priority queue. Subsequently, as many
+elements of the queue are returned as defined by the
+\emph{IP\_return\_count} parameter. The actual sorting is carried out by
+the queue in the background.
 
@@
 of a \emph{Voron 2.4} 3D printer, which has a separately controlled
-internal heating system, is used as the temperature chamber. To verify
-the temperature, an additional thermometer \emph{VC-7055BT} is placed on
-the base plate. A \emph{10mm} thick \emph{PTFE} insulation plate is
-placed between the floor and the sensor base plate to prevent direct and
-uneven heating of the base plate by the heated floor.
+internal equipped heating system, is used as the temperature chamber. To
+verify the temperature, an additional thermometer \emph{VC-7055BT} is
+placed on the base plate. A \emph{10mm} thick \emph{PTFE} insulation
+plate is placed between the floor and the sensor base plate to prevent
+direct and uneven heating of the base plate by the heated floor.
 

### 2024-02-16 documentation/thesis/thesis_document.tex
.

@@
 applications, articulates the research question driving this thesis and
-delineates the anticipated usecases and benefits that will be explored
+delineates the anticipated use cases and benefits that will be explored
 and analysed throughout the study.
@@
 analysis, and their data storage formats are not compatible with each
-other.
-
-The accompanying open-source software for this thesis is designed not
-only to facilitate measurements with different sensors but also to
+other. The accompanying open-source software for this thesis is designed
+not only to facilitate measurements with different sensors but also to
 enable the characterisation of different objects.
@@
 \centering
-\includegraphics{./generated_images/border_Example_Hallbach_ring_with_cutouts_for_eight_magnets.png}
-\caption{Example Hallbach ring with cutouts for eight magnets
-\label{Example_Hallbach_ring_with_cutouts_for_eight_magnets.png}}
+\includegraphics{./generated_images/border_Example_Halbach_ring_with_cutouts_for_eight_magnets.png}
+\caption{Example Halbach ring with cutouts for eight magnets
+\label{Example_Halbach_ring_with_cutouts_for_eight_magnets.png}}
 \end{figure}
@@
 A Halbach ring of this type is usually based on a ring with permanent
-magnets arranged in a circle. The graphic
-\ref{Example_Hallbach_ring_with_cutouts_for_eight_magnets.png} shows an
-example \gls{cad} model of such a ring, in which in this case eight
+magnets arranged in a circle. The figure
+\ref{Example_Halbach_ring_with_cutouts_for_eight_magnets.png} shows an
+example \gls{cad} model of such a ring. In this generated model eight
 cubic \emph{12x12x12mm} magnets are embedded to generate homogeneous
@@
 impressive homogeneity of \emph{2400}\gls{ppm} over a \emph{20cm}
-diameter using smaller magnets (\emph{12 x 12 x 12 mm\^{}3}). This
-exceptional homogeneity enables the utilization of coil-based gradients
-for spatial encoding, significantly enhancing the flexibility of image
-acquisition.
+diameter using smaller magnets (\(12 x 12 x 12 mm^3\)). This exceptional
+homogeneity enables the utilization of coil-based gradients for spatial
+encoding, significantly enhancing the flexibility of image acquisition.
 
@@
 
-\hypertarget{usecases}{%
-\section{Usecases}\label{usecases}}
-
-The following section defines possible usecases that the future project
-need to cover. These usecases define the setup of the hard- and
+\hypertarget{use-cases}{%
+\section{Use cases}\label{use-cases}}
+
+The following chapter defines possible use cases that the future project
+need to cover. These use cases define the setup of the hard- and
 software. These illustrate practical situations to understand the
@@
 
-The usecases are defined in the course of project planning and provide
+The use cases are defined in the course of project planning and provide
 an overview of how the user interacts with the project and what
 functionalities can be expected. In the later accomplished evaluation
-process \ref{usecase-evaluation}, the defined usecases are also used as
-a reference to demonstrate the implemented capabilities of the solution.
-This is essential for understanding the needs of the target group and
-designing the end result accordingly.
+process \ref{use-case-evaluation}, the defined use cases are also used
+as a reference to demonstrate the implemented capabilities of the
+solution. This is essential for understanding the needs of the target
+group and designing the end result accordingly.
 
@@
 
-Chapter \ref{usecase-evaluation}. \textbf{Usecase Evaluation} describes
-the application of the framework to the previously defined usecases and
-thus forms the basis for later evaluation.
+Chapter \ref{use-case-evaluation}. \textbf{Use Case Evaluation}
+describes the application of the framework to the previously defined use
+cases and thus forms the basis for later evaluation.
 
@@
 synthesizes study outcomes, discusses implications, and provides
-insights for future work. This section ensures closure and aids readers
+insights for future work. This chapter ensures closure and aids readers
 in grasping the broader context and significance of the research.
@@
 platform for the data evaluation \gls{mrp} library and provide real
-measurement data from magnets. In addition, the interface firmware
-creates a basis for the development of a data protocol for exchanging
-measured values.
-
-This makes it easy to integrate an own measuring devices into the
-\gls{mrp} ecosystem at a later date. This is only possible with a
-minimal functional hardware and firmware setup and is developed for this
-purpose first.
+measurement data from magnets. Further, the interface firmware creates a
+basis for the development of a data protocol for exchanging measured
+values.
+
+It simplifies of own measuring devices into the \gls{mrp} ecosystem at a
+later date. This is only applicable with a minimal functional hardware
+and firmware setup; it is developed for this purpose in the first step.
 
@@
 The firmware is responsible for detecting the possible connected sensors
-\ref{Implemented_digital_magnetic_field_sensors.csv} and query
-measurements. This measured data can be forwarded to a host \gls{pc} via
-a user interface and can then be further processed there.
+from table \ref{Implemented_digital_magnetic_field_sensors.csv} and
+query measurements. This measured data can be forwarded to a host
+\gls{pc} via a user interface and can then be further processed there.
 
@@
 according to the sensors found at startup. If new hardware is to be
-integrated, only the required functions \ref{lst:CustomSensorClass} need
-to be implemented.
+integrated, only the required functions from listing
+\ref{lst:CustomSensorClass} need to be implemented.
 
@@
 
-The flow chart
-\ref{Unified_sensor_firmware_simplified_program_structure.png} shows the
-start process and the subsequent main loop for processing the user
-commands and sensor results. When the microcontroller is started, the
-software checks whether known sensors are connected to \gls{i2c} or
-\gls{uart} interfaces.
+The figure
+\ref{Unified_sensor_firmware_simplified_program_structure.png} shows a
+flow chart of the start process after powering on the sensor and the
+subsequent main loop for processing the user commands and sensor
+results. When the microcontroller is started, the software checks
+whether known sensors are connected to \gls{i2c} or \gls{uart}
+interfaces.
 
@@
 The next initialisation system is dedicated for multi-sensor
-synchronisation \ref{sensor-syncronisation-interface}. The last step in
-the setup is to configure communication with the host or connected
-\gls{pc}. All implemented microcontroller platforms used
-(\emph{Raspberry Pi Pico}, \emph{STM32F4}) have a \gls{usb} slave port.
+synchronisation described in chapter
+\ref{sensor-syncronisation-interface}. The last step in the setup is to
+configure communication with the host or connected \gls{pc}. All
+implemented microcontroller platforms used (\emph{Raspberry Pi Pico},
+\emph{STM32F4}) have a \gls{usb} slave port.
 
@@
 ensures that in a multi-sensor setup with several sensors. The
-measurements are synchronized \ref{sensor-syncronisation-interface} in
-time and are not out of sequence or drift.
+measurements are synchronized in time and are not out of sequence or
+drift.
 
@@
 \item
-  Use with \gls{mrp} \ref{software-readout-framework}-library
+  Use with \gls{mrp}-library - see chapter
+  \ref{software-readout-framework}
 \item
@@
 behaves like terminal programmes, displaying a detailed command
-reference \ref{Sensors_(+cli).png} to the user after connecting. The
-current measured value can be output using the \emph{readout} command
-\ref{Query_sensors_b_value_using_(+cli).png}.
+reference as shown in the figure \ref{Sensors_(+cli).png} to the user
+after connecting. The figure
+\ref{Query_sensors_b_value_using_(+cli).png} shows the current measured
+value queried by using the \emph{readout} command by the user.
 
@@
 
-The other option is to use the \gls{mrp}
-\ref{software-readout-framework}-library. The serial interface is also
-used here. However, after a connection attempt by the \gls{hal}
-\ref{mrphal} module of the \gls{mrp}
-\ref{software-readout-framework}-library, the system switches to binary
-mode, which is initiated using the \emph{sbm} command. The same commands
-are available as for \gls{cli}-based communication, but in a binary
-format.
+The other option is to use the devloped \gls{mrp}-library from chapter
+\ref{software-readout-framework}. The serial interface is also used
+here. However, After a connection attempt by the \gls{hal} \ref{mrphal}
+module of the \gls{mrp}-library \ref{software-readout-framework} , the
+system switches to binary mode, which is initiated using the \emph{sbm}
+command. The same commands are available as for \gls{cli}-based
+communication, but in a binary format.
 
@@
 device drivers, data transfer speed and system resources. High-quality
-\gls{usb} devices and modern drivers often minimise latencies.
-Nevertheless, complex data processing tasks and overloaded \gls{usb}
-ports can lead to delays.
+\gls{usb} devices and modern drivers often minimise
+latencies.\cite{Wimmer2019} Nevertheless, complex data processing
+tasks and overloaded \gls{usb} ports can lead to delays.
 
@@
 \item
-  \gls{mrp} \ref{software-readout-framework}-library - Version
-  \emph{1.4.1}
-\item
-  Unified Sensor \ref{unified-sensor}-firmware - Version \emph{1.0.1}
+  \gls{mrp}-library (see chapter \ref{software-readout-framework}) -
+  Version \emph{1.4.1}
+\item
+  Unified Sensor-firmware - Version \emph{1.0.1}
 \end{itemize}
@@
 electrical connection between sensors. This is used together with the
-firmware to synchronise the readout intervals. The schematic
-\ref{Multi_sensor_synchronisation_wiring_example.png} shows how several
-sensors must be wired together in order to implement this form of
-synchronisation.
+firmware to synchronise the readout intervals. The figure
+\ref{Multi_sensor_synchronisation_wiring_example.png} illustrates the
+schematic how several sensors must be wired together in order to
+implement this form of synchronisation.
 
@@
 \emph{primary} and several \emph{secondary} sensors, each sensor waits
-for an initial pulse on the SYNC-\gls{gpio}
-\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
-Each sensor starts a random timer beforehand, which sends a pulse on the
-sync line. All others receive this and switch to \emph{secondary} mode
-and synchronise the measurements based on each sync pulse received.
+for an initial pulse on the SYNC-\gls{gpio}. A random timer is started
+beforehand by each sensor, which sends a pulse on the sync line. All
+others receive this and switch to \emph{secondary mode} and synchronise
+the measurements based on each sync pulse received.
 
@@
 sensor operation through the \emph{got impulse within 1000ms} branch
-result. The synchronisation status can be queried via the user interface
-\ref{communication-interface} using the \emph{opmode}
-\ref{Query_opmode_using_(+cli).png} command. An important aspect of the
-implementation here is that there is no numbering or sequence of the
-individual sensors.
+result. The figure \ref{Query_opmode_using_(+cli).png} shows the
+synchronisation status of the sensor which can be queried via the user
+interface described in chapter \ref{communication-interface} by using
+the \emph{opmode} command. An important aspect of the implementation
+here is that there is no numbering or sequence of the individual
+sensors.
 
@@
 only important that they are taken at the same interval across all
-sensors. The sensor differentiation takes place later in the \gls{mrp}
-\ref{software-readout-framework}-library by using the sensor \gls{uuid}.
+sensors. The sensor differentiation takes place later in the
+\gls{mrp}-library \ref{software-readout-framework} by using the sensor
+\gls{uuid}.
 
@@
 
-Two functional sensor platforms
-\ref{Build_sensors_with_different_capabilities.csv} are built in order
-to create a solid test platform for later tests and for the development
-of the \gls{mrp} \ref{software-readout-framework}-library with the
-previously developed sensor concepts.
+Two functional sensor platforms are built in order to create a solid
+test platform for later tests and for the development of the
+\gls{mrp}-library \ref{software-readout-framework} with the previously
+developed sensor concepts.
 
@@
 \endhead
-Maximal magnet size & Cubic 30x30x30 & Cubic 30x30x30 & Cubic
-20x20x20\tabularnewline
+Maximal magnet size & Cubic 30x30x30mm & Cubic 30x30x30mm & Cubic
+20x20x20mm\tabularnewline
 Sensor type & MMC5603NJ & TLV493D & TLV493D\tabularnewline
@@
 
-These cover all the required functions described in the usecases
-\ref{usecases}. The most important difference, apart from the sensor
-used, is the \emph{scan mode}. In this context, this describes whether
-the sensor can measure a \emph{static} fixed point on the magnet or if
-the sensor can move \emph{dynamically} around the magnet using a
+The table \ref{Build_sensors_with_different_capabilities.csv} shows the
+various prototype sensor platforms equipped with different magnetic
+field sensors. These cover all the required functions described in the
+use cases \ref{use-cases}. The most important difference, apart from the
+sensor used, is the \emph{scan mode}. In this context, this describes
+whether the sensor can measure a \emph{static} fixed point on the magnet
+or if the sensor can move \emph{dynamically} around the magnet using a
 controllable manipulator.
@@
 
-The 1D sensor
+The 1D sensor shown in figure
 \ref{1D_sensor_construction_with_universal_magnet_mount.png} is the
@@
 \centering
-\includegraphics{./generated_images/border_Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
-\caption{Full-Sphere sensor implementation using two Nema17 stepper
+\includegraphics{./generated_images/border_Full-sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
+\caption{Full-sphere sensor implementation using two Nema17 stepper
 motors in a polar coordinate system
-\label{Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}}
+\label{Full-sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}}
 \end{figure}
 
-The 3D full sphere sensor
-\ref{Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
+The 3D full sphere sensor shown in figure
+\ref{Full-sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
 offers the possibility to create a 3D map of the inserted magnet.
 
-The graphic
-\ref{3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}
+The figure
+\ref{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_3D_full-sphere_sensor.png}
 shows the visualisation of such a scan in the form of a spherical 3D
@@
 \centering
-\includegraphics{./generated_images/border_3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}
-\caption{3D plot of an N45 12x12x12 magnet using the 3D fullsphere
+\includegraphics{./generated_images/border_3D_plot_of_an_N45_12x12x12mm_magnet_using_the_3D_full-sphere_sensor.png}
+\caption{3D plot of an N45 12x12x12mm magnet using the 3D full-sphere
 sensor
-\label{3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}}
+\label{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_3D_full-sphere_sensor.png}}
 \end{figure}
@@
 As the sensors shown so far relate exclusively to self-built, low-cost
-hardware, the following section shows how existing hardware can be
+hardware, the following chapter shows how existing hardware can be
 integrated into the system. A temperature-compensated \emph{Voltcraft
-GM-70} telsameter
+GM-70} telsameter shown in figure
 \ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
@@
 This connectivity makes it possible to make the device compatible with
-the unified sensor ecosystem using a separate interface software
-\cite{VoltcraftGM70Rest} executable on the host \gls{pc}. However,
-it does not offer the range of functions that the unified sensor
-firmware offers.
+the unified sensor ecosystem using a separate
+\href{https://github.com/RBEGamer/VoltcraftGM70Rest}{interface software}
+executable on the host \gls{pc}. However, it does not offer the range of
+functions that the unified sensor firmware offers.
 
@@
 the data from the microcontroller, the serial protocol of the sensor is
-implemented in a customised version of the \emph{CustomSensor} class
-\ref{lst:CustomSensorClass}.
+implemented in a customised version of the \emph{CustomSensor} class as
+shown in listing \ref{lst:CustomSensorClass}.
 
@@
 \item
-  Data acquisition - from hardware sensors \ref{unified-sensor} or other
-  data sources
-\item
-  Storage - export of data in various open formats
+  Data acquisition - from hardware sensors or other data sources - see
+  chapter \ref{unified-sensor}
+\item
+  Storage - export of data in various open formats - see chapter
   \ref{storage-and-datamanagement}
 \item
-  Analysis - algorithms to analyse different data sets \ref{analysis}
+  Analysis - algorithms to analyse different data sets - see chapter
+  \ref{analysis}
 \end{itemize}
 
-All these possible task parts is divided into different blocks and users
-is given the possibility of adding their own functionalities.
-
-As the following, this concept is referred to as \emph{user interaction
-points} \ref{user-interaction-points} and is explained in the following
-chapter.
+All these steps are divided into different blocks with an editional
+functionality for users to add own modules. This concept is explained in
+the following chapter.
 
@@
 
-User interaction points represent the core concept of the developed
+User interaction points represent one core concept of the developed
 library and are intended to provide user-friendliness on the one hand
 and the rapid development of own analysis and optimisation algorithms on
-the other.
+the other. For this thesis it also eases the option to change sensors
+for measurments.
 
 For this purpose, the library is divided into individual modules, which
-are shown in the graphic
+are shown in the figure
 \ref{MRP_library_module_high_level_overview.png}. In combination, these
@@
 According to this concept, the user should be able to replace individual
-components from this chain with their own modules without having to
-worry about implementing other of these to make the project work.
+components from this chain with own modules without having to worry
+about implementing other of these to make the project work.
 
@@
 circular section using given mechanical dimensions as input parameters
-of the magnets used. For this purpose, a mutation of the magnet
-positions and rotations is performed. The result is a list of positions
-for each magnet.
-
-The \emph{HalbachMRIDesigner} \cite{HalbachMRIDesigner} opensource
-project, can generate basic \gls{cad} drawings for \gls{mri} magnets in
-a Halbach configuration. To do this, the number of magnets and
-additional parameters for the properties of the \gls{cad} model to be
-created are passed to the function provided as input parameters using a
-\gls{json} file. The result is an \emph{OpenSCAD} \cite{OpenSCAD}
+of the magnets which are used. For this purpose, a mutation of the
+magnet positions and rotations is performed. The result is a list of
+positions for each magnet.
+
+The \emph{HalbachMRIDesigner} \cite{HalbachMRIDesigner} is an
+opensource project and generates basic \gls{cad} drawings for \gls{mri}
+magnets in a Halbach configuration. To do this, the number of magnets
+and additional parameters for the properties of the \gls{cad} model to
+be created are passed to the function provided as input parameters using
+a \gls{json} file. The result is an \emph{OpenSCAD} \cite{OpenSCAD}
 based 3D model of the magnet holder.
@@
 
-The library created is intended to solve one problem by providing
-standardized and flexible data structures for use with this form of
+The library created is intended to solve this compatibility problem by
+providing standardized and flexible data structures with this format of
 magnetic field data. By separating the processing pipeline into defined
-sub-steps, it should be possible to make individual modules and as a
-result functionalities interchangeable by the user.
-
-The implementation of the same functionalities looks as follows after
-using the library:
+sub-steps, it is feasible to connect individual modules and as a result
+functionalities interchangeable by the user.
+
+The implementation of the same functionalities appears as the following
+by using the library:
 
@@
 \cite{HalbachMRIDesigner} project, which creates the \gls{cad} model
-of the magnet holder. The data can also be exported as files here. To
-make the project compatible, the function signatures are also adapted
-here. In this case, more changes are required, as the configuration file
-is loaded from the file system. This logic must be removed in order to
-use the added meta data in the input parameter instead.
-
-After these customisation steps, it is possible to execute both projects
-one after the other and all required configuration parameters are
+of the magnet holder. The data can also be exported as files. To make
+the project compatible, the function signatures are also adapted. In
+this case, more changes are required, as the configuration file is
+loaded from the file system. This logic needs to be removed in order to
+use the added meta data as input parameter instead.
+
+After these customisation steps, executing both projects one after the
+other is possible and all required configuration parameters are
 contained in the data structure looped through the individual steps as
@@
 which provide an overview of the basic functions in the \emph{Examples}
-\ref{examples} section, as well as further examples in the online
-documentation \cite{MagneticReadoutProcessingReadTheDocs}.
+\ref{examples} chapter, as well as further examples in the
+\href{https://magneticreadoutprocessing.readthedocs.io/en/latest/}{online documentation}.
 
@@
 Ideally, this should be human-readable and viewable with a simple text
-editor. This eliminates all binary-based formats such as the Python
-pickle built into Python.
+editor. This eliminates all binary-based formats such as the
+\href{https://docs.python.org/3/library/pickle.html}{Python-Pickle}
+package.
 
@@
 
-The following code snippet \ref{lst:json_export_format_example} shows
-the \gls{json} structure which is generated when a measurement that
-using the library is exported. It can be seen that by using the
-\gls{json} format, all measurement points and metadata are available in
-readable plain text.
+The following listing \ref{lst:json_export_format_example} shows an
+example \gls{json} structure which is generated when a measurement that
+using the library is dumped to the filesystem. It can be seen that by
+using the \gls{json} format, all measurement points and metadata are
+available in readable plain text.
 
@@
 
-The exported example \ref{lst:json_export_format_example} contains the
-following different object keys, which contain the following
-information:
+The exported example listing \ref{lst:json_export_format_example}
+contains different object keys, which contain the following information:
 
@@
 \item
-  \emph{MRPReadingSourceFullsphere} - for 3D sensors such as \emph{3D:
-  Fullsphere} \ref{d-fullsphere}
+  \emph{MRPReadingSourceFullSphere} - for 3D sensors such as \emph{3D:
+  Full Sphere} \ref{d-full-sphere}
 \end{itemize}
@@
 \item
-  \emph{MRPPolarVisualization} - fullsphere map plots
+  \emph{MRPPolarVisualization} - full sphere map plots
 \end{itemize}
@@
 requires measurement data with additionally set spatial coordinates.
-These can be generated automatically with the \emph{3D: Fullsphere}
-\ref{d-fullsphere} sensor, or the user must provide the spatial
+These can be generated automatically with the \emph{3D: Full Sphere}
+\ref{d-full-sphere} sensor, or the user must provide the spatial
 information from another source.
@@
 
-At the current described scenarios, it is only possible to detect and
+In the previouse described scenarios, it is only possible to detect and
 use sensors that are directly connected to the host \gls{pc}. It has the
@@
 queried. This information is added to the previously created \gls{lut}.
-Duplicate entries are summarised (see Table
+Duplicate entries are summarised (see table
 \ref{Sensor_capabilities_merging_algorithm.csv}) and returned to the
@@
 
-\begin{lstlisting}[language=bash, caption={MRPproxy REST enpoiint query examples}, label=lst:mtsc]
+\begin{lstlisting}[language=bash, caption={MRPproxy REST entrypoint query examples}, label=lst:mtsc]
 # QUERY Network-Proxy capabilities
@@
 used to manage the measurement data and can be imported and exported.
-The following example \ref{lst:mrpexample_reading} shows how a
+The following example listing \ref{lst:mrpexample_reading} shows how a
 measurement is created and measurement points are added in the form of
@@
 
-The example \ref{lst:mrpexample_simulation} illustrated the basic usage.
-Different variations of the \emph{generate\_reading} function offers the
-user additional parameterisation options, such as random polarisation
-direction or a defined centre-of-gravity vector. The data is generated
-in the background using the \emph{magpylib}
+The example listing \ref{lst:mrpexample_simulation} illustrated the
+basic usage. Different variations of the \emph{generate\_reading}
+function offers the user additional parameterisation options, such as
+random polarisation direction or a defined centre-of-gravity vector. The
+data is generated in the background using the \emph{magpylib}
 \cite{ortner2020magpylib} library according to the specified
@@
 reading = MRPSimulation.generate_reading(MagnetType.N45_CUBIC_12x12x12,_add_random_polarisation=True)
-# GENERATE A FULLSPHERE MAP READING
+# GENERATE A FULL SPHERE MAP READING
 reading_fullsphere = MRPSimulation.generate_random_full_sphere_reading()
@@
 a measurement. This is particularly helpful for full-sphere measurements
-recorded with the \emph{3D: Fullsphere} \ref{d-fullsphere} sensor. The
+recorded with the \emph{3D: Full sphere} \ref{d-full-sphere} sensor. The
 sub-module \emph{MRPPolarVisualisation} is specially designed for these.
@@
 \ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
-shows a plot of a fullsphere measurement. It is also possible to export
+shows a plot of a full sphere measurement. It is also possible to export
 the data from the \emph{MRPAnalysis} module graphically as diagrams. The
@@
 
-\begin{lstlisting}[language=Python, caption={MRPVisualisation example which plots a fullsphere to an image file}, label=lst:mrpexample_visualisation]
+\begin{lstlisting}[language=Python, caption={MRPVisualisation example which plots a full sphere to an image file}, label=lst:mrpexample_visualisation]
 from MRP import MRPPolarVisualization
@@
 
-The following example code \ref{lst:mrpexample_halbach}, shows how a
+The following example listing \ref{lst:mrpexample_halbach}, shows how a
 simple Halbach magnetic ring can be generated.
@@
 position and rotation offset according to the Halbach design and
-calculation scheme \cite{HallbachMagnetDesignPaper} using the
+calculation scheme \cite{HalbachOptimisation} using the
 \emph{MRPHalbachArrayGenerator} module.
@@
 generated. After computing the model using the \emph{OpenSCAD} \gls{cli}
-utility, the following model rendering
-\ref{Generated_Hallbach_array_with_generated_cutouts_for_eight_magnets.png}
+utility, the following model rendering shown in figure
+\ref{Generated_Halbach_array_with_generated_cutouts_for_eight_magnets.png}
 can be generated.
@@
 \centering
-\includegraphics{./generated_images/border_Generated_Hallbach_array_with_generated_cutouts_for_eight_magnets.png}
-\caption{Generated Hallbach array with generated cutouts for eight
+\includegraphics{./generated_images/border_Generated_Halbach_array_with_generated_cutouts_for_eight_magnets.png}
+\caption{Generated Halbach array with generated cutouts for eight
 magnets
-\label{Generated_Hallbach_array_with_generated_cutouts_for_eight_magnets.png}}
+\label{Generated_Halbach_array_with_generated_cutouts_for_eight_magnets.png}}
 \end{figure}
@@
 > ....
-> dump_to_file testreading_ID:525771256544952_SID:0_MAG:N45_CUBIC_12x12x12.mag.json
+> dump_to_file testreading_ID:525771256544952_SID:0_MAG:N45_CUBIC_12x12x12mm.mag.json
 \end{lstlisting}
@@
 enables the user to create and execute complex evaluation pipelines for
-measurement data without programming. The example
+measurement data without programming. The figure
 \ref{Example_measurement_analysis_pipeline.png} shows a typical
@@
 The signatures in the \emph{yaml} file are called using reflection and a
-real-time search of the loaded \emph{global()} functions symbol table
-\cite{PythonGlobalSymbolTable}. This system makes almost all Python
-functions available to the user. To simplify use, a pre-defined list of
-verified functions for use in pipelines is listed in the documentation
+real-time search of the loaded \emph{global()} functions
+\href{https://docs.python.org/3/library/functions.html#globals}{symbol table}.
+This system makes almost all Python functions available to the user. To
+simplify use, a pre-defined list of verified functions for use in
+pipelines is listed in the documentation
 \cite{MagneticReadoutProcessingReadTheDocs}. The following pipeline
@@
     IP_export_folder: ./readings/fullsphere/plots/
-    IP_plot_headline_prefix: Sample N45 12x12x12 magnets calibrated
+    IP_plot_headline_prefix: Sample N45 12x12x12mm magnets calibrated
 
@@
 which is particularly important when libraries are used by different
-users and for different usecases.
+users and for different use cases.
 
 During the development of the \gls{mrp}-library, test cases are also
-created for all important functionalities and usecases. The test
-framework \emph{PyTest} \cite{PyTest} is used for this purpose, as
-it offers direct integration in most \gls{ide}s (see
+created for all important functionalities and use cases. The test
+framework \emph{PyTest} \cite{Pajankar2017} is used for this
+purpose, as it offers direct integration in most \gls{ide}s (see
 \ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
@@
 excluding certain tests in certain build environment scenarios. Since
-all intended usecases are mapped using the test cases created, the code
+all intended use cases are mapped using the test cases created, the code
 of the test cases could later be used in slightly simplified variants
@@
 In the other scenario, the tests are to be carried out before a new
-release in the repository on the basis of \emph{Github Actions}
-\cite{GithubActions}. Here there is the possibility to host local
-runner software, which then has access to the hardware, but then a
-\gls{pc} must be permanently available for this task. Instead, the
-hardware sensors are simulated by software and executed via
-virtualisation on the systems provided by \emph{Github Actions}.
+release in the repository on the basis of
+\href{https://github.com/features/actions}{GithubActions}. Here there is
+the possibility to host local runner software, which then has access to
+the hardware, but then a \gls{pc} must be permanently available for this
+task. Instead, the hardware sensors are simulated by software and
+executed via virtualisation on the services systems.
 
@@
 programming language, there are several public package registry where
-users can provide their software modules. Here, \emph{PyPi}
-\cite{PyPI}
-\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}
-\cite{MagneticReadoutProcessingPyPI} is the most commonly used
-package registry and offers direct support for the package installation
-program \gls{pip} \ref{lst:setup_lib_with_pip}.
+users can provide their software modules. Here,
+\href{https://pypi.org}{PyPI} screenshot shown in figure
+\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png} is the most
+commonly used package registry and offers direct support for the package
+installation program \gls{pip} \ref{lst:setup_lib_with_pip}.
 
@@
 package in an isolated environment and then provide an installation
-\emph{wheel} archive. This can then be uploaded to the package registry.
-Since the \gls{mrp}-library requires additional Python dependencies,
-which cannot be assumed to be already installed on the target system,
-these must be installed prior to the actual installation. These can be
-specified in the library installation configuration \emph{setup.py}
-\ref{lst:setup_py_req} for this purpose.
+\href{https://peps.python.org/pep-0427/}{wheel} archive. This can then
+be uploaded to the package registry. Since the \gls{mrp}-library
+requires additional Python dependencies, which cannot be assumed to be
+already installed on the target system, these must be installed prior to
+the actual installation. These can be specified in the library
+installation configuration \emph{setup.py} \ref{lst:setup_py_req} for
+this purpose.
 
@@
 In order to provide comprehensive documentation for the enduser, the
-source code is documented using Python-\emph{docstrings}
-\cite{PythonDocstringReference} and the Python type annotations. The
-use of type annotations also simplifies further development, as modern
-\gls{ide}s can more reliably display possible methods to the user as an
-assistance. \ref{lst:pydocstring}
+source code is documented using
+Python-\href{https://peps.python.org/pep-0257/}{Docstrings} and the
+Python type annotations. The use of type annotations also simplifies
+further development, as modern \gls{ide}s can more reliably display
+possible methods to the user as an assistance. \ref{lst:pydocstring}
 
@@
 publication option is to host the documentation via online services such
-as \emph{ReadTheDocs} \cite{ReadTheDocs}, where users can make
+as \href{https://readthedocs.com}{ReadTheDocs}, where users can make
 documentation for typical software projects available to others.
 
-The documentation has also been uploaded to \emph{ReadTheDocs}
-\cite{MagneticReadoutProcessingReadTheDocs} and linked in the
-repository and on the overview page
+The documentation has also been uploaded to the
+\href{https://magneticreadoutprocessing.readthedocs.io/}{ReadTheDocs}
+service. The figure
 \ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
-on \emph{PyPi}.
+shows a screenshot of the start page, which also shows separate menu
+items for tutorials on the individual functionalities.
 
 The process of creating and publishing the documentation has been
-automated using \emph{GitHub Actions}, so that it is always
-automatically kept up to date with new features.
+automated using
+\href{https://github.com/features/actions}{GithubActions}, so that it is
+always automatically kept up to date with new features.
 
@@
 
-\hypertarget{usecase-evaluation}{%
-\chapter{Usecase Evaluation}\label{usecase-evaluation}}
+\hypertarget{use-case-evaluation}{%
+\chapter{Use Case Evaluation}\label{use-case-evaluation}}
 
 The practical application of the hardware and software framework is
-shown below. This is shown using the previously defined usecases
-\ref{usecases}. In the application example, various permanent magnets
+shown below. This is shown using the previously defined use cases
+\ref{use-cases}. In the application example, various permanent magnets
 are measured and then sorted according to their field strength. The
@@
 comprehensive characterisation of permanent magnets. These are
-previously described in the Usecases \ref{usecases} chapter. The
-developed framework not only offers a cost-effective and flexible
+previously described in the \emph{Use cases} \ref{use-cases} chapter.
+The developed framework not only offers a cost-effective and flexible
 hardware solution, but also enables customisation of the analysis
@@
 
-For the hardware setup, the 3D-Fullsphere\ref{d-fullsphere} sensor is
+For the hardware setup, the 3D-Full Sphere \ref{d-full-sphere} sensor is
 used for the evaluation of the framework. As this is equipped with an
@@
 
-These are placed in modified 3D printed holders
+These are placed in modified 3D printed holders shown in figure
 \ref{Ten_numbered_test_magnets_in_separate_holders.png} and then
@@
 measurement is configured for an measurement run, using the following
-configuration commands \ref{lst:evaluation_measurement_config}.
+configuration commands from listing
+\ref{lst:evaluation_measurement_config}.
 
@@
 > OUTPUT-FOLDER: ./readings/evaluation/ 
-> NUMBER DATAPOINTS: 18 # FOR A FULLSPHERE READING USE MULTIBLE OF 18
+> NUMBER DATAPOINTS: 18 # FOR A FULL SPHERE READING USE MULTIBLE OF 18
 > NUMBER AVERAGE READINGS PER DATAPOINT: 10
@@
 
-The \emph{MRPcli measure run} command is then called up for each
+The \emph{MRPcli measure ruxn} command is then called up for each
 individual magnet to execute a measurement. After each run, the
@@
 \ref{lst:custom_find_similar_values_algorithm_refmagnet} shows the
-modified filter algorithm code, with added *\_ref* input parameter for
-the reference measurement.
+modified filter algorithm code, with added \_ref input parameter for the
+reference measurement.
 
@@
 
-On the right-hand side
-\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png},
-the measured values are plotted as a result of the filter algorithm. As
-the \emph{IP\_return\_count} parameter is set to four, only the four
-most similar measurements are exported here. It can be seen from the
-plotted \emph{CoG} \(\mu\)T deviation values, that these are closest to
-an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal value is
-calculated with the function
+Also, the figure
+\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png}
+illustrates, the measured values are plotted as a result of the filter
+algorithm. As the \emph{IP\_return\_count} parameter is set to four,
+only the four most similar measurements are exported here. It can be
+seen from the plotted \emph{CoG} \(\mu\)T deviation values, that these
+are closest to an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal
+value is calculated with the function
 \emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
@@
 they correspond to the mechanical structure of the used hardware sensor
-\ref{d-fullsphere}.
+\ref{d-full-sphere}.
 
@@
 
-In the previous chapter \emph{Usecase Evaluation}
-\ref{usecase-evaluation} it is shown that the implementation of the
+In the previous chapter \emph{Use Case Evaluation}
+\ref{use-case-evaluation} it is shown that the implementation of the
 hardware and software framework for various magnetic field sensors is
@@
 
-The graphic
+The figure
 \ref{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
@@
 suitable to perform an ambient temperature compensation of measured
-values and calibration of the sensor. This is considered in section
+values and calibration of the sensor. This is considered in chapter
 \emph{Temperature Sensitivity}
@@
 with the developed framework. In particular, the use of analogue
-Hallbach sensors with separate bias voltage should be evaluated, as a
-simplified characterisation procedure can be applied due to the lack of
-a base offset.
+magnetic field sensors with separate bias voltage should be evaluated,
+as a simplified characterisation procedure can be applied due to the
+lack of a base offset.
 
@@
 can be performed using a defined measurement setup. This concept has
-already been successfully realised with implemented
+already been successfully implemented in chapter \emph{Example Sensors}
 \ref{example-sensors}, in particular \emph{1D: Single Sensor}
@@
 magnetic fields by scaling the measured values accordingly. This was
-shown in the chapter \emph{Usecase Evaluation} \ref{usecase-evaluation}
-by comparing and sorting different permanent magnets using these
-sensors.
+shown in the chapter \emph{Use Case Evaluation}
+\ref{use-case-evaluation} by comparing and sorting different permanent
+magnets using these sensors.
 
@@
 measurement runs were carried out, which achieved results for the sensor
-noise of \emph{71}\(\mu\)T* to \emph{41\(\mu\)T} when averaging
-\emph{100} measured values and \emph{1000} measured values. However,
-further measurement runs must be carried out to verify these results.
+noise of \emph{71\(\mu\)T} to \emph{41\(\mu\)T} when averaging
+\emph{100} to \emph{1000} measured values. However, further measurement
+runs must be carried out to verify these results.
 
@@
 documentation to make it easier to get started. Together with examples
-for various usecases, a user can quickly evaluate the framework.
+for various use cases, a user can quickly evaluate the framework.
 

### 2024-02-17 documentation/thesis/thesis_document.tex
.

@@
 
-As the following, the motivation for the development of this framework
+In the following, the motivation for the development of this framework
 is listed. The chapter provides a brief introduction into the problem
@@
 
-Magnetic Resonance Imaging \gls{mri} stands as a cornerstone in clinical
-diagnostics, utilizing the principles of nuclear magnetic resonance
-\gls{nmr} to generate cross-sectional black-and-white images of the
-body. This indispensable method plays a central role in contemporary
-medicine and research, contributing significantly to saving lives.
-Despite its widespread use, traditional \gls{mri} systems often rely on
-large, heavy, and expensive magnets to achieve the necessary homogeneity
-of the magnetic field for accurate imaging. \cite{Nitz2016}
+\gls{mri} stands as a cornerstone in clinical diagnostics, utilizing the
+principles of nuclear magnetic resonance \gls{nmr} to generate
+cross-sectional black-and-white images of the body. This indispensable
+method plays a central role in contemporary medicine and research,
+contributing significantly to saving lives. Despite its widespread use,
+traditional \gls{mri} systems often rely on large, heavy, and expensive
+magnets to achieve the necessary homogeneity of the magnetic field for
+accurate imaging. \customcite{NK16}
 
@@
 Permanent magnets generate a steady yet relatively weak magnetic field,
-electro magnets are energized by electrical currents, and
-superconducting electro magnets produce magnetic fields through electric
-induction. Regardless of the type, the primary objective is to create a
-homogeneous magnetic field within the \gls{mri}. The higher the
-homogeneity, the more accurate the measurements. This uniform magnetic
-field aligns the molecules within the body or object, setting the stage
-for a second magnetic system to stimulate these molecules for
-spin-measurements.
+electromagnets are energized by electrical currents and superconducting
+electromagnets produce magnetic fields through electric induction.
+Regardless of the type, the primary objective is to create a homogeneous
+magnetic field within the \gls{mri}. The higher the homogeneity, the
+more accurate the measurements. Homogeneity in composed \gls{mri} can be
+adapted using the shimming procedure which requires a lot of effort and
+is prone to errors. This uniform magnetic field aligns the molecules
+within the body or object, setting the stage for a second magnetic
+system to stimulate these molecules for spin-measurements.
 
@@
 kinds of irritations. O'Reilly and Teeuwisse and de Gans
-\cite{OReilly2019-rn} have already demonstrated low-cost and
-small-scale implementations with low-field \gls{mri} in 2021 calculating
-images of a head successfully.
-
-Permanent magnets, usually arranged in a circular ``Halbach array''
+\customcite{OTW19} have already demonstrated low-cost and small-scale
+implementations with low-field \gls{mri} in 2021 calculating images of a
+head successfully.
+
+Permanent magnets, usually arranged in a circular \emph{Halbach array}
 inside the \gls{mri}, are commonly used in low-field systems. However,
@@
 \gls{mri} systems by enhancing the accuracy of permanent magnet
-characterisation. The outcomes of this thesis provides insights into the
+characterisation. The outcome of this thesis provides insights into the
 selection and evaluation of sensors for future low-field \gls{mri}
@@
 the potential advantages and applications of low-field \gls{mri}
-systems. \cite{Nitz2016}
+systems. \customcite{NK16}
 
@@
 \emph{0.1T} and \emph{0.3T} compared to the usual \emph{1.5T} to
-\emph{3T} and above in high-field \gls{mri} scanners
-\cite{Hori2021-pt}.
+\emph{3T} and above in high-field \gls{mri} scanners \customcite{HH21}.
 
@@
 It also offers more cost-effective alternatives to high-field \gls{mri}
-systems \cite{Hori2021-pt}, cost reduction, a smaller device
-footprint, alleviated safety concerns and leading to diminished image
-resolution within clinically feasible scan durations.
-\cite{Arnold2023-cn}
+systems \customcite{HH21}, cost reduction, a smaller device footprint,
+alleviated safety concerns and leading to diminished image resolution
+within clinically feasible scan durations. \customcite{AFL23}
 
@@
 a limited \gls{snr} due to the constrained field strength.
-\cite{Nitz2016}
+\customcite{NK16}
 
@@
 constructing an \gls{mri} and is influencing the homogeneity of the
-\emph{B0} magnetic field. Halbach ring magnets
-\cite{Halbach1980DesignOP} have become a common design for low field
-\gls{mri} and \gls{nmr} systems \cite{cmr.a.20165}.
+\emph{B0} magnetic field. Halbach ring magnets \customcite{H80} have
+become a common design for low field \gls{mri} and \gls{nmr} systems
+\customcite{SB10}.
 
@@
 particularly attractive for larger magnets as their design has the best
-flux-to-mass ratio \cite{Wickenbrock_2021}.
+flux-to-mass ratio \customcite{WZC21}.
 
@@
   magnets from different production batches are compared.
-  \cite{inbook}
+  \customcite{BC16}
 \end{itemize}
@@
 per unit of magnetic mass, coupled with minimal stray fields. The term
-``Halbach Array'' (commonly known as ``magic rings'') denotes a precise
-configuration of permanent magnets designed to amplify magnetic flux on
-one side while concurrently mitigating or eliminating it on the opposite
-side. \cite{inbook}
-
-The Halbach magnetic array appears as a essential element for future
+\emph{Halbach Array} (commonly known as \emph{magic rings}) denotes a
+precise configuration of permanent magnets designed to amplify magnetic
+flux on one side while concurrently mitigating or eliminating it on the
+opposite side. \customcite{BC16}
+
+The Halbach magnetic array appears as an essential element for future
 Magnet characterisation. Based on this fact this thesis centres on
@@
 
-The shimming process is a essential step in magnetic resonance imaging
-\gls{mri} to ensure homogeneous magnetic fields for precise imaging.
-Shimming corrects irregularities in the static magnetic field that can
-be caused by external influences or internal system errors. This process
-optimizes field homogeneity, which is essential for high-resolution and
-artifact-free images \cite{10.3389/fphy.2021.704566}.
+The shimming process is an essential step in \gls{mri} to ensure
+homogeneous magnetic fields for precise imaging. Shimming corrects
+irregularities in the static magnetic field that can be caused by
+external influences or internal system errors. This process optimizes
+field homogeneity, which is essential for high-resolution and
+artifact-free images \customcite{WAH21}.
 
@@
 magnets or magnets that can be effortlessly opened without applying
-force. \cite{inbook}
+force. \customcite{BC16}
 
@@
 Hardware shimming involves the use of gradient and radio frequency coils
-that are specifically placed to align the magnetic field. Software
-shimming, on the other hand, uses algorithms to adjust the control
-parameters of the \gls{mri} system and improve homogeneity
-\cite{10.3389/fphy.2021.704566}.
+that are specifically placed to align the magnetic field.
+\customcite{BPA22} Software shimming, on the other hand, uses algorithms
+to adjust the control parameters of the \gls{mri} system and improve
+homogeneity \customcite{WAH21}.
 
@@
 systems, 20\% 3.0 T system, 14.4\% low field with \textless0.5T}).
-\cite{Nitz2016}
+\customcite{NK16}
 
@@
 homogeneous \emph{27cm} diameter Bore Halbach Array magnet''
-\cite{OReilly2019-rn} in 2019.This innovative setup is subsequently
-employed in 2020 to acquire in vivo MR images, showcasing the practical
-applications of their pioneering research \cite{OReilly2021-ep}. In
-2023, de Vos, Remis and Webb published a summary of the design of a
-point-of-care Halbach array low-field \gls{mri} system
-\cite{De_Vos2023-pb}.
+\customcite{OTW19} in 2019.This innovative setup is subsequently employed
+in 2020 to acquire in vivo MR images, showcasing the practical
+applications of their pioneering research \customcite{OTW21}. In 2023, de
+Vos, Remis and Webb published a summary of the design of a point-of-care
+Halbach array low-field \gls{mri} system \customcite{DRW23}.
 
@@
 groundbreaking ``three-dimensional \gls{mri} in a homogeneous 27cm
-diameter Bore Halbach Array magnet'' \cite{OReilly2019-rn} in 2019.
-This innovative setup is subsequently employed in 2020 to acquire in
-vivo MR images, showcasing the practical applications of their
-pioneering research \cite{OReilly2021-ep}. In 2023, de Vos, Remis
-and Webb published a summary of the design of an oint-of-care halbach
-array low-field \gls{mri} system \cite{De_Vos2023-pb}.
+diameter Bore Halbach Array magnet'' \customcite{OTW19} in 2019. This
+innovative setup is subsequently employed in 2020 to acquire in vivo MR
+images, showcasing the practical applications of their pioneering
+research \customcite{OTW21}. In 2023, de Vos, Remis and Webb published a
+summary of the design of a point-of-care Halbach array low-field
+\gls{mri} system \customcite{DRW23}.
 
@@
 recorded. This data is then evaluated in separate software
-\cite{Wickenbrock_2021}.
+\customcite{WZC21}.
 
@@
 is currently being implemented experimentally in projects using various
-algorithms \cite{Wickenbrock_2021}. Standard sorting algorithms are
-used as well as specialized algorithms for optimizing homogeneity by
-rotating the individual magnets in a Halbach ring relative to each other
-\cite{HalbachMRIDesigner}.
+algorithms \customcite{WZC21}. Standard sorting algorithms are used as
+well as specialized algorithms for optimizing homogeneity by rotating
+the individual magnets in a Halbach ring relative to each other
+\customcite{MWO24}.
 
@@
 
-Special algorithms from various projects are used to optimize
-homogeneity. The challenge here is to ensure the seamless integration
-and compatibility of these algorithms into the overall process. This
-should make it possible to create a workflow from the individual magnet
-to the finished optimized \gls{cad} model of a halbach ring.
+Special algorithms from various, public projects are used to optimize
+homogeneity, like a genetic algorithms which O'Reilly implemented
+\customcite{O24}. Therefore, the challenge is to ensure the seamless
+integration and compatibility of these algorithms into the overall
+process. This should make it possible to create a workflow from the
+individual magnet to the finished optimized \gls{cad} model of a Halbach
+ring.
 
@@
 
-In addition \emph{DeLoRI} efforts to achieve heightened accuracy,
+In addition, \emph{DeLoRI} efforts to achieve heightened accuracy,
 striving for precision levels below 1000\gls{ppm}. While O'Reilly,
 Teeuwisse, and Webb were able to modify the ring diameter to influence
-field homogeneity, the unique goal here is to characterize the magnets
-pre-installation, allowing for proactive assessments of homogeneity
-characteristics. This approach aims to provide insights into magnetic
-field uniformity before the magnets are integrated, thereby streamlining
-the optimisation process. Furthermore,
+field homogeneity, the unique goal at this point is to characterize the
+magnets pre-installation, allowing for proactive assessments of
+homogeneity characteristics. This approach aims to provide insights into
+magnetic field uniformity before the magnets are integrated, thereby
+streamlining the optimisation process. Furthermore,
 
@@
 functionalities can be expected. In the later accomplished evaluation
-process \ref{use-case-evaluation}, the defined use cases are also used
-as a reference to demonstrate the implemented capabilities of the
-solution. This is essential for understanding the needs of the target
-group and designing the end result accordingly.
+process in chapter \ref{use-case-evaluation}, the defined use cases are
+also used as a reference to demonstrate the implemented capabilities of
+the solution. This is essential for understanding the needs of the
+target group and designing the end result accordingly.
 
@@
 possible for the user to analyse and visualize this data using various
-algorithms. The focus here should be on extending the framework with
-user-created algorithms.
+algorithms. The focus at this point should be on extending the framework
+with user-created algorithms.
 
@@
 \item
-  \textbf{User programmable data processing pipelines}
+  \textbf{User-programmable data processing pipelines}
 \end{enumerate}
@@
 not only be economically attractive, but also facilitate the integration
-of magnetic field sensors in different contexts.
+of magnetic field sensors in different contexts like for compasses or
+other devices.
 
@@
 The selection process for possible magnetic field sensors initially
-focussed on the most common and cost-effective ones, especially those
+focisses on the most common and cost-effective ones, especially those
 that are already used in smartphones and are therefore widely available.
@@
 digital interfaces to facilitate implementation in the circuit layout
-since these kind of sensors are easy to integrate compared to
+since these kinds of sensors are easy to integrate compared to
 non-digital sensors, which require specific frameworks. The integration
@@
 \begin{longtable}[]{@{}lllll@{}}
-\caption{Implemented digital magnetic field sensors
-\label{Implemented_digital_magnetic_field_sensors.csv}}\tabularnewline
+\caption{List of in unified firmware implemented digital magnetic field
+sensors with focus on different sensor capabilities
+\label{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}}\tabularnewline
 \toprule
@@
 
-The table \ref{Implemented_digital_magnetic_field_sensors.csv} shows a
-selection of sensors for which hardware and software support has been
-implemented. The resolution of the selected sensors covers the expected
-range of values required by the various magnets to be tested.
-
-In the Evaluation \ref{evaluation} chapter, basic characterisation
-methods are used to evaluate the sensors listed in
-\ref{Implemented_digital_magnetic_field_sensors.csv} with regard to
-their sensitivity and other parameters. This is done at this point, as
-the components of the readout interface that enable interaction with the
-sensors are considered first.
+The table
+\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
+shows a selection of sensors for which hardware and software support has
+been implemented. The resolution of the selected sensors covers the
+expected range of values required by the various magnets to be tested.
+
+In the \emph{Evaluation} in chapter \ref{evaluation} basic
+characterisation methods are used to evaluate the sensors listed in
+table
+\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
+with regard to their sensitivity and other parameters. This is done at
+this point, as the components of the readout interface that enable
+interaction with the sensors are considered first.
 
@@
 \centering
-\includegraphics{./generated_images/border_Mechanical_components_for_the_1D_sensor_using_3D_printed_parts.png}
-\caption{Mechanical components for the 1D sensor using 3D printed parts
-\label{Mechanical_components_for_the_1D_sensor_using_3D_printed_parts.png}}
+\includegraphics{./generated_images/border_Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png}
+\caption{Rendered mechanical structure of the 1D sensor \gls{cad} model
+with different parts colored separately, and universal magnet mount
+shown in green
+\label{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png}}
 \end{figure}
@@
 
-The following figure
-\ref{Mechanical_components_for_the_1D_sensor_using_3D_printed_parts.png},
-shows a sectional view of the \gls{cad} drawing of the 1D-Single sensor
-\ref{d-single-sensor}.
-
-All parts are produced using the 3D printing additive manufacturing
-processes. The sensor circuit board is glued underneath the magnet
-holder. This is interchangeable, so different distances between sensor
-and magnet can be realised.
-
-The exchangeable magnetic holder (shown in green) can be adapted to
-different magnets. It can be produced quickly due to the small amount of
-parts used. The two recesses lock the magnet holder with the inserted
-magnet over the sensor. The specified tolerances allow the magnet to be
-inserted into the holder with repeat accuracy and without backlash. This
-is important if several magnets have to be measured, where the
-positioning over the sensor must always be the same.
+Figure
+\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png},
+shows rendered view of the 1D-Single sensor \gls{cad} drawing, which is
+described in chapter \ref{d-single-sensor}.
+
+All parts are produced using 3D printing additive manufacturing proces.
+The sensor circuit board is glued underneath the magnet holder. This is
+interchangeable, so different distances between sensor and magnet can be
+realised.
+
+The exchangeable magnetic holder (shown in green in figure
+\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
+can be adapted to different magnets. It can be produced quickly due to
+the small number of parts used. The two recesses lock the magnet holder
+with the inserted magnet over the sensor. The specified tolerances allow
+the magnet to be inserted into the holder with repeat accuracy and
+without backlash. This is important if several magnets have to be
+measured, where the positioning over the sensor must always be the same.
 
@@
 \centering
-\includegraphics{./generated_images/border_1D_sensor_schematic_and_circuit_board.png}
-\caption{1D sensor schematic and circuit board
-\label{1D_sensor_schematic_and_circuit_board.png}}
+\includegraphics{./generated_images/border_1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}
+\caption{1D sensor schematic using an Raspberry Pi Pico with a TLV493D
+footprint in the center
+\label{1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}}
 \end{figure}
@@
 for basic operation. This not only enabled a time-saving implementation,
-but also ensured a cost-efficient realisation.
+but also ensured a cost-efficient realisation. A \emph{Raspberry Pi
+Pico} and a \emph{STM32F4} are used as an computer-sensor interface for
+this thesis, which are populare, cost-effective and simple to implement.
 
 All the necessary components and their circuitry are recorded on a
-\gls{pcb} \ref{1D_sensor_schematic_and_circuit_board.png} and
-subsequently manufactured. In addition, footprints are provided for
+\gls{pcb} shown in figure
+\ref{1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}
+and subsequently manufactured. In addition, footprints are provided for
 various sensor \gls{ic} packages. By placing mounting holes on the
 \gls{pcb}, it is possible to attach various mechanical mounts on top of
-the sensor \gls{ic}s.
+the sensor \gls{ic}s. These hole are necessary for later adaptions and
+sensor changes, such as different magnet holders or measurement
+equipment (e.g.~temperature sensors).
 
@@
 SYNC-\gls{gpio} connector. This enables subsequent multi-sensor
-synchronization and also offers options for later extensions. This
-functionality opens up the possibility of synchronising data from
+synchronization and also offers options for later sensor-extensions.
+This functionality opens up the possibility of synchronising data from
 different sensors to achieve precise and coherent measurement results.
@@
 \centering
-\includegraphics{./generated_images/border_Unified_sensor_firmware_simplified_program_structure.png}
-\caption{Unified sensor firmware simplified program structure
-\label{Unified_sensor_firmware_simplified_program_structure.png}}
+\includegraphics{./generated_images/border_Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}
+\caption{Unified sensor firmware program structure with listed setup and
+main loop routines using simplified function blocks
+\label{Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}}
 \end{figure}
@@
 The firmware is responsible for detecting the possible connected sensors
-from table \ref{Implemented_digital_magnetic_field_sensors.csv} and
-query measurements. This measured data can be forwarded to a host
+shown in table
+\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
+and query measurements. This measured data can be forwarded to a host
 \gls{pc} via a user interface and can then be further processed there.
@@
 is implemented using abstract class design. These are initiated
-according to the sensors found at startup. If new hardware is to be
-integrated, only the required functions from listing
+according to the sensors found at startup. If new hardware needs to be
+integrated, only the required functions in listing
 \ref{lst:CustomSensorClass} need to be implemented.
 
-\begin{lstlisting}[language={C++}, caption={CustomSensor-Class for adding new sensor hardware support}, label=lst:CustomSensorClass]
+\begin{lstlisting}[language={C++}, caption={CustomSensor-Class for adding new sensor hardware support into the unified sensor firmware package}, label=lst:CustomSensorClass]
 #ifndef __CustomSensor_h__
@@
 The figure
-\ref{Unified_sensor_firmware_simplified_program_structure.png} shows a
-flow chart of the start process after powering on the sensor and the
-subsequent main loop for processing the user commands and sensor
+\ref{Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}
+shows a flow chart of the start process after powering on the sensor and
+the subsequent main loop for processing the user commands and sensor
 results. When the microcontroller is started, the software checks
@@
 
-The used usb descriptor is a \gls{usb} \gls{cdc}. This is used to
-emulate a virtual \emph{RS232} communication port using a \gls{usb} port
-on a \gls{pc} and usually no additional driver is needed on modern host
+The used usb descriptor is a (+usb)-\gls{cdc}. This is used to emulate a
+virtual \emph{RS232} communication port using a \gls{usb} port on a
+\gls{pc} and usually no additional driver is needed on modern host
 systems.
@@
 host. Each sensor measurement result is transmitted from the buffer to
-the host together with a time stamp and a sequential number. This
-ensures that in a multi-sensor setup with several sensors. The
-measurements are synchronized in time and are not out of sequence or
+the host together with a time stamp and a sequential number.
+
+This ensures that in a multi-sensor setup with several sensors. The
+measurements are synchronized in time like described in chapter
+\ref{sensor-syncronisation-interface} and are not out of sequence or
 drift.
@@
 \centering
-\includegraphics{./generated_images/border_Sensors_(+cli).png}
-\caption{Sensors \gls{cli} \label{Sensors_(+cli).png}}
+\includegraphics{./generated_images/border_Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
+\caption{Unified sensor firmware provided serial terminal based
+\gls{cli} allows the user to configure the sensor manually
+\label{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}}
 \end{figure}
@@
 \item
-  Use with \gls{mrp}-library - see chapter
+  Use with \gls{mrp}-library, explained in chapter
   \ref{software-readout-framework}
@@
 behaves like terminal programmes, displaying a detailed command
-reference as shown in the figure \ref{Sensors_(+cli).png} to the user
-after connecting. The figure
-\ref{Query_sensors_b_value_using_(+cli).png} shows the current measured
-value queried by using the \emph{readout} command by the user.
+reference as shown in the figure
+\ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
+to the user after connecting. The figure
+\ref{Result_of_an_executed_b_field_query_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
+shows the current measured value queried by using the \emph{readout}
+command by the user.
 
@@
 \centering
-\includegraphics{./generated_images/border_Query_sensors_b_value_using_(+cli).png}
-\caption{Query sensors b value using \gls{cli}
-\label{Query_sensors_b_value_using_(+cli).png}}
+\includegraphics{./generated_images/border_Result_of_an_executed_b_field_query_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
+\caption{Result of an executed b field query using the sensors \gls{cli}
+with immediate user readable response
+\label{Result_of_an_executed_b_field_query_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}}
 \end{figure}
 
-The other option is to use the devloped \gls{mrp}-library from chapter
-\ref{software-readout-framework}. The serial interface is also used
-here. However, After a connection attempt by the \gls{hal} \ref{mrphal}
-module of the \gls{mrp}-library \ref{software-readout-framework} , the
-system switches to binary mode, which is initiated using the \emph{sbm}
-command. The same commands are available as for \gls{cli}-based
-communication, but in a binary format.
+The other option is to use the \gls{mrp}-library explained in chapter
+\ref{software-readout-framework}. The serial interface is also used at
+this point. However, after a connection attempt by the \gls{hal} module
+(explained in chapter \ref{mrphal}) of the \gls{mrp}-library (explained
+in chapter \ref{software-readout-framework}), the system switches to
+binary mode, which is initiated using the \emph{sbm} command. The
+command is only sent by the library, not by the user. The same commands
+are available as for \gls{cli}-based communication, but in a binary
+format.
 
@@
 \centering
-\includegraphics{./generated_images/border_Multi_sensor_synchronisation_wiring_example.png}
-\caption{Multi sensor synchronisation wiring example
-\label{Multi_sensor_synchronisation_wiring_example.png}}
+\includegraphics{./generated_images/border_Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
+\caption{Multi sensor synchronisation wiring example using three sensors
+together with one host \gls{pc} performing the triggering and readout
+processing
+\label{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}}
 \end{figure}
@@
 \gls{usb} devices and modern drivers often minimise
-latencies.\cite{Wimmer2019} Nevertheless, complex data processing
-tasks and overloaded \gls{usb} ports can lead to delays.
+latencies.\customcite{W19} Nevertheless, complex data processing tasks and
+overloaded \gls{usb} ports can lead to delays.
 
 \begin{longtable}[]{@{}lllll@{}}
-\caption{Measured sensor readout to processing using host software
-\label{Measured_sensor_readout_to_processing_using_host_software.csv}}\tabularnewline
+\caption{\gls{usb} connected sensor latency test results using several
+sensor readout requests togehter with variable host system cpu loads
+testing for jitter variations
+\label{(+usb)_connected_sensor_latency_test_results_using_several_sensor_readout_requests_togehter_with_variable_host_system_cpu_loads_testing_for_jitter_variations.csv}}\tabularnewline
 \toprule
@@
 
-The table
-shows\ref{Measured_sensor_readout_to_processing_using_host_software.csv}
-shows various jitter measurements. These are performed on a
-\emph{RaspberryPi 4 4GB}-\gls{sbc} together with an \emph{1D: Single
-Sensor} \ref{d-single-sensor} and the following software settings:
+Table
+\ref{(+usb)_connected_sensor_latency_test_results_using_several_sensor_readout_requests_togehter_with_variable_host_system_cpu_loads_testing_for_jitter_variations.csv}
+contains various jitter measurements. These are performed on a
+\emph{Raspberry Pi 4 4GB}-\gls{sbc} together with an \emph{1D: Single
+Sensor} explained in chapter \ref{d-single-sensor} and the following
+software settings:
 
@@
 \item
-  \emph{Raspberry Pi OS Lite} - \gls{os} \emph{Debian bookworm x64},
-\item
-  \gls{mrp}-library (see chapter \ref{software-readout-framework}) -
-  Version \emph{1.4.1}
-\item
-  Unified Sensor-firmware - Version \emph{1.0.1}
+  \emph{Raspberry Pi OS Lite} - \gls{os} \emph{Debian bookworm x64}
+\item
+  \gls{mrp}-library described in chapter
+  \ref{software-readout-framework} - Version \emph{1.4.1}
+\item
+  Unified Sensor-firmware described in chapter \ref{unified-sensor} -
+  Version \emph{1.0.1}
 \end{itemize}
@@
 
-The other issue is sending the trigger signal from the readout software
-\ref{software-readout-framework}. Here too, unpredictable latencies can
-occur, depending on which other tasks are also executed on this port.
+The other issue is sending the trigger signal from the readout software,
+which is described in chapter \ref{software-readout-framework}. At this
+point unpredictable latencies can occur, too, depending on which other
+tasks are also executed on this port.
 
@@
 firmware to synchronise the readout intervals. The figure
-\ref{Multi_sensor_synchronisation_wiring_example.png} illustrates the
-schematic how several sensors must be wired together in order to
-implement this form of synchronisation.
+\ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
+illustrates the schematic how several sensors must be wired together in
+order to implement this form of synchronisation.
 
@@
 \centering
-\includegraphics{./generated_images/border_Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}
+\includegraphics{./generated_images/border_Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
 \caption{Unified sensor firmware multi sensor synchronisation procedure
-\label{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}}
+using sync \gls{gpio} input for operation (primary or secondary) mode
+decision
+\label{Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}}
 \end{figure}
@@
 Once the hardware has been prepared, the task of the firmware of the
-various sensors is to find a common synchronisation clock. To do this,
-the function \emph{register irq on sync pin} is overwritten. To set one
+various sensors is to find a common synchronisation clock. The figure
+\ref{Unified_sensor_fiUnified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.pngrmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
+shows how the firmware handles the decision task if the sensor is
+\emph{primary} or \emph{secondary} at startup. The firmware-function
+\emph{register irq on sync pin} is overwritten. To set one
 \emph{primary} and several \emph{secondary} sensors, each sensor waits
-for an initial pulse on the SYNC-\gls{gpio}. A random timer is started
-beforehand by each sensor, which sends a pulse on the sync line. All
-others receive this and switch to \emph{secondary mode} and synchronise
-the measurements based on each sync pulse received.
+for an initial pulse on the SYNC-\gls{gpio}, which is a pin at the
+microcontroller with the funtionality to detect if the sensor is a
+primary or a secondary sensor. A random timer is started beforehand by
+each sensor, which sends a pulse on the sync line. All others receive
+this and switch to \emph{secondary mode} and synchronise the
+measurements based on each sync pulse received.
 
@@
 sensor operation through the \emph{got impulse within 1000ms} branch
-result. The figure \ref{Query_opmode_using_(+cli).png} shows the
-synchronisation status of the sensor which can be queried via the user
-interface described in chapter \ref{communication-interface} by using
-the \emph{opmode} command. An important aspect of the implementation
-here is that there is no numbering or sequence of the individual
-sensors.
+result. The figure
+\ref{Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}
+shows the synchronisation status of the sensor which can be queried via
+the user interface described in chapter \ref{communication-interface} by
+using the \emph{opmode} command. An important aspect of the
+implementation is that there is no numbering or sequence of the
+individual sensors.
 
@@
 \centering
-\includegraphics{./generated_images/border_Query_opmode_using_(+cli).png}
-\caption{Query opmode using \gls{cli}
-\label{Query_opmode_using_(+cli).png}}
+\includegraphics{./generated_images/border_Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}
+\caption{Result of the opmode command execution on a sensor which is
+connected to another as primary configured sensor
+\label{Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}}
 \end{figure}
@@
 \begin{longtable}[]{@{}llll@{}}
-\caption{Build sensors with different capabilities
-\label{Build_sensors_with_different_capabilities.csv}}\tabularnewline
+\caption{Build hardware sensors with equipped with different sensor
+\gls{ic}s to cover different magnet charaterisation setups
+\label{Build_hardware_sensors_with_equipped_with_different_sensor_(+ic)s_to_cover_different_magnet_charaterisation_setups.csv}}\tabularnewline
 \toprule
@@
 
-The table \ref{Build_sensors_with_different_capabilities.csv} shows the
-various prototype sensor platforms equipped with different magnetic
-field sensors. These cover all the required functions described in the
-use cases \ref{use-cases}. The most important difference, apart from the
-sensor used, is the \emph{scan mode}. In this context, this describes
-whether the sensor can measure a \emph{static} fixed point on the magnet
-or if the sensor can move \emph{dynamically} around the magnet using a
-controllable manipulator.
+The table
+\ref{Build_hardware_sensors_with_equipped_with_different_sensor_(+ic)s_to_cover_different_magnet_charaterisation_setups.csv}
+shows the various prototype sensor platforms equipped with different
+magnetic field sensors. These cover all the required functions described
+in the use cases \ref{use-cases}. The most important difference, apart
+from the sensor used, is the \emph{scan mode}. In this context, this
+describes whether the sensor can measure a \emph{static} fixed point on
+the magnet or if the sensor can move \emph{dynamically} around the
+magnet using a controllable manipulator.
 
@@
 \centering
-\includegraphics{./generated_images/border_1D_sensor_construction_with_universal_magnet_mount.png}
-\caption{1D sensor construction with universal magnet mount
-\label{1D_sensor_construction_with_universal_magnet_mount.png}}
+\includegraphics{./generated_images/border_Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_populated_with_N45_12x12x12mm_magnet.png}
+\caption{Manufactured 1D sensor construction from different angles and
+universal magnet mount (green 3D printed part) populated with N45
+12x12x12mm magnet
+\label{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_populated_with_N45_12x12x12mm_magnet.png}}
 \end{figure}
@@
 The 1D sensor shown in figure
-\ref{1D_sensor_construction_with_universal_magnet_mount.png} is the
-simplest possible sensor that is compatible with the Unified Sensor
-firmware \ref{firmware} platform.
-
-The electrical level here is based on a \emph{Raspberry-Pi Pico}
-together with the \emph{MMC5603NJ} magnetic sensor. The mechanical setup
-consists of four 3D printed components, which are fixed together with
-nylon screws to minimise possible influences on the measurement.
+\ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_populated_with_N45_12x12x12mm_magnet.png}
+is the simplest possible sensor that is compatible with the Unified
+Sensor firmware.
+
+The electrical level is based on a \emph{Raspberry Pi Pico} together
+with the \emph{MMC5603NJ} magnetic sensor. The mechanical setup consists
+of four 3D printed components, which are fixed together with nylon
+screws to minimise possible influences on the measurement.
 
@@
 \emph{6uT}, even small coin sized neodymium magnets already saturates
-the sensor. It is possible to mount 3D printed spacers over the sensor
-to increase the distance between the magnet and the sensor and thus also
-measure these magnets.
+the sensor. It is possible to mount 3D printed spacers (see green part
+in figure
+\ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_populated_with_N45_12x12x12mm_magnet.png})over
+the sensor to increase the distance between the magnet and the sensor
+and thus also measure these magnets.
 
@@
 The figure
-\ref{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_3D_full-sphere_sensor.png}
+\ref{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full-sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
 shows the visualisation of such a scan in the form of a spherical 3D
@@
 \centering
-\includegraphics{./generated_images/border_3D_plot_of_an_N45_12x12x12mm_magnet_using_the_3D_full-sphere_sensor.png}
-\caption{3D plot of an N45 12x12x12mm magnet using the 3D full-sphere
-sensor
-\label{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_3D_full-sphere_sensor.png}}
+\includegraphics{./generated_images/border_3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full-sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
+\caption{3D plot of an N45 12x12x12mm magnet using the build 3D
+full-sphere sensor with visible magnetic field strength deviations using
+different shaded vertices on a sphere
+\label{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full-sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}}
 \end{figure}
@@
 This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
-offer an physical \emph{RS232} interface. As with the other sensors,
-this interface consists of a \emph{Raspberry-Pi Pico} with an additional
+offer a physical \emph{RS232} interface. As with the other sensors, this
+interface consists of a \emph{Raspberry Pi Pico} with an additional
 level shifter.
@@
 
-All these steps are divided into different blocks with an editional
+All these steps are divided into different blocks with an additional
 functionality for users to add own modules. This concept is explained in
@@
 the other. For this thesis it also eases the option to change sensors
-for measurments.
+for measurements.
 
@@
 are shown in the figure
-\ref{MRP_library_module_high_level_overview.png}. In combination, these
-represent a typical measurement-analysis-evaluation workflow of data.
-For this purpose, a module system with standardised functional patterns
-and data types is developed and packed together in a extendable Python
-library.
+\ref{MRP_library_implemented_modules_high_level_overview_each_of_which_can_be_replaced_by_the_user_with_custom_ones.png}.
+In combination, these represent a typical
+measurement-analysis-evaluation workflow of data. For this purpose, a
+module system with standardised functional patterns and data types is
+developed and packed together in an extendable Python library.
 
@@
 \centering
-\includegraphics{./generated_images/border_MRP_library_module_high_level_overview.png}
-\caption{MRP library module high level overview
-\label{MRP_library_module_high_level_overview.png}}
+\includegraphics{./generated_images/border_MRP_library_implemented_modules_high_level_overview_each_of_which_can_be_replaced_by_the_user_with_custom_ones.png}
+\caption{MRP library implemented modules high level overview each of
+which can be replaced by the user with custom ones
+\label{MRP_library_implemented_modules_high_level_overview_each_of_which_can_be_replaced_by_the_user_with_custom_ones.png}}
 \end{figure}
@@
 
-A project called \emph{HalbachOptimisation}
-\cite{HalbachOptimisation} implements a data analysis step and
-optimizes a magnetic field that is as homogeneous as possible within a
-circular section using given mechanical dimensions as input parameters
-of the magnets which are used. For this purpose, a mutation of the
-magnet positions and rotations is performed. The result is a list of
-positions for each magnet.
-
-The \emph{HalbachMRIDesigner} \cite{HalbachMRIDesigner} is an
-opensource project and generates basic \gls{cad} drawings for \gls{mri}
-magnets in a Halbach configuration. To do this, the number of magnets
-and additional parameters for the properties of the \gls{cad} model to
-be created are passed to the function provided as input parameters using
-a \gls{json} file. The result is an \emph{OpenSCAD} \cite{OpenSCAD}
-based 3D model of the magnet holder.
+A project called \emph{HalbachOptimisation} \customcite{O24} implements a
+data analysis step and optimizes a magnetic field that is as homogeneous
+as possible within a circular section using given mechanical dimensions
+as input parameters of the magnets which are used. For this purpose, a
+mutation of the magnet positions and rotations is performed. The result
+is a list of positions for each magnet.
+
+The \emph{MWO24} \customcite{MWO24} is an opensource project and generates
+basic \gls{cad} drawings for \gls{mri} magnets in a Halbach
+configuration. To do this, the number of magnets and additional
+parameters for the properties of the \gls{cad} model to be created are
+passed to the function provided as input parameters using a \gls{json}
+file. The result is an \emph{OpenSCAD} \customcite{MMN19} based 3D model
+of the magnet holder.
 
@@
 
-The input parameters of the \emph{HalbachOptimisation}
-\cite{HalbachOptimisation} project are on the one hand the
-mechanical dimensions and the number of magnets to be used. We assume
-ideal magnets here. However, it should also be possible to import field
-data in a more measured form later on. Using the DataAquisition
-sub-step, it is possible to generate any number of ideal magnets.
+The input parameters of the \emph{HalbachOptimisation} \customcite{O24}
+project are on the one hand the mechanical dimensions and the number of
+magnets to be used. Idal magnets are assumed at this point. However, it
+should also be possible to import field data in a more measured form
+later on. Using the DataAquisition sub-step, it is possible to generate
+any number of ideal magnets.
 
@@
 up its functions. In the case of the \emph{HalbachOptimisation}
-\cite{HalbachOptimisation} project, the function signature of the
-start function must be changed. This receives the result of the previous
-step, in this case the generated magnet data. By optionally setting meta
-data in the universal library data type, constants can be replaced in
-the analysis function and made dynamically configurable. The return
-result also corresponds to this data type so that subsequent steps are
-compatible and contains the magnet data with modified position and
-rotation data.
+\customcite{O24} project, the function signature of the start function
+must be changed. This receives the result of the previous step, in this
+case the generated magnet data. By optionally setting meta data in the
+universal library data type, constants can be replaced in the analysis
+function and made dynamically configurable. The return result also
+corresponds to this data type so that subsequent steps are compatible
+and contains the magnet data with modified position and rotation data.
 
@@
 
-The last step is to call up the \emph{HalbachMRIDesigner}
-\cite{HalbachMRIDesigner} project, which creates the \gls{cad} model
-of the magnet holder. The data can also be exported as files. To make
-the project compatible, the function signatures are also adapted. In
-this case, more changes are required, as the configuration file is
-loaded from the file system. This logic needs to be removed in order to
-use the added meta data as input parameter instead.
+The last step is to call up the \emph{MWO24} \customcite{MWO24} project,
+which creates the \gls{cad} model of the magnet holder. The data can
+also be exported as files. To make the project compatible, the function
+signatures are also adapted. In this case, more changes are required, as
+the configuration file is loaded from the file system. This logic needs
+to be removed in order to use the added meta data as input parameter
+instead.
 
@@
 interchangeable. If the user now wishes to use a different \gls{cad}
-algorithm instead of the \emph{HalbachMRIDesigner}
-\cite{HalbachMRIDesigner}, the other steps can simply be preserved
-and only the new step needs to be implemented.
+algorithm instead of the example \emph{HalbachMRIDesigner}
+\customcite{MWO24} project, the other steps can simply be preserved and
+only the new step needs to be implemented.
 
@@
 the subchapters as the following. There are also introductory examples
-which provide an overview of the basic functions in the \emph{Examples}
-\ref{examples} chapter, as well as further examples in the
+which provide an overview of the provided functions in the
+\emph{Examples} \ref{examples} chapter, as well as further examples in
+the
 \href{https://magneticreadoutprocessing.readthedocs.io/en/latest/}{online documentation}.
@@
 
-The \emph{MRPReading} module performs a essential role in streamlining
+The \emph{MRPReading} module performs an essential role in streamlining
 the centralized management of measurement data. It serves as a storage
@@
 To configure parameters, ensuring a tailored approach to the entire
-measurement process, these parameters act as a essential bridge between
+measurement process, these parameters act as an essential bridge between
 user preferences and the robust capabilities of the \emph{MRPReading}
@@
 serialization, the \emph{MRPReading} class inherited from
-Python-\emph{Object} class is serialized via an dictionary conversion
+Python-\emph{Object} class is serialized via a dictionary conversion
 step. This \gls{json} string can then be processed directly or written
@@
 Since there are popular data processing frameworks such as \emph{Numpy}
-\cite{harris2020array}, or the program for mathematical
-calculations, \emph{MATLAB} are often used, the library also supports
-export formats for these systems.
+\customcite{HMW20}, or the program for mathematical calculations,
+\emph{MATLAB} are often used, the library also supports export formats
+for these systems.
 
@@
 compatible with the firmware developed in the \emph{Unified Sensor}
-\ref{unified-sensor} chapter are supported here. The library provides
-the following sensor \gls{hal} modules for this purpose:
+\ref{unified-sensor} chapter are supported. The library provides the
+following sensor \gls{hal} modules for this purpose:
 
@@
 \emph{MRPReadingSource}, which automatically creates the appropriate
-instance based on the sensor capabilites.
+instance based on the sensor capabilities.
 
@@
 \item
-  \emph{MRPVisualization} - different table and graph based plots
+  \emph{MRPVisualization} - different table and graph-based plots
 \item
@@
 Data analysis offers the user the greatest flexibility to implement
-their own modules. For this reason \emph{MRPAnalysis} contains functions
-for calculating the following data analyses, which are compatible with
-class instances of \emph{MRPReading}:
+their own modules. For this reason, \emph{MRPAnalysis} contains
+functions for calculating the following data analyses, which are
+compatible with class instances of \emph{MRPReading}:
 
@@
 In addition, the export function \emph{.to\_numpy\_matrix} enables
-further processing of the data in the \emph{Numpy}
-\cite{harris2020array} framework, in which many other standard
-analysis functions are implemented.
+further processing of the data in the \emph{Numpy} \customcite{HMW20}
+framework, in which many other standard analysis functions are
+implemented.
 
@@
 
-In the previouse described scenarios, it is only possible to detect and
-use sensors that are directly connected to the host \gls{pc}. It has the
-disadvantage that there must always be a physical connection. This can
-make it difficult to install multiple sensors in measurement setups
-where space or cable routing options are limited.
-
-Multiple sensor can be connected to any \gls{pc} which is available on
-the network. This can be a \gls{sbc} (e.g.~a Raspberry Pi). The small
-footprint and low power consumption make it a good choice. It can also
-be used in a temperature chamber.
-
-The \emph{MRPProxy} \ref{MRPlib_Proxy_Module.png} module has been
-developed to allow forwarding and interaction with several sensors over
-a network connection using a \gls{rest} interface.
+In the previous described scenarios, only the sensors that are directly
+connected to the host \gls{pc} can be detected and used. That
+functionality has the disadvantage that there must always be a physical
+connection. Difficulties arise when installing multiple sensors in
+measurement setups where space or cable routing options are limited.
+
+Multiple sensors can be connected to any \gls{pc} which is available on
+the network. This can be a \gls{sbc} (e.g.~a \emph{Raspberry Pi}). The
+small footprint and low power consumption make it a good choice. It can
+also be used in a temperature chamber.
+
+The \emph{MRPProxy} module in figure
+\ref{MRPlib_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_communicating_together_using_the_http_protocol.png}
+has been developed to allow forwarding and interaction with several
+sensors over a network connection using a \gls{rest} interface.
 
@@
 \centering
-\includegraphics{./generated_images/border_MRPlib_Proxy_Module.png}
-\caption{MRPlib Proxy Module \label{MRPlib_Proxy_Module.png}}
+\includegraphics{./generated_images/border_MRPlib_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_communicating_together_using_the_http_protocol.png}
+\caption{MRPlib proxy module usage example with host \gls{pc} for
+readout processing and remote \gls{pc} for sensor communication
+communicating together using the http protocol
+\label{MRPlib_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_communicating_together_using_the_http_protocol.png}}
 \end{figure}
@@
 the proxy module, it is possible to link several instances and all
-sensors available in the network are available to the \emph{control}
+sensors available in the network are accessable to the \emph{control}
 \gls{pc}.
@@
 
-The figure
-\ref{Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png} shows
-the modified \emph{multi-proxy - multi-sensor} topology. Here, both
+Figure \ref{Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png}
+shows the modified \emph{multi-proxy - multi-sensor} topology. Both
 proxy instances do not communicate directly with the \emph{control}
@@
 
-The figure \ref{MRPlib_Proxy_Module.png} shows the separation of the
-various \gls{hal} instances, which communicate with the physically
-connected sensors on the \emph{remote} \gls{pc} and the \emph{control}
-\gls{pc} side, which communicates with the remote side via the network.
-For the user, nothing changes in the procedure for setting up a
-measurement. The \emph{MRPProxy} \gls{cli} application must always be
-started \ref{lst:mrpcli_proxy_start} on the \gls{pc} with connected
+Figure \ref{MRPlib_Proxy_Module.png} shows the separation of the various
+\gls{hal} instances, which communicate with the physically connected
+sensors on the \emph{remote} \gls{pc} and the \emph{control} \gls{pc}
+side, which communicates with the remote side via the network. For the
+user, nothing changes in the procedure for setting up a measurement. The
+\emph{MRPProxy} \gls{cli} application must always be started like shown
+in listing \ref{lst:mrpcli_proxy_start} on the \gls{pc} with connected
 hardware sensors attached.
@@
 After the proxy instance has been successfully started, it is optionally
-possible to check the status via the \gls{rest} interface:
-\ref{lst:mrpcli_config_rest}
+possible to check the status via the \gls{rest} interface, which is
+shown in listing \ref{lst:mrpcli_config_rest}:
 
@@
 The query result shows that the sensors are connected correctly and that
-their capabilites have also been recognised correctly. To be able to
+the capabilities have also been recognised correctly. To be able to
 configure a measurement on the \emph{control} \gls{pc}, only the
 \gls{ip} address or hostname of the \gls{pc} running an \emph{MRPProxy}
-instance is required \ref{lst:mrpcli_config_using_rpc}.
+instance is required as shown in listing
+\ref{lst:mrpcli_config_using_rpc}.
 
@@
 
-Another important aspect when using several sensors via the proxy system
+Another important aspect for using several sensors via the proxy system
 is the synchronisation of the measurement intervals between the sensors.
@@
 other via their sync input using short cables. One sensor acts as the
-central clock as described in \ref{sensor-syncronisation-interface}.
-this no longer works for long distances and the syncronisation must be
-made via a shared network connection.
+central clock as described in chapter
+\ref{sensor-syncronisation-interface}. This no longer works for long
+distances and the syncronisation must be established via a shared
+network connection.
 
 If time-critical synchronisation over the network is required, \gls{ptp}
-and \gls{pps} output functionality \cite{PTPIEEE1588} can be used on
-many \gls{sbc}, such as the \emph{Raspberry-Pi Compute Module}.
+and \gls{pps} output functionality \customcite{O24} can be used on many
+\gls{sbc}, such as the \emph{Raspberry Pi Compute Module}.
 
@@
 
-As it is possible to connect many identical sensors to one host, it must
-be possible to address them separately. This separation is done by the
-\emph{MRPProxy} module and is a separate part from the core
-\gls{mrp}-library, to keep installation package dependencies small.
-
-Each connected sensor is accessed via the text-based \gls{cli}, this is
+As it is possible to connect many identical sensors to one host,
+therefore it needs to be possible to address them separately. This
+separation is done by the \emph{MRPProxy} module, which is a separate
+part from the core \gls{mrp}-library, to keep installation package
+dependencies small.
+
+Each connected sensor is accessed via the text-based \gls{cli}, which is
 initially the same for each sensor. The only identification feature is
@@
 The \emph{MRPProxy} instance claims to be a sensor to the host \gls{pc}
-running \gls{mrp} \gls{cli}, so the multiple sensors must be combined
-into one virtual one. This is done in several steps, start procedure
+running \gls{mrp} \gls{cli}, so multiple sensors must be combined into
+one virtual one. This is done in several steps, start procedure
 described by the following sub-chapters.
@@
 \subsubsection{Construct the Sensor ID
-LookUp-Table}\label{construct-the-sensor-id-lookup-table}}
+Lookup-Table}\label{construct-the-sensor-id-lookup-table}}
 
@@
 
-When using sensors with different capabilites, these must be combined.
+When using sensors with different capabilities, these must be combined.
 These are used to select the appropriate measurement mode for a
@@
 
-\begin{lstlisting}[language=bash, caption={MRPproxy REST entrypoint query examples}, label=lst:mtsc]
+\begin{lstlisting}[language=bash, caption={MRPproxy REST entry point query examples}, label=lst:mtsc]
 # QUERY Network-Proxy capabilities
@@
 
-The same procedure is performed for the \emph{commands}
-\gls{cli}-command of each sensor, to merge available commands of
-connected sensors into the \gls{lut}.
+The same procedure is performed for all available \gls{cli}-command of
+each sensor, to merge available commands of connected sensors into the
+\gls{lut}.
 
@@
 In order for the host to be able to send a command to the network
-multi-sensor setup, the command received must be forwarded to the
+multi-sensor setup, the command received needs to be forwarded to the
 correct sensor. In addition, there are commands such as the previously
@@
 the \emph{MRPProxy} module so that it can be handled differently (see
-example \ref{lst:mtsc}).
+example listing \ref{lst:mtsc}).
 
@@
 
-For commands where there are several entries for \emph{CAPABLE SENSORS
-ID LUT} \ref{Sensor_capabilities_merging_algorithm.csv}, there are two
-possible approaches to how the command is processed:
+For commands, which have several entries for \emph{CAPABLE SENSORS ID
+LUT} from table \ref{Sensor_capabilities_merging_algorithm.csv}, there
+are two possible approaches to how the command is processed:
 
@@
 \emph{readsensor} command, all sensors are read out via one command and
-the summarized result is transmitted to the host.
+the summarised result is transmitted to the host.
 
 The \emph{extend commands using an id parameter} strategy is used for
-different sensors. Each command is extended on the \emph{Network-Proxy}
-\ref{network-proxy} by another \gls{uuid} parameter, according to the
-following scheme:
+different sensors. Each command is extended on the \emph{Network-Proxy},
+which is explained in chapter \ref{network-proxy} by another \gls{uuid}
+parameter, according to the following scheme:
 
@@
 
-The following shows some examples of how the \gls{mrp}-library can be
-used. These examples are limited to a functional minimum for selected
-modules of the \gls{mrp}-library. The documentation \ref{documentation}
-contains further and more detailed examples. Many basic examples are
-also supplied in the form of the test scripts used for testing
-\ref{testing}.
+The following chapter shows some examples of how the \gls{mrp}-library
+can be used. These examples are limited to a functional minimum for
+selected modules of the \gls{mrp}-library. The documentation in chapter
+\ref{documentation} contains further and more detailed examples. Many
+basic examples are also supplied in the form of the test scripts used
+for testing in chapter \ref{testing}.
 
@@
 
-\begin{lstlisting}[language=Python, caption={MRPReading example for setting up an basic measurement}, label=lst:mrpexample_reading]
+\begin{lstlisting}[language=Python, caption={MRPReading example for setting up a basic measurement}, label=lst:mrpexample_reading]
 from MRP import MRPReading, MRPMeasurementConfig
@@
 After generating simple measurements with random values in the previous
-example \ref{mrpreading}, the next step is to record real sensor data.
-For this purpose, the \emph{MRPHal} module is developed, which can
-interact with all \emph{Unified Sensor} \ref{unified-sensor}-compatible
-sensors. In the following example \ref{lst:mrpexample_hal}, an \emph{1D:
-Single Sensor} \ref{d-single-sensor} is connected locally to the host
-\gls{pc}.
-
-\begin{lstlisting}[language=Python, caption={MRPHal example to use an connected hardware sensor to store readings inside of a measurement}, label=lst:mrpexample_hal]
+example in chapter \ref{mrpreading}, the next step is to record real
+sensor data. For this purpose, the \emph{MRPHal} module is developed,
+which can interact with all \emph{Unified Sensor} from chapter
+\ref{unified-sensor}-compatible sensors. In the following example
+listing \ref{lst:mrpexample_hal}, an \emph{1D: Single Sensor}, which is
+explained in chapter \ref{d-single-sensor}, is connected locally to the
+host \gls{pc}.
+
+\begin{lstlisting}[language=Python, caption={MRPHal example to use a connected hardware sensor to store readings inside of a measurement}, label=lst:mrpexample_hal]
 from MRP import MRPHalSerialPortInformation, MRPHal, MRPBaseSensor, MRPReadingSource
@@
 In general, a sensor can be connected using its specific system path or
-the sensor-\gls{uuid} via the \emph{MRPHalSerialPortInformation}
+the sensor \gls{uuid} via the \emph{MRPHalSerialPortInformation}
 function. Locally connected or network sensors can also be automatically
@@
 
-If no hardware sensor is available or for the generation of test data,
-the \emph{MRPSimulation} module is available. This contains a series of
+If no hardware sensor is available for the generation of test data, the
+\emph{MRPSimulation} module is available. This contains a series of
 functions that simulate various magnets and their fields. The result is
@@
 
-The example listing \ref{lst:mrpexample_simulation} illustrated the
+The example listing \ref{lst:mrpexample_simulation} illustrates the
 basic usage. Different variations of the \emph{generate\_reading}
-function offers the user additional parameterisation options, such as
+function offer the user additional parameterisation options, such as
 random polarisation direction or a defined centre-of-gravity vector. The
 data is generated in the background using the \emph{magpylib}
-\cite{ortner2020magpylib} library according to the specified
-parameters.
+\customcite{OB20} library according to the specified parameters.
 
@@
 functions for this purpose. The code example shows the basic use of the
-module. The \emph{Evaluation} \ref{evaluation} chapter shows how the
-user can implement their own algorithms and add them to the library.
+module. The \emph{Evaluation} in chapter \ref{evaluation} chapter shows
+how the user can implement their own algorithms and add them to the
+library.
 
@@
 visualisation options make it possible to visually assess the results of
-a measurement. This is particularly helpful for full-sphere measurements
-recorded with the \emph{3D: Full sphere} \ref{d-full-sphere} sensor. The
-sub-module \emph{MRPPolarVisualisation} is specially designed for these.
-The figure
-\ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
+a measurement. This is particularly helpful for full sphere measurements
+recorded with the \emph{3D: Full sphere} sensor introduced in chapter
+\ref{d-full-sphere}. The sub-module \emph{MRPPolarVisualisation} is
+specially designed for these. Figure
+\ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module_using_different_shaded_vertices_on_a_sphere.png}
 shows a plot of a full sphere measurement. It is also possible to export
 the data from the \emph{MRPAnalysis} module graphically as diagrams. The
-\emph{MRPVisualisation} modules are used here. The following example
-\ref{lst:mrpexample_visualisation} shows the usage of both modules.
+\emph{MRPVisualisation} modules are used for this. The following example
+listing \ref{lst:mrpexample_visualisation} shows the usage of both
+modules.
 
@@
 # CREATE MRPPolarVisualization INSTANCE
-## IT CAN BE REUSED CALLING plot2d AGAIN, AFTER LINKED READING DATA WERE MODIFIED
+## IT CAN BE REUSED CALLING plot2d AGAIN, AFTER LINKED READING DATA ARE MODIFIED
 visu = MRPPolarVisualization.MRPPolarVisualization(reading)
@@
 \centering
-\includegraphics{./generated_images/border_Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
+\includegraphics{./generated_images/border_Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module_using_different_shaded_vertices_on_a_sphere.png}
 \caption{Example full sphere plot of an measurement using the
-MRPVisualisation module
-\label{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}}
+MRPVisualisation module using different shaded vertices on a sphere
+\label{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module_using_different_shaded_vertices_on_a_sphere.png}}
 \end{figure}
@@
 
-The following example listing \ref{lst:mrpexample_halbach}, shows how a
+The following example listing \ref{lst:mrpexample_halbach} shows how a
 simple Halbach magnetic ring can be generated.
 
-This can then be used to construct a Halbach ring magnet (see chapter
+This can be used to construct a Halbach ring magnet (see chapter
 \ref{magnet-system}) for a low-field \gls{mri}.
 
-Eight random measurements are generated here. It is important that the
-magnet type (for example \emph{N45\_CUBIC\_15x15x15}) is specified. This
-is necessary so that the correct magnet cutouts can be generated when
-creating the 3D model.
+Eight random measurements are generated at this point. It is important
+that the magnet type (for example \emph{N45\_CUBIC\_15x15x15}) is
+specified. This is necessary so that the correct magnet cutouts can be
+generated when creating the 3D model.
 
@@
 position and rotation offset according to the Halbach design and
-calculation scheme \cite{HalbachOptimisation} using the
+calculation scheme \customcite{O24} using the
 \emph{MRPHalbachArrayGenerator} module.
 
-\begin{lstlisting}[language=Python, caption={MRPHalbachArrayGenerator example for generating an OpenSCAD based halbach ring}, label=lst:mrpexample_halbach]
+\begin{lstlisting}[language=Python, caption={MRPHalbachArrayGenerator example for generating an OpenSCAD based Halbach ring}, label=lst:mrpexample_halbach]
 readings = []
@@
 is generated from the generated magnet positions. The result is an
-\emph{OpenSCAD} \cite{OpenSCAD} file, which contains the module
+\emph{OpenSCAD} \customcite{MMN19} file, which contains the module
 generated. After computing the model using the \emph{OpenSCAD} \gls{cli}
@@
 possible for programming beginners in particular to use them. To
-simplify these tasks, a \gls{cli}
-\ref{Example_measurement_analysis_pipeline.png} is implemented. The
-library \gls{cli} implements the following functionalities:
+simplify these tasks, a \gls{cli} is implemented and implements the
+following functionalities:
 
@@
 connect a sensor to the \gls{pc}, configure a measurement series with it
-and run it at the end. The result is an exported file with the measured
-values. These can then be read in again using the \emph{MRPReading}
-module and processed further. The following bash code
-\ref{lst:mrpcli_config_run} shows the setup procedure in detail:
+and run it at the end, which is shown in figure
+\ref{MRP_(+cli)_output_to_configure_a_new_measurement.png}. The result
+is an exported file with the measured values. These can then be read in
+again using the \emph{MRPReading} module and processed further. The
+following bash listing \ref{lst:mrpcli_config_run} shows the setup
+procedure in detail:
 
@@
 
-After it is easy for users to carry out measurements using the
-\gls{cli}, the next logical step is to analyse the recorded data. This
+It is more applicable for users to carry out measurements using the
+\gls{cli}-, the next logical step is to analyse the recorded data. This
 can involve one or several hundred data records. Again, the procedure
@@
 
-For this purpose, a further \gls{cli} application is created, which
-enables the user to create and execute complex evaluation pipelines for
+For this purpose, \gls{cli} application is created further, to enable
+the user to create and execute complex evaluation pipelines for
 measurement data without programming. The figure
@@
 In order to implement such a pipeline, the \emph{yaml} file format is
-chosen for the definition of the pipeline, as this is for non
-programmers to understand and can also be easily edited with a plain
-text editor. Detailed examples can be found in the documentation
-\cite{MagneticReadoutProcessingReadTheDocs}. The pipeline definition
-consists of sections which execute the appropriate Python commands in
-the background.
+chosen for the definition of the pipeline, as this is for
+non-programmers to understand and can also be easily edited with a plain
+text editor. Detailed examples can be found in the
+\href{https://magneticreadoutprocessing.readthedocs.io/en/latest/}{documentation}.
+
+The pipeline definition consists of sections which execute the
+appropriate Python commands in the background.
 
@@
 This system makes almost all Python functions available to the user. To
-simplify use, a pre-defined list of verified functions for use in
-pipelines is listed in the documentation
-\cite{MagneticReadoutProcessingReadTheDocs}. The following pipeline
-definition \ref{lst:mrpuddp_example_yaml} shows the previously defined
-steps \ref{Example_measurement_analysis_pipeline.png} as \emph{yaml}
+simplify usage, a pre-defined list of verified functions for use in
+pipelines is listed in the
+\href{https://magneticreadoutprocessing.readthedocs.io/en/latest/}{documentation}.
+The following pipeline definition in listing
+\ref{lst:mrpuddp_example_yaml} shows the previously defined steps shown
+in figure \ref{Example_measurement_analysis_pipeline.png} as \emph{yaml}
 syntax.
 
-\begin{lstlisting}[caption={Example YAML code of an user defined processing pipeline with six stages linked together}, label=lst:mrpuddp_example_yaml]
+\begin{lstlisting}[caption={Example YAML code of a user defined processing pipeline with six stages linked together}, label=lst:mrpuddp_example_yaml]
 stage import_readings:
@@
 
-The various steps are then linked by using the \emph{stage } makro as
-input parameter of the next function to be executed (see comments in
+The various steps are linked by using the \emph{stage } makro as input
+parameter of the next function to be executed (see comments in listing
 \ref{lst:mrpuddp_example_yaml}).
 
-It is therefore also possible to use the results of one function in
-several others without them directly following each other. The
-disadvantages of this system are the following:
+Therefore it is feasable to use the results of one function in several
+others without them directly following each other. The disadvantages of
+this system are the following:
 
@@
 determination of possible start steps and repeated traversal, the final
-execution sequence can be determined in the form of a call tree
+execution sequence can be determined in the form of a call tree in
+figure
 \ref{Example_result_of_an_step_execution_tree_from_user_defined_processing_pipeline.png}.
 The individual steps are then executed along the graph. The intermediate
-results and the final results
+results and the final results in figure
 \ref{Pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
@@
 Software tests in libraries offer numerous advantages for improving
-quality and efficiency. Software tests make it possible to identify
-errors and vulnerabilities before the software is released as a new
-version.
+quality and efficiency. Software tests ease to identify errors and
+vulnerabilities before the software is released as a new version.
 
 This significantly improves the reliability of \gls{mrp}-library
-applications. Tests also ensures consistent and reliable performance,
+applications. Tests also ensure consistent and reliable performance,
 which is particularly important when libraries are used by different
@@
 created for all important functionalities and use cases. The test
-framework \emph{PyTest} \cite{Pajankar2017} is used for this
-purpose, as it offers direct integration in most \gls{ide}s (see
+framework \emph{PyTest} \customcite{P17} is used for this purpose, as it
+offers direct integration in most \gls{ide}s (see figure
 \ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
@@
 all intended use cases are mapped using the test cases created, the code
-of the test cases could later be used in slightly simplified variants
-\ref{lst:pytest_example_code} as examples for the documentation.
+of the test cases could later be used in slightly simplified variants of
+listing \ref{lst:pytest_example_code} as examples for the documentation.
 
@@
 class TestMPRReading(unittest.TestCase):
-  # PREPARE A INITIAL CONFIGURATION FILE FOR ALL FOLLOWING TEST CASES IN THIS FILE
+  # PREPARE AN INITIAL CONFIGURATION FILE FOR ALL FOLLOWING TEST CASES IN THIS FILE
   def setUp(self) -> None:
@@
 
-One problem, is the parts of the \gls{mrp}-library that require direct
-access to external hardware. These are, for example, the \emph{MRPHal}
-and \emph{MRPHalRest} modules, which are required to read out sensors
-connected via the network. Two different approaches are used here. In
-the case of local development, the test runs are carried out on a
-\gls{pc} that can reach the network hardware and thus the test run could
-be carried out with real data.
+Difficulties arise with the parts of the \gls{mrp}-library that require
+direct access to external hardware. These are, for example, the
+\emph{MRPHal} and \emph{MRPHalRest} modules, which are required to read
+out sensors connected via the network. Two different approaches are
+used. In the case of local development, the test runs are carried out on
+a \gls{pc} that can reach the network hardware and thus the test run
+could be carried out with real data.
 
@@
 release in the repository on the basis of
-\href{https://github.com/features/actions}{GithubActions}. Here there is
-the possibility to host local runner software, which then has access to
-the hardware, but then a \gls{pc} must be permanently available for this
-task. Instead, the hardware sensors are simulated by software and
+\href{https://github.com/features/actions}{GithubActions}. It has the
+possibility to host local runner software, which then has access to the
+hardware, but in this case a \gls{pc} must be permanently available for
+this task. Instead, the hardware sensors are simulated by software and
 executed via virtualisation on the services systems.
@@
 installation of all \gls{mrp} modules. As it is created in the Python
-programming language, there are several public package registry where
-users can provide their software modules. Here,
-\href{https://pypi.org}{PyPI} screenshot shown in figure
+programming language, there are several public package registries where
+users can provide their software modules.
+
+For this purpose \href{https://pypi.org}{PyPI} figure
 \ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png} is the most
 commonly used package registry and offers direct support for the package
-installation program \gls{pip} \ref{lst:setup_lib_with_pip}.
+installation program \gls{pip} shown in listing
+\ref{lst:setup_lib_with_pip}.
 
@@
 package in an isolated environment and then provide an installation
-\href{https://peps.python.org/pep-0427/}{wheel} archive. This can then
-be uploaded to the package registry. Since the \gls{mrp}-library
-requires additional Python dependencies, which cannot be assumed to be
-already installed on the target system, these must be installed prior to
-the actual installation. These can be specified in the library
-installation configuration \emph{setup.py} \ref{lst:setup_py_req} for
-this purpose.
+\href{https://peps.python.org/pep-0427/}{wheel} archive. This can be
+uploaded to the package registry. Since the \gls{mrp}-library requires
+additional Python dependencies, which cannot be assumed to be already
+installed on the target system, these must be installed prior to the
+actual installation. These can be specified in the library installation
+configuration \emph{setup.py} in listing \ref{lst:setup_py_req} for this
+purpose.
 
@@
 
-To make the \gls{cli} scripts written in Python easier for the user to
-execute without having to use the \emph{python3} prefix. This has been
-configured in the installation configuration using the
+The \gls{cli} scripts are written in Python and simplifiys the execution
+for the user since there ist no \emph{python3} prefix needed. This has
+been configured in the installation configuration using the
 \emph{entry\_points} option, and the following commands are available to
@@
 
-In order to provide comprehensive documentation for the enduser, the
+In order to provide comprehensive documentation for the end-user, the
 source code is documented using
@@
 further development, as modern \gls{ide}s can more reliably display
-possible methods to the user as an assistance. \ref{lst:pydocstring}
+possible methods to the user as an assistance. It is implemented in
+listing \ref{lst:pydocstring}.
 
@@
   :type _title: str
-  :param _filename: export graphic to an given absolute filepath with .png
+  :param _filename: export graphic to a given absolute file path with .png
   :type _filename: str
-  :returns: returns the abs filepath of the generated file
+  :returns: returns the abs file path of the generated file
   :rtype: str
@@
 provide simple how-to-use instructions, the documentation framework
-\emph{Sphinx} \cite{SphinxDocumentation} is used for this purpose.
-This framework makes it possible to generate \gls{html} or \gls{pdf}
+\emph{Sphinx} \customcite{G17} is used for this purpose. This framework
+offers the functionality to generate \gls{html} or \gls{pdf}
 documentation from various source code documentation formats, such as
@@
 this also allows to add further user documentation such as examples or
-installation instructions. In order to make the documentation created by
-\emph{Sphinx} accessible to the user, there are, as with the package
-management by \emph{PyPi} services, which provide the \gls{mrp}-library
-documentation online.
+installation instructions.
 
@@
 \ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
-shows a screenshot of the start page, which also shows separate menu
+shows a screenshot of the start page, which also lists separate menu
 items for tutorials on the individual functionalities.
@@
 The practical application of the hardware and software framework is
-shown below. This is shown using the previously defined use cases
-\ref{use-cases}. In the application example, various permanent magnets
-are measured and then sorted according to their field strength. The
-result should then list the magnets that deviate the least from each
-other in terms of their field strength. This is determined using a
-sorting algorithm developed by the user.
+shown below. It is implemented by using the previously defined use cases
+in chapter \emph{Use cases} \ref{use-cases}. In the application example,
+various permanent magnets are measured and then sorted according to
+their field strength. The result should then list the magnets that
+deviate the least from each other in terms of their field strength. This
+is determined using a sorting algorithm developed by the user.
 
 The process is broken down into the following steps and the practical
-application of \emph{User Interaction Points}
+application of \emph{User Interaction Points} in chapter
 \ref{user-interaction-points} is shown:
@@
 \hypertarget{hardware-preparation}{%
-\section{Hardware preparation}\label{hardware-preparation}}
+\section{Hardware Preparation}\label{hardware-preparation}}
 
@@
 
-For the hardware setup, the 3D-Full Sphere \ref{d-full-sphere} sensor is
-used for the evaluation of the framework. As this is equipped with an
-exchangeable magnetic holder mount, suitable holders are required for
-the magnets to be measured. Ten random \emph{N45 12x12x12mm} neodymium
-magnets are used, which are shown in figure
-\ref{Ten_numbered_test_magnets_in_separate_holders.png}.
+For the hardware setup, the 3D-Full Sphere sensor, explained in chapter
+\ref{d-full-sphere}, is used for the evaluation of the framework. As
+this is equipped with an exchangeable magnetic holder mount, suitable
+holders are required for the magnets to be measured. Ten random
+\emph{N45 12x12x12mm} neodymium magnets are used, which are shown in
+figure \ref{Ten_numbered_test_magnets_in_separate_holders.png}.
 
 These are placed in modified 3D printed holders shown in figure
-\ref{Ten_numbered_test_magnets_in_separate_holders.png} and then
-numbered. This allows them to be matched to the measurement results
+\ref{Ten_numbered_test_magnets_in_separate_holders.png} and afterwards
+numbered. This allows to match the magnets to the measurement results
 later.
@@
 
-The configured hardware is then connected to the host system using the
-\emph{MRPcli config setupsensor}-\gls{cli} command. Afterwards, the
-measurement is configured for an measurement run, using the following
-configuration commands from listing
-\ref{lst:evaluation_measurement_config}.
+The configured hardware is connected to the host system using the
+\emph{MRPcli config setupsensor}-\gls{cli} command. The measurement is
+configured for a measurement run, using the following configuration
+commands from listing \ref{lst:evaluation_measurement_config}.
 
@@
 The next step for the user is the implementation of the filter algorithm
-\ref{lst:custom_find_similar_values_algorithm}. This can have any
-function signature and is implemented in the file
+in listing \ref{lst:custom_find_similar_values_algorithm}. This can have
+any function signature and is implemented in the file
 \emph{UDPPFunctionCollection.py}. This Python file is loaded when the
-pipeline is started and all functions that are imported here as a module
-or implemented directly can be called via the pipeline. As this is a
-short algorithm, it is inserted directly into the file.
+pipeline is started and all functions that are imported as a module or
+implemented directly can be called via the pipeline. As this is a short
+algorithm, it is inserted directly into the file.
 
 The parameter \_readings should later receive the imported measurements
-from the \emph{stage rawimport} \ref{lst:pipeline_mrp_evaluation_yaml}
-and the optional \emph{IP\_return\_count} parameter specifies the number
-of best measurements that are returned. The return parameter is a list
-of measurements containing the most similar measurements, measured by
-the smallest distance between all measurements. The distance for each
+from the \emph{stage rawimport} in listing
+\ref{lst:pipeline_mrp_evaluation_yaml} and the optional
+\emph{IP\_return\_count} parameter specifies the number of best
+measurements that are returned. The return parameter is a list of
+measurements containing the most similar measurements, measured by the
+smallest distance between all measurements. The distance for each
 measurement is determined using the centre of gravity function
@@
 The calculated distances from the \emph{CoG} value of the measurements
-to are inserted into a heapq priority queue. Subsequently, as many
-elements of the queue are returned as defined by the
+to are inserted into a \emph{heapq} priority queue. Subsequently, as
+many elements of the queue are returned as defined by the
 \emph{IP\_return\_count} parameter. The actual sorting is carried out by
@@
 
-Another possibility here would be for the user to use a reference
-measurement instead of a simulated ideal magnet as a reference. This can
-come from a magnet selected as a reference magnet. As a result, the
-filter algorithm returns the measurements that are most similar to the
-selected reference magnet.The code snipped
+Another possibility for filterin is to use a reference measurement
+instead of a simulated ideal magnet as a reference, as described before.
+This can initialy come from a magnet selected as a reference magnet. As
+a result, the filter algorithm returns the measurements that are most
+similar to the selected reference magnet. The code snipped in listing
 \ref{lst:custom_find_similar_values_algorithm_refmagnet} shows the
@@
 Once the filter function has been implemented, it still needs to be
-integrated into the analysis
-pipeline\ref{lst:pipeline_mrp_evaluation_yaml}. Here, the example
-pipeline \ref{Example_measurement_analysis_pipeline.png} is simplified
-and an additional stage \emph{find\_similar\_values} has been added,
-which has set \emph{FindSimilarValuesAlgorithm} as the function to be
-called. As a final step, the result is used in the \emph{plot\_filtered}
-stage for visualisation.
+integrated into the analysis pipeline in listing
+\ref{lst:pipeline_mrp_evaluation_yaml}. At this point, he example
+pipeline in figure \ref{Example_measurement_analysis_pipeline.png} is
+simplified and an additional stage \emph{find\_similar\_values} has been
+added, which has set \emph{FindSimilarValuesAlgorithm} as the function
+to be called. As a final step, the result is used in the
+\emph{plot\_filtered} stage for visualisation.
 
@@
 \emph{pipeline\_mrp\_evaluation.yaml} file and is ready for execution.
-This is carried out using the \emph{MRPudpp} \gls{cli}
-\ref{lst:bash_pipeline_mrp_evaluation_yaml}. After the run has been
-successfully completed, the results are saved in the result folder
-specified in the pipeline using the \emph{IP\_export\_folder} parameter.
+This is carried out using the \emph{MRPudpp} \gls{cli}, which is
+described in listing \ref{lst:bash_pipeline_mrp_evaluation_yaml}. After
+the run has been successfully completed, the results are saved in the
+result folder specified in the pipeline using the
+\emph{IP\_export\_folder} parameter.
 
@@
 \ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png}
-shows this result. The plot of the raw measured values is shown on the
-left. The value of the determined \emph{GoG} \(\mu\)T values is plotted
-on ten individual measured values. Here it can be seen that there are
-measured values with larger deviations (see measurement
+summarizes this result. The plot of the raw measured values is
+represented on the left. The value of the determined \emph{GoG} \(\mu\)T
+values is plotted on ten individual measured values. It can be seen that
+there are measured values with larger deviations (see measurement
 \emph{7:0},\emph{10-2:0},\emph{10-1:0}).
@@
 algorithm. As the \emph{IP\_return\_count} parameter is set to four,
-only the four most similar measurements are exported here. It can be
-seen from the plotted \emph{CoG} \(\mu\)T deviation values, that these
-are closest to an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal
+only the four most similar measurements are exported. It can be seen
+from the plotted \emph{CoG} \(\mu\)T deviation values, that these are
+closest to an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal
 value is calculated with the function
@@
 they correspond to the mechanical structure of the used hardware sensor
-\ref{d-full-sphere}.
+in chapter \ref{d-full-sphere}.
 
@@
 Filter Algorithm Implementation}
-\ref{alternative-filter-algorithm-implementation} is executed here, the
-same result is returned if the magnet measurement with \gls{id}
-\emph{5:0} is used as the reference magnet.
+\ref{alternative-filter-algorithm-implementation} is executed at this
+point, the same result is returned if the magnet measurement with
+\gls{id} \emph{5:0} is used as the reference magnet.
 
@@
 In the previous chapter \emph{Use Case Evaluation}
-\ref{use-case-evaluation} it is shown that the implementation of the
-hardware and software framework for various magnetic field sensors is
-successfully implemented.
+\ref{use-case-evaluation} it is demonstrated that the implementation of
+the hardware and software framework for various magnetic field sensors
+is successfully implemented.
 
@@
 After discussing the developed hardware and software components in
-particular, this chapter will answer the question of whether the
+particular, the following chapter answers the question of whether the
 selected sensors meet the requirements:
@@
 \item
-  Automated measurement of the homogeneity of Halbach rings with an
-  accuracy of less than \emph{1000\gls{ppm}}
+  Automated measurement of the homogeneity with an accuracy of less than
+  \emph{1000\gls{ppm}} what is demanded to measure Halbach rings
 \end{itemize}
 
-These questions are answered in the following, as a basic readout and
+These questions are answered in the following as a basic readout and
 analysis functionality platform had to be created first and thus an
@@
 \ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
-are used for sensor characterisation. The additional column for the
-\emph{Background-Noise} is taken from the respective data sheets of the
-sensors and will be verified in the later \emph{Background-Noise}
-measurement \ref{sensor-characterisation-background-noise}.
+are used for sensor characterisation. The selection of sensors is
+described in chapter \ref{sensor-selection}. The additional column for
+the \emph{Background-Noise} is taken from the respective data sheets of
+the sensors and will be verified in the later \emph{Background-Noise}
+measurement in chapter \ref{sensor-characterisation-background-noise}.
 
@@
 
-It is possible to carry out the sensor characterisation shown here for
+It is possible to carry out the sensor characterisation demonstrated for
 other compatible sensors using the same procedure. Pre-configured
-measurements \ref{command-line-interface} and analysis pipelines
-\ref{programmable-data-processing-pipeline}, which are available for
-this purpose, are packaged within the library.
+measurements in chapter \ref{command-line-interface} and analysis
+pipelines in chapter \ref{programmable-data-processing-pipeline}, which
+are available for this purpose, are packaged within the library.
 
@@
 
-The sensor platform used here is an adapted version of the \emph{1D:
-Single Sensor} \ref{d-single-sensor} sensor platform. The sensors to be
-measured are fixed together on an aluminium plate with thermally
+The sensor platform used is an adapted version of the \emph{1D: Single
+Sensor} from chapter \ref{d-single-sensor} sensor platform. The sensors
+to be measured are fixed together on an aluminium plate with thermally
 conductive adhesive. This compensates for thermal differences. This is
@@
 readout hardware, on which the \emph{Unified Sensor Firmware} is
-running. With additional connected switch, its possible to isolate or
+running. With additional connected switch, it is possible to isolate or
 select a sensor or both sensors to be queried from the firmware.
@@
 A separate battery power supply is used as low-noise power supply for
-the sensors boards. An \emph{Raspberry Pi 4} is implemented as the host
+the sensor boards. An \emph{Raspberry Pi 4} is implemented as the host
 computer, which is connected to the sensors via a \emph{Hailege
@@
 field interference. The temperature chamber for all noise tests is set
-to \emph{\(\mu_{trev}\)=21.0\(^{\circ}\)} and the sensors are placed
+to \emph{\(\mu_{trev}\)=21.0\(^{\circ}\)C} and the sensors are placed
 \emph{24} hours before the measurement run in the final measurement
@@
 \ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
-shows the measured values of these sensors. In the next phases these are
-analysed for each sensor examined.
+contains the measured values of these sensors. In the next phases these
+are analysed for each sensor examined.
 
@@
 \item
-  Plot of the sensors internal temperature sensor
+  Plot of the sensor's internal temperature sensor
 \item
@@
 The table \ref{Sensor_noise_evaluation_results.csv} lists the measured
-values that are extracted from the measurement data of the sensors
+values that are extracted from the measurement data of the sensors in
+figure
 \ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}.
@@
 The temperature stability of the \emph{TLV493D} with a mean value of
-\emph{20.68\(^{\circ}\)C} and a \gls{sd} of
-\emph{\(\sigma_{t}\)=0.53\(^{\circ}\)C} indicates a consistent trend.
-This implies a constant tendency. The close grouping of the measured
-values around the mean value indicates good stability. The confidence
-interval is expected to be between \emph{20.15\(^{\circ}\)C} and
-\emph{21.21\(^{\circ}\)C}, which indicates a stable and consistent
-temperature measurement. This result is more noisy compared to the
-temperature stability of the \emph{MMC5603}. Both sensors provide an
-offset to the measured chamber temperature \(\mu_{trev}\).
+20.68\(^{\circ}\)C and a \gls{sd} of \(\sigma_{t}\)=0.53\(^{\circ}\)C
+indicates a consistent trend. This implies a constant tendency. The
+close grouping of the measured values around the mean value indicates
+good stability. The confidence interval is expected to be between
+\emph{20.15\(^{\circ}\)C} and \emph{21.21\(^{\circ}\)C}, which indicates
+a stable and consistent temperature measurement. This result is noisier
+compared to the temperature stability of the \emph{MMC5603}.
+
+Both sensors provide an offset to the measured chamber temperature
+\(\mu_{trev}\).
 
@@
 The noise of a sensor describes unwanted, random fluctuations or signals
-in the measured data. These are clearly recognisable in the figure ** in
-the raw data plot. The baseline determined for each sensor is shown by
-the red ** line. Here it can be seen that each sensor has a different
-mean value or baseline offset in the same environment.
-
-The noise of a sensor describes unwanted, random fluctuations or signals
 in the measured data. These are clearly recognisable in the figure
@@
 in the raw data plot. The baseline determined for each sensor is shown
-by the red \(\mu_{rv}\) {[}\(\mu\)T{]} line. Here can be seen that each
+by the red \(\mu_{rv}\) {[}\(\mu\)T{]} line. It can be seen that each
 sensor has a different mean value or baseline offset in the same
@@
 specified by the manufacturer. The \gls{sd} approaches
-\emph{\(\sigma_{rv}\)=0.20\(^{\mu}\)T} and is negligible, especially
-when additional averaging is used.
-
-As the baseline was determined first for each sensor, it can be seen
-that the Another recognisable feature is Further measurement series were
-also recorded with inserted \emph{N45 12x12x12mm} magnets, so that these
-are saturated halfway through the measurement range. This allows the
-noise measurement values to be compared with a blank measurement. These
-values correspond, so it can be concluded that the noise is within the
-same range across the measuring range.
+\emph{\(\sigma_{rv}\)=0.20\({\mu}\)T} and is negligible, especially when
+additional averaging is used.
+
+As the baseline is determined first for each sensor, it can be seen that
+the Another recognisable feature is Further measurement series are also
+recorded with inserted \emph{N45 12x12x12mm} magnets, so that these are
+saturated halfway through the measurement range. This allows the noise
+measurement values to be compared with a blank measurement. These values
+correspond, so it can be concluded that the noise is within the same
+range across the measuring range.
 
@@
 
-This is achieved here by means of an additional linear axis installed
-above the sensor setup. A holder for an \emph{N45 12x12x12mm} magnet is
+This is achieved by means of an additional linear axis installed above
+the sensor setup. A holder for an \emph{N45 12x12x12mm} magnet is
 attached to the end effector of this axis, which can thus be moved at
 different distances above the respective sensor \gls{ic}. The ambient
-temperature is set to \emph{\(\mu_{trev}\)=21.0\(^{\circ}\)} in the
+temperature is set to \emph{\(\mu_{trev}\)=21.0\(^{\circ}\)C} in the
 measurement runs and thus corresponds to the same conditions as in the
-\emph{Background-Noise}\ref{sensor-characterisation-background-noise}
-setup.
+\emph{Background-Noise} chapter
+\ref{sensor-characterisation-background-noise} setup.
 
 The figure \ref{Sensor_evaluation_setup_for_linearity_measurements.png}
-shows this updated measurement setup with the added components. To
-control the linear axis, an additional motion controller of the type
+contains this updated measurement setup with the added components. To
+control the linear axis an additional motion controller of the type
 \emph{SKR-Pico} placed outside the temperature chamber is required,
@@
 The measurement run is then started using a script. The user defines the
-path to be travelled by the linear axis. The complete range of
-\emph{120mm} in \emph{1mm} steps is selected here. The following
-automated process then runs as follows:
+path to be travelled by the linear axis. A complete range of
+\emph{120mm} in \emph{1mm} steps is selected. The following automated
+process then runs as follows:
 
@@
 
-After the measurements are exported, they are analysed for linearity
-using \emph{MRPAnalysis} \ref{mrpanalysis} functions.
+After the measurements are exported, these are analysed for linearity
+using \emph{MRPAnalysis} functions in chapter \ref{mrpanalysis}.
 
@@
 \ref{Sensor_linearity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
-shows the visual representation of linearity as a plot. The distance
+combines the visual representation of linearity as a plot. The distance
 from the magnet to the sensor is plotted in \emph{mm} on the x-axis. The
@@
 resolution. With the \emph{MMC5603NJ} this is on average only
-\emph{0.04\%}. With the \emph{TLV493D}, however, the \gls{sd} is
-\emph{3.64\%}, for which the deviations at the end in particular (with
-field strengths towards zero) are decisive. The previously performed
-\emph{Background-Noise} \ref{sensor-characterisation-background-noise}
-characterisation shows that the linearity deviation here is due to the
-sensitivity of the sensor.
+\emph{0.04\%}. With the \emph{TLV493D} the \gls{sd} is \emph{3.64\%},
+for which the deviations at the end in particular (with field strengths
+towards zero) are decisive. The previously performed
+\emph{Background-Noise} characterisation in chapter
+\ref{sensor-characterisation-background-noise} is explained that the
+linearity deviation is due to the sensitivity of the sensor.
 
@@
 specifications of both sensors, which specify a value of \emph{5\%}. It
-is also possible to calculate these small deviations using curve fitting
+is also feasible to calculate these small deviations using curve fitting
 methods. Suitable functions are implemented in the library.
@@
 \ref{Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}
-shows these modifications in detail. These changes makes it possible to
-accurately determine the sensors \gls{ic} temperature. The temperature
-measuring device \emph{VC-7055BT} can be analysed using a \gls{pc}
-interface. The controller of the temperature chamber can also be
-programmed via a \gls{pc} interface and a target temperature can be
+represents these modifications in detail. These changes makes it
+possible to accurately determine the sensors \gls{ic} temperature. The
+temperature measuring device \emph{VC-7055BT} can be analysed using a
+\gls{pc} interface. The controller of the temperature chamber can also
+be programmed via a \gls{pc} interface and a target temperature can be
 specified.
@@
 
-The same procedure is used as for the \emph{Linearity}
-\ref{sensor-characterisation-linearity} measurement, except that instead
-of moving the linear axis, the temperature of the temperature chamber is
+The same procedure is used as for the \emph{Linearity} measurement in
+chapter \ref{sensor-characterisation-linearity}, except that instead of
+moving the linear axis, the temperature of the temperature chamber is
 systematically increased from \emph{20\(^{\circ}\)} to
@@
 \emph{\textgreater=80\(^{\circ}\)} for non-high-quality type N magnets
-\cite{magna-c}). The temperature range is selected so that it is
+\customcite{GKT16}). The temperature range is selected so that it is
 within a sufficient range for the application.
@@
 \ref{Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
-shows the measured data as a plot with the temperature measured by the
-measuring devices on the X-axis and the sensor measured value on the
+represents the measured data as a plot with the temperature measured by
+the measuring devices on the X-axis and the sensor measured value on the
 Y-axis. The ideal baseline is also shown as a red line. It can be seen
@@
 The graph of the \emph{TLV493d} is significantly steeper with a gradient
-of \emph{-5.13 \(\mu\)T / \(^{\circ}\)C}, and it is also not as linear
-as the \emph{MMC5603NJ}; there are clear jumps in the gradient. However,
-the total change between the temperature regions of \emph{175\(\mu\)T}
-is less than that of the \emph{MMC5603NJ} with \emph{70\(\mu\)T}, if the
-total measurement range of the sensors is also taken into account.
+of -5.13 \(\mu\)T / \(^{\circ}\)C, and it is also not as linear as the
+\emph{MMC5603NJ}; there are clear jumps in the gradient. However, the
+total change between the temperature regions of 175\(\mu\)T is less than
+that of the \emph{MMC5603NJ} with \emph{70\(\mu\)T}, if the total
+measurement range of the sensors is also taken into account.
 
 In the evaluation (see figure
-\ref{Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}),
-a linear function was also calculated using curve fitting to determine
+\ref{Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png})
+a linear function is also calculated using curve fitting to determine
 the temperature coefficients of the sensors. This makes it possible to
@@
 
-Table \ref{Overview_of_all_characterised_sensor_properties.csv} shows a
-summary of all recorded and analysed measured values of the two
-characterised sensors \emph{TLV493D} and \emph{MMC5603NJ}. It can be
+Table \ref{Overview_of_all_characterised_sensor_properties.csv}
+represents a summary of all recorded and analysed measured values of the
+two characterised sensors \emph{TLV493D} and \emph{MMC5603NJ}. It can be
 clearly seen that these differ significantly by a factor of \emph{x10}.
@@
 the large measuring range, which fulfils the required specifications
-from chapter \emph{Research Question}
+from chapter \emph{Research Question} in chapter
 \ref{research-question-and-approach}, must be taken into account here,
@@
 temperature coefficients. In the following chapter, recommendations for
-action are defined, which were derived from the analysis results.
+action are defined, which are derived from the analysis results.
 
@@
 
-In the following, methods will be shown with which it is nevertheless
-possible to use these sensors.
-
-\hypertarget{permanent-magnet-charakterisation}{%
+In the following, alternative methods for sensor adaptions will be
+described that the sensors can still be used for these measurement.
+
+\hypertarget{permanent-magnet-characterisation}{%
 \subsubsection{Permanent Magnet
-charakterisation}\label{permanent-magnet-charakterisation}}
+Characterisation}\label{permanent-magnet-characterisation}}
 
@@
 The \emph{MMC5603NJ} sensor has a limited measuring range, which means
-that it may not the best choise for this application parameters.
-However, this limitation also makes it possible to compare relative
-magnetic field strengths with each other. Furthermore, by using
+that it may not the best choice considering these application
+parameters. However, this limitation also makes it possible to compare
+relative magnetic field strengths with each other. Furthermore, by using
 software, it is possible to achieve absolute comparability of the
-magnetic fields by scaling the measured values accordingly. This was
+magnetic fields by scaling the measured values accordingly. This is
 shown in the chapter \emph{Use Case Evaluation}
@@
 
-The \emph{MMC5603NJ} cannot be used here due to the limited value range.
-The method of increasing the distance, as with permanent magnet
-characterisation, cannot be used here as the magnet is located within a
+The \emph{MMC5603NJ} cannot be used for this due to the limited value
+range. The method of increasing the distance, as with permanent magnet
+characterisation, cannot be used as the magnet is located within a
 limited space in the Halbach ring.
@@
 \emph{50\(\mu\)T} with the \emph{TLV493D}. As a test, several further
-measurement runs were carried out, which achieved results for the sensor
+measurement runs are carried out, which achieved results for the sensor
 noise of \emph{71\(\mu\)T} to \emph{41\(\mu\)T} when averaging
@@
 
-In general post-processing of the measurements should, include
+In general, post-processing of the measurements should, include
 temperature compensation with a separate temperature sensor, especially
@@
 
-A solid foundation has been built in this version of the framework,
-which contains all the necessary functions and is ready for immediate
-use. During development, particular emphasis is placed on comprehensive
+A solid basement has been built in this version of the framework, which
+contains all the necessary functions and is ready for immediate use.
+During development, particular emphasis is placed on comprehensive
 documentation to make it easier to get started. Together with examples
@@
 created that can be used directly for the intended purpose. It provides
-a suitable working foundation, but can be further developed by
-integrating professional measurement devices to enable a more
-comprehensive evaluation and improvement of the sensor hardware.
+a suitable base for working, but further developments by integrating
+professional measurement devices to enable a more comprehensive
+evaluation and improvement of the sensor hardware are necessary.

### 2024-02-17 documentation/thesis/generate_citealias.py

@@ -32,25 +32,26 @@ text_content:str = ""
 lines : [str] = []
 
 out_lines : [str] = []
+
+pattern: [] = [r"\\cite{(\w+)}", r"\\customcite{(\w+)}", r"\\autocite{(\w+)}"]
 with open(file_to_open,'r') as file:
     text_content = file.read()
     #lines = text_content.split('\n')
     
-    
-    regex_pattern = r"\\customcite{(\w+)}"
-    regex = re.compile(regex_pattern, re.IGNORECASE) # FOR CLOSING CASE ```
+    for rp in pattern:
+        regex = re.compile(rp, re.IGNORECASE) # FOR CLOSING CASE ```
 
-    groups = re.findall(regex, text_content)
-    unique_groups = list(set(groups))
-    # SCAN FOR \customcite{ AND PARSE \customcite{xXx}
-    # GET GROUPS
-    for idx, gr in enumerate(unique_groups):
-        
-        cite: str = gr #"SB2010"
-        cite_text: str = gr #"SB2010"
-        #xout_lines.append("\\"+"citefield{"+ "{}".format(cite) + "}{"+ "{}".format('shortauthor') + "}")
-        out_lines.append("\\"+"defcitealias{"+ "{}".format(cite) + "}{"+ "{}".format(cite_text) + "}")
-        out_lines.append("\n")
+        groups = re.findall(regex, text_content)
+        unique_groups = list(set(groups))
+        # SCAN FOR \customcite{ AND PARSE \customcite{xXx}
+        # GET GROUPS
+        for idx, gr in enumerate(unique_groups):
+            
+            cite: str = gr #"SB2010"
+            cite_text: str = gr #"SB2010"
+            #out_lines.append("\\"+"citefield{"+ "{}".format(cite) + "}{"+ "{}".format('shortauthor') + "}")
+            out_lines.append("\\"+"defcitealias{"+ "{}".format(cite) + "}{"+ "{}".format(cite_text) + "}")
+            out_lines.append("\n")
 
 
 

### 2024-02-17 documentation/thesis/thesis_document.tex
.

@@
 cross-sectional black-and-white images of the body. This indispensable
-method plays a central role in contemporary medicine and research,
+method plays a significant role in contemporary medicine and research,
 contributing significantly to saving lives. Despite its widespread use,
@@
 
-Various types of magnets are applicated in different \gls{mri} systems.
+Several types of magnets are applicated in different \gls{mri} systems.
 Permanent magnets generate a steady yet relatively weak magnetic field,
@@
 homogeneity can be measured post-assembly, the intricate task of
-readjustment is taken into account. It is less cost-intensive and less
+readjustment is considered. It is less cost-intensive and less
 complicated to measure the magnets proactively, prior to the
@@
 comprehensive hardware and software framework. The hardware system aims
-to selectively measure magnetic fields at different locations or fully
+to selectively measure magnetic fields at various locations or fully
 around a permanent magnet using different sensors. Several existing
@@
 less than \emph{50\(\mu\)T} to characterise precisely a magnetic field
-in a Halbach-Array of an \gls{mri}with precision greater than
-\emph{1000\gls{ppm}}.
+in a Halbach-Array of an \gls{mri} with precision greater than
+\emph{1000 \gls{ppm}}.
 
@@
 
-The positioning of permanent magnets holds an important role in
+The positioning of permanent magnets holds a significant role in
 constructing an \gls{mri} and is influencing the homogeneity of the
@@
   \textbf{Material}: The magnetic properties of a material influence the
-  generated field strength. Different materials have different magnetic
+  generated field strength. Various materials have different magnetic
   susceptibilities.
@@
 diameter, a \emph{B0} field strength of 50.4mT, and an impressive
-homogeneity of 2400\gls{ppm} over a \emph{20cm} diameter using smaller
-magnets (\(12 x 12 x 12 mm^3\)). This exceptional homogeneity enables
-the utilization of coil-based gradients for spatial encoding,
+homogeneity of \emph{2400 \gls{ppm}} over a \emph{20cm} diameter using
+smaller magnets (\(12 x 12 x 12 mm^3\)). This exceptional homogeneity
+enables the utilization of coil-based gradients for spatial encoding,
 significantly enhancing the flexibility of image acquisition.
@@
 diameter, a \emph{B0} field strength of \emph{50.4 mT}, and an
-impressive homogeneity of \emph{2400}\gls{ppm} over a \emph{20cm}
+impressive homogeneity of \emph{2400 \gls{ppm}} over a \emph{20cm}
 diameter using smaller magnets (\(12 x 12 x 12 mm^3\)). This exceptional
@@
 Special algorithms from various, public projects are used to optimize
-homogeneity, like a genetic algorithms which O'Reilly implemented
+homogeneity, like a genetic algorithm which O'Reilly implemented
 \customcite{O24}. Therefore, the challenge is to ensure the seamless
@@
 The focus of the ongoing efforts is to improve the homogeneity of
-magnets within low-field \gls{mri}systems below \emph{1000}\gls{ppm},
+magnets within low-field \gls{mri}systems below \emph{1000 \gls{ppm}},
 primarily driven by the goal of establishing a compact low-field
@@
 In addition, \emph{DeLoRI} efforts to achieve heightened accuracy,
-striving for precision levels below 1000\gls{ppm}. While O'Reilly,
-Teeuwisse, and Webb were able to modify the ring diameter to influence
-field homogeneity, the unique goal at this point is to characterize the
-magnets pre-installation, allowing for proactive assessments of
-homogeneity characteristics. This approach aims to provide insights into
-magnetic field uniformity before the magnets are integrated, thereby
-streamlining the optimisation process. Furthermore,
+striving for precision levels below \emph{1000 \gls{ppm}}. While
+O'Reilly, Teeuwisse, and Webb were able to modify the ring diameter to
+influence field homogeneity, the unique goal at this point is to
+characterize the magnets pre-installation, allowing for proactive
+assessments of homogeneity characteristics. This approach aims to
+provide insights into magnetic field uniformity before the magnets are
+integrated, thereby streamlining the optimisation process. Furthermore,
 
@@
 The ultimate objective is to assess whether these selected sensors align
-with the stringent criteria of achieving an accuracy level of
-\emph{1000}\gls{ppm}. Furthermore, the study seeks to validate whether
-the measuring range of these sensors appropriately corresponds to the
+with the stringent criteria of achieving an accuracy level of \emph{1000
+\gls{ppm}}. Furthermore, the study seeks to validate whether the
+measuring range of these sensors appropriately corresponds to the
 required field strength, ensuring their suitability for the intended
@@
 difference and connection between deviation and resolution of the
-system. To measure a deviation of better than \emph{1000}\gls{ppm} in a
-\emph{50mT} magnetic field, a resolution that is less than
-\emph{1000}\gls{ppm} of \emph{50mT} is needed.
+system. To measure a deviation of better than \emph{1000 \gls{ppm}} in a
+\emph{50mT} magnetic field, a resolution that is less than \emph{1000
+\gls{ppm}} of \emph{50mT} is needed.
 
@@
   measure the homogeneity of a Halbach ring-based B0 field within the
-  stringent limit of less than \emph{1000}\gls{ppm}? The desired outcome
-  is a measurement of less than \emph{50} \(\mu\)T at
-  \emph{1000}\gls{ppm}, with a specific focus on determining the
-  sensors' viability for noise measurements.
+  stringent limit of less than \emph{1000 \gls{ppm}}? The desired
+  outcome is a measurement of less than \emph{50} \(\mu\)T at \emph{1000
+  \gls{ppm}}, with a specific focus on determining the sensors'
+  viability for noise measurements.
 \end{itemize}
@@
 
-The following chapter defines possible use cases that the future project
-need to cover. These use cases define the setup of the hard- and
+The following chapter defines desirable use cases that the future
+project need to cover. These use cases define the setup of the hard- and
 software. These illustrate practical situations to understand the
@@
 
-The use cases are defined in the course of project planning and provide
-an overview of how the user interacts with the project and what
+The use cases are defined during project planning and provide an
+overview of how the user interacts with the project and what
 functionalities can be expected. In the later accomplished evaluation
@@
 the solution. This is essential for understanding the needs of the
-target group and designing the end result accordingly.
+target group and designing the result accordingly.
 
@@
 Finally, a comprehensive hardware and software framework needs to be
-established, which is capable of measuring diverse objects using various
-sensors. Additionally, remarks need to be provided regarding the
-suitability of the employed sensors for magnetic field measurements.
+established, which can measure diverse objects using various sensors.
+Additionally, remarks need to be provided regarding the suitability of
+the employed sensors for magnetic field measurements.
 
@@
 
-It simplifies of own measuring devices into the \gls{mrp} ecosystem at a
-later date. This is only applicable with a minimal functional hardware
-and firmware setup; it is developed for this purpose in the first step.
+It simplifies of own measuring devices into the \gls{mrp} ecosystem
+later. This is only applicable with a minimal functional hardware and
+firmware setup; it is developed for this purpose in the first step.
 
@@
 The selection process for possible magnetic field sensors initially
-focisses on the most common and cost-effective ones, especially those
+focuses on the most common and cost-effective ones, especially those
 that are already used in smartphones and are therefore widely available.
@@
 \ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
-with regard to their sensitivity and other parameters. This is done at
-this point, as the components of the readout interface that enable
+regarding their sensitivity and other parameters. This is done at this
+point, as the components of the readout interface that enable
 interaction with the sensors are considered first.
@@
 
-All parts are produced using 3D printing additive manufacturing proces.
+All parts are produced using 3D printing additive manufacturing process.
 The sensor circuit board is glued underneath the magnet holder. This is
@@
 the magnet to be inserted into the holder with repeat accuracy and
-without backlash. This is important if several magnets have to be
-measured, where the positioning over the sensor must always be the same.
+without backlash. This is important if several magnets must be measured,
+where the positioning over the sensor must always be the same.
 
@@
 but also ensured a cost-efficient realisation. A \emph{Raspberry Pi
-Pico} and a \emph{STM32F4} are used as an computer-sensor interface for
-this thesis, which are populare, cost-effective and simple to implement.
+Pico} and a \emph{STM32F4} are used as a computer-sensor interface for
+this thesis, which are popular, cost-effective and simple to implement.
 
@@
 \gls{pcb}, it is possible to attach various mechanical mounts on top of
-the sensor \gls{ic}s. These hole are necessary for later adaptions and
+the sensor \gls{ic}s. These holes are necessary for later adaptions and
 sensor changes, such as different magnet holders or measurement
@@
 SYNC-\gls{gpio} connector. This enables subsequent multi-sensor
-synchronization and also offers options for later sensor-extensions.
-This functionality opens up the possibility of synchronising data from
-different sensors to achieve precise and coherent measurement results.
-Overall, this integrated approach represents an effective solution for
-the flexible evaluation of sensors and helps to optimise the development
+synchronization and offers options for later sensor-extensions. This
+functionality opens the possibility of synchronising data from different
+sensors to achieve precise and coherent measurement results. Overall,
+this integrated approach represents an effective solution for the
+flexible evaluation of sensors and helps to optimise the development
 process.
@@
 
-It handles communication with sensors, actuators and other peripheral
+It manages communication with sensors, actuators and other peripheral
 devices, processing data and making decisions. Firmware is critical to
@@
 
-An important component is that as many common sensors as possible can be
-easily connected without having to adapt the firmware. This modularity
-is implemented using abstract class design. These are initiated
-according to the sensors found at startup. If new hardware needs to be
-integrated, only the required functions in listing
-\ref{lst:CustomSensorClass} need to be implemented.
+A key component is that as many common sensors as possible can be easily
+connected without having to adapt the firmware. This modularity is
+implemented using abstract class design. These are initiated according
+to the sensors found at startup. If new hardware needs to be integrated,
+only the required functions in listing \ref{lst:CustomSensorClass} need
+to be implemented.
 
@@
   ~CustomSensor();
-  // implement depending sensor communication interface
+  // implement depending on sensor communication interface
   bool begin(TwoWire& _wire_instance); // I2C
   bool begin(HardwareSerial& _serial_instance); // UART
-  bool begin(Pin& _pin_instance); // ANALOG or DIGITAL PIN like onewire
+  bool begin(Pin& _pin_instance); // ANALOG or DIGITAL PIN like one wire
   // FUNCTIONS USED BY READOUT LOGIC
@@
 synchronisation described in chapter
-\ref{sensor-syncronisation-interface}. The last step in the setup is to
+\ref{sensor-synchronisation-interface}. The last step in the setup is to
 configure communication with the host or connected \gls{pc}. All
@@
 After execution of the setup routine is completed, the system switches
-to an infinite loop, which processes several possible actions. One task
-is, to react to user commands which can be sent to the system by the
-user via the integrated \gls{cli}. All sensors are read out via a timer
-interval set in the setup procedure and their values are stored in a
-ring buffer. Ring buffer offers efficient data management in limited
-memory. Its cyclic structure enables continuous overwriting of older
-data, saves memory space and facilitates seamless processing of
-real-time data.
+to an infinite loop, which processes several actions. One task is, to
+react to user commands which can be sent to the system by the user via
+the integrated \gls{cli}. All sensors are read out via a timer interval
+set in the setup procedure and their values are stored in a ring buffer.
+Ring buffer offers efficient data management in limited memory. Its
+cyclic structure enables continuous overwriting of older data, saves
+memory space and facilitates seamless processing of real-time data.
 
@@
 measurements are synchronized in time like described in chapter
-\ref{sensor-syncronisation-interface} and are not out of sequence or
+\ref{sensor-synchronisation-interface} and are not out of sequence or
 drift.
@@
 
-\hypertarget{sensor-syncronisation-interface}{%
-\subsection{Sensor Syncronisation
-Interface}\label{sensor-syncronisation-interface}}
+\hypertarget{sensor-synchronisation-interface}{%
+\subsection{Sensor Synchronisation
+Interface}\label{sensor-synchronisation-interface}}
 
@@
 is that the measurements may drift over time. On the one hand, \gls{usb}
-latencies can occur. This can occur due to various factors, including
+latencies can occur. This can occur due to numerous factors, including
 device drivers, data transfer speed and system resources. High-quality
@@
 
-It can be seen that a jitter time of up to an additional \emph{1ms} is
-added between the triggering of the measurements by the host system and
-the receipt of the command by the sensor hardware. If the host system is
-still under load, this value increases many times over. This means that
-synchronising several sensors via the \gls{usb} connection alone is not
-sufficient.
+A jitter time of up to an additional \emph{1ms} is added between the
+triggering of the measurements by the host system and the receipt of the
+command by the sensor hardware. If the host system is still under load,
+this value increases many times over. This means that synchronising
+several sensors via the \gls{usb} connection alone is not sufficient.
 
@@
 
-In order to enable the most stable possible synchronisation between
-several sensors, an option has already been created to establish an
-electrical connection between sensors. This is used together with the
-firmware to synchronise the readout intervals. The figure
+To enable the most stable possible synchronisation between several
+sensors, an option has already been created to establish an electrical
+connection between sensors. This is used together with the firmware to
+synchronise the readout intervals. The figure
 \ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
-illustrates the schematic how several sensors must be wired together in
-order to implement this form of synchronisation.
+illustrates the schematic how several sensors must be wired together to
+implement this form of synchronisation.
 
@@
 for an initial pulse on the SYNC-\gls{gpio}, which is a pin at the
-microcontroller with the funtionality to detect if the sensor is a
+microcontroller with the functionality to detect if the sensor is a
 primary or a secondary sensor. A random timer is started beforehand by
@@
 magnetic field sensors. These cover all the required functions described
-in the use cases \ref{use-cases}. The most important difference, apart
+in the use cases \ref{use-cases}. The most significant difference, apart
 from the sensor used, is the \emph{scan mode}. In this context, this
@@
 of four 3D printed components, which are fixed together with nylon
-screws to minimise possible influences on the measurement.
+screws to minimise influences on the measurement.
 
@@
 The designed magnet holder can be adapted for different magnet shapes
-and can be placed on the spacer without backlash in order to be able to
-perform a repeatable measurement without introducing measurement
-irregularities by mechanically changing the magnet.
+and can be placed on the spacer without backlash to be able to perform a
+repeatable measurement without introducing measurement irregularities by
+mechanically changing the magnet.
 
@@
 The magnet sensor is mounted on a movable arm, which can move 180
-degrees around the magnet on one axis. In order to be able to map the
-full sphere, the magnet is mounted on a turntable. This permits the
+degrees around the magnet on one axis. To be able to map the full
+sphere, the magnet is mounted on a turntable. This permits the
 manipulator to move a polar coordinate system.
@@
 GM-70} telsameter shown in figure
-\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
-used, which has a measuring range of \emph{0T} to \emph{3T} with a
+\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board_using_a_(+usb)_to_serial_converter_and_needed_additional_pull-up_resistors.png}
+is used, which has a measuring range of \emph{0T} to \emph{3T} with a
 resolution of \emph{0.1mT}. It offers an \emph{RS232} interface with a
@@
 
-This software or hardware integration can be carried out on any other
+This software or hardware integration can be conducted on any other
 measuring device with a suitable communication interface and a known
@@
 \centering
-\includegraphics{./generated_images/border_Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png}
+\includegraphics{./generated_images/border_Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board_using_a_(+usb)_to_serial_converter_and_needed_additional_pull-up_resistors.png}
 \caption{Voltcraft GM70 teslameter with custom \gls{pc} interface board
-\label{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png}}
+using a \gls{usb} to serial converter and needed additional pull-up
+resistors
+\label{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board_using_a_(+usb)_to_serial_converter_and_needed_additional_pull-up_resistors.png}}
 \end{figure}
@@
 The data structures are not compatible with each other. However, they
-are executed manually one after the other to obtain a final result with
-manual data conversation.
+are executed manually one after the other to obtain a result with manual
+data conversation.
 
@@
 should also be possible to import field data in a more measured form
-later on. Using the DataAquisition sub-step, it is possible to generate
-any number of ideal magnets.
+later. Using the DataAquisition sub-step, it is possible to generate any
+number of ideal magnets.
 
@@
 
-Next, the user creates his own analysis step in order to be able to call
-up its functions. In the case of the \emph{HalbachOptimisation}
-\customcite{O24} project, the function signature of the start function
-must be changed. This receives the result of the previous step, in this
-case the generated magnet data. By optionally setting meta data in the
-universal library data type, constants can be replaced in the analysis
-function and made dynamically configurable. The return result also
-corresponds to this data type so that subsequent steps are compatible
-and contains the magnet data with modified position and rotation data.
+Next, the user creates his own analysis step to be able to call up its
+functions. In the case of the \emph{HalbachOptimisation} \customcite{O24}
+project, the function signature of the start function must be changed.
+This receives the result of the previous step, in this case the
+generated magnet data. By optionally setting meta data in the universal
+library data type, constants can be replaced in the analysis function
+and made dynamically configurable. The return result also corresponds to
+this data type so that subsequent steps are compatible and contains the
+magnet data with modified position and rotation data.
 
@@
 the configuration file is loaded from the file system. This logic needs
-to be removed in order to use the added meta data as input parameter
-instead.
+to be removed to use the added meta data as input parameter instead.
 
@@
 For this purpose, an open, documented export format must be selected.
-Ideally, this should be human-readable and viewable with a simple text
+Ideally, this should be human-readable and viewable with a plain text
 editor. This eliminates all binary-based formats such as the
@@
 Taking these points into account, the \gls{json} format is chosen. This
-is human and machine readable and there is a compatible parser for
-almost every programming language.
+is human and machine readable and there is a compatible parser for every
+programming language.
 
@@
 example \gls{json} structure which is generated when a measurement that
-using the library is dumped to the filesystem. It can be seen that by
-using the \gls{json} format, all measurement points and metadata are
-available in readable plain text.
+using the library is dumped to the filesystem. By using the \gls{json}
+format, all measurement points and metadata are available in readable
+plain text.
 
@@
 
-\begin{lstlisting}[caption={JSON export structure of an MRPReading based measurement}, label=lst:json_export_format_example]
+\begin{lstlisting}[caption={JSON structure of an exported MRPReading based measurement with information about the measurement environment, additional meta-data and raw data value objects}, label=lst:json_export_format_example]
 {
@@
 
-In order to give the user the possibility to display the recorded data
-visually, two modules are created, which can graphically prepare
-\emph{MRPReading} instances:
+To give the user the possibility to display the recorded data visually,
+two modules are created, which can graphically prepare \emph{MRPReading}
+instances:
 
@@
 the network. This can be a \gls{sbc} (e.g.~a \emph{Raspberry Pi}). The
-small footprint and low power consumption make it a good choice. It can
-also be used in a temperature chamber.
+small footprint and low power consumption make it a viable choice. It
+can also be used in a temperature chamber.
 
@@
 the proxy module, it is possible to link several instances and all
-sensors available in the network are accessable to the \emph{control}
+sensors available in the network are accessible to the \emph{control}
 \gls{pc}.
@@
 
-\begin{lstlisting}[language=bash, caption={MRPproxy usage to enable local sensor usage over network}, label=lst:mrpcli_proxy_start]
+\begin{lstlisting}[language=bash, caption={MRPproxy usage to enable local sensor forwarding over the network.
+The (+cli) output shows the available sensor to the connected (+host) pc}, label=lst:mrpcli_proxy_start]
 # START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
@@
 
-\begin{lstlisting}[language=bash, caption={MRPProxy REST endpoint query examples}, label=lst:mrpcli_config_rest]
+\begin{lstlisting}[language=bash, caption={MRPProxy provided (+rest) endpoint query example using wget command line tool to send requests}, label=lst:mrpcli_config_rest]
 # GET PROXY STATUS
@@
 
-\begin{lstlisting}[language=bash, caption={MRPcli usage example to connect with a network sensor}, label=lst:mrpcli_config_using_rpc]
+\begin{lstlisting}[language=bash, caption={MRPcli usage example to connect with a MRPproxy based network sensor}, label=lst:mrpcli_config_using_rpc]
 # CONFIGURE MEASUREMENT JOB USING A PROXY INSTANCE
@@
 
-\hypertarget{sensor-syncronisation}{%
-\subsection{Sensor Syncronisation}\label{sensor-syncronisation}}
+\hypertarget{sensor-synchronisation}{%
+\subsection{Sensor Synchronisation}\label{sensor-synchronisation}}
 
@@
 central clock as described in chapter
-\ref{sensor-syncronisation-interface}. This no longer works for long
-distances and the syncronisation must be established via a shared
+\ref{sensor-synchronisation-interface}. This no longer works for long
+distances and the synchronisation must be established via a shared
 network connection.
@@
 
-\begin{lstlisting}[language=bash, caption={MRPproxy REST entry point query examples}, label=lst:mtsc]
+\begin{lstlisting}[language=bash, caption={MRPproxy (+rest) capabilities query result after execution of the merging algorithm}, label=lst:mtsc]
 # QUERY Network-Proxy capabilities
@@
 
-In order for the host to be able to send a command to the network
-multi-sensor setup, the command received needs to be forwarded to the
-correct sensor. In addition, there are commands such as the previously
-used \emph{info} or \emph{status} command, which must be intercepted by
-the \emph{MRPProxy} module so that it can be handled differently (see
+For the host to be able to send a command to the network multi-sensor
+setup, the command received needs to be forwarded to the correct sensor.
+In addition, there are commands such as the previously used \emph{info}
+or \emph{status} command, which must be intercepted by the
+\emph{MRPProxy} module so that it can be handled differently (see
 example listing \ref{lst:mtsc}).
@@
 LUT} from table \ref{Sensor_capabilities_merging_algorithm.csv}, there
-are two possible approaches to how the command is processed:
+are two approaches to how the command is processed:
 
@@
 
-An important point is the management of the meta data, which further
+A crucial point is the management of the meta data, which further
 describes the measurement. This is realised in the example using the
@@
 
-\begin{lstlisting}[language=Python, caption={MRPReading example for setting up a basic measurement}, label=lst:mrpexample_reading]
+\begin{lstlisting}[language=Python, caption={MRPReading example for setting up a basic measurement using Python code}, label=lst:mrpexample_reading]
 from MRP import MRPReading, MRPMeasurementConfig
@@
 
-\begin{lstlisting}[language=Python, caption={MRPHal example to use a connected hardware sensor to store readings inside of a measurement}, label=lst:mrpexample_hal]
+\begin{lstlisting}[language=Python, caption={MRPHal example to use a connected hardware sensor to store raw sensor readings inside of a measurement}, label=lst:mrpexample_hal]
 from MRP import MRPHalSerialPortInformation, MRPHal, MRPBaseSensor, MRPReadingSource
@@
 # OR USE SPECIFIED SENSOR DEVICE
-device_path = MRPHalSerialPortInformation("UNFSensor1")
+device_path = MRPHalSerialPortInformation("UnifiedSensor_4242")
 sensor = MRPHal(device_path)
@@
 # EXPORT TO OPENSCAD
-## 2D MODE DXF e.g. for lasercutting
+## 2D MODE DXF e.g. for laser cutting
 MRPHalbachArrayGenerator.MRPHalbachArrayGenerator.generate_openscad_model([halbach_array], "./2d_test.scad",_2d_object_code=True)
@@
 
-\begin{lstlisting}[language=bash, caption={CLI example for configuring a measurement run}, label=lst:mrpcli_config_run]
+\begin{lstlisting}[language=bash, caption={MRP(+cli) example usage for configuration of a measurement run}, label=lst:mrpcli_config_run]
 # CLI EXAMPLE FOR CONFIGURING A MEASUREMENT RUN
@@
 
-In order to implement such a pipeline, the \emph{yaml} file format is
+In order to implement such a pipeline, the\gls{yaml} file format is
 chosen for the definition of the pipeline, as this is for
@@
 
-The signatures in the \emph{yaml} file are called using reflection and a
+The signatures in the \gls{yaml} file are called using reflection and a
 real-time search of the loaded \emph{global()} functions
 \href{https://docs.python.org/3/library/functions.html#globals}{symbol table}.
-This system makes almost all Python functions available to the user. To
-simplify usage, a pre-defined list of verified functions for use in
-pipelines is listed in the
+This system is capable to make all Python functions available to the
+user. To simplify usage, a pre-defined list of verified functions for
+use in pipelines is listed in the
 \href{https://magneticreadoutprocessing.readthedocs.io/en/latest/}{documentation}.
@@
 \ref{lst:mrpuddp_example_yaml} shows the previously defined steps shown
-in figure \ref{Example_measurement_analysis_pipeline.png} as \emph{yaml}
+in figure \ref{Example_measurement_analysis_pipeline.png} as \gls{yaml}
 syntax.
 
-\begin{lstlisting}[caption={Example YAML code of a user defined processing pipeline with six stages linked together}, label=lst:mrpuddp_example_yaml]
+\begin{lstlisting}[caption={Example (+yaml) code of a user defined processing pipeline with six stages linked together}, label=lst:mrpuddp_example_yaml]
 stage import_readings:
@@
 
-The various steps are linked by using the \emph{stage } makro as input
+The various steps are linked by using the \emph{stage } macro as input
 parameter of the next function to be executed (see comments in listing
@@
 
-Therefore it is feasable to use the results of one function in several
+Therefore, it is feasible to use the results of one function in several
 others without them directly following each other. The disadvantages of
@@
 parameter form the edges. After several simplification steps,
-determination of possible start steps and repeated traversal, the final
-execution sequence can be determined in the form of a call tree in
-figure
+determination of start steps and repeated traversal, the final execution
+sequence can be determined in the form of a call tree in figure
 \ref{Example_result_of_an_step_execution_tree_from_user_defined_processing_pipeline.png}.
 The individual steps are then executed along the graph. The intermediate
-results and the final results in figure
+results and the results in figure
 \ref{Pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
@@
 quality and efficiency. Software tests ease to identify errors and
-vulnerabilities before the software is released as a new version.
+vulnerabilities before the software is released as an updated version.
 
@@
 In the other scenario, the tests are to be carried out before a new
-release in the repository on the basis of
+release in the repository based on
 \href{https://github.com/features/actions}{GithubActions}. It has the
@@
 
-One important point that improves usability for users is the simple
+One crucial point that improves usability for users is the simple
 installation of all \gls{mrp} modules. As it is created in the Python
@@
 \ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png} is the most
-commonly used package registry and offers direct support for the package
+used package registry and offers direct support for the package
 installation program \gls{pip} shown in listing
@@
 
-\gls{pip} not only manages possible package dependencies, but also
-manages the installation of different versions of a package. In
-addition, the version compatibility is also checked during the
-installation of a new package, which can be resolved manually by the
-user in the event of conflicts.
+\gls{pip} not only manages package dependencies, but also manages the
+installation of different versions of a package. In addition, the
+version compatibility is also checked during the installation of a new
+package, which can be resolved manually by the user in the event of
+conflicts.
 
@@
 
-The \gls{cli} scripts are written in Python and simplifiys the execution
-for the user since there ist no \emph{python3} prefix needed. This has
+The \gls{cli} scripts are written in Python and simplify the execution
+for the user since there is no \emph{python3} prefix needed. This has
 been configured in the installation configuration using the
@@
 In addition, these commands are available globally in the system without
-the terminal shell being located in the \gls{mrp}-library folder.
+the terminal shell located in the \gls{mrp}-library folder.
 
@@
 
-In order to provide comprehensive documentation for the end-user, the
-source code is documented using
+To provide comprehensive documentation for the end-user, the source code
+is documented using
 Python-\href{https://peps.python.org/pep-0257/}{Docstrings} and the
@@
 further development, as modern \gls{ide}s can more reliably display
-possible methods to the user as an assistance. It is implemented in
-listing \ref{lst:pydocstring}.
+methods to the user as an assistance. It is implemented in listing
+\ref{lst:pydocstring}.
 
@@
 
-Another possibility for filterin is to use a reference measurement
+Another possibility for filtering is to use a reference measurement
 instead of a simulated ideal magnet as a reference, as described before.
-This can initialy come from a magnet selected as a reference magnet. As
+This can initially come from a magnet selected as a reference magnet. As
 a result, the filter algorithm returns the measurements that are most
@@
 added, which has set \emph{FindSimilarValuesAlgorithm} as the function
-to be called. As a final step, the result is used in the
+to be called. As a decisive step, the result is used in the
 \emph{plot\_filtered} stage for visualisation.
@@
 executed using the user-programmable pipeline. The calculation result is
-successfully verified using raw measurement data and the final result of
-the algorithm.
+successfully verified using raw measurement data and the result of the
+algorithm.
 
@@
   Automated measurement of the homogeneity with an accuracy of less than
-  \emph{1000\gls{ppm}} what is demanded to measure Halbach rings
+  \emph{1000 \gls{ppm}} what is demanded to measure Halbach rings
 \end{itemize}
@@
 and recorded. It is important to carry out the measurement over a
-sufficiently long period of time in order to record both short-term and
-long-term fluctuations. For this purpose, \emph{N=2000} further measured
-values are taken with a trigger and readout rate of one measurement per
-second. In order to quantify the noise, the \gls{sd} of the signal is
-calculated. These parameters provide information about the variation of
-the signal over time and therefore about the sensor background noise.
+sufficiently lengthy period of time in order to record both short-term
+and long-term fluctuations. For this purpose, \emph{N=2000} further
+measured values are taken with a trigger and readout rate of one
+measurement per second. In order to quantify the noise, the \gls{sd} of
+the signal is calculated. These parameters provide information about the
+variation of the signal over time and therefore about the sensor
+background noise.
 
@@
 
-As the temperature sensor \emph{TLV493D} in particular produced very
+As the temperature sensor \emph{TLV493D} in particular produced vastly
 different results in the previous measurements, an additional
@@
 that of the \emph{MMC5603NJ} with \emph{70\(\mu\)T}, if the total
-measurement range of the sensors is also taken into account.
+measurement range of the sensors is also considered.
 
@@
 from chapter \emph{Research Question} in chapter
-\ref{research-question-and-approach}, must be taken into account here,
-which is not met by the \emph{MMC5603NJ}.
+\ref{research-question-and-approach}, must be considered here, which is
+not met by the \emph{MMC5603NJ}.
 
@@
 measurement averaging, very precise measurement results can be achieved,
-which achieve a measurement accuracy of less than \emph{1000\gls{ppm}}.
+which achieve a measurement accuracy of less than \emph{1000 \gls{ppm}}.
 
@@
 In the following, alternative methods for sensor adaptions will be
-described that the sensors can still be used for these measurement.
+described that the sensors can still be used for these measurements.
 
@@
 \hypertarget{homogeneity-measurement-of-a-halbach-ring-based-b0-field}{%
-\subsubsection{Homogeneity Measurement of a Halbach ring-based B0
-field}\label{homogeneity-measurement-of-a-halbach-ring-based-b0-field}}
+\subsubsection{Homogeneity Measurement of a Halbach Ring-based B0
+Field}\label{homogeneity-measurement-of-a-halbach-ring-based-b0-field}}
 
@@
 values cannot be used directly without post-processing. With software
-calibration, it is probably possible to reduce the noise to below
+calibration, it is possible to reduce the noise to below
 \emph{50\(\mu\)T} with the \emph{TLV493D}. As a test, several further

### 2024-02-18 documentation/thesis/thesis_document.tex
.

@@
 
+\newpage
+
 The challenge with conventional homogeneity systems lies in their
 substantial size, weight, and cost. Even when targeting smaller areas of
-the body, large devices are often necessary.
-
-In response to this, there is a growing interest in developing low-field
-\gls{mri} systems that utilize in many cases permanent magnets. These
-systems, while offering advantages in energy efficiency and reduced
-complexity, face a significant challenge related to the inherent
-variability in the strength of permanent magnets. Achieving homogeneity
-in the magnetic field is crucial for accurate imaging or comparative
-analyses. While typically calculated images have lower resolution due to
-lower magnetic field strength, low-field systems facilitate the
-comparison of different field behaviours and the identification of all
-kinds of irritations. O'Reilly and Teeuwisse and de Gans
-\customcite{OTW19} have already demonstrated low-cost and small-scale
-implementations with low-field \gls{mri} in 2021 calculating images of a
-head successfully.
+the body, large devices are often necessary. In response to this, there
+is a growing interest in developing low-field \gls{mri} systems that
+utilize in many cases permanent magnets. These systems, while offering
+advantages in energy efficiency and reduced complexity, face a
+significant challenge related to the inherent variability in the
+strength of permanent magnets. Achieving homogeneity in the magnetic
+field is crucial for accurate imaging or comparative analyses. While
+typically calculated images have lower resolution due to lower magnetic
+field strength, low-field systems facilitate the comparison of different
+field behaviours and the identification of all kinds of irritations.
+O'Reilly and Teeuwisse and de Gans \customcite{OTW19} have already
+demonstrated low-cost and small-scale implementations with low-field
+\gls{mri} in 2021 calculating images of a head successfully.
 
@@
 cubic \emph{12x12x12mm} magnets are embedded to generate homogeneous
-magnetic flux densities of around \emph{20mT}.
-
-The homogeneity in this configuration depends, among other things, on
-the following main aspects:
+magnetic flux densities of around \emph{20mT}. The homogeneity in this
+configuration depends, among other things, on the following main
+aspects:
 
@@
 The focus of the ongoing efforts is to improve the homogeneity of
-magnets within low-field \gls{mri}systems below \emph{1000 \gls{ppm}},
+magnets within low-field \gls{mri} systems below \emph{1000 \gls{ppm}},
 primarily driven by the goal of establishing a compact low-field
@@
 scanners, the project encompasses electromagnetic simulation of
-components within the low-field \gls{mri}system, coupled with machine
+components within the low-field \gls{mri} system, coupled with machine
 learning-driven control and data acquisition. The resultant software
@@
 
+\newpage
+
 It is important to note that the primary objective of this thesis is not
@@
 the selection and comparison of potential sensors for the
-characterisation process.
-
-To achieve this, a versatile hardware setup is in development, designed
-to accommodate various sensors for the measurement of magnets or other
-objects. Simultaneously, a software interface is being crafted to
-universally read data from different sensors and interact seamlessly
-with the diverse firmware associated with various Halbach sensors. A key
-feature of this system is the ease of sensor interchangeability,
-facilitating adaptability and versatility in the characterisation
-process.
+characterisation process. To achieve this, a versatile hardware setup is
+in development, designed to accommodate various sensors for the
+measurement of magnets or other objects. Simultaneously, a software
+interface is being crafted to universally read data from different
+sensors and interact seamlessly with the diverse firmware associated
+with various Halbach sensors. A key feature of this system is the ease
+of sensor interchangeability, facilitating adaptability and versatility
+in the characterisation process.
 
@@
 
-This means that to measure a deviation of better than
-\emph{1000}\gls{ppm} in a \(50mT\) magnetic field, a resolution of less
-than \emph{50} \(\mu\)T is needed.
+This means that to measure a deviation of better than \emph{1000
+\gls{ppm}} in a \(50mT\) magnetic field, a resolution of less than
+\emph{50} \(\mu\)T is needed.
 
@@
 
+\newpage
+
 \begin{enumerate}
@@
 
+\newpage
+
 \hypertarget{sensor-selection}{%
 \section{Sensor Selection}\label{sensor-selection}}
-
-The selection process for possible magnetic field sensors initially
-focuses on the most common and cost-effective ones, especially those
-that are already used in smartphones and are therefore widely available.
-
-A key aspect of this selection is the preference for sensors with
-digital interfaces to facilitate implementation in the circuit layout
-since these kinds of sensors are easy to integrate compared to
-non-digital sensors, which require specific frameworks. The integration
-of integrated temperature sensors represents a significant enhancement
-that will later enable precise temperature compensation.
-
-The use of analogue sensors is purposefully avoided, though they are
-suitable for more precise measurements and extended measuring ranges.
-They are excluded because they require more carefully designed circuits
-and more complicated energy management.
-
-In the context of the desired goal of developing a cost-efficient and
-universally expandable Hall sensor interface, the decision in favour of
-digital sensors seems appropriate.
-
-Focussing on the digital \gls{i2c} interface not only facilitates
-implementation, but also contributes to overall cost efficiency. At the
-same time, the integration of temperature sensors enables precise
-measurements under varying environmental conditions. This strategic
-choice forms the basis for a flexible, universally applicable Hall
-sensor interface that can be seamlessly integrated into various existing
-systems.
 
@@
 
+The selection process for possible magnetic field sensors initially
+focuses on the most common and cost-effective ones, especially those
+that are already used in smartphones and are therefore widely available.
+
+A key aspect of this selection is the preference for sensors with
+digital interfaces to facilitate implementation in the circuit layout
+since these kinds of sensors are easy to integrate compared to
+non-digital sensors, which require specific frameworks. The integration
+of integrated temperature sensors represents a significant enhancement
+that will later enable precise temperature compensation.
+
+The use of analogue sensors is purposefully avoided, though they are
+suitable for more precise measurements and extended measuring ranges.
+They are excluded because they require more carefully designed circuits
+and more complicated energy management. In the context of the desired
+goal of developing a cost-efficient and universally expandable Hall
+sensor interface, the decision in favour of digital sensors seems
+appropriate.
+
+\newpage
+
+Focussing on the digital \gls{i2c} interface not only facilitates
+implementation, but also contributes to overall cost efficiency. At the
+same time, the integration of temperature sensors enables precise
+measurements under varying environmental conditions. This strategic
+choice forms the basis for a flexible, universally applicable Hall
+sensor interface that can be seamlessly integrated into various existing
+systems.
+
 The table
@@
 \section{Mechanical Structure}\label{mechanical-structure}}
+
+The mechanical design of a sensor is kept as simple as possible so that
+it can be replicated as easily as possible. The focus is on providing a
+stable foundation for the sensor \gls{ic} and an exchangeable holder for
+different magnets.
 
@@
 
-The mechanical design of a sensor is kept as simple as possible so that
-it can be replicated as easily as possible. The focus is on providing a
-stable foundation for the sensor \gls{ic} and an exchangeable holder for
-different magnets.
-
 Figure
@@
 interchangeable, so different distances between sensor and magnet can be
-realised.
-
-The exchangeable magnetic holder (shown in green in figure
+realised. The exchangeable magnetic holder (shown in green in figure
 \ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
@@
 possible to read out current measured values, obtain debug information
-and set operating parameters. This allows to quickly determine whether
-the hardware is working properly after installation. The \gls{cli}
-behaves like terminal programmes, displaying a detailed command
-reference as shown in the figure
+and set operating parameters. This allows to quickly inspeaction whether
+the hardware is working properly after firmware installation. The
+command \emph{help}, displays a detailed command reference wit all
+available commands as shown in the figure
 \ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
-to the user after connecting. The figure
-\ref{Result_of_an_executed_b_field_query_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
+to the user. The figure
+\ref{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
 shows the current measured value queried by using the \emph{readout}
@@
 \centering
-\includegraphics{./generated_images/border_Result_of_an_executed_b_field_query_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
-\caption{Result of an executed b field query using the sensors \gls{cli}
-with immediate user readable response
-\label{Result_of_an_executed_b_field_query_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}}
+\includegraphics{./generated_images/border_Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
+\caption{Result of an executed b value measurement readout command using
+the sensors \gls{cli} with immediate user readable response
+\label{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}}
 \end{figure}
@@
 command is only sent by the library, not by the user. The same commands
-are available as for \gls{cli}-based communication, but in a binary
-format.
+are available to \gls{mrp}-library as for user \gls{cli}-based
+communication, but in a binary format.
 
@@
 point unpredictable latencies can occur, too, depending on which other
-tasks are also executed on this port.
-
-To enable the most stable possible synchronisation between several
-sensors, an option has already been created to establish an electrical
-connection between sensors. This is used together with the firmware to
-synchronise the readout intervals. The figure
+tasks are also executed on this port. \newpage To enable the most stable
+possible synchronisation between several sensors, an option has already
+been created to establish an electrical connection between sensors. This
+is used together with the firmware to synchronise the readout intervals.
+The figure
 \ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
@@
 \begin{longtable}[]{@{}llll@{}}
-\caption{Build hardware sensors with equipped with different sensor
-\gls{ic}s to cover different magnet charaterisation setups
-\label{Build_hardware_sensors_with_equipped_with_different_sensor_(+ic)s_to_cover_different_magnet_charaterisation_setups.csv}}\tabularnewline
+\caption{Build hardware sensors equipped with different sensor \gls{ic}s
+to cover various magnet charaterisation setups
+\label{Build_hardware_sensors_equipped_with_different_sensor_(+ic)s_to_cover_various_magnet_charaterisation_setups.csv}}\tabularnewline
 \toprule
@@
 The table
-\ref{Build_hardware_sensors_with_equipped_with_different_sensor_(+ic)s_to_cover_different_magnet_charaterisation_setups.csv}
+\ref{Build_hardware_sensors_equipped_with_different_sensor_(+ic)s_to_cover_various_magnet_charaterisation_setups.csv}
 shows the various prototype sensor platforms equipped with different
@@
 \centering
-\includegraphics{./generated_images/border_Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_populated_with_N45_12x12x12mm_magnet.png}
+\includegraphics{./generated_images/border_Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png}
 \caption{Manufactured 1D sensor construction from different angles and
-universal magnet mount (green 3D printed part) populated with N45
+universal magnet mount (green 3D printed part) equipped with N45
 12x12x12mm magnet
-\label{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_populated_with_N45_12x12x12mm_magnet.png}}
+\label{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png}}
 \end{figure}
@@
 The 1D sensor shown in figure
-\ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_populated_with_N45_12x12x12mm_magnet.png}
+\ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png}
 is the simplest possible sensor that is compatible with the Unified
@@
 
+\newpage
+
 Since the \emph{MMC5603NJ} only has limited measurement range of total
@@
 in figure
-\ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_populated_with_N45_12x12x12mm_magnet.png})over
+\ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png})over
 the sensor to increase the distance between the magnet and the sensor
-and thus also measure these magnets.
-
-The designed magnet holder can be adapted for different magnet shapes
-and can be placed on the spacer without backlash to be able to perform a
-repeatable measurement without introducing measurement irregularities by
-mechanically changing the magnet.
+and thus also measure these magnets. The designed magnet holder can be
+adapted for different magnet shapes and can be placed on the spacer
+without backlash to be able to perform a repeatable measurement without
+introducing measurement irregularities by mechanically changing the
+magnet.
 
@@
 \centering
-\includegraphics{./generated_images/border_Full-sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
-\caption{Full-sphere sensor implementation using two Nema17 stepper
+\includegraphics{./generated_images/border_Full_sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
+\caption{Full sphere sensor implementation using two Nema17 stepper
 motors in a polar coordinate system
-\label{Full-sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}}
+\label{Full_sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}}
 \end{figure}
@@
 The 3D full sphere sensor shown in figure
-\ref{Full-sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
+\ref{Full_sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
 offers the possibility to create a 3D map of the inserted magnet.
@@
 The figure
-\ref{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full-sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
+\ref{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full_sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
 shows the visualisation of such a scan in the form of a spherical 3D
@@
 \centering
-\includegraphics{./generated_images/border_3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full-sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
-\caption{3D plot of an N45 12x12x12mm magnet using the build 3D
-full-sphere sensor with visible magnetic field strength deviations using
+\includegraphics{./generated_images/border_3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full_sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
+\caption{3D plot of an N45 12x12x12mm magnet using the build 3D full
+sphere sensor with visible magnetic field strength deviations using
 different shaded vertices on a sphere
-\label{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full-sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}}
+\label{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full_sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}}
 \end{figure}
+
+\newpage
 
@@
 can influence the measurements of the magnetic field sensor, the
-distance between these components and the sensor or magnets is
-increased. The turntable and its drive motor are connected to each other
-via a belt.
+distance between these and the sensor and magnet is increased by using
+nylon and 3D printed spacer. The turntable and its drive motor are
+connected to each other via a belt.
 
@@
 are shown in the figure
-\ref{MRP_library_implemented_modules_high_level_overview_each_of_which_can_be_replaced_by_the_user_with_custom_ones.png}.
+\ref{A_high_level_overview_of_all_MRP_library_implemented_Python_modules_which_can_be_changed_by_the_user.png}.
 In combination, these represent a typical
@@
 \centering
-\includegraphics{./generated_images/border_MRP_library_implemented_modules_high_level_overview_each_of_which_can_be_replaced_by_the_user_with_custom_ones.png}
-\caption{MRP library implemented modules high level overview each of
-which can be replaced by the user with custom ones
-\label{MRP_library_implemented_modules_high_level_overview_each_of_which_can_be_replaced_by_the_user_with_custom_ones.png}}
+\includegraphics{./generated_images/border_A_high_level_overview_of_all_MRP_library_implemented_Python_modules_which_can_be_changed_by_the_user.png}
+\caption{A high level overview of all MRP library implemented Python
+modules which can be changed by the user
+\label{A_high_level_overview_of_all_MRP_library_implemented_Python_modules_which_can_be_changed_by_the_user.png}}
 \end{figure}
@@
 
+\newpage
+
 For this purpose, an open, documented export format must be selected.
@@
 \href{https://docs.python.org/3/library/pickle.html}{Python-Pickle}
-package.
-
-Taking these points into account, the \gls{json} format is chosen. This
-is human and machine readable and there is a compatible parser for every
-programming language.
+package. Taking these points into account, the \gls{json} format is
+chosen. This is human and machine readable and there is a compatible
+parser for every programming language.
 
@@
 format, all measurement points and metadata are available in readable
-plain text.
-
-This means that they can also be read out in other programs. Using
-serialization, the \emph{MRPReading} class inherited from
+plain text. This means that they can also be read out in other programs.
+Using serialization, the \emph{MRPReading} class inherited from
 Python-\emph{Object} class is serialized via a dictionary conversion
@@
 In addition, further custom objects can be inserted into the \gls{json}
-using the functions provided.
-
-Since there are popular data processing frameworks such as \emph{Numpy}
-\customcite{HMW20}, or the program for mathematical calculations,
-\emph{MATLAB} are often used, the library also supports export formats
-for these systems.
-
-The different formats can be triggered by the user by calling up the
-corresponding \emph{MRPReading} class functions:
+using the functions provided. Since there are popular data processing
+frameworks such as \emph{Numpy} \customcite{HMW20}, or the program for
+mathematical calculations, \emph{MATLAB} are often used, the library
+also supports export formats for these systems. The different formats
+can be triggered by the user by calling up the corresponding
+\emph{MRPReading} class functions:
 
@@
 following sensor \gls{hal} modules for this purpose:
+
+\newpage
 
@@
 \item
-  \emph{std\_deviation} - Standard deviation
+  \emph{std\_deviation} - \gls{sd}
 \item
@@
 The \emph{MRPProxy} module in figure
-\ref{MRPlib_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_communicating_together_using_the_http_protocol.png}
+\ref{MRP_library_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_using_the_http_protocol.png}
 has been developed to allow forwarding and interaction with several
@@
 \centering
-\includegraphics{./generated_images/border_MRPlib_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_communicating_together_using_the_http_protocol.png}
-\caption{MRPlib proxy module usage example with host \gls{pc} for
-readout processing and remote \gls{pc} for sensor communication
-communicating together using the http protocol
-\label{MRPlib_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_communicating_together_using_the_http_protocol.png}}
+\includegraphics{./generated_images/border_MRP_library_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_using_the_http_protocol.png}
+\caption{MRP library proxy module usage example with host \gls{pc} for
+readout processing and remote \gls{pc} for sensor communication using
+the http protocol
+\label{MRP_library_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_using_the_http_protocol.png}}
 \end{figure}
@@
 \centering
-\includegraphics{./generated_images/border_Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png}
-\caption{Example MRP proxy module usage, using two remote \gls{pc}s
-\label{Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png}}
+\includegraphics{./generated_images/border_Example_MRP_proxy_module_usage_using_two_remote_(+pc)s.png}
+\caption{Example MRP proxy module usage using two remote \gls{pc}s
+\label{Example_MRP_proxy_module_usage_using_two_remote_(+pc)s.png}}
 \end{figure}
 
-Figure \ref{Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png}
+Figure \ref{Example_MRP_proxy_module_usage_using_two_remote_(+pc)s.png}
 shows the modified \emph{multi-proxy - multi-sensor} topology. Both
@@
 
-Figure \ref{MRPlib_Proxy_Module.png} shows the separation of the various
-\gls{hal} instances, which communicate with the physically connected
-sensors on the \emph{remote} \gls{pc} and the \emph{control} \gls{pc}
-side, which communicates with the remote side via the network. For the
-user, nothing changes in the procedure for setting up a measurement. The
-\emph{MRPProxy} \gls{cli} application must always be started like shown
-in listing \ref{lst:mrpcli_proxy_start} on the \gls{pc} with connected
-hardware sensors attached.
-
-\begin{lstlisting}[language=bash, caption={MRPproxy usage to enable local sensor forwarding over the network.
-The (+cli) output shows the available sensor to the connected (+host) pc}, label=lst:mrpcli_proxy_start]
+Figure \ref{Example_MRP_proxy_module_usage_using_two_remote_(+pc)s.png}
+shows the separation of the various \gls{hal} instances, which
+communicate with the physically connected sensors on the \emph{remote}
+\gls{pc} and the \emph{control} \gls{pc} side, which communicates with
+the remote side via the network. For the user, nothing changes in the
+procedure for setting up a measurement. The \emph{MRPProxy} \gls{cli}
+application must always be started like shown in listing
+\ref{lst:mrpcli_proxy_start} on the \gls{pc} with connected hardware
+sensors attached.
+
+\begin{lstlisting}[language=bash, caption={MRPProxy usage to enable local sensor forwarding over the network.
+The CLI output shows the available sensor to the connected host PC}, label=lst:mrpcli_proxy_start]
 # START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
@@
 possible to check the status via the \gls{rest} interface, which is
-shown in listing \ref{lst:mrpcli_config_rest}:
-
-\begin{lstlisting}[language=bash, caption={MRPProxy provided (+rest) endpoint query example using wget command line tool to send requests}, label=lst:mrpcli_config_rest]
+shown in listing \ref{lst:mrpcli_config_rest}.
+
+\begin{lstlisting}[language=bash, caption={MRPProxy provided REST endpoint query example using wget command line tool to send requests}, label=lst:mrpcli_config_rest]
 # GET PROXY STATUS
@@
 
-\begin{lstlisting}[language=bash, caption={MRPcli usage example to connect with a MRPproxy based network sensor}, label=lst:mrpcli_config_using_rpc]
+\begin{lstlisting}[language=bash, caption={MRPcli usage example to connect with a MRPProxy based network sensor}, label=lst:mrpcli_config_using_rpc]
 # CONFIGURE MEASUREMENT JOB USING A PROXY INSTANCE
-$ MRPcli config setupsensor testcfg --path http://proxyinstance.local:5556
+$ MRPCli config setupsensor testcfg --path http://proxyinstance.local:5556
 > remote sensor connected: True using proxy connection:
@@
 part from the core \gls{mrp}-library, to keep installation package
-dependencies small.
-
-Each connected sensor is accessed via the text-based \gls{cli}, which is
-initially the same for each sensor. The only identification feature is
-the sensor \gls{uuid} by using the \emph{id} command of the sensor
-\gls{cli}.
-
-The \emph{MRPProxy} instance claims to be a sensor to the host \gls{pc}
-running \gls{mrp} \gls{cli}, so multiple sensors must be combined into
-one virtual one. This is done in several steps, start procedure
-described by the following sub-chapters.
+dependencies small. Each connected sensor is accessed via the text-based
+\gls{cli}, which is initially the same for each sensor. The only
+identification feature is the sensor \gls{uuid} by using the \emph{id}
+command of the sensor \gls{cli}. The \emph{MRPProxy} instance claims to
+be a sensor to the host \gls{pc} running \gls{mrp} \gls{cli}, so
+multiple sensors must be combined into one virtual one. This is done in
+several steps, start procedure described by the following sub-chapters.
 
@@
 
-\begin{lstlisting}[language=bash, caption={MRPproxy (+rest) capabilities query result after execution of the merging algorithm}, label=lst:mtsc]
+\begin{lstlisting}[language=bash, caption={MRPProxy REST capabilities query result after executing the merging algorithm}, label=lst:mtsc]
 # QUERY Network-Proxy capabilities
@@
 
-The \emph{extend commands using an id parameter} strategy is used for
-different sensors. Each command is extended on the \emph{Network-Proxy},
-which is explained in chapter \ref{network-proxy} by another \gls{uuid}
-parameter, according to the following scheme:
+The \emph{extend commands using an id parameter} strategy is used to
+differentiate sensors. Each command is extended on the
+\emph{Network-Proxy}, which is explained in chapter \ref{network-proxy}
+by another \gls{uuid} parameter, according to the following scheme:
 
@@
 \item
-  \emph{readsensor } -\textgreater{} \emph{readsensor }
-\item
-  \emph{opmode} -\textgreater{} \emph{opmode }
+  \emph{readsensor AXIS SENSOR\_INDEX} -\textgreater{} \emph{readsensor
+  ID AXIS SENSOR\_INDEX}
+\item
+  \emph{opmode} -\textgreater{} \emph{opmode ID}
 \end{itemize}
@@
 This allows the host to address individual sensors directly via their
-specific \gls{uuid}.
+specific \gls{uuid} and extendet id parameter.
 
@@
 describes the measurement. This is realised in the example using the
-\emph{set\_additional\_data} function.
+\emph{set\_additional\_data} function. Finally, the measurement is
+exported for archiving and further processing; various export formats
+are available. Using the \emph{dump\_to\_file} function, the measurement
+can be converted into an open \gls{json} format.
 
@@
 
-Finally, the measurement is exported for archiving and further
-processing; various export formats are available. Using the
-\emph{dump\_to\_file} function, the measurement can be converted into an
-open \gls{json} format.
-
 \hypertarget{mrphal}{%
@@
 
-\begin{lstlisting}[language=Python, caption={MRPHal example to use a connected hardware sensor to store raw sensor readings inside of a measurement}, label=lst:mrpexample_hal]
+\newpage
+
+\begin{lstlisting}[language=Python, caption={MRPHal example to use a connected hardware sensor to store raw sensor readings inside a measurement}, label=lst:mrpexample_hal]
 from MRP import MRPHalSerialPortInformation, MRPHal, MRPBaseSensor, MRPReadingSource
@@
 a complete \emph{MRPReading} measurement with a wide range of set meta
-data.
-
-The example listing \ref{lst:mrpexample_simulation} illustrates the
-basic usage. Different variations of the \emph{generate\_reading}
+data. The example listing \ref{lst:mrpexample_simulation} illustrates
+the basic usage. Different variations of the \emph{generate\_reading}
 function offer the user additional parameterisation options, such as
@@
 
-\begin{lstlisting}[language=Python, caption={MRPSimulation example illustrates the usage of several data analysis functions}, label=lst:mrpexample_simulation]
+\begin{lstlisting}[language=Python, caption={MRPSimulation example illustrates the usage of several functions how to generate simulated magnets}, label=lst:mrpexample_simulation]
 from MRP import MRPSimulation, MRPPolarVisualization, MRPReading
@@
 visu = MRPPolarVisualization(reading)
-visu.plot3d(None)
 visu.plot3d("simulated_reading.png")
@@
 The following example listing \ref{lst:mrpexample_halbach} shows how a
-simple Halbach magnetic ring can be generated.
-
-This can be used to construct a Halbach ring magnet (see chapter
-\ref{magnet-system}) for a low-field \gls{mri}.
+simple Halbach magnetic ring can be generated. This can be used to
+construct a Halbach ring magnet (see chapter \ref{magnet-system}) for a
+low-field \gls{mri}.
 
@@
 specified. This is necessary so that the correct magnet cutouts can be
-generated when creating the 3D model.
-
-After the measurements have been generated, they are provided with a
-position and rotation offset according to the Halbach design and
-calculation scheme \customcite{O24} using the
-\emph{MRPHalbachArrayGenerator} module.
+generated when creating the 3D model. After the measurements have been
+generated, they are provided with a position and rotation offset
+according to the Halbach design and calculation scheme \customcite{O24}
+using the \emph{MRPHalbachArrayGenerator} module.
 
@@
 again using the \emph{MRPReading} module and processed further. The
-following bash listing \ref{lst:mrpcli_config_run} shows the setup
+following bash listing \ref{lst:MRPCli_config_run} shows the setup
 procedure in detail:
 
-\begin{lstlisting}[language=bash, caption={MRP(+cli) example usage for configuration of a measurement run}, label=lst:mrpcli_config_run]
+\begin{lstlisting}[language=bash, caption={MRPCli example usage for configuration of a measurement run}, label=lst:MRPCli_config_run]
 # CLI EXAMPLE FOR CONFIGURING A MEASUREMENT RUN
 ## CONFIGURE THE SENSOR TO USE
-$ MRPcli config setupsensor testcfg
+$ MRPCli config setupsensor testcfg
 > 0 - Unified Sensor 386731533439 - /dev/cu.usbmodem3867315334391
@@
 ## CONFIGURE THE MEASUREMENT
-$ MRPcli config setup testcfg
+$ MRPCli config setup testcfg
 > CONFIGURE testcfg
@@
 # RUN THE CONFIGURED MEASUREMENT
-$ MRPcli measure run
+$ MRPCli measure run
 > STARTING MEASUREMENT RUN WITH FOLLOWING CONFIGS: ['testcfg']
@@
 for the user is to write their own evaluation scripts using the
-\gls{mrp}-library.
-
-This is particularly useful for complex analyses or custom algorithms,
-but not necessarily for simple standard tasks such as bias compensation
-or graphical plot outputs.
+\gls{mrp}-library. This is particularly useful for complex analyses or
+custom algorithms, but not necessarily for simple standard tasks such as
+bias compensation or graphical plot outputs.
 
@@
 \href{https://magneticreadoutprocessing.readthedocs.io/en/latest/}{documentation}.
-
 The pipeline definition consists of sections which execute the
@@
 
-\begin{lstlisting}[caption={Example (+yaml) code of a user defined processing pipeline with six stages linked together}, label=lst:mrpuddp_example_yaml]
+\begin{lstlisting}[caption={Example YAML code of a user defined processing pipeline with six stages linked together}, label=lst:mrpuddp_example_yaml]
 stage import_readings:
@@
 
+\newpage
+
 Each pipeline step is divided into \emph{stages}, which contain a name,
@@
 
-\newpage
-
 The various steps are linked by using the \emph{stage } macro as input
 parameter of the next function to be executed (see comments in listing
-\ref{lst:mrpuddp_example_yaml}).
-
-Therefore, it is feasible to use the results of one function in several
-others without them directly following each other. The disadvantages of
-this system are the following:
+\ref{lst:mrpuddp_example_yaml}). Therefore, it is feasible to use the
+results of one function in several others without them directly
+following each other. The disadvantages of this system are the
+following:
 
@@
 
-\newpage
-
 In the other scenario, the tests are to be carried out before a new
@@
 
-\begin{lstlisting}[language=Python, caption={setup.py with dynamic requirement parsing used given requirements.txt}, label=lst:setup_py_req]
+\begin{lstlisting}[language=Python, caption={setup.py with dynamic requirement parsing using a given requirements.txt}, label=lst:setup_py_req]
 # dynamic requirement loading using 'requirements.txt'
@@
   url='https://github.com/LFB-MRI/MagnetCharacterization/',
-  packages= ['MRP', 'MRPcli', 'MRPudpp', 'MRPproxy'],
+  packages= ['MRP', 'MRPCli', 'MRPudpp', 'MRPproxy'],
   install_requires=install_requires,
@@
     'console_scripts': [
-      'MRPCli = MRPcli.cli:run',
-      'MRPUdpp = MRPudpp.uddp:run',
-      'MRPproxy = MRPproxy.mrpproxy:run'
+      'MRPCli = MRPCli.cli:run',
+      'MRPUdpp = MRPUdpp.uddp:run',
+      'MRPProxy = MRPProxy.mrpproxy:run'
     ]
@@
 \item
-  \emph{\$ MRPcli --help} instead of \emph{\$ python3 cli.py --help}
-\item
-  \emph{\$ MRPudpp --help} instead of \emph{\$ python3 udpp.py --help}
-\item
-  \emph{\$ MRPproxy --help} instead of \emph{\$ python3 proxy.py --help}
+  \emph{\$ MRPCli --help} instead of \emph{\$ python3 cli.py --help}
+\item
+  \emph{\$ MRPUdpp --help} instead of \emph{\$ python3 udpp.py --help}
+\item
+  \emph{\$ MRPProxy --help} instead of \emph{\$ python3 proxy.py --help}
 \end{itemize}
@@
 
+\newpage
+
 This process covers all the essential functionalities required for a
@@
 The configured hardware is connected to the host system using the
-\emph{MRPcli config setupsensor}-\gls{cli} command. The measurement is
+\emph{MRPCli config setupsensor}-\gls{cli} command. The measurement is
 configured for a measurement run, using the following configuration
@@
 
-\newpage
+The \emph{MRPCli measure ruxn} command is then called up for each
+individual magnet to execute a measurement. After each run, the
+\emph{READING-NAME} parameter is filled with the id of the next magnet
+so that all measurements could be assigned to the physical magnets.
 
@@
 ## CONFIGURE THE MEASUREMENT
-$ MRPcli config setup eval_measurement_config
+$ MRPCli config setup eval_measurement_config
 > READING-NAME: 360_eval_magnet_<id>
@@
 \end{lstlisting}
-
-The \emph{MRPcli measure ruxn} command is then called up for each
-individual magnet to execute a measurement. After each run, the
-\emph{READING-NAME} parameter is filled with the id of the next magnet
-so that all measurements could be assigned to the physical magnets.
 
@@
 
-\begin{lstlisting}[language=bash, caption={Bash result log of evaluation pipeline run}, label=lst:bash_pipeline_mrp_evaluation_yaml]
+\begin{lstlisting}[language=bash, caption={Bash result log of the analysis pipeline run}, label=lst:bash_pipeline_mrp_evaluation_yaml]
 # LIST ACTIVE PIPELINES IN PIPELINE DIRECTORY 
@@
 The figure
-\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png}
+\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
 summarizes this result. The plot of the raw measured values is
@@
 \centering
-\includegraphics{./generated_images/border_MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png}
-\caption{MRP evaluation result after execution of the user defined
-pipeline, using find similar values algorithm
-\label{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png}}
+\includegraphics{./generated_images/border_MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
+\caption{MRP evaluation result after find similar values algorithm
+execution in the user defined pipeline
+\label{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}}
 \end{figure}
@@
 Also, the figure
-\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png}
+\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
 illustrates, the measured values are plotted as a result of the filter
@@
 magnetic field sensors without modifications, including those listed in
-the table \ref{Implemented_digital_magnetic_field_sensors.csv}.
+the table
+\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}.
 

### 2024-02-18 documentation/thesis/build_out/deploly_server/.vitepress/dist/assets/index.md.c68979f2.js

@@ -1,1 +1,0 @@
-import{_ as e,o as t,c as a}from"./chunks/framework.e51e4293.js";const p=JSON.parse('{"title":"","description":"","frontmatter":{"layout":"home","hero":{"name":"Awesome Master Thesis","text":"A online thesis viewer","tagline":"My great project tagline"},"features":[{"title":"Download PDF","details":"Lorem ipsum dolor sit amet, consectetur adipiscing elit","actions":[{"theme":"brand","text":"Markdown Examples","link":"/markdown-examples"},{"theme":"alt","text":"API Examples","link":"/api-examples"}]}]},"headers":[],"relativePath":"index.md","filePath":"index.md"}'),n={name:"index.md"};function s(i,o,r,l,m,d){return t(),a("div")}const x=e(n,[["render",s]]);export{p as __pageData,x as default};

### 2024-02-18 documentation/thesis/build_thesis.sh

@@ -46,12 +46,15 @@ echo "-- STARTING BUILDING THESIS DOCUMENT --"
 pandoc --version
 
 # CONVERT CSV TABLES to MARKDOWN
-if [[ ! -v BUILD_FAST ]]; then
+
 cp ./thesis_document.md ./thesis_document_tmp.md 
+
 FILES="./tables/*.csv"
 for f in $FILES
 do
     FN="${f##*/}"
+
+    if [[ ! -v BUILD_FAST ]]; then
     FNWOE="${FN%%.*}"
     echo "Processing table $FN file..."
     cat "$f"
@@ -68,7 +71,7 @@ do
     ## INSERT TABLE
     csv2md "$f" >> "$f.md"
     cat "$f.md"
-
+    fi
 
     # REPLACE CONTENT WITH SED
     #cat "$f.md" | sed -e 's/[@table:'$FN']/g/' ./thesis_document_tmp.md 
@@ -76,12 +79,12 @@ do
     echo "$str"
     sed -e "/$str/ {" -e "r $f.md" -e 'd' -e '}' -i ./thesis_document_tmp.md 
 done
-fi
 
 
 
 
-if [[ ! -v BUILD_FAST ]]; then
+
+
 # ADD IMAGES
 imagefiles="./images/*.png"
 for f in $imagefiles
@@ -95,8 +98,9 @@ do
     filenameimageboarder="./generated_images/border_$FN"
     cp "$f" "$filenameimageboarder"
     # ADD IMAGE BORDERS
+    if [[ ! -v BUILD_FAST ]]; then
     convert -bordercolor transparent -border 10 "$f" "$filenameimageboarder"
-
+    fi
 
     
     # CREATE TABLE MARKDOWN FILE
@@ -120,9 +124,8 @@ do
     echo "$str"
     sed -e "/$str/ {" -e "r $f.md" -e 'd' -e '}' -i ./thesis_document_tmp.md 
 done
-fi
 
-if [[ ! -v BUILD_FAST ]]; then
+
 # CONVERT LISTINGS
 python3 convert_listings_head.py ./thesis_document_tmp.md 
 
@@ -139,7 +142,7 @@ pandoc ./thesis_attachments.md -o ./thesis_attachments.tex --from markdown --top
 sed -i 's/\\autocite{/\\customcite{/g' ./thesis_document.tex
 
[…]

### 2024-02-18 documentation/thesis/thesis_document.tex
.

@@
 Magnet characterisation. Based on this fact this thesis centres on
-assessing the sensors' applicability, the Halbach magnetic array serves
+assessing the sensors applicability, the Halbach magnetic array serves
 as a tool for later measurements, although its implementation and
@@
 exemplar instance is the work by O'Reilly, Teeuwisse, and Webb, who
-introduced a groundbreaking ``three-dimensional \gls{mri} in a
-homogeneous \emph{27cm} diameter Bore Halbach Array magnet''
-\customcite{OTW19} in 2019.This innovative setup is subsequently employed
-in 2020 to acquire in vivo MR images, showcasing the practical
-applications of their pioneering research \customcite{OTW21}. In 2023, de
-Vos, Remis and Webb published a summary of the design of a point-of-care
-Halbach array low-field \gls{mri} system \customcite{DRW23}.
-
-Within the research domain, various implementations came up. An exemplar
-instance is the work by O'Reilly, Teeuwisse, and Webb, who introduced a
-groundbreaking ``three-dimensional \gls{mri} in a homogeneous 27cm
-diameter Bore Halbach Array magnet'' \customcite{OTW19} in 2019. This
-innovative setup is subsequently employed in 2020 to acquire in vivo MR
-images, showcasing the practical applications of their pioneering
-research \customcite{OTW21}. In 2023, de Vos, Remis and Webb published a
-summary of the design of a point-of-care Halbach array low-field
-\gls{mri} system \customcite{DRW23}.
-
-The Halbach magnet incorporated in this system boasts a \emph{27cm}
-diameter, a \emph{B0} field strength of 50.4mT, and an impressive
-homogeneity of \emph{2400 \gls{ppm}} over a \emph{20cm} diameter using
-smaller magnets (\(12 x 12 x 12 mm^3\)). This exceptional homogeneity
-enables the utilization of coil-based gradients for spatial encoding,
-significantly enhancing the flexibility of image acquisition.
+introduced a groundbreaking three-dimensional \gls{mri} in a homogeneous
+\emph{27cm} diameter Bore Halbach Array magnet \customcite{OTW19} in
+2019.This innovative setup is subsequently employed in 2020 to acquire
+in vivo MR images, showcasing the practical applications of their
+pioneering research \customcite{OTW21}. In 2023, de Vos, Remis and Webb
+published a summary of the design of a point-of-care Halbach array
+low-field \gls{mri} system \customcite{DRW23}.
 
@@
 
-To further refine the magnet's homogeneity, optimisation techniques are
+To further refine the magnets homogeneity, optimisation techniques are
 employed by adjusting the radius of the Halbach ring along the length of
@@
 
-The application of the developed framework for the characterisation of
-different magnets and the integration of various available magnetic
-field sensors serve the practical application and validation of the
-developed solution.
+The application of the develox field sensors serve the practical
+application and validation of the developed solution.
 
@@
   outcome is a measurement of less than \emph{50} \(\mu\)T at \emph{1000
-  \gls{ppm}}, with a specific focus on determining the sensors'
-  viability for noise measurements.
+  \gls{ppm}}, with a specific focus on determining the sensors viability
+  for noise measurements.
 \end{itemize}
@@
 \item
-  *.dump()` - \gls{json}
+  *.dump() - \gls{json}
 \item
@@
 \begin{lstlisting}[language=Python, caption={setup.py with dynamic requirement parsing using a given requirements.txt}, label=lst:setup_py_req]
-# dynamic requirement loading using 'requirements.txt'
+# dynamic requirement loading using requirements.txt
 req_path = './requirements.txt'
@@
 
-\hypertarget{use-case-evaluation}{%
-\chapter{Use Case Evaluation}\label{use-case-evaluation}}
+\hypertarget{haluation}{%
+\chapter{Haluation}\label{haluation}}
 
@@
 \item
-  Plot of the sensor's internal temperature sensor
+  Plot of the sensors internal temperature sensor
 \item

### 2024-02-18 documentation/thesis/build_thesis.sh

@@ -46,7 +46,7 @@ echo "-- STARTING BUILDING THESIS DOCUMENT --"
 pandoc --version
 
 # CONVERT CSV TABLES to MARKDOWN
-
+if [[ ! -v BUILD_FAST ]]; then
 cp ./thesis_document.md ./thesis_document_tmp.md 
 
 FILES="./tables/*.csv"
@@ -54,7 +54,7 @@ for f in $FILES
 do
     FN="${f##*/}"
 
-    if [[ ! -v BUILD_FAST ]]; then
+
     FNWOE="${FN%%.*}"
     echo "Processing table $FN file..."
     cat "$f"
@@ -71,7 +71,7 @@ do
     ## INSERT TABLE
     csv2md "$f" >> "$f.md"
     cat "$f.md"
-    fi
+
 
     # REPLACE CONTENT WITH SED
     #cat "$f.md" | sed -e 's/[@table:'$FN']/g/' ./thesis_document_tmp.md 
@@ -98,9 +98,8 @@ do
     filenameimageboarder="./generated_images/border_$FN"
     cp "$f" "$filenameimageboarder"
     # ADD IMAGE BORDERS
-    if [[ ! -v BUILD_FAST ]]; then
     convert -bordercolor transparent -border 10 "$f" "$filenameimageboarder"
-    fi
+    
 
     
     # CREATE TABLE MARKDOWN FILE
@@ -143,7 +142,7 @@ sed -i 's/\\autocite{/\\customcite{/g' ./thesis_document.tex
 
 echo "------------- PANDOC GENERATION FINISHED -----------"
 
-
+fi
 
 python3 ./generate_citealias.py ./thesis_document.tex  ./thesis_references_alias.tex
 #sed -i 's/\\autocite{/\\cite{/g' ./thesis_document.tex
@@ -154,8 +153,11 @@ python3 ./generate_citealias.py ./thesis_document.tex  ./thesis_references_alias
 pdflatex ./thesis.tex ./thesis.pdf
 # GENERATE BIBTEX INDEX
 makeglossaries thesis # ACRONYM
-bibtex thesis # REFERENCES
+#bibtex thesis # REFERENCES
+bibtex thesis
 pdflatex ./thesis.tex ./thesis.pdf
+
+#biber thesis
 # BUILD FINAL DOCUMENT
 pdflatex ./thesis.tex ./thesis.pdf
 

### 2024-02-18 documentation/thesis/thesis_document.tex
.

@@
 
-This work describes the development of a universal Python library that
-is used to efficiently process data from magnetic field sensors from
-acquisition to analysis. In order to ensure a practical application and
-to give users the opportunity to directly acquire their own magnetic
-field data, cost-effective and easily reproducible hardware is also
-developed.
-
-The hardware is based on widely used magnetic field sensors and low-cost
-microcontrollers, which enables an easily expandable and applicable
-solution for measuring magnets with repeatable accuracy.
-
-A particular focus is placed on expandability by the user.
-Interchangeable modules allow the user to develop their own analysis
-algorithms without having to redesign everything from scratch.
-
-This extensibility and customisability is successfully demonstrated
-during the evaluation. This underlines the performance of the developed
-framework and shows that it is not only effective in the processing of
-magnetic field sensor data, but also offers a flexible platform for the
-implementation of user-specific analyses.
+This thesis describes the development of a universal Python library that
+can be used to efficiently process data from magnetic field sensors from
+acquisition to analysis. To ensure a practical application and allow
+users to acquire their own magnetic field data directly, a low-cost and
+easily reproducible hardware is also developed. The hardware is based on
+widely used consumer magnetic field sensors and low-cost
+microcontrollers, enabling an easily expandable and applicable solution
+for measuring magnets with repeatable accuracy. Special attention is
+paid to the expandability by the user. Interchangeable modules allow the
+user to develop their own analysis algorithms without having to design
+everything from scratch. The software framework was evaluated on the
+basis of the previously defined use cases. A user-defined sorting
+algorithm was implemented and integrated into the framework. The result
+is a list of the magnets that deviate least from the magnetic strength.
+The result was successfully verified by means of manual checks for
+various other series of measurements. In this way, extensibility and
+customisability were also successfully demonstrated during the software
+evaluation. This underlines the power of the developed framework and
+shows that it is not only effective in processing magnetic field sensor
+data, but also provides a flexible platform for the implementation of
+user-specific analyses. Subsequently, the developed framework was used
+to automatically characterise various magnetic field sensors. For this
+purpose, the developed pipeline feature of the software was used to
+determine various sensor characteristics, including background noise,
+temperature coefficients and linearity. The evaluation of the
+measurement data showed that the selected sensors only partially fulfil
+the defined requirements. Based on these results, it is proposed to
+characterise further digital and analogue sensors, in particular
+analogue magnetic field sensors with separate bias voltage. Alternative
+methods for sensor adaptation are described in order to be able to use
+these widely used consumer magnetic field sensors for the
+characterisation of neodymium magnet-based permanent magnets.
 

### 2024-02-18 documentation/thesis/thesis_document.tex
.

@@
 
-A solid basement has been built in this version of the framework, which
-contains all the necessary functions and is ready for immediate use.
-During development, particular emphasis is placed on comprehensive
-documentation to make it easier to get started. Together with examples
-for various use cases, a user can quickly evaluate the framework.
-
-However, it should be noted that the framework has already been released
-with its first stable version, but extensions and improvements are still
-necessary. The stable version distributed via the package registry is
-well suited for the intended purpose. All tests and evaluations took
-place under normal conditions, especially for the developed hardware
-sensors, as the \gls{mrp} library works successfully with the
-measurement data.
-
-On the software side, the focus is on integration for the support of
-more professional measuring devices. Only in this way is it possible to
-evaluate and improve the sensor hardware and quantify the measurement
-results.
-
-To summarise, it can be said that a solid software framework has been
-created that can be used directly for the intended purpose. It provides
-a suitable base for working, but further developments by integrating
-professional measurement devices to enable a more comprehensive
-evaluation and improvement of the sensor hardware are necessary.
+With this version of the framework, a solid basis has been created that
+contains all the necessary functions to solve various problems in the
+acquisition and processing of magnetic fields. Easy-to-assemble
+measurement hardware has created an easy-to-use platform for the
+characterisation of permanent magnets, for example. An exemplary
+characterisation of the magnetic field sensors used allows the possible
+areas of application for these to be narrowed down. The framework has
+already been published in a first stable version, but extensions and
+improvements are still necessary. The stable version is also distributed
+via a package registration and can therefore be quickly evaluated by new
+users. In addition, further user experience and actual measurements
+under real laboratory conditions on \gls{mri} B0 field magnets are still
+missing. This is limited by the currently restricted selection of
+characterised sensors. The aim for the next revision of the hardware and
+software framework is therefore to support additional magnetic field
+sensors. The current restriction to purely digital sensor interfaces is
+also to be extended to analogue interfaces. This will open up the use of
+a wide range of magnetic field sensors. It is also possible to integrate
+high-resolution magnetic field probes based onNMR samples, which can
+cover measurement errors of less than \emph{10nT} in fields of more than
+\emph{1T} \customcite{DBN08}. Another possibility already supported by the
+software, but for which hardware development is still necessary, is 2D
+arrays of magnetic field sensors to display fields on a
+surface\customcite{CP16}. This means that deviations can also be
+visualised graphically without physically moving the senso such as in
+the implemented \emph{3D: Full Sphere} \ref{d-full-sphere} sensor. In
+addition, larger areas or volumes, such as in a large \emph{B0} field,
+can be measured more quickly.

### 2024-02-18 documentation/thesis/thesis_abstract.tex
.

@@
 
-A passive shimming process is typically used to adjust the field
+A passive shimming process is typically used to adjust the B0 field
 afterwards. This is complex and time-consuming and requires manual
@@
 systematically measured in advance. Sensor accuracy and repeatability
-Data acquisition, storage and subsequent analysis play an important role
+data acquisition, storage and subsequent analysis play an important role
 in this methodology.

### 2024-02-18 documentation/thesis/thesis_document.tex
.

@@
 analysis, and their data storage formats are not compatible with each
-other. The accompanying open-source software for this thesis is designed
-not only to facilitate measurements with different sensors but also to
-enable the characterisation of different objects.
+other. The accompanying open source software for this work is not only
+designed to enable measurements with various sensors, but also to
+characterise permanent magnets, magnetic fields and the sensors
+themselves.
 
@@
 \ref{Example_Halbach_ring_with_cutouts_for_eight_magnets.png} shows an
-example \gls{cad} model of such a ring. In this generated model eight
-cubic \emph{12x12x12mm} magnets are embedded to generate homogeneous
-magnetic flux densities of around \emph{20mT}. The homogeneity in this
-configuration depends, among other things, on the following main
-aspects:
+example \gls{cad} model of such a ring.
+
+\newpage
+
+In this generated model eight cubic \emph{12x12x12mm} magnets are
+embedded to generate homogeneous magnetic flux densities of around
+\emph{20mT}. The homogeneity in this configuration depends, among other
+things, on the following main aspects:
 
@@
 
-The application of the develox field sensors serve the practical
-application and validation of the developed solution.
+The characterisation of field sensors in consumer quality serves the
+practical application and validation of the developed solution.
 
@@
 Finally, a comprehensive hardware and software framework needs to be
-established, which can measure diverse objects using various sensors.
-Additionally, remarks need to be provided regarding the suitability of
-the employed sensors for magnetic field measurements.
+established, which can measure diverse objects using various sensors. In
+addition, comments must be made on the suitability of the sensors used
+for magnetic field measurements.
 
@@
 shows rendered view of the 1D-Single sensor \gls{cad} drawing, which is
-described in chapter \ref{d-single-sensor}.
-
-All parts are produced using 3D printing additive manufacturing process.
-The sensor circuit board is glued underneath the magnet holder. This is
-interchangeable, so different distances between sensor and magnet can be
-realised. The exchangeable magnetic holder (shown in green in figure
+described in chapter \ref{d-single-sensor}. All parts are produced using
+3D printing additive manufacturing process. The sensor circuit board is
+glued underneath the magnet holder. This is interchangeable, so
+different distances between sensor and magnet can be realised. The
+exchangeable magnetic holder (shown in green in figure
 \ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
@@
 possible to read out current measured values, obtain debug information
-and set operating parameters. This allows to quickly inspeaction whether
-the hardware is working properly after firmware installation. The
-command \emph{help}, displays a detailed command reference wit all
-available commands as shown in the figure
+and set operating parameters. This allows to quickly inspect whether the
+hardware is working properly after firmware installation. The command
+\emph{help}, displays a detailed command reference with all available
+commands as shown in the figure
 \ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
@@
 
-Once the hardware has been prepared, the task of the firmware of the
-various sensors is to find a common synchronisation clock. The figure
-\ref{Unified_sensor_fiUnified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.pngrmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
-shows how the firmware handles the decision task if the sensor is
+Once the hardware has been prepared, the task of the firmware of each of
+the chained sensors is to find a common synchronisation clock. The
+figure
+\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
+illustrates how the firmware handles the decision task if the sensor is
 \emph{primary} or \emph{secondary} at startup. The firmware-function
@@
 & 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
-Fullsphere\ref{d-fullsphere}\tabularnewline
+Fullsphere\ref{d-full-sphere}\tabularnewline
 \midrule
@@
 This allows the host to address individual sensors directly via their
-specific \gls{uuid} and extendet id parameter.
+specific \gls{uuid} and extended id parameter.
 
@@
 
-The various steps are linked by using the \emph{stage } macro as input
-parameter of the next function to be executed (see comments in listing
-\ref{lst:mrpuddp_example_yaml}). Therefore, it is feasible to use the
-results of one function in several others without them directly
+The various steps are linked by using the \emph{stage NAME} macro as
+input parameter of the next function to be executed (see comments in
+listing \ref{lst:mrpuddp_example_yaml}). Therefore, it is feasible to
+use the results of one function in several others without them directly
 following each other. The disadvantages of this system are the
@@
 results and the results in figure
-\ref{Pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
+\ref{Generated_pipeline_output_files_and example_results_combined_into_one_plot_after_running_example_pipeline_on_a_set_of_readings.png}
 are saved for optional later use.
@@
 \centering
-\includegraphics{./generated_images/border_Pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
-\caption{Pipeline output files after running example pipeline on a set
-of readings
-\label{Pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}}
+\includegraphics{./generated_images/border_Generated_pipeline_output_files_and example_results_combined_into_one_plot_after_running_example_pipeline_on_a_set_of_readings.png}
+\caption{Generated pipeline output files and example results combined
+into one plot after running example pipeline on a set of readings
+\label{Generated_pipeline_output_files_and example_results_combined_into_one_plot_after_running_example_pipeline_on_a_set_of_readings.png}}
 \end{figure}
@@
 
-\begin{lstlisting}[language=Python, caption={Example pytest class for testing MRPReading module functions}, label=lst:pytest_example_code]
+\begin{lstlisting}[language=Python, caption={Example of a PyTest class for testing the internal functions of the MRPReading and MRPSimulation modules}, label=lst:pytest_example_code]
 class TestMPRReading(unittest.TestCase):
@@
 
-\hypertarget{haluation}{%
-\chapter{Haluation}\label{haluation}}
+\hypertarget{use-case-evaluation}{%
+\chapter{Use Case Evaluation}\label{use-case-evaluation}}
 
@@
 \centering
-\includegraphics{./generated_images/border_Ten_numbered_test_magnets_in_separate_holders.png}
-\caption{Ten numbered test magnets in separate holders
-\label{Ten_numbered_test_magnets_in_separate_holders.png}}
+\includegraphics{./generated_images/border_Ten_numbered_N45_12x12x12mm_test_magnets_in_separate_3D_printed_holders.png}
+\caption{Ten numbered N45 12x12x12mm test magnets in separate 3D printed
+holders
+\label{Ten_numbered_N45_12x12x12mm_test_magnets_in_separate_3D_printed_holders.png}}
 \end{figure}
@@
 \emph{N45 12x12x12mm} neodymium magnets are used, which are shown in
-figure \ref{Ten_numbered_test_magnets_in_separate_holders.png}.
+figure
+\ref{Ten_numbered_N45_12x12x12mm_test_magnets_in_separate_3D_printed_holders.png}.
 
 These are placed in modified 3D printed holders shown in figure
-\ref{Ten_numbered_test_magnets_in_separate_holders.png} and afterwards
-numbered. This allows to match the magnets to the measurement results
-later.
+\ref{Ten_numbered_N45_12x12x12mm_test_magnets_in_separate_3D_printed_holders.png}
+and afterwards numbered. This allows to match the magnets to the
+measurement results later.
 
@@
 integrated into the analysis pipeline in listing
-\ref{lst:pipeline_mrp_evaluation_yaml}. At this point, he example
+\ref{lst:pipeline_mrp_evaluation_yaml}. At this point, the example
 pipeline in figure \ref{Example_measurement_analysis_pipeline.png} is
@@
 
-\begin{lstlisting}[caption={User defined processing pipeline using custom implemented filter algorithm}, label=lst:pipeline_mrp_evaluation_yaml]
+\begin{lstlisting}[caption={User defined processing pipeline using custom implemented filter algorithm in third stage}, label=lst:pipeline_mrp_evaluation_yaml]
 settings:
@@
 values is plotted on ten individual measured values. It can be seen that
-there are measured values with larger deviations (see measurement
-\emph{7:0},\emph{10-2:0},\emph{10-1:0}).
+there are measured values with larger deviations (see measurement plots
+\emph{7:0},\emph{10-2:0},\emph{10-1:0} in figure
+\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}).
 
@@
 a wide range of magnetic field sensors. It is also possible to integrate
-high-resolution magnetic field probes based onNMR samples, which can
+high-resolution magnetic field probes based on NMR samples, which can
 cover measurement errors of less than \emph{10nT} in fields of more than

### 2024-02-18 documentation/thesis/thesis_document.tex
.

@@
 sensor changes, such as different magnet holders or measurement
-equipment (e.g.~temperature sensors).
+equipment (e.g.~for additional temperature sensors).
 
@@
 process input data, control output devices and performs specific tasks
-according to the program code.
-
-It manages communication with sensors, actuators and other peripheral
-devices, processing data and making decisions. Firmware is critical to
-the functioning of devices.
-
-The firmware is responsible for detecting the possible connected sensors
+according to the program code. It manages communication with sensors,
+actuators and other peripheral devices, processing data and making
+decisions. Firmware is critical to the functioning of devices. The
+firmware is responsible for detecting the possible connected sensors
 shown in table
@@
 several sensors via the \gls{usb} connection alone is not sufficient.
-
 The other issue is sending the trigger signal from the readout software,
@@
 point unpredictable latencies can occur, too, depending on which other
-tasks are also executed on this port. \newpage To enable the most stable
-possible synchronisation between several sensors, an option has already
-been created to establish an electrical connection between sensors. This
-is used together with the firmware to synchronise the readout intervals.
-The figure
+tasks are also executed on this port.
+
+To enable the most stable possible synchronisation between several
+sensors, an option has already been created to establish an electrical
+connection between sensors. This is used together with the firmware to
+synchronise the readout intervals. The figure
 \ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
@@
 implementation is that there is no numbering or sequence of the
-individual sensors.
-
-This means that for the subsequent readout of the measurements, it is
-only important that they are taken at the same interval across all
-sensors. The sensor differentiation takes place later in the
-\gls{mrp}-library \ref{software-readout-framework} by using the sensor
-\gls{uuid}.
+individual sensors. This means that for the subsequent readout of the
+measurements, it is only important that they are taken at the same
+interval across all sensors. The sensor differentiation takes place
+later in the \gls{mrp}-library \ref{software-readout-framework} by using
+the sensor \gls{uuid}.
 
@@
 Since the \emph{MMC5603NJ} only has limited measurement range of total
-\emph{6uT}, even small coin sized neodymium magnets already saturates
+\emph{6mT}, even small coin sized neodymium magnets already saturates
 the sensor. It is possible to mount 3D printed spacers (see green part
@@
 
-The magnet sensor is mounted on a movable arm, which can move 180
+The magnet sensor is mounted on a movable arm, which can move \emph{180}
 degrees around the magnet on one axis. To be able to map the full
@@
 should also be possible to import field data in a more measured form
-later. Using the DataAquisition sub-step, it is possible to generate any
-number of ideal magnets.
+later. Using the data aquisition sub-step, it is possible to generate
+any number of ideal magnets.
 
@@
 \emph{MRPProxy} module so that it can be handled differently (see
-example listing \ref{lst:mtsc}).
-
-To realize this, a \gls{lut} is created in the previous steps, which
-contains information regarding \emph{requested capability}
--\textgreater{} \emph{sensor}-\gls{uuid} -\textgreater{} \emph{physical
-sensor} and allows the commands to be routed.
+example listing \ref{lst:mtsc}). To realize this, a \gls{lut} is created
+in the previous steps, which contains information regarding
+\emph{requested capability} -\textgreater{} \emph{sensor}-\gls{uuid}
+-\textgreater{} \emph{physical sensor} and allows the commands to be
+routed.
 

### 2024-02-18 documentation/thesis/thesis_document.tex
.

@@
 \section{Sensor Selection}\label{sensor-selection}}
+
+The selection process for possible magnetic field sensors initially
+focuses on the most common and cost-effective ones, especially those
+that are already used in smartphones and are therefore widely available.
+
+A key aspect of this selection is the preference for sensors with
+digital interfaces to facilitate implementation in the circuit layout
+since these kinds of sensors are easy to integrate compared to
+non-digital sensors, which require specific frameworks. The integration
+of integrated temperature sensors represents a significant enhancement
+that will later enable precise temperature compensation.
+
+Focussing on the digital \gls{i2c} interface not only facilitates
+implementation, but also contributes to overall cost efficiency. At the
+same time, the integration of temperature sensors enables precise
+measurements under varying environmental conditions. This strategic
+choice forms the basis for a flexible, universally applicable Hall
+sensor interface that can be seamlessly integrated into various existing
+systems.
 
@@
 
-The selection process for possible magnetic field sensors initially
-focuses on the most common and cost-effective ones, especially those
-that are already used in smartphones and are therefore widely available.
-
-A key aspect of this selection is the preference for sensors with
-digital interfaces to facilitate implementation in the circuit layout
-since these kinds of sensors are easy to integrate compared to
-non-digital sensors, which require specific frameworks. The integration
-of integrated temperature sensors represents a significant enhancement
-that will later enable precise temperature compensation.
-
 The use of analogue sensors is purposefully avoided, though they are
@@
 appropriate.
-
-\newpage
-
-Focussing on the digital \gls{i2c} interface not only facilitates
-implementation, but also contributes to overall cost efficiency. At the
-same time, the integration of temperature sensors enables precise
-measurements under varying environmental conditions. This strategic
-choice forms the basis for a flexible, universally applicable Hall
-sensor interface that can be seamlessly integrated into various existing
-systems.
 
@@
 interface to connect it to a \gls{pc} in the form of a microcontroller.
-
 The focus is on utilising existing microcontroller development and
@@
 to be implemented.
+
+\newpage
 
@@
 
-\newpage
-
 As the magnets in the motors, as with the screws used in the 1D sensor,
@@
 add meta-data, users have the flexibility to configure parameters
-through the dedicated \emph{MRPMeasurementConfig} module into an
+through the dedicated \emph{MRPMeasurementConfig} module into a
 \emph{MRPReading} instance.
@@
 are available. Using the \emph{dump\_to\_file} function, the measurement
-can be converted into an open \gls{json} format.
+can be converted into a open \gls{json} format.
+
+\newpage
 
@@
 
+\newpage
+
 \begin{lstlisting}[language=Python, caption={setup.py with dynamic requirement parsing using a given requirements.txt}, label=lst:setup_py_req]
@@
 \ref{lst:pydocstring}.
+
+\newpage
 
@@
 
+\newpage
+
 \begin{lstlisting}[language=Python, caption={Modified user implemented custom find algorithm using a reference magnet reading}, label=lst:custom_find_similar_values_algorithm_refmagnet]

### 2024-02-18 documentation/thesis/thesis_document.tex
.

@@
 recognisable and corresponds to the orientation of the magnet in the
-holder.
-
-The magnet sensor is mounted on a movable arm, which can move \emph{180}
-degrees around the magnet on one axis. To be able to map the full
-sphere, the magnet is mounted on a turntable. This permits the
+holder. The magnet sensor is mounted on a movable arm, which can move
+\emph{180} degrees around the magnet on one axis. To be able to map the
+full sphere, the magnet is mounted on a turntable. This permits the
 manipulator to move a polar coordinate system.
@@
 resolution of \emph{0.1mT}. It offers an \emph{RS232} interface with a
-documented protocol for connection to a \gls{pc}.
-
-This connectivity makes it possible to make the device compatible with
-the unified sensor ecosystem using a separate
+documented protocol for connection to a \gls{pc}. This connectivity
+makes it possible to make the device compatible with the unified sensor
+ecosystem using a separate
 \href{https://github.com/RBEGamer/VoltcraftGM70Rest}{interface software}
@@
 interface consists of a \emph{Raspberry Pi Pico} with an additional
-level shifter.
-
-The teslameter is connected to the microcontroller using two free
-\gls{gpio}s in \gls{uart} mode. The firmware is adapted using a separate
-build configuration. In order to be able to read and correctly interpret
-the data from the microcontroller, the serial protocol of the sensor is
-implemented in a customised version of the \emph{CustomSensor} class as
-shown in listing \ref{lst:CustomSensorClass}.
-
-This software or hardware integration can be conducted on any other
-measuring device with a suitable communication interface and a known
-protocol thanks to the modular design.
+level shifter. The teslameter is connected to the microcontroller using
+two free \gls{gpio}s in \gls{uart} mode. The firmware is adapted using a
+separate build configuration. In order to be able to read and correctly
+interpret the data from the microcontroller, the serial protocol of the
+sensor is implemented in a customised version of the \emph{CustomSensor}
+class as shown in listing \ref{lst:CustomSensorClass}. This software or
+hardware integration can be conducted on any other measuring device with
+a suitable communication interface and a known protocol thanks to the
+modular design.
 

### 2024-02-19 documentation/thesis/thesis_document.tex
.

@@
 \item
-  \emph{Raspberry Pi OS Lite} - \gls{os} \emph{Debian bookworm x64}
+  \emph{Raspberry Pi OS Lite} - \gls{os}
 \item
@@
 illustrates how the firmware handles the decision task if the sensor is
-\emph{primary} or \emph{secondary} at startup. The firmware-function
-\emph{register irq on sync pin} is overwritten. To set one
-\emph{primary} and several \emph{secondary} sensors, each sensor waits
-for an initial pulse on the SYNC-\gls{gpio}, which is a pin at the
+\emph{primary} or \emph{secondary} at startup. The internal
+firmware-function \emph{register irq on sync pin} is overwritten. To set
+one \emph{primary} and several \emph{secondary} sensors, each sensor
+waits for an initial pulse on the SYNC-\gls{gpio}, which is a pin at the
 microcontroller with the functionality to detect if the sensor is a
@@
 \toprule
-& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
-Fullsphere\ref{d-full-sphere}\tabularnewline
+& 1D: single sensor & 1D: dual sensor & 3D: Fullsphere\tabularnewline
 \midrule
@@
 documented protocol for connection to a \gls{pc}. This connectivity
-makes it possible to make the device compatible with the unified sensor
-ecosystem using a separate
-\href{https://github.com/RBEGamer/VoltcraftGM70Rest}{interface software}
+makes it possible to make the device compatible with the previously
+build unified sensor firmware using a separate
+\href{https://github.com/RBEGamer/VoltcraftGM70Rest}{VoltcraftGM70Rest interface software}
 executable on the host \gls{pc}. However, it does not offer the range of
@@
 
-The following example shows the advantages of using the \emph{User
-interaction points}:
-
-A project called \emph{HalbachOptimisation} \customcite{O24} implements a
-data analysis step and optimizes a magnetic field that is as homogeneous
-as possible within a circular section using given mechanical dimensions
-as input parameters of the magnets which are used. For this purpose, a
-mutation of the magnet positions and rotations is performed. The result
-is a list of positions for each magnet.
-
-The \emph{MWO24} \customcite{MWO24} is an opensource project and generates
-basic \gls{cad} drawings for \gls{mri} magnets in a Halbach
-configuration. To do this, the number of magnets and additional
+The following example shows the advantages of using \emph{user
+interaction points}. In the following, two different projects are shown,
+which are based on each other in terms of their functions for analysing
+and optimising magnetic fields, but they are not compatible with each
+other due to the different data formats and programming paradigms used.
+
+The first project is a project called \emph{HalbachOptimisation}
+\customcite{O24} implements a data analysis step and optimizes a magnetic
+field that is as homogeneous as possible within a circular section using
+given mechanical dimensions as input parameters of the magnets which are
+used. For this purpose, a mutation of the magnet positions and rotations
+is performed. The result is a list of positions for each magnet.
+
+The \emph{HalbachMRIDesigner} \customcite{MWO24} is an opensource project
+and generates basic \gls{cad} drawings for \gls{mri} magnets in a
+Halbach configuration. To do this, the number of magnets and additional
 parameters for the properties of the \gls{cad} model to be created are
@@
 
-As a result, there are two projects which are both suitable for the task
-of optimizing and creating Halbach magnets for \gls{mri} applications.
-The data structures are not compatible with each other. However, they
-are executed manually one after the other to obtain a result with manual
-data conversation.
-
-The library created is intended to solve this compatibility problem by
-providing standardized and flexible data structures with this format of
-magnetic field data. By separating the processing pipeline into defined
-sub-steps, it is feasible to connect individual modules and as a result
-functionalities interchangeable by the user.
-
-The implementation of the same functionalities appears as the following
-by using the library:
+As a result, there are two projects which are both in combination
+suitable for the task of optimizing and generating Halbach magnets for
+\gls{mri} applications. The data structures are not compatible with each
+other and are usually executed manually one after the other by the user
+in order to obtain a result, whereby additional manual data conversion
+is required.
+
+The \gls{mrp}-library solve this compatibility problem by providing
+standardized and flexible data structures for of magnetic field data and
+specified data flow guidelines.
+
+The functionalities mapped by the two projects mentioned can be broken
+down into the following steps so that an optimised Halbach array can be
+generated from magnetic field data. The implementation of the same
+functionalities from the mentioned projects above looks as follows when
+using the \gls{mrp}-library:
 
@@
 \item
-  \textbf{Create a static set of magnets}
+  \textbf{Create magnetic field data}
 \end{enumerate}
@@
 The input parameters of the \emph{HalbachOptimisation} \customcite{O24}
-project are on the one hand the mechanical dimensions and the number of
-magnets to be used. Idal magnets are assumed at this point. However, it
-should also be possible to import field data in a more measured form
-later. Using the data aquisition sub-step, it is possible to generate
-any number of ideal magnets.
+project are the mechanical dimensions and the number of magnets to be
+used. Ideal magnets are assumed at this point. However, it should also
+be possible to import measured magnetic field data from measured
+magnets. Using the \gls{mri}-library data aquisition sub-step, it is
+possible to generate any number of ideal magnets or import measured
+magnets using sensor data from hardware sensors (see chapter
+\ref{example-sensors}).
 
@@
 This receives the result of the previous step, in this case the
-generated magnet data. By optionally setting meta data in the universal
-library data type, constants can be replaced in the analysis function
-and made dynamically configurable. The return result also corresponds to
-this data type so that subsequent steps are compatible and contains the
-magnet data with modified position and rotation data.
+generated magnet data. By optionally setting meta data in data type,
+constants can be replaced in the analysis function and made dynamically
+configurable. The return result also corresponds to the same data type
+so that subsequent steps are compatible and contains the magnet data
+with modified position and rotation data.
 
@@
 
-The last step is to call up the \emph{MWO24} \customcite{MWO24} project,
-which creates the \gls{cad} model of the magnet holder. The data can
-also be exported as files. To make the project compatible, the function
-signatures are also adapted. In this case, more changes are required, as
-the configuration file is loaded from the file system. This logic needs
-to be removed to use the added meta data as input parameter instead.
+The last step is to call the \emph{MWO24} \customcite{MWO24} project,
+which creates the \gls{cad} model of the magnet holder and the model can
+be exported as file. To make the project compatible, the function
+signatures are adapted. In this case, more changes are required, as the
+configuration file is loaded from the file system. This logic needs to
+be removed to use the added meta data as input parameter instead.
 
@@
 This also fulfils the goal of making individual user-created algorithms
-interchangeable. If the user now wishes to use a different \gls{cad}
+interchangeable. If the user wishes to use a different \gls{cad}
 algorithm instead of the example \emph{HalbachMRIDesigner}
@@
 
-In order to realise the concept of user interaction points, the library
-is divided into different modules. These modules can be divided into two
-main categories:
+In order to realise the concept of \emph{user interaction points} from
+chapter \ref{user-interaction-points}, the library is divided into
+different modules. These modules can be divided into two main
+categories:
 
@@
 
+\newpage
+
 The following modules are implemented in detail:
@@
 the data in other programs.
-
-\newpage
 
@@
 following sensor \gls{hal} modules for this purpose:
-
-\newpage
 
@@
 Individual sensor setups do not require any additional synchronisation
-information, as this is communicated via the \gls{usb} interface.
-
-If several sensors are connected locally, they can be connected to each
+information, as this is communicated via the \gls{usb} interface. If
+several sensors are connected locally, they can be connected to each
 other via their sync input using short cables. One sensor acts as the
@@
 distances and the synchronisation must be established via a shared
-network connection.
-
-If time-critical synchronisation over the network is required, \gls{ptp}
-and \gls{pps} output functionality \customcite{O24} can be used on many
-\gls{sbc}, such as the \emph{Raspberry Pi Compute Module}.
+network connection. If time-critical synchronisation over the network is
+required, \gls{ptp} and \gls{pps} output functionality \customcite{O24}
+can be used on many \gls{sbc}, such as the \emph{Raspberry Pi Compute
+Module}.
 
@@
 
-\hypertarget{construct-the-sensor-id-lookup-table}{%
-\subsubsection{Construct the Sensor ID
-Lookup-Table}\label{construct-the-sensor-id-lookup-table}}
+\hypertarget{merging-the-sensor-capabilities}{%
+\subsubsection{Merging the Sensor
+Capabilities}\label{merging-the-sensor-capabilities}}
 
@@
 the class instance of the \emph{MRPHal} module in a \gls{lut}. This
-makes it possible to address a sensor directly using its \gls{uuid}.
-
-\hypertarget{merging-the-sensor-capabilities}{%
-\subsubsection{Merging the Sensor
-Capabilities}\label{merging-the-sensor-capabilities}}
+makes it possible to address and interact with a sensor directly using
+its \gls{uuid}.
 
@@
 
-When using sensors with different capabilities, these must be combined.
+When using sensors with the same capabilities, these must be combined.
 These are used to select the appropriate measurement mode for a
@@
 can be converted into a open \gls{json} format.
-
-\newpage
 
@@
 this also allows to add further user documentation such as examples or
-installation instructions.
-
-Once the finished documentation has been generated from static
-\gls{html} files, it is stored in the project repository. Another
-publication option is to host the documentation via online services such
-as \href{https://readthedocs.com}{ReadTheDocs}, where users can make
-documentation for typical software projects available to others.
+installation instructions. Once the finished documentation has been
+generated from static \gls{html} files, it is stored in the project
+repository. Another publication option is to host the documentation via
+online services such as \href{https://readthedocs.com}{ReadTheDocs},
+where users can make documentation for typical software projects
+available to others.
 
@@
 shows a screenshot of the start page, which also lists separate menu
-items for tutorials on the individual functionalities.
-
-The process of creating and publishing the documentation has been
-automated using
+items for tutorials on the individual functionalities. The process of
+creating and publishing the documentation has been automated using
 \href{https://github.com/features/actions}{GithubActions}, so that it is
@@
 
-This thesis describes the development of a universal Python library that
+This thesis describes the development of a \gls{mrp} Python library that
 can be used to efficiently process data from magnetic field sensors from
@@
 is a list of the magnets that deviate least from the magnetic strength.
+
 The result was successfully verified by means of manual checks for
@@
 determine various sensor characteristics, including background noise,
-temperature coefficients and linearity. The evaluation of the
-measurement data showed that the selected sensors only partially fulfil
-the defined requirements. Based on these results, it is proposed to
-characterise further digital and analogue sensors, in particular
-analogue magnetic field sensors with separate bias voltage. Alternative
-methods for sensor adaptation are described in order to be able to use
-these widely used consumer magnetic field sensors for the
-characterisation of neodymium magnet-based permanent magnets.
+temperature coefficients and linearity.
+
+The evaluation of the measurement data showed that the selected sensors
+only partially fulfil the defined requirements.
+
+The \emph{TLV493D} and \emph{MMC5603NJ} sensors are both suitable for
+characterising permanent magnets and enable linearity compensation with
+a defined measurement setup. Although the \emph{MMC5603NJ} has a limited
+measuring range, it can still be used for relative comparisons of
+permanent magnets without additional devices and without software
+calibration. It also has a minimal long-term background noise. Absolute
+comparability can be achieved by prior software calibration and using
+reference measurements, making it an ideal sensor for the task of
+characterising permanent magnets in field tests.
+
+The \emph{MMC5603NJ} is not recommended for measuring the homogeneity of
+a \emph{50\(\mu\)T} \emph{B0} field on a Halbach ring basis with an
+accuracy of better than \emph{1000 \gls{ppm}} due to its limited
+measuring range. The \emph{TLV493D} sensor, on the other hand, has too
+much noise. It has been shown that this can be compensated for by
+software calibration and long-term averaging of measured values. Despite
+constant ambient conditions, temperature compensation is necessary for
+this sensor. Due to the large measuring range and the constant
+linearity, no software compensation is necessary. These results show
+that the analysed sensors are generally suitable for the application
+scenarios using the developed \gls{mrp} library with some limitations.
+
+Based on these results, it is proposed to characterise further digital
+and analogue sensors, in particular analogue magnetic field sensors with
+separate bias voltage. Alternative methods for sensor adaptation are
+described in order to be able to use these widely used consumer magnetic
+field sensors for the characterisation of neodymium magnet-based
+permanent magnets.
 

### 2024-02-19 documentation/thesis/thesis_document.tex
.

@@
 The evaluation of the measurement data showed that the selected sensors
-only partially fulfil the defined requirements.
-
-The \emph{TLV493D} and \emph{MMC5603NJ} sensors are both suitable for
-characterising permanent magnets and enable linearity compensation with
-a defined measurement setup. Although the \emph{MMC5603NJ} has a limited
-measuring range, it can still be used for relative comparisons of
-permanent magnets without additional devices and without software
-calibration. It also has a minimal long-term background noise. Absolute
-comparability can be achieved by prior software calibration and using
-reference measurements, making it an ideal sensor for the task of
-characterising permanent magnets in field tests.
+only partially fulfil the defined requirements. The \emph{TLV493D} and
+\emph{MMC5603NJ} sensors are both suitable for characterising permanent
+magnets and enable linearity compensation with a defined measurement
+setup. Although the \emph{MMC5603NJ} has a limited measuring range, it
+can still be used for relative comparisons of permanent magnets without
+additional devices and without software calibration. It also has a
+minimal long-term background noise. Absolute comparability can be
+achieved by prior software calibration and using reference measurements,
+making it an ideal sensor for the task of characterising permanent
+magnets in field tests.
 

### 2024-02-19 documentation/thesis/thesis_document.tex
.

@@
 
-\newpage
-
 It is important to note that the primary objective of this thesis is not
@@
 overview of how the user interacts with the project and what
-functionalities can be expected. In the later accomplished evaluation
-process in chapter \ref{use-case-evaluation}, the defined use cases are
-also used as a reference to demonstrate the implemented capabilities of
-the solution. This is essential for understanding the needs of the
-target group and designing the result accordingly.
+functionalities can be expected.
+
+In the later accomplished evaluation process in chapter
+\ref{use-case-evaluation}, the defined use cases are also used as a
+reference to demonstrate the implemented capabilities of the solution.
+
+This is important in order to understand the needs of the target group
+and design the result accordingly. For this purpose, these were defined
+into the following blocks:
 
@@
 
+Each sensor that is loaded with the firmware, registers on to the host
+\gls{pc} as a serial interface. There are several ways for the user to
+interact with the sensor:
+
+\begin{itemize}
+\tightlist
+\item
+  Use with \gls{mrp}-library, explained in chapter
+  \ref{software-readout-framework}
+\item
+  Stand-alone mode via sending commands using built-in \gls{cli}
+\end{itemize}
+
+The \gls{cli} mode is a simple text-based interface with which it is
+possible to read out current measured values, obtain debug information
+and set operating parameters. This allows to quickly inspect whether the
+hardware is working properly after firmware installation. The command
+\emph{help}, displays a detailed command reference with all available
+commands as shown in the figure
+\ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
+to the user.
+
 \begin{figure}
@@
 
-Each sensor that is loaded with the firmware, registers on to the host
-\gls{pc} as a serial interface. There are several ways for the user to
-interact with the sensor:
-
-\begin{itemize}
-\tightlist
-\item
-  Use with \gls{mrp}-library, explained in chapter
-  \ref{software-readout-framework}
-\item
-  Stand-alone mode via sending commands using built-in \gls{cli}
-\end{itemize}
-
-The \gls{cli} mode is a simple text-based interface with which it is
-possible to read out current measured values, obtain debug information
-and set operating parameters. This allows to quickly inspect whether the
-hardware is working properly after firmware installation. The command
-\emph{help}, displays a detailed command reference with all available
-commands as shown in the figure
-\ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
-to the user. The figure
+The figure
 \ref{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
@@
 command by the user.
-
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
-\caption{Result of an executed b value measurement readout command using
-the sensors \gls{cli} with immediate user readable response
-\label{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}}
-\end{figure}
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
+\caption{Result of an executed b value measurement readout command using
+the sensors \gls{cli} with immediate user readable response
+\label{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}}
+\end{figure}
+
 \hypertarget{sensor-synchronisation-interface}{%
@@
 \gls{usb} devices and modern drivers often minimise
-latencies.\customcite{W19} Nevertheless, complex data processing tasks and
-overloaded \gls{usb} ports can lead to delays.
+latencies.\customcite{WSB19} Nevertheless, complex data processing tasks
+and overloaded \gls{usb} ports can lead to delays.
 
@@
 point unpredictable latencies can occur, too, depending on which other
-tasks are also executed on this port.
-
-To enable the most stable possible synchronisation between several
-sensors, an option has already been created to establish an electrical
-connection between sensors. This is used together with the firmware to
-synchronise the readout intervals. The figure
+tasks are also executed on this port. To enable the most stable possible
+synchronisation between several sensors, an option has already been
+created to establish an electrical connection between sensors. This is
+used together with the firmware to synchronise the readout intervals.
+The figure
 \ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
@@
 
-\newpage
-
 Since the \emph{MMC5603NJ} only has limited measurement range of total
@@
 the sensor to increase the distance between the magnet and the sensor
-and thus also measure these magnets. The designed magnet holder can be
-adapted for different magnet shapes and can be placed on the spacer
-without backlash to be able to perform a repeatable measurement without
-introducing measurement irregularities by mechanically changing the
-magnet.
+and thus also measure these magnets.
+
+The designed magnet holder can be adapted for different magnet shapes
+and can be placed on the spacer without backlash to be able to perform a
+repeatable measurement without introducing measurement irregularities by
+mechanically changing the magnet.
 
@@
 \href{https://github.com/RBEGamer/VoltcraftGM70Rest}{VoltcraftGM70Rest interface software}
-executable on the host \gls{pc}. However, it does not offer the range of
-functions that the unified sensor firmware offers.
+executable on the host \gls{pc}.
+
+\newpage
 
@@
 two free \gls{gpio}s in \gls{uart} mode. The firmware is adapted using a
-separate build configuration. In order to be able to read and correctly
-interpret the data from the microcontroller, the serial protocol of the
-sensor is implemented in a customised version of the \emph{CustomSensor}
-class as shown in listing \ref{lst:CustomSensorClass}. This software or
-hardware integration can be conducted on any other measuring device with
-a suitable communication interface and a known protocol thanks to the
-modular design.
+separate build configuration.
+
+In order to be able to read and correctly interpret the data from the
+microcontroller, the serial protocol of the sensor is implemented in a
+customised version of the \emph{CustomSensor} class as shown in listing
+\ref{lst:CustomSensorClass}. This software or hardware integration can
+be conducted on any other measuring device with a suitable communication
+interface and a known protocol thanks to the modular design.
 
@@
 
-The \emph{HalbachMRIDesigner} \customcite{MWO24} is an opensource project
+The \emph{HalbachMRIDesigner} \customcite{MWO24} is an open-source project
 and generates basic \gls{cad} drawings for \gls{mri} magnets in a
@@
 internally.
-
-\newpage
 
@@
       "sensor_id": "386731533439",
-      "sensor_capabilities": ["static", "axis_b", "axis_x", "axis_y", "axis_z", "axis_temp", "axis_stimestamp"],
+      "sensor_capabilities": ["static", "axis_b", "axis_x", "axis_y", "axis_z", "axis_temp", "time"],
       "configname": "calibrationtemp30.yaml",
-      "runner": "cli"
-  },
+      "runner": "cli"},
   "data": [{
-      "value": 0.135,
-      "is_valid": true,
+      "value": {"b":0.135},
       "id": 0,
-      "temperature": 34.32
-  }],
+      "temperature": 34.32}],
   "measurement_config": {
-      "id": "525771256544952",
       "sensor_distance_radius": 40.0,
-      "magnet_type": 0
-  },
-  "name": "calibrationtemp30",
-}
+      "magnet_type": 1// CUBIC 12x12x12mm N45
+  },}
 \end{lstlisting}
@@
 
+\newpage
+
 \begin{itemize}
@@
 can also be used in a temperature chamber.
+
+\newpage
 
@@
 sensors available in the network are accessible to the \emph{control}
-\gls{pc}.
+\gls{pc} by routing the requests through each \emph{control} \gls{pc} in
+the chain to the target.
 
@@
 \gls{pc}, but the proxy instance \emph{remote} \gls{pc} \emph{\#2} can
-access the proxy running on \emph{remote} \gls{pc} \emph{\#1}.
-
-The \emph{control} \gls{pc} only communicates with the \emph{remote}
-\gls{pc} \emph{\#1}, but can access all sensors in this chain.
+access the proxy running on \emph{remote} \gls{pc} \emph{\#1}. The
+\emph{control} \gls{pc} only communicates with the \emph{remote}
+\gls{pc} \emph{\#1}, but can access all sensors in this chain thought
 
@@
 
-Immediately after starting the \emph{MRPProxy}, the \gls{uuid}s of all
-locally connected sensors are read out. These are stored together with
-the class instance of the \emph{MRPHal} module in a \gls{lut}. This
-makes it possible to address and interact with a sensor directly using
-its \gls{uuid}.
-
 \begin{longtable}[]{@{}llll@{}}
@@
 
-When using sensors with the same capabilities, these must be combined.
-These are used to select the appropriate measurement mode for a
-measurement. For this purpose, the \emph{info} command of each sensor is
-queried. This information is added to the previously created \gls{lut}.
-Duplicate entries are summarised (see table
+Immediately after starting the \emph{MRPProxy}, the \gls{uuid}s of all
+locally connected sensors are read out. These are stored together with
+the class instance of the \emph{MRPHal} module in a \gls{lut}. This
+makes it possible to address and interact with a sensor directly using
+its \gls{uuid}. When using sensors with the same capabilities, these
+must be combined. These are used to select the appropriate measurement
+mode for a measurement. For this purpose, the \emph{info} command of
+each sensor is queried. This information is added to the previously
+created \gls{lut}. Duplicate entries are summarised (see table
 \ref{Sensor_capabilities_merging_algorithm.csv}) and returned to the
@@
 a complete \emph{MRPReading} measurement with a wide range of set meta
-data. The example listing \ref{lst:mrpexample_simulation} illustrates
-the basic usage. Different variations of the \emph{generate\_reading}
+data.
+
+The example listing \ref{lst:mrpexample_simulation} illustrates the
+basic usage. Different variations of the \emph{generate\_reading}
 function offer the user additional parameterisation options, such as
@@
 construct a Halbach ring magnet (see chapter \ref{magnet-system}) for a
-low-field \gls{mri}.
-
-Eight random measurements are generated at this point. It is important
-that the magnet type (for example \emph{N45\_CUBIC\_15x15x15}) is
-specified. This is necessary so that the correct magnet cutouts can be
-generated when creating the 3D model. After the measurements have been
-generated, they are provided with a position and rotation offset
-according to the Halbach design and calculation scheme \customcite{O24}
-using the \emph{MRPHalbachArrayGenerator} module.
+low-field \gls{mri}. Eight random measurements are generated at this
+point. It is important that the magnet type (for example
+\emph{N45\_CUBIC\_15x15x15}) is specified. This is necessary so that the
+correct magnet cutouts can be generated when creating the 3D model.
+
+After the measurements have been generated, they are provided with a
+position and rotation offset according to the Halbach design and
+calculation scheme \customcite{O24} using the
+\emph{MRPHalbachArrayGenerator} module.
 
@@
 developer experience. A \gls{gui} or \gls{cli} application for complex
-libraries can make it easier to use, especially for developers with less
-experience. Continuous feedback through automated tests and
+libraries can make them more user-friendly, especially for developers
+with less experience. Continuous feedback through automated tests and
 comprehensive error logs enable faster bug fixing.
@@
 
-Thanks to this functionality of the \gls{cli}, it is now possible to
-connect a sensor to the \gls{pc}, configure a measurement series with it
-and run it at the end, which is shown in figure
-\ref{MRP_(+cli)_output_to_configure_a_new_measurement.png}. The result
-is an exported file with the measured values. These can then be read in
-again using the \emph{MRPReading} module and processed further. The
-following bash listing \ref{lst:MRPCli_config_run} shows the setup
+As a result of this implemented functionality of the \gls{cli}, it is
+now possible to connect a sensor to the \gls{pc}, configure a
+measurement series with it and run it at the end, which is shown in
+figure \ref{MRP_(+cli)_output_to_configure_a_new_measurement.png}. The
+result is an exported file with the measured values. These can then be
+read in again using the \emph{MRPReading} module and processed further.
+The following bash listing \ref{lst:MRPCli_config_run} shows the setup
 procedure in detail:
@@
 
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Example_measurement_analysis_pipeline.png}
+\caption{Example measurement analysis pipeline
+\label{Example_measurement_analysis_pipeline.png}}
+\end{figure}
+
 It is more applicable for users to carry out measurements using the
@@
 custom algorithms, but not necessarily for simple standard tasks such as
-bias compensation or graphical plot outputs.
-
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Example_measurement_analysis_pipeline.png}
-\caption{Example measurement analysis pipeline
-\label{Example_measurement_analysis_pipeline.png}}
-\end{figure}
-
-For this purpose, \gls{cli} application is created further, to enable
-the user to create and execute complex evaluation pipelines for
-measurement data without programming. The figure
-\ref{Example_measurement_analysis_pipeline.png} shows a typical
-measurement data analysis pipeline, which consists of the following
-steps:
+bias compensation or graphical plot outputs. For this purpose, \gls{cli}
+application is created further, to enable the user to create and execute
+complex evaluation pipelines for measurement data without programming.
+The figure \ref{Example_measurement_analysis_pipeline.png} shows a
+typical measurement data analysis pipeline, which consists of the
+following steps:
 
@@
 The pipeline definition consists of sections which execute the
-appropriate Python commands in the background.
-
-The signatures in the \gls{yaml} file are called using reflection and a
-real-time search of the loaded \emph{global()} functions
+appropriate Python commands in the background. The function signatures
+in the \gls{yaml} file are called using reflection and a real-time
+search of the loaded \emph{global()} functions
 \href{https://docs.python.org/3/library/functions.html#globals}{symbol table}.
 This system is capable to make all Python functions available to the
-user. To simplify usage, a pre-defined list of verified functions for
-use in pipelines is listed in the
+user. To simplify usage, a pre-defined list of verified and tested
+functions for use in pipelines is listed in the
 \href{https://magneticreadoutprocessing.readthedocs.io/en/latest/}{documentation}.
@@
 syntax.
+
+\newpage
 
@@
 out sensors connected via the network. Two different approaches are
-used. In the case of local development, the test runs are carried out on
-a \gls{pc} that can reach the network hardware and thus the test run
-could be carried out with real data.
-
-In the other scenario, the tests are to be carried out before a new
-release in the repository based on
-\href{https://github.com/features/actions}{GithubActions}. It has the
-possibility to host local runner software, which then has access to the
-hardware, but in this case a \gls{pc} must be permanently available for
-this task. Instead, the hardware sensors are simulated by software and
-executed via virtualisation on the services systems.
+used:
+
+\begin{itemize}
+\item
+  \textbf{Local Test Execution}: In the case of local development, the
+  test runs are carried out on a \gls{pc} that can reach the network
+  hardware and thus the test run could be carried out with real data.
+\item
+  \textbf{Remote Test Execution}: In the other scenario, the tests are
+  to be executed out before a new published release in the repository
+  based on \href{https://github.com/features/actions}{GithubActions}. It
+  has the possibility to host local build (runner) software, which then
+  has access to the hardware, but in this case a \gls{pc} must be
+  permanently available for this task. Instead, the hardware sensors are
+  simulated by software and executed via virtualisation on the services
+  systems. The simulation of the hardware is implemented using \gls{usb}
+  emulation, which uses a \gls{lut} to provide the expected or incorrect
+  feedback.
+\end{itemize}
+
+\newpage
 
@@
 programming language, there are several public package registries where
-users can provide their software modules.
-
-For this purpose \href{https://pypi.org}{PyPI} figure
+users can provide their software modules. For this purpose
+\href{https://pypi.org}{PyPI} figure
 \ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png} is the most
@@
 \href{https://peps.python.org/pep-0427/}{wheel} archive. This can be
-uploaded to the package registry. Since the \gls{mrp}-library requires
-additional Python dependencies, which cannot be assumed to be already
-installed on the target system, these must be installed prior to the
-actual installation. These can be specified in the library installation
-configuration \emph{setup.py} in listing \ref{lst:setup_py_req} for this
-purpose.
+uploaded to the package registry.
+
+Since the \gls{mrp}-library requires additional Python dependencies,
+which cannot be assumed to be already installed on the target system,
+these must be installed prior to the actual installation. These can be
+specified in the library installation configuration \emph{setup.py} in
+listing \ref{lst:setup_py_req} for this purpose.
 
@@
 \(\sigma_{nl}\) & 0.76 & 0.00 & \% & \gls{sd} noise level\tabularnewline
-\(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Mean sensor value
-(Baseline)\tabularnewline
+\(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Mean Baseline without offset
+compensation\tabularnewline
 \(\sigma_{rv}\) & 172.00 & 0.20 & \(\mu\)T & \gls{sd} sensor

### 2024-02-19 documentation/thesis/build_thesis.sh

@@ -11,6 +11,8 @@ rm -f *.gls
 rm -f *.aux
 rm -f *.lof
 rm -f *.lot
+rm -f *.bcf
+rm -f *.lol
 rm -f *.aux
 rm -f *.out
 rm -f *.toc
@@ -18,6 +20,7 @@ rm -f *.log
 rm -f *.synctex.gz
 rm -f *.bbl
 rm -f *.blg
+rm -f *-blx.bib
 rm -f *.fls
 rm -f *.fdb_latexmk
 rm -f *.run.xml
@@ -192,7 +195,8 @@ rm -f *.fls
 rm -f *.fdb_latexmk
 rm -f *.run.xml
 rm -Rf tmp
-
-
+rm -f *-blx.bib
+rm -f *.bcf
+rm -f *.lol
 
 exit 0

### 2024-02-20 documentation/thesis/thesis_document.tex
.

@@
 The calculated distances from the \emph{CoG} value of the measurements
-to are inserted into a \emph{heapq} priority queue. Subsequently, as
-many elements of the queue are returned as defined by the
-\emph{IP\_return\_count} parameter. The actual sorting is carried out by
-the queue in the background.
+to are inserted into a \emph{heapq} priority queue. As the measured
+values are full sphere measurements, the \emph{CoG} in this
+implementation is calculated using this formula:
+
+\[\text{CoG} = \frac{\sum{D_{istance} \times W_{eight}}}{\sum{W_{eight}}}\]
+
+Where \emph{\(D_{distance}\)} corresponds to the set distance from the
+centre of the magnet to the surface of the sensor \gls{ic}. This is the
+same for each measuring point in the measurement and corresponds to the
+mechanical structure of the \emph{3D: Full Sphere} \ref{d-full-sphere}
+sensor \emph{40mm}. The weighting \emph{\(W_{eight}\)} corresponds here
+to the \emph{B}-field value in \(\mu\)T measured by the \emph{TLV493D}
+sensor.
+
+Subsequently, as many elements of the queue are returned as defined by
+the \emph{IP\_return\_count} parameter. The actual sorting is carried
+out by the queue in the background.
 
@@
 reference measurement.
-
-\newpage
 
@@
 \toprule
-& TLV493D-A1B6 & MMC5603NJ\tabularnewline
+& TLV493D & MMC5603NJ\tabularnewline
 \midrule
@@
 
+The values in table
+\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
+were taken from the data sheets of the relevant manufacturers as a
+reference for comparison with the later measurement results.
+
 For this evaluation, the sensors listed in the table
@@
 described in chapter \ref{sensor-selection}. The additional column for
-the \emph{Background-Noise} is taken from the respective data sheets of
-the sensors and will be verified in the later \emph{Background-Noise}
+the \emph{Background Noise} is taken from the respective data sheets of
+the sensors and will be verified in the later \emph{Background Noise}
 measurement in chapter \ref{sensor-characterisation-background-noise}.
@@
 are available for this purpose, are packaged within the library.
+
+The following parameters were determined and analysed for the sensor
+evaulation:
+
+\begin{itemize}
+\tightlist
+\item
+  Background Noise
+\item
+  Linearity
+\item
+  \gls{dr}
+\item
+  Temperature Sensitivity
+\end{itemize}
+
+The characterisation methodology was modified and adapted from
+Crescentini,Gibiino and Piero \customcite{CSG22}, as their approaches are
+geared towards the analysis of analogue Hall sensors. Direct
+transmission is not possible, as their methods are specially tailored to
+these sensors. This includes measuring the analogue bias currents and
+raw sensor output voltages, which are not accessible with these
+digital-only sensors. Adaptations were therefore necessary to extend the
+characterisation to the choosen digital sensors
+\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}.
 
@@
 essential for the subsequent temperature deviation tests in order to
-obtain comparable measurement results.
+obtain comparable measurement results.\customcite{J21}
 
@@
 
-\hypertarget{sensor-characterisation-background-noise}{%
+\hypertarget{sensor-characterisation-backgroundnoise}{%
 \section{Sensor Characterisation:
-Background-Noise}\label{sensor-characterisation-background-noise}}
+BackgroundNoise}\label{sensor-characterisation-backgroundnoise}}
 
@@
 the sensor without external magnetic fields. For this purpose, a sample
-size of \emph{N=10000} measured values is recorded for the baseline
-measurement. The output signal of the sensor is continuously measured
-and recorded. It is important to carry out the measurement over a
-sufficiently lengthy period of time in order to record both short-term
-and long-term fluctuations. For this purpose, \emph{N=2000} further
-measured values are taken with a trigger and readout rate of one
-measurement per second. In order to quantify the noise, the \gls{sd} of
-the signal is calculated. These parameters provide information about the
-variation of the signal over time and therefore about the sensor
-background noise.
+size of \emph{\(N_{baseline}\)=10000} measured values is recorded for
+the baseline measurement. The output signal of the sensor is
+continuously measured and recorded. It is important to carry out the
+measurement over a sufficiently lengthy period of time in order to
+record both short-term and long-term fluctuations. For this purpose,
+\emph{\(N_{measurement}\)=2000} further measured values are taken with a
+trigger and readout rate of one measurement per second. In order to
+quantify the noise, the \gls{sd} of the signal is calculated. These
+parameters provide information about the variation of the signal over
+time and therefore about the sensor background noise.
 
@@
 \ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
-in the raw data plot. The baseline determined for each sensor is shown
-by the red \(\mu_{rv}\) {[}\(\mu\)T{]} line. It can be seen that each
-sensor has a different mean value or baseline offset in the same
-environment. For verification, a reference measurement of the
-environment is carried out with the calibrated \emph{Voltcraft GM70}
-Telsameter next to the sensor \gls{ic}. This provides a reference
-baseline value of \emph{\(\mu_{rev}\)=-21.0\(\mu\)T}.
+in the raw data plot. The baseline measurement which was previously
+determined for each sensor is shown by the red \(\mu_{rv}\)
+{[}\(\mu\)T{]} line. It can be seen that each sensor has a different
+baseline offset in the same environment. This variable is the result of
+multiple effects, including the electrical offset introduced by the
+front end and the effect of the earth's magnetic field \customcite{CSG22}
+and the test environment.
+
+For verification, a reference measurement of the environment is carried
+out with the calibrated \emph{Voltcraft GM70} Telsameter next to the
+sensor \gls{ic}. This provides a reference baseline value of
+\emph{\(\mu_{rev}\)=-21.0\(\mu\)T}.
 
 The noise of the sensor is drawn around this using the blue line. For
-the \emph{TLV493D} the \gls{sd} \emph{\(\sigma_{rv}\)=172.0\(^{\mu}\)T},
-which is twice the value given by the datasheet as the noise value.
+the \emph{TLV493D} the \gls{sd} \emph{\(\sigma_{rv}\)=172.0\({\mu}\)T},
+which is twice the value given by the datasheet as the noise value
+(refer to table
+\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}).
 Under the same conditions, the \emph{MMC5603NJ} undercuts the value
@@
 
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_linearity_measurements.png}
-\caption{Sensor evaluation setup for linearity measurements
-\label{Sensor_evaluation_setup_for_linearity_measurements.png}}
-\end{figure}
-
-The sensor linearity of a magnetic field sensor describes the ability of
-the sensor to provide a proportional linear response to changes in the
-magnetic field without non-linear distortions. This means that the
-output signals of the sensor vary directly proportional to the input
-magnetic fields without deviations or distortions and is therefore an
-important indicator for measurements of fields at different distances or
-objects.
+The sensor linearity of a magnetic field sensor or describes the ability
+of the sensor to provide a proportional linear response to changes in
+the magnetic field without non-linear distortions \customcite{CSG22}. This
+means that the output signals of the sensor vary directly proportional
+to the input magnetic fields without deviations or distortions and is
+therefore an important indicator for measurements of fields at different
+distances or objects.
 
@@
 measurement runs and thus corresponds to the same conditions as in the
-\emph{Background-Noise} chapter
+\emph{Background Noise} chapter
 \ref{sensor-characterisation-background-noise} setup.
@@
 
+In addition, the \gls{dr} for both sensors was measured before the
+measurement run to determine the linearity. In this case, this indicates
+the minimum and maximum linear measuring range for the selected linear
+Hall sensors. A high \gls{dr} enables a more precise detection of
+magnetic fields, while a low \gls{dr} can lead to the sensor detecting
+magnetic fields outside its detection range \customcite{CSG22}.
+
 \hypertarget{measurement-setup}{%
@@
 
-After the sensor baseline has been determined with \emph{N=10000}
-samples, the magnet is inserted into the holder. The linear axis is
-moved by the user until it is maximally saturated. With the
-\emph{TLV493D}, this corresponds to \emph{250.000\(\mu\)T} and below in
-low resolution mode. \emph{MCC5603NJ} around \emph{3000\(\mu\)T}. This
-ensures that the linearity is determined over the entire measuring
-range.
+After the sensor baseline has been determined with
+\emph{\(N_{baseline}\)=10000} samples, the magnet is inserted into the
+holder. The linear axis is moved by the user until it is maximally
+saturated. With the \emph{TLV493D}, this corresponds to
+\emph{250.000\(\mu\)T} and below in low resolution mode.
+\emph{MCC5603NJ} around \emph{3000\(\mu\)T}. This ensures that the
+linearity is determined over the entire measuring range.
 
@@
 \item
-  De-energise the axis motor
-\item
-  Create measurement using \emph{MRPCli} with \emph{N=2000} data points
-  per reading
+  De-energise the axis stepper motor
+\item
+  Create measurement using \emph{MRPCli} with
+  \emph{\(N_{measurement}\)=2000} data points per reading and step
 \item
@@
 for which the deviations at the end in particular (with field strengths
-towards zero) are decisive. The previously performed
-\emph{Background-Noise} characterisation in chapter
+towards zero) are decisive. The previously performed \emph{Background
+Noise} characterisation in chapter
 \ref{sensor-characterisation-background-noise} is explained that the
@@
 measurement accuracy. A low temperature sensitivity reduces errors due
-to temperature changes. An accurate temperature sensitivity
-characteristic is therefore crucial for subsequent precise magnetic
-field measurements.
+to temperature changes \customcite{J21}. An accurate temperature
+sensitivity characteristic is therefore crucial for subsequent precise
+magnetic field measurements.
 
@@
 \endhead
+\(N_{baseline}\) & 10000 & 10000 & - & Number of samples measured for
+baseline run\tabularnewline
+\(N_{measurement}\) & 2000 & 2000 & - & Number of samples measured for
+measurement run\tabularnewline
 \(\mu_{nl}\) & 0.79 & 0.00 & \% & Mean noise level\tabularnewline
@@
 temperature coefficients\tabularnewline
+DR & {[}-138;220{]} & {[}-3.1;3.4{]} & \(\mu\)T & maximum linear
+\gls{dr}\tabularnewline
 \bottomrule
@@
 in the data sheet (\emph{98\(\mu\)T} instead of \emph{175\(\mu\)T}), but
-the large measuring range, which fulfils the required specifications
-from chapter \emph{Research Question} in chapter
+the large \gls{dr}, which fulfils the required specifications from
+chapter \emph{Research Question} in chapter
 \ref{research-question-and-approach}, must be considered here, which is
@@
 
-However, due to the limited measuring range of \emph{±3mT}, direct
+However, due to the limited \gls{dr} of around \emph{±3mT}, direct
 measurement of stronger magnets is not possible using the
@@
 
-The \emph{TLV493D}, on the other hand, is able to measure these ranges,
-but does not achieve the required accuracy due to strong noise and steep
-temperature coefficients. In the following chapter, recommendations for
-action are defined, which are derived from the analysis results.
+The \emph{TLV493D}, on the other hand, is able to measure these ranges
+with a specified \gls{dr} of \emph{±150mT}, but does not achieve the
+required accuracy due to strong noise and steep temperature
+coefficients. In the following chapter, recommendations for action are
+defined, which are derived from the analysis results.
 

### 2024-02-20 documentation/thesis/thesis_document.tex
.

@@
 This is important in order to understand the needs of the target group
-and design the result accordingly. For this purpose, these were defined
+and design the result accordingly. For this purpose, these are defined
 into the following blocks:
@@
 The selection process for possible magnetic field sensors initially
-focuses on the most common and cost-effective ones, especially those
-that are already used in smartphones and are therefore widely available.
+focuses on the most common and cost-effective hall effect ones,
+especially those that are already used in smartphones and are therefore
+widely available to consumers.
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}
+\caption{Typical block diagram of a digital hall sensor sensing chain
+using three hall plates
+\label{Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}}
+\end{figure}
+
+A Hall effect sensor utilises the Hall effect that occurs when current
+flows in a conductor through which a magnetic field passes. The sensor
+consists of a semiconductor material such as gallium arsenide or indium
+antimonide. Inside the sensor are Hall effect plates, which essentially
+consist of a thin layer of this semiconductor material \customcite{BJJ16}.
 
@@
 appropriate.
+
+Another point that contributed to the selection of this module is the
+availability of the sensor \gls{ic}s as a ready-made and readily
+available evaluation module. This ensured that the electrical design is
+verified by the manufacturer so that the sensor could be operated with
+the correct electrical parameters. On the other hand, it is possible to
+evaluate several sensors in a shorter time, as a separate \gls{pcb} has
+to be produced here.
 
@@
 
-The developed framework is directly compatible with a variety of
-magnetic field sensors without modifications, including those listed in
-the table
-\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}.
+For this evaluation, the sensors listed in the table
+\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
+are used for sensor characterisation. The selection of sensors is
+described in chapter \ref{sensor-selection}. The additional column for
+the \emph{Background Noise} is taken from the respective data sheets of
+the sensors and will be verified in the later \emph{Background Noise}
+measurement in chapter \ref{sensor-characterisation-background-noise}.
 
@@
 \ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
-were taken from the data sheets of the relevant manufacturers as a
+are taken from the data sheets of the relevant manufacturers as a
 reference for comparison with the later measurement results.
-
-For this evaluation, the sensors listed in the table
-\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
-are used for sensor characterisation. The selection of sensors is
-described in chapter \ref{sensor-selection}. The additional column for
-the \emph{Background Noise} is taken from the respective data sheets of
-the sensors and will be verified in the later \emph{Background Noise}
-measurement in chapter \ref{sensor-characterisation-background-noise}.
-
-This selection is made for the following reasons:
 
@@
 
-The following parameters were determined and analysed for the sensor
+The following parameters are determined and analysed for the sensor
 evaulation:
@@
 
-The characterisation methodology was modified and adapted from
-Crescentini,Gibiino and Piero \customcite{CSG22}, as their approaches are
-geared towards the analysis of analogue Hall sensors. Direct
+The characterisation methodology is modified and adapted from
+Crescentini, Gibiino and Piero \customcite{CSG22}, as their approaches are
+focused towards the analysis of analogue Hall sensors. Direct
 transmission is not possible, as their methods are specially tailored to
@@
 raw sensor output voltages, which are not accessible with these
-digital-only sensors. Adaptations were therefore necessary to extend the
+digital-only sensors. Adaptations are therefore necessary to extend the
 characterisation to the choosen digital sensors
@@
 
-The setup is placed and pre-wired in the temperature chamber 24 hours
-before the series of measurements are carried out. The insulated housing
+The set-up is set up and pre-wired in the temperature chamber \emph{24}
+hours before the measurement series is performed. The insulated housing
 of a \emph{Voron 2.4} 3D printer, which has a separately controlled
 internal equipped heating system, is used as the temperature chamber. To
-verify the temperature, an additional thermometer \emph{VC-7055BT} is
+verify the temperature, an additional thermometer \emph{7055BT} is
 placed on the base plate. A \emph{10mm} thick \emph{PTFE} insulation
@@
 
-\hypertarget{sensor-characterisation-backgroundnoise}{%
-\section{Sensor Characterisation:
-BackgroundNoise}\label{sensor-characterisation-backgroundnoise}}
+\hypertarget{sensor-characterisation-background-noise}{%
+\section{Sensor Characterisation: Background
+Noise}\label{sensor-characterisation-background-noise}}
 
@@
 record both short-term and long-term fluctuations. For this purpose,
-\emph{\(N_{measurement}\)=2000} further measured values are taken with a
-trigger and readout rate of one measurement per second. In order to
-quantify the noise, the \gls{sd} of the signal is calculated. These
+\emph{\(N_{measurement}\)=2000} additional measured values are taken
+with a trigger and readout rate of one measurement per second. In order
+to quantify the noise, the \gls{sd} of the signal is calculated. These
 parameters provide information about the variation of the signal over
@@
 \item
-  Background noise level with reference to the initial baseline
+  Noise level with reference to the initial baseline
 \item
@@
 The temperature stability of the \emph{TLV493D} with a mean value of
-20.68\(^{\circ}\)C and a \gls{sd} of \(\sigma_{t}\)=0.53\(^{\circ}\)C
-indicates a consistent trend. This implies a constant tendency. The
-close grouping of the measured values around the mean value indicates
-good stability. The confidence interval is expected to be between
-\emph{20.15\(^{\circ}\)C} and \emph{21.21\(^{\circ}\)C}, which indicates
-a stable and consistent temperature measurement. This result is noisier
-compared to the temperature stability of the \emph{MMC5603}.
+20.68\(^{\circ}\)C and a \gls{sd} of
+\(\sigma_{t,tlv}\)=0.53\(^{\circ}\)C indicates a consistent trend. This
+implies a constant tendency. The close grouping of the measured values
+around the mean value indicates good stability. The confidence interval
+is expected to be between \emph{20.15\(^{\circ}\)C} and
+\emph{21.21\(^{\circ}\)C}, which indicates a stable and consistent
+temperature measurement. This result is noisier compared to the
+temperature stability of the \emph{MMC5603} with stable
+\emph{19.40\(^{\circ}\)C} with an accuracy of two decimal places.
 
 Both sensors provide an offset to the measured chamber temperature
-\(\mu_{trev}\).
+\(\mu_{trev, 7055BT}\).
 
@@
 \ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
-in the raw data plot. The baseline measurement which was previously
+in the raw data plot. The baseline measurement which is previously
 determined for each sensor is shown by the red \(\mu_{rv}\)
@@
 sensor \gls{ic}. This provides a reference baseline value of
-\emph{\(\mu_{rev}\)=-21.0\(\mu\)T}.
+\emph{\(\mu_{rev, GM70}\)=-21.0\(\mu\)T}.
 
 The noise of the sensor is drawn around this using the blue line. For
-the \emph{TLV493D} the \gls{sd} \emph{\(\sigma_{rv}\)=172.0\({\mu}\)T},
-which is twice the value given by the datasheet as the noise value
-(refer to table
+the \emph{TLV493D} the \gls{sd}
+\emph{\(\sigma_{rv,tlv}\)=172.0\({\mu}\)T}, which is twice the value
+given by the datasheet as the noise value (refer to table
 \ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}).
@@
 specified by the manufacturer. The \gls{sd} approaches
-\emph{\(\sigma_{rv}\)=0.20\({\mu}\)T} and is negligible, especially when
-additional averaging is used.
+\emph{\(\sigma_{rv, mmc}\)=0.20\({\mu}\)T} and is negligible, especially
+when additional averaging is used.
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_linearity_measurements.png}
+\caption{Sensor evaluation setup for linearity measurements
+\label{Sensor_evaluation_setup_for_linearity_measurements.png}}
+\end{figure}
+
 The sensor linearity of a magnetic field sensor or describes the ability
@@
 different distances above the respective sensor \gls{ic}. The ambient
-temperature is set to \emph{\(\mu_{trev}\)=21.0\(^{\circ}\)C} in the
-measurement runs and thus corresponds to the same conditions as in the
-\emph{Background Noise} chapter
+temperature is set to \emph{\(\mu_{trev, 7055BT}\)=21.0\(^{\circ}\)C} in
+the measurement runs and thus corresponds to the same conditions as in
+the \emph{Background Noise} chapter
 \ref{sensor-characterisation-background-noise} setup.
@@
 
-In addition, the \gls{dr} for both sensors was measured before the
+In addition, the \gls{dr} for both sensors are measured before the
 measurement run to determine the linearity. In this case, this indicates
@@
 directly comparable for both plots, as the sensors have different
-measuring ranges. To ensure comparability, the ideal curve is
-determined. In order to be able to make quantifiable statements about
-the measurement results, the mean and \gls{sd} deviation of these two
-curves is determined.
+measuring ranges. To ensure comparability, the ideal curve is determined
+\customcite{CSG22}. In order to be able to make quantifiable statements
+about the measurement results, the mean and \gls{sd} deviation of these
+two curves is determined.
 
@@
 possible to accurately determine the sensors \gls{ic} temperature. The
-temperature measuring device \emph{VC-7055BT} can be analysed using a
+temperature measuring device \emph{7055BT} can be analysed using a
 \gls{pc} interface. The controller of the temperature chamber can also
@@
 
-The field of permanent magnets is very temperature-dependent and can
+The field of permanent magnets is high temperature-dependent and can
 lose its magnetisation at higher temperatures (typically
-\emph{\textgreater=80\(^{\circ}\)} for non-high-quality type N magnets
-\customcite{GKT16}). The temperature range is selected so that it is
-within a sufficient range for the application.
+\emph{\textgreater=80\(^{\circ}\)} for non-high-quality \emph{Type-N}
+magnets \customcite{GKT16}). The temperature range is selected so that it
+is within a sufficient range for the application.
 
@@
 user to develop their own analysis algorithms without having to design
-everything from scratch. The software framework was evaluated on the
+everything from scratch. The software framework is evaluated on the
 basis of the previously defined use cases. A user-defined sorting
-algorithm was implemented and integrated into the framework. The result
+algorithm is implemented and integrated into the framework. The result
 is a list of the magnets that deviate least from the magnetic strength.
 
-The result was successfully verified by means of manual checks for
+The result is successfully verified by means of manual checks for
 various other series of measurements. In this way, extensibility and
-customisability were also successfully demonstrated during the software
+customisability are also successfully demonstrated during the software
 evaluation. This underlines the power of the developed framework and
@@
 data, but also provides a flexible platform for the implementation of
-user-specific analyses. Subsequently, the developed framework was used
-to automatically characterise various magnetic field sensors. For this
-purpose, the developed pipeline feature of the software was used to
+user-specific analyses. Subsequently, the developed framework is used to
+automatically characterise various magnetic field sensors. For this
+purpose, the developed pipeline feature of the software is used to
 determine various sensor characteristics, including background noise,
@@
 surface\customcite{CP16}. This means that deviations can also be
-visualised graphically without physically moving the senso such as in
+visualised graphically without physically moving the sensors such as in
 the implemented \emph{3D: Full Sphere} \ref{d-full-sphere} sensor. In
-addition, larger areas or volumes, such as in a large \emph{B0} field,
-can be measured more quickly.
+addition, larger areas or volumes, for example in a large \emph{B0}
+field, can be measured more quickly.

### 2024-02-20 documentation/thesis/build_thesis.sh
Update build_thesis.sh

@@ -24,6 +24,7 @@ rm -f *-blx.bib
 rm -f *.fls
 rm -f *.fdb_latexmk
 rm -f *.run.xml
+rm -f *.equ
 rm -Rf tmp
 
 
@@ -198,5 +199,6 @@ rm -Rf tmp
 rm -f *-blx.bib
 rm -f *.bcf
 rm -f *.lol
+rm -f *.equ
 
 exit 0

### 2024-02-21 documentation/thesis/thesis_document.tex
.

@@
 
-\[\frac{1000}{1000000} \times 50 \, mT = 0.05 \, mT \]
+\noteworthy{\frac{1000}{1000000} \times 50 \, mT = 0.05 \, mT }{1000ppm from 50mT needed resolution calucation I}
 
@@
 
-\[ 0.05 \, mT \times 1000 = 50 \, \mu T \]
+\noteworthy{0.05 \, mT \times 1000 = 50 \, \mu T}{1000ppm from 50mT needed resolution calucation II}
 
@@
 
-\newpage
-
 \begin{enumerate}
@@
 A Hall effect sensor utilises the Hall effect that occurs when current
-flows in a conductor through which a magnetic field passes. The sensor
+flows in a conductor that is exposed to a magnetic field. The sensor
 consists of a semiconductor material such as gallium arsenide or indium
 antimonide. Inside the sensor are Hall effect plates, which essentially
-consist of a thin layer of this semiconductor material \customcite{BJJ16}.
+consist of a thin layer of this semiconductor material. \customcite{BJJ16}
+
+The figure
+\ref{Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}
+shows the internal structure of a digital Hall effect sensor as a block
+diagram. The Hall effect takes place in the Hall plates. These are
+orientated differently depending on the axis inside the \gls{ic}s. In
+this case, it is a three-axis hall effect sensor. The output voltage
+generated by the Hall plates is then digitised by a \gls{adc}. The
+values can then be read out via a digital interface.
 
@@
 \toprule
-& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
+& TLV493D & HMC5883L & MMC5603NJ & AS5510\tabularnewline
 \midrule
@@
 to be implemented.
-
-\newpage
 
@@
 device drivers, data transfer speed and system resources. High-quality
-\gls{usb} devices and modern drivers often minimise
-latencies.\customcite{WSB19} Nevertheless, complex data processing tasks
-and overloaded \gls{usb} ports can lead to delays.
+\gls{usb} devices and modern drivers often minimise latencies.
+\customcite{WSB19} Nevertheless, complex data processing tasks and
+overloaded \gls{usb} ports can lead to delays.
 
@@
 
+\newpage
+
 Table
@@
 \item
-  \emph{CoG} - Centre of gravity
-\item
   \emph{binning} - Distribution of a sample by means of a histogram
+  using bins
 \item
@@
 
-\newpage
-
 The \emph{MRPProxy} module in figure
@@
 has been developed to allow forwarding and interaction with several
-sensors over a network connection using a \gls{rest} interface.
-
-The approach of implementing this via a \gls{rest} interface also offers
-the advantage that several measurements or experiments can be recorded
-at the same time with one remote sensor setup.
+sensors over a network connection using a \gls{rest} interface. The
+approach of implementing this via a \gls{rest} interface also offers the
+advantage that several measurements or experiments can be recorded at
+the same time with one remote sensor setup.
 
@@
 host when the \emph{info} \ref{lst:mtsc} command is received over
-network.
+network. \newpage
 
@@
 can be converted into a open \gls{json} format.
+
+\newpage
 
@@
 explained in chapter \ref{d-single-sensor}, is connected locally to the
-host \gls{pc}.
-
-\newpage
+host \gls{pc}. \newpage
 
@@
 measurements containing the most similar measurements, measured by the
-smallest distance between all measurements. The distance for each
-measurement is determined using the centre of gravity function
-\emph{CoG}, the length is then calculated from the result vector. This
-value can then be used for sorting.
+smallest distance between all measurements.
+
+The sorting indicator for each measurement is determined using the
+\emph{\gls{cog}} function and is implemented using the following
+equation:
+
+\noteworthy{\text{CoG} = \frac{\sum{D_{istance} \times W_{eight}}}{\sum{W_{eight}}}}{Center of Gravity}
+
+Where \emph{\(D_{distance}\)} corresponds to the set distance from the
+centre of the magnet to the surface of the sensor \gls{ic}. This is the
+same for each measuring point in the measurement and corresponds to the
+mechanical structure of the \emph{3D: Full Sphere} \ref{d-full-sphere}
+sensor \emph{40mm}. The weighting \emph{\(W_{eight}\)} corresponds here
+to the \emph{B}-field value in \(\mu\)T measured by the \emph{TLV493D}
+sensor.
 
@@
       cog = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(r)
-      # COMPUTE LENGTH OF VECTOR
+      # COMPUTE LENGTH OF VECTOR = B value
       cog_value: float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
@@
 
-The calculated distances from the \emph{CoG} value of the measurements
-to are inserted into a \emph{heapq} priority queue. As the measured
-values are full sphere measurements, the \emph{CoG} in this
-implementation is calculated using this formula:
-
-\[\text{CoG} = \frac{\sum{D_{istance} \times W_{eight}}}{\sum{W_{eight}}}\]
-
-Where \emph{\(D_{distance}\)} corresponds to the set distance from the
-centre of the magnet to the surface of the sensor \gls{ic}. This is the
-same for each measuring point in the measurement and corresponds to the
-mechanical structure of the \emph{3D: Full Sphere} \ref{d-full-sphere}
-sensor \emph{40mm}. The weighting \emph{\(W_{eight}\)} corresponds here
-to the \emph{B}-field value in \(\mu\)T measured by the \emph{TLV493D}
-sensor.
-
+The calculated distances from the \emph{\gls{cog}} value of the
+measurements to are inserted into a \emph{heapq} priority queue.
 Subsequently, as many elements of the queue are returned as defined by
@@
 
+\newpage
+
 \begin{lstlisting}[caption={User defined processing pipeline using custom implemented filter algorithm in third stage}, label=lst:pipeline_mrp_evaluation_yaml]
-settings:
-  enabled: true
-  export_intermediate_results: false
 name: pipeline_mrp_evaluation
-
 stage rawimport:
@@
 only the four most similar measurements are exported. It can be seen
-from the plotted \emph{CoG} \(\mu\)T deviation values, that these are
-closest to an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal
+from the plotted \emph{\gls{cog}} \(\mu\)T deviation values, that these
+are closest to an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal
 value is calculated with the function
@@
 pipelines in chapter \ref{programmable-data-processing-pipeline}, which
-are available for this purpose, are packaged within the library.
-
-The following parameters are determined and analysed for the sensor
+are available for this purpose, are packaged within the library. The
+following parameters are determined and analysed for the sensor
 evaulation:
@@
 essential for the subsequent temperature deviation tests in order to
-obtain comparable measurement results.\customcite{J21}
+obtain comparable measurement results. \customcite{J21}
 
@@
 configuration inside of the chamber.
-
-The procedure starts with the acquisition of the baseline by operating
-the sensor without external magnetic fields. For this purpose, a sample
-size of \emph{\(N_{baseline}\)=10000} measured values is recorded for
-the baseline measurement. The output signal of the sensor is
-continuously measured and recorded. It is important to carry out the
-measurement over a sufficiently lengthy period of time in order to
-record both short-term and long-term fluctuations. For this purpose,
-\emph{\(N_{measurement}\)=2000} additional measured values are taken
-with a trigger and readout rate of one measurement per second. In order
-to quantify the noise, the \gls{sd} of the signal is calculated. These
-parameters provide information about the variation of the signal over
-time and therefore about the sensor background noise.
-
-\begin{figure}
-\centering
-\includegraphics{./generated_images/border_Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
-\caption{Sensor noise evaluation results for TLV493D and MMC5603NJ with
-N=2000 samples and no averaging
-\label{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}}
-\end{figure}
-
-The following figure
-\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
-contains the measured values of these sensors. In the next phases these
-are analysed for each sensor examined.
-
-The following data is shown in the plots:
-
-\begin{itemize}
-\tightlist
-\item
-  Plot of the raw data of the sensor
-\item
-  Plot of the sensor's internal temperature sensor
-\item
-  Noise level with reference to the initial baseline
-\item
-  Histogram of the background noise level
-\end{itemize}
-
-The table \ref{Sensor_noise_evaluation_results.csv} lists the measured
-values that are extracted from the measurement data of the sensors in
-figure
-\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}.
-These measured values are categorised below.
 
@@
 
+The procedure starts with the acquisition of the baseline by operating
+the sensor without external magnetic fields. For this purpose, a sample
+size of \emph{\(N_{baseline}\)=10000} measured values is recorded for
+the baseline measurement. The output signal of the sensor is
+continuously measured and recorded. It is important to carry out the
+measurement over a sufficiently lengthy period of time in order to
+record both short-term and long-term fluctuations. For this purpose,
+\emph{\(N_{measurement}\)=2000} additional measured values are taken
+with a trigger and readout rate of one measurement per second. In order
+to quantify the noise, the \gls{sd} of the signal is calculated. These
+parameters provide information about the variation of the signal over
+time and therefore about the sensor background noise.
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
+\caption{Sensor noise evaluation results for TLV493D and MMC5603NJ with
+N=2000 samples and no averaging
+\label{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}}
+\end{figure}
+
+The following figure
+\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
+contains the measured values of these sensors. In the next phases these
+are analysed for each sensor examined. The following data is shown in
+the plots:
+
+\begin{itemize}
+\tightlist
+\item
+  Plot of the raw data of the sensor
+\item
+  Plot of the sensor's internal temperature sensor
+\item
+  Noise level with reference to the initial baseline
+\item
+  Histogram of the background noise level
+\end{itemize}
+
+The table \ref{Sensor_noise_evaluation_results.csv} lists the measured
+values that are extracted from the measurement data of the sensors in
+figure
+\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}.
+These measured values are categorised below.
+
 \hypertarget{sensor-temperature-analysis}{%
@@
 20.68\(^{\circ}\)C and a \gls{sd} of
-\(\sigma_{t,tlv}\)=0.53\(^{\circ}\)C indicates a consistent trend. This
-implies a constant tendency. The close grouping of the measured values
-around the mean value indicates good stability. The confidence interval
-is expected to be between \emph{20.15\(^{\circ}\)C} and
+\(\sigma_{t,TLV493D}\)=0.53\(^{\circ}\)C indicates a consistent trend.
+This implies a constant tendency. The close grouping of the measured
+values around the mean value indicates good stability. The confidence
+interval is expected to be between \emph{20.15\(^{\circ}\)C} and
 \emph{21.21\(^{\circ}\)C}, which indicates a stable and consistent
@@
 temperature stability of the \emph{MMC5603} with stable
-\emph{19.40\(^{\circ}\)C} with an accuracy of two decimal places.
+\emph{\(\mu_{t, MMC5603NJ}\)=0.53\(^{\circ}\)C} with an accuracy of two
+decimal places.
 
@@
 the \emph{TLV493D} the \gls{sd}
-\emph{\(\sigma_{rv,tlv}\)=172.0\({\mu}\)T}, which is twice the value
+\emph{\(\sigma_{rv,TLV493D}\)=172.0\({\mu}\)T}, which is twice the value
 given by the datasheet as the noise value (refer to table
@@
 specified by the manufacturer. The \gls{sd} approaches
-\emph{\(\sigma_{rv, mmc}\)=0.20\({\mu}\)T} and is negligible, especially
-when additional averaging is used.
+\emph{\(\sigma_{rv, MMC5603NJ}\)=0.20\({\mu}\)T} and is negligible,
+especially when additional averaging is used.
 
@@
 therefore an important indicator for measurements of fields at different
-distances or objects.
-
-This is achieved by means of an additional linear axis installed above
-the sensor setup. A holder for an \emph{N45 12x12x12mm} magnet is
-attached to the end effector of this axis, which can thus be moved at
-different distances above the respective sensor \gls{ic}. The ambient
-temperature is set to \emph{\(\mu_{trev, 7055BT}\)=21.0\(^{\circ}\)C} in
-the measurement runs and thus corresponds to the same conditions as in
-the \emph{Background Noise} chapter
-\ref{sensor-characterisation-background-noise} setup.
+distances or objects. This is achieved by means of an additional linear
+axis installed above the sensor setup. A holder for an \emph{N45
+12x12x12mm} magnet is attached to the end effector of this axis, which
+can thus be moved at different distances above the respective sensor
+\gls{ic}. The ambient temperature is set to
+\emph{\(\mu_{trev, 7055BT}\)=21.0\(^{\circ}\)C} in the measurement runs
+and thus corresponds to the same conditions as in the \emph{Background
+Noise} chapter \ref{sensor-characterisation-background-noise} setup.
 
@@
 temperature sensor is attached to the sensor circuit board for this
-measurement. The figure
+measurement.
+
+The figure
 \ref{Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}
@@
 software calibration.
+
+\newpage
 
@@
 \endhead
-\(N_{baseline}\) & 10000 & 10000 & - & Number of samples measured for
-baseline run\tabularnewline
-\(N_{measurement}\) & 2000 & 2000 & - & Number of samples measured for
-measurement run\tabularnewline
+\(N_{baseline}\) & 10000 & 10000 & - & Samples measured for
+baseline\tabularnewline
+\(N_{measurement}\) & 2000 & 2000 & - & Samples measured for
+measurement\tabularnewline
 \(\mu_{nl}\) & 0.79 & 0.00 & \% & Mean noise level\tabularnewline
 \(\sigma_{nl}\) & 0.76 & 0.00 & \% & \gls{sd} noise level\tabularnewline
-\(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Mean Baseline without offset
+\(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Baseline without offset
 compensation\tabularnewline
@@
 linearity\tabularnewline
-\(\mu_{td}\) & -1.99 & -5.13 & \(\mu\)T / \(^{\circ}\)C & Mean sensor
+\(\mu_{td}\) & -1.99 & -5.13 & \(\mu\)T / \(^{\circ}\)C & Sensor
 temperature coefficients\tabularnewline
@@
 which achieve a measurement accuracy of less than \emph{1000 \gls{ppm}}.
-
-However, due to the limited \gls{dr} of around \emph{±3mT}, direct
-measurement of stronger magnets is not possible using the
-\emph{MMC5603NJ}. The \emph{N45 12x12x12mm} magnets used in the
-application typically have a field strength of around \emph{100mT} at a
-distance of \emph{10mm} which is more than the \emph{MMC5603NJ} can
-measure.
-
-The \emph{TLV493D}, on the other hand, is able to measure these ranges
-with a specified \gls{dr} of \emph{±150mT}, but does not achieve the
-required accuracy due to strong noise and steep temperature
-coefficients. In the following chapter, recommendations for action are
-defined, which are derived from the analysis results.
+Due to the limited \gls{dr} of around \emph{±3mT}, direct measurement of
+stronger magnets is not possible using the \emph{MMC5603NJ}. The
+\emph{N45 12x12x12mm} magnets used in the application typically have a
+field strength of around \emph{100mT} at a distance of \emph{10mm} which
+is more than the \emph{MMC5603NJ} can measure. The \emph{TLV493D}, on
+the other hand, is able to measure these ranges with a specified
+\gls{dr} of \emph{±150mT}, but does not achieve the required accuracy
+due to strong noise and steep temperature coefficients. In the following
+chapter, recommendations for action are defined, which are derived from
+the analysis results.
 

### 2024-02-21 documentation/thesis/thesis_document.tex
final

@@
 
-\noteworthy{\frac{1000}{1000000} \times 50 \, mT = 0.05 \, mT }{1000ppm from 50mT needed resolution calucation I}
+\noteworthy{\frac{1000}{1000000} \times 50 \, mT = 0.05 \, mT }{: 1000ppm from 50mT needed resolution calucation I}
 
@@
 
-\noteworthy{0.05 \, mT \times 1000 = 50 \, \mu T}{1000ppm from 50mT needed resolution calucation II}
+\noteworthy{0.05 \, mT \times 1000 = 50 \, \mu T}{: 1000ppm from 50mT needed resolution calucation II}
 
@@
 
-\noteworthy{\text{CoG} = \frac{\sum{D_{istance} \times W_{eight}}}{\sum{W_{eight}}}}{Center of Gravity}
+\noteworthy{\text{CoG} = \frac{\sum{D_{istance} \times W_{eight}}}{\sum{W_{eight}}}}{: Center of Gravity}
 
@@
 temperature coefficients\tabularnewline
-DR & {[}-138;220{]} & {[}-3.1;3.4{]} & \(\mu\)T & maximum linear
+DR & {[}-178;220{]} & {[}-3.1;3.4{]} & \(\mu\)T & maximum linear
 \gls{dr}\tabularnewline

### 2024-02-21 documentation/thesis/thesis_abstract.tex
.

@@
 corrections to the magnets used. To avoid this process, magnets can be
-systematically measured in advance. Sensor accuracy and repeatability
-data acquisition, storage and subsequent analysis play an important role
-in this methodology.
+systematically measured in advance. Data acquisition, storage and
+subsequent analysis of the recorded data play an important role in this
+method. It is also essential that the sensors used are repeatable and
+work with the specified accuracy, which must also be characterised in
+advance for this purpose.
 

### 2024-02-21 documentation/thesis/thesis_document.tex
.

@@
 analysis, and their data storage formats are not compatible with each
-other. The accompanying open source software for this work is not only
-designed to enable measurements with various sensors, but also to
-characterise permanent magnets, magnetic fields and the sensors
-themselves.
+other. These projects and their incompatibilities are explained in
+detail in chapter \ref{user-interaction-points-example}.
+
+The accompanying open source software for this work is not only designed
+to enable measurements with various sensors, but also to characterise
+permanent magnets, magnetic fields and the sensors themselves.
 
@@
 For modern medical imaging high-field superconducting magnets dominate
-most \gls{mri} machines, providing high black-withe image resolution.
-However, the substantial costs, space requirements and safety
+most \gls{mri} machines, providing in general a higher image contrast.
+The substantial costs, space requirements and safety and installation
 considerations cause considerable challenges.
@@
 \includegraphics{./generated_images/border_Example_Halbach_ring_with_cutouts_for_eight_magnets.png}
-\caption{Example Halbach ring with cutouts for eight magnets
+\caption{Example Halbach ring with cutouts for eight magnets.
 \label{Example_Halbach_ring_with_cutouts_for_eight_magnets.png}}
@@
 A Halbach ring of this type is usually based on a ring with permanent
-magnets arranged in a circle. The figure
+magnets arranged in a circle. The Figure
 \ref{Example_Halbach_ring_with_cutouts_for_eight_magnets.png} shows an
 example \gls{cad} model of such a ring.
-
-\newpage
 
@@
   magnets from different production batches are compared.
-  \customcite{BC16}
 \end{itemize}
 
-These aspects can also be applied to individual magnets. As a result,
-this also complicates the effect on the structure of a Halbach ring
-magnet. If these are joined together to form a ring, positioning
-tolerances are also added.
+These aspects \customcite{BC16} can also be applied to individual magnets.
+As a result, this also complicates the effect on the structure of a
+Halbach ring magnet. If these are joined together to form a ring,
+positioning tolerances are also added.
 
@@
 used \gls{mri} systems are low-field \gls{mri} (\emph{66.6\% 1.5T
-systems, 20\% 3.0 T system, 14.4\% low field with \textless0.5T}).
+systems, 20\% 3.0T system, 14.4\% low field with \textless0.5T}).
 \customcite{NK16}
@@
 
-The shimming process described describes how, after the field magnet has
+The shimming process mentioned describes how, after the field magnet has
 been set up, if the homogeneous magnetic flux densities are not
@@
 will be instrumental in reconstruction, with a specific focus on
-leveraging AI-based methodologies.
-
-This comprehensive effort serves to bolster the prototyping phase of the
-low-field \gls{mri}. Diverging from the approach implemented by
+leveraging \gls{ai}-based methodologies.
+
+This comprehensive effort is designed to support the prototyping phase
+of the low-field \gls{mri}. Diverging from the approach implemented by
 O'Reilly, Teeuwisse, and Webb, \emph{DeLoRI} aims to design an open
@@
 integrated, thereby streamlining the optimisation process. Furthermore,
-
-It is important to note that the primary objective of this thesis is not
+it is important to note that the primary objective of this thesis is not
 merely to characterize the magnet itself; rather, the emphasis lies in
@@
 
-\noteworthy{\frac{1000}{1000000} \times 50 \, mT = 0.05 \, mT }{: 1000ppm from 50mT needed resolution calucation I}
-
-To convert this into microtesla (\(\mu\)T), a multiplication by
-\emph{1000} is needed:
-
-\noteworthy{0.05 \, mT \times 1000 = 50 \, \mu T}{: 1000ppm from 50mT needed resolution calucation II}
+\noteworthy{\frac{1000}{1000000} \times 50 \, mT = 0.05 \, mT \times 1000 = 50 \, \mu T}{: 1000ppm from 50mT needed resolution calucation I}
 
@@
 \caption{Typical block diagram of a digital hall sensor sensing chain
-using three hall plates
+using three hall plates.
 \label{Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}}
@@
 
-The figure
+The Figure
 \ref{Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}
@@
 \caption{List of in unified firmware implemented digital magnetic field
-sensors with focus on different sensor capabilities
+sensors with focus on different sensor capabilities.
 \label{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}}\tabularnewline
@@
 the correct electrical parameters. On the other hand, it is possible to
-evaluate several sensors in a shorter time, as a separate \gls{pcb} has
-to be produced here.
-
-The table
+analyse several sensors in a shorter time, so that no separate \gls{pcb}
+has to be designed and manufactured.
+
+The Table
 \ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
@@
 characterisation methods are used to evaluate the sensors listed in
-table
+Table
 \ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
@@
 with different parts colored separately, and universal magnet mount
-shown in green
+shown in green.
 \label{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png}}
@@
 different distances between sensor and magnet can be realised. The
-exchangeable magnetic holder (shown in green in figure
+exchangeable magnetic holder (shown in green in Figure
 \ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
@@
 \caption{1D sensor schematic using an Raspberry Pi Pico with a TLV493D
-footprint in the center
+footprint in the center.
 \label{1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}}
@@
 All the necessary components and their circuitry are recorded on a
-\gls{pcb} shown in figure
+\gls{pcb} shown in Figure
 \ref{1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}
@@
 \caption{Unified sensor firmware program structure with listed setup and
-main loop routines using simplified function blocks
+main loop routines using simplified function blocks.
 \label{Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}}
@@
 firmware is responsible for detecting the possible connected sensors
-shown in table
+shown in Table
 \ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
@@
 to the sensors found at startup. If new hardware needs to be integrated,
-only the required functions in listing \ref{lst:CustomSensorClass} need
+only the required functions in Listing \ref{lst:CustomSensorClass} need
 to be implemented.
@@
 
-The figure
+The Figure
 \ref{Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}
@@
 
-This ensures that in a multi-sensor setup with several sensors. The
-measurements are synchronized in time like described in chapter
+This ensures that in a multi-sensor setup with several sensors are
+synchronized in time like described in chapter
 \ref{sensor-synchronisation-interface} and are not out of sequence or
@@
 \item
-  Use with \gls{mrp}-library, explained in chapter
+  \gls{mrp}-library, explained in chapter
   \ref{software-readout-framework}
@@
 \emph{help}, displays a detailed command reference with all available
-commands as shown in the figure
+commands as shown in the Figure
 \ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
@@
 \caption{Unified sensor firmware provided serial terminal based
-\gls{cli} allows the user to configure the sensor manually
+\gls{cli} allows the user to configure the sensor manually.
 \label{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}}
@@
 
-The figure
+The Figure
 \ref{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
@@
 \caption{Result of an executed b value measurement readout command using
-the sensors \gls{cli} with immediate user readable response
+the sensors \gls{cli} with immediate user readable response.
 \label{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}}
@@
 together with one host \gls{pc} performing the triggering and readout
-processing
+processing.
 \label{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}}
@@
 sensor readout requests togehter with variable host system cpu loads
-testing for jitter variations
+testing for jitter variations.
 \label{(+usb)_connected_sensor_latency_test_results_using_several_sensor_readout_requests_togehter_with_variable_host_system_cpu_loads_testing_for_jitter_variations.csv}}\tabularnewline
@@
 used together with the firmware to synchronise the readout intervals.
-The figure
+The Figure
 \ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
@@
 using sync \gls{gpio} input for operation (primary or secondary) mode
-decision
+decision.
 \label{Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}}
@@
 the chained sensors is to find a common synchronisation clock. The
-figure
+Figure
 \ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
@@
 sensor operation through the \emph{got impulse within 1000ms} branch
-result. The figure
+result. The Figure
 \ref{Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}
@@
 \caption{Result of the opmode command execution on a sensor which is
-connected to another as primary configured sensor
+connected to another as primary configured sensor.
 \label{Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}}
@@
 \caption{Build hardware sensors equipped with different sensor \gls{ic}s
-to cover various magnet charaterisation setups
+to cover various magnet charaterisation setups.
 \label{Build_hardware_sensors_equipped_with_different_sensor_(+ic)s_to_cover_various_magnet_charaterisation_setups.csv}}\tabularnewline
@@
 
-The table
+The Table
 \ref{Build_hardware_sensors_equipped_with_different_sensor_(+ic)s_to_cover_various_magnet_charaterisation_setups.csv}
@@
 universal magnet mount (green 3D printed part) equipped with N45
-12x12x12mm magnet
+12x12x12mm magnet.
 \label{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png}}
@@
 
-The 1D sensor shown in figure
+The 1D sensor shown in Figure
 \ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png}
@@
 the sensor. It is possible to mount 3D printed spacers (see green part
-in figure
+in Figure
 \ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png})over
@@
 \caption{Full sphere sensor implementation using two Nema17 stepper
-motors in a polar coordinate system
+motors in a polar coordinate system.
 \label{Full_sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}}
@@
 
-The 3D full sphere sensor shown in figure
+The 3D full sphere sensor shown in Figure
 \ref{Full_sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
@@
 
-The figure
+The Figure
 \ref{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full_sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
@@
 sphere sensor with visible magnetic field strength deviations using
-different shaded vertices on a sphere
+different shaded vertices on a sphere.
 \label{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full_sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}}
@@
 integrated into the system. A temperature-compensated \emph{Voltcraft
-GM-70} telsameter shown in figure
+GM-70} telsameter shown in Figure
 \ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board_using_a_(+usb)_to_serial_converter_and_needed_additional_pull-up_resistors.png}
@@
 microcontroller, the serial protocol of the sensor is implemented in a
-customised version of the \emph{CustomSensor} class as shown in listing
+customised version of the \emph{CustomSensor} class as shown in Listing
 \ref{lst:CustomSensorClass}. This software or hardware integration can
@@
 using a \gls{usb} to serial converter and needed additional pull-up
-resistors
+resistors.
 \label{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board_using_a_(+usb)_to_serial_converter_and_needed_additional_pull-up_resistors.png}}
@@
 For this purpose, the library is divided into individual modules, which
-are shown in the figure
+are shown in the Figure
 \ref{A_high_level_overview_of_all_MRP_library_implemented_Python_modules_which_can_be_changed_by_the_user.png}.
@@
 \caption{A high level overview of all MRP library implemented Python
-modules which can be changed by the user
+modules which can be changed by the user.
 \label{A_high_level_overview_of_all_MRP_library_implemented_Python_modules_which_can_be_changed_by_the_user.png}}
@@
 
-The following listing \ref{lst:json_export_format_example} shows an
+The following Listing \ref{lst:json_export_format_example} shows an
 example \gls{json} structure which is generated when a measurement that
@@
 
-The exported example listing \ref{lst:json_export_format_example}
+The exported example Listing \ref{lst:json_export_format_example}
 contains different object keys, which contain the following information:
@@
 Currently, data re-import of an exported measurement is only supported
-via the \gls{json} format, as an export using the other options
-(\emph{Numpy}, \emph{MATLAB})loses data during the export procedure.
+via the \gls{json} format, as an export using the \emph{Numpy} or
+\emph{MATLAB} based formats loses meta-data during the export procedure.
+These only exports the raw measured values as an array represenation, so
+the additional attributes such as \emph{additional\_data} meta-data
+field (refer to Listing: \ref{lst:json_export_format_example}) are lost.
 
@@
 
-The \emph{MRPProxy} module in figure
+The \emph{MRPProxy} module in Figure
 \ref{MRP_library_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_using_the_http_protocol.png}
@@
 readout processing and remote \gls{pc} for sensor communication using
-the http protocol
+the http protocol.
 \label{MRP_library_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_using_the_http_protocol.png}}
@@
 \includegraphics{./generated_images/border_Example_MRP_proxy_module_usage_using_two_remote_(+pc)s.png}
-\caption{Example MRP proxy module usage using two remote \gls{pc}s
+\caption{Example MRP proxy module usage using two remote \gls{pc}s.
 \label{Example_MRP_proxy_module_usage_using_two_remote_(+pc)s.png}}
@@
 procedure for setting up a measurement. The \emph{MRPProxy} \gls{cli}
-application must always be started like shown in listing
+application must always be started like shown in Listing
 \ref{lst:mrpcli_proxy_start} on the \gls{pc} with connected hardware
@@
 possible to check the status via the \gls{rest} interface, which is
-shown in listing \ref{lst:mrpcli_config_rest}.
+shown in Listing \ref{lst:mrpcli_config_rest}.
 
@@
 \gls{ip} address or hostname of the \gls{pc} running an \emph{MRPProxy}
-instance is required as shown in listing
+instance is required as shown in Listing
 \ref{lst:mrpcli_config_using_rpc}.
@@
 multiple sensors must be combined into one virtual one. This is done in
-several steps, start procedure described by the following sub-chapters.
+several steps, the procedure described by the following sub-chapters.
 
@@
 \begin{longtable}[]{@{}llll@{}}
-\caption{Sensor capabilities merging algorithm
+\caption{Sensor capabilities merging algorithm.
 \label{Sensor_capabilities_merging_algorithm.csv}}\tabularnewline
@@
 each sensor is queried. This information is added to the previously
-created \gls{lut}. Duplicate entries are summarised (see table
+created \gls{lut}. Duplicate entries are summarised (see Table
 \ref{Sensor_capabilities_merging_algorithm.csv}) and returned to the
@@
 \emph{MRPProxy} module so that it can be handled differently (see
-example listing \ref{lst:mtsc}). To realize this, a \gls{lut} is created
+example Listing \ref{lst:mtsc}). To realize this, a \gls{lut} is created
 in the previous steps, which contains information regarding
@@
 For commands, which have several entries for \emph{CAPABLE SENSORS ID
-LUT} from table \ref{Sensor_capabilities_merging_algorithm.csv}, there
+LUT} from Table \ref{Sensor_capabilities_merging_algorithm.csv}, there
 are two approaches to how the command is processed:
@@
 used to manage the measurement data and can be imported and exported.
-The following example listing \ref{lst:mrpexample_reading} shows how a
+The following example Listing \ref{lst:mrpexample_reading} shows how a
 measurement is created and measurement points are added in the form of
@@
 reading.set_name("example reading")
-## ADD FURTHER DETAILS
 reading.set_additional_data("description", "abc")
 reading.set_additional_data("test-number", 1)
-# INSERT A DATAPOINT
+# EXAMPLE: INSERT A RANDOM DATAPOINT HERE
 measurement = MRPReadingEntry.MRPReadingEntry()
@@
 reading.insert_reading_instance(measurement, False)
-# USE MEASURED VALUES IN OTHER FRAMEWORKS / DATAFORMATS
-## NUMPY
-npmatrix: np.ndarray = reading.to_numpy_matrix()
-## CSV
-csv: []= reading.to_value_array()
-## JSON
-js: dict= reading.dump()
+# EXPORT MEASURED VALUES INto OTHER DATAFORMATS
+npmatrix: np.ndarray = reading.to_numpy_matrix() ## NUMPY
+csv: []= reading.to_value_array() ## CSV
+js: dict= reading.dump() ## JSON
 # EXPORT READING TO FILE
@@
 
-After generating simple measurements with random values in the previous
-example in chapter \ref{mrpreading}, the next step is to record real
+The main function of the \emph{MRPReading} module is to manage the
+measurement and meta-data. The next step is to record and store real
 sensor data. For this purpose, the \emph{MRPHal} module is developed,
-which can interact with all \emph{Unified Sensor} from chapter
-\ref{unified-sensor}-compatible sensors. In the following example
-listing \ref{lst:mrpexample_hal}, an \emph{1D: Single Sensor}, which is
+which can interact with all \emph{Unified Sensor} compatible sensors
+(refer to chapter \ref{unified-sensor}). In the following example
+Listing \ref{lst:mrpexample_hal}, an \emph{1D: Single Sensor}, which is
 explained in chapter \ref{d-single-sensor}, is connected locally to the
@@
 a complete \emph{MRPReading} measurement with a wide range of set meta
-data. The example listing \ref{lst:mrpexample_simulation} illustrates
+data. The example Listing \ref{lst:mrpexample_simulation} illustrates
 the basic usage. Different variations of the \emph{generate\_reading}
@@
 functions for this purpose. The code example shows the basic use of the
-module. The \emph{Evaluation} in chapter \ref{evaluation} chapter shows
-how the user can implement their own algorithms and add them to the
-library.
+module. The chapter \emph{Evaluation} \ref{evaluation} shows how the
+user can implement their own algorithms and add them to the library.
 
@@
 \emph{MRPVisualisation} modules are used for this. The following example
-listing \ref{lst:mrpexample_visualisation} shows the usage of both
+Listing \ref{lst:mrpexample_visualisation} shows the usage of both
 modules.
@@
 \caption{Example full sphere plot of an measurement using the
-MRPVisualisation module using different shaded vertices on a sphere
+MRPVisualisation module using different shaded vertices on a sphere.
 \label{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module_using_different_shaded_vertices_on_a_sphere.png}}
@@
 
-The following example listing \ref{lst:mrpexample_halbach} shows how a
+The following example Listing \ref{lst:mrpexample_halbach} shows how a
 simple Halbach magnetic ring can be generated. This can be used to
@@
 point. It is important that the magnet type (for example
-\emph{N45\_CUBIC\_15x15x15}) is specified. This is necessary so that the
-correct magnet cutouts can be generated when creating the 3D model.
+\emph{N45\_CUBIC\_15x15x15} refers to a type \emph{N45} cubic 15x15x15mm
+neodymium magnet) is specified. This is necessary so that the correct
+magnet cutouts can be generated when creating the 3D model.
 
@@
 generated. After computing the model using the \emph{OpenSCAD} \gls{cli}
-utility, the following model rendering shown in figure
+utility, the following model rendering shown in Figure
 \ref{Generated_Halbach_array_with_generated_cutouts_for_eight_magnets.png}
@@
 \caption{Generated Halbach array with generated cutouts for eight
-magnets
+magnets.
 \label{Generated_Halbach_array_with_generated_cutouts_for_eight_magnets.png}}
@@
 \includegraphics{./generated_images/border_MRP_(+cli)_output_to_configure_a_new_measurement.png}
-\caption{MRP \gls{cli} output to configure a new measurement
+\caption{MRP \gls{cli} output to configure a new measurement.
 \label{MRP_(+cli)_output_to_configure_a_new_measurement.png}}
@@
 measurement series with it and run it at the end, which is shown in
-figure \ref{MRP_(+cli)_output_to_configure_a_new_measurement.png}. The
+Figure \ref{MRP_(+cli)_output_to_configure_a_new_measurement.png}. The
 result is an exported file with the measured values. These can then be
 read in again using the \emph{MRPReading} module and processed further.
-The following bash listing \ref{lst:MRPCli_config_run} shows the setup
+The following bash Listing \ref{lst:MRPCli_config_run} shows the setup
 procedure in detail:
@@
 \includegraphics{./generated_images/border_Example_measurement_analysis_pipeline.png}
-\caption{Example measurement analysis pipeline
+\caption{Example measurement analysis pipeline.
 \label{Example_measurement_analysis_pipeline.png}}
@@
 
-It is more applicable for users to carry out measurements using the
-\gls{cli}-, the next logical step is to analyse the recorded data. This
-can involve one or several hundred data records. Again, the procedure
-for the user is to write their own evaluation scripts using the
+The next logical step is to analyse the recorded data. This can involve
+one or several hundred data records. Again, the procedure for the user
+is to write their own evaluation Python scripts using the
 \gls{mrp}-library. This is particularly useful for complex analyses or
@@
 complex evaluation pipelines for measurement data without programming.
-The figure \ref{Example_measurement_analysis_pipeline.png} shows a
+The Figure \ref{Example_measurement_analysis_pipeline.png} shows a
 typical measurement data analysis pipeline, which consists of the
@@
 \href{https://magneticreadoutprocessing.readthedocs.io/en/latest/}{documentation}.
-The following pipeline definition in listing
+The following pipeline definition in Listing
 \ref{lst:mrpuddp_example_yaml} shows the previously defined steps shown
-in figure \ref{Example_measurement_analysis_pipeline.png} as \gls{yaml}
+in Figure \ref{Example_measurement_analysis_pipeline.png} as \gls{yaml}
 syntax.
@@
 input parameter of the next function to be executed (see comments in
-listing \ref{lst:mrpuddp_example_yaml}). Therefore, it is feasible to
+Listing \ref{lst:mrpuddp_example_yaml}). Therefore, it is feasible to
 use the results of one function in several others without them directly
@@
 determination of start steps and repeated traversal, the final execution
-sequence can be determined in the form of a call tree in figure
+sequence can be determined in the form of a call tree in Figure
 \ref{Example_result_of_an_step_execution_tree_from_user_defined_processing_pipeline.png}.
 The individual steps are then executed along the graph. The intermediate
-results and the results in figure
+results and the results in Figure
 \ref{Generated_pipeline_output_files_and example_results_combined_into_one_plot_after_running_example_pipeline_on_a_set_of_readings.png}
@@
 \caption{Example result of an step execution tree from user defined
-processing pipeline
+processing pipeline.
 \label{Example_result_of_an_step_execution_tree_from_user_defined_processing_pipeline.png}}
@@
 \caption{Generated pipeline output files and example results combined
-into one plot after running example pipeline on a set of readings
+into one plot after running example pipeline on a set of readings.
 \label{Generated_pipeline_output_files_and example_results_combined_into_one_plot_after_running_example_pipeline_on_a_set_of_readings.png}}
@@
 \caption{MRP library test results for different submodules executed in
-PyCharm \gls{ide}
+PyCharm \gls{ide}.
 \label{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png}}
@@
 framework \emph{PyTest} \customcite{P17} is used for this purpose, as it
-offers direct integration in most \gls{ide}s (see figure
+offers direct integration in most \gls{ide}s (see Figure
 \ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
@@
 of the test cases could later be used in slightly simplified variants of
-listing \ref{lst:pytest_example_code} as examples for the documentation.
+Listing \ref{lst:pytest_example_code} as examples for the documentation.
 
@@
 \includegraphics{./generated_images/border_MagneticReadoutProcessing_library_hosted_on_PyPi.png}
-\caption{MagneticReadoutProcessing library hosted on PyPi
+\caption{MagneticReadoutProcessing library hosted on PyPi.
 \label{MagneticReadoutProcessing_library_hosted_on_PyPi.png}}
@@
 users can provide their software modules. For this purpose
-\href{https://pypi.org}{PyPI} figure
+\href{https://pypi.org}{PyPI} Figure
 \ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png} is the most
 used package registry and offers direct support for the package
-installation program \gls{pip} shown in listing
+installation program \gls{pip} shown in Listing
 \ref{lst:setup_lib_with_pip}.
@@
 specified in the library installation configuration \emph{setup.py} in
-listing \ref{lst:setup_py_req} for this purpose.
+Listing \ref{lst:setup_py_req} for this purpose.
 
@@
 further development, as modern \gls{ide}s can more reliably display
-methods to the user as an assistance. It is implemented in listing
+methods to the user as an assistance. It is implemented in Listing
 \ref{lst:pydocstring}.
@@
 \href{https://magneticreadoutprocessing.readthedocs.io/}{ReadTheDocs}
-service. The figure
+service. The Figure
 \ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
@@
 \includegraphics{./generated_images/border_MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
-\caption{MagneticReadoutProcessing documentation hosted on ReadTheDocs
+\caption{MagneticReadoutProcessing documentation hosted on ReadTheDocs.
 \label{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}}
@@
 comprehensive characterisation of permanent magnets. These are
-previously described in the \emph{Use cases} \ref{use-cases} chapter.
+previously described in the chapter \emph{Use cases} \ref{use-cases}.
 The developed framework not only offers a cost-effective and flexible
@@
 \caption{Ten numbered N45 12x12x12mm test magnets in separate 3D printed
-holders
+holders.
 \label{Ten_numbered_N45_12x12x12mm_test_magnets_in_separate_3D_printed_holders.png}}
@@
 \emph{N45 12x12x12mm} neodymium magnets are used, which are shown in
-figure
+Figure
 \ref{Ten_numbered_N45_12x12x12mm_test_magnets_in_separate_3D_printed_holders.png}.
 
-These are placed in modified 3D printed holders shown in figure
+These are placed in modified 3D printed holders shown in Figure
 \ref{Ten_numbered_N45_12x12x12mm_test_magnets_in_separate_3D_printed_holders.png}
@@
 configured for a measurement run, using the following configuration
-commands from listing \ref{lst:evaluation_measurement_config}.
+commands from Listing \ref{lst:evaluation_measurement_config}.
 
@@
 The next step for the user is the implementation of the filter algorithm
-in listing \ref{lst:custom_find_similar_values_algorithm}. This can have
+in Listing \ref{lst:custom_find_similar_values_algorithm}. This can have
 any function signature and is implemented in the file
@@
 The parameter \_readings should later receive the imported measurements
-from the \emph{stage rawimport} in listing
+from the \emph{stage rawimport} in Listing
 \ref{lst:pipeline_mrp_evaluation_yaml} and the optional
@@
 a result, the filter algorithm returns the measurements that are most
-similar to the selected reference magnet. The code snipped in listing
+similar to the selected reference magnet. The code snipped in Listing
 \ref{lst:custom_find_similar_values_algorithm_refmagnet} shows the
@@
 Once the filter function has been implemented, it still needs to be
-integrated into the analysis pipeline in listing
+integrated into the analysis pipeline in Listing
 \ref{lst:pipeline_mrp_evaluation_yaml}. At this point, the example
-pipeline in figure \ref{Example_measurement_analysis_pipeline.png} is
+pipeline in Figure \ref{Example_measurement_analysis_pipeline.png} is
 simplified and an additional stage \emph{find\_similar\_values} has been
@@
 This is carried out using the \emph{MRPudpp} \gls{cli}, which is
-described in listing \ref{lst:bash_pipeline_mrp_evaluation_yaml}. After
+described in Listing \ref{lst:bash_pipeline_mrp_evaluation_yaml}. After
 the run has been successfully completed, the results are saved in the
@@
 
-The figure
+The Figure
 \ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
@@
 there are measured values with larger deviations (see measurement plots
-\emph{7:0},\emph{10-2:0},\emph{10-1:0} in figure
+\emph{7:0},\emph{10-2:0},\emph{10-1:0} in Figure
 \ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}).
@@
 \caption{MRP evaluation result after find similar values algorithm
-execution in the user defined pipeline
+execution in the user defined pipeline.
 \label{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}}
@@
 
-Also, the figure
+Also, the Figure
 \ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
@@
 
-For this evaluation, the sensors listed in the table
+For this evaluation, the sensors listed in the Table
 \ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
@@
 \begin{longtable}[]{@{}lll@{}}
-\caption{Digital magnetic field sensors characterised for evaluation
+\caption{Digital magnetic field sensors characterised for evaluation.
 \label{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}}\tabularnewline
@@
 
-The values in table
+The values in Table
 \ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
@@
 magnetic field sensors without modifications, including those listed in
-the table. For this evaluation, the sensors listed in the table are used
+the Table. For this evaluation, the sensors listed in the Table are used
 for sensor characterisation. This selection is made for the following
@@
 digital-only sensors. Adaptations are therefore necessary to extend the
-characterisation to the choosen digital sensors
+characterisation to the choosen digital sensors listed in Table
 \ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}.
@@
 \caption{Sensor evaluation plattform with TLV493D and MMC5603 sensors
-placed with thermal conductive glue on an aluminium baseplate
+placed with thermal conductive glue on an aluminium baseplate.
 \label{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}}
@@
 
-The figure
+The Figure
 \ref{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
@@
 \includegraphics{./generated_images/border_Sensor_evaluation_setup_for_noise_measurements.png}
-\caption{Sensor evaluation setup for noise measurements
+\caption{Sensor evaluation setup for noise measurements.
 \label{Sensor_evaluation_setup_for_noise_measurements.png}}
@@
 \begin{longtable}[]{@{}lllll@{}}
-\caption{Sensor noise evaluation results
+\caption{Sensor noise evaluation results.
 \label{Sensor_noise_evaluation_results.csv}}\tabularnewline
@@
 \endhead
-\(\mu_{nl}\) & 0.79 & 0.00 & \% & Mean noise level\tabularnewline
-\(\sigma_{nl}\) & 0.76 & 0.00 & \% & \gls{sd} noise level\tabularnewline
 \(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Mean sensor value
@@
 \caption{Sensor noise evaluation results for TLV493D and MMC5603NJ with
-N=2000 samples and no averaging
+N=2000 samples and no averaging.
 \label{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}}
@@
 
-The following figure
+The following Figure
 \ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
@@
 
-The table \ref{Sensor_noise_evaluation_results.csv} lists the measured
+The Table \ref{Sensor_noise_evaluation_results.csv} lists the measured
 values that are extracted from the measurement data of the sensors in
-figure
+Figure
 \ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}.
@@
 The noise of a sensor describes unwanted, random fluctuations or signals
-in the measured data. These are clearly recognisable in the figure
+in the measured data. These are clearly recognisable in the Figure
 \ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
@@
 \emph{\(\sigma_{rv,TLV493D}\)=172.0\({\mu}\)T}, which is twice the value
-given by the datasheet as the noise value (refer to table
+given by the datasheet as the noise value (refer to Table
 \ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}).
@@
 \includegraphics{./generated_images/border_Sensor_evaluation_setup_for_linearity_measurements.png}
-\caption{Sensor evaluation setup for linearity measurements
+\caption{Sensor evaluation setup for linearity measurements.
 \label{Sensor_evaluation_setup_for_linearity_measurements.png}}
@@
 \emph{\(\mu_{trev, 7055BT}\)=21.0\(^{\circ}\)C} in the measurement runs
-and thus corresponds to the same conditions as in the \emph{Background
-Noise} chapter \ref{sensor-characterisation-background-noise} setup.
-
-The figure \ref{Sensor_evaluation_setup_for_linearity_measurements.png}
+and thus corresponds to the same conditions as in the chapter
+\emph{Background Noise} \ref{sensor-characterisation-background-noise}
+setup.
+
+The Figure \ref{Sensor_evaluation_setup_for_linearity_measurements.png}
 contains this updated measurement setup with the added components. To
@@
 \includegraphics{./generated_images/border_Sensor_linearity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
-\caption{Sensor linearity evaluation results for TLV493D and MMC5603NJ
+\caption{Sensor linearity evaluation results for TLV493D and MMC5603NJ.
 \label{Sensor_linearity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}}
@@
 
-The figure
+The Figure
 \ref{Sensor_linearity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
@@
 for which the deviations at the end in particular (with field strengths
-towards zero) are decisive. The previously performed \emph{Background
-Noise} characterisation in chapter
-\ref{sensor-characterisation-background-noise} is explained that the
-linearity deviation is due to the sensitivity of the sensor.
-
-In general, the measured values correspond to the data sheet
-specifications of both sensors, which specify a value of \emph{5\%}. It
-is also feasible to calculate these small deviations using curve fitting
-methods. Suitable functions are implemented in the library.
+towards zero) are decisive. In general, the measured values correspond
+to the data sheet specifications of both sensors, which specify a value
+of \emph{5\%}. It is also feasible to calculate these small deviations
+using curve fitting methods. Suitable functions are implemented in the
+library.
 
@@
 \caption{Sensor evaluation setup for temperature sensitivity
-measurements
+measurements.
 \label{Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}}
@@
 
-The figure
+The Figure
 \ref{Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}
@@
 
-The field of permanent magnets is high temperature-dependent and can
+The field of permanent magnets is highly temperature-dependent and can
 lose its magnetisation at higher temperatures (typically
@@
 \caption{Sensor temperature sensitivity evaluation results for TLV493D
-and MMC5603NJ
+and MMC5603NJ.
 \label{Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}}
@@
 
-The figure
+The Figure
 \ref{Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
@@
 
-In the evaluation (see figure
+In the evaluation (see Figure
 \ref{Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png})
@@
 \begin{longtable}[]{@{}lllll@{}}
-\caption{Overview of all characterised sensor properties
+\caption{Overview of all characterised sensor properties.
 \label{Overview_of_all_characterised_sensor_properties.csv}}\tabularnewline
@@
 measurement\tabularnewline
-\(\mu_{nl}\) & 0.79 & 0.00 & \% & Mean noise level\tabularnewline
-\(\sigma_{nl}\) & 0.76 & 0.00 & \% & \gls{sd} noise level\tabularnewline
 \(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Baseline without offset
@@
 The \emph{TLV493D} performs in noise measurements worse than specified
-in the data sheet (\emph{98\(\mu\)T} instead of \emph{175\(\mu\)T}), but
-the large \gls{dr}, which fulfils the required specifications from
+in the data sheet (\emph{100\(\mu\)T} instead of \emph{175\(\mu\)T}),
+but the large \gls{dr}, which fulfils the required specifications from
 chapter \emph{Research Question} in chapter

### 2024-02-21 documentation/thesis/build_thesis.sh

@@ -70,7 +70,7 @@ do
     TABLENAME="${FNWOE//${replace}/${replacewith}}"
     echo "tablename: $TABLENAME"
     ## INSERT TABLE HEADER AND REF
-    echo ": $TABLENAME \label{$FN}" >> "$f.md"
+    echo ": $TABLENAME. \label{$FN}" >> "$f.md"
     echo "" >> "$f.md"
     ## INSERT TABLE
     csv2md "$f" >> "$f.md"
@@ -111,10 +111,10 @@ do
     touch "$f.md"
     replace="_"
     replacewith=" "
-    IMAGENAME="${FNWOE//${replace}/${replacewith}}"
+    IMAGENAME="${FNWOE//${replace}/${replacewith}}" # CAPTION
     echo "image: $IMAGENAME"
     ## INSERT TABLE HEADER AND REF
-    echo "![$IMAGENAME \label{$FN}]($filenameimageboarder)" >> "$f.md"
+    echo "![$IMAGENAME. \label{$FN}]($filenameimageboarder)" >> "$f.md"
     #echo ": $IMAGENAME \label{$FN}" >> "$f.md"
     echo "" >> "$f.md"
     ## INSERT TABLE

### 2024-02-21 documentation/thesis/thesis_document.tex
.

@@
 
-The Figure
-\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
-summarizes this result. The plot of the raw measured values is
-represented on the left. The value of the determined \emph{GoG} \(\mu\)T
-values is plotted on ten individual measured values. It can be seen that
-there are measured values with larger deviations (see measurement plots
-\emph{7:0},\emph{10-2:0},\emph{10-1:0} in Figure
-\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}).
-
 \begin{figure}
@@
 
-Also, the Figure
+The Figure
 \ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
-illustrates, the measured values are plotted as a result of the filter
-algorithm. As the \emph{IP\_return\_count} parameter is set to four,
-only the four most similar measurements are exported. It can be seen
-from the plotted \emph{\gls{cog}} \(\mu\)T deviation values, that these
-are closest to an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal
-value is calculated with the function
+shows the measured values filtered by the implemented filter algorithm
+of Listing \ref{lst:custom_find_similar_values_algorithm}. It can be
+seen that of the initial \emph{10} measurements (upper plot), only four
+measurements that are most similar to the \emph{\gls{cog}} mean value
+were filtered (lower plot). The number of desired result measurements
+was defined here by the parameter \emph{IP\_return\_count}. It can be
+seen from the plotted \emph{\gls{cog}} \(\mu\)T mean values values, that
+these are closest to an ideal Magnet with a \emph{\gls{cog}} value of
+0\(\mu\)T. This ideal value is calculated with the function
 \emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
-measurement parameters (magnet type, dimensions, sensor distance) as
-they correspond to the mechanical structure of the used hardware sensor
-in chapter \ref{d-full-sphere}.
+measurement parameters (\emph{magnet type}, \emph{dimensions},
+\emph{sensor distance}) as they correspond to the mechanical structure
+of the used hardware sensor in chapter \ref{d-full-sphere}.
+
+It can be seen that there are measured magnets with larger deviations
+(see magnet index plots for \emph{7:0},\emph{10-2:0},\emph{10-1:0} in
+Figure
+\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}).
 
@@
 The filter algorithm implemented by the user is thus successfully
-executed using the user-programmable pipeline. The calculation result is
+executed via the user-programmable pipeline The calculation result was
 successfully verified using raw measurement data and the result of the
-algorithm.
+algorithm and verified using reference measurements. The streamlined
+pipeline approach enables the user to re-execute the implemented
+measurement pipeline example with further measurement data. Changes to
+filter parameters, for example, are also possible without having to
+adapt the code. Using this example, all the required functional
+capabilities from the chapter \emph{Use cases} \ref{use-cases} of this
+implemented solution were demonstrated in their functional capability.
 
@@
 the hardware and software framework for various magnetic field sensors
-is successfully implemented.
-
-In addition, the basic application by the user is demonstrated based on
-an example. Based on this it is possible to systematically characterise
-magnets from the software and readout hardware side by means of data
-acquisition, storage and analysis.
-
-After discussing the developed hardware and software components in
-particular, the following chapter answers the question of whether the
-selected sensors meet the requirements:
+is successfully implemented. In addition, the basic application of the
+framework for the user and the resulting advantages are demonstrated
+using the specific example.
+
+Based on this it is possible to systematically characterise magnets from
+the software and readout hardware side by means of data acquisition,
+storage and analysis.
+
+After the hardware and software components developed have been discussed
+in detail, the following chapter answers the question of which sensors
+fulfill the requirements described in chapter
+\ref{research-question-and-approach}:
 

### 2024-02-22 documentation/thesis/thesis_document.tex
.

@@
 complicated to measure the magnets proactively, prior to the
-finalization of the \gls{mri} system.
+finalization of the \gls{mri} system. \customcite{W14}
 
@@
 
-Finally, a comprehensive hardware and software framework needs to be
-established, which can measure diverse objects using various sensors. In
-addition, comments must be made on the suitability of the sensors used
-for magnetic field measurements.
+A comprehensive hardware and software framework needs to be established,
+which can measure diverse objects using various sensors. In addition,
+comments must be made on the suitability of the sensors used for
+magnetic field measurements.
 
@@
 
+The field of permanent magnets is highly temperature-dependent and can
+lose its magnetisation at higher temperatures (typically
+\emph{\textgreater=80\(^{\circ}\)} for non-high-quality \emph{Type-N}
+magnets \customcite{GKT16}). The temperature range is selected so that it
+lies within a sufficient range for typical subsequent measurement tasks.
+
 The same procedure is used as for the \emph{Linearity} measurement in
@@
 \emph{50\(^{\circ}\)}. Between each of these temperature changes, the
-system is given a waiting time of 30 minutes after reaching the target
-temperature.
-
-The field of permanent magnets is highly temperature-dependent and can
-lose its magnetisation at higher temperatures (typically
-\emph{\textgreater=80\(^{\circ}\)} for non-high-quality \emph{Type-N}
-magnets \customcite{GKT16}). The temperature range is selected so that it
-is within a sufficient range for the application.
+system is given a additional waiting time of \emph{30} minutes after
+reaching the target temperature.
 

### 2024-02-23 src/MagneticReadoutProcessing/MRP/MRPDataVisualization.py
.

@@ -161,7 +161,7 @@ class MRPDataVisualization:
     def inverse_proportional_curve_func(x, a, b, c):
         return a * np.exp(-b * x) + c
     @staticmethod
-    def plot_linearity(_readings: [MRPReading.MRPReading], _title: str = '', _filename: str = None, _unit: str = "$\mu$T", _as_linear_fkt: bool = False, _max_y: int = None):
+    def plot_linearity(_readings: [MRPReading.MRPReading], _title: str = '', _filename: str = None, _unit: str = "$\mu$T", _as_linear_fkt: bool = False, _max_y: int = None,_min_y: int = None):
         """
         Plots the linearity from several readings
 
@@ -276,6 +276,8 @@ class MRPDataVisualization:
 
         if _max_y is not None:
             distance_plot.set_ylim([0, _max_y])
+        if _min_y is not None and _max_y is not None:
+            distance_plot.set_ylim([_min_y, _max_y])
 
         if _as_linear_fkt:
             distance_plot.set_yscale('squareroot')

### 2024-02-23 src/MagneticReadoutProcessing/tests/test_MRPDataVisualization.py

@@ -108,12 +108,11 @@ class TestMPRDataVisualization(unittest.TestCase):
     def test_dynamicrange_realdata(self):
         files = [f for f in os.listdir(self.asset_linearity_folder_path) if re.match(r'(.)*.mag.json', f)]
 
-        sensors:set = set()
+        sensors: set = set()
 
         for e in files:
             sp: [str] = e.split('_')
             sensors.add(sp[0])
-
 
         to_process: dict = {}
         for sensor in sensors:
@@ -153,8 +152,10 @@ class TestMPRDataVisualization(unittest.TestCase):
             e = to_process[k]
 
             total_dst: int = to_process[s]['dist_max'] - to_process[s]['dist_min']
-            reading_name: str = "Dynamic Range of " + k + " using " + str(len(e['files'])-1) + " samples over an distance of {}".format(total_dst) + "mm"
-            export_filename: str = os.path.join(self.result_folder_path, reading_name.replace(" ", "_").replace("mm", "").replace("{}","") + ".png")
+            reading_name: str = "Linearity outside of the manufacturer specified range of " + k
+            export_filename: str = os.path.join(self.result_folder_path,
+                                                reading_name.replace(" ", "_").replace("mm", "").replace("{}",
+                                                                                                         "") + ".png")
 
             # IMPORT READINGS
             readings: [MRPReading.MRPReading] = []
@@ -164,16 +165,21 @@ class TestMPRDataVisualization(unittest.TestCase):
                 if 'tlv493d' in k.lower() and not 'ID230972496757412434' in reading.get_name():
                     reading.set_unit_import_scale_factor(10000.0)
 
-
-
-
                 import_file: str = os.path.join(self.asset_linearity_folder_path, r)
                 reading.load_from_file(import_file)
                 reading.set_name("DISTANCE={}".format(e['distance'][idx]))
+
                 readings.append(reading)
+            my: int = None
+            mx: int = None
+            if 'tlv' in k.lower():
+                mx = 250000
+                my = 100000
+            if 'mmc' in k.lower():
+                mx = 4000
+                my = 2500
 
-
-            MRPDataVisualization.MRPDataVisualization.plot_linearity(readings, reading_name, export_filename, _as_linear_fkt=False)
+            MRPDataVisualization.MRPDataVisualization.plot_linearity(readings, reading_name, export_filename,_as_linear_fkt=False, _min_y=my, _max_y=mx)
 
 
     def test_linearity_realdata(self):

### 2024-02-23 documentation/thesis/thesis_document.tex
.

@@
 principles of nuclear magnetic resonance \gls{nmr} to generate
-cross-sectional black-and-white images of the body. This indispensable
-method plays a significant role in contemporary medicine and research,
-contributing significantly to saving lives. Despite its widespread use,
-traditional \gls{mri} systems often rely on large, heavy, and expensive
-magnets to achieve the necessary homogeneity of the magnetic field for
-accurate imaging. \customcite{NK16}
+cross-sectional images of the body. This indispensable method plays a
+significant role in contemporary medicine and research, contributing
+significantly to saving lives. Despite its widespread use, traditional
+\gls{mri} systems often rely on large, heavy, and expensive magnets to
+achieve the necessary homogeneity of the magnetic field for accurate
+imaging. \customcite{NK16}
 
 Several types of magnets are applicated in different \gls{mri} systems.
-Permanent magnets generate a steady yet relatively weak magnetic field,
-electromagnets are energized by electrical currents and superconducting
-electromagnets produce magnetic fields through electric induction.
 Regardless of the type, the primary objective is to create a homogeneous
@@
 substantial size, weight, and cost. Even when targeting smaller areas of
-the body, large devices are often necessary. In response to this, there
-is a growing interest in developing low-field \gls{mri} systems that
-utilize in many cases permanent magnets. These systems, while offering
-advantages in energy efficiency and reduced complexity, face a
-significant challenge related to the inherent variability in the
-strength of permanent magnets. Achieving homogeneity in the magnetic
-field is crucial for accurate imaging or comparative analyses. While
-typically calculated images have lower resolution due to lower magnetic
-field strength, low-field systems facilitate the comparison of different
-field behaviours and the identification of all kinds of irritations.
-O'Reilly and Teeuwisse and de Gans \customcite{OTW19} have already
-demonstrated low-cost and small-scale implementations with low-field
-\gls{mri} in 2021 calculating images of a head successfully.
+the body, large devices are often necessary with a higher field-strength
+of at least 1.5 T. \customcite{HH21} In response to this, there is a
+growing interest in developing low-field \gls{mri} systems that utilize
+in many cases permanent magnets. Permanent magnets generate a steady yet
+relatively weak magnetic field. These systems, while offering advantages
+in energy efficiency and reduced complexity, face a significant
+challenge related to the inherent variability in the strength of
+permanent magnets. Achieving homogeneity in the magnetic field is
+crucial for accurate imaging or comparative analyses. Low-field systems
+facilitate the comparison of different field behaviours and the
+identification of all kinds of irritations. O'Reilly, Teeuwisse and de
+Gans \customcite{OTW19} have already demonstrated low-cost and small-scale
+implementations with low-field \gls{mri} in 2021 calculating images of a
+head successfully.
 
@@
 For modern medical imaging high-field superconducting magnets dominate
-most \gls{mri} machines, providing in general a higher image contrast.
-The substantial costs, space requirements and safety and installation
+most \gls{mri} machines, providing in general a higher contrast. The
+substantial costs, space requirements and safety and installation
 considerations cause considerable challenges.
@@
 proportional to the magnetic \emph{B0} field; growing magnetic field
-leads automatically to higher \gls{snr}. The initial \emph{B0} field of
-an \gls{mri} aims to be homogeneous, for image acquisition the second
-step requires inhomogeneity of the \emph{B0} field to stimulate spin in
-the atoms of materials. For high resolution images, the initial
-\emph{B0} field aims to be a homogeneous as possible.
+leads automatically to higher \gls{snr}. For high resolution images, the
+initial \emph{B0} field aims to be a homogeneous as possible.
 
@@
 research. The main advantage of low-field \gls{mri}s is the improved
-imaging of soft material, especially when examining joints and muscles.
-It also offers more cost-effective alternatives to high-field \gls{mri}
-systems \customcite{HH21}, cost reduction, a smaller device footprint,
-alleviated safety concerns and leading to diminished image resolution
-within clinically feasible scan durations. \customcite{AFL23}
+contrasting of soft material. It also offers more cost-effective
+alternatives to high-field \gls{mri} systems \customcite{HH21}, cost
+reduction, a smaller device footprint, alleviated safety concerns and
+leading to diminished image resolution within clinically feasible scan
+durations. \customcite{AFL23}
 
@@
 permanent magnets show drawbacks such as high temperature dependence and
-a limited \gls{snr} due to the constrained field strength.
-\customcite{NK16}
+used in \gls{mri}s a limited \gls{snr} due to the constrained field
+strength. \customcite{NK16}
 
@@
 A Halbach ring of this type is usually based on a ring with permanent
-magnets arranged in a circle. The Figure
+magnets arranged in a circle. Figure
 \ref{Example_Halbach_ring_with_cutouts_for_eight_magnets.png} shows an
@@
 
-The sources for the shimming process can be hardware and software based.
-Hardware shimming involves the use of gradient and radio frequency coils
-that are specifically placed to align the magnetic field.
-\customcite{BPA22} Software shimming, on the other hand, uses algorithms
-to adjust the control parameters of the \gls{mri} system and improve
-homogeneity \customcite{WAH21}.
+The sources for the shimming process can be passive and active based.
+Passive shimming uses ferromagnetic metal materials inserted into the
+inner magnet bore. \customcite{BPA22} Active shimming, on the other hand,
+can use additional coils or existing gradient coils controlled by
+special circuitry. Also, software algorithms can be used to adjust the
+control parameters of the \gls{mri} system and improve homogeneity
+\customcite{WAH21}.
 
@@
 impressive homogeneity of \emph{2400 \gls{ppm}} over a \emph{20cm}
-diameter using smaller magnets (\(12 x 12 x 12 mm^3\)). This exceptional
-homogeneity enables the utilization of coil-based gradients for spatial
-encoding, significantly enhancing the flexibility of image acquisition.
+diameter using smaller magnets (\(12 x 12 x 12 mm^3\)). \customcite{OTW19}
 
@@
 field strength of individual magnets and individual measuring points are
-recorded. This data is then evaluated in separate software
-\customcite{WZC21}.
+recorded. \customcite{WZC21}
 
@@
 individual magnet to the finished optimized \gls{cad} model of a Halbach
-ring.
+ring. In addition, it is possible to find a selection of suitable
+magnets whose magnetic field is as identical as possible
 
@@
 
-Two sensors have been meticulously chosen for inclusion in the study.
-The ultimate objective is to assess whether these selected sensors align
-with the stringent criteria of achieving an accuracy level of \emph{1000
-\gls{ppm}}. Furthermore, the study seeks to validate whether the
-measuring range of these sensors appropriately corresponds to the
-required field strength, ensuring their suitability for the intended
+A practical application of the framework is shown, which demonstrates
+the characterization of two magnetic field sensors. For this use case,
+two sensors were selected to be included in the study. The aim is to use
+the framework to verify whether the selected sensors meet the strict
+criteria for an accuracy of \emph{1000 \gls{ppm}}. It is also to check
+whether the measuring range of these sensors corresponds to the required
+field strength and whether they are suitable for the intended
 application.
@@
 the realm of permanent magnets employed for creating a homogeneous
-\emph{B0} field through Halbach rings. Other systems and spin generation
-for measurements are deliberately excluded from consideration but will
-be necessary in later stages of the \emph{DeLoRI} project.
+\emph{B0} field through Halbach rings. Other systems for measurements
+are deliberately excluded from consideration but will be necessary in
+later stages of the \emph{DeLoRI} project.
 
@@
 
-The Figure
+Figure
 \ref{Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}
@@
 Resolution {[}uT{]} & 98 & 0.2 & 0.007 & 48\tabularnewline
-Range {[}mT{]} & ±130.0 & ±0.8 & ±3 & ±50\tabularnewline
+\gls{dr} {[}mT{]} & ±130.0 & ±0.8 & ±3 & ±50\tabularnewline
 Interface & \gls{i2c} & \gls{i2c} & \gls{i2c} & \gls{i2c}\tabularnewline
@@
 
-The Table
+Table
 \ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
@@
 the small number of parts used. The two recesses lock the magnet holder
-with the inserted magnet over the sensor. The specified tolerances allow
-the magnet to be inserted into the holder with repeat accuracy and
-without backlash. This is important if several magnets must be measured,
-where the positioning over the sensor must always be the same.
+with the inserted magnet over the sensor. The mechanical design created
+is able to accommodate cylinders, cubes, up to a maximum length of
+\emph{30mm}. Other magnet shapes require a modification of the base
+plate and the sensor holder. The specified tolerances of \emph{0.45mm}
+allow the magnet to be inserted into the 3D printed holder with repeat
+accuracy and without backlash. This was accomplished with the help of
+tolerance tests for the 3D printing material used \gls{pla} and the 3D
+printer used \emph{Voron 2.4 350mm} through several series of tests.
+This is important if several magnets must be measured, where the
+positioning over the sensor must always be the same.
 
@@
 
-The Figure
+Figure
 \ref{Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}
@@
 \item
-  \gls{mrp}-library, explained in chapter
+  \gls{mrp}-library, is introduced in chapter
   \ref{software-readout-framework}
@@
 \emph{help}, displays a detailed command reference with all available
-commands as shown in the Figure
+commands as shown in Figure
 \ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
@@
 
-The Figure
+Figure
 \ref{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
@@
 used together with the firmware to synchronise the readout intervals.
-The Figure
+Figure
 \ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
@@
 Once the hardware has been prepared, the task of the firmware of each of
-the chained sensors is to find a common synchronisation clock. The
-Figure
+the chained sensors is to find a common synchronisation clock. Figure
 \ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
@@
 sensor operation through the \emph{got impulse within 1000ms} branch
-result. The Figure
+result. Figure
 \ref{Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}
@@
 
-The Table
+Table
 \ref{Build_hardware_sensors_equipped_with_different_sensor_(+ic)s_to_cover_various_magnet_charaterisation_setups.csv}
@@
 
-The Figure
+Figure
 \ref{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full_sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
@@
 For this purpose, the library is divided into individual modules, which
-are shown in the Figure
+are shown in Figure
 \ref{A_high_level_overview_of_all_MRP_library_implemented_Python_modules_which_can_be_changed_by_the_user.png}.
@@
 multiple sensors must be combined into one virtual one. This is done in
-several steps, the procedure described by the following sub-chapters.
+several steps, the procedure is described in the following sub-chapters.
 
@@
 describes the measurement. This is realised in the example using the
-\emph{set\_additional\_data} function. Finally, the measurement is
-exported for archiving and further processing; various export formats
-are available. Using the \emph{dump\_to\_file} function, the measurement
-can be converted into a open \gls{json} format.
+\emph{set\_additional\_data} function. The measurement is exported for
+archiving and further processing; various export formats are available.
+Using the \emph{dump\_to\_file} function, the measurement can be
+converted into a open \gls{json} format.
 
@@
 The main function of the \emph{MRPReading} module is to manage the
-measurement and meta-data. The next step is to record and store real
-sensor data. For this purpose, the \emph{MRPHal} module is developed,
-which can interact with all \emph{Unified Sensor} compatible sensors
-(refer to chapter \ref{unified-sensor}). In the following example
-Listing \ref{lst:mrpexample_hal}, an \emph{1D: Single Sensor}, which is
-explained in chapter \ref{d-single-sensor}, is connected locally to the
-host \gls{pc}. \newpage
+measurement and meta-data. The next step is to record and store data
+points using hardware sensors. For this purpose, the \emph{MRPHal}
+module is developed, which can interact with all \emph{Unified Sensor}
+compatible sensors (refer to chapter \ref{unified-sensor}). In the
+following example Listing \ref{lst:mrpexample_hal}, an \emph{1D: Single
+Sensor}, which is explained in chapter \ref{d-single-sensor}, is
+connected locally to the host \gls{pc}. \newpage
 
@@
 complex evaluation pipelines for measurement data without programming.
-The Figure \ref{Example_measurement_analysis_pipeline.png} shows a
-typical measurement data analysis pipeline, which consists of the
-following steps:
+Figure \ref{Example_measurement_analysis_pipeline.png} shows a typical
+measurement data analysis pipeline, which consists of the following
+steps:
 
@@
 \href{https://magneticreadoutprocessing.readthedocs.io/}{ReadTheDocs}
-service. The Figure
+service. Figure
 \ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
@@
 
-The Figure
+Figure
 \ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
@@
 of Listing \ref{lst:custom_find_similar_values_algorithm}. It can be
-seen that of the initial \emph{10} measurements (upper plot), only four
-measurements that are most similar to the \emph{\gls{cog}} mean value
-were filtered (lower plot). The number of desired result measurements
-was defined here by the parameter \emph{IP\_return\_count}. It can be
-seen from the plotted \emph{\gls{cog}} \(\mu\)T mean values values, that
-these are closest to an ideal Magnet with a \emph{\gls{cog}} value of
-0\(\mu\)T. This ideal value is calculated with the function
-\emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
+seen that out of the initial \emph{10} measurements (upper plot) only
+four measurements that are most similar to the \emph{\gls{cog}} mean
+value are filtered (lower plot). The number of desired result
+measurements are defined here by the parameter \emph{IP\_return\_count}.
+It can be seen from the plotted \emph{\gls{cog}} \(\mu\)T mean values
+are close to an ideal Magnet with a \emph{\gls{cog}} value of 0\(\mu\)T.
+This ideal value is calculated with the function
+\emph{MRP.MRPSimulation.generate\_simulated\_reading}, using the same
 measurement parameters (\emph{magnet type}, \emph{dimensions},
@@
 The filter algorithm implemented by the user is thus successfully
-executed via the user-programmable pipeline The calculation result was
+executed via the user-programmable pipeline. The calculation result is
 successfully verified using raw measurement data and the result of the
@@
 capabilities from the chapter \emph{Use cases} \ref{use-cases} of this
-implemented solution were demonstrated in their functional capability.
+implemented solution are demonstrated in their functional capability.
 
@@
 
-For this evaluation, the sensors listed in the Table
+For this evaluation, the sensors listed in Table
 \ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
@@
 Resolution {[}uT{]} & 98 & 0.007\tabularnewline
-Range {[}mT{]} & ±130.0 & ±3\tabularnewline
+\gls{dr} {[}mT{]} & ±130.0 & ±3\tabularnewline
 Background-Noise {[}uT{]} & 100 & 0.2\tabularnewline
@@
 magnetic field sensors without modifications, including those listed in
-the Table. For this evaluation, the sensors listed in the Table are used
+the table. For this evaluation, the sensors listed in the table are used
 for sensor characterisation. This selection is made for the following
@@
   Linearity
-\item
-  \gls{dr}
 \item
@@
 
-The Figure
+Figure
 \ref{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
@@
 
-The Table \ref{Sensor_noise_evaluation_results.csv} lists the measured
+Table \ref{Sensor_noise_evaluation_results.csv} lists the measured
 values that are extracted from the measurement data of the sensors in
@@
 The noise of a sensor describes unwanted, random fluctuations or signals
-in the measured data. These are clearly recognisable in the Figure
+in the measured data. These are clearly recognisable in Figure
 \ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
@@
 
-The Figure \ref{Sensor_evaluation_setup_for_linearity_measurements.png}
+Figure \ref{Sensor_evaluation_setup_for_linearity_measurements.png}
 contains this updated measurement setup with the added components. To
@@
 
-The Figure
+Figure
 \ref{Sensor_linearity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
-combines the visual representation of linearity as a plot. The distance
-from the magnet to the sensor is plotted in \emph{mm} on the x-axis. The
-measured value of the sensor is plotted on the y-axis. This is not
-directly comparable for both plots, as the sensors have different
-measuring ranges. To ensure comparability, the ideal curve is determined
-\customcite{CSG22}. In order to be able to make quantifiable statements
-about the measurement results, the mean and \gls{sd} deviation of these
-two curves is determined.
+combines the visual representation of linearity as a plot. Only the
+measuring range specified in the sensors data sheet is considered here,
+as linearity is guaranteed for this range. In terms of the
+\emph{TLV493D} this is \emph{0.5\%} and in the case of the
+\emph{MMC5603NJ} \emph{0.1\%}.
+
+The distance from the magnet to the sensor is plotted in \emph{mm} on
+the x-axis. The measured value of the sensor is plotted on the y-axis.
+This is not directly comparable for both plots, as the sensors have
+different measuring ranges. To ensure comparability, the ideal curve is
+determined \customcite{CSG22}. In order to be able to make quantifiable
+statements about the measurement results, the mean and \gls{sd}
+deviation of these two curves is determined.
 
@@
 
-The Figure
+Figure
 \ref{Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}
@@
 
-The Figure
+Figure
 \ref{Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
@@
 temperature coefficients\tabularnewline
-DR & {[}-178;220{]} & {[}-3.1;3.4{]} & \(\mu\)T & maximum linear
-\gls{dr}\tabularnewline
 \bottomrule
@@
 the other hand, is able to measure these ranges with a specified
-\gls{dr} of \emph{±150mT}, but does not achieve the required accuracy
+\gls{dr} of \emph{±130mT}, but does not achieve the required accuracy
 due to strong noise and steep temperature coefficients. In the following

### 2024-02-23 documentation/thesis/thesis_document.tex
.

@@
 Despite their cost-effectiveness in production and maintenance,
-permanent magnets show drawbacks such as high temperature dependence and
-used in \gls{mri}s a limited \gls{snr} due to the constrained field
-strength. \customcite{NK16}
+permanent magnets show drawbacks such as high temperature dependencies.
+\customcite{NK16}
 
@@
 The temperature stability of the \emph{TLV493D} with a mean value of
-20.68\(^{\circ}\)C and a \gls{sd} of
-\(\sigma_{t,TLV493D}\)=0.53\(^{\circ}\)C indicates a consistent trend.
-This implies a constant tendency. The close grouping of the measured
-values around the mean value indicates good stability. The confidence
-interval is expected to be between \emph{20.15\(^{\circ}\)C} and
-\emph{21.21\(^{\circ}\)C}, which indicates a stable and consistent
-temperature measurement. This result is noisier compared to the
-temperature stability of the \emph{MMC5603} with stable
-\emph{\(\mu_{t, MMC5603NJ}\)=0.53\(^{\circ}\)C} with an accuracy of two
-decimal places.
+\emph{20.68\(^{\circ}\)C} and a \gls{sd} of
+\(\sigma_{t,TLV493D}\)=0.53\(^{\circ}\)C shows a strongly noisy
+characteristic with an accuracy of two decimal places. The confidence
+interval varies between \emph{20.15\(^{\circ}\)C} and
+\emph{21.21\(^{\circ}\)C}, which is In contrast to the \emph{MMC5603}
+with stable \emph{19.40\(^{\circ}\)C}, this result is not suitable for
+use, e.g.~for temperature compensation. A second measurement run with
+another \emph{TLV493D} confirms this result.
 
@@
 
-The sensor internal temperature sensors of both tested sensors are
-suitable to perform an ambient temperature compensation of measured
-values and calibration of the sensor. This is considered in chapter
-\emph{Temperature Sensitivity}
+As a result, an external temperature sensor should be used for
+temperature-critical measurements with the \emph{TLV493D}. This is
+considered for the \emph{Temperature Sensitivity} run in chapter
 \ref{sensor-characterisation-temperature-sensitivity}.
-
-Though it is recommended to use a separate temperature sensor when using
-the \emph{TLV493D} or to use a suitable averaging of the temperature and
-measured values in order to perform temperature compensation.
 
@@
 
-In addition, the \gls{dr} for both sensors are measured before the
-measurement run to determine the linearity. In this case, this indicates
-the minimum and maximum linear measuring range for the selected linear
-Hall sensors. A high \gls{dr} enables a more precise detection of
-magnetic fields, while a low \gls{dr} can lead to the sensor detecting
-magnetic fields outside its detection range \customcite{CSG22}.
-
 \hypertarget{measurement-setup}{%
@@
 library.
+
+\hypertarget{dynamic-range-analysis}{%
+\subsection{Dynamic Range Analysis}\label{dynamic-range-analysis}}
+
+\begin{figure}
+\centering
+\includegraphics{./generated_images/border_Sensor_dynamic_range_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
+\caption{Sensor dynamic range evaluation results for TLV493D and
+MMC5603NJ.
+\label{Sensor_dynamic_range_evaluation_results_for_TLV493D_and_MMC5603NJ.png}}
+\end{figure}
+
+With the same setup as for the linearity measurement, the \gls{dr} can
+be determined outside the range specified by the manufacturer. As a
+result, it is possible to analyze how the sensor behaves when the
+defined \gls{dr} is exceeded. This allows the extent to which the limits
+of the sensors can be exhausted to be taken into account in subsequent
+measurement setups. A high \gls{dr} enables a more precise detection of
+magnetic fields, while a low \gls{dr} can lead to the sensor detecting
+magnetic fields outside its detection range.
+
+Figure
+\ref{Sensor_dynamic_range_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
+shows the plot of the linearity measurement outside the specified
+\gls{dr} for the respective sensor. For the \emph{TLV493D} a \gls{dr} of
+almost double the specified \gls{dr} could be measured, with a peak
+value of \emph{240mT} with constant linearity deviation. The
+\emph{MMC5603NJ} measures the same linear values as in the linearity
+measurement. From a measured value of \emph{3.4mT} it reaches a plateau
+and does not increase any further. As a result, the full specified
+\gls{dr} can be fully utilized with both sensors.
+
+This extended characterized \gls{dr} is not used in the further
+analyses. Reference is made exclusively to the values specified by the
+manufacturer, as the values determined do not apply to every sensor
+\gls{ic} of the same type.
 

### 2024-02-26 documentation/colloquium/presentation/index.qmd
.

---
title: "Development of a permanent magnet characterisation framework for use in low-field MRI systems"
subtitle: "FH Aachen – University of Applied Sciences"
author: Marcel Ochsendorf
institute: Faculty of Electrical Enginnering and Information Technology - Information Systems Engineering
date: today
date-format: "dddd, [the] D[<sup style='font-size:65%;font-style:italic;'>th</sup>] [of] MMMM, YYYY"
embed-resources: false
format: coeos-revealjs
---

```{r}
#| include: false
sysfonts::font_add_google("Alegreya Sans", "Alegreya Sans", regular.wt = 300)
showtext::showtext_auto()
source("_extensions/mcanouil/coeos/setup-ggplot2-coeos.R")
```

## Table of Content

## Introduction

* test

## Aim of this Project

## Software Framework

Simply tasks of data:

* data aqusition
* storage
* analysis tasks

---

### Software Concept

test

## Use Cases

# 
<h1 class="r-fit-text" style="text-align: center;">Questions ?</h1>

<table>
<tr><td><p>[<img src="images/github-mark-white.png" alt="image" width="150" height="auto">](https://github.com/LFB-MRI/MagneticReadoutProcessing) </p></td><td><p>[<img src="images/researchgate.svg" alt="image" width="150" height="auto">](https://www.researchgate.net/publication/374388764_Development_of_a_permanent_magnet_characterisation_framework_for_use_in_low-field_MRI_systems) </p><td>[<img src="images/avatar.png" alt="image" width="150" height="auto">](https://marcelochsendorf.com)</td></td></tr>
</table>

### 2024-02-26 documentation/colloquium/_presentation/run_docker_run.sh

@@ -1,0 +1,19 @@
+#!/bin/bash
+cd "$(dirname "$0")"
+
+if [[ "$(docker images -q mrpcolloquium:latest 2> /dev/null)" == "" ]]; then
+  echo "mrpcolloquium:latest IMAGE BUILD STARTED"
+  docker build -t mrpcolloquium:latest .
+else
+ echo "mrpcolloquium:latest IMAGE EXISTS; NO BUILD REQUIRED"
+fi
+
+
+docker run -i --rm -p 8081:8080  \
+    -v "$(pwd)/:/base/" \
+    mrpcolloquium:latest
+   # -v "$(pwd)/images:/base/images" \
+   # -v "$(pwd)/fusumarc.yml:/base/.fusumarc.yml" \
+   # -v "$(pwd)/package.json:/base/package.json" \
+
+

### 2024-02-26 documentation/colloquium/_presentation/slides/scripts/sample.js

@@ -1,0 +1,2 @@
+// Sample.js
+export const Sample = () => <p>Hello from jsx!!</p>;

### 2024-02-26 documentation/colloquium/presentation/run_docker_run.sh

@@ -1,17 +1,0 @@
-#!/bin/bash
-
-if [[ "$(docker images -q mrpcolloquium:latest 2> /dev/null)" == "" ]]; then
-  echo "mrpcolloquium:latest IMAGE BUILD STARTED"
-  docker build -t mrpcolloquium:latest .
-else
- echo "mrpcolloquium:latest IMAGE EXISTS; NO BUILD REQUIRED"
-fi
-
-
-docker run -i --rm -p 8080:8080  \
-    -v "$(pwd)/:/base/" \
-    mrpcolloquium:latest
-   # -v "$(pwd)/images:/base/images" \
-   # -v "$(pwd)/fusumarc.yml:/base/.fusumarc.yml" \
-   # -v "$(pwd)/package.json:/base/package.json" \
-    

### 2024-02-26 documentation/colloquium/_presentation/run.sh
.

@@ -1,23 +1,0 @@
-#! /bin/bash
-export NODE_OPTIONS=--openssl-legacy-provider
-
-env
-
-
-if [[ -z "${FUSUM_EXPORT_ONLY}" ]]; then
-    npx fusuma start
-else
-    # BUILD HTML
-    npx fusuma build
-    mv dist dist_html
-    #  BUILD PDF
-    npx fusuma pdf
-    mv dist dist_pdf
-fi
-
-
-
-
-#npm build
-#npm install fusuma
-#fusuma start

### 2024-02-26 documentation/colloquium/_presentation/run_docker_export.sh

@@ -1,18 +1,0 @@
-#!/bin/bash
-
-if [[ "$(docker images -q mrpcolloquium:latest 2> /dev/null)" == "" ]]; then
-  echo "mrpcolloquium:latest IMAGE BUILD STARTED"
-  docker build -t mrpcolloquium:latest .
-else
- echo "rbegamer/fusuma:latest IMAGE EXISTS; NO BUILD REQUIRED"
-fi
-
-
-docker run -i --rm -p 8080:8080  \
-    -v "$(pwd)/:/base/" \
-    -e FUSUM_EXPORT_ONLY='1' \
-    mrpcolloquium:latest
-   # -v "$(pwd)/images:/base/images" \
-   # -v "$(pwd)/fusumarc.yml:/base/.fusumarc.yml" \
-   # -v "$(pwd)/package.json:/base/package.json" \
-    

### 2024-02-26 documentation/colloquium/_presentation/run_docker_run.sh

@@ -1,19 +1,0 @@
-#!/bin/bash
-cd "$(dirname "$0")"
-
-if [[ "$(docker images -q mrpcolloquium:latest 2> /dev/null)" == "" ]]; then
-  echo "mrpcolloquium:latest IMAGE BUILD STARTED"
-  docker build -t mrpcolloquium:latest .
-else
- echo "mrpcolloquium:latest IMAGE EXISTS; NO BUILD REQUIRED"
-fi
-
-
-docker run -i --rm -p 8081:8080  \
-    -v "$(pwd)/:/base/" \
-    mrpcolloquium:latest
-   # -v "$(pwd)/images:/base/images" \
-   # -v "$(pwd)/fusumarc.yml:/base/.fusumarc.yml" \
-   # -v "$(pwd)/package.json:/base/package.json" \
-
-

### 2024-02-26 documentation/colloquium/_presentation/slides/scripts/sample.js

@@ -1,2 +1,0 @@
-// Sample.js
-export const Sample = () => <p>Hello from jsx!!</p>;

### 2024-02-26 documentation/colloquium/presentation/index.qmd
added first quarto slides

@@
 
-## Table of Content
-
 ## Introduction
@@
 
-## Software Framework
+---
 
-Simply tasks of data:
+##
 
-* data aqusition
-* storage
-* analysis tasks
+<h1 class="r-fit-text" style="text-align: center;">MagneticReadoutProcessing</h1>
 
@@
 
-### Software Concept
+##
 
-test
+<h1 class="r-fit-text" style="text-align: center;">MagneticReadoutProcessing</h1>
+
+Provides and user-oriented **open** magnetic field data hardware and software framework:
+
+* Harware support for several magnetic field sensors
+* Easy to integrate into existing projects
+* Easy to extend
+
+---
+
+### Hardware Framework
+
+---
+
+### Software Framework
+
+Simply tasks of:
+
+* data aqusition
+* data storage
+* data analysis tasks
+
+---
+
+### User Interaction Points
+
+![](images/MRP_high_level_overview.png)
+
+---
+
+### Usability Improvements
+
+<p class="fragment">Fade in</p>
+<p class="fragment fade-out">Fade out</p>
+<p class="fragment highlight-red">Highlight red</p>
+<p class="fragment fade-in-then-out">Fade in, then out</p>
+<p class="fragment fade-up">Slide up while fading in</p>
+
+---
 
 ## Use Cases
+
+### Sensor Chraterisation
 

### 2024-02-26 documentation/colloquium/presentation/run_build.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+cd "$(dirname "$0")"
+
+docker build -t mrppresentation:latest .
+
+#docker run --rm -it -v $(pwd):/presentation mrppresentation:latest /bin/bash -c 'cd /presentation && quarto render'
+docker run --rm -it mrppresentation:latest /bin/bash -c 'cd /presentation && quarto render'
+docker run --rm -it mrppresentation:latest /bin/bash -c 'cd /presentation && quarto render --to pdf --toc'
+

### 2024-02-26 documentation/colloquium/presentation/run_server.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+cd "$(dirname "$0")"
+
+docker build -t mrppresentation:latest .
+
+#docker run --rm -it -p 8800:8800 -v $(pwd):/presentation mrppresentation:latest /bin/bash -c 'cd /presentation && quarto preview index.qmd --to coeos-revealjs --no-browser --port 8800 --host 0.0.0.0'
+docker run --rm -it -p 8800:8800 mrppresentation:latest /bin/bash -c 'cd /presentation && quarto preview index.qmd --to coeos-revealjs --no-browser --port 8800 --host 0.0.0.0'

### 2024-02-27 documentation/colloquium/presentation/index.qmd
.

--- 2024-02-26 documentation/colloquium/presentation/index.qmd
@@
 
-## Software Framework
+---
 
-Simply tasks of data:
+##
 
-* data aqusition
-* storage
-* analysis tasks
+<h1 class="r-fit-text" style="text-align: center;">MagneticReadoutProcessing</h1>
+
+<p class="fragment">Provides and user-oriented **open** magnetic field data hardware and software framework:</p>
+<br />
+<p class="fragment">&#x2022; Harware support for several magnetic field sensors</p>
+<br />
+<p class="fragment">&#x2022; Easy to integrate into existing projects</p>
+<br />
+<p class="fragment">&#x2022; Easy to extend</p>
 
@@
 
-### Software Concept
+### Hardware Framework
 
-test
+![](images/3D_sensor.png)
+
+---
+
+### Hardware Framework
+
+Cheap and easy to construct using consumer grade magnetic field sensors:
+<br />
+<p class="fragment">&#x2022; One software for most common digital magnetic field sensors</p>
+<br />
+<p class="fragment">&#x2022; Synchronised multi sensor setups</p>
+<br />
+<p class="fragment">&#x2022; Universal and interachangable magnet mount</p>
+
+<aside class="notes">
+    In der software sind aktuelll 8 typische sensoren hinterlegt.
+    Magnet mount für viele Magnetformen anpassbar, ohne dass die sensor hardware geaendert werden muss
+</aside>
+
+---
+
+### Software Framework
+
+Simply tasks of:
+
+* data aqusition using hardware sensors
+* data storage
+* data analysis tasks
+
+---
+
+### User Interaction Points
+
+![](images/MRP_high_level_overview.png)
+
+---
+
+### User Interaction Points
+
+Allows rapid development of software analysation functions, witout implementation of typical data processing pipelines needed by providing:
+
+<br />
+<p class="fragment">&#x2022; Expandable open datatypes for magnetic field data</p>
+<br />
+<p class="fragment">&#x2022; Prebuild pipelines ready for customisation</p>
+<br />
+<p class="fragment">&#x2022; Full online documentation, tested library and user tutorials</p>
+
+---
 
 ## Use Cases
+
+Two pratical application of the framework will be shown using two examples:
+
+<br />
+<p class="fragment">&#x2022; Characterization of a *MM5603NJ* and determination of background noise and temperature linearity</p>
+<br />
+<p class="fragment">&#x2022; Usage of the chrakterised sensor for sorting permanent magnets</p>
+
+<aside class="notes">
+    Es wurden wärend der Arbeit weitere Sensoren chrakterisiert, es wird jedoch nur dieser sensor als beispiel genommen.
+    Mittels der chraktisierung im vorfeld ist eine genauerer chrakterisierung der Magnete möglich.
+
+</aside>
+---
+
+### Sensor Chraterisation
+
+![](images/MRP_high_level_overview.png)
+
+<aside class="notes">
+    Grafik zeigt den vereinfachten Aufbau welcher für die Chrakterisierung verwendet wurde.
+    Platte zeigen, verschiedene Sensoren wurden unter den geleichen bedingungen vermessen.
+</aside>
+
+---
+
+### Manget Sorting
+
+<aside class="notes">
+    Die Sortierung wird anhand einer Demo des Frameworks durchgeführt.
+    Dabei werden die sensor charakterisiungsdaten verwendet
+    Hierbei wird eine preconfiguierte Pipeline verwendet.
+    Das ergebnis wird am ende eine reduktion der vermessenen Magnete sein.
+    Somit kann dann ein optimierter hallbach ring generiert werden um so die homogentität zu verbessern
+</aside>
+
+---
+
+#### DEMO: MRPCli
+
+![](images/MRPCli.gif)
+
+---
+
+#### DEMO: MRPUdpp
+
+![](images/MRPUdpp.gif)
+
+---
+
+## Conclusion
+
+---
 

### 2024-02-27 documentation/colloquium/presentation/index.qmd
.

@@
 
+<aside class="notes">
+    *
+    Folgend ein paar beispiele
+</aside>
+
 ---
@@
 
-![](images/3D_sensor.png)
+::: {.container}
+:::: {.col}
+<h4 style="text-align: center;">3D Rotational Sensor</h4>
+::::
+:::
+
+::: {.container}
+:::: {.col}
+<img src="images/3D_sensor.png" alt="image" height="320px">
+::::
+
+:::: {.col}
+<img src="images/3D_sensor_measurement.png" alt="image" height="320px" >
+::::
+:::
+
+---
+
+### Hardware Framework
+
+::: {.container}
+:::: {.col}
+<h4 style="text-align: center;">1D Static Sensor</h4>
+::::
+:::
+
+::: {.container}
+:::: {.col}
+<img src="images/1D_sensor.png" alt="image" height="320px">
+::::
+
+:::: {.col}
+<img src="images/1D_sensor_measurement.png" alt="image" height="320px" >
+::::
+:::
 
@@
 
-* data aqusition using hardware sensors
+*
+* data aqusition
 * data storage
@@
 
-![](images/MRP_high_level_overview.png)
+![](images/Sensor_evaluation_setup_for_linearity_measurements.png)
 
@@
 </aside>
+
+---
+
+### *MM5603NJ* chraterisation results
 
@@
 
+* Generate automated measurement using hardware sensors
+* Save results to filesystem for later analysation
+
 ![](images/MRPCli.gif)
@@
 #### DEMO: MRPUdpp
+
+* Execution of pre-configured analysation and pipeline
+* User implements filter algorithm only
 
@@
 <table>
-<tr><td><p>[<img src="images/github-mark-white.png" alt="image" width="150" height="auto">](https://github.com/LFB-MRI/MagneticReadoutProcessing) </p></td><td><p>[<img src="images/researchgate.svg" alt="image" width="150" height="auto">](https://www.researchgate.net/publication/374388764_Development_of_a_permanent_magnet_characterisation_framework_for_use_in_low-field_MRI_systems) </p><td>[<img src="images/avatar.png" alt="image" width="150" height="auto">](https://marcelochsendorf.com)</td></td></tr>
+<tr><td><p>[<img src="images/github-mark-white.png" alt="image" width="150" height="auto">](https://github.com/LFB-MRI/MagneticReadoutProcessing) </p></td><td><p>[<img src="images/researchgate.svg" alt="image" width="150" height="auto">](https://www.researchgate.net/publication/374388764_Development_of_a_permanent_magnet_characterisation_framework_for_use_in_low-field_MRI_systems) </p><td>[<img src="images/avatar.png" alt="image" width="150" height="auto">](https://marcelochsendorf.com)</td><td><p>[<img src="images/pypi.svg" alt="image" width="150" height="auto">](https://pypi.org/project/MagneticReadoutProcessing/) </p></td><td><p>[<img src="images/rtd.png" alt="image" width="150" height="auto">](https://magneticreadoutprocessing.readthedocs.io/en/latest/) </p></td></tr>
 </table>

### 2024-02-27 documentation/colloquium/presentation/index.qmd
.

@@
 <aside class="notes">
+* dazu wurde das MRP framework erstellt
+* welche die folgenden Probleme behen soll:
+
 *
-    Folgend ein paar beispiele
+
+</aside>
+
+---
+
+### Hardware Framework
+
+Cheap and easy to construct sensors using consumer grade magnetic field sensors:
+<br />
+<p class="fragment">&#x2022; One software for most common digital magnetic field sensors</p>
+<br />
+<p class="fragment">&#x2022; Synchronised multi sensor setups</p>
+<br />
+<p class="fragment">&#x2022; Universal and interachangable magnet mount</p>
+<br />
+<p class="fragment">&#x2022; **Open** hardware designs</p>
+
+<aside class="notes">
+* es werden 8 von den günstigen sensoren verwendet
+* diese werden in ähnlichen projketen verwendet
+* Magnet mount für viele Magnetformen anpassbar
+* ohne dass die sensor hardware geaendert werden muss
 </aside>
@@
 
-### Hardware Framework
+### Software Framework
 
-Cheap and easy to construct using consumer grade magnetic field sensors:
+Allows rapid development of software analysation functions, without implementation of typical data processing pipelines needed by providing:
+
 <br />
-<p class="fragment">&#x2022; One software for most common digital magnetic field sensors</p>
+<p class="fragment">&#x2022; Expandable **open** datatypes for magnetic field data</p>
 <br />
-<p class="fragment">&#x2022; Synchronised multi sensor setups</p>
+<p class="fragment">&#x2022; Prebuild analysis pipelines ready for user customisation</p>
 <br />
-<p class="fragment">&#x2022; Universal and interachangable magnet mount</p>
+<p class="fragment">&#x2022; Full online documentation, CI tested and user tutorials</p>
 
 <aside class="notes">
-    In der software sind aktuelll 8 typische sensoren hinterlegt.
-    Magnet mount für viele Magnetformen anpassbar, ohne dass die sensor hardware geaendert werden muss
+* messdaten und meta-daten management
+* integration zu magpylib, matlab, 
 </aside>
-
----
-
-### Software Framework
-
-Simply tasks of:
-
-*
-* data aqusition
-* data storage
-* data analysis tasks
 
@@
 
----
-
-### User Interaction Points
-
-Allows rapid development of software analysation functions, witout implementation of typical data processing pipelines needed by providing:
-
-<br />
-<p class="fragment">&#x2022; Expandable open datatypes for magnetic field data</p>
-<br />
-<p class="fragment">&#x2022; Prebuild pipelines ready for customisation</p>
-<br />
-<p class="fragment">&#x2022; Full online documentation, tested library and user tutorials</p>
+<aside class="notes">
+* nutzer kann jeden punkt implementieren ohne die komplette pipelines zu implemtieren
+* 
+* dieses konzept wird im folgenden demonstriert an zwei usecases
+</aside>
 
@@
 <br />
-<p class="fragment">&#x2022; Characterization of a *MM5603NJ* and determination of background noise and temperature linearity</p>
+<p class="fragment">&#x2022; Characterization of a *MM5603NJ* and *TLV493D* to measure background noise, temperature coefficients and linearity</p>
 <br />
-<p class="fragment">&#x2022; Usage of the chrakterised sensor for sorting permanent magnets</p>
+<p class="fragment">&#x2022; Usage of the chrakterised sensor for sorting permanent magnets and measure magnetic fields</p>
 
 <aside class="notes">
-    Es wurden wärend der Arbeit weitere Sensoren chrakterisiert, es wird jedoch nur dieser sensor als beispiel genommen.
-    Mittels der chraktisierung im vorfeld ist eine genauerer chrakterisierung der Magnete möglich.
-
+* dazu wurde das entwicklete framework verwendet
+* voll automatisiert
+* diese sensoren als beispiel für die in anderen arbeiteten verwendeten sensoren
+* diese wie TLV wurden nur anhand von Datenblatt chrakterisiert
+* Ergebnisse werden bei der magnet chrakterisierung verwendet
 </aside>
@@
 
-### Sensor Chraterisation
+### Sensor Chraterisation Setup
 
@@
 <aside class="notes">
-    Grafik zeigt den vereinfachten Aufbau welcher für die Chrakterisierung verwendet wurde.
-    Platte zeigen, verschiedene Sensoren wurden unter den geleichen bedingungen vermessen.
+* vereinfachter aufbau
+* sensorplatte zeigen
+* gleiche befdinungen
+* zweites set an sensoren
 </aside>
@@
 
-### *MM5603NJ* chraterisation results
+### Chraterisation results : Noise
+
+::: {.container}
+:::: {.col}
+<img src="images/eval/n_mmc.png" alt="image" >
+::::
+
+:::: {.col}
+<img src="images/eval/n_tlv.png" alt="image" >
+::::
+:::
+
+<aside class="notes">
+* TLV abweichung 0.2C (bitsprüunge) => nicht für temperatur compensation zu nutzen
+* TLV mehr als doppelt so hoch wie im datenblatt (12bit 4096/260mT)
+* Ergebnisse mit einem zweiten set an sensoren verifiziert
+* MMC im noise weit unter datenblatt
+</aside>
+
+---
+
+### Chraterisation results : Temperature
+
+::: {.container}
+:::: {.col}
+<img src="images/eval/t_mmc.png" alt="image" >
+::::
+
+:::: {.col}
+<img src="images/eval/t_tlv.png" alt="image" >
+::::
+:::
+
+<aside class="notes">
+* Temperaturen wurden mit ref thermometer erstellt.
+* TLV doppelt so steil liegt bei 5% jedoch im Datenblatt zum drift
+</aside>
+
+---
+
+### Chraterisation results : Dynamic Range
+
+::: {.container}
+:::: {.col}
+<img src="images/eval/dr_mmc.png" alt="image" >
+::::
+
+:::: {.col}
+<img src="images/eval/dr_tlv.png" alt="image" >
+::::
+:::
+
+<aside class="notes">
+
+* DR am äußeren messbreich weiterhin gut
+* gleiche aussehende abweichung weisst anfängliche fehler im messaufbau hin
+
+</aside>
 
@@
 
+![](images/magnet_sorting_pipeline.png)
+
+1. Configure sensor and measurement parameters
+2. Run measurement
+3. Implement custom filter function
+4. Run analysation pipeline using custom algorithm
+
 <aside class="notes">
-    Die Sortierung wird anhand einer Demo des Frameworks durchgeführt.
-    Dabei werden die sensor charakterisiungsdaten verwendet
-    Hierbei wird eine preconfiguierte Pipeline verwendet.
-    Das ergebnis wird am ende eine reduktion der vermessenen Magnete sein.
-    Somit kann dann ein optimierter hallbach ring generiert werden um so die homogentität zu verbessern
+
+* Ziel: automatisierten Sortieren von Magneten um dann spätereinen Hallbach ring zu erstellen
+* Diese Daten dann in optimierungsalgorithmen zu verwenden.
+* Vordefinierte Pipeline verwendet
+* Die X besten Magnete sollen anhand mittelwert sollen zurueckgegben werden
 </aside>
@@
 
-#### DEMO: MRPCli
+#### Manget Sorting - DEMO MRP
+
+* Simple installation using pip
+* Commandline interface available system wide
+* Compatible with Docker and CI pipelines
+
+![](images/MRP.gif)
+
+---
+
+#### Manget Sorting - DEMO MRPCli
 
@@
 
-#### DEMO: MRPUdpp
+#### Manget Sorting - DEMO MRPUdpp
 
@@
 
----
-
 # 

### 2024-02-27 documentation/colloquium/presentation/images/render_terminalizer.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+cd "$(dirname "$0")"
+
+for i in *.yml; do
+    [ -f "$i" ] || break
+
+    terminalizer render -o "${i%.*}.gif" -q 100 "$i"
+done

### 2024-02-27 documentation/colloquium/presentation/index.qmd
.

@@
 
-* test
+## Lets build an MRI
 
@@
 <br />
+<p class="fragment">&#x2022; Ready to use data analysis pipelines</p>
+<br />
 <p class="fragment">&#x2022; Easy to integrate into existing projects</p>
@@
 * welche die folgenden Probleme behen soll:
-
-*
+* viele derzeitigen magnetfeldmessungen in low field mrt bereich verwenden magentfeld sensoren
+* datenanalyse pipelines sind identsisch bis auf einzelne algorithmen
+* gemeinsame grundlage soll geschaffen werden um solche optimierungsalgorithmen verlgeichen zu können
 
@@
 
+* The implemented framework was successfully used to automatically record and analyze measurement data
+* Characterized sensors are only conditionally suitable for measuring low field MRI B0 fields
+* Implementation of other sensor types required for a wider use of the implemented solution
+
+<aside class="notes">
+* dies liegt vorallem an dem Messbereich und Aufloesung
+* implementierung von besonders analogen sensoren ist notwendig um die geforderten genauigkeiten von B0 feldern genauigkeiten zu vermessen
+
+* verbreitung des frameworks durch integration in bestehende optimierungs projekte such as the MRIHallbachDesigner
+
+</aside>
+
 # 

### 2024-02-27 documentation/colloquium/presentation/index.qmd
.

--- 2024-02-27 documentation/colloquium/presentation/index.qmd
@@
 author: Marcel Ochsendorf
-institute: Faculty of Electrical Enginnering and Information Technology - Information Systems Engineering
+institute: Faculty of Electrical Engineering and Information Technology - Information Systems Engineering
 date: today
@@
 
-* test
+::: {.container}
+:::: {.col}
+<h4 style="text-align: center;"><img style="text-align: center;" src="images/open_source_magnetic_resonance_imaging_projects_MagnetLUMC_feature.png" alt="image"></h4>
+::::
+:::
 
-## Aim of this Project
+<aside class="notes">
+* stellen wir uns vor wir möchten ein kleines MRT
+* dazu benötigen wir einen möglichst homogenen magneten welcher das Hauptfeld erzeugt.
+* B0 oder Nullgradient stellt die resonanzbedingungen her = spinausrichtung
+
+* für kleine Feldstärken von <0.3T = niederfeld
+* ist es möglich diesen aus vielen kleinen permanent Magneten zu bauen (s bild)
+</aside>
+
+## Problem
+
+<br />
+
+<p class="fragment">&#x2022; Permanent magnets differ in their field strength due to their manufacture process and environmental changes</p>
+
+<p class="fragment">&#x2022; This influences the homogeneity of the assembled magnet</p>
+
+<p class="fragment">&#x2022; This influences the homogeneity of the assembled magnet</p>
+<p class="fragment">&#x2022; It can be improved by means of a complex shimming process</p>
+
+<aside class="notes">
+* das problem  herstellung physik diese Magnete
+* nicht optimal für die gemsamt homogenität
+* mittels shimming im nachhinein = auswändig
+* GIBT ES EINEN BESSEREN PROZESS ?
+</aside>
+
+---
+
+## Solution
+
+<p class="fragment"> Measure magnets in advance</p>
+<p class="fragment"> Execute optimization or sorting algorithms on the magnet field data</p>
+<p class="fragment"> Buld an optimized magnet</p>
+
+<hr>
+
+::: {.container}
+:::: {.col}
+<h4 style="text-align: center;">BUT</h4>
+::::
+:::
+
+<hr>
+
+<p class="fragment">Projects exists that follow this approach but only implement individual parts</p>
+<p class="fragment">Incompatible dataformats</p>
+<p class="fragment">Complex magnetic field sensor integrations</p>
+<p class="fragment">Usage of non opensource software</p>
+<aside class="notes">
+* diverse projekte welche einzelne algrothmen dazu haben
+* jedoch nicht kompatible zueinander
+
+DESWEGEN: wurde entwickelt
+</aside>
 
@@
 <br />
-<p class="fragment">&#x2022; Easy to integrate into existing projects</p>
+<p class="fragment">&#x2022; Ready to use data analysis pipelines</p>
 <br />
-<p class="fragment">&#x2022; Easy to extend</p>
+<p class="fragment">&#x2022; Easy to integrate and extend into existing projects</p>
 
@@
 * welche die folgenden Probleme behen soll:
-
-*
-
+* viele derzeitigen magnetfeldmessungen in low field mrt bereich verwenden magentfeld sensoren
+* datenanalyse pipelines sind identsisch bis auf einzelne algorithmen
+* gemeinsame grundlage soll geschaffen werden um solche optimierungsalgorithmen verlgeichen zu können
 </aside>
@@
 <br />
+<br />
 <p class="fragment">&#x2022; One software for most common digital magnetic field sensors</p>
@@
 <p class="fragment">&#x2022; Universal and interachangable magnet mount</p>
-<br />
-<p class="fragment">&#x2022; **Open** hardware designs</p>
 
@@
 * ohne dass die sensor hardware geaendert werden muss
+</aside>
+
+---
+
+### Hardware Framework
+
+::: {.container}
+:::: {.col}
+<h4 style="text-align: center;">1D Static Sensor</h4>
+::::
+:::
+
+::: {.container}
+:::: {.col}
+<img src="images/1D_sensor.png" alt="image" height="320px">
+::::
+
+:::: {.col}
+<img src="images/1D_sensor_measurement.png" alt="image" height="320px" >
+::::
+:::
+
+<aside class="notes">
+* einfachster möglicher sensor
+* nur ein microcontroller und der mangetfeld sensor
 </aside>
@@
 
----
-
-### Hardware Framework
-
-::: {.container}
-:::: {.col}
-<h4 style="text-align: center;">1D Static Sensor</h4>
-::::
-:::
-
-::: {.container}
-:::: {.col}
-<img src="images/1D_sensor.png" alt="image" height="320px">
-::::
-
-:::: {.col}
-<img src="images/1D_sensor_measurement.png" alt="image" height="320px" >
-::::
-:::
+<aside class="notes">
+* kartographiert den eingesetzten magneten
+* zeigt interaktion mit einem manipulator
+* 3D Karte des feldes
+</aside>
 
@@
 
-Allows rapid development of software analysation functions, without implementation of typical data processing pipelines needed by providing:
+Allows rapid development of software analysation functions, without implementation of typical data processing pipelines providing:
 
@@
 * messdaten und meta-daten management
-* integration zu magpylib, matlab, 
+* integration zu andern projekten magpylib, matlab, 
+* analysepipeline schauen wir uns später an
+* volle doku, getestet
+
 </aside>
@@
 * nutzer kann jeden punkt implementieren ohne die komplette pipelines zu implemtieren
-* 
 * dieses konzept wird im folgenden demonstriert an zwei usecases
@@
 
-Two pratical application of the framework will be shown using two examples:
+Two examples are used to demonstrate the practical application of the framework:
 
@@
 <aside class="notes">
-
 * DR am äußeren messbreich weiterhin gut
+* TLV bleibt linearbis hin zum doppelten des messbereichs
+* nicht gültig für andere chips
 * gleiche aussehende abweichung weisst anfängliche fehler im messaufbau hin
-
 </aside>
@@
 <aside class="notes">
-
 * Ziel: automatisierten Sortieren von Magneten um dann spätereinen Hallbach ring zu erstellen
@@
 
+* The implemented framework was successfully used to automatically record and analyze measurement data
+* Characterized sensors are only conditionally suitable for measuring low field MRI B0 fields
+* Implementation of other sensor types required for a wider use of the implemented solution
+
+<aside class="notes">
+* dies liegt vorallem an dem Messbereich und Aufloesung
+* implementierung von besonders analogen sensoren ist notwendig um die geforderten genauigkeiten von B0 feldern genauigkeiten zu vermessen
+* verbreitung des frameworks durch integration in bestehende optimierungs projekte such as the MRIHallbachDesigner
+</aside>
+
 # 

### 2024-02-27 documentation/colloquium/presentation/index.qmd
.

@@
 
-<p class="fragment">&#x2022; Permanent magnets differ in their field strength due to their manufacture process and environmental changes</p>
-
-<p class="fragment">&#x2022; This influences the homogeneity of the assembled magnet</p>
-
+<p class="fragment">&#x2022; Permanent magnets differ in their field strength due to their manufacturing process and environmental changes</p>
 <p class="fragment">&#x2022; This influences the homogeneity of the assembled magnet</p>
@@
 
-<p class="fragment"> Measure magnets in advance</p>
-<p class="fragment"> Execute optimization or sorting algorithms on the magnet field data</p>
-<p class="fragment"> Buld an optimized magnet</p>
+<p class="fragment">&#x2022; Measure magnets in advance</p>
+<p class="fragment">&#x2022; Execute optimization or sorting algorithms on the magnet field data</p>
+<p class="fragment">&#x2022; Build an optimized magnet</p>
+
+<aside class="notes">
+* diverse projekte welche einzelne algrothmen dazu haben
+* jedoch nicht kompatible zueinander
+
+DESWEGEN: wurde entwickelt
+</aside>
+
+---
+
+---
+
+## Solution
+
+<p class="">&#x2022; Measure magnets in advance</p>
+<p class="">&#x2022; Execute optimization or sorting algorithms on the magnet field data</p>
+<p class="">&#x2022; Build an optimized magnet</p>
 
@@
 
-<p class="fragment">Projects exists that follow this approach but only implement individual parts</p>
-<p class="fragment">Incompatible dataformats</p>
-<p class="fragment">Complex magnetic field sensor integrations</p>
-<p class="fragment">Usage of non opensource software</p>
+<p class="fragment">&#x2022; Existing projects follow this approach but only implement individual parts</p>
+<p class="fragment">&#x2022; Incompatible data-formats</p>
+<p class="fragment">&#x2022; Complex magnetic field sensor integrations</p>
+<p class="fragment">&#x2022; Usage of non open source software</p>
 <aside class="notes">
@@
 
-<p class="fragment">Provides and user-oriented **open** magnetic field data hardware and software framework:</p>
+<p class="fragment">Provides and user-oriented **open** magnetic field hardware and software framework:</p>
 <br />
-<p class="fragment">&#x2022; Harware support for several magnetic field sensors</p>
+<p class="fragment">&#x2022; Hardware support for several magnetic field sensors</p>
 <br />
@@
 
-Cheap and easy to construct sensors using consumer grade magnetic field sensors:
+Cheap and easy to construct magnetic field sensors:
 <br />
@@
 <br />
-<p class="fragment">&#x2022; Universal and interachangable magnet mount</p>
+<p class="fragment">&#x2022; Universal and interchangeable mount for different magnet shapes</p>
 
@@
 
-Allows rapid development of software analysation functions, without implementation of typical data processing pipelines providing:
+Provides rapid development of analysis functions without the need to implement typical data processing pipelines:
 
@@
 <aside class="notes">
+* mit der hardware können wird magnetfeld daten aufnehmen
+* jetzt fehlt noch die software dazu
 * messdaten und meta-daten management

### 2024-02-27 documentation/colloquium/presentation/index.qmd
.

@@
 <br />
-<p class="fragment">&#x2022; Expandable **open** datatypes for magnetic field data</p>
+<p class="fragment">&#x2022; Expandable **open** data types for magnetic field data</p>
 <br />
@@
 <br />
-<p class="fragment">&#x2022; Full online documentation, CI tested and user tutorials</p>
+<p class="fragment">&#x2022; Full online documentation,tests and user tutorials</p>
 
@@
 <br />
-<p class="fragment">&#x2022; Characterization of a *MM5603NJ* and *TLV493D* to measure background noise, temperature coefficients and linearity</p>
+<p class="fragment">&#x2022; Characterisation of a *MM5603NJ* and *TLV493D* to measure background noise, temperature coefficients and linearity</p>
 <br />
-<p class="fragment">&#x2022; Usage of the chrakterised sensor for sorting permanent magnets and measure magnetic fields</p>
+<p class="fragment">&#x2022; Usage of the chracterised sensor for sorting permanent magnets and measure magnetic fields</p>
 
@@
 <aside class="notes">
-* vereinfachter aufbau
+* vereinfachter aufbau fuer alle gleich
 * sensorplatte zeigen
@@
 <aside class="notes">
+* aufgenommen weil
 * TLV abweichung 0.2C (bitsprüunge) => nicht für temperatur compensation zu nutzen
@@
 
-### Manget Sorting
+### Magnet Sorting
 
@@
 
-#### Manget Sorting - DEMO MRP
+#### Magnet Sorting - DEMO MRP
 
@@
 
-#### Manget Sorting - DEMO MRPCli
+#### Magnet Sorting - DEMO MRPCli
 
@@
 
-#### Manget Sorting - DEMO MRPUdpp
+#### Magnet Sorting - DEMO MRPUdpp
 
@@
 
-* The implemented framework was successfully used to automatically record and analyze measurement data
-* Characterized sensors are only conditionally suitable for measuring low field MRI B0 fields
+* The implemented framework is successfully used to automatically record and analyse measurement data
+* Characterised sensors are only conditionally suitable for measuring low field MRI fields
 * Implementation of other sensor types required for a wider use of the implemented solution

### 2024-02-27 documentation/colloquium/presentation/index.qmd
.

@@
 
+### Sensor Chraterisation Setup
+
+::: {.container}
+:::: {.col}
+<p style="text-align: center;"><img style="text-align: center;" src="images/eval.png" alt="image" height="270px"></p>
+::::
+:::
+
+|                       | TLV493D | MMC5603NJ |
+| --------------------- | ------- | --------- |
+| Temperature-Sensor    | yes     | yes       |
+| Resolution [uT]       | 98      | 0.007     |
+| Dynamic Range [mT]    | ±130.0  | ±3        |
+| Background-Noise [uT] | 100     | 0.2       |
+
+</p>
+
+<aside class="notes">
+* unterschiedliche messbereiche
+*
+</aside>
+
+---
+
 ### Chraterisation results : Noise
@@
 <aside class="notes">
+* TLV: 98uT MMC: 0.007uT
 * aufgenommen weil
@@
 <aside class="notes">
+* TLV: keine Angabe
 * Temperaturen wurden mit ref thermometer erstellt.
@@
 <aside class="notes">
+* TLV: 130mT MMC: 3mT
 * DR am äußeren messbreich weiterhin gut

### 2024-02-27 documentation/colloquium/presentation/index.qmd
.

@@
 * unterschiedliche messbereiche
-*
+* sind diese passend für die magnet chrakterisierung bis zu welchem grad
 </aside>
@@
 :::: {.col}
-<img src="images/eval/n_mmc.png" alt="image" >
+<img src="images/eval/n_tlv.png" alt="image" >
 ::::
@@
 :::: {.col}
-<img src="images/eval/n_tlv.png" alt="image" >
+<img src="images/eval/n_mmc.png" alt="image" >
 ::::
@@
 * TLV: 98uT MMC: 0.007uT
-* aufgenommen weil
+* rauschen gibt untere greenze an
 * TLV abweichung 0.2C (bitsprüunge) => nicht für temperatur compensation zu nutzen
@@
 :::: {.col}
-<img src="images/eval/t_mmc.png" alt="image" >
+<img src="images/eval/t_tlv.png" alt="image" >
 ::::
@@
 :::: {.col}
-<img src="images/eval/t_tlv.png" alt="image" >
+<img src="images/eval/t_mmc.png" alt="image" >
 ::::
@@
 :::: {.col}
-<img src="images/eval/dr_mmc.png" alt="image" >
+<img src="images/eval/dr_tlv.png" alt="image" >
 ::::
@@
 :::: {.col}
-<img src="images/eval/dr_tlv.png" alt="image" >
+<img src="images/eval/dr_mmc.png" alt="image" >
 ::::

### 2024-02-28 documentation/colloquium/presentation/index.qmd
.

@@
 <br />
-<p class="fragment">&#x2022; Characterisation of a *MM5603NJ* and *TLV493D* to measure background noise, temperature coefficients and linearity</p>
+<p class="fragment">&#x2022; Characterisation of a *MM5603NJ* and *TLV493D* to measure background noise, temperature coefficients and dynamic range</p>
 <br />

### 2024-02-28 src/MagneticReadoutProcessing/MRPcli/cli_measure.py

@@ -1,6 +1,5 @@
 import os
 from pathlib import Path
-from typing import Annotated, List
 import typer
 from MRPcli import cli_helper
 from MRPcli import cli_datastorage
@@ -93,7 +92,7 @@ def perform_measurement(configname: str, alternativefilename: str = "", generate
 
 
 @app.command()
-def run(ctx: typer.Context, configname: Annotated[str, typer.Argument()] = "", alternativefilename: str = "", generate_plots: bool = False, ignoreinvalid: bool = False, ignoremeasurementerror: bool = True):
+def run(ctx: typer.Context, configname: str, alternativefilename: str = "", generate_plots: bool = False, ignoreinvalid: bool = False, ignoremeasurementerror: bool = True):
 
     configs:[str] = []
     if configname is not None and len(configname) > 0:

### 2024-02-28 src/MagneticReadoutProcessing/MRPcli/cli_proxy.py

@@ -2,7 +2,6 @@ import random
 import signal
 import string
 import time
-from typing import Annotated
 import typer
 import socket
 import sys
@@ -41,8 +40,8 @@ def getMachine_addr():
     return ''.join(random.choices(string.ascii_lowercase + string.digits, k=10))
 
 @app.command()
-def start(ctx: typer.Context, advertised_port: Annotated[int, typer.Argument()] = 10001,
-          advertised_sensor_id: Annotated[str, typer.Argument()] = ""):
+def start(ctx: typer.Context, advertised_port: int = 10001,
+          advertised_sensor_id: str = ""):
     sock = socket.socket(socket.AF_INET, socket.SOCK_DGRAM)
     server_address = ('', 9434)
 

### 2024-02-28 src/MagneticReadoutProcessing/MRPcli/cli_sensor.py

@@ -8,7 +8,7 @@ app = typer.Typer()
 
 
 @app.command()
-def info(ctx: typer.Context, configname: Annotated[str, typer.Argument()]):
+def info(ctx: typer.Context, configname: str):
 
     sensor_connection: MRPHal.MRPHal = cli_helper.create_hal_instance_using_config(_configname=configname)
 
@@ -23,7 +23,7 @@ def info(ctx: typer.Context, configname: Annotated[str, typer.Argument()]):
 
 
 @app.command()
-def query(ctx: typer.Context, configname: Annotated[str, typer.Argument()]):
+def query(ctx: typer.Context, configname: str):
     sensor_connection: MRPHal.MRPHal = cli_helper.create_hal_instance_using_config(_configname=configname)
     sensor_connection.connect()
     caps = sensor_connection.get_sensor_capabilities()

### 2024-02-28 src/MagneticReadoutProcessing/setup.py

@@ -10,7 +10,7 @@ with pathlib.Path(req_path).open() as requirements_txt:
     install_requires = [str(requirement) for requirement in pkg_resources.parse_requirements(requirements_txt)]
 
 setup(name='MagneticReadoutProcessing',
-      version='1.9.3',
+      version='1.9.4',
       license='Apache 2',
       description='This library was created for the Low-Field MRI project and allows processing of data measured by magnetic field sensors. The focus is on visualization, followed by the provision of simple interfaces to work with this data. In general its possible to use this lib on all kinds of sensor data.',
       author='Marcel Ochsendorf',

### 2024-02-28 documentation/colloquium/presentation/index.qmd
a

@@
 
-## Solution
-
-<p class="">&#x2022; Measure magnets in advance</p>
-<p class="">&#x2022; Execute optimization or sorting algorithms on the magnet field data</p>
-<p class="">&#x2022; Build an optimized magnet</p>
-
-<hr>
-
-::: {.container}
-:::: {.col}
-<h4 style="text-align: center;">BUT</h4>
-::::
-:::
-
-<hr>
+## But
 
@@
 <p class="fragment">&#x2022; Usage of non open source software</p>
+
 <aside class="notes">

### 2024-02-28 documentation/colloquium/presentation/index.qmd
Update index.qmd

@@
 
-<p class="fragment">&#x2022; Permanent magnets differ in their field strength due to their manufacturing process and environmental changes</p>
+<p class="fragment">&#x2022; Permanent magnets differ in their field strength due to the manufacturing process and environmental changes</p>
 <p class="fragment">&#x2022; This influences the homogeneity of the assembled magnet</p>
@@
 <p class="fragment">&#x2022; Measure magnets in advance</p>
-<p class="fragment">&#x2022; Execute optimization or sorting algorithms on the magnet field data</p>
-<p class="fragment">&#x2022; Build an optimized magnet</p>
+<p class="fragment">&#x2022; Execute optimisation or sorting algorithms on the magnetic field data</p>
+<p class="fragment">&#x2022; Build an optimised magnet</p>
 
@@
 
----
-
-## But
+## ... but
 
